\subsubsection{Crodlu, Heavy Warmount}
\begin{MonsterStats}
{Large Animal}
{6d8+30 (57 hp)}
{+3}
{12 m (8 squares)}
{18 ($-1$ size, +3 Dex, +6 natural), touch 12, flat-footed 15}
{+4/+15}
{Claw +10 melee (1d8+7)}
{2 claw +10 melee (1d8+7) and bite +5 melee (1d8+3)}
{3 m/1.5 m}
{Improved grab, pounce, rake 1d8+3}
{Low-light vision, scent}
{Fort +10, Ref +8, Will +3}
{Str 24, Dex 17, Con 20, Int 2, Wis 13, Cha 7}
{\skill{Jump} +21, \skill{Listen} +6, \skill{Move Silently} +6, \skill{Spot} +2}
{\feat{Alertness}, \feat{Endurance}, \feat{Improved Natural Attack} (claw), \feat{Run}\textsuperscript{B}}
{Plains}
{Herd (5--30)}
{4}
{None}
{Always neutral}
{7--12 HD (Lage)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    The heavy warmount crodlu, also known as the war crodlu, is a breed of crodlu reared for its superior Strength, armor and weaponry. Occasionally used as heavy beasts of burden, war crodlu are most frequently put to use in combat as mounts for specially trained cavalry. Heavier and slower than the regular and heavy crodlus, the heavy warmount crodlu makes up for these weaknesses through its proven usefulness to sorcerer-monarch, merchant house and nomad alike.

    Heavy warmount crodlu have the same ecology as other crodlu but are never found in the wild. War crodlu are bred exclusively through animal husbandry and are commensurately expensive.
}

Heavy warmount crodlu are fearless and formidable foes, striking at the slightest provocation, unless their riders and handlers keep their belligerent natures in check. They prefer to charge an enemy and then unleash a devastating flurry of claws and snapping jaws. They are steady on their feet, allowing for mounted attacks by their riders.

\textbf{Improved Grab (Ex):} To use this ability, a heavy warmount crodlu must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can rake.

\textbf{Pounce (Ex):} If a heavy warmount crodlu charges a foe, it can make a full attack, including two rake attacks.

\textbf{Rake (Ex):} Attack bonus +10 melee, damage 1d8+3.

\textbf{Skills:} Heavy crodlu receive a +10 racial bonus on Jump checks and a -4 penalty on Spot checks.
