\subsection{Sample Traps}
The costs listed for mechanical traps are market prices; those for magic traps are raw material costs. Caster level and class for the spells used to produce the trap effects are provided in the entries for magic device traps and spell traps. For all other spells used (in triggers, for example), the caster level is assumed to be the minimum required.

\subsubsection{CR 1 Traps}
\textbf{Basic Arrow Trap:} CR 1; mechanical; proximity trigger; manual reset; Atk +10 ranged (1d6/$\times$3, arrow); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 2,000 cp.

\textbf{Camouflaged Pit Trap:} CR 1; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 3 m deep (1d6, fall); \skill{Search} DC 24; \skill{Disable Device} DC 20. Market Price: 1,800 cp.

\textbf{Deeper Pit Trap:} CR 1; mechanical; location trigger; manual reset; hidden switch bypass (\skill{Search} DC 25); DC 15 Reflex save avoids; 6 m deep (2d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); \skill{Search} DC 20; \skill{Disable Device} DC 23. Market Price: 1,300 cp.

\textbf{Fusillade of Darts:} CR 1; mechanical; location trigger; manual reset; Atk +10 ranged (1d4+1, dart); multiple targets (fires 1d4 darts at each target in two adjacent 1.5 m squares); \skill{Search} DC 14; \skill{Disable Device} DC 20. Market Price: 500 cp.

\textbf{Poison Dart Trap:} CR 1; mechanical; location trigger; manual reset; Atk +8 ranged (1d4 plus poison, dart); poison (bloodroot, DC 12 Fortitude save resists, 0/1d4 Con plus 1d3 Wis); \skill{Search} DC 20; \skill{Disable Device} DC 18. Market Price: 700 cp.

\textbf{Poison Needle Trap:} CR 1; mechanical; touch trigger; manual reset; Atk +8 ranged (1 plus greenblood oil poison); \skill{Search} DC 22; \skill{Disable Device} DC 20. Market Price: 1,300 cp.

\textbf{Portcullis Trap:} CR 1; mechanical; location trigger; manual reset; Atk +10 melee (3d6); \skill{Search} DC 20; \skill{Disable Device} DC 20. Note: Damage applies only to those underneath the portcullis. Portcullis blocks passageway. Market Price: 1,400 cp.

\textbf{Razor-Wire across Hallway:} CR 1; mechanical; location trigger; no reset; Atk +10 melee (2d6, wire); multiple targets (first target in each of two adjacent 1.5 m squares); \skill{Search} DC 22; \skill{Disable Device} DC 15. Market Price: 400 cp.

\textbf{Rolling Rock Trap:} CR 1; mechanical; location trigger; manual reset; Atk +10 melee (2d6, rock); \skill{Search} DC 20; \skill{Disable Device} DC 22. Market Price: 1,400 cp.

\textbf{Scything Blade Trap:} CR 1; mechanical; location trigger; automatic reset; Atk +8 melee (1d8/$\times$3); \skill{Search} DC 21; \skill{Disable Device} DC 20. Market Price: 1,700 cp.

\textbf{Spear Trap:} CR 1; mechanical; location trigger; manual reset; Atk +12 ranged (1d8/$\times$3, spear); \skill{Search} DC 20; \skill{Disable Device} DC 20. Note: 60 m max range, target determined randomly from those in its path. Market Price: 1,200 cp.

\textbf{Swinging Block Trap:} CR 1; mechanical; touch trigger; manual reset; Atk +5 melee (4d6, stone block); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 500 cp.

\textbf{Wall Blade Trap:} CR 1; mechanical; touch trigger; automatic reset; hidden switch bypass (\skill{Search} DC 25); Atk +10 melee (2d4/$\times$4, scythe); \skill{Search} DC 22; \skill{Disable Device} DC 22. Market Price: 2,500 cp.

\subsubsection{CR 2 Traps}
\textbf{Box of Brown Mold:} CR 2; mechanical; touch trigger (opening the box); automatic reset; 1.5 m cold aura (3d6, cold nonlethal); \skill{Search} DC 22; \skill{Disable Device} DC 16. Market Price: 3,000 cp.

\textbf{Bricks from Ceiling:} CR 2; mechanical; touch trigger; repair reset; Atk +12 melee (2d6, bricks); multiple targets (all targets in two adjacent 1.5 m squares); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 2,400 cp.

\textbf{Burning Hands Trap:} CR 2; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{burning hands}, 1st-level wizard, 1d4 fire, DC 11 Reflex save half damage); \skill{Search} DC 26; \skill{Disable Device} DC 26. Cost: 500 cp, 40 XP.

\textbf{Camouflaged Pit Trap:} CR 2; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 6 m deep (2d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); \skill{Search} DC 24; \skill{Disable Device} DC 19. Market Price: 3,400 cp.

\textbf{Inflict Light Wounds Trap:} CR 2; magic device; touch trigger; automatic reset; spell effect (\spell{inflict light wounds}, 1st-level cleric, 1d8+1, DC 11 Will save half damage); \skill{Search} DC 26; \skill{Disable Device} DC 26. Cost: 500 cp, 40 XP.

\textbf{Javelin Trap:} CR 2; mechanical; location trigger; manual reset; Atk +16 ranged (1d6+4, javelin); \skill{Search} DC 20; \skill{Disable Device} DC 18. Market Price: 4,800 cp.

\textbf{Large Net Trap:} CR 2; mechanical; location trigger; manual reset; Atk +5 melee (see note); \skill{Search} DC 20; \skill{Disable Device} DC 25. Note: Characters in 3-m square are grappled by net (Str 18) if they fail a DC 14 Reflex save. Market Price: 3,000 cp.

\textbf{Pit Trap:} CR 2; mechanical, location trigger; manual reset; DC 20 Reflex save avoids; 12 m deep (4d6, fall); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 2,000 cp.

\textbf{Poison Needle Trap:} CR 2; mechanical; touch trigger; repair reset; lock bypass (\skill{Open Lock} DC 30); Atk +17 melee (1 plus poison, needle); poison (blue whinnis, DC 14 Fortitude save resists (poison only), 1 Con/unconsciousness); \skill{Search} DC 22; \skill{Disable Device} DC 17. Market Price: 4,720 cp.

\textbf{Spiked Pit Trap:} CR 2; mechanical; location trigger; automatic reset; DC 20 Reflex save avoids; 6 m deep (2d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+2 each); \skill{Search} DC 18; \skill{Disable Device} DC 15. Market Price: 1,600 cp.

\textbf{Tripping Chain:} CR 2; mechanical; location trigger; automatic reset; multiple traps (tripping and melee attack); Atk +15 melee touch (trip), Atk +15 melee (2d4+2, spiked chain); \skill{Search} DC 15; \skill{Disable Device} DC 18. Market Price: 3,800 cp. Note: This trap is really one CR 1 trap that trips and a second CR 1 trap that attacks with a spiked chain. If the tripping attack succeeds, a +4 bonus applies to the spiked chain attack because the opponent is prone.

\textbf{Well-Camouflaged Pit Trap:} CR 2; mechanical; location trigger; repair reset; DC 20 Reflex save avoids; 3 m deep (1d6, fall); \skill{Search} DC 27; \skill{Disable Device} DC 20. Market Price: 4,400 cp.

\subsubsection{CR 3 Traps}
\textbf{Burning Hands Trap:} CR 3; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{burning hands}, 5th-level wizard, 5d4 fire, DC 11 Reflex save half damage); \skill{Search} DC 26; \skill{Disable Device} DC 26. Cost: 2,500 cp, 200 XP.

\textbf{Camouflaged Pit Trap:} CR 3; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 9 m deep (3d6, fall); multiple targets (first target in each of two adjacent squares); \skill{Search} DC 24; \skill{Disable Device} DC 18. Market Price: 4,800 cp.

\textbf{Ceiling Pendulum:} CR 3; mechanical; timed trigger; automatic reset; Atk +15 melee (1d12+8/$\times$3, greataxe); \skill{Search} DC 15; \skill{Disable Device} DC 27. Market Price: 14,100 cp.

\textbf{Fire Trap:} CR 3; spell; spell trigger; no reset; spell effect (\spell{fire trap}, 3rd-level druid, 1d4+3 fire, DC 13 Reflex save half damage); \skill{Search} DC 27; \skill{Disable Device} DC 27. Cost: 85 cp to hire NPC spellcaster.

\textbf{Extended Bane Trap:} CR 3; magic device; proximity trigger (\spell{detect good}); automatic reset; spell effect (\emph{extended} \spell{bane}, 3rd-level cleric, DC 13 Will save negates); \skill{Search} DC 27; \skill{Disable Device} DC 27. Cost: 3,500 cp, 280 XP.

\textbf{Ghoul Touch Trap:} CR 3; magic device; touch trigger; automatic reset; spell effect (\spell{ghoul touch}, 3rd-level wizard, DC 13 Fortitude save negates); \skill{Search} DC 27; \skill{Disable Device} DC 27. Cost: 3,000 cp, 240 XP.

\textbf{Hail of Needles:} CR 3; mechanical; location trigger; manual reset; Atk +20 ranged (2d4); \skill{Search} DC 22; \skill{Disable Device} DC 22. Market Price: 5,400 cp.

\textbf{Acid Arrow Trap:} CR 3; magic device; proximity trigger (\spell{alarm}); automatic reset; Atk +2 ranged touch; spell effect (\spell{acid arrow}, 3rd-level wizard, 2d4 acid/round for 2 rounds); \skill{Search} DC 27; \skill{Disable Device} DC 27. Cost: 3,000 cp, 240 XP.

\textbf{Pit Trap:} CR 3; mechanical, location trigger; manual reset; DC 20 Reflex save avoids; 18 m deep (6d6, fall); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 3,000 cp.

\textbf{Poisoned Arrow Trap:} CR 3; mechanical; touch trigger; manual reset; lock bypass (\skill{Open Lock} DC 30); Atk +12 ranged (1d8 plus poison, arrow); poison (Large monstrous scorpion venom, DC 14 Fortitude save resists, 1d4 Con/1d4 Con); \skill{Search} DC 19; \skill{Disable Device} DC 15. Market Price: 2,900 cp.

\textbf{Spiked Pit Trap:} CR 3; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 6 m deep (2d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+2 each); \skill{Search} DC 21; \skill{Disable Device} DC 20. Market Price: 3,600 cp.

\textbf{Stone Blocks from Ceiling:} CR 3; mechanical; location trigger; repair reset; Atk +10 melee (4d6, stone blocks); \skill{Search} DC 25; \skill{Disable Device} DC 20. Market Price: 5,400 cp.

\subsubsection{CR 4 Traps}
\textbf{Bestow Curse Trap:} CR 4; magic device; touch trigger (\spell{detect chaos}); automatic reset; spell effect (\spell{bestow curse}, 5th-level cleric, DC 14 Will save negates); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 8,000 cp, 640 XP.

\textbf{Camouflaged Pit Trap:} CR 4; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 12 m deep (4d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); \skill{Search} DC 25; \skill{Disable Device} DC 17. Market Price: 6,800 cp.

\textbf{Collapsing Column:} CR 4; mechanical; touch trigger (attached); no reset; Atk +15 melee (6d6, stone blocks); \skill{Search} DC 20; \skill{Disable Device} DC 24. Market Price: 8,800 cp.

\textbf{Glyph of Warding (Blast):} CR 4; spell; spell trigger; no reset; spell effect (\spell{glyph of warding} [blast], 5th-level cleric, 2d8 acid, DC 14 Reflex save half damage); multiple targets (all targets within 1.5 m); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 350 cp to hire NPC spellcaster.

\textbf{Lightning Bolt Trap:} CR 4; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{lightning bolt}, 5th-level wizard, 5d6 electricity, DC 14 Reflex save half damage); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 7,500 cp, 600 XP.

\textbf{Pit Trap:} CR 4; mechanical, location trigger; manual reset; DC 20 Reflex save avoids; 24 m deep (8d6, fall); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 4,000 cp.

\textbf{Poisoned Dart Trap:} CR 4; mechanical; location trigger; manual reset; Atk +15 ranged (1d4+4 plus poison, dart); multiple targets (1 dart per target in a 3-m-by-3-m area); poison (Small monstrous centipede poison, DC 10 Fortitude save resists, 1d2 Dex/1d2 Dex); \skill{Search} DC 21; \skill{Disable Device} DC 22. Market Price: 12,090 cp.

\textbf{Sepia Snake Sigil Trap:} CR 4; spell; spell trigger; no reset; spell effect (\spell{sepia snake sigil}, 5th-level wizard, DC 14 Reflex save negates); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 650 cp to hire NPC spellcaster.

\textbf{Spiked Pit Trap:} CR 4; mechanical; location trigger; automatic reset; DC 20 Reflex save avoids; 18 m deep (6d6, fall); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+5 each); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 4,000 cp.

\textbf{Wall Scythe Trap:} CR 4; mechanical; location trigger; automatic reset; Atk +20 melee (2d4+8/$\times$4, scythe); \skill{Search} DC 21; \skill{Disable Device} DC 18. Market Price: 17,200 cp.

\textbf{Water-Filled Room Trap:} CR 4; mechanical; location trigger; automatic reset; multiple targets (all targets in a 3-m-by-3-m room); never miss; onset delay (5 rounds); liquid; \skill{Search} DC 17; \skill{Disable Device} DC 23. Market Price: 11,200 cp.

\textbf{Wide-Mouth Spiked Pit Trap:} CR 4; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 6 m deep (2d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+2 each); \skill{Search} DC 18; \skill{Disable Device} DC 25. Market Price: 7,200 cp.

\subsubsection{CR 5 Traps}
\textbf{Camouflaged Pit Trap:} CR 5; mechanical; location trigger; manual reset; DC 20 Reflex save avoids; 50 ft. deep (5d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); \skill{Search} DC 25; \skill{Disable Device} DC 17. Market Price: 8,500 cp.

\textbf{Doorknob Smeared with Contact Poison:} CR 5; mechanical; touch trigger (attached); manual reset; poison (nitharit, DC 13 Fortitude save resists, 0/3d6 Con); \skill{Search} DC 25; \skill{Disable Device} DC 19. Market Price: 9,650 cp.

\textbf{Falling Block Trap:} CR 5; mechanical; location trigger; manual reset; Atk +15 melee (6d6); multiple targets (can strike all characters in two adjacent specified squares); \skill{Search} DC 20; \skill{Disable Device} DC 25. Market Price: 15,000 cp.

\textbf{Fire Trap:} CR 5; spell; spell trigger; no reset; spell effect (\spell{fire trap}, 7th-level wizard, 1d4+7 fire, DC 16 Reflex save half damage); \skill{Search} DC 29; \skill{Disable Device} DC 29. Cost: 305 cp to hire NPC spellcaster.

\textbf{Fireball Trap:} CR 5; magic device; touch trigger; automatic reset; spell effect (\spell{fireball}, 8th-level wizard, 8d6 fire, DC 14 Reflex save half damage); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 12,000 cp, 960 XP.

\textbf{Flooding Room Trap:} CR 5; mechanical; proximity trigger; automatic reset; no attack roll necessary (see note below); \skill{Search} DC 20; \skill{Disable Device} DC 25. Note: Room floods in 4 rounds. Market Price: 17,500 cp.

\textbf{Fusillade of Darts:} CR 5; mechanical; location trigger; manual reset; Atk +18 ranged (1d4+1, dart); multiple targets (1d8 darts per target in a 3-m-by-3-m area); \skill{Search} DC 19; \skill{Disable Device} DC 25. Market Price: 18,000 cp.

\textbf{Moving Executioner Statue:} CR 5; mechanical; location trigger; automatic reset; hidden switch bypass (\skill{Search} DC 25); Atk +16 melee (1d12+8/$\times$3, greataxe); multiple targets (both arms attack); \skill{Search} DC 25; \skill{Disable Device} DC 18. Market Price: 22,500 cp.

\textbf{Phantasmal Killer Trap:} CR 5; magic device; proximity trigger (\spell{alarm} covering the entire room); automatic reset; spell effect (\spell{phantasmal killer}, 7th-level wizard, DC 16 Will save for disbelief and DC 16 Fort save for partial effect); \skill{Search} DC 29; \skill{Disable Device} DC 29. Cost: 14,000 cp, 1,120 XP.

\textbf{Pit Trap:} CR 5; mechanical, location trigger; manual reset; DC 20 Reflex save avoids; 30 m deep (10d6, fall); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 5,000 cp.

\textbf{Poison Wall Spikes:} CR 5; mechanical; location trigger; manual reset; Atk +16 melee (1d8+4 plus poison, spike); multiple targets (closest target in each of two adjacent 1.5 m squares); poison (Medium monstrous spider venom, DC 12 Fortitude save resists, 1d4 Str/1d4 Str); \skill{Search} DC 17; \skill{Disable Device} DC 21. Market Price: 12,650 cp.

\textbf{Spiked Pit Trap:} CR 5; mechanical; location trigger; manual reset; DC 25 Reflex save avoids; 12 m deep (4d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+4 each); \skill{Search} DC 21; \skill{Disable Device} DC 20. Market Price: 13,500 cp.

\textbf{Spiked Pit Trap (24 m Deep):} CR 5; mechanical; location trigger, manual reset; DC 20 Reflex save avoids; 24 m deep (8d6, fall), pit spikes (Atk +10 melee, 1d4 spikes for 1d4+5 each); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 5,000 cp.

\textbf{Ungol Dust Vapor Trap:} CR 5; mechanical; location trigger; manual reset; gas; multiple targets (all targets in a 3-m-by-3-m room); never miss; onset delay (2 rounds); poison (ungol dust, DC 15 Fortitude save resists, 1 Cha/1d6 Cha plus 1 Cha drain); \skill{Search} DC 20; \skill{Disable Device} DC 16. Market Price: 9,000 cp.

\subsubsection{CR 6 Traps}
\textbf{Built-to-Collapse Wall:} CR 6; mechanical; proximity trigger; no reset; Atk +20 melee (8d6, stone blocks); multiple targets (all targets in a 3-m-by-3-m area); \skill{Search} DC 14; \skill{Disable Device} DC 16. Market Price: 15,000 cp.

\textbf{Compacting Room:} CR 6; mechanical; timed trigger; automatic reset; hidden switch bypass (\skill{Search} DC 25); walls move together (12d6, crush); multiple targets (all targets in a 3-m by 3-m room); never miss; onset delay (4 rounds); \skill{Search} DC 20; \skill{Disable Device} DC 22. Market Price: 25,200 cp.

\textbf{Flame Strike Trap:} CR 6; magic device; proximity trigger (\spell{detect magic}); automatic reset; spell effect (\spell{flame strike}, 9th-level cleric, 9d6 fire, DC 17 Reflex save half damage); \skill{Search} DC 30; \skill{Disable Device} DC 30. Cost: 22,750 cp, 1,820 XP.

\textbf{Fusillade of Spears:} CR 6; mechanical; proximity trigger; repair reset; Atk +21 ranged (1d8, spear); multiple targets (1d6 spears per target in a 3 m-by-3-m area); \skill{Search} DC 26; \skill{Disable Device} DC 20. Market Price: 31,200 cp.

\textbf{Glyph of Warding (Blast):} CR 6; spell; spell trigger; no reset; spell effect (\spell{glyph of warding} [blast], 16th-level cleric, 8d8 sonic, DC 14 Reflex save half damage); multiple targets (all targets within 1.5 m); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 680 cp to hire NPC spellcaster.

\textbf{Lightning Bolt Trap:} CR 6; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{lightning bolt}, 10th-level wizard, 10d6 electricity, DC 14 Reflex save half damage); \skill{Search} DC 28; \skill{Disable Device} DC 28. Cost: 15,000 cp, 1,200 XP.

\textbf{Spiked Blocks from Ceiling:} CR 6; mechanical; location trigger; repair reset; Atk +20 melee (6d6, spikes); multiple targets (all targets in a 3-m-by-3-m area); \skill{Search} DC 24; \skill{Disable Device} DC 20. Market Price: 21,600 cp.

\textbf{Spiked Pit Trap (30 m Deep):} CR 6; mechanical; location trigger, manual reset; DC 20 Reflex save avoids; 30 m deep (10d6, fall); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+5 each); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 6,000 cp.

\textbf{Whirling Poison Blades:} CR 6; mechanical; timed trigger; automatic reset; hidden lock bypass (\skill{Search} DC 25, \skill{Open Lock} DC 30); Atk +10 melee (1d4+4/19-20 plus poison, dagger); poison (purple worm poison, DC 24 Fortitude save resists, 1d6 Str/2d6 Str); multiple targets (one target in each of three preselected 1.5 m squares); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 30,200 cp.

\textbf{Wide-Mouth Pit Trap:} CR 6; mechanical; location trigger, manual reset; DC 25 Reflex save avoids; 12 m deep (4d6, fall); multiple targets (all targets within a 3-m-by-3-m area); \skill{Search} DC 26; \skill{Disable Device} DC 25. Market Price: 28,200 cp.

\textbf{Wyvern Arrow Trap:} CR 6; mechanical; proximity trigger; manual reset; Atk +14 ranged (1d8 plus poison, arrow); poison (wyvern poison, DC 17 Fortitude save resists, 2d6 Con/2d6 Con); \skill{Search} DC 20; \skill{Disable Device} DC 16. Market Price: 17,400 cp.

\subsubsection{CR 7 Traps}
\textbf{Acid Fog Trap:} CR 7; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{acid fog}, 11th-level wizard, 2d6/round acid for 11 rounds); \skill{Search} DC 31; \skill{Disable Device} DC 31. Cost: 33,000 cp, 2,640 XP.

\textbf{Blade Barrier Trap:} CR 7; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{blade barrier}, 11th-level cleric, 11d6 slashing, DC 19 Reflex save half damage); \skill{Search} DC 31; \skill{Disable Device} DC 31. Cost: 33,000 cp, 2,640 XP.

\textbf{Burnt Othur Vapor Trap:} CR 7; mechanical; location trigger; repair reset; gas; multiple targets (all targets in a 3-m-by-3-m room); never miss; onset delay (3 rounds); poison (burnt othur fumes, DC 18 Fortitude save resists, 1 Con drain/3d6 Con); \skill{Search} DC 21; \skill{Disable Device} DC 21. Market Price: 17,500 cp.

\textbf{Chain Lightning Trap:} CR 7; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{chain lightning}, 11th-level wizard, 11d6 electricity to target nearest center of trigger area plus 5d6 electricity to each of up to eleven secondary targets, DC 19 Reflex save half damage); \skill{Search} DC 31; \skill{Disable Device} DC 31. Cost: 33,000 cp, 2,640 XP.

\textbf{Black Tentacles Trap:} CR 7; magic device; proximity trigger (\spell{alarm}); no reset; spell effect (\spell{black tentacles}, 7th-level wizard, 1d4+7 tentacles, Atk +7 melee [1d6+4, tentacle]); multiple targets (up to six tentacles per target in each of two adjacent 1.5 m squares); \skill{Search} DC 29; \skill{Disable Device} DC 29. Cost: 1,400 cp, 112 XP.

\textbf{Fusillade of Greenblood Oil Darts:} CR 7; mechanical; location trigger; manual reset; Atk +18 ranged (1d4+1 plus poison, dart); poison (greenblood oil, DC 13 Fortitude save resists, 1 Con/ 1d2 Con); multiple targets (1d8 darts per target in a 3-m-by-3-m area); \skill{Search} DC 25; \skill{Disable Device} DC 25. Market Price: 33,000 cp.

\textbf{Lock Covered in Dragon Bile:} CR 7; mechanical; touch trigger (attached); no reset; poison (dragon bile, DC 26 Fortitude save resists, 3d6 Str/0); \skill{Search} DC 27; \skill{Disable Device} DC 16. Market Price: 11,300 cp.

\textbf{Summon Monster VI Trap:} CR 7; magic device; proximity trigger (\spell{alarm}); no reset; spell effect (\spell{summon monster VI}, 11th-level wizard), \skill{Search} DC 31; \skill{Disable Device} DC 31. Cost: 3,300 cp, 264 XP.

\textbf{Water-Filled Room:} CR 7; mechanical; location trigger; manual reset; multiple targets (all targets in a 3-m-by-3-m room); never miss; onset delay (3 rounds); water; \skill{Search} DC 20; \skill{Disable Device} DC 25. Market Price: 21,000 cp.

\textbf{Well-Camouflaged Pit Trap:} CR 7; mechanical; location trigger; repair reset; DC 25 Reflex save avoids; 21 m deep (7d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); \skill{Search} DC 27; \skill{Disable Device} DC 18. Market Price: 24,500 cp.

\subsubsection{CR 8 Traps}
\textbf{Deathblade Wall Scythe:} CR 8; mechanical; touch trigger; manual reset; Atk +16 melee (2d4+8 plus poison, scythe); poison (deathblade, DC 20 Fortitude save resists, 1d6 Con/2d6 Con); \skill{Search} DC 24; \skill{Disable Device} DC 19. Market Price: 31,400 cp.

\textbf{Destruction Trap:} CR 8; magic device; touch trigger (alarm); automatic reset; spell effect (\spell{destruction}, 13th-level cleric, DC 20 Fortitude save for 10d6 damage); \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 45,500 cp, 3,640 XP.

\textbf{Earthquake Trap:} CR 8; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{earthquake}, 13th-level cleric, 65-ft. radius, DC 15 or 20 Reflex save, depending on terrain); \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 45,500 cp, 3,640 XP.

\textbf{Insanity Mist Vapor Trap:} CR 8; mechanical; location trigger; repair reset; gas; never miss; onset delay (1 round); poison (insanity mist, DC 15 Fortitude save resists, 1d4 Wis/2d6 Wis); multiple targets (all targets in a 3-m-by-3-m room); \skill{Search} DC 25; \skill{Disable Device} DC 20. Market Price: 23,900 cp.

\textbf{Acid Arrow Trap:} CR 8; magic device; visual trigger (true seeing); automatic reset; multiple traps (two simultaneous acid arrow traps); Atk +9 ranged touch and +9 ranged touch; spell effect (\spell{acid arrow}, 18th-level wizard, 2d4 acid damage for 7 rounds); \skill{Search} DC 27; \skill{Disable Device} DC 27. Cost: 83,500 cp, 4,680 XP. Note: This trap is really two CR 6 acid arrow traps that fire simultaneously, using the same trigger and reset.

\textbf{Power Word Stun Trap:} CR 8; magic device; touch trigger; no reset; spell effect (\spell{power word stun}, 13th-level wizard), \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 4,550 cp, 364 XP.

\textbf{Prismatic Spray Trap:} CR 8; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{prismatic spray}, 13th-level wizard, DC 20 Reflex, Fortitude, or Will save, depending on effect); \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 45,500 cp, 3,640 XP.

\textbf{Reverse Gravity Trap:} CR 8; magic device; proximity trigger (\spell{alarm}, 3-m area); automatic reset; spell effect (\spell{reverse gravity}, 13th-level wizard, 6d6 fall [upon hitting the ceiling of the 60-ft.- high room], then 6d6 fall [upon falling 18 m to the floor when the spell ends], DC 20 Reflex save avoids damage); \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 45,500 cp, 3,640 XP.

\textbf{Well-Camouflaged Pit Trap:} CR 8; mechanical; location trigger; repair reset; DC 20 Reflex save avoids; 30 m deep (10d6, fall); \skill{Search} DC 27; \skill{Disable Device} DC 18. Market Price: 16,000 cp.

\textbf{Word of Chaos Trap:} CR 8; magic device; proximity trigger (\spell{detect law}); automatic reset; spell effect (\spell{word of chaos}, 13th-level cleric); \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 46,000 cp, 3,680 XP.

\subsubsection{CR 9 Traps}
\textbf{Drawer Handle Smeared with Contact Poison:} CR 9; mechanical; touch trigger (attached); manual reset; poison (black lotus extract, DC 20 Fortitude save resists, 3d6 Con/3d6 Con); \skill{Search} DC 18; \skill{Disable Device} DC 26. Market Price: 21,600 cp.

\textbf{Dropping Ceiling:} CR 9; mechanical; location trigger; repair reset; ceiling moves down (12d6, crush); multiple targets (all targets in a 3-m-by-3-m room); never miss; onset delay (1 round); \skill{Search} DC 20; \skill{Disable Device} DC 16. Market Price: 12,600 cp.

\textbf{Incendiary Cloud Trap:} CR 9; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{incendiary cloud}, 15th-level wizard, 4d6/round for 15 rounds, DC 22 Reflex save half damage); \skill{Search} DC 33; \skill{Disable Device} DC 33. Cost: 60,000 cp, 4,800 XP.

\textbf{Wide-Mouth Pit Trap:} CR 9; mechanical; location trigger; manual reset; DC 25 Reflex save avoids; 30 m deep (10d6, fall); multiple targets (all targets within a 3-m-by-3-m area); \skill{Search} DC 25; \skill{Disable Device} DC 25. Market Price: 40,500 cp.

\textbf{Wide-Mouth Spiked Pit with Poisoned Spikes:} CR 9; mechanical; location trigger; manual reset; hidden lock bypass (\skill{Search} DC 25, \skill{Open Lock} DC 30); DC 20 Reflex save avoids; 21 m deep (7d6, fall); multiple targets (all targets within a 3-m-by-3-m area); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+5 plus poison each); poison (giant wasp poison, DC 14 Fortitude save resists, 1d6 Dex/1d6 Dex); \skill{Search} DC 20; \skill{Disable Device} DC 20. Market Price: 11,910 cp.

\subsubsection{CR 10 Traps}
\textbf{Crushing Room:} CR 10; mechanical; location trigger; automatic reset; walls move together (16d6, crush); multiple targets (all targets in a 3-m-by-3-m room); never miss; onset delay (2 rounds); \skill{Search} DC 22; \skill{Disable Device} DC 20. Market Price: 29,000 cp.

\textbf{Crushing Wall Trap:} CR 10; mechanical; location trigger; automatic reset; no attack roll required (18d6, crush); \skill{Search} DC 20; \skill{Disable Device} DC 25. Market Price: 25,000 cp.

\textbf{Energy Drain Trap:} CR 10; magic device; visual trigger (true seeing); automatic reset; Atk +8 ranged touch; spell effect (\spell{energy drain}, 17th-level wizard, 2d4 negative levels for 24 hours, DC 23 Fortitude save negates); \skill{Search} DC 34; \skill{Disable Device} DC 34. Cost: 124,000 cp, 7,920 XP.

\textbf{Forcecage and Summon Monster VII trap:} CR 10; magic device; proximity trigger (\spell{alarm}); automatic reset; multiple traps (one \spell{forcecage} trap and one \spell{summon monster VII} trap that summons a hamatula); spell effect (\spell{forcecage}, 13th-level wizard), spell effect (\spell{summon monster VII}, 13th-level wizard, hamatula); \skill{Search} DC 32; \skill{Disable Device} DC 32. Cost: 241,000 cp, 7,280 XP. Note: This trap is really one CR 8 trap that creates a \spell{forcecage} and a second CR 8 trap that summons a hamatula in the same area. If both succeed, the hamatula appears inside the \spell{forcecage}. These effects are independent of each other.

\textbf{Poisoned Spiked Pit Trap:} CR 10; mechanical; location trigger; manual reset; hidden lock bypass (\skill{Search} DC 25, \skill{Open Lock} DC 30); DC 20 Reflex save avoids; 50 ft. deep (5d6, fall); multiple targets (first target in each of two adjacent 1.5 m squares); pit spikes (Atk +10 melee, 1d4 spikes per target for 1d4+5 plus poison each); poison (purple worm poison, DC 24 Fortitude save resists, 1d6 Str/2d6 Str); \skill{Search} DC 16; \skill{Disable Device} DC 25. Market Price: 19,700 cp.

\textbf{Wail of the Banshee Trap:} CR 10; magic device; proximity trigger (\spell{alarm}); automatic reset; spell effect (\spell{wail of the banshee}, 17th-level wizard, DC 23 Fortitude save negates); multiple targets (up to 17 creatures); \skill{Search} DC 34; \skill{Disable Device} DC 34. Cost: 76,500 cp, 6,120 XP.
