\subsubsection{How Far Can Your Character Move?}
Your speed is determined by your race and your armor (see \tabref{Tactical Speed}). Your speed while unarmored is your base land speed.

\textbf{Encumbrance:} A character encumbered by carrying a large amount of gear, treasure, or fallen comrades may move slower than normal.

\textbf{Hampered Movement:} Difficult terrain, obstacles, or poor visibility can hamper movement.

\textbf{Movement in Combat:} Generally, you can move your speed in a round and still do something (take a move action and a standard action).

If you do nothing but move (that is, if you use both of your actions in a round to move your speed), you can move double your speed.

If you spend the entire round running, you can move quadruple your speed. If you do something that requires a full round you can only take a 1.5-meter step.

\textbf{Bonuses to Speed:} A barbarian has a +3 meters bonus to his speed (unless he's wearing heavy armor). In addition, many spells and magic items can affect a character's speed. Always apply any modifiers to a character's speed before adjusting the character's speed based on armor or encumbrance, and remember that multiple bonuses of the same type to a character's speed don't stack.

\Table{Tactical Speed}{y{33mm}CC}{
\tableheader Race & \tableheader No Armor or Light Armor & \tableheader Medium or Heavy Armor \\
Elf, half-giant, thri-kreen & 12m(8 squares) & 9m(6 squares) \\
Human, half-elf, mul, pterran & 9m(6 squares) & 6m(4 squares) \\
Dwarf & 6m(4 squares) & 6m(4 squares) \\
Aarakocra, halfling & 6m(4 squares) & 4.5m(3 squares) \\
}