\subsubsection{Moving through a Square}
\textbf{Friend:} You can move through a square occupied by a friendly character, unless you are charging. When you move through a square occupied by a friendly character, that character doesn't provide you with cover.

\textbf{Opponent:} You can't move through a square occupied by an opponent, unless the opponent is helpless. You can move through a square occupied by a helpless opponent without penalty. (Some creatures, particularly very large ones, may present an obstacle even when helpless. In such cases, each square you move through counts as 2 squares.)

\textbf{Ending Your Movement:} You can't end your movement in the same square as another creature unless it is helpless.

\textbf{Overrun:} During your movement you can attempt to move through a square occupied by an opponent.

\textbf{Tumbling:} A trained character can attempt to tumble through a square occupied by an opponent (see the Tumble skill).

\textbf{Very Small Creature:} A Fine, Diminutive, or Tiny creature can move into or through an occupied square. The creature provokes attacks of opportunity when doing so.

\textbf{Square Occupied by Creature Three Sizes Larger or Smaller:} Any creature can move through a square occupied by a creature three size categories larger than it is.

A big creature can move through a square occupied by a creature three size categories smaller than it is.

\textbf{Designated Exceptions:} Some creatures break the above rules. A creature that completely fills the squares it occupies cannot be moved past, even with the Tumble skill or similar special abilities.