\subsubsection{Terrain and Obstacles}
\textbf{Difficult Terrain:} Difficult terrain hampers movement. Each square of difficult terrain counts as 2 squares of movement. (Each diagonal move into a difficult terrain square counts as 3 squares.) You can't run or charge across difficult terrain.

If you occupy squares with different kinds of terrain, you can move only as fast as the most difficult terrain you occupy will allow.

Flying and incorporeal creatures are not hampered by difficult terrain.

\textbf{Obstacles:} Like difficult terrain, obstacles can hamper movement. If an obstacle hampers movement but doesn't completely block it each obstructed square or obstacle between squares counts as 2 squares of movement. You must pay this cost to cross the barrier, in addition to the cost to move into the square on the other side. If you don't have sufficient movement to cross the barrier and move into the square on the other side, you can't cross the barrier. Some obstacles may also require a skill check to cross.

On the other hand, some obstacles block movement entirely. A character can't move through a blocking obstacle.

Flying and incorporeal creatures can avoid most obstacles.

\textbf{Squeezing:} In some cases, you may have to squeeze into or through an area that isn't as wide as the space you take up. You can squeeze through or into a space that is at least half as wide as your normal space. Each move into or through a narrow space counts as if it were 2 squares, and while squeezed in a narrow space you take a $-4$ penalty on attack rolls and a $-4$ penalty to AC.

When a Large creature (which normally takes up four squares) squeezes into a space that's one square wide, the creature's miniature figure occupies two squares, centered on the line between the two squares. For a bigger creature, center the creature likewise in the area it squeezes into.

A creature can squeeze past an opponent while moving but it can't end its movement in an occupied square.

To squeeze through or into a space less than half your space's width, you must use the \skill{Escape Artist} skill. You can't attack while using \skill{Escape Artist} to squeeze through or into a narrow space, you take a $-4$ penalty to AC, and you lose any Dexterity bonus to AC.
