\subsubsection{Special Purpose Items}
Many of the great intelligent items in Athas were created with a special purpose in mind, which gives them and their wielder access to new powers. Most of them were created during the Preserver Jihad and the Cleansing Wars (see \chapref{Other Ages of Play}).

\textbf{Purpose:} An item's purpose must suit the type and alignment of the item and should always be treated reasonably. A purpose of ``defeat/slay arcane spellcasters'' doesn't mean that the sword forces the wielder to kill every wizard she sees. Nor does it mean that the sword believes it is possible to kill every wizard in the world. It does mean that the item hates arcane spellcasters and wants to bring the local wizard's cabal to ruin, as well as end the rule of a sorceress-queen in a nearby land. Likewise, a purpose of ``defend elves'' doesn't mean that if the wielder is an elf, he only wants to help himself. It means that the item wants to be used in furthering the cause of elves, stamping out their enemies and aiding their leaders. A purpose of ``defeat/slay all'' isn't just a matter of self-preservation. It means that the item won't rest (or let its wielder rest) until it places itself above all others.

\Table{Intelligent Item Purpose}{cX}{
  \tableheader d\%
& \tableheader Purpose \\
01--20 & Defeat/slay diametrically opposed alignment\footnotemark[1] \\
21--30 & Defeat/slay arcane spellcasters (including spellcasting monsters and those that use spell-like abilities) \\
31--40 & Defeat/slay divine spellcasters (including divine entities and servitors) \\
41--45 & Defeat/slay manifesters (including manifesting monsters and those that use psi-like abilities) \\
46--50 & Defeat/slay nonspellcasters \\
51--55 & Defeat/slay a particular creature type (see the \emph{bane} special ability for choices) \\
56--60 & Defeat/slay a particular race or kind of creature \\
61--70 & Defend a particular race or kind of creature \\
71--80 & Defeat/slay the servants of a specific deity \\
81--90 & Defend the servants and interests of a specific deity \\
91--95 & Defeat/slay all (other than the item and the wielder) \\
96--100 &  Choose one \\
\TableNote{2}{1 The purpose of the neutral (N) version of this item is to preserve the balance by defeating/slaying powerful beings of the extreme alignments (LG, LE, CG, CE).}
}

