\subsubsection{Items Against Characters}
When an item has an Ego of its own, it has a will of its own. The item is, of course, absolutely true to its alignment. If the character who possesses the item is not true to that alignment's goals or the item's special purpose, personality conflict---item against character---results. Similarly, any item with an Ego score of 20 or higher always considers itself superior to any character, and a personality conflict results if the possessor does not always agree with the item.

When a personality conflict occurs, the possessor must make a Will saving throw (DC = item's Ego). If the possessor succeeds, she is dominant. If she fails, the item is dominant. Dominance lasts for one day or until a critical situation occurs (such as a major battle, a serious threat to either the item or the character, and so on). Should an item gain dominance, it resists the character's desires and demands concessions such as any of the following.

\begin{itemize*}
\item Removal of associates or items whose alignment or personality is distasteful to the item.
\item The character divesting herself of all other magic items or items of a certain type.
\item Obedience from the character so the item can direct where they go for its own purposes.
\item Immediate seeking out and slaying of creatures hateful to the item.
\item Magical protections and devices to protect the item from molestation when it is not in use.
\item That the character carry the item with her on all occasions.
\item That the character relinquish the item in favor of a more suitable possessor due to alignment differences or conduct.
\end{itemize*}

In extreme circumstances, the item can resort to even harsher measures, such as the following acts:
\begin{itemize*}
\item Force its possessor into combat.
\item Refuse to strike opponents.
\item Strike at its wielder or her associates.
\item Force its possessor to surrender to an opponent.
\item Cause itself to drop from the character's grasp.
\end{itemize*}

Naturally, such actions are unlikely when harmony reigns between the character's and item's alignments or when their purposes and personalities are well matched. Even so, an item might wish to have a lesser character possess it in order to easily establish and maintain dominance over him, or a higher-level possessor so as to better accomplish its goals.

All magic items with personalities desire to play an important role in whatever activity is under way, particularly combat. Such items are rivals of each other, even if they are of the same alignment. No intelligent item wants to share its wielder with others. An intelligent item is aware of the presence of any other intelligent item within 60 feet, and most intelligent items try their best to mislead or distract their host so that she ignores or destroys the rival. Of course, alignment might change this sort of behavior.

Items with personalities are never totally controlled or silenced by the characters who possess them, even though they may never successfully control their possessors. They may be powerless to force their demands but remain undaunted and continue to air their wishes and demands.
