\section{Manifesting Powers}
Psionic characters and creatures manifest powers. Whether they cost power points when manifest by a psionic character, or are manifested as psi-like abilities, powers' effects remain the same. The process of manifesting a power is akin to casting a spell, but with significant differences.

\subsection{Choosing A Power}
First you must choose which power to manifest. You can select any power you know, provided you are capable of manifesting powers of that level or higher. To manifest a power, you must pay power points, which count against your daily total. You can manifest the same power multiple times if you have points left to pay for it.

\input{subsections/psionics/manifesting-powers/concentration.tex}

\subsection{Manifester Level}
The variables of a power's effect often depend on its manifester level, which is equal to your psionic class level. A power that can be augmented for additional effect is also limited by your manifester level (you can't spend more power points on a power than your manifester level). See Augment under Descriptive Text, below.

You can manifest a power at a lower manifester level than normal, but the manifester level must be high enough for you to manifest the power in question, and all level-dependent features must be based on the same manifester level.

In the event that a class feature or other special ability provides an adjustment to your manifester level, this adjustment applies not only to all effects based on manifester level (such as range, duration, and augmentation potential) but also to your manifester level check to overcome your target's power resistance and to the manifester level used in dispel checks (both the dispel check and the DC of the check).

\subsection{Power Failure}
If you try to manifest a power in conditions where the characteristics of the power (range, area, and so on) cannot be made to conform, the manifestation fails and the power points are wasted.

Powers also fail if your concentration is broken (see Concentration, above).

\subsection{The Power's Result}
Once you know which creatures (or objects or areas) are affected, and whether those creatures have made successful saving throws (if any were allowed), you can apply whatever results a power entails.

\input{subsections/psionics/manifesting-powers/special-power-effects.tex}
\input{subsections/psionics/manifesting-powers/combining-psionic-and-magical-effects.tex}