\section{Power Descriptions}
The description of each power is presented in a standard format. Each category of information is explained and defined below.

\subsection{Name}
The first line of every power description gives the name by which the power is generally known. A power might be known by other names in some locales, and specific manifesters might have names of their own for their powers.

\input{subsections/psionics/power-descriptions/discipline.tex}

\subsection{[Descriptor]}
Appearing on the same line as the discipline and subdiscipline (when applicable) is a descriptor that further categorizes the power in some way. Some powers have more than one descriptor.

The descriptors that apply to powers are acid, cold, death, electricity, evil, fire, force, good, language-dependent, light, mind-affecting, and sonic.

Most of these descriptors have no game effect by themselves, but they govern how the power interacts with other powers, with spells, with special abilities, with unusual creatures, with alignment, and so on.

A language-dependent power uses intelligible language as a medium.

A mind-affecting power works only against creatures with an Intelligence score of 1 or higher.

\subsection{Level}
The next line of the power description gives a power's level, a number between 1 and 9 that defines the power's relative strength. This number is preceded by the name of the class whose members can manifest the power. If a power is part of a discipline's list instead of the psion's general power list, this will be indicated by the name of the discipline's specialist. The specialists a power can be associated with include Egoist (psychometabolism), Kineticist (psychokinesis), Nomad (psychoportation), Seer (clairsentience), Shaper (metacreativity), and Telepath (telepathy).

\input{subsections/psionics/power-descriptions/display.tex}

\subsection{Manifesting Time}
Most powers have a manifesing time of 1 standard action. Others take 1 round or more, while a few require only a free action.

A power that takes 1 round to manifest requires a full-round action. It comes into effect just before the beginning of your turn in the round after you began manifesting the power. You then act normally after the power is completed.

A power that takes 1 minute to manifest comes into effect just before your turn 1 minute later (and for each of those 10 rounds, you are manifesting a power as a full-round action, as noted above for 1-round manifesting times). These actions must be consecutive and uninterrupted, or the power points are lost and the power fails.

When you use a power that takes 1 round or longer to manifest, you must continue the concentration from the current round to just before your turn in the next round (at least). If you lose concentration before the manifesting time is complete, the power points are lost and the power fails.

You make all pertinent decisions about a power (range, target, area, effect, version, and so forth) when the power comes into effect.

\subsection{Range}
A power's range indicates how far from you it can reach, as defined in the Range entry of the power description. A power's range is the maximum distance from you that the power's effect can occur, as well as the maximum distance at which you can designate the power's point of origin. If any portion of the area would extend beyond the range, that area is wasted. Standard ranges include the following.

\textbf{Personal:} The power affects only you.

\textbf{Touch:} You must touch a creature or object to affect it. A touch power that deals damage can score a critical hit just as a weapon can. A touch power threatens a critical hit on a natural roll of 20 and deals double damage on a successful critical hit. Some touch powers allow you to touch multiple targets. You can touch as many willing targets as you can reach, but all targets of the spell must be touched in the same round that you manifest the power.

% \textbf{Close:} The power reaches as far as 7.5 meters away from you. The maximum range increases 1.5 meter for every two manifester levels you have.

% \textbf{Medium:} The power reaches as far as 30 meters + 3 meters per manifester level.

% \textbf{Long:} The power reaches as far as 120 meters + 12 meters per manifester level.

\textbf{Range Expressed in Meters:} Some powers have no standard range category, just a range expressed in meters.

\input{subsections/psionics/power-descriptions/aiming-a-power.tex}
\input{subsections/psionics/power-descriptions/duration.tex}
\input{subsections/psionics/power-descriptions/saving-throw.tex}

\subsection{Power Resistance}
Power resistance is a special defensive ability. If your power is being resisted by a creature with power resistance, you must make a manifester level check (d20 + manifester level) at least equal to the creature's power resistance for the power to affect that creature. The defender's power resistance functions like an Armor Class against psionic attacks. %Spell resistance is equivalent to power resistance unless the Psionics Is Different option is in use. Include any adjustments to your manifester level on this manifester level check.

The Power Resistance line and the descriptive text of a power description tell you whether power resistance protects creatures from the power. In many cases, power resistance applies only when a resistant creature is targeted by the power, not when a resistant creature encounters a power that is already in place.

The terms ``object'' and ``harmless'' mean the same thing for power resistance as they do for saving throws. A creature with power resistance must voluntarily lower the resistance (a standard action) to be affected by a power noted as harmless. In such a case, you do not need to make the manifester level check described above.

\input{subsections/psionics/power-descriptions/power-points.tex}

\subsection{Descriptive Text}
This portion of a power description details what the power does and how it works. If one of the previous lines in the description included ``see text,'' this is where the explanation is found. If the power you're reading about is based on another power you might have to refer to a different power for the ``see text'' information. If a power is the equivalent of a spell an entry of ``see spell text'' directs you to the appropriate spell description.

\textbf{Augment:} Many powers have variable effects based on the number of power points you spend when you manifest them. The more points spent, the more powerful the manifestation. How this extra expenditure affects a power is specific to the power. Some augmentations allow you to increase the number of damage dice, while others extend a power's duration or modify a power in unique ways. Each power that can be augmented includes an entry giving how many power points it costs to augment and the effects of doing so. However, you can spend only a total number of points on a power equal to your manifester level.

Augmenting a power takes place as part of another action (manifesting a power). Unless otherwise noted in the Augment section of an individual power description, you can augment a power only at the time you manifest it.

