\section{Telepathic Attacks}
In order to use some telepathic powers, you must establish contact with the target's mind. There are two ways to invade someone's mind:

\begin{itemize*}
	\item Using the \psionic{contact} power to reach an open mind (a non-psionic intelligent creature, or a willing psionic creature);
	\item Using one of the five telepathic attacks to open a closed mind (an unwilling psionic creature).
\end{itemize*}

\textbf{Partial Contact:} Whenever you make a successful telepathic attack, you establish partial contact with the target's mind. Once you successfully create three partial contacts, you make full contact. It does not matter which telepathic power was used to make any of the partial contacts. You can only make partial contact with one mind at a time.

\textit{Maintaining Partial Contact:} Each partial contact requires a maintenance cost of 1 power point per round. You do not need to spend power points to maintain full contact. Once a mind is open, you have no need to force yourself into it.

\textbf{Contact:} Once contact is made, either via telepathic attacks or via the \psionic{contact} power, you are able to use some powers that require contacted minds. Telepathic attacks also have specific effects when they target a contacted mind.

\subsection{Attacking}
There are five telepathic powers that can be used to attack a psionic mind: \psionic{ego whip}, \psionic{id insinuation}, \psionic{mind thrust}, \psionic{psionic blast}, and \psionic{psychic crush}. These telepathic attacks share the following characteristics:

\begin{itemize*}
	\item Will save Difficulty Class = 10 + \textit{manifester level}.
	\item You can increase their save DC by up to 4 points.
	\item You can increase their range up to 120 meters.
	\item You can make two power checks with a single manifestation, to make two telepathic attacks against a single mind.
\end{itemize*}

To attack a closed mind, you need to succeed in the power check of the telepathic attack and the target must fail in their saving throw. If you choose a ``two-pronged attack'', each attack requires a separate power check and a separate saving throw.

\subsection{Defending}
Psions have access to a number of telepathic defenses: \psionic{intellect fortress}, \psionic{mental barrier}, \psionic{mind blank}, \psionic{thought shield}, \psionic{tower of iron will}. These psionic powers are universal and available to any psion, no matter which discipline they chose to specialize.

Each telepathic defense apply modifiers to the power check of any telepathic attack that targets you. These modifiers depend on the telepathic attack that is being used, and are described at \tabref{Power Check Modifiers of Telepathic Defenses}. The defenses may hinder the ability of an attacker but they do not grant any bonus or penalty in your saving throw against any telepathic attack.

\Table{Power Check Modifiers of Telepathic Defenses}{l*5{C}}{
& \tableheader \psionic{Intellect Fortress}
& \tableheader \psionic{Mental Barrier}
& \tableheader \psionic{Mind Blank}
& \tableheader \psionic{Thought Shield}
& \tableheader \psionic{Tower of Iron Will} \\
\psionic{Ego Whip}       & $-4$ & $-3$ &  +5  &  +0  & $-3$ \\
\psionic{Id Insinuation} & $-1$ &  +4  & $-3$ &  +2  & $-3$ \\
\psionic{Mind Thrust}    & $-4$ & $-4$ &  +5  & $-2$ & $-5$ \\
\psionic{Psionic Blast}  & $-1$ &  +0  &  +2  &  +3  & $-2$ \\
\psionic{Psychic Crush}  & $-3$ & $-1$ &  +1  & $-3$ & $-4$ \\
}

\subsection{Psychic Contest}

\textbf{Example:} An attacker is using \psionic{ego whip}. The defender has erected a \psionic{mental barrier}. The attacker's Wisdom is 16, and their manifester level is 5th.
\begin{enumerate*}
	\item Attacker must succeed in the power check for \psionic{ego whip} (DC 23). Their power check total bonus is

	\begin{Formula}{+13 = 16 (\textit{Wisdom score}) $-3$ (\textit{mental barrier})}\end{Formula}

	So, they succeed with a d20 roll of 10 or more.


	\item On a successful power check of the telepathic attack, the defender must make a Will saving throw.

	\begin{Formula}{DC 15 = 10 + 5 (\textit{manifester level})}\end{Formula}

	With a Will bonus of +7, the defender succeeds with a d20 roll of 8 or more.
\end{enumerate*}
