\WarriorTable{The Epic Gladiator}{
21 & +21/+16/+11/+6/+1   & +12 & +7  & +7  & Uncanny initiative \\
22 & +22/+17/+12/+7/+2   & +13 & +7  & +7  & Exotic weapon, martial prowess \\
23 & +23/+18/+13/+8/+3   & +13 & +7  & +7  &\\
24 & +24/+19/+14/+9/+4   & +14 & +8  & +8  & Wounding strike \\
25 & +25/+20/+15/+10/+5  & +14 & +8  & +8  & Armor optimization 5, martial prowess, dirty trick $\pm$10/$\pm$12 \\
26 & +26/+21/+16/+11/+6  & +15 & +8  & +8  & Exotic weapon \\
27 & +27/+22/+17/+12/+7  & +15 & +9  & +9  & Lethal strike \\
28 & +28/+23/+18/+13/+8  & +16 & +9  & +9  & Martial prowess \\
29 & +29/+24/+19/+14/+9  & +16 & +9  & +9  &\\
30 & +30/+25/+20/+15/+10 & +17 & +10 & +10 & Armor optimization 6, exotic weapon, \emph{time stands still} \\
}

\subsectionA{Epic Gladiator}
The epic gladiator is the center of attention no matter where he fights, as his arena performances become even more bloody and spectacular.

\textbf{Hit Die:} d8.

\textbf{Skill Points per Level:} 4 + Int modifier.

\textbf{Arena Performance:} An epic gladiator continues to gain one additional daily use of arena performance per level. Each arena performance effect continues to improve by the same rate.

\textit{Dirty Trick (Ex):} At 25th level, an epic gladiator can do one of the following, once per encounter per opponent:

\begin{itemize*}
\item Gain +10 circumstance bonus on his attack rolls against target opponent for one round per gladiator level.
\item Gain +12 circumstance bonus on his damage rolls against target opponent for one round per gladiator level.
\item Impose $-10$ circumstance penalty on target opponent's attack rolls for one round per gladiator level.
\item Impose $-12$ circumstance penalty on target opponent's damage rolls for one round per gladiator level.
\end{itemize*}

The epic gladiator also gains new arena performance abilities. Each ability requires both a minimum gladiator level and a minimum number of ranks in the \skill{Perform} (arena fighting) skill to qualify; if an epic gladiator does not have the required number of ranks in at least one \skill{Perform} (arena fighting) skill, he does not gain the arena performance ability until he acquires the needed ranks.

\textit{Uncanny Initiative (Ex):} An epic gladiator of 21st level or higher with 24 or more ranks in \skill{Perform} (arena fighting) can spend two of his daily arena performance as an immediate action to treat his initiative roll as if it resulted in any number of his choosing (from 1 to 20). This can only be done at the moment of the initiative, not later.

\textit{Wounding Strike (Ex):} An epic gladiator of 24th level or higher with 27 or more ranks in \skill{Perform} (arena fighting) can turn an attack into a wounding strike. The epic gladiator must declare the wounding strike before making the attack. If the attack hits, it deals 2d10 points of Constitution damage in addition to the normal damage.

\textit{Lethal Strike (Ex):}  An epic gladiator of 27th level or higher with 30 or more ranks in \skill{Perform} (arena fighting) can attempt to kill his opponent with a single brutally overwhelming assault. As a full-round action, he makes a single attack. The target is considered flat-footed against this attack. If this attack deals damage, the target must make a successful Fortitude save (DC 10 + \onehalf his gladiator level + his Str modifier) or be instantly slain (hit points drop to $-10$). If the save is successful, the attack deals an extra 1d6 damage per gladiator level. Creatures immune to critical hits are immune to the death effect of this strike.

\textit{Time Stands Still (Su):} An epic gladiator of 30th level with 33 in \skill{Perform} (arena fighting) can lash out with his blade, striking his opponent so rapidly that observers can't keep track of his moves. The epic gladiator can use a full attack action two times in succession. He takes his first full attack as normal. Once he has resolved those attacks, he can then take another full attack action. He must resolve these actions separately. He cannot combine the attacks provided by both actions as he wishes. Instead, he must take them separately and in order as normal for a full attack.

\textbf{Martial Prowess:} At 22nd level and every three epic gladiator levels thereafter (25th and 28th level), an epic gladiator learns a new technique. This technique can be chosen from the normal gladiator list or the following list:

\textit{Concealing Acrobat (Ex):} An epic gladiator with 25 or more ranks in \skill{Tumble} has 20\% miss chance if he moves at least 3 meters during his turn. When in total defense, the epic gladiator has 50\% miss chance if he moves at least 3 meters, instead. He loses this benefit if he is caught flat-footed, or if he loses his Dexterity bonus to AC.


\PsychicTable{The Epic Psion}{
21 & +15/+10/+5        & +7  & +7  & +12 &            &  84 & 26 & 6 \\
22 & +16/+11/+6/+1     & +7  & +7  & +13 &            &  86 & 27 & 6 \\
23 & +17/+12/+7/+2     & +7  & +7  & +13 &            &  88 & 28 & 6 \\
24 & +18/+13/+8/+3     & +8  & +8  & +14 &            &  90 & 29 & 6 \\
25 & +18/+13/+8/+3     & +8  & +8  & +14 & Bonus feat &  92 & 30 & 6 \\
26 & +19/+14/+9/+4     & +8  & +8  & +15 &            &  94 & 31 & 6 \\
27 & +20/+15/+10/+5    & +9  & +9  & +15 &            &  96 & 32 & 6 \\
28 & +21/+16/+11/+6/+1 & +9  & +9  & +16 &            &  98 & 33 & 6 \\
29 & +21/+16/+11/+6/+1 & +9  & +9  & +16 &            & 100 & 34 & 6 \\
30 & +22/+17/+12/+7/+2 & +10 & +10 & +17 & Bonus feat & 102 & 35 & 6 \\
}


\textit{Counterstrike (Ex):} Whenever an adjacent creature that swings at an epic gladiator and misses, he gains a free attack against that creature with his highest base attack bonus.

\textit{Epic Fighter Feat:} An epic gladiator may select an epic fighter feat in place of a martial prowess.

\textit{Epic Leadership:} An epic gladiator may gain the \feat{Epic Leadership} feat as a bonus feat.

% \feat{Energy Resistance},
% \feat{Epic Leadership},
% \feat{Epic Speed},
% \feat{Epic Toughness},
% \feat{Fast Healing},
% \feat{Improved Armor Optimization},
% \feat{Legendary Acrobat},
% \feat{Legendary Commander},
% \feat{Legendary Rider},
% \feat{Perfect Health}.

\textit{Greater Flurry (Ex):} An epic gladiator with uses the highest base attack bonus for all attacks when he uses flurry of blows. All attacks still take the $-2$ penalty for flurry of blows. This ability requires improved flurry. For example, a 22nd-level gladiator would attack with a base attack bonus +22/+22/+22/+22/+22/+22 instead of +22/+22/+22/+17/+12/+7.

\textit{Intimidating Presence (Ex):} An epic gladiator with 25 or more ranks in \skill{Intimidate} can unsettle foes with its mere presence. The ability takes effect automatically whenever the epic gladiator attacks or charges. Creatures within a radius of 45 meters are subject to the effect. A potentially affected creature that succeeds on a Will save (DC 10 + the epic gladiator's \skill{Intimidate} bonus) remains immune to the intimidating presence for 24 hours. On a failure, creatures with 4 or less HD become panicked for 4d6 rounds and those with 5 or more HD become shaken for 4d6 rounds. Epic gladiators ignore the intimidating presence of other epic gladiators.

\textit{Master Escapist (Ex):} An epic gladiator with 25 or more ranks in \skill{Escape Artist} can slip out of grapples easily. This ability duplicates the effect of a \spell{freedom of movement} spell, except that it is always active. As a swift action, the epic gladiator may expend three of his daily arena performances to effectively reduce his size by one size category for one round. The epic gladiator gains the standard size bonuses or penalties on attacks, \skill{Hide} checks, and so forth.

\textit{Master Feint (Ex):} An epic gladiator with 25 or more ranks in \skill{Bluff} can feint multiples attacks with a single skill check. Whenever the epic gladiator successfully feints one attack, that foe loses their Dexterity bonus to AC for all of his attacks until the epic gladiator's next turn. As a swift action, the epic gladiator may expend three of his daily arena performances to gain sneak attack +10d6 until his next turn.

\textit{Piercing Eyes (Ex):} An epic gladiator with 25 or more ranks in \skill{Spot} is immune to blindness and cannot be harmed by any spell or power with the light descriptor. As a swift action, he may spend three of his daily arena performances to make all his melee attacks resolve as melee touch attacks until the end of his turn.

\textit{Pressing Tactics (Ex):} An epic gladiator with 25 or more ranks in \skill{Balance} can move 1.5 meter each time he makes a successful melee attack. This movement does not provoke attacks of opportunity from the creature he struck. A gladiator cannot use this technique to move more than his current speed in a single round. As a swift action, the epic gladiator may expend three of his daily arena performances to make two additional attacks with each weapon he wields. These extra attacks are made at his highest attack bonus for each respective weapon.

\textit{Stone Will (Ex):} An epic gladiator with 25 or more ranks in \skill{Autohypnosis} is immune to critical hits. As a swift action, the epic gladiator may expend three of his daily arena performances to end one spell, effect, or other condition currently affecting him with a duration of 1 or more rounds. That effect ends immediately.

\textbf{Exotic Weapon:} At 22nd level and every four levels thereafter, an epic gladiator gains \feat{Exotic Weapon Proficiency} as a bonus feat.

\textbf{Armor Optimization (Ex):} At 25th level, an epic gladiator increases the armor bonus to AC and reduces the armor check penalty by 5 whenever he is wearing any armor he is proficient with. At 30th level, these improvements increase to 6.
