\subsectionA{Epic Druid}
The epic druid is the epitome of primal protection, able to telepathically call any species inside her guarded lands or even create an impenetrable dome to protect it. Her abilities to transform increase even further with new sizes and creature types to transform.

\SpellcasterTable{3mm}{The Epic Druid}{
\SpellHeader{9} \\
21 & +15/+10/+5        & +12 & +7  & +12 & Wild shape (7/day, Diminutive)    & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
22 & +16/+11/+6/+1     & +13 & +7  & +13 & Guardian telepathy                & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
23 & +17/+12/+7/+2     & +13 & +7  & +13 & Guardian call                     & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
24 & +18/+13/+8/+3     & +14 & +8  & +14 & Wild shape (8/day, magical beast) & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
25 & +18/+13/+8/+3     & +14 & +8  & +14 & Wild shape (Gargantuan)           & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
26 & +19/+14/+9/+4     & +15 & +8  & +15 & Guardian dome                     & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
27 & +20/+15/+10/+5    & +15 & +9  & +15 & Wild shape (9/day)                & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
28 & +21/+16/+11/+6/+1 & +16 & +9  & +16 & Guardian sacrifice                & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
29 & +21/+16/+11/+6/+1 & +16 & +9  & +16 & Wild shape (Colossal)             & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
30 & +22/+17/+12/+7/+2 & +17 & +10 & +17 & Wild shape (10/day, aberration)   & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 \\
}

\textbf{Hit Die:} d8.

\textbf{Skill Points per Level:} 2 + Int modifier.

\textbf{Spells:} An epic druid does not gain additional spell slots. % gain access to psionic enchantments: 10th-level spells that need profound psionic knowledge. In order to cast those psionic enchantments, the epic druid must have Intelligence and Wisdom scores both equal to at least 20, and access to all six psionic disciplines. Casting a psionic enchantment requires spending 50 power points, besides the spell slot of 10th-level. The Difficulty Class for a saving throw against a psionic enchantment is 20 + the epic druid's Wisdom modifier.

\textbf{Wild Shape (Su):} At 21st level, the epic druid can use this ability to take the form of an animal one additional time per day. An epic druid can use this ability more times per day at 24th and every three levels thereafter (27th and 30th level).

In addition, she gains the ability to take the shape of a Diminutive animal at 21st level, a Gargantuan animal at 25th level, and a Colossal animal at 29th level.

At 24th level, an epic druid becomes able to use wild shape to change into a magical beast with the same size restrictions as for animal forms.

At 30th level, an epic druid becomes able to use wild shape to change into an aberration with the same size restrictions as for animal forms. This transformation uses two wild shape daily uses.

\textbf{Guardian Telepathy (Su):} At 22nd level, an epic druid can communicate telepathically with any creature within her guarded lands. This ability has no range limit, and language does not interfere with this communication. The epic druid does not need to be on her guarded lands to communicate.

\textbf{Guardian Call (Su):} At 23rd level, an epic druid can call upon an entire species within her guarded lands. The epic druid must first wild shape into the desired creature and use her telepathy to call for all members of the same species. All able creatures will move to her location at their best speed. The number of creatures cannot be decrease---it's all who live on her guarded lands or nothing. The called creatures will obey all of the epic druid's commands, provided she stays with them in wild shape. Once she returns to her original form, all creatures return to their homes.

\textbf{Guardian Dome (Su):} At 26th level, an epic druid can create an impenetrable dome around her guarded lands. The dome rises 300 meters above the highest point of the guarded lands. The dome is impossible to cross with the following exceptions: creatures designated by the epic druid or creatures with more Hit Dice than the epic druid can cross the dome. The dome prohibits passage in both directions---those inside cannot get out and those without cannot get in.

The nature of the dome is up to the epic druid's imagination---an array of spinning blades, a field of pure force, a curtain of flame and magma, etc.

\textbf{Guardian Sacrifice (Su):} At 28th level, an epic druid senses precisely where a defiler casts a spell within her guarded lands she knows the location of the act---even if she is not in the area. She can protect her lands through sacrificing part of her own life force. This nullifies a wizard's defiling radius and any effects it entails, such as penalties to attacks and saving throws, and damage to plants. It also nullifies the benefits of any raze feats used in the casting of the defiling spell. She loses 1 hit point per 3 meter of defiling radius nullified.
