\SpellcasterTable[7]{3mm}{The Epic Bard}{
\SpellHeader{6}\\
21 & +15/+10/+5        & +12 & +12 & +12 & Chance 3/day, quick thinking +8, inspire excellence & 3 & 2 & 1 & & & & \\
22 & +16/+11/+6/+1     & +13 & +13 & +13 & \feat{Brew Potion}                                  & 3 & 2 & 2 & & & & \\
23 & +17/+12/+7/+2     & +13 & +13 & +13 & \feat{Scribe Scroll}                                & 3 & 2 & 2 & 1 & & & \\
24 & +18/+13/+8/+3     & +14 & +14 & +14 & Trade secret, deafening song                        & 3 & 2 & 2 & 2 & & & \\
25 & +18/+13/+8/+3     & +14 & +14 & +14 & Special ability, inspire courage +5                 & 3 & 2 & 2 & 2 & 1 & & \\
26 & +19/+14/+9/+4     & +15 & +15 & +15 & Quick thinking +10                                  & 3 & 2 & 2 & 2 & 2 & & \\
27 & +20/+15/+10/+5    & +15 & +15 & +15 & Hindering song                                      & 3 & 2 & 2 & 2 & 2 & 1 & \\
28 & +21/+16/+11/+6/+1 & +16 & +16 & +16 & Chance 4/day, trade secret                          & 3 & 2 & 2 & 2 & 2 & 2 & \\
29 & +21/+16/+11/+6/+1 & +16 & +16 & +16 & Master minstrel                                     & 3 & 2 & 2 & 2 & 2 & 2 & 1 \\
30 & +22/+17/+12/+7/+2 & +17 & +17 & +17 & \emph{Mass dominate}, special ability                 & 3 & 2 & 2 & 2 & 2 & 2 & 2 \\
}

\subsectionA{Epic Bard}
The epic bard becomes tuned with the magic and gains the capability of casting as a wizard. His talents with poison and subterfuge are unrivaled.

\textbf{Hit Die:} d6.

\textbf{Skill Points per Level:} 6 + Int modifier.

\textbf{Bardic Music:} An epic bard continues to gain one additional daily use of bardic music per level. Each bardic music effect continues to improve by the same rate.

\textit{Fascinate (Sp):} At 21st level, an epic bard can target 8 creatures with this ability with a single use. For every three levels a bard attains beyond 21st, he can target one additional creature with a single use of this ability.

\textit{Inspire Greatness (Su):} At 21st level, an epic bard can target five allies with a single use of this ability. For every three levels an epic bard attains beyond 21st, he can target one additional ally with a single use of this ability (six at 24th level, seven at 27th, eight at 30th).

\textit{Inspire Courage (Su):} At 25th level, the bonus of this ability increases to +5.

The epic bard also gains new bardic music abilities. Each ability requires both a minimum bard level and a minimum number of ranks in the \skill{Perform} skill to qualify; if an epic bard does not have the required number of ranks in at least one \skill{Perform} skill, he does not gain the bardic music ability until he acquires the needed ranks. An epic bard cannot use \skill{Perform} (arena fighting) to use his bardic music abilities.

\textit{Inspire Excellence (Su):} An epic bard of 21st level or higher with 24 or more ranks in \skill{Perform} skill can use his song or poetics to grant a bonus to one ability score to one of his allies. For every three levels a bard attains beyond 21st, he can target one additional ally with a single use of this ability (two at 24th level, three at 27th, four at 30th). To be affected, an ally must hear him sing for 1 full round. The effect lasts as long as the ally hears the epic bard sing and for 5 rounds thereafter. Each ally to be inspired gains a +4 competence bonus to the same ability score, which the epic bard must choose before he begins inspiring. Inspire excellence is a mind-affecting ability.

\textit{Deafening Song (Su):} An epic bard of 24th level or higher with 27 or more ranks in \skill{Perform} skill can use his song or poetics to temporarily deafen all enemies within a 9-meter spread. A successful Fortitude save (DC 10 + \onehalf his class level + the his Charisma modifier) negates the effect. The deafening effect lasts for as long as he continues the deafening song. He can choose to exclude any characters from this effect. He may keep up the deafening song for a maximum of 10 rounds.

\textit{Hindering Song (Su):} An epic bard of 27th level or higher with 30 or more ranks in \skill{Perform} skill can use his song or poetics to hinder enemy spellcasters within a 9-meter spread centered on him. To successfully cast a spell within this area, a spellcaster must make a \skill{Concentration} check as if they were casting defensively, and all such checks have a penalty equal to half the epic bard's level. He can choose to exclude any characters from this effect. The epic bard may keep up the hindering song for a maximum of 10 rounds.

\textit{Mass Dominate (Sp):} An epic bard of 30th level with 33 ranks in \skill{Perform} skill can use his song or poetics to \emph{dominate} (as the \spell{dominate monster} spell) all creatures that he has already fascinated. Using this ability does not break the bard's concentration on the fascinate effect, nor does it allow a second saving throw against the fascinate effect.

\emph{Dominating} doesn't count against a bard's daily limit on bardic music performances. A Will saving throw (DC 25 + bard's Cha modifier) negates the effect. \emph{Mass dominate} is an enchantment (compulsion), mind-affecting, language-dependent ability.


\textbf{Chance (Ex):} An epic bard gains a new daily use of this ability at 21st level, and another at 28th level.

\textbf{Quick Thinking (Ex):} At 21st and 26th level, the initiative bonus increases by 2 (+8 at 21st, and +10 at 26th level).

\textbf{Spells:} At 21st level, the epic bard gains the ability to cast spells as a preserver (an epic bard can't defile). An epic bard can choose enchantment, illusion, or transmutation spells from the wizard spell list or the assassin spell list; if a spell appears on both lists at different levels, he uses the assassin version of the spell. An epic bard does not have access to any universal spell (such as \spell{permanency}).

% As a preserver, an epic bard must choose and prepare his spells ahead of time (see below).

To learn, prepare, or cast a spell, the epic bard must have an Intelligence score equal to at least 10 + the spell level. The Difficulty Class for a saving throw against an epic bard's spell is 10 + the spell level + the epic bard's Intelligence modifier.

Like other spellcasters, an epic bard can cast only a certain number of spells of each spell level per day. His base daily spell allotment is given on \tabref{The Epic Bard}. In addition, he receives bonus spells per day if he has a high Intelligence score.

% An epic bard may know any number of spells. She must choose and prepare his spells ahead of time by getting a good night's sleep and spending 1 hour studying his spellbook. While studying, the epic bard decides which spells to prepare.

\textbf{Brew Potion:} At 22nd level, an epic bard gains the \feat{Brew Potion} feat as a bonus feat.

\textbf{Scribe Scroll:} At 23rd level, an epic bard gains the \feat{Scribe Scroll} feat as a bonus feat.

\textbf{Trade Secret:} At 24th and 28th level, an epic bard learns a trade secret. This secret can be chosen from the normal bard list or the following list:

\textit{Arcane Poison (Su):} An epic bard may infuse poison with the effect of an arcane spell of 5th-level or lower that targets one or more creatures. This requires raw materials that cost a value equal to the spell level $\times$ the epic bard's caster level $\times$ 25 cp. Crafting an arcane poison increases the craft time by one day, but only after the base poison has been completed (see \skill{Craft} skill).

When the target is inflicted with the poison, he is the target of the spell infused.

\textit{Combine Songs (Ex):} An epic bard with this trade secret can combine two types of bardic music to provide the benefit of both. The epic bard chooses two music abilities and activates both using the same standard action. If either or both require concentration, the epic bard can maintain concentration on both by using one standard action each round to concentrate. The normal stacking rules for bonus types apply to music abilities combined with this ability.

% \textit{Reactive Countersong (Ex):} An epic bard can begin a countersong at any time, even when it isn't his turn (much like a wizard who has readied a counterspell action), though he doesn't have to ready an action to do so. An epic bard can't use reactive countersong at the same time he is using another bardic music ability (though he could stop the other bardic music ability to begin reactive countersong if so desired).

\textit{Self-Concealment (Ex):} Attacks against an epic bard have a 20\% miss chance, similar to the effect of concealment. He loses this benefit whenever he would lose his Dexterity bonus to AC. This ability can be taken multiple times, each time the miss chance increases by 20\%.


\textbf{Special Ability:} The epic bard continues to gain new special abilities at 25th and 30th level. He may choose from the normal bard special abilities or the following list:

\textit{Dexterous Fortitude (Ex):} Once per round, when targeted by an effect that requires a Fortitude saving throw, an epic bard may make a Reflex save instead to avoid the effect (evasion is not applicable).

\textit{Dexterous Will (Ex):} Once per round, when targeted by an effect that requires a Will saving throw, an epic bard may make a Reflex save instead to avoid the effect (evasion is not applicable).

\textbf{Master Minstrel (Su):} At 29th level, an epic bard has mastered the ability to inspire allies. All inspire music effects affect double the normal number of creatures with a single use of the ability. This affects inspire competence, inspire greatness, inspire heroics, and inspire excellence.

Additionally, all bardic music can affect even those normally immune to mind-affecting effects. However, such creatures gain a +10 bonus on their Will saves to resist such effects.
