\WarriorTable{The Epic Barbarian}{
21 & +21/+16/+11/+6/+1   & +12 & +7  & +7  & Incite rage \\
22 & +22/+17/+12/+7/+2   & +13 & +7  & +7  & Martial prowess \\
23 & +23/+18/+13/+8/+3   & +13 & +7  & +7  & Bonus feat \\
24 & +24/+19/+14/+9/+4   & +14 & +8  & +8  & Rage 7/day \\
25 & +25/+20/+15/+10/+5  & +14 & +8  & +8  & Martial prowess, superior rage \\
26 & +26/+21/+16/+11/+6  & +15 & +8  & +8  & Bonus feat \\
27 & +27/+22/+17/+12/+7  & +15 & +9  & +9  & \\
28 & +28/+23/+18/+13/+8  & +16 & +9  & +9  & Martial prowess, rage 8/day \\
29 & +29/+24/+19/+14/+9  & +16 & +9  & +9  & Bonus feat, unbreakable will \\
30 & +30/+25/+20/+15/+10 & +17 & +10 & +10 & Eternal rage \\
}

\subsectionA{Epic Barbarian}
The epic barbarian becomes a raging leader, not only becoming the very incarnation of rage but inciting rage into his allies.

\textbf{Hit Die:} d12.

\textbf{Skill Points per Level:} 4 + Int modifier.

\textbf{Incite Rage (Ex):} At 21st level, when an epic barbarian enters a rage, he can incite a barbarian rage in any or all allies within 18 meters. (Any ally who doesn't wish to become enraged is unaffected.) The ally gains +4 to Strength, +4 to Constitution, and a +2 morale bonus on Will saves, but takes a $-2$ penalty to AC, for as long as the epic barbarian remains raging. The rage of affected allies lasts a number of rounds equal to 3 + their Constitution modifier, regardless of whether they remain within 18 meters of him. This is otherwise identical with normal barbarian rage (including the fatigue at its end). This is a mind-affecting ability.

\textbf{Martial Prowess:} At 22nd level and every three barbarian levels thereafter (25th and 28th level), an epic barbarian learns a new technique. This technique can be chosen from the normal barbarian list or the following list:

\textit{Aura of Courage (Su):} An epic barbarian is immune to fear (magical or otherwise). Each ally within 3 meters of him gains a +4 morale bonus on saving throws against fear effects. This ability functions while the epic barbarian is conscious, but not if he is unconscious or dead.

\textit{Devastating Blow (Ex):} As a standard action, an epic barbarian may make a single melee attack with a two-handed weapon at a $-5$ penalty. If the attack hits, it is treated as a critical threat.

\textit{Penetrating Strike (Ex):} An epic barbarian's attacks ignore up to 10 points of damage reduction.

\textit{Ruinous Rage (Ex):} While in a rage, an epic barbarian ignore the hardness of any object he strikes. Also, double his Strength bonus for the purposes of any Strength check made to break an object with sudden force rather than by dealing normal damage (including bursting bindings, such as ropes or manacles).

\textit{Savage Charge (Ex):} An epic barbarian gains +4 bonus on the attack roll when charging, instead of +2. He can also charge through friendly creatures and difficult terrain.

\textit{Stunning Critical (Ex):} Whenever an epic barbarian scores a critical hit, the target becomes stunned for 1d3+1 rounds. A successful Fortitude save (DC equal) reduces this to 1 round.

\textit{Terrifying Rage (Ex):} While an epic barbarian is raging, any enemy that views him must make a Will save opposed by his \skill{Intimidate} check of become panicked (if it has HD less than his character level) or shaken (if it has HD equal to or up to twice his character level) for 4d6 rounds. An enemy with Hit Dice greater than twice his character level is not affected by this ability.


\textbf{Bonus Feat:} At 23rd level and every three barbarian levels thereafter (26th, and 29th level), an epic barbarian gains a bonus feat. These bonus feat must be selected from the normal barbarian bonus feat list or the following list of epic feats:
\feat{Armor Skin},
\feat{Chaotic Rage},
\feat{Damage Reduction},
\feat{Devastating Critical},
\feat{Legendary Climber},
\feat{Legendary Leaper},
\feat{Fast Healing},
\feat{Perfect Health}.
% Ruinous Rage,
% Terrifying Rage.

\textbf{Rage (Ex):} At 24th and 28th level, an epic barbarian gains one additional use of rage (7/day at 24th, and 8/day at 28th level).

\textbf{Superior Rage (Ex):} At 25th level, an epic barbarian's bonuses to Strength and Constitution during his rage each increase to +10, and his morale bonus on Will saves increases to +5. The penalty to AC remains at $-2$.

\textbf{Unbreakable Will (Ex):} While in rage, an epic barbarian becomes immune to any enchantment and illusion spells, telepathy powers, and any mind-affecting effects. Against other effects that require Will saves, he gains +8 bonus to resist.

\textbf{Eternal Rage (Ex):} At 30th level, an epic barbarian is always considered to be raging. This means that the bonuses, penalties, and restrictions of rage apply at all times. He may stop the rage at any time, if the need arises. Flying into a rage again spends one daily use of rage and it lasts indefinitely.
