\SpellcasterTable[4]{5mm}{The Epic Ranger}{
\SpellHeader[1]{4}\\
21 & +21/+16/+11/+6/+1   & +12 & +12 & +7  & Epic combat style                       & 3 & 3 & 3 & 3 \\
22 & +22/+17/+12/+7/+2   & +13 & +13 & +7  & Bonus domain, martial prowess           & 3 & 3 & 3 & 3 \\
23 & +23/+18/+13/+8/+3   & +13 & +13 & +7  & \feat{Epic Endurance}, improved evasion & 3 & 3 & 3 & 3 \\
24 & +24/+19/+14/+9/+4   & +14 & +14 & +8  & \feat{Scribe Scroll}                    & 3 & 3 & 3 & 3 \\
25 & +25/+20/+15/+10/+5  & +14 & +14 & +8  & Favored enemy, favored terrain          & 3 & 3 & 3 & 3 \\
26 & +26/+21/+16/+11/+6  & +15 & +15 & +8  & Martial prowess                         & 3 & 3 & 3 & 3 \\
27 & +27/+22/+17/+12/+7  & +15 & +15 & +9  & \feat{Legendary Tracker}                & 3 & 3 & 3 & 3 \\
28 & +28/+23/+18/+13/+8  & +16 & +16 & +9  & Bonus domain                            & 3 & 3 & 3 & 3 \\
29 & +29/+24/+19/+14/+9  & +16 & +16 & +9  & Death of enemies                        & 3 & 3 & 3 & 3 \\
30 & +30/+25/+20/+15/+10 & +17 & +17 & +10 & Favored enemy, martial prowess          & 3 & 3 & 3 & 3 \\
}

\subsectionA{Epic Ranger}
The epic ranger is completely attuned with his element and an unparalleled danger to his favored enemies.

\textbf{Hit Die:} d8.

\textbf{Skill Points per Level:} 6 + Int modifier.

\textbf{Animal Companion:} The epic ranger's animal companion continues to increase in power. At every three levels higher than 18th (21st, 24th, 27th, and so on), the companion gains +2 bonus Hit Dice, its natural armor increases by 2, its Strength and Dexterity modifiers increase by 1, and it learns one additional bonus trick.

\textbf{Spells:} The ranger's caster level is equal to one-half his class level, as normal. The ranger's number of spells per day does not increase after 20th level.

\textbf{Epic Combat Style:} At 21st level, an epic ranger's aptitude in his chosen combat style (archery or two-weapon combat) reaches its peak. If he selected archery at 2nd level, he is treated as having the \feat{Uncanny Accuracy} feat, even if he does not have the normal prerequisites for that feat.

If the ranger selected two-weapon combat at 2nd level, he is treated as having the \feat{Perfect Two-Weapon Fighting} feat, even if he does not have the normal prerequisites for that feat.

As before, the benefits of the ranger's chosen style apply only when he wears light or no armor. He loses all benefits of his combat style when wearing medium or heavy armor.

\textbf{Bonus Domain:} At 22nd and 28th level, an epic ranger gain full access to a domain of his choice. The character can choose any domain made available by his element. The character gains the granted power associated with the domain he chooses.

\textbf{Martial Prowess:} At 22nd level and every four epic ranger levels thereafter (26th and 30th level), an epic ranger learns a new technique. This technique can be chosen from the normal ranger list or the following list:


% ????

\textbf{Epic Endurance:} At 23rd level, an epic ranger gain \feat{Epic Endurance} as a bonus feat.

\textbf{Improved Evasion (Ex):} At 23rd level, an epic ranger improves his agility. This ability works like evasion, except that while the epic ranger still takes no damage on a successful Reflex saving throw against attacks henceforth he takes only half damage on a failed save. A helpless epic ranger does not gain the benefit of improved evasion.
% \textbf{Bane of Enemies (Ex):} At 23rd level, any weapon an epic ranger wields against one of his favored enemies is treated as a \emph{bane weapon} for that creature type (thus, its enhancement bonus is increased by +2 and it deals +2d6 points of damage). This ability doesn't stack with similar abilities.

\textbf{Scribe Scroll:} At 24th level, an epic ranger gain \feat{Scribe Scroll} as a bonus feat.

\textbf{Favored Enemy (Ex):} At 25th and 30th level, an epic ranger may select an additional favored enemy. In addition, the bonus against any one favored enemy (including the one just selected, if so desired) increases by 2.

\textbf{Favored Terrain (Ex):} At 25th level, an epic ranger may select an additional favored terrain. In addition, the bonus for any one favored terrain (including the one just selected, if so desired) increases by 2.

\textbf{Legendary Tracker:} At 27th level, an epic ranger gains \feat{Legendary Tracker} as a bonus feat.

\textbf{Death of Enemies (Ex):} At 29th level, any time an epic ranger scores a critical hit against one of his favored enemies, it must make a Fortitude save (DC 10 + \onehalf his ranger class level + his Wisdom modifier) or die instantly.
