\subsectionA{Epic Scout}

\textbf{Hit Die:} d8.

\textbf{Skill Points per Level:} 8 + Int modifier.

\textbf{Skirmish (Ex):} At 21st level, the extra damage increases by 1d6. It increases again for every four levels gained above 21st (7d6 at 25th, and 8d6 at 29th level).

At 23rd level, the competence bonus to AC improves by 1. This bonus improves by 1 again at 27th level.

\textbf{Trade Secret:} At 22th, 26th and 30th level, an epic scout learns a trade secret. This secret can be chosen from the normal scout list or from the following list:


\MiniWarriorTable{The Epic Scout}{
% \Table{The Epic Scout}{ll*3{Z{5mm}}L}{
%   \tableheader Level
% & \tableheader Base Attack Bonus
% & \tableheader Fort Save
% & \tableheader Ref Save
% & \tableheader Will Save
% & \tableheader Special\\
21 & +15/+10/+5        & +7  & +12 & +7  & Skirmish ~~~~~~ (+6d6/+5 AC)\\
22 & +16/+11/+6/+1     & +7  & +13 & +7  & Trade secret\\
23 & +17/+12/+7/+2     & +7  & +13 & +7  & Skirmish ~~~~~~ (+6d6/+6 AC)\\
24 & +18/+13/+8/+3     & +8  & +14 & +8  & Bonus feat\\
25 & +18/+13/+8/+3     & +8  & +14 & +8  & Special ability, skirmish ~~~~~~ (+7d6/+6 AC)\\
26 & +19/+14/+9/+4     & +8  & +15 & +8  & Trade secret\\
27 & +20/+15/+10/+5    & +9  & +15 & +9  & Skirmish ~~~~~~ (+7d6/+7 AC)\\
28 & +21/+16/+11/+6/+1 & +9  & +16 & +9  & Bonus feat\\
29 & +21/+16/+11/+6/+1 & +9  & +16 & +9  & Skirmish ~~~~~~ (+8d6/+7 AC)\\
30 & +22/+17/+12/+7/+2 & +10 & +17 & +10 & Special ability, trade secret\\
}


\textit{Epic Scout Feat:} An epic scout can select one of the following epic feats:
\feat{Epic Skill Focus},
\feat{Legendary Acrobat},
\feat{Legendary Climber},
\feat{Legendary Equilibrist},
\feat{Legendary Leaper},
\feat{Legendary Prowler},
\feat{Legendary Rider},
\feat{Legendary Tracker},
\feat{Polyglot}.

\SpellcasterTable[7]{3mm}{The Epic Thief}{
\SpellHeader{6}\\
21 & +15/+10/+5        & +7  & +12 & +7  & Sneak attack +11d6                  & 3 & 2 & 1 & & & & \\
22 & +16/+11/+6/+1     & +7  & +13 & +7  & Special ability, trade secret       & 4 & 2 & 2 & & & & \\
23 & +17/+12/+7/+2     & +7  & +13 & +7  & Sneak attack +12d6                  & 4 & 3 & 2 & 1 & & & \\
24 & +18/+13/+8/+3     & +8  & +14 & +8  &                                     & 4 & 3 & 3 & 2 & & & \\
25 & +18/+13/+8/+3     & +8  & +14 & +8  & Special ability, sneak attack +13d6 & 4 & 4 & 3 & 2 & 1 & & \\
26 & +19/+14/+9/+4     & +8  & +15 & +8  & Trade secret                        & 4 & 4 & 4 & 3 & 2 & & \\
27 & +20/+15/+10/+5    & +9  & +15 & +9  & Sneak attack +14d6                  & 4 & 4 & 4 & 3 & 2 & 1 & \\
28 & +21/+16/+11/+6/+1 & +9  & +16 & +9  & Special ability                     & 4 & 4 & 4 & 4 & 3 & 2 & \\
29 & +21/+16/+11/+6/+1 & +9  & +16 & +9  & Sneak attack +15d6                  & 4 & 4 & 4 & 4 & 3 & 2 & 1 \\
30 & +22/+17/+12/+7/+2 & +10 & +17 & +10 & Trade secret                        & 4 & 4 & 4 & 4 & 4 & 3 & 2 \\
}

\textit{Self-Concealment (Ex):} Attacks against an epic scout have a 20\% miss chance, similar to the effect of concealment. He loses this benefit whenever he would lose his Dexterity bonus to AC. This ability can be taken multiple times, each time the miss chance increases by 20\%.

\textit{Scent (Ex):} An epic scout gains the scent ability.
%%%

\textbf{Bonus Feat:} At 24th and 28th level, an epic scout gains a bonus feat. These bonus feat must be selected from the normal scout bonus feat list or from the following list of epic feats:
\feat{Distant Shot},
\feat{Epic Endurance},
\feat{Epic Fortitude},
\feat{Epic Initiative},
\feat{Epic Reflex},
% \feat{Epic Skill Focus},
\feat{Epic Speed},
\feat{Epic Will},
\feat{Instant Reload},
% \feat{Legendary Acrobat},
% \feat{Legendary Climber},
% \feat{Legendary Rider},
% \feat{Legendary Tracker},
\feat{Perfect Health},
\feat{Storm of Throws},
\feat{Swarm of Arrows},
\feat{Uncanny Accuracy}.

\textbf{Special Ability:} The epic scout continues to gain new special abilities at 25th and 30th level. He may choose from the normal scout special abilities or from the following list:

\textit{Blindsight (Ex):} An epic scout gains the blindsight ability out to 18 meters. His senses become so acute that she can maneuver and fight flawlessly even in total darkness. Invisibility, darkness, and most kinds of concealment are irrelevant, though he must have line of effect to a creature or object to discern it. This ability requires blindsense.

\textit{Dexterous Fortitude (Ex):} Once per round, when targeted by an effect that requires a Fortitude saving throw, an epic scout may make a Reflex save instead to avoid the effect (evasion is not applicable).

\textit{Dexterous Will (Ex):} Once per round, when targeted by an effect that requires a Will saving throw, an epic scout may make a Reflex save instead to avoid the effect (evasion is not applicable).

\textit{Epic Feat:} An epic scout may gain a bonus epic feat in place of a special ability.

\textit{Haste (Su):} An epic scout can act as if under the \spell{haste} spell for a number of rounds per day equal to \onefifth his scout levels. The duration of the effect need not be consecutive rounds. Activating this power is a free action.
