\SpellcasterTable[7]{3mm}{The Epic Thief}{
\SpellHeader{6}\\
21 & +15/+10/+5        & +7  & +12 & +7  & Sneak attack +11d6                  & 3 & 2 & 1 & & & & \\
22 & +16/+11/+6/+1     & +7  & +13 & +7  & Special ability, trade secret       & 4 & 2 & 2 & & & & \\
23 & +17/+12/+7/+2     & +7  & +13 & +7  & Sneak attack +12d6                  & 4 & 3 & 2 & 1 & & & \\
24 & +18/+13/+8/+3     & +8  & +14 & +8  &                                     & 4 & 3 & 3 & 2 & & & \\
25 & +18/+13/+8/+3     & +8  & +14 & +8  & Special ability, sneak attack +13d6 & 4 & 4 & 3 & 2 & 1 & & \\
26 & +19/+14/+9/+4     & +8  & +15 & +8  & Trade secret                        & 4 & 4 & 4 & 3 & 2 & & \\
27 & +20/+15/+10/+5    & +9  & +15 & +9  & Sneak attack +14d6                  & 4 & 4 & 4 & 3 & 2 & 1 & \\
28 & +21/+16/+11/+6/+1 & +9  & +16 & +9  & Special ability                     & 4 & 4 & 4 & 4 & 3 & 2 & \\
29 & +21/+16/+11/+6/+1 & +9  & +16 & +9  & Sneak attack +15d6                  & 4 & 4 & 4 & 4 & 3 & 2 & 1 \\
30 & +22/+17/+12/+7/+2 & +10 & +17 & +10 & Trade secret                        & 4 & 4 & 4 & 4 & 4 & 3 & 2 \\
}

\subsectionA{Epic Thief}

\textbf{Hit Die:} d6.

\textbf{Skill Points per Level:} 10 + Int modifier.

\textbf{Sneak Attack:} The epic rogue's sneak attack damage increases by +1d6 at every odd-numbered level.

\textbf{Spells:} At 21st level, the epic thief gains the ability to cast spells as a preserver (an epic thief can't defile). An epic thief can choose divination, illusion, or transmutation spells from the wizard spell list or the assassin spell list; if a spell appears on both lists at different levels, he uses the assassin version of the spell. An epic thief does not have access to any universal spell (such as \spell{permanency}).

% As a preserver, an epic thief must choose and prepare his spells ahead of time (see below).

To learn, prepare, or cast a spell, the epic thief must have an Intelligence score equal to at least 10 + the spell level. The Difficulty Class for a saving throw against an epic thief's spell is 10 + the spell level + the epic thief's Intelligence modifier.

Like other spellcasters, an epic thief can cast only a certain number of spells of each spell level per day. His base daily spell allotment is given on \tabref{The Epic Thief}. In addition, he receives bonus spells per day if he has a high Intelligence score.

\textbf{Trade Secret:} At 22th, 26th, and 30th level, an epic thief learns a trade secret. This secret can be chosen from the normal thief list or the following list:

\textit{Deadly Range (Ex):} An epic thief with this talent increases the range at which he can deal sneak attack damage by 6 meters. An epic thief can select this talent more than once; its effects stack.

\textit{Greater Sneak Attack (Ex):} An epic thief's sneak attack damage improves by 1d6. This trade secret can be selected multiple times.

\textit{Self-Concealment (Ex):} Attacks against an epic thief have a 20\% miss chance, similar to the effect of concealment. She loses this benefit whenever she would lose her Dexterity bonus to AC. This ability can be taken multiple times, each time the miss chance increases by 20\%.


\textbf{Special Ability:} The epic thief continues to gain new special abilities at 22nd, 26th, and 30th level. He may choose from the normal thief special abilities or the following list:

\textit{Dexterous Fortitude (Ex):} Once per round, when targeted by an effect that requires a Fortitude saving throw, an epic thief may make a Reflex save instead to avoid the effect (evasion is not applicable).

\textit{Dexterous Will (Ex):} Once per round, when targeted by an effect that requires a Will saving throw, an epic thief may make a Reflex save instead to avoid the effect (evasion is not applicable).

\textit{Haste (Su):} An epic thief can act as if under the \spell{haste} spell for a number of rounds per day equal to \onefifth his thief levels. The duration of the effect need not be consecutive rounds. Activating this power is a free action.

\textit{Lingering Damage (Ex):} Any time an epic thief deals damage with a sneak attack, that target takes damage equal to his sneak attack bonus damage on his next turn as well. This ability requires crippling strike.

\textit{Sneak Attack of Opportunity (Ex):} Any attack of opportunity an epic thief makes is considered a sneak attack. This ability requires opportunist.


