\subsectionA{Epic Fighter}
The epic fighter is a master of combat maneuvers and a natural leader, his martial reach a lethality that inspire his allies.

\Table{The Epic Fighter}{ll*3{Z{4mm}}L}{
  \tableheader Level
& \tableheader Base Attack Bonus
& \tableheader Fort Save
& \tableheader Ref Save
& \tableheader Will Save
& \tableheader Special\\
21 & +21/+16/+11/+6/+1   & +12 & +7  & +7  & Martial prowess \\
22 & +22/+17/+12/+7/+2   & +13 & +7  & +7  & Bonus feat      \\
23 & +23/+18/+13/+8/+3   & +13 & +7  & +7  & Martial prowess \\
24 & +24/+19/+14/+9/+4   & +14 & +8  & +8  & Bonus feat      \\
25 & +25/+20/+15/+10/+5  & +14 & +8  & +8  & Martial prowess \\
26 & +26/+21/+16/+11/+6  & +15 & +8  & +8  & Bonus feat      \\
27 & +27/+22/+17/+12/+7  & +15 & +9  & +9  & Martial prowess \\
28 & +28/+23/+18/+13/+8  & +16 & +9  & +9  & Bonus feat      \\
29 & +29/+24/+19/+14/+9  & +16 & +9  & +9  & Martial prowess \\
30 & +30/+25/+20/+15/+10 & +17 & +10 & +10 & Bonus feat      \\
}


\textbf{Hit Die:} d10.

\textbf{Skill Points per Level:} 4 + Int modifier.

\textbf{Martial Prowess:} At 21st level and every two epic fighter levels thereafter (23th, 25th, 27th, and 29th level), an epic fighter learns a new technique. This technique can be chosen from the normal fighter list or the following list:

\textit{Aura of Courage (Su):} An epic fighter is immune to fear (magical or otherwise). Each ally within 3 meters of him gains a +4 morale bonus on saving throws against fear effects. This ability functions while the epic fighter is conscious, but not if he is unconscious or dead.

\textit{Counterstrike (Ex):} Whenever an adjacent creature that swings at an epic fighter and misses, he gains a free attack against that creature with his highest base attack bonus.

\textit{Devastating Blow (Ex):} As a standard action, an epic fighter may make a single melee attack with a two-handed weapon at a $-5$ penalty. If the attack hits, it is treated as a critical threat.

\textit{Epic Leadership:} An epic fighter may gain \feat{Epic Leadership} as a bonus feat.

\textit{Improved Tactics (Ex):} The bonuses provided by coordinate allies, defensive tactics, flanking tactics, lead the charge, and harden resolve improve by 1. This martial prowess can be taken more than once.

\textit{Indomitable Charge (Ex):} An epic fighter with 24 or more ranks in \skill{Knowledge} (warcraft) can lead his allies into an epic charge. As he charges an opponent, all allies within 9 meters at the beginning of his turn can also charge at this target as an immediate action. The epic fighter and his allies do not block each other when determining if they can charge. The epic fighter's charge deals an extra damage equal to 3 $\times$ his fighter levels, and his allies' charges deal an extra damage equal to 1\onehalf $\times$ his fighter levels. The epic fighter and his allies do not provoke attacks of opportunity for moving as part of this charge.

\textit{Martial Mastery (Ex):} An epic fighter may apply any feat that applies to only a single weapon (such as \feat{Weapon Focus}) to any simple or martial weapon.

\textit{Penetrating Strike (Ex):} An epic fighter's attacks ignore up to 10 points of damage reduction.

\textit{Piercing Shot (Ex):} An epic fighter can pierce through foes with his crossbow attacks. If an attack deals 20 or more points of damage, the bolt pierces the target and can strike another creature in line behind it. The epic fighter must be able to trace a line starting at his location and passing through both targets to make this additional attack. The secondary attack is made at a $-4$ penalty, in addition to any modifiers for added range. The damage threshold for piercing changes according to the target's size category. For each size increase from Medium, double the threshold; and for each size decrease from Medium, halve it.

\textit{Stalwart Shield (Ex):} As an immediate action, an epic fighter can redirect an attack made at an adjacent creature, as long as the attacking creature is within the epic fighter's reach. The attack is made against the epic fighter's AC. In addition, the epic fighter's shield cannot be disarmed or sundered.

\textit{Stunning Critical (Ex):} Whenever an epic fighter scores a critical hit, the target becomes stunned for 1d3+1 rounds. A successful Fortitude save (DC 10 + his base attack bonus) reduces this to 1 round.

\textit{Two-Weapon Riposte (Ex):} When an epic fighter makes a full attack with two weapons, every creature that hits him with a melee attack before the beginning of his next turn provokes an attack of opportunity from the epic fighter.

\textbf{Bonus Feat:} At 22nd and every even-numbered level thereafter, an epic fighter gains a bonus feat. These bonus feat must be selected from the normal fighter bonus feat list or epic fighter feats.
