\subsectionA{Divine Feats}

\Feat[Divine]{Elemental Affinity}
{You are protected by your patron element.}
{Cha 13, ability to turn or rebuke undead.}
{As a free action, spend one of your turn or rebuke undead attempts to add a +4 sacred bonus to Fortitude saving throws against attacks by the energy type associated with your patron element for a number of rounds equal to your Charisma modifier.}
{}{}

\Feat[Divine]{Elemental Might}
{You can channel your element's energy to increase the damage you deal in combat.}
{Str 13, ability to turn or rebuke undead, \feat{Power Attack}.}
{As a free action, spend one of your turn or rebuke undead attempts to add your Charisma bonus as energy damage to your weapon for 1 full round. The type of damage dealt must match your patron element's descriptor.}
{}{}

\Feat[Divine]{Elemental Vengeance}
{You can channel your element's energy to deal extra damage against undead in melee.}
{Ability to turn undead, \feat{Extra Turning}.}
{As a free action, spend one of your turn undead attempts to add 2d6 points of energy damage to all your successful melee attacks against undead until the end of your next action. This is a supernatural ability. The type of damage dealt must match your patron element's descriptor.}
{}{}

\Feat[Divine]{Superior Blessing}
{You can bless your element with stronger positive energies.}
{Ability to turn or rebuke undead.}
{As a standard action, spend one of your turn or rebuke undead attempts to double the potency of your blessed element. Creatures exposed to your blessed element take 4d4 points of damage.}
{Creatures exposed to blessed elements receive 2d4 points of damage.}
{}