\subsectionA{Item Creation Feats}

\Feat[Item Creation]{Brew Potion}
{}
{Caster level 3rd.}
{You can create a potion of any 3rd-level or lower spell that you know and that targets one or more creatures. Brewing a potion takes one day. When you create a potion, you set the caster level, which must be sufficient to cast the spell in question and no higher than your own level. The base price of a potion is its spell level $\times$ its caster level $\times$ 50 cp. To brew a potion, you must spend 1/25 of this base price in XP and use up raw materials costing one half this base price.

When you create a potion, you make any choices that you would normally make when casting the spell. Whoever drinks the potion is the target of the spell.

Any potion that stores a spell with a costly material component or an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must expend the material component or pay the XP when creating the potion.}
{}
{On Athas, potions take many different forms. The most common form is an enchanted fruit, often called a \emph{potionfruit}. Other common items for enchantment include obsidian orbs, packs of herbs, and bone fetishes. The potion, regardless of material used to make it, is consumed or destroyed when used.

Due to the nature of their magic, defilers cannot enchant organic materials, such as fruits, as a potion. As a consequence, most non-defilers use those receptacles almost exclusively, as a way of assuring the potion is not a product of defiler magic.}

\Feat[Item Creation]{Craft Cognizance Crystal}
{You can create psionic cognizance crystals that store power points.}
{Manifester level 3rd.}
{You can create a cognizance crystal. Doing so takes one day for each 1,000 cp in its base price. The base price of a cognizance crystal is equal to the highest-level power it could manifest using all its stored power points, squared, multiplied by 1,000 cp. To create a cognizance crystal, you must spend 1/25 of its base price in XP and use up raw materials costing one-half its base price.}{}{}

\GFeat[Item Creation]{Craft Construct}
{\feat{Craft Magic Arms and Armor}, \feat{Craft Wondrous Item}.}
{A creature with this feat can create any construct whose prerequisites it meets. Enchanting a construct takes one day for each 1,000 cp in its market price. To enchant a construct, a spellcaster must spend 1/25 the item's price in XP and use up raw materials costing half of this price (see individual construct monster entries for details).

A creature with this feat can repair constructs that have taken damage. In one day of work, the creature can repair up to 20 points of damage by expending 50 cp per point of damage repaired.

A newly created construct has average hit points for its Hit Dice.}

% \Feat[Item Creation]{Craft Dorje}
% {You can create slender crystal wands called dorjes than manifest powers when charges are expended.}
% {Manifester level 5th.}
% {You can create a dorje of any psionic power you know (barring exceptions, such as bestow power, as noted in a power's description). Crafting a dorje takes one day for each 1,000 cp in its base price. The base price of a dorje is its manifester level $\times$ the power level $\times$ 750 cp. To craft a dorje, you must spend 1/25 of this base price in XP and use up raw materials costing one-half of this base price.

% A newly created dorje has 50 charges.

% Any dorje that stores a power with an XP cost also carries a commensurate cost. In addition to the XP cost derived from the base price, you must pay fifty times the XP cost.}{}{}

\GFeat[Item Creation]{Craft Magic Arms and Armor}
{Caster level 5th.}
{You can create any magic weapon, armor, or shield whose prerequisites you meet. Enhancing a weapon, suit of armor, or shield takes one day for each 1,000 cp in the price of its magical features. To enhance a weapon, suit of armor, or shield, you must spend 1/25 of its features' total price in XP and use up raw materials costing one-half of this total price.

The weapon, armor, or shield to be enhanced must be a masterwork item that you provide. Its cost is not included in the above cost.

You can also mend a broken magic weapon, suit of armor, or shield if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to craft that item in the first place.}

\GFeat[Item Creation]{Craft Psionic Item}
{Manifester level 9th.}
{You can create any psionic item whose prerequisites you meet. Empowering a psionic item takes one day for each 1,000 cp in its price. To empower a psionic item, you must spend 1/25 of the item's price in XP and use up raw materials costing half of this price.

You can also mend a broken psionic item if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to craft that item in the first place.

Some psionic items incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the item's base price. You must pay such a cost to create an item or to mend a broken one.}

% \Feat[Item Creation]{Craft Psicrown}
% {You can create psicrowns, which have multiple psionic effects.}
% {Manifester level 12th.}
% {You can create any psicrown whose prerequisites you meet. Crafting a psicrown takes one day for each 1,000 cp in its base price. To craft a psicrown, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price. Some psicrowns incur extra costs in XP as noted in their descriptions. These costs are in addition to those derived from the psicrown's base price.}{}{}

% \Feat[Item Creation]{Craft Psionic Arms and Armor}
% {You can create psionic weapons, armor, and shields.}
% {Manifester level 5th.}
% {You can create any psionic weapon, armor, or shield whose prerequisites you meet. Enhancing a weapon, suit of armor, or shield takes one day for each 1,000 cp in the price of its psionic features. To enhance a weapon, you must spend 1/25 of its features' total price in XP and use up raw materials costing one-half of this total price.

% The weapon, armor, or shield to be enhanced must be a masterwork item that you provide. Its cost is not included in the above cost.

% You can also mend a broken psionic weapon, suit of armor, or shield if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to enhance that item in the first place.}{}{}

% \Feat[Item Creation]{Craft Psionic Construct}
% {You can create golems and other psionic automatons that obey your orders.}
% {\feat{Craft Psionic Arms and Armor}, \feat{Craft Universal Item}.}
% {You can create any psionic construct whose prerequisites you meet. Creating a construct takes one day for each 1,000 cp in its base price. To create a construct, you must spend 1/25 of the construct's base price in XP and use up raw materials costing one-half of this price. A newly created construct has average hit points for its Hit Dice.}{}{}

\GFeat[Item Creation]{Craft Rod}
{Caster level 9th.}
{You can create any rod whose prerequisites you meet. Crafting a rod takes one day for each 1,000 cp in its base price. To craft a rod, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price.

Some rods incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the rod's base price.}

\GFeat[Item Creation]{Craft Staff}
{Caster level 12th.}
{You can create any staff whose prerequisites you meet.

Crafting a staff takes one day for each 1,000 cp in its base price. To craft a staff, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price. A newly created staff has 50 charges.

Some staffs incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the staff's base price.}

% \Feat[Item Creation]{Craft Universal Item}
% {You can create universal psionic items.}
% {Manifester level 3rd.}
% {You can create any universal psionic item whose prerequisites you meet. Crafting a universal psionic item takes one day for each 1,000 cp in its base price. To craft a universal psionic item, you must spend 1/25 of the item's base price in XP and use up raw materials costing one-half of this price.

% You can also mend a broken universal item if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to craft that item in the first place.

% Some universal items incur extra costs in XP, as noted in their descriptions. These costs are in addition to those derived from the item's base price. You must pay such a cost to create an item or to mend a broken one.}{}{}

\GFeat[Item Creation]{Craft Wand}
{Caster level 5th.}
{You can create a wand of any 4th-level or lower spell that you know. Crafting a wand takes one day for each 1,000 cp in its base price. The base price of a wand is its caster level $\times$ the spell level $\times$ 750 cp. To craft a wand, you must spend 1/25 of this base price in XP and use up raw materials costing one-half of this base price. A newly created wand has 50 charges.

Any wand that stores a spell with a costly material component or an XP cost also carries a commensurate cost. In addition to the cost derived from the base price, you must expend fifty copies of the material component or pay fifty times the XP cost.}

\GFeat[Item Creation]{Craft Wondrous Item}
{Caster level 3rd.}
{You can create any wondrous item whose prerequisites you meet. Enchanting a wondrous item takes one day for each 1,000 cp in its price. To enchant a wondrous item, you must spend 1/25 of the item's price in XP and use up raw materials costing half of this price.

You can also mend a broken wondrous item if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to craft that item in the first place.

Some wondrous items incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the item's base price. You must pay such a cost to create an item or to mend a broken one.}

\GFeat[Item Creation]{Forge Ring}
{Caster level 12th.}
{You can create any ring whose prerequisites you meet. Crafting a ring takes one day for each 1,000 cp in its base price. To craft a ring, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price.

You can also mend a broken ring if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to forge that ring in the first place.

Some magic rings incur extra costs in material components or XP, as noted in their descriptions. You must pay such a cost to forge such a ring or to mend a broken one.}

% \Feat[Item Creation]{Imprint Stone}
% {You can create power stones to store psionic powers.}
% {Manifester level 1st.}
% {You can create a power stone of any power that you know. Encoding a power stone takes one day for each 1,000 cp in its base price. The base price of a power stone is the level of the stored power $\times$ its manifester level $\times$ 25 cp. To imprint a power stone, you must spend 1/25 of this base price in XP and use up raw materials costing one-half of this base price.

% Any power stone that stores a power with an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must pay the XP when encoding the stone.}{}{}

\Feat[Item Creation]{Scribe Scroll}
{}
{Caster level 1st, literacy.}
{You can create a scroll of any spell that you know. Scribing a scroll takes one day for each 1,000 cp in its base price. The base price of a scroll is its spell level $\times$ its caster level $\times$ 25 cp. To scribe a scroll, you must spend 1/25 of this base price in XP and use up raw materials costing one-half of this base price.

Any scroll that stores a spell with a costly material component or an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must expend the material component or pay the XP when scribing the scroll.}
{}
{On Athas, scrolls take many different forms. Common forms include paper or papyrus sheets, clay tablets, and woven cloth.}

\Feat[Item Creation]{Scribe Tattoo}
{You can create psionic tattoos, which store powers within their designs.}
{Manifester level 3rd.}
{You can create a psionic tattoo of any power that you know and that targets one or more creatures and has duration other than instantaneous. Scribing a psionic tattoo takes one day for each 1,000 cp in its base price. When you create a psionic tattoo, you set the manifester level. The manifester level must be sufficient to manifest the power in question and no higher than your own level. The base price of a psionic tattoo is its power level $\times$ its manifester level $\times$ 6,000 cp. To scribe a tattoo, you must spend 1/25 of this base price in XP and use up raw materials (special inks, masterwork needles, and so on) costing one-half of this base price.

When you create a psionic tattoo, you make any choices that you would normally make when manifesting the power.

If the power has a duration measured in rounds, multiply the cost by 4. If the duration of the power is 1 minute/level, multiply the cost by 2, and if the duration is 10 minutes/level, multiply the cost by 1.5. If the power has a 24-hour duration or greater, divide the cost in half.

Any psionic tattoo that stores a power with an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must pay the XP when creating the tattoo.}{}{}

% \Feat[Item Creation]{Scribe Tattoo}
% {You can create psionic tattoos, which store powers within their designs.}
% {Manifester level 3rd.}
% {You can create a psionic tattoo of any power of 3rd level or lower that you know and that targets one or more creatures. Scribing a psionic tattoo takes one day. When you create a psionic tattoo, you set the manifester level. The manifester level must be sufficient to manifest the power in question and no higher than your own level. The base price of a psionic tattoo is its power level $\times$ its manifester level $\times$ 50 cp. To scribe a tattoo, you must spend 1/25 of this base price in XP and use up raw materials (special inks, masterwork needles, and so on) costing one-half of this base price.

% When you create a psionic tattoo, you make any choices that you would normally make when manifesting the power.

% When its wearer physically activates the tattoo, the wearer is the target of the power.

% Any psionic tattoo that stores a power with an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must pay the XP when creating the tattoo.}{}{}
