\section{Racial Feats}

\Feat[Racial]{Active Glands}
{Your venom glands are particularly active.}
{Thri-kreen.}
{You can use your poisonous bite two additional times per day.}
{}{}

\Feat[Racial]{Advanced Antennae}
{Your antennae are more developed than those of your fellow thri-kreen, enabling you to detect both predators and prey near you.}
{Thri-kreen.}
{You gain the scent ability.}
{}{}

\Feat[Racial]{Blend}
{Your carapace meshes better with your surroundings.}
{Thri-kreen.}
{Your racial bonus on \skill{Hide} checks in sandy or arid terrain is increased by +3.}
{}{}

\Feat[Racial]{Blessed by the Ancestors}
{Your egg-clutch hatched near the remains of great ancestors, positively influencing your life.}
{Thri-kreen.}
{You get a +1 bonus on all saves.}
{}
{This feat must be selected at 1st level.}

\Feat[Racial]{Cannibalism Ritual}
{You know the secrets of ingesting a defeated opponent's flesh to improve your physical attributes.}
{Wis 13, halfling.}
{When you have slain a creature in combat with Hit Dice equal or superior to your character level you may devour its remains after performing a ritual alone that lasts two hours. If you do, you receive a +2 enhancement bonus to either Strength, Dexterity or Constitution for 24 hours. This effect is not cumulative.}
{}{}

\Feat[Racial]{Dwarven Vision}
{You are born with the full heritage of your dwarven parent's vision.}
{Mul.}
{You have darkvision up to 60 feet.}
{}{}

\Feat[Racial]{Elfeater}
{You open yourself fully to your racial hate and taste for elves.}
{Thri-kreen.}
{You gain a +2 bonus on \skill{Bluff}, \skill{Listen}, \skill{Sense Motive}, \skill{Spot}, and \skill{Survival} checks when using these skills against elves. Likewise, you get a +1 bonus on attack rolls and a +2 to confirm critical hits against elves.}
{}{}

\Feat[Racial]{Improved Gyth'sa}
{You are born with a better than normal gyth'sa, your blood-producing organ, giving you a better than normal healing time.}
{Thri-kreen, Con 13.}
{With a full night's rest (8 hours or more), you recover 2 hit points per character level. If you are tended successfully by someone with the \skill{Heal} skill, you instead regain double the normal amount of hit points.}
{You recover 1 hit point per character level with a full night's rest.}
{This feat must be selected at 1st level.}

\Feat[Racial]{Longshanks}
{You are as fast a full-blooded elf.}
{Half-elf, both parents must be half-elves.}
{Your land speed is faster than the norm for a half-elf by +10 feet.}
{}{}

\Feat[Racial]{Tikchak}
{Your racial memories awaken and along with it your hunting skills.}
{Thri-kreen, character level 5th.}
{You are proficient with the chatkcha. You also receive a bonus on \skill{Survival} checks while hunting equal to your Wisdom modifier (add the bonus twice).}
{}{}

\Feat[Racial]{Tokchak}
{You have a very strong clutch mentality.}
{Thri-kreen.}
{Allies adjacent to you gain a +1 bonus to Reflex saves. This benefit does not apply when you are flat-footed.}
{}{}