\section{Raze Feats}

\Feat[Raze]{Agonizing Radius}
{Your defiling techniques are particularly painful.}
{Defiler}
{The penalties for being caught within your defiling radius increase by one (i.e. from $-1$ to $-2$).}
{}{}

\Feat[Raze]{Controlled Raze}
{You increase your defiling radius and may specify unaffected squares.}
{Defiler}
{Your defiling radius increases by 5 feet. You can specify one 5 ft. square per 5 ft. radius of your defiling circle that is unaffected by your energy gathering. Creatures in unaffected squares do not suffer the adverse effects of being caught in the defiling circle, nor is vegetation in that square turned to ash.}
{}{}

\Feat[Raze]{Distance Raze}
{You can gather energy for spells at a distance.}
{Defiler}
{You can move the center of your defiling circle (on the ground) up to 10 feet per caster level, in effect moving the entire circle of defiling.}
{Your defiling circle is centered on you.}
{}

\Feat[Raze]{Destructive Raze}
{You can focus the energy you absorb from plants to increase the damage your spells inflict.}
{Defiler}
{Add +1 to damage per damage die inflicted by evocation spells when defiling.}
{}{}

\Feat[Raze]{Efficient Raze}
{You can gather energy more efficiently, utilizing the maximum energy potential of a given terrain.}
{Defiler}
{Treat the terrain you gather energy in as one category better when you defile. e.g. a spell cast in barren terrain ($-1$ spell save DC and $-1$ penalty to caster level checks) is treated as if cast in infertile terrain (no spell save modifier and no penalty to caster level checks). In abundant terrain the bonuses to spell save DCs and spell checks are increased by an additional +1. This feat has no effect in the Obsidian Plains.}
{}{}

\Feat[Raze]{Exterminating Raze}
{Your defiling techniques are particularly damaging to plant creatures.}
{Defiler}
{Plant creatures caught in your defiling radius suffer 4 points of damage per spell level.}
{Plant creatures caught in your defiling radius suffer 2 points of damage per spell level.}
{}

\Feat[Raze]{Fast Raze}
{You can gather energy faster.}
{Defiler}
{When defiling, you can spend a move action to gain a +1 caster level bonus. Spells with a normal casting time of 1 round or longer still require an extra round to be cast in this manner. Your defiling radius increases by 5 ft. when using Fast Raze.}
{It takes one round to gain the caster level benefit.}
{}

\Feat[Raze]{Sickening Raze}
{Your defilement makes others sick.}
{\feat{Agonizing Radius}, defiler.}
{Creatures within your defiling radius become nauseated in addition to any other penalties for 1 round.}
{}{}