\subsectionA{Psiumarkh}
\textbf{Location:} Raam.

\textbf{Members:} .

The most prestigious psionic school in Raam, and possibly the entire Tyr region. is the Psiumarkh. This ancient school is descended directly from the order founded by Tarandas herself more than 300 years ago.

\subsubsection{Brief History}
The ancient home of Tarandas's first school, Raam remains one of the leading cities for psionic research. Dozens of small colleges, circles, and orders reside here. studying the works of Tarandas and expanding the knowledge of the Way. A number of these groups are little more than misguided cults, but the largest organizations are making excellent progress.

\subsubsection{Psiumarkh Benefits}
\textbf{Access:} 

\subsubsection{Psiumarkh on Athas}
For centuries the masters of the Psiumarkh have carefully maintained a policy of strict neutrality, avoiding the petty squabbles and intrigues of the city. This has allowed them to survive the civil wars and oppressive purges that have cycled through the city for decades.

The Psiumarkh is currently led by a Grand Master named Tierard, a wizened old man who sometimes is distracted by strict adherence to propriety and form. The masters of the various disciplines are beginning to maneuver for Tierard's seat, which they believe will become vacant soon.

% Another school worth mentioning is the Yellow Monastery. The Yellow Monks form an order devoted to the development of telepathic powers. The Monastery has a fair amount of influence in the city and is noted as a symbol of resistance to the rule of Abalach-Re. The monks themselves are completely dedicated to a set of principles, including opposition to slavery, magic of any kind, and gladiatorial games. Students of the Yellow Monastery almost always remain there to become monks instead of moving on to different studies.

\textbf{Organization:} 

\textbf{NPC Reactions:} 

\subsubsection{Psiumarkh Lore}
Characters with ranks in \skill{Knowledge} (local [Draj]) or \skill{Knowledge} (psionics) can research the Psiumarkh to learn more about it. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 10:}

\textbf{DC 15:}

\textbf{DC 20:}

\textbf{DC 30:}

A bardic knowledge check or a \skill{Gather Information} check (wherever a psionic academy can be found) check can reveal the same information as these knowledge checks, but in each case the DC is 5 higher than the given value.

\subsubsection{Psiumarkh in the Game}
