\subsectionA{The Brotherhood of the Mind}
\textbf{Location:} Makla.

\textbf{Members:} 12 members.

The Brotherhood of the Mind is an ancient society of evil psionicists that conspire to destroy all sorcerer-kings and rule Athas supreme. In the Sanctuary, they secretly plot and scheme while constantly searching for ancient psionic texts.

\subsubsection{Brief History}
The Brotherhood was founded by a noble Nibenese psionicist named Liumakh almost 500 years ago. Liumakh is a powerful telepath who dreamed of unseating the Shadow King of Nibenay. He was convinced that a sufficient gathering of psionic power could defeat the tyrant. Unfortunately, the Shadow King learned of his plots, and he and his followers were forced to flee. At that time, Hamanu of Urik was feuding with Nibenay, and he gave them sanctuary.

Liumakh and his followers constantly work to bring down the Shadow King, but they've never been able to succeed. In studying his enemy, Liumakh realized the nature of the sorcerer-kings, and his secret order changed its goal to the accumulation of raw power. He planned to destroy the sorcerer-kings and assume his role as the ruler of Athas.

Over the centuries, the Brotherhood's importance has fluctuated. Despite this, not one sorcerer-king has fallen to its plots. The Order closely watches the Brotherhood, but to date it has not achieved a level of power that would require intervention. Hamanu of Urik pretends to ignore them, but he occasionally spies on the Brotherhood to see what they are up to.

The Brotherhood has taken advantage of the recent events that shook the Tablelands, falsely advertising that the sorcerer-kings of Tyr, Raam, and Draj were killed by members of the Brotherhood, which has caused their ranks to substantially grow in the last few years. The insulation of Urik has further helped the Brotherhood to further grow, since now they are unfettered by Hamanu's templars.

\subsubsection{The Sanctuary}
The headquarters of the Brotherhood of the Mind is a hidden monastery cradled in the fiery slopes of the Smoking Crown, overlooking the Lake of Golden Dreams.

The Sanctuary lies in the slopes of the Smoking Crowns, north of Makla, along a narrow and sinuous path. Its entrance is marked by a stone gatehouse protected with several clairsentient psionics. After that, stone stairs lead to the front hall. The Sanctuary has three floors. On the ground floor the dormitories house the apprentices and can hold one hundred students comfortably. Classrooms and meditating rooms are on the first floor, with rooms for the instructors and senior members flanking them. The library is located in the basement, together with a series of closed down tunnels that go deep into the Smoking Crowns. No one knows why these tunnels were closed.

Aside from the high-level psions and other manifesters responsible for instructing the apprentices, the House employs many guardians to watch the gatehouse and patrol the region surrounding the monastery.

\subsubsection{The Brotherhood of the Mind Benefits}
\textbf{Access:} As members of the Brotherhood, PCs have access to knowledge for the prestige class \class{Psion Uncarnate}. The most preeminent students may be taught by Liumakh himself.

\subsubsection{The Brotherhood on Athas}
The Brotherhood of the Mind is a secretive and somewhat large body of evil manifesters, spreading out into Athas searching for more members and ancient psionic mysteries.

The Brotherhood is a network of like-minded individuals, all committed to advancement of their craft and power. Although most train at the Sanctuary, only a few members remain there. Most leave, returning on occasion to share information, learn new powers, or seek an audience with Liumakh.

Officially, members are free to come and go as they please, but in reality, any ex-member will suffer a terrible, fatal accident soon after leaving the Brotherhood. After all it is a steep climb down. Liumakh is afraid that ex-members could reveal any important information to the sorcerer-kings.

\textbf{Organization:} For years, the Brotherhood has been engaged in a quest for ancient texts of psionic enchantments, hoping to find something that would make possible the destruction of the remaining sorcerer-kings. The Brotherhood is still led by Liumakh (LE male undead [human], telepath 7/psion uncarnate 10), whose unending ambition for power continued even after his death. Currently, there are about fifty members of the Brotherhood scattered across the Tyr Region.

\textbf{NPC Reactions:} Traditional psionicists view the Brotherhood of the Mind's purpose as hideous and against the basic principles of the Way; therefore most manifesters aware of the Brotherhood are unfriendly. Templars and good-aligned characters are always unfriendly.

\subsubsection{The Brotherhood Lore}
Characters with ranks in \skill{Knowledge} (local [Urik]) or \skill{Knowledge} (psionics) can research the Brotherhood of the Mind to learn more about it. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 20:} A Brother is a psionicist bent on using psionics for evil and domination.

\textbf{DC 25:} The Brotherhood of the Mind operates out of the Sanctuary, a monastery where apprentice members are trained.

\textbf{DC 30:} Brothers are always searching for new talent to add to their ranks, and so members always watch for those with psionic talents.

A bardic knowledge check or a \skill{Gather Information} check (wherever a psionic academy can be found) check can reveal the same information as these knowledge checks, but in each case the DC is 5 higher than the given value.


\subsubsection{The Brotherhood in the Game}
The Brotherhood represents a great vehicle for introducing psionics into your campaign. The Brotherhood could be an anonymous group not previously encountered. If a PC has interest in psionics, he can research the organization and seek out the Sanctuary.

Most often than not, the Brotherhood will work as antagonist for the PCs, since sooner or later, the PCs will learn about the true nature of the organization or even be the victim of one of its members.