\subsectionA{The House of the Mind}
\textbf{Location:} Draj.

\textbf{Members:} 200+ students (15 advanced students).

A psionic academy located in Two Moon City---the walled fortress in the heart of Draj---the House of the Mind is personally supervised by Tectuktitlay, sorcerer-king of Draj. Every child with promise is taken to the House of the Mind and schooled by Tectuktitlay's mindbenders.

\subsubsection{Brief History}
No one knows why the king takes such an interest in tutoring talented students. Some claim that the king is looking for a special and unique talent, others believe that the king wants to make his armies invincible by fielding more psionicists than other city-states, and a few whisper that Tectuktitlay is building a priesthood of mindbenders or some dark purpose.

\subsubsection{The House of the Mind Benefits}
\textbf{Access:} As students of the House of the Mind, PCs have access to the prestige classes \class{Metamind} and \class{War Mind}. These advanced students frequently receive personal instruction from Tectuktitlay, who trusts high-level training to no one else.

\subsubsection{The House of the Mind on Athas}
The House of the Mind is not a forgiving place. The students are driven ruthlessly by the lesser masters, who seek to impress the higher masters by obtaining results quickly. Students are often subjected to severe punishments for minor mistakes, and Tectuktitlay has been known to kill those who disappoint him.

It is against the law to tutor a person in the Way outside of the House of the Mind. A few wandering masters can be found practicing their trade in secret in the poorer hovels of the city, but no other psionic schools exist. One of these masters, Tlotipec (LG human nomad 10), is tied to the city's Veiled Alliance and has accumulated several disciples among the city's slaves and criminals.

\textbf{Organization:} Although Tectuktitlay devotes a good deal of time to the school, he cannot be there constantly. The master of the House of the Mind is an aging psionicist known as Ixtabai the Blind (LE telepath [auditor] 17). He oversees the day-to-day operation of the House and the routine instruction of the students. Ixtabai is aided by two dozen lesser psionicists and several powerful Moon Priests.

\textbf{NPC Reactions:} High-ranking students of the House of the Mind are revered (and feared), even outside the city-state, as they have personal tutelage from Tectuktitlay. Surviving the known brutal teachings of the House is a feat in and of itself. Low-ranking students are more of the same, and don't get any bonus or penalties.

\subsubsection{The House of the Mind Lore}
Characters with ranks in \skill{Knowledge} (local [Draj]) or \skill{Knowledge} (psionics) can research the House of the Mind to learn more about it. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 10:} The House of the Mind is a home to the best psionic minds of Draj.

\textbf{DC 15:} The House is supervised by Tectuktitlay himself.

\textbf{DC 20:} Students of the House may suffer severe punishments, and even death, for minor mistakes.

\textbf{DC 30:} Tectuktitlay's eagerness to train the best psionic minds is still unclear. It may serve as a double purpose, to create a psionic army and to find a special talent---but for what?

A bardic knowledge check or a \skill{Gather Information} check (wherever a psionic academy can be found) check can reveal the same information as these knowledge checks, but in each case the DC is 5 higher than the given value.

\subsubsection{The House of the Mind in the Game}
The House can be introduced as a harsh and strict school that antagonizes some free masters that help slaves and members of the Veiled Alliance. The House of the Mind offers great contrast between the brutal and orthodox way of teaching and the gentle and more personal methods of the free masters. Since the House of the Mind is an institution tied to the sorcerer-king, any free master is an outlaw and is hunted by templars. This increases the number of moving parts, as both the House of the Mind and the templarate join forces against free masters and the Veiled Alliance.

Higher level characters might uncover the secrets behind the true nature of the House of the Mind, and why is Tectuktitlay so focused on training people with extraordinary psionic abilities.