\subsection{The Cerebran}
\textbf{Location:} Balic.

\textbf{Members:} 100+ students.

The Cerebran is considered to be one of the best psionic universities. It is located in Balic and it is sponsored by Andropinis, its Dictator. He believes that is is easier to keep track of the psionicists in his city if he sponsors a single training center. The people of Balic are proud of their university and view it as a great accomplishment for their city.

\subsubsection{Brief History}
The Cerebran is located on the outskirts of the city, by the shores of the Silt Estuary. It is an impressive collection of majestic marble buildings surrounded by groves of olive trees. The masters of the university believe that the tending of the groves aids young students in developing patience.

Andropinis allows the university to administer itself, and no templars or soldiers are stationed on its grounds. This creates a seething hotbed of revolutionary ideas and conspiracies. Unfortunately, the dictator has thoroughly infiltrated the Cerebran with loyal spies who keep tabs on the most disloyal.

\subsubsection{The Cerebran Benefits}
\textbf{Access:} As students of the Cerebran, PCs have access to the prestige class \class{Metamind}.

\subsubsection{The Cerebran on Athas}
\textbf{Organization:} The Cerebran is led by an aging woman known as Iphignea, a powerful telepath (LN human telepath 9/psiologist 7) referred to as the Speaker of the Cerebran. Iphignea is not pleased by Andropinis's rule, but she feels that the school will run better if the dictator is not angered, so she cultivates an appearance of loyalty.

\textbf{NPC Reactions:} The Cerebran students are treated as members of a prestigious university. Even NPCs without psionic capabilities know of the fame of the university. However, raamites and nibenese may react unfavorably when the university is mentioned, as they have their own renowned universities.

\subsubsection{The Cerebran Lore}
Characters with ranks in \skill{Knowledge} (local [Balic]) or \skill{Knowledge} (psionics) can research the Cerebran to learn more about it. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 10:} The Cerebran is a prestigious psionic university in Balic. Many of the great names came from there.

\textbf{DC 15:} The university is sponsored by Andropinis himself.

\textbf{DC 20:} The Speaker of the Cerebran is unhappy with Andropinis, but she puts her university above her feelings.

A bardic knowledge check or a \skill{Gather Information} check (wherever a psionic academy can be found) check can reveal the same information as these knowledge checks, but in each case the DC is 5 higher than the given value.

\subsubsection{The Cerebran in the Game}
The Cerebran could be used as a starting point for psionic characters, giving them a place to call home. Giving a fixed point to recover and research can be a way to make your campaign feel grounded.

The Cerebran can also be used as a way to introduce the dynamics of the schools of psionics, and the rivalries between schools and how the templarate and the Order affect the decisions of each school.