\Psionic{Aura Sight}{aura sight}
{Clairsentience}
{
	\textbf{Level:}
	Seer 4\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	9 meters\\
	\textbf{Area:}
	Cone-shaped emanation centered on you\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	20 power points\\
	\textbf{Maintenance Cost:}
	4 pp/minute\\
	% \textbf{Critical Success:}
	% You can examine up to four auras per round\\
	% \textbf{Critical Failure:}
	% You can't use this power for 24 hours\\
}
{
	You discern auras. Auras are invisible to the naked eye, but to a psionic viewer manifesting this power they appear as glowing halos or envelopes of colored light that surround all objects. The color of each aura reveals information to the psionic character. A creature's aura reveals information about its alignment, its Hit Dice, and its type.

	During each round, you can examine up to two auras. Examining an aura is a free action and requires a power check. Each check reveals one information about the creature: one of its alignment axis (i.e., only chaotic from its chaotic neutral alignment), its type, or its Hit Dice. Failure in this check doesn't give you any information.

	Creatures with many Hit Dice require extra effort to examine:

	\Table{}{CC}{
	\tableheader Hit Dice & \tableheader Power Check DC Modifier \\
	 1--5  & +0 \\
	 6--11 & +1 \\
	12--17 & +2 \\
	18--20 & +3 \\
	21+    & +4 \\
	}

	\textit{Augment:} For every 5 additional power points you spend, this power's range increases by 3 meters and the Difficulty Class of the power check by +1.
}