\Psionic{Bend Reality}{bend reality}
{Metacreativity}
{
	\textbf{Level:}
	Shaper 8\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	See text\\
	\textbf{Target, Effect, or Area:}
	See text\\
	\textbf{Saving Throw:}
	None; see text\\
	\textbf{Cost:}
	40 power points, 300 XP or more (see below)\\
	\textbf{Maintenance Cost:}
	See text\\
	\textbf{Prerequisites:}
	Manifester level 16th\\
}
{
	\emph{Bend reality} lets you create nearly any type of effect. For example, \emph{bend reality} can do any of the following:

	\begin{itemize*}
		\item Duplicate any power of 6th level or lower, provided the power is not of a discipline prohibited to you.
		% \item Duplicate any other power (but not a spell) of 5th level or lower, provided the power is not of a discipline prohibited to you.
		\item Duplicate any power of 5th level or lower, even if it's of a prohibited discipline.
		% \item Duplicate any other power (but not a spell) of 4th level or lower, even if it's of a prohibited discipline.
		\item Duplicate any spell of 4th level or lower.
		\item Undo the harmful effects of many powers, such as \psionic{psionic dominate}, \spell{geas/quest}, or \psionic{insanity}.
		\item Produce any other effect whose power level is in line with the above effects, such as a single creature automatically hitting on its next attack or taking a $-8$ penalty on its next saving throw.
		\item A duplicated power allows saving throws as normal (but the save DC is for a 8th-level power).
	\end{itemize*}

	When \emph{bend reality} duplicates a power that has a maintenance cost, you must pay that cost to maintain the power. When \emph{bend reality} duplicates a power or spell that has an XP cost, you must pay that cost or 300 XP, whichever is more. When \emph{bend reality} duplicates a spell with a material component, you must pay additional XP equal to the value of the material component divided by 5.
}