\Psionic{Bone Reading}{bone reading}
{Clairsentience}
{
	\textbf{Level:}
	Seer 6\\
	\textbf{Manifesting Time:}
	1 minute\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	A creature's remains touched\\
	\textbf{Cost:}
	11 power points\\
	\textbf{Maintenance Cost:}
	6 pp/minute\\
	\textbf{Prerequisites:}
	\psionic{object reading}\\
	% \textbf{Critical Success:}
	% You are able to view the last 10 minutes of the deceased's life from their perspective\\
	% \textbf{Critical Failure:}
	% You anger the spirits and a malicious entity that attempts to use \spell{magic jar} on you\\
}
{
	You can use a creature's remains to learn who they were and what they were doing when they perished. Fragments of bone are usually used, but the power works on any corpse or portion of a corpse.

	The amount of information revealed depends on how long you study the remains. You can maintain this power for one additional minute per point above the power check DC on your power check. You may stop maintaining this power before you reach your time limit.

	\textit{1st Minute:} Deceased's race.

	\textit{2nd Minute:} Deceased's gender.

	\textit{3rd Minute:} Deceased's age.

	\textit{4th Minute:} Deceased's identity.

	\textit{5th Minute:} Deceased's alignment.

	\textit{6th Minute:} Appearance in life.

	\textit{7th Minute:} Date of death.

	\textit{8th Minute:} Method of death.

	The power is difficult to use on very old remains. The more recently a creature died, the more accurate the reading will be.

	\Table{}{Cc}{
	\tableheader Time Since Death & \tableheader Power Check DC Modifier \\
	Up to 1 day       & +0  \\
	Up to 1 week      & +1  \\
	Up to 1 month     & +2  \\
	Up to 1 year      & +3  \\
	Up to 10 years    & +4  \\
	Up to 100 years   & +6  \\
	Up to 1,000 years & +12 \\
	}
}