\Psionic{Concentrate Water}{concentrate water}
{Psychokinesis}
{
	\textbf{Level:}
	Kineticist 2\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	9 meters\\
	\textbf{Area:}
	9-meter-radius emanation around you\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	10 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	\psionic{psionic telekinesis}\\
	% \textbf{Critical Success:}
	% The range is increased by 26\%, doubling the amount of water collected.\\
	% \textbf{Critical Failure:}
	% You also collect water from your own body, and lose half of your hit points.\\
}
{
	\emph{Concentrate water} allows you to collect all moisture within the area of effect as water in a single container. The amount of water depends on the terrain type:
	\begin{itemize*}
		\item \textbf{Salt flats, sandy wastes:} 2d4$-4$ liters (minumum 0).
		\item \textbf{Boulder fields, rocky badlands, stony barrens:} 3d6$-5$ liters (minimum 0).
		\item \textbf{Mountains, scrub plains:} 2d12$-2$ liters.
		\item \textbf{Forest, verdant belts:} 5d8+1 liters.
	\end{itemize*}

	You must hold the container while manifesting \emph{concentrate water}. If the container is too small to hold the water, or if it is leaky, the excess spills onto the ground.

	\emph{Concentrate water} only collects uncollected vapor and droplets around the caster. Free-standing water in a glass, poll, or  other container is not collected. It does not adversely affect plants or animals in the area. The drying effect on any local flora becomes evident in the next few days, but most Athasian plants can survive the temporary loss of ground moisture.
}