\Psionic{Control Light}{control light}
{Psychokinesis [Light]}
{
	\textbf{Level:}
	Kineticist 2\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	18 meters\\
	\textbf{Area:}
	Four 3-meter cubes\\
	\textbf{Saving Throw:}
	See text\\
	\textbf{Cost:}
	10 power point\\
	\textbf{Maintenance Cost:}
	2 pp/round\\
	% \textbf{Critical Success:}
	% Characters in blinding light become blind, instead\\
	% \textbf{Critical Failure:}
	% The effect is opposite of what is desired, and maintenance fails\\
}
{
	By manipulating the ambient light level, you can decrease or increase the illumination of an area. The change in illumination can be gradual (taking as long as 1 minute) or sudden (occurring immediately when you manifest this power). You can alter the level of illumination from its original level at any time during the power's duration. This power does not function in darkness. You cannot create light from darkness, but you can create darkness from light.

	You can accomplish the following:
	\begin{itemize*}
	\item Darken an area in bright light to shadowy illumination. Creatures within this area have concealment relative to that character. A creature in an area of shadowy illumination can make a \skill{Hide} check to conceal itself.
	\item Darken an area in shadowy illumination. The area gives 30\% miss chance, instead of the normal 20\% miss chance. Characters in the area gain a +4 circumstance bonus on \skill{Hide} checks.
	\item Brighten an area in shadowy illumination to bright light.
	\item Brighten an area in bright light to blinding light. Characters in the area become dazzled while they remain in the area, unless they make a successful Fortitude save. Dazzled characters take $-1$ penalty on attack rolls, \skill{Search} checks, and \skill{Spot} checks.
	\end{itemize*}
}