\Psionic{Cosmic Awareness}{cosmic awareness}
{Clairsentience}
{
	\textbf{Level:}
	Psion 9\\
	\textbf{Casting Time:}
	1 minute\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Cost:}
	17 power points\\
	\textbf{Maintenance Cost:}
	9 pp/round\\
	\textbf{Prerequisites:}
	Manifester level 11th, \psionic{clairvoyance}, \psionic{psionic true seeing}, \psionic{ubiquitous vision}\\
	% \textbf{Critical Success:}
	% You begin with a sensorial radius of 9 meters\\
	% \textbf{Critical Failure:}
	% You must make a Will check or become blind and deaf for 1d4 hours\\
}
{
	You expand your senses in a sensorial 3-meter-radius sphere that extends into the Astral and Ethereal Planes. You see all inanimate features within the area of effect; you can see what is on the other side of the hill, detect hidden caves, see secret doors and traps, and even detect lodes of unusual minerals or other geological phenomena. You also perceive the flow of the wind and water currents.

	You learn about the location and alignment of every creature within range, even if they are hiding, invisible, or in the Astral or Ethereal Planes. Their equipment is detected down to the number of gold pieces in their purses.

	You hear all sounds and detect all smells within the area.

	You also detect magic within range as the \spell{detect magic} spell, but without needing to study the area. You learn about the auras and their strength instantly.

	Otherwise, this power functions as the \spell{true seeing} spell, as if everything within range was in your line of sight.

	\textit{Augment:} For every additional power point you spend, the radius of your \emph{cosmic awareness} field increases by 3 meters.
}