\Psionic{Dimensional Screen}{dimensional screen}
{Metacreativity}
{
	\textbf{Level:}
	Shaper 5\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	25 power points\\
	\textbf{Maintenance Cost:}
	5 pp/round\\
	\textbf{Prerequisites:}
	\psionic{inertial barrier}, \psionic{psionic dimension door}\\
	% \textbf{Critical Success:}
	% You are bounced away by bull rush or overrun attempts from creatures larger than you.\\
	% \textbf{Critical Failure:}
	% You are \emph{dimension doored} 1d10$\times$30 meters in a random direction and stunned for 1d4 rounds.\\
}
{
	You wrap yourself with a \psionic{psionic dimensional door} around your body to protect against your enemies' attacks. The \emph{dimensional screen} is a shimmering cylinder as tall as yourself that surrounds your at a range of 50 centimeters. Any physical attack that strikes the \emph{screen} is instantly transported to a corresponding point on the other side. This applies to ranged attacks (so arrows and spears pass through your space without harming you, or even being impeded in their flight), as well as natural attacks. Effects that deal damage in an area will also be diverted by the \emph{screen}.

	The \emph{dimensional screen} has limitations, however:
	\begin{itemize*}
		\item You can't use any physical attack against any opponent, as the \emph{screen} can't be pierced.
		\item You do not have line of effect against anyone outside your own personal space (a 1.5-meter square), as the \emph{screen} blocks your vision from the outside.
		\item The \emph{screen} does not stop bull rush or overrun attempts from creatures one or more size categories larger than you.
	\end{itemize*}

	Opponents can still target you with spells, spell-like abilities, psionic powers, and psi-like abilities. So spells like \spell{charm person} or psionic powers like \emph{contact} can still affect you.
}