\Psionic{Dimension Door, Psionic}{psionic dimension door}
{Psychoportation (Teleportation)}
{
	\textbf{Level:}
	Nomad 4\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	45 meters; see text\\
	\textbf{Effect:}
	Two extradimensional portals\\
	\textbf{Saving Throw:}
	Fortitude negates; see text\\
	\textbf{Cost:}
	20 power points\\
	\textbf{Maintenance Cost:}
	4 pp/round\\
	% \textbf{Critical Success:}
	% Travelers are not dazed after transit.\\
	% \textbf{Critical Failure:}
	% You briefly step into the alternate dimension and are dazed for one round.\\
}
{
	With \emph{psionic dimensional door}, you open a Medium portal which leads to the edge of another dimension. The edge acts as a lightning-quick transit system, carrying travelers to a destination of your choice.

	When you use this power, you create a door leading into the alternate dimension. The door is a vaguely outlined portal, which appears in front of you. At the same time, an identical portal appears wherever you want it, within range. The door can have whatever orientation you choose. If someone (including you) steps into either portal, they immediately step out of the other. Both doors remain in place for as long as you maintain the power.

	% The dimension accessed by this power is not fully understood. Clearly, it has very different qualities of time and space, such that motion is greatly accelerated. For many years this transit was thought to be instantaneous, but arduous experiments have proved that a very tiny bit of time does elapse. What this means is still unknown.

	Travel via this power is disorienting. Presumably, exposure to the alternate dimension traumatizes the body in some way. As a result, a traveler is dazed for one round after stepping through a \emph{psionic dimensional door}. Quick transit is advisable. People who shove only an arm through a portal suffer intense pain. Fools who poke their head through a portal must make a Fortitude save; failure means they lose one-half of their current hit points and fall unconscious.

	Inanimate objects are not affected by exposure to the dimension's edge. In fact, a character can throw or fire objects through a portal, and they'll come out on the other side. Attackers suffer a $-4$ penalty on their attack rolls against targets on the other side of a \emph{psionic dimension door}.

	If a trespassing creature arrives in a place that is already occupied by a solid body, they take 1d6 points of damage and are shunted to a random open space on a suitable surface within 30 meters of the intended location.

	If there is no free space within 30 meters, trespassing creatures take an additional 2d6 points of damage and are shunted to a free space within 300 meters. If there is no free space within 300 meters, they take an additional 4d6 points of damage and the you simply can't maintain the power.

	The normal range of this power is 45 meters. The distance can be extended only with severe penalties to your power check, as shown below.

	\Table{}{CC}{
	  \tableheader Range
	& \tableheader Power Check DC Modifier \\
	 45 meters & +0 \\
	 60 meters & +2 \\
	 90 meters & +4 \\
	120 meters & +6 \\
	150 meters & +8 \\
	180 meters & +10 \\
	200 meters & +12 \\
	}
}
