\Psionic{Ectoplasmic Form}{ectoplasmic form}
{Psychometabolism}
{
	\textbf{Level:}
	Egoist 4\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	20 power points\\
	\textbf{Maintenance Cost:}
	4 pp/round\\
	% \textbf{Critical Success:}
	% The maintenance cost is 3 pp/round.\\
	% \textbf{Critical Failure:}
	% Your items become ectoplasmic, but you don't. You must use this power again to retrieve them.\\
}
{
	You and all your gear become a partially translucent mass of rippling ectoplasm that generally conforms to your normal shape. You gain damage reduction 10/magic, and you gain immunity to poison and critical hits. Your material armor becomes meaningless, although your size, Dexterity, deflection bonuses, and armor bonuses from force effects (such as those gained by inertial armor) still apply to your Armor Class.

	You can manifest powers while in ectoplasmic form, but you must make a Concentration check (DC 20 + power level) for each power you attempt to manifest.

	You cannot physically attack, you lose supernatural abilities (if any), and you can't speak while in ectoplasmic form. You can't run, but you can fly at a speed of 20 feet (perfect). You can pass through small holes or narrow openings, even mere cracks, with all you were wearing or holding in your hands. You are subject to the effects of wind, and you can't enter water or other liquid. You also can't manipulate objects or activate items, even those carried along with you. Continuously active items remain active, though in some cases their effects may be moot (such as items that provide armor or natural armor bonuses).
}