\Psionic{Ejection}{ejection}
{Telepathy}
{
	\textbf{Level:}
	Telepath 3\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	One mind in \psionic{contact} with you\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	See text\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	% \textbf{Critical Success:}
	% Roll 1d6 on \tabref{Ejection Side Effects} and apply to the \emph{ejected} mind.\\
	% \textbf{Critical Failure:}
	% Roll 1d6 on \tabref{Ejection Side Effects} and apply to you.\\
}
{
	\emph{Ejection} is the final defense against unwanted \psionic{contact}, as the unwanted mind can be ejected from yours. You must \emph{eject} each unwanted mind separately.

	The cost of \emph{ejection} is twice the unwanted mind's telepathy key ability score.

	Manifesting \emph{ejection} is risky for you, depending on your expertise on telepathy. The table below shows the side effects that can affect you. These side effects happen as you pay its cost.

	\Table{Ejection Side Effects}{lX}{
	  \tableheader Result
	& \tableheader Side Effect \\

	DC    & Lose access to all powers for 1d10 hours \\
	DC +1 & Lose access to one power for 1d10 hours\footnotemark[1] \\
	DC +2 & Lose 1d10+10 power points \\
	DC +3 & Lose 1d10 power points \\
	DC +4 & Take 1 point of Constitution damage \\
	DC +5 & Lose 1d10 hit points \\
	DC +6 & Sever one partial contact\footnotemark[2] \\
	More than DC +6 & --- \\

	\TableNote{2}{1 You lose access to the power of highest level. If two or more powers fit this criteria, you decide which one becomes inaccessible.}\\
	\TableNote{2}{2 One successful psionic attack reestablishes \psionic{contact}.}\\
	}
}
