\Psionic{Elemental Composition}{elemental composition}
{Psychometabolism [Air, Earth, Fire, Water]}
{
	\textbf{Level:}
	Egoist 9\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	45 power points\\
	\textbf{Maintenance Cost:}
	9 pp/round\\
	\textbf{Prerequisites:}
	\psionic{flesh armor}, \psionic{metamorphosis}\\
	% \textbf{Critical Success:}
	% You gain all extraordinary special attacks of your chosen elemental form.\\
	% \textbf{Critical Failure:}
	% You must make a Fortitude save or take 3d10 points of damage.\\
}
{
	You can transform your body into a particular type of elemental substance. You and your possessions appear to be made of that element, though in the same general shape and size as your normal appearance.

	You gain the following abilities when you manifest \emph{elemental composition}:
	\begin{itemize*}
		\item You are immune to poison, sleep, paralysis, and stunning, and are not subject to extra damage from critical hits or flanking.
		\item Your creature type remains unchanged, so you are unaffected by spells that target elementals, but you gain the air, earth, fire, or water subtype depending on the elemental substance you chose.
		\item You gain damage reduction 15/magic.
	\end{itemize*}

	In addition, you gain the following exceptional abilities according to the element chosen:

	\textit{Air:} Fly at your normal speed (perfect maneuverability).

	\textit{Earth:} Earth glide (as an earth elemental).

	\textit{Fire:} Immunity to fire.

	\textit{Water:} Swim at your normal speed.

	You can change form once each round as a free action. The change takes place either immediately before your regular action or immediately after it, but not during the action. 
}