\Psionic{Energy Adaptation}{energy adaptation}
{Psychometabolism [Acid, Cold, Electricity, Fire, Sonic]}
{
	\textbf{Level:}
	Egoist 4\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	20 power points\\
	\textbf{Maintenance Cost:}
	4 pp/minute\\
	% \textbf{Critical Success:}
	% You gain energy invulnerability to all types for one round.\\
	% \textbf{Critical Failure:}
	% You gain energy vulnerability to all types for one round.\\
}
{
	Your body assimilates some of the effect of an energy attack and converts it to harmless light. You gain protection against any attack that deals acid, cold, electricity, fire, or sonic damage. You take only half damage from energy-based attacks. If such an attack allows a Reflex save for half damage, you take no damage on a successful save. The power protects your equipment as well.

	When you absorb damage, you can choose to radiate visible light that illuminates a 18-meter radius for a number of rounds equal to the points of damage you successfully resisted, or merely dissipate the energy without giving off a visual display.

	\textit{Augment:} If you spend additional power points, you can gain energy resistance to all forms of energy. This also increases the Difficulty Class of the power check:

	\Table{}{cCc}{
	  \tableheader Cost
	& \tableheader Energy Resistance
	& \tableheader Power Check DC Modifier \\
	30 & Resistance 5  & +2 \\
	40 & Resistance 10 & +4 \\
	50 & Resistance 20 & +6 \\
	60 & Resistance 30 & +8 \\
	}

	The resistance provided by this power does not stack with other forms of energy resistance.
}
