\Psionic{Expansion}{expansion}
{Psychometabolism}
{
	\textbf{Level:}
	Egoist 2\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	10 power points\\
	\textbf{Maintenance Cost:}
	2 pp/round\\
	% \textbf{Critical Success:}
	% You can increase your size by two size categories instead of one.\\
	% \textbf{Critical Failure:}
	% You shrink and gain a $-2$ size penalty to Strength.\\
}
{
	This power causes instant growth, doubling your height, length, and width and multiplying your weight by 8. This increase changes your size category to the next larger one. You gain a +2 size bonus to Strength, a $-2$ size penalty to Dexterity (to a minimum effective Dexterity score of 1), a $-1$ size penalty on attack rolls, and a $-1$ size penalty to Armor Class due to your increased size.

	If your new size is Large or larger, you have a space of at least 3 meters and a natural reach of at least 3 meters. This power doesn't change your speed. If insufficient room is available for the desired growth, you attain the maximum possible size and can make a Strength check (using your increased Strength score) to burst any enclosures in the process. If you fail, you are constrained without harm by the materials enclosing you—you cannot crush yourself to death by increasing your size.

	All your equipment, worn or carried, is similarly expanded by this power. Melee and projectile weapons deal more damage.

	Other psionic or magical properties are not affected by this power. Any affected item that leaves your possession (including a projectile or thrown weapon) instantly returns to its normal size. This means that thrown weapons deal their normal damage (projectiles deal damage based on the size of the weapon that fired them). Multiple effects that increase size do not stack, which means (among other things) that you can't use a second manifestation of this power to further expand yourself.

	\textit{Augment:} If you spend 10 additional power points, this power increases your size by two size categories instead of one. You gain a +4 size bonus to Strength, a $-4$ size penalty to Dexterity (to a minimum effective Dexterity score of 1), a $-2$ size penalty on attack rolls, and a $-2$ size penalty to Armor Class due to your increased size. This increases the Difficulty Class of the power check by +2.
}