\Psionic{Graft Weapon}{graft weapon}
{Psychometabolism}
{
	\textbf{Level:}
	Egoist 3\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	15 power points\\
	\textbf{Maintenance Cost:}
	3 pp/round\\
	% \textbf{Critical Success:}
	% You gain a +4 competence bonus on all attack and damage rolls while using the weapon, instead.\\
	% \textbf{Critical Failure:}
	% The weapon breaks on any attack roll of 1.\\
}
{
	You attach any melee weapon you can use in one hand---mundane or magical---onto the end of one of your arms. The weapon becomes a natural extension of your arm, and that hand blends seamlessly into the shaft, hilt, or head of the weapon. Now that the weapon and you are one, you gain a +1 competence bonus on all attack and damage rolls while using the weapon.

	The grafted weapon is considered both a standard weapon and a natural weapon for the purpose of effects that distinguish between either weapon type. For instance, the grafted weapon is treated as a natural weapon for the purpose of delivering a touch attack with a power in conjunction with the weapon attack. As with any power (or spell) melee touch attack made in conjunction with a natural weapon attack, the touch attack effect is not delivered unless the natural weapon strikes normally; on a failed attack, the touch power (or spell) is wasted.

	While your hand is grafted to a weapon, you lose the use of that hand and take a $-2$ penalty on all skill checks requiring the use of hands. Powers that temporarily polymorph or metamorph you can ignore the grafted weapon or alter it normally, at your discretion. If the weapon takes damage, you take damage as well. If you are healed, so is your grafted weapon. If your weapon is destroyed, you permanently lose 2 points of Constitution; the ability drain persists until you can restore your natural anatomy (by means of \spell{regenerate} or a similar effect).

	When this power's duration expires, the grafted weapon falls to the ground and your hand returns.
}