\Psionic{Inertial Barrier}{inertial barrier}
{Psychokinesis [Air]}
{
	\textbf{Level:}
	Kineticist 4\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	3 meters\\
	\textbf{Area:}
	3-meter radius emanation, centered on you\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	20 power points\\
	\textbf{Maintenance Cost:}
	4 pp/round\\
	\textbf{Prerequisites:}
	\psionic{psionic telekinesis}\\
	% \textbf{Critical Success:}
	% The barrier blocks additional 3 points of damage.\\
	% \textbf{Critical Failure:}
	% You create a bizarre wind-pocket that knocks you prone.\\
}
{
	You create a barrier of ``elastic'' air around yourself and anyone else within 3 meters. Like an unpoppable, semipermeable bubble, this barrier helps soften missile blows and can shield those inside from many forms of damage.

	The barrier protects against the following:
	\begin{itemize*}
		\item \textit{Acid/Fire:} Acid or fire of any nature does not enter the barrier from outside, but they can be created from within the barrier.
		\item \textit{Falling damage:} \emph{Inertial barrier} absorbs half of the damage from a fall---you still get banged around inside.
		\item \textit{Gas:} Any gas is slowed and turned aside, but after one turn it works its way inside and take full effect.
		\item \textit{Missile weapons:} Anyone inside ignore the damage from any dice rolled, but not the damage modifiers. For example, a \emph{+2 composite longbow (Str +3)} can deal 1d8+5 damage in normal circumstances. Against people protected by an \emph{inertial barrier}, an arrow would deal only 5 damage.
	\end{itemize*}

	The barrier cannot keep enemies out, but it slows them. Anyone trying to cross the barrier stops when they hit it. They can cross inside (or outside) in the their following turn.
}