\Psionic{Intellect Fortress}{intellect fortress}
{Universal}
{
	\textbf{Level:}
	Psion 3\\
	\textbf{Manifesting Time:}
	1 immediate action\\
	\textbf{Range:}
	3 meters\\
	\textbf{Area:}
	3-meter emanation centered on you\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	15 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	% \textbf{Critical Success:}
	% No other effect.\\
	% \textbf{Critical Failure:}
	% You cannot use \emph{intellect fortress} for 1d4 rounds.\\
}
{
	\emph{Intellect fortress} calls forth the powers of the ego and the superego to stop attacks. This power protects an area of effect beyond your mind for 3 rounds. Every mind within the area defends against telepathic attacks with your Will save.

	This power imposes a modifier to the power check of any telepathic attack that targets anyone within its area of effect. This modifier depends on the telepathic attack that is being used, and are described below. This power does not grant any bonus or penalty in your saving throw against any telepathic attack.

	\Table{}{XC}{
	  \tableheader Telepathic Attack
	& \tableheader Power Check Modifier \\
	\psionic{Ego Whip}       & $-5$ \\
	\psionic{Id Insinuation} & $-3$ \\
	\psionic{Mind Thrust}    & $-5$ \\
	\psionic{Psionic Blast}  & $-3$ \\
	\psionic{Psychic Crush}  & $-3$ \\
	}

	You can manifest this power instantly, quickly enough to gain its benefits in an emergency. Manifesting the power is an immediate action. You can use this power even when it's not your turn.
}