\Psionic{Matter Bonding}{matter bonding}
{Psychokinesis}
{
	\textbf{Level:}
	Kineticist 5\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	9 meters\\
	\textbf{Area:}
	Surface of contact between two objects of no more than 40 cm$^2$\\
	\textbf{Saving Throw:}
	None (object)\\
	\textbf{Cost:}
	25 power points\\
	\textbf{Maintenance Cost:}
	5 pp/round\\
	\textbf{Prerequisites:}
	\psionic{psionic telekinesis}\\
	% \textbf{Critical Success:}
	% The rate of bonding increases to 160 cm$^2$ per round\\
	% \textbf{Critical Failure:}
	% You bond your own boots to the ground and become stuck\\
}
{
	\emph{Matter bonding} allows you to join two surfaces at the molecular level. The bond is permanent, but you can maintain the power to join larger surfaces. The rate of joining is 40 cm$^2$ per round, so large surfaces can be joined together with enough time. This power can be used on the following ways:

	\begin{enumerate*}
		\item \textit{Join objects together:} You can glue together objects, such as a sword to its sheath. You can use this option to fix a broken object by joining the shattered pieces. You need one manifestation of \emph{matter bonding} for each pair of pieces.

		\item \textit{Freeze an opponent's armor:} You can join two pieces of someone's armor, hindering their movement. If you freeze one boot, the opponent will not be able to move. If you freeze any other joint, the opponent will be entangled. The opponent may make a Strength check as a move action to tear free. The Strength check DC depends on the type of armor they are wearing:

		\TableOdd{}{*{2}{z{35mm}}}{
		\tableheader Armor type & \tableheader Strength Check DC \\
		Light armor  & 12 \\
		Medium armor & 15 \\
		Heavy armor  & 20 \\
		}
	\end{enumerate*}

	This power does not affect living matter.
}
