\Psionic{Matter Rearrangement}{matter rearrangement}
{Psychokinesis}
{
	\textbf{Level:}
	Kineticist 6\\
	\textbf{Manifesting Time:}
	2 hours\\
	\textbf{Range:}
	1.5 meter\\
	\textbf{Target:}
	One object\\
	\textbf{Saving Throw:}
	None \\
	\textbf{Cost:}
	30 power points\\
	\textbf{Maintenance Cost:}
	6 pp/hour\\
	\textbf{Prerequisites:}
	\psionic{matter manipulation}, \psionic{psionic telekinesis}\\
	% \textbf{Critical Success:}
	% The new material is extraordinary\\
	% \textbf{Critical Failure:}
	% The item is seriously flawed and utterly useless\\
}
{
	\emph{Matter rearrangement} is the psionic equivalent of alchemy. This power cannot create matter or mass from nothing, however. Nor can it change a material's state from liquid to solid, gas to liquid, and so on.% It is best suited to converting one sort of element into another, but it can also be used for more complex operations---neutralizing a poison, for example.

	This power has two uses: convert one element into another, or improving a non-consumable item. No matter the use, only 30 grams of material can be rearranged each hour.

	\textit{Convert Element:} Converting one element to another is usually a simple operation. The duration depends on the nature of the elements---if the materials are of different types, the process takes four times longer.

	\Table{}{lL}{
	\tableheader Material Type & \tableheader Examples \\
	Animal bone & Bone, ivory \\
	Animal skin & Fur, hide, scales \\
	Metal & Gold, iron, silver, steel, lead \\
	Mineral & Glass, obsidian, salt, stone \\
	Wood & Agafari, hardwood \\
	}

	% Typical conversions include steel to lead, or any metal to gold. More complex rearrangement, like changing a metal to glass or changing a wooden goblet to a ruby goblet, takes four times longer.

	The creation of gold coins from other metals is possible, but it's no way to get rich quick. At the rate of 30 grams per hour, it would take 16 hours---about two work days---to change 10 silver pieces into 10 gold pieces, for a net profit of 9 gold pieces.

	\textit{Improve an Item:} You can convert one regular piece of equipment into a masterwork. This can be done to weapons, armors, and some non-consumable equipment. The list of non-consumable equipment capable of becoming masterwork is: artisan's tools, manacles, musical instruments, and thieves' tools.

	For each day of use, you must succeed on an appropriate skill check to make the masterwork item (see \skill{Craft} skill).
}
