\Psionic{Metaconcert}{metaconcert}
{Metacreativity}
{
	\textbf{Level:}
	Shaper 5\\
	\textbf{Manifesting Time:}
	1 minute\\
	\textbf{Range:}
	6 meters\\
	\textbf{Target:}
	You and up to nine other willing psionic creatures in range\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	25 power points\\
	\textbf{Maintenance Cost:}
	5 pp/minute\\
	\textbf{Prerequisites:}
	Manifester level 9th, \psionic{adrenaline control}, \psionic{mindlink}\\
}
{
	You link your psychic might with other psionic creatures, creating an entity more powerful than the sum of its parts.

	When you manifest this power, a number of power points you designate flows from each participant into a collective pool. One individual is chosen as the \emph{metaconcert} conductor by mutual consent of the other participants (this is usually the manifester, but doesn't have to be). Until the power ends, this conductor directs the efforts of the group. Misty strands of glowing power link the brows of all the participants in a complex and shifting pattern.

	All the powers of each participant are known to the mental entity created with \emph{metaconcert} (which is under the conductor's command). This entity can't take any more actions than a normal individual, but it manifests all its powers more effectively. Each participant contributing to the entity provides a cumulative +1 bonus to save DCs that apply when manifesting a power or using a psi-like ability. Likewise, each individual provides a cumulative +1 bonus when the entity makes its own saving throws in response to powers or psi-like abilities.

	If the psionic entity takes ability damage from a psionic attack the total is divided among all the members as determined by the conductor.

	If the entity manifests a power that has an XP cost, all the participants pay an equal share (the conductor pays the remainder if the cost can't be divided evenly).

	Once linked, the participants must remain within a 6-meter-radius area, and as a group can move at a speed of 3 meters. If a participant moves outside the 6-meter-radius area occupied by the others (whether willingly or involuntarily), that individual drops out of the group, and the power point pool of the \emph{metaconcert} is instantly recalculated.

	All participants who leave before a \emph{metaconcert} ends or is dismissed reclaim a number of power points equal to the current power point pool divided by the number of members. If the conductor drops out, the power ends. That same number of points is removed from the power point pool.

	When a \emph{metaconcert} ends normally or is dismissed, remaining power points in the pool are divided among all the participants (the conductor receives the remainder if the points can't be divided evenly).
}