\Psionic{Mind Switch, True}{true mind switch}
{Telepathy [Mind-Affecting]}
{
	\textbf{Level:}
	Telepath 9\\
	\textbf{Manifesting Time:}
	1 minute\\
	\textbf{Saving Throw:}
	Will negates\\
	\textbf{Cost:}
	\psionic{contact}, 10,000 XP\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	Manifester level 18th, \psionic{mind switch}\\
}
{
	As \psionic{mind switch}, except as noted here. You permanently exchange bodies with the subject. Since this power's duration is instantaneous, you cannot be forced to return to your natural body by means of an \spell{antimagic field}, or a similar effect. If the subject's body dies while you are in it, you are dead. The subject immediately loses one level, but otherwise survives the experience in your natural body. If your natural body dies while the subject is in it, you immediately lose one level, but you likewise survive the experience in your new body.

	Your ``natural'' body is always considered to be the last one you switched out of. If you exchange bodies with a chain of multiple subjects, you need worry only about the welfare of the last body you switched with. In other words, if your mind is expelled from your current body, your mind returns to the last body you switched with, not to your original body. Similarly, if your original body dies but you have since switched minds with a second subject, you take no penalty. You lose a level only if the body you inhabited immediately prior to your current body is killed.
}