\Psionic{Mind Switch}{mind switch}
{Telepathy [Mind-Affecting]}
{
	\textbf{Level:}
	Telepath 7\\
	\textbf{Manifesting Time:}
	1 round\\
	\textbf{Range:}
	9 meters\\
	\textbf{Target:}
	You and one other \emph{contacted} creature\\
	\textbf{Saving Throw:}
	Will negates\\
	\textbf{Cost:}
	\psionic{contact}, 100 XP\\
	\textbf{Maintenance Cost:}
	7 pp/minute\\
	\textbf{Prerequisites:}
	Manifester level 14th, \psionic{psionic dominate}\\
}
{
	You can attempt to take control of a nearby living creature, forcing your mind (and soul) into its body, and its mind into your body. You can target any creature whose Hit Dice are equal to or less than your manifester level.

	You possess the target's body and force the creature's mind into your body unless it succeeds on a Will save. You can move your mind back into your own body whenever you desire, which returns the subject's mind to its own body and ends the power. If the manifestation succeeds, your life force occupies the host body, and the host's life force takes over yours.

	You can call on rudimentary or instinctive knowledge of the subject creature, but not upon its acquired or learned knowledge (such as skills and feats it possesses). The same is true for the subject in your body. The mind switch brings about the following changes.

	\begin{itemize*}
    \item You gain the type of your assumed body.
    \item You gain the Strength, Dexterity, and Constitution scores of your assumed body.
    \item You gain the natural armor, natural attacks, movement, and other simple physical characteristics of your assumed body.
    \item You gain the extraordinary special attacks and qualities of your assumed body, but you do not gain supernatural or spell-like abilities.
    \item You gain the possessions and equipment of your assumed body.
    \item You retain your own hit points, saving throws (possibly modified by new ability scores), class abilities, supernatural and spell-like abilities, spells and powers, and skills and feats (although skill checks use your new ability scores, and you may be temporarily unable to use feats whose requirements you do not meet in your new body).
	\end{itemize*}

	Supernatural abilities that require a certain body part may be unavailable in your new form.

	If either body is killed while the power is in effect, the other participant also dies when the power ends. If one participant's body becomes petrified, imprisoned by \spell{temporal stasis} or \spell{imprisonment}, or incapacitated in some other way, the other participant will be incapacitated in that way when the power ends.
}
