\Psionic{Mind Thrust}{mind thrust}
{Telepathy}
{
	\textbf{Level:}
	Telepath 2\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	See text\\
	\textbf{Target:}
	One creature\\
	\textbf{Saving Throw:}
	Will negates (see text)\\
	\textbf{Cost:}
	10 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	\psionic{contact}, \psionic{mindlink}\\
	% \textbf{Critical Success:}
	% No effect.\\
	% \textbf{Critical Failure:}
	% You lose all partial \emph{contacts}.\\
}
{
	\emph{Mind thrust} tries to ``short'' the synapses of the target.

	As a telepathic attack, \emph{mind thrust} has the following characteristics:
	\begin{itemize*}
		\item Will saving throw DC equal to 10 + \textit{manifester level}. Only psionic creatures can resist attempts of partial \psionic{contact}.
		\item You can attack the same target twice with a single manifestation. This requires two different power checks and two different saving throws (if applicable).
	\end{itemize*}

	\textbf{Contact:} If the target's mind has already been \emph{contacted}, and they lose one random power known for 2d6 days. This effect does not allow for a saving throw. Beyond establishing \psionic{contact}, \emph{mind thrust} has no effect on creatures without psionic powers.
	
	\textbf{Range:} You can increase the range of this power, but the farther the target is from you, the more difficult it is to use this power.

	\Table{}{CC}{
	  \tableheader Range
	& \tableheader Power Check DC Modifier \\
	27 meters & +0 \\
	60 meters & +2 \\
	90 meters & +5 \\
	}

	\textit{Augment:} For every 2 additional power points you spend, you increase the DC by 1. You can only spend a maximum of 8 additional power points this way.
}
