\Psionic{Mindflame}{mindflame}
{Telepathy [Evil]}
{
	\textbf{Level:}
	Telepath 6\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	6 meters\\
	\textbf{Area:}
	Cone-shaped spread\\
	\textbf{Saving Throw:}
	Fortitude negates (see text)\\
	\textbf{Cost:}
	30 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	Manifester level 8th, \psionic{mind thrust}, \psionic{psychic crush}\\
	% \textbf{Critical Success:}
	% Your manifester level is considered 5 levels higher.\\
	% \textbf{Critical Failure:}
	% You can't use this power for 2d8 weeks.\\
}
{
	All creatures with no active telepathic defenses within the area suffer the following ill effects.

	\Table{}{XX}{
	  \tableheader HD
	& \tableheader Effect \\

	Equal to manifester level   & Dazed \\
	Up to manifester level --1  & Stunned \\
	Up to manifester level --5  & Paralyzed \\
	Up to manifester level --10 & Unconscious \\
	Up to manifester level --15 & Comatose \\
	}

	The effects are not cumulative.

	\textit{Dazed:} The creature is dazed for 1d3 rounds.

	\textit{Stunned:} The creature is stunned for 2d6 rounds.

	\textit{Paralyzed:} The creature is paralyzed and helpless for 1d4 minutes.

	\textit{Unconscious:} The creature is unconscious for 2d4 minutes, and takes 1 point of Intelligence burn. The creature must make another Fortitude save or lapse into a coma (without the risk of death).

	\textit{Comatose:} The creature is rendered comatose for 1d6 days, and takes 1d3 points of Intelligence burn. The creature must make another Fortitude save or die at the end of their coma.

	The effects of \emph{mindflame} can be removed by \psionic{psychic chirurgery}, \spell{heal}, \spell{limited wish}, \spell{miracle}, \spell{wish}, \psionic{bend reality}, or \psionic{reality revision}.
}
