\Psionic{Planar Energy}{planar energy}
{Psychoportation [see text]}
{
	\textbf{Level:}
	Nomad 8\\
	\textbf{Manifesting Time:}
	1 round\\
	\textbf{Range:}
	54 meters; see text\\
	\textbf{Area or Target:}
	See text\\
	\textbf{Saving Throw:}
	See text\\
	\textbf{Cost:}
	40 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	\psionic{summon planar creature}\\
	% \textbf{Critical Success:}
	% Add one die of damage.\\
	% \textbf{Critical Failure:}
	% You summon a planar creature native to the plane you were trying to tap.\\
}
{
	You call upon one of the Inner Planes to smite your enemies. Each plane energy responds differently when you summon it. All energy summoned by this power goes back to its original plane.

	\Table{}{lz{19mm}L}{
	  \tableheader Plane
	& \tableheader Damage
	& \tableheader Area or Target \\
	% Elemental Fire            & 3d6 fire            & 3-meter cube \\
	% Paraelemental Sun         & 2d6 fire            & Up to two targets \\
	% Paraelemental Magma       & 6d6 fire            & One target \\
	% Quasi-elemental Ash       & 4d4 cold            & 54-meter cone \\
	% Quasi-elemental Lightning & 4d6 electricity     & 54-meter line \\
	% Quasi-elemental Salt      & 4d4 Strength        & 3-meter cube \\
	Elemental Air        & 8d6 sonic                & 18-meter cone-shaped burst \\
	Elemental Earth      & 6d6 plus speed penalty   & Cylinder (3-m-radius, 12 m high) \\
	Elemental Fire       & 8d6 fire                 & 3-m-radius spread \\
	Elemental Water      & 8d6 cold                 & Cylinder (3-m-radius, 12 m high) \\
	Paraelemental Magma  & 10d6 fire for 1d3 rounds & One target \\
	Paraelemental Rain   & 8d6 electricity          & 54-m line \\
	Paraelemental Silt   & 8d4 acid plus gray death & One target \\
	Paraelemental Sun    & 4d6 fire plus blindness  & 9-meter cone-shaped burst \\
	Negative Energy      & 2d4 negative levels      & One target \\
	Positive Energy      & 5d8 positive energy      & One target \\
	}

	\textbf{Elemental Air:} You summon the loud noises of unimaginable vortexes from the Elemental Plane of Air. The air comes as a cone of 18 meters, blasting 8d6 points of sonic damage from your location. A successful Reflex save reduces the damage in half.

	This use of the power give the subtypes Air and Sonic.

	\textbf{Elemental Earth:} You summon the rocks and minerals from the Elemental Plane of Earth. A rain of 200-kg rocks starts pouring from 12 meters above the ground dealing 1d6 points of bludgeoning damage plus 1d6 for each 3-meter increment of distance to any creature within the area. And minerals spike from the ground, dealing 1d6 points of piercing damage to any creature within the area. A successful Reflex save reduces all damage in half. Creatures on the ground who fail the Reflex save have their speed reduced to half normal for 24 hours. A \spellref{cure light wounds}{cure} spell or a successful \skill{Heal} check (using the power's save DC) remove this penalty.

	This use of the power give the subtype Earth.

	\textbf{Elemental Fire:} You summon heat from the Elemental Plane of Fire, that explodes similar to a \spell{fireball} when in contact to the Athasian pressure. A successful Reflex save reduces the damage in half.

	This use of the power give the subtype Fire.

	\textbf{Elemental Water:} You summon waters from the coldest depths of the Elemental Plane of Water, removing any heat from those within its volume. A successful Reflex save reduces the damage in half.

	This use of the power give the subtypes Cold and Water.

	\textbf{Paraelemental Magma:} You summon flowing lava from the Paraelemental Plane of Magma, engulfing the target. The lava deals 10d6 points damage. The damage continues for 1d3 rounds after the initial blast. A successful Reflex save reduces the damage in half, including the continuous damage.

	This use of the power give the subtypes Earth and Fire.

	\textbf{Paraelemental Rain:} You summon a lightning bolt directly from the Paraelemental Plane of Rain. The lightning bolt damages each creature in its area. The bolt starts starts at your fingertips. A successful Reflex save reduces the damage in half.

	This use of the power give the subtypes Air, Electricity, and Water.

	\textbf{Paraelemental Silt:} You summon a blast of silt from the Paraelemental Plane of Silt. This blast deals 8d4 points of acid damage. A successful Reflex save reduces the damage in half. If the target fails their Reflex save, they must make a Fortitude save or contract gray death immediately (no incubation period). The initial saving throw uses \emph{summon planar creature}'s normal save DC.

	This use of the power give the subtypes Acid, Earth, and Water.

	\textbf{Paraelemental Sun:} You summon a cone of radiant fire from the Paraelemental Plane of Sun. This attack deals 4d6 points of fire damage to any creature in the area. A successful Reflex save reduces the damage in half. If a creature fails their Reflex save, they also become temporarily blind. The blindness lasts for 1 round.

	This use of the power give the subtypes Air, Light, and Fire.

	\textbf{Negative Energy:} You summon a blast from the Negative Energy Plane. This blast deals 2d4 negative levels to the target. A successful Reflex save reduces the damage in half. An undead struck by this blast gains 2d4$\times$5 temporary hit points for 1 hour, instead.

	This use of the power give no subtypes.
	
	\textbf{Positive Energy:} You summon a blast from the Positive Energy Plane. This blast deals 5d8 points of damage to an undead target. A successful Reflex save reduces the damage in half. A living target struck by this blast gains 5d8 temporary hit points for 1 hour, instead.

	This use of the power give no subtypes.
}
