\Psionic{Precognition}{precognition}
{Clairsentience}
{
	\textbf{Level:}
	Seer 6\\
	\textbf{Casting Time:}
	5 minutes\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Cost:}
	11 power points\\
	\textbf{Maintenance Cost:}
	6 pp/hour\\
	% \textbf{Critical Success:}
	% The insight bonus increases to +4\\
	% \textbf{Critical Failure:}
	% No effect\\
}
{
	\emph{Precognition} allows your mind to glimpse fragments of potential future events---what you see will probably happen if no one takes action to change it. However, your vision is incomplete, and it makes no real sense until the actual events you glimpsed begin to unfold. That's when everything begins to come together, and you can act, if you act swiftly, on the information you previously received when you manifested this power.

	In practice, manifesting this power grants you a ``precognitive edge.'' This edge can be used in two different ways:
	\begin{enumerate*}
	\item +2 insight bonus that you can apply at any time to either an attack roll, a damage roll, or a saving throw;
	\item You can have advantage in a single skill check.
	\end{enumerate*}

	You can elect to apply the edge to the roll after you determine that your unmodified roll is lower than desired.

	You can maintain the precognitive edge for one hour plus one hour for each three points you exceed the power check DC. The power is discharged when you use the edge.

	\emph{Precognition} is tiring. Regardless of the edge chosen, you must rest for at least 10 minutes before you can use another clairsentient power (the use of other disciplines is not affected).

	You can have only a single precognitive edge at one time.
}