\Psionic{Predestination}{predestination}
{Clairsentience}
{
	\textbf{Level:}
	Seer 7\\
	\textbf{Manifesting Time:}
	1 hour\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	Creature touched\\
	\textbf{Cost:}
	35 power points\\
	\textbf{Maintenance Cost:}
	7 pp/year\\
	\textbf{Prerequisites:}
	\psionic{precognition}\\
	% \textbf{Critical Success:}
	% You peer twice as far into the future\\
	% \textbf{Critical Failure:}
	% No effect\\
}
{
	You predict the general destiny of a single creature. That destiny is based on the current situation only---future actions may change the target's predicted destiny.

	Before making the power check, you must spend a full hour alone with the subject (or isolated if you are using the power on yourself). The two converse about the past and present, and the subject makes known their plans for at least the immediate future. If the subject is not completely honest with you, the power check automatically fails.

	If you succeed, you gain a broad understanding of the target creature's prospects for one year in the future. By instructing the target, you infuse them with three ``predestination edges'' per year. This edge can be used in two different ways:
	\begin{enumerate*}
	\item +5 insight bonus that they can apply at any time to either an attack roll, a damage roll, or a saving throw;
	\item They can take 10 with advantage in a single skill check, even if distracted or threatened.
	\end{enumerate*}

	A creature can't have more than one \emph{predestination} active. Both you and the target can dismiss this power at any time. The power is discharged when the target uses all predestination edges.

	\textit{Augment:} For every 5 additional power points you spend, this power can foresee another year in advance and the Difficulty Class of the power check increases by +1.
}