\Psionic{Reality Revision}{reality revision}
{Metacreativity}
{
	\textbf{Level:}
	Shaper 9\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	See text\\
	\textbf{Target, Effect, or Area:}
	See text\\
	\textbf{Saving Throw:}
	None; see text\\
	\textbf{Cost:}
	45 power points, 5,000 XP or more (see below)\\
	\textbf{Maintenance Cost:}
	See text\\
	\textbf{Prerequisites:}
	Manifester level 18th, \psionic{bend reality}\\
}
{
	As \psionic{bend reality}, but with more farreaching effects. A \emph{reality revision} can produce any one of the following effects.

	\begin{itemize*}
	\item Duplicate any power of 8th level or lower, provided the power is not prohibited to you.
	% \item Duplicate any other power (but not a spell) of 6th level or lower, such as a psychic warrior power.
	\item Duplicate any power of 7th level or lower even if it's a power prohibited to you.
	\item Duplicate any spell of 6th level or lower.
	\item Undo the harmful effects of many other powers, such as \psionic{microcosm}, \spell{geas/quest}, or \psionic{insanity}.
	\item Create a mundane item of up to 25,000 cp in value.
	\item Create a psionic item, or add to the powers of an existing psionic item (see XP cost below).
	\item Grant a creature a +1 inherent bonus to an ability score. Two to five reality revisions manifested in immediate succession can grant a creature a +2 to +5 inherent bonus to an ability score. Inherent bonuses are instantaneous, so they cannot be negated or dispelled. An inherent bonus cannot exceed +5 for a single ability score. Inherent bonuses to a particular ability score do not stack; only the best one applies.
	\item Remove injuries and afflictions. A single \emph{reality revision} can aid one creature per manifester level, and all subjects are cured of the same kind of affliction. \emph{Reality revision} can not restore the experience point loss from manifesting a power or casting a spell, or the level or Constitution loss from being returned to life by those effects that reduce level or Constitution.
	\item Revive the dead. \emph{Reality revision} can bring a dead creature back to life by duplicating a \spell{resurrection} spell. This power can revive a dead creature whose body has been destroyed, but the task takes two manifestations of \emph{reality revision}, one to recreate the body and another to infuse the body with life again. \emph{Reality revision} cannot prevent a character who is brought back to life from losing a level.
	\item Transport travelers. This power can lift one creature per manifester level from anywhere on any plane and place those creatures anywhere else on any plane regardless of local conditions. An unwilling target gets a Will save to negate the effect, and power resistance (if any) applies.
	\item Undo misfortune. \emph{Reality revision} can undo a single recent event. Manifesting the power forces a reroll of any roll made within the last round (including your last turn). Reality reshapes itself to accommodate the new result. The reroll, however, may be as bad as or worse than the original roll. An unwilling target gets a Will save to negate the effect, and power resistance (if any) applies.
	\end{itemize*}

	You can try to use \emph{reality revision} to produce more powerful effects than these, but doing so is dangerous. The manifestation may pervert your intent into a literal but undesirable fulfillment or only a partial fulfillment.

	Duplicated powers allow saves as normal (but save DCs are calculated as though the power is 9th level).

	When a manifestation duplicates a power that has an XP cost, you must pay 5,000 XP or that cost, whichever is more. When a manifestation creates or improves a psionic item, you must pay twice the normal XP cost for crafting or improving the item, plus an additional 5,000 XP.
}