\Psionic{Reduction}{reduction}
{Psychometabolism}
{
	\textbf{Level:}
	Egoist 2\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	10 power points\\
	\textbf{Maintenance Cost:}
	2 pp/round\\
	% \textbf{Critical Success:}
	% You can decrease your size by two size categories instead of one.\\
	% \textbf{Critical Failure:}
	% You grow and gain a $-2$ size penalty to Dexterity.\\
}
{
	This power causes instant diminution, halving your height, length, and width and dividing your weight by 8. This decrease changes your size category to the next smaller one. You gain a +2 size bonus to Dexterity, a $-2$ size penalty to Strength (to a minimum effective Strength score of 1), a +1 size bonus on attack rolls, and a +1 size bonus to Armor Class due to your reduced size. If your new size is Tiny, you have a space of 75 centimeters and a natural reach of 0 meters (meaning that you must enter an opponent's square to attack). If your new size is Diminutive, you have a space of 30 centimeters and a natural reach of 0 meters. This power doesn't change your speed.

	All your equipment, worn or carried, is similarly reduced by the power. Melee and projectile weapons deal less damage. Other psionic or magical properties are not affected by this power. Any affected item that leaves your possession (including a projectile or thrown weapon) instantly returns to its normal size. This means that thrown weapons deal their normal damage (projectiles deal damage based on the size of the weapon that fired them). Multiple effects that reduce size do not stack, which means (among other things) that you can't use a second manifestation of this power to further reduce yourself.

	\textit{Augment:} If you spend 10 additional power points,  this power decreases your size by two size categories. You gain a +4 size bonus to Dexterity, a $-4$ size penalty to Strength (to a minimum effective Strength score of 1), a +2 size bonus on attack rolls, and a +2 size bonus to Armor Class due to your reduced size. This increases the Difficulty Class of the power check by +2.
}