\Psionic{Schism}{schism}
{Metacreativity}
{
	\textbf{Level:}
	Shaper 8\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	40 power points\\
	\textbf{Maintenance Cost:}
	8 pp/round\\
	\textbf{Prerequisites:}
	Manifester level 13th, \psionic{psychic chirurgery}\\
}
{
	Your mind splits into two independent parts. Each part functions in complete autonomy, like two characters in one body. Your new ``second mind'' does not control your body physically but is free to take one standard action in each round if the action is purely mental (such as manifesting a power) in the same round you take your normal actions.

	Your second mind can manifest powers using your power point reserve, but all its abilities have a special $-3$ penalty. This special penalty limits the highest power level it can manifest, as well as any power check it makes to manifest or win a psychic contest. Your second mind doesn't provoke attacks of opportunity when manifesting a power, because doing so doesn't distract your primary mind.

	Your second mind takes its first action on your turn in the round after \emph{schism} is manifested.

	Both your minds communicate with each other telepathically. If you are subject to a compulsion or charm effect while you are of two minds, make a second saving throw if you fail the first. If you fail both, then the \emph{schism} ends and you are affected normally by the power. If you fail just one, the \emph{schism} ends immediately, but you are not subject to the compulsion or charm.

	Your second mind does not gain any advantages if you are subject to a \spell{haste} effect, although you gain the overall standard benefits.
}