\Psionic{Secrete Poison}{secrete poison}
{Psychometabolism}
{
    \textbf{Level:}
    Egoist 3\\
    \textbf{Manifesting Time:}
    1 minute\\
    \textbf{Range:}
    Personal\\
    \textbf{Target:}
    You\\
    \textbf{Saving Throw:}
    None\\
    \textbf{Cost:}
    15 power points\\
    \textbf{Maintenance Cost:}
    Instantaneous\\
}
{
    You produce natural toxins from your own body. These toxins can be secreted by your saliva, or be in your bloodstream. If you chose to create in your bloodstream, you can nick yourself with a blade to get it. There are two uses for this power:

    \textit{Produce Poison:} The poison can be used as an injury poison, dealing 1d10 points of temporary Dexterity damage immediately and another 1d10 points of temporary Dexterity damage 1 minute later.

    \textit{Produce Antitoxin:} You can produce one vial of antitoxin per manifestation. Drinking this vial grants +5 alchemical bonus on Fortitude saves against poison for 1 hour.

    \textit{Augment:} You can augment this power in one or more of the following ways.
    \begin{enumerate*}
    \item If you spend  5 additional power points, you can change the type of poison to ingested.
    \item If you spend 10 additional power points, you can change the type of poison to contact or inhaled.
    \item You can change the poison damage. This can also increase the cost or the Difficulty Class of the power check:
    \end{enumerate*}

        \Table{}{cCc}{
      \tableheader Cost
    & \tableheader Primary/Secondary Damage
    & \tableheader Power Check DC Modifier \\
    15 & 1d10 Dex               & +0 \\
    15 & Paralysis for 1 minute & +1 \\
    20 & 1d10 Str               & +2 \\
    20 & 1d10 Con               & +3 \\
    }
}
