\Psionic{Sensitivity to Psychic Impressions}{sensitivity to psychic impressions}
{Clairsentience}
{
	\textbf{Level:}
	Seer 2\\
	\textbf{Casting Time:}
	2 minutes\\
	\textbf{Range:}
	18 meters\\
	\textbf{Effect:}
	18-m-radius emanation, centered on you\\
	\textbf{Cost:}
	3 power points\\
	\textbf{Maintenance Cost:}
	2 pp/minute\\
	% \textbf{Critical Success:}
	% You gain an unusally clear understanding of each event\\
	% \textbf{Critical Failure:}
	% You are a target of a \spell{magic jar} from an angry ghost\\
}
{
	You gain historical vision in a given location. Rooms, streets, tunnels, and other discrete locations accumulate psychic impressions left by powerful emotions experienced in a given area. These impressions offer you a picture of the location's past.

	The types of events most likely to leave psychic impressions are those that elicited strong emotions: battles and betrayals, marriages and murders, births and great pain, or any other event where one emotion dominates. Everyday occurrences leave no residue for a manifester to detect.

	The vision of the event is dreamlike and shadowy. You do not gain special knowledge of those involved in the vision, though you might be able to read large banners or other writing if they are in your language.

	Beginning with the most recent significant event at a location and working backward in time, you can sense one distinct event for every minute you maintain concentration, if any such events exist to be sensed. Your sensitivity depends on your power check: for every point exceeding the power check DC, you may sense an additional strong event.
}