\Psionic{Shadow Body}{shadow body}
{Psychometabolism}
{
	\textbf{Level:}
	Egoist 5\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	25 power points\\
	\textbf{Maintenance Cost:}
	5 pp/round\\
	% \textbf{Critical Success:}
	% You gain all special abilities of a shadow.\\
	% \textbf{Critical Failure:}
	% You must make a Reflex save, or one random item becomes shadow and is lost forever.\\
}
{
	Your body and all your equipment are subsumed by your shadow. As a living shadow, you blend perfectly into any other shadow and vanish in darkness. You appear as an unattached shadow in areas of full light.

	You can move at your normal speed, on any surface, including walls and ceilings, as well as across the surfaces of liquids---even up the face of a waterfall.

	Your space does not change, so you cannot move into locations you would not normally be able to move into.

	While in your shadow body, you gain damage reduction 10/magic and darkvision out to 18 meters. You are immune to extra damage from critical hits, ability damage, disease, drowning, and poison. You take only half damage from acid, electricity, and fire of all kinds.

	While affected by this power, you can be detected by powers that read thoughts, life, or presences (including \spell{true seeing}), or if you make suspicious movements in lighted areas.

	You cannot harm anyone physically or manipulate any objects, but you can use your powers normally. Doing so may attract notice, but if you remain in a shadowed area, you get a +15 bonus on your \skill{Hide} check to remain unnoticed.
}