\Psionic{Summon Planar Creature}{summon planar creature}
{Psychoportation [Summoning]}
{
	\textbf{Level:}
	Nomad 7\\
	\textbf{Manifesting Time:}
	12 minutes\\
	\textbf{Range:}
	180 meters (see text)\\
	\textbf{Effect:}
	One \emph{teleported} creature\\
	\textbf{Cost:}
	35 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	\psionic{psionic teleport}\\
	% \textbf{Critical Success:}
	% The creature enjoys the summoning and won't be angry with you\\
	% \textbf{Critical Failure:}
	% You attract the attention of a powerful, extraplanar creature without summoning it\\
}
{
	You reach into another plane, grab whatever creature you happen to find there, and \emph{teleport} it to your own plane. The victim will be sickened for one round after arriving. A magical summons offers some control over a planar creature, and usually returns that creature to its home automatically. This psionic power does neither; it merely \emph{teleports} something. To be rid of the creature, you must \spell{banish} it, \emph{teleport} it again, kill it, or control it somehow. If the creature is intelligent, you might reason with it. However, the creature is almost certain to fly into a murderous rage when it discovers its plight. The creature, at least initially, has no idea who summoned it. Its anger is likely to be vented against the first target it finds.

	The range of this power depends on how much your power check exceeds the DC.

	\Table{}{lC}{
	  \tableheader Power Check Result
	& \tableheader Range \\
	DC                 & 9 meters \\
	DC +1              & 24 meters \\
	Greater than DC +1 & 180 meters \\
	}

	You choose the plane from which the creature will come, but you do not choose the creature; that's determined at random.
}