\Psionic{Teleport, Psionic}{psionic teleport}
{Psychoportation (Teleportation)}
{
	\textbf{Level:}
	Nomad 5\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	9 meters (see text)\\
	\textbf{Target:}
	You (see text)\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	See text\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	% \textbf{Critical Success:}
	% Manifestation cost reduced by 20\%\\
	% \textbf{Critical Failure:}
	% You and affected creatures become dazed for 1 round, and sickened for 2 rounds\\
}
{
	You instantly transfer yourself from your current location to any other spot within range. You always arrive at exactly the spot desired---whether by simply visualizing the area or by stating direction. You can bring along objects as long as their weight doesn't exceed your light load.

	You simply cease to exist in your previous location and springs into being at the destination. There is a slight, audible ``pop'' at both ends, as air rushes into the sudden vacuum or is instantly displaced.

	If you arrive in a place that is already occupied by a solid body, you and each creature traveling with you take 1d6 points of damage and are shunted to a random open space on a suitable surface within 30 meters of the intended location.

	If there is no free space within 30 meters, you and each creature traveling with you take an additional 2d6 points of damage and are shunted to a free space within 300 meters. If there is no free space within 300 meters, you and each creature traveling with you take an additional 4d6 points of damage and the spell simply fails.

	\textit{Augment:} You can augment this power in one or more of the following ways.
	\begin{enumerate*}
	\item If you spend 20 additional power points, you may also bring two additional willing Medium or smaller creatures (carrying gear or objects up to their light load). A Large creature counts as two Medium creatures. All creatures to be transported must be in contact with one another, and at least one of those creatures must be in contact with you.
	\item If you spend 10 additional power points, you can bring along objects if their weight doesn't exceed your heavy load.
	\item If you spend additional power points, you can increase this power's range. The range also increases the Difficulty Class of the power check: 
	\end{enumerate*}

	\Table{}{cCc}{
	\tableheader Cost & \tableheader Range & \tableheader Power Check DC Modifier \\
	 9 & 9 meters         & $-1$ \\
	20 & 90 meters        &  +0  \\
	30 & 900 meters       &  +1  \\
	40 & 9 kilometers     &  +2  \\
	50 & 90 kilometers    &  +3  \\
	60 & 900 kilometers   &  +4  \\
	70 & 9,000 kilometers &  +5  \\
	}

}