\Psionic{Telekinesis, Psionic}{psionic telekinesis}
{Psychokinesis}
{
	\textbf{Level:}
	Kineticist 2\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	15 meters\\
	\textbf{Target:}
	One object of up to 3 kg (see text)\\
	\textbf{Saving Throw:}
	Will negates (object)\\
	\textbf{Cost:}
	3 power points\\
	\textbf{Maintenance Cost:}
	2 pp/round\\
	% \textbf{Critical Success:}
	% The blow also knocks the target on a failed save\\
	% \textbf{Critical Failure:}
	% You are the target\\
}
{
	\emph{Telekinesis} is the ability to move objects through space without touching them.  All telekinetic efforts tend to be physically taxing, because they involve real work. Moving small, light objects is relatively easy. As the objects become more massive, the task becomes significantly more difficult.

	You can move an object up to 9 meters per round. You can use the object as a weapon. In this case, you attack using your base attack bonus and your Intelligence modifier in place of your Strength or Dexterity modifier, with a penalty equaling \onethird the object's weight in kilograms.

	\textit{Augment:} Every kilogram above the initial 3 kg increases the cost by 1 power point, the maintenance cost by \onehalf power point per round, and the power check DC by \onethird, as shown in the table. 

	\Table{}{Lccc}{
	\tableheader Weight & \tableheader Cost & \tableheader Maintenance Cost & \tableheader Power Check DC Modifier \\
	Up to 3 kg  &  3 & 2 pp/round & +0 \\
	3.1--4.0 kg &  4 & 2 pp/round & +0 \\
	4.1--5.0 kg &  5 & 3 pp/round & +0 \\
	5.1--6.0 kg &  6 & 3 pp/round & +1 \\
	6.1--7.0 kg &  7 & 4 pp/round & +1 \\
	7.1--8.0 kg &  8 & 4 pp/round & +1 \\
	8.1--9.0 kg &  9 & 5 pp/round & +2 \\
	+1 kg       & +1 & +\onehalf pp/round & +\onethird \\
	}
}