\Psionic{Time Duplicate}{time duplicate}
{Psychoportation}
{
	\textbf{Level:}
	Nomad 8\\
	\textbf{Manifesting Time:}
	1 swift action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	40 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	\textbf{Prerequisites:}
	\psionic{time travel}\\
	% \textbf{Critical Success:}
	% The present self also gains the insight bonus, as the future self warns about the future.\\
	% \textbf{Critical Failure:}
	% You must make a successful Will save, or become dazed for 1d6 hours.\\
}
{
	You travel forward in time to borrow a future self, bringing it back to aid you in the present and creating an identical duplicate of yourself. You only travel a round or two into the future, creating a strange hiccup in your own existence:

	\textit{1st Round:} Your self from round two arrives, so there are now two of you. Both can act normally during this round, but remember that the present self has used his swift action to manifest this power. 

	The future self gains gains a +4 insight bonus to Armor Class, +4 insight bonus to saving throws, and a +2 insight bonus to any attack rolls he makes. The future self is also never surprised or flat-footed during this round.

	\textit{2nd Round:} You journey back to round one to help yourself, so you are nowhere. You have no existence at all during this round.

	\textit{3rd Round:} The future you who was borrowed from round two returns at the same spot and in the same condition he was in when round two ended. The \emph{time duplicate} has ended.

	If the future self is injured or killed, there is no effect on the present you, other than the fact that you can cringe in anticipation of the wounds you are going to get and possibly die from. However, any injuries to the present self are immediately duplicated on the future self.
}
