\Psionic{Time Dilation}{time dilation}
{Psychoportation}
{
	\textbf{Level:}
	Nomad 5\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	25 power points; see text\\
	\textbf{Maintenance Cost:}
	None; see text\\
	\textbf{Prerequisites:}
	\psionic{time travel}\\
	% \textbf{Critical Success:}
	% The \emph{time dilation} is improved by one step at no additional cost.\\
	% \textbf{Critical Failure:}
	% You must make a successful Will save or age 1d10 years.\\
}
{
	You change the way time flows through you. You can make yourself faster or slower relative to the world around you.

	You need a successful power check each time you cast spells or manifest powers that interact with creatures in the normal time frame. Interacting with the normal time frame is not easy.

	\textit{Haste:} You gain additional turns each round. The total number of additional turns you can maintain with a single manifestation is equal to your level. For example, a 9th-level psion could speed up her time flow $\times2$ for 9 rounds (9 extra turns), $\times3$ for 4 rounds (8 extra turns), or $\times4$ for 3 rounds (9 extra turns).

	Those additional turns count as full rounds for duration of spells, maintenance costs, and so on. You accelerated your time frame in all aspects.

	\textit{Slow:} You slow yourself down relative to the outside world. You can maintain this slowed state for 10 minutes per level (in your own time frame), with a single manifestation. For example, a 9th-level psion could slow down her time flow for a total of 90 minutes of her own time, which could mean for the outside world: 900 minutes (15 hours), if \nicefrac{1}{10}; 1,800 minutes (30 hours), if \nicefrac{1}{20}; or 4,500 minutes (75 hours), if \nicefrac{1}{50}.

	You are effectively in a different time frame for all purposes, so poison, spell duration, maintenance costs, and even water consumption are all in respect to this slowed down time frame.

	You can end this power at any time, but your perception is slowed down. You are flat-footed for one round after you end \emph{time dilation}.

	\textit{Augment:} If you spend additional power points, you can increase the rate at which time is dilated. This also increases the Difficulty Class of the power check:

	\Table{}{cCCc}{
	& \multicolumn{2}{c}{\tableheader Time Rate} &\\
	\cmidrule[0.5pt]{2-3}
	  \tableheader Cost
	& \tableheader Haste
	& \tableheader Slow
	& \tableheader Power Check DC Modifier \\
	25 & $\times2$ (+1 turn)  & \nicefrac{1}{10} & +0 \\
	35 & $\times3$ (+2 turns) & \nicefrac{1}{20} & +2 \\
	45 & $\times4$ (+3 turns) & \nicefrac{1}{50} & +4 \\
	}
}
