\Psionic{Time Hop, Personal}{personal time hop}
{Psychoportation}
{
	\textbf{Level:}
	Nomad 3\\
	\textbf{Manifesting Time:}
	1 mental action\\
	\textbf{Range:}
	Personal\\
	\textbf{Target:}
	You\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	15 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	% \textbf{Critical Success:}
	% No effect.\\
	% \textbf{Critical Failure:}
	% You are sickened for the same number of rounds as you intended to hop.\\
}
{
	You \emph{hop} forward in time 1 round. In effect, you seem to disappear in a shimmer of silver energy, then reappear after the duration of this power expires. You see everything frozen around you just as it will be when that moment in the future actually arrives. For gameplay purposes, you reposition yourself in the turn you reapear.

	You enter a different reality when you use this power. No one in the ``still life'' that surrounds you can see or detect you in any way. You can move freely through the environment, putting yourself wherever you want to be when you return to normal time. But you cannot affect anything around yourself, nor can anything affect you. Even two time-hopping characters are completely invisible to each other. 

	You do not exist for any normal game purpose during the period when you \emph{time hop}. If, for example, a \spell{fireball} spell detonates in the room while you \emph{time hop}, you are completely protected against its effects. In fact, unless the blast leaves visible effects (charred walls or corpses or sulfurous fumes), you won't even know it happened. You see none of the intervening events.

	\textit{Augment:} If you spend additional power points, you can increase this power's duration. The duration also increases the Difficulty Class of the power check:

	\Table{}{cCc}{
	  \tableheader Cost
	& \tableheader Duration
	& \tableheader Power Check DC Modifier \\
	15 & 1 round  & +0 \\
	20 & 2 rounds & +2 \\
	30 & 3 rounds & +5 \\
	}
}
