\Psionic{Tower of Iron Will}{tower of iron will}
{Universal}
{
	\textbf{Level:}
	Psion 2\\
	\textbf{Manifesting Time:}
	1 immediate action\\
	\textbf{Range:}
	1.5 meter\\
	\textbf{Area:}
	1.5-meter emanation centered on you\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Cost:}
	10 power points\\
	\textbf{Maintenance Cost:}
	None (Instantaneous)\\
	% \textbf{Critical Success:}
	% The area of effect increases to 3 meters.\\
	% \textbf{Critical Failure:}
	% You are ``lost inside yourself'' and cannot use psionic powers for 1d4 hours.\\
}
{
	\emph{Tower of iron will} relies upon the superego to build an unassailable haven for the brain. This power protects an area of effect beyond your mind for one round. Every mind within the area defends against telepathic attacks with your Will save.

	This power imposes a modifier to the power check of any telepathic attack that targets anyone within its area of effect. This modifier depends on the telepathic attack that is being used, and are described below. This power does not grant any bonus or penalty in your saving throw against any telepathic attack.

	\Table{}{XC}{
	  \tableheader Telepathic Attack
	& \tableheader Power Check Modifier \\
	\psionic{Ego Whip}       & $-4$ \\
	\psionic{Id Insinuation} & $-4$ \\
	\psionic{Mind Thrust}    & $-4$ \\
	\psionic{Psionic Blast}  & $-4$ \\
	\psionic{Psychic Crush}  & $-4$ \\
	}

	You can manifest this power instantly, quickly enough to gain its benefits in an emergency. Manifesting the power is an immediate action. You can use this power even when it's not your turn.
}