\Psionic{Wormhole}{wormhole}
{Psychoportation [Teleportation]}
{
	\textbf{Level:}
	Nomad 5\\
	\textbf{Manifesting Time:}
	10 minutes\\
	\textbf{Range:}
	18 meters\\
	\textbf{Effect:}
	Two extradimensional portals\\
	\textbf{Saving Throw:}
	Will negates; see text\\
	\textbf{Cost:}
	25 power points\\
	\textbf{Maintenance Cost:}
	5 pp/round\\
	\textbf{Prerequisites:}
	\psionic{psionic dimension door}\\
	% \textbf{Critical Success:}
	% The maintenance costs are cut in half (rounded down).\\
	% \textbf{Critical Failure:}
	% You create a dimensional vortex that transports you 15 to 150 kilometers in a random (horizontal) direction, unless you succeed in a Will save.\\
}
{
	You can open a door between two points, no matter how far apart they may happen to be (at least theoretically). It resembles the power \psionic{psionic dimension door}, but on a much larger scale. You must open one end within 18 meters of yourself. The portal may have any orientation and be any size up to 3 meters by 3 meters square.

	The other end of the wormhole will be of identical size and can be placed at any point you have ever seen. It can also be positioned at any place you can reference from where you currently are, whether or not you have ever actually been there. For example, ``10 kilometers east of where I am now.''

	Once created, the wormhole's entrances remain motionless. Anything can pass through. to be instantly transported to the other side. You could conceivably transport an entire army or a mekillot wagon by spending enough power points. If an object cannot fit entirely within the wormhole's mouth, it cannot be transported.

	If you try to use this power to transport an unwilling creature, that creature gains a Will saving throw to avoid being affected.

	\textit{Augment:} You can augment this power in one or more of the following ways.
	\begin{enumerate*}
	\item You can increase the size of the wormhole, increasing the Difficulty Class of the power check by 2 for each doubling.
	
	\vskip.5em
	
	\TableOdd{}{p{42mm}c}{
	  \tableheader Wormhole Size
	& \tableheader Power Check DC Modifier \\
	 3 m $\times$  3 m & +0 \\
	 6 m $\times$  6 m & +2 \\
	12 m $\times$ 12 m & +4 \\
	24 m $\times$ 24 m & +6 \\
	Double the size    & additional +2 \\
	}

	\item If you spend additional power points, you can increase the distance between portals. Increasing this distance also increases the maintenance cost: 

	\vskip.5em

	\TableOdd{}{p{36mm}cc}{
	  \tableheader Distance between Portals
	& \tableheader Initial Cost
	& \tableheader Maintenance Cost \\
	90 meters         &  25 & 5 pp/round \\
	900 meters        &  35 & 10 pp/round \\
	15 kilometers     &  45 & 15 pp/round \\
	150 kilometers    &  60 & 20 pp/round \\
	1,500 kilometers  &  75 & 25 pp/round \\
	15,000 kilometers & 100 & 30 pp/round \\
	Interplanetary    & 150 & 50 pp/round \\
	}
	\end{enumerate*}
}
