\subsection{Vision and Light}

\Table{Light Sources and Illumination}{lCCc}{
\tableheader Object & \tableheader Bright & \tableheader Shadowy & \tableheader Duration\\
Candle & n/a\footnotemark[1] & 5 ft. & 1 hr. \\
Everburning torch & 6 m & 12 m & Permanent \\
Lamp, common & 4.5 m & 9 m & 6 hr./pint \\
Lantern, bullseye\footnotemark[2] & 18-m cone & 36-m cone & 6 hr./pint \\
Lantern, hooded & 9 m & 18 m & 6 hr./pint \\
Sunrod & 9 m & 18 m & 6 hr. \\
Torch & 6 m & 12 m & 1 hr. \\

\rowcolor{white}\\
\cmidrule[0pt]{1-4}
\tableheader Spell & \tableheader Bright & \tableheader Shadowy & \tableheader Duration \\
\spell{Continual Flame} & 6 m & 12 m & Permanent \\
\spell{Dancing Lights} (torches) & 6 m (each) & 12 m (each) & 1 min. \\
\spell{Daylight} & 18 m & 36 m & 30 min. \\
\spell{Light} & 6 m & 12 m & 10 min. \\
\TableNote{4}{1 A candle does not provide bright illumination, only shadowy illumination.}\\
\TableNote{4}{2 A bullseye lantern illuminates a cone, not a radius.}\\
}

Dwarves and half-orcs have darkvision, but everyone else needs light to see by. See \tabref{Light Sources and Illumination} for the radius that a light source illuminates and how long it lasts.

In an area of bright light, all characters can see clearly. A creature can't hide in an area of bright light unless it is invisible or has cover.

In an area of shadowy illumination, a character can see dimly. Creatures within this area have concealment relative to that character. A creature in an area of shadowy illumination can make a Hide check to conceal itself.

In areas of darkness, creatures without darkvision are effectively blinded. In addition to the obvious effects, a blinded creature has a 50\% miss chance in combat (all opponents have total concealment), loses any Dexterity bonus to AC, takes a $-2$ penalty to AC, moves at half speed, and takes a $-4$ penalty on Search checks and most Strength and Dexterity-based skill checks.

Characters with low-light vision (elves, gnomes, and half-elves) can see objects twice as far away as the given radius. Double the effective radius of bright light and of shadowy illumination for such characters.

Characters with darkvision (dwarves and half-orcs) can see lit areas normally as well as dark areas within 60 feet. A creature can't hide within 60 feet of a character with darkvision unless it is invisible or has cover.