\documentclass{report}

\begin{document}
\chapter*{}
\section*{Credits}
\begin{tabular}{l l}
  Designers: & Brax, Bruno Fernandes, Chris Flipse, Jon // Oracle \\
  Development Team: & Nels Anderson, Bryan Bock, Daniel Bandera, Yanick Moreau, \\
    & Christopher Nahumck \\
  Editors: & Bruno Fernandes \\
  Rules Assistance and Review: & Brax, Gabriel Cormier, Paul Liss, Nathan Guest \\
  Layout: & Bruno Fernandes, Fabrício Lopes \\
  Background Graphic: & Dan Eveland \\
  Interior Artists: & Steven James \\
  Thanks to: & Robert Aldrich, Andrej Damjanovic, Alexis Gervais, Jan Groeneveld, \\
    & Mark Hope, Fabrício Lopes, Fabiano de Oliveira, Michael Ring, \\
    & David Schwarz, the hordes of the Dark Sun message boards, \\
    & and the athas.org playtester group \\
\end{tabular}

\section*{Legal Notice}
Dungeons and Dragons®, D\&D, and Dark Sun® are registered trademarks of Wizards of the Coast, Inc., a subsidiary of Hasbro, Inc. This Dark Sun on–line product has been recognized by Wizards of the Coast as an Official Dark Sun release on the Internet. The content here in is considered to be derivative work (as it is based on the intellectual property owned by Wizards of the Coast), and the articles within are jointly owned by both Wizards of the Coast and their authors. As such neither can do anything outside the official website without the permission of the other. This project may be reproduced for personal use, but may not be used to generate revenue. This product is a work of fiction. Any similarity to actual people, organizations, places, or events is purely coincidental.

\section*{Open Game Content and Dark Sun Copyrights}
This edition of Dark Sun Core Rules is produced under version 1.0, 1.0a, and/or draft versions of the Open Game License, the d20 System Trademark Logo Guide, and System Reference Document by permission of Wizards of the Coast. Subsequent versions of this product will incorporate final versions of the license, guide, and document.

\section*{Designation of Product Identity}
The following items are hereby designated as Product Identity in accordance with Section 1(e) of the Open Game License, version 1.0a: Any and all Wizards of the Coast logos and identifying marks and trade dress, including all Wizards of the Coast product and product line names including but not limited to Dark Sun, The City-state of Tyr, Dune Trader, Elves of Athas, Veiled Alliance, and any specific characters, monsters, creatures, and places; capitalized names and names of places, magical or psionic items, artifacts, characters, countries, creatures, geographic locations, gods, historic events, magic items, organizations, spells, and powers; and any and all stories, storylines, histories, plots, thematic elements, and dialogue; all spells monsters in the Monstrous Compendium Appendix: Terrors Beyond Tyr; and all artwork, symbols, designs, depictions, illustrations, maps, and cartography, likenesses, poses, logos, or graphic designs, except such elements that already appear in final or draft versions of the d20 System Reference Document and are already Open Game Content by virtue of appearing there. The above Product Identity is not Open Game Content.

\section*{Designation of Open Game Content}
Some portions of this book which are OGC originate from the System Reference Document and are ©1999, 2000, and 2001 Wizards of the Coast, Inc. \"Open Game Content\" is designated in this product by text appearing in this color (excluding headers). Any other portion of this product, unless already appearing in the System Reference Document or already Wizards' of the Coast intellectual property, is joint property of Wizards of the Coast and the author.
\end{document}
