\section{Character Progress}
As the characters overcome the numerous challenges in the course of the adventure, they should improve and gain new abilities to overcome greater challenges.

\subsection{Advancing in Level}
Instead of the standard of using Experience Points (XP) to attain new character levels as is described in the Player's Handbook and Dungeon Master's Guide, we recommend that players gain levels based on the number of sessions for your adventure. And it can also depend on the frequency of the sessions, e.g., if your group can only play once per month it may be better to speed up the progress of the characters.

\Table{Sessions Per Level}{X R}{
\tableheader Pace of Campaign & \tableheader Number of Sessions per Level\\
Rushed & 1\\
Fast & 2\\
Default & 3\\
Slow & 4\\
Dragged & 5+\\
}

Since the traditional leveling system via XP was tailored for 13.33 encounters per level, this would mean that the default pace is based on having between 4 and 5 encounters per session.

\subsubsection{Level-Dependent Benefits}
Besides the bonuses given by their character classes, all characters gain additional feats and increase their abilities from advancing in level as seen in \tabref{Level-Dependent Benefits}.

\textbf{Feat:} Every character gets their first feat at 1st level. At 3rd level and every other 3 levels, characters gain another feat. More information on feats on \chapref{Feats}.

\textbf{Ability Score Increase:} At 4th level and every 4 levels thereafter, the player chooses one of their character's ability scores to increase by 1 point. This improvement is permanent.

\Table{Level-Dependent Benefits}{X C C}{
\tableheader Character Level & \tableheader Feat & \tableheader Ability Score Increase\\
1 & 1st & \\
2 & & \\
3 & 2nd & \\
4 & & 1st \\
5 & & \\
6 & 3rd & \\
7 & & \\
8 & & 2nd \\
9 & 4th & \\
10 & & \\
11 & & \\
12 & 5th & 3rd \\
13 & & \\
14 & & \\
15 & 6th & \\
16 & & 4th \\
17 & & \\
18 & 7th & \\
19 & & \\
20 & & 5th \\
}

\subsection{Gaining Experience}
Award players for combat and role-playing. These are some guidelines to award experience points players for their roleplay. Awards are only for successful atempts of each action. The awards are cumulative, e.g., a gladiator that defeated a creature alone in an arena gains XP for defeating a creature and for defeating alone in an arena---a total of 15 XP $\times$ creature's CR.

If you are using experience points to advance levels, multiply these awards by the character's effective character level (ECL). Remember that this will quicken the rate of progress of the characters.

\subsubsection{Awards per Race}
\textbf{Aarakocra}:
\XPTable{Aarakocras}{

}

\textbf{Dwarf}:
\XPTable{Dwarves}{
Pursue present focus & 5 XP $\times$ days\\
Ignore present focus & -50 XP $\times$ days\\
Complete major focus & 500 XP
}

\textbf{Elf}:
\XPTable{Elves}{

}

\textbf{Half-Elf}:
\XPTable{Half-Elves}{

}

\textbf{Half-Giant}:
\XPTable{Half-Giants}{

}

\textbf{Halfling}:
\XPTable{Halflings}{

}

\textbf{Human}:
\XPTable{Humans}{

}

\textbf{Mul}:
\XPTable{Muls}{

}

\textbf{Pterran}:
\XPTable{Pterrans}{

}

\textbf{Thri-Kreen}:
\XPTable{Thri-Kreens}{

}

\subsubsection{Awards per Class}
Multiclass characters must choose which class to consider when receiving awards---you can only gain award for a single class.

\textbf{\class{Barbarian}}: Barbarians are survivalists, so beyond defeating living creatures, defeating traps and natural hazards on their might alone award them bonus experience points.

\XPTable{Barbarians}{
Use special attack & 5 XP\\
Use rage & 10 XP\\
Defeat a creature & 10 XP $\times$ creature's CR\\
Defeat trap or natural hazard & 10 XP $\times$ trap's CR\\
}

\textbf{\class{Bard}}: Bards gain bonus experience points for successful use of their bardic abilities. However they also gain XP for using poison against a creature---to weaken or kill the victim.

\XPTable{Bards}{
Use bardic music & 10 XP\\
Use bardic knowledge & 25 XP\\
Use poison effectively & 5 XP $\times$ creature's CR\\
Defeat a creature & 5 XP $\times$ creature's CR\\
Obtain treasure & 5 XP $\times$ value in cp\\
}

\textbf{\class{Cleric}}: Using elements with finesse and flair to overcome an obstacle should reaward clerics bonus experience points.

\XPTable{Clerics}{
Use domain power & 10 XP\\
Use element creatively & 50 XP\\
Cast spell & 5 XP $\times$ spell level\\
Cast Healing spell & 10 XP $\times$ spell level\\
Turn/rebuke undead & 25 XP $\times$ undead's CR\\
Destroy/command undead & 50 XP $\times$ undead's CR\\
Create magic item & 200 XP\\
}

\textbf{\class{Druid}}:

\XPTable{Druids}{
Cast spell & 5 XP $\times$ spell level\\
Case Healing spell & 10 XP $\times$ spell level\\
Use wild empathy & 25 XP\\
Use wild shape & 10 XP\\
Defeat defiler & 50 XP $\times$ defiler's CR\\
Create magic item & 200 XP\\
}

\textbf{\class{Fighter}}: The fighter's role in society is about mass warfare, so being a good soldier during these times will award her additional experience points. Fighters do not gain experience points for spending weeks in reserve, even if they're commanding followers.

\XPTable{Fighters}{
Use special attack & 5 XP\\
Defeat a creature alone & 5 XP $\times$ creature's CR\\
Defeat a creature with a group & 10 XP $\times$ creature's CR\\
Follow commands in battle & 25 XP\\
Command a battle & 50 XP\\
Build a war machine & 100 XP\\
}

\textbf{\class{Gladiator}}: Gladiators desire to be in the spotlight of an arena, to be the victor of a duel. Therefore, they receive additional experience points for defeating creatures in an arena without outside aid. The glory must be their alone.

\XPTable{Gladiators}{
Use special attack & 5 XP\\
Use gladiatorial perfomance & 10 XP\\
Defeat a creature & 5 XP $\times$ creature's CR\\
Defeat a creature alone in an arena & 10 XP $\times$ creature's CR\\
}

\textbf{\class{Psion}}:

\XPTable{Psions}{
Defeat a psionic creature & 5 XP $\times$ creature's CR\\
Research new psionic knowledge & 50 XP\\
Manifest a power & 5 XP $\times$ power level\\
Manifest a power to avoid combat & 10 XP $\times$ power level\\
Create psionic item & 200 XP\\
}

\textbf{\class{Psychic Warrior}}:

\XPTable{Psychic Warriors}{
Defeat a creature & 5 XP $\times$ creature's CR\\
Defeat a psionic creature & 5 XP $\times$ creature's CR\\
Manifest a power & 5 XP $\times$ power level\\
}

\textbf{\class{Ranger}}: Rangers track their foes and hunt favored enemies. Accomplishing these taks award them additional experience points.

\XPTable{Ranger}{
Cast spell & 5 XP $\times$ spell level\\
Defeat a creature & 5 XP $\times$ creature's CR\\
Defeat a creature in a favorite territory & 5 XP $\times$ creature's CR\\
Defeat a favorite enemy & 10 XP $\times$ enemy's CR\\
Track a creature & 10 XP\\
Track a creature in a favorite territory & 10 XP\\
Track a favorite enemy & 10 XP\\
Use wild empathy & 25 XP\\
}

\textbf{\class{Rogue}}:

\XPTable{Rogue}{
Defeat a creature & 5 XP $\times$ creature's CR\\
Disable trap & 25 XP $\times$ trap's CR\\
Obtain treasure & 5 XP $\times$ value in cp\\
Obtain treasure for patron & 5 XP $\times$ value in cp\\
Use sneak attack & 5 XP\\
}

\textbf{\class{Templar}}:

\XPTable{Templar}{
Cast spell & 5 XP $\times$ spell level\\
Use secular authority on slave & 5 XP\\
Use secular authority on freeman & 10 XP\\
Use secular authority on noble & 25 XP\\
Use secular authority on templar & 50 XP\\
Fulfill sorcerer-king's mission & 100 XP\\
}

\textbf{\class{Wilder}}:

\XPTable{Wilders}{
Defeat a psionic creature & 5 XP $\times$ creature's CR\\
Create psionic item & 200 XP\\
Surge without enervation & 10 XP $\times$ bonus level\\
Manifest a power & 5 XP $\times$ power level\\
Manifest a power to avoid combat & 10 XP $\times$ power level\\
}

\textbf{\class{Wizard}}: Preservers and defilers serve different roles in the athasian society. Preservers want to remain hidden from the eyes of the templars, so they gain additional experience points for keeping spellcasting secret. Defilers on the other hand are aligned with the \emph{status quo} and are awarded additional experience points for carrying out the business of their sorcerer-monarchs.

\XPTable{Wizards}{
Cast spell & 5 XP $\times$ spell level\\
Cast spell for sorcerer-king (defiler) & 5 XP $\times$ spell level\\
Find new spell to spellbook & 50 XP $\times$ spell level\\
Maintain spellcasting secret (preserver) & 25 XP\\
Create magic item & 200 XP\\
}


\subsubsection{Awards per Skill Check}