\subsectionA{Aarakocra}
Aarakocra are the most commonly encountered bird-people of the Tablelands. Some are from Winter Nest in the White Mountains near Kurn, while others are from smaller tribes scattered in the Ringing Mountains and elsewhere. These freedom-loving creatures rarely leave their homes high in the mountains, but sometimes, either as young wanderers or cautious adventurers, they venture into the inhabited regions of the Tablelands.

\subsubsection{Aarakocra Society}
The aarakocra have a tribal society. The civilized tribes of Winter Nest form the largest known community of aarakocra in the Tyr region. Though their communities are lead by a chieftain, the aarakocra have a great love of personal freedom. So while the chieftain makes all major decisions for the community, unless she consults with the tribal elders and builds a strong consensus within the tribe first, her decisions may be ignored.

Air and sun shamans play an important role in aarakocra societies. Aarakocra worship the sun because it provides them with the thermals they need to soar. The air shamans of Winter Nest lead their community in daily worship of the air spirits.

Aarakocra of Winter Nest have a deep and abiding respect for the gifts of nature and little patience for those who abuse those gifts. They look after the natural resources of the White Mountains and have been known to punish those who despoil or abuse them.

In more primitive societies, female aarakocra rarely travel far from the safety of the nest, and focus solely on raising the young. In Winter Nest, both sexes participate in all aspects of society, with females more often elected by the elders to be chieftains.

Aarakocra believe that their ability to fly makes them superior to all other races and thus they have great confidence and pride in themselves. Though they often express sympathy for people unable to fly, this more often comes across as condescending.

Aarakocra are carnivores, but do not eat intelligent prey.

\subsubsection{Aarakocra Racial Traits}
\begin{itemize*}
    \item $-2$ Strength, +4 Dexterity, $-2$ Constitution: Aarakocra have keen reflexes, but their lightweight bones are fragile.
    \item Humanoid (aarakocra): Aarakocra are humanoid creatures with the aarakocra subtype.
    \item Medium: As Medium creatures, aarakocra have no special bonuses or penalties due to size.
    \item Low-Light Vision: Aarakocra can see twice as far as a human in moonlight and similar conditions of poor illumination, retaining the ability to distinguish color and detail.
    \item Aarakocra base land speed is 6 meters. They also have a fly speed of 27 meters (average).
    \item +6 racial bonus to \skill{Spot} checks in daylight. Aarakocra have excellent vision.
    \item +1 natural armor bonus.
    \item Natural Weaponry: An aarakocra can rake with its claws for 1d3 points of damage, and use its secondary bite attack for 1d2 points of damage.
    \item Claustrophobic: Aarakocra receive a $-2$ morale penalty on all rolls when in an enclosed space. Being underground or in enclosed buildings is extremely distressing for them.
    \item Aerial Dive: Aarakocra can make dive attacks. A dive attack works just like a charge, but the diving creature must move a minimum of 9 meters. If attacking with a lance, the aarakocra deals double damage on a successful attack. Optionally, the aarakocra can make a full attack with its natural weapons (two claws and one bite) at the end of the charge, dealing normal damage.
    \item Automatic Languages: Auran and Common. Bonus Languages: Elven, Gith, and Saurian.
    \item Favored Class: Cleric.
    \item Level Adjustment: +1.
\end{itemize*}