\subsectionA{Dray}
The dray are mutated humanoids created by the sorcerer-monarch of New Giustenal, Dregoth. He believed that humans had to ``evolve'' as he was evolving, if they were to be fit servants in the new age to come. Two different types of dray were created, since Dregoth saw the first successful transformations as failures.

Dray are tall, lean draconic beings with scaly skin. They have clawed limbs, tails, but no wings. The first generation has a more mutated look to them, each person with a different mutation: jagged claws, uneven mottled scales, no tail, or bodies slightly bent. The second generation has a long neck with a proud draconic head atop, colorful scales, and whiplike tails. First generation dray live as long as a half-elf, while second-generation dray live as long as a half-giant.

Both generations speak the ancient tongue of Giustenal, as it was spoken thousands of years ago, though the first generation speaks a rougher dialect. Neither dray speaks any language from the surface.

\subsubsection{Dray Society}
The first generation dray, full of mutations, were banished from his underground city. They live in the ruins of the halfling city of Kragmorta, below Giustenal. First generation dray distrust surface dwellers, but they do not hate them. They are ruled by the Clan Father Mosak. These dray still worship Dregoth as their god, but they also hate him for the rejection. Even in exile, they receive occasional visits from New Giustenal's High Templar to teach and preach. Some day they hope to be taken back into the fold.

The second generation dray live in New Giustenal, under the eyes of the undead dragon. They are free to work and raise families, while protected by the templars. Although they have this peaceful life now, all second generation dray are expected to fight for Dregoth on the Day of Light, when the undead dragon will rise to surface and continue the Cleansing Wars. As chosen of Dregoth, the second generation looks down up the first, seen as mutated failures. They were brainwashed into believing that all non-humans are to be scorned and killed, while humans should are to be pitied until they can be transformed into dray themselves.

\subsubsection{Dray Racial Traits}
All dray share these traits.
\begin{itemize*}
    \item +2 Strength, +2 Constitution, $-2$ Wisdom, $-6$ Charisma: Dray were transformed to be an army, but they have trouble interacting with other people.
    \item Humanoid (fire, reptilian): Dray are humanoid creatures with the fire and reptilian subtypes.
    \item Medium: As Medium creatures, dray have no special bonuses or penalties due to size.
    \item Dray base land speed is 9 meters.

    \item Natural Armor: +3 natural armor bonus to AC.
    \item Natural Weapons: 2 claws (1d6), and bite (1d4).

    \item Water Efficient: Dray need half the amount of water per day that a human would need.

    \item Immunity to Fire: Dray never takes fire damage.
    \item Light Sensitivity: Dray are dazzled in bright sunlight or within the radius of a \spell{daylight} spell.
    \item Vulnerability to Cold: Dray take half again as much (+50\%) damage as normal from cold, regardless of whether a saving throw is allowed, or if the save is a success or failure.

    \item Automatic Languages: Giustenalese. Bonus Languages: Common.
\end{itemize*}

\subsubsection{First-Generation Dray Traits}
These traits are in \textbf{addition} to the dray traits, except where noted.
\begin{itemize*}
    \item +2 Strength, +2 Constitution, $-4$ Intelligence.
    \item Darkvision: First-generation dray can see in the dark up to 18 meters.
    \item +2 racial bonus on \skill{Hide} and \skill{Move Silently} checks.
    \item +1 racial bonus on attack and damage rolls made with natural weapons.
    \item Favored Class: Gladiator.
    \item Level Adjustment: +2.
\end{itemize*}

\subsubsection{Second-Generation Dray Traits}
These traits are in \textbf{addition} to the dray traits, except where noted.
\begin{itemize*}
    \item +2 Intelligence.
    \item Darkvision: Second-generation dray can see in the dark up to 9 meters.
    \item Favored Class: Psion or Wizard.
    \item Level Adjustment: +1.
\end{itemize*}
