\subsectionA{Ettin}
Ettins, or two-headed giants, are vicious and unpredictable hunters that stalk the night.

An ettin never bathes if it can help it, which usually leaves it so grimy and dirty its skin resembles thick, gray hide. Adult ettins are about 4 meters tall and weigh 2,600 kilograms. They live about 75 years.

Ettins have no language of their own but speak a pidgin of Belgoi, Giant, and Gith. Creatures that can speak any of these languages must succeed on a DC 15 Intelligence check to communicate with an ettin. Check once for each bit of information: If the other creature speaks two of these languages, the DC is 10, and for someone who speaks all three, the DC is 5.

\subsubsection{Ettin Society}
Ettins like to establish their lairs in remote, rocky areas. They dwell in dark, underground caves that stink of decaying food and offal. Ettins are generally solitary, and mated pairs only stay together for a few months after a young ettin is born to them. Young ettins mature very quickly, and within eight to ten months after they are born, they are self-sufficient enough to go off on their own.

On rare occasions, however, a particularly strong ettin may gather a small group of up to four ettins together. This small band of ettins stays together only as long as the leader remains alive and undefeated in battle. Any major defeat shatters the leader's hold over the band, and they each go their separate ways.

Ettins collect treasure only because it can buy them the services of other creatures. These creatures sometimes serve ettins by building traps around their lairs, or helping to fight off a powerful opponent. Ettins have also been known to occasionally keep large animals in the area of their lairs.

The sloppy caves of ettins are a haven for parasites and vermin, and it isn't unusual for the ettins themselves to be infected with various parasitic diseases. Adventurers rummaging through ettin lairs for valuables will find the task disgusting, if not dangerous.

\subsubsection{Ettin Racial Traits}
\begin{itemize*}
    \item +12 Strength, $-2$ Dexterity, +4 Constitution, $-4$ Intelligence: Ettin are strong and sturdy, but clumsy and dull.
    \item Giant: Ettin are creatures with the giant type.
    \item Large: As a Large creature, an ettin takes a $-1$ penalty to Armor Class, a $-1$ penalty on attack rolls, and a $-4$ penalty on \skill{Hide} checks. He gains a +4 size bonus on grapple checks, and his lifting and carrying limits are double those of Medium characters, but he uses bigger weapons than humans use.
    \item Ettin occupy a space of 3 meters and have a reach of 3 meters.
    \item Ettin base land speed is 12 meters.

    \item Low-Light Vision: Ettins can see twice as far as a human in moonlight and similar conditions of poor illumination, retaining the ability to distinguish color and detail.

    \item Racial Hit Dice: An ettin begins with ten levels of giant, which provide 10d8 Hit Dice, a base attack bonus of +7, and base saving throw bonuses of Fort +7, Ref +3, and Will +3.
    \item Racial Skills: An ettin's giant levels give it skill points equal to 13 $\times$ (2 + Int modifier). Its class skills are \skill{Climb}, \skill{Intimidate}, \skill{Listen}, \skill{Search}, \skill{Spot}, and \skill{Survival}.
    \item Racial Feats: An ettin's giant levels give it 4 feats.
    \item Weapon Proficiency: An ettin is proficient with simple and martial weapons as well as its natural weaponry.

    \item Natural Armor: +7 natural armor bonus to AC.

    \item Superior Two-Weapon Fighting (Ex): An ettin fights with a weapon in each hand. Because each of its two heads controls an arm, the ettin does not take a penalty on attack or damage rolls for attacking with two weapons.
    \item The ettin's two heads give it a +2 racial bonus on Listen, Spot, and Search checks.

    \item Automatic Languages: None. Bonus Languages: Belgoi, Giant, and Gith.
    \item Favored Class: Scout.
    \item Level Adjustment: +1.
\end{itemize*}
