\subsection{Using the Environment}
Athasian wizards drain energy from the surrounding soil. The method used labels wizards as defilers or preservers. Preservers have the self-control to gather energy without destroying plants. Those who do not, or who feel no remorse about the damage caused, become defilers. Defilers leave behind sterile soil and infertile ash when they cast spells. Due to this fact, most wastelanders blame wizards for the desert landscape that dominates the Tablelands today, and their hatred extends to defilers and preservers alike.

\subsubsection{Terrain Modifiers}
Terrain types affect arcane magic depending on the amount of plant life available. Barren and desolate terrains weaken spells, while fertile and abundant terrains boost spells. Spell save DCs and caster level checks are affected by the modifiers indicated in \tabref{Terrain Modifiers}.

The Obsidian Plains are completely devoid of plant life. If arcane spellcasters have no alternative energy sources, or magical items such as wands, they are unable to cast spells in this terrain.

\Table{Terrain Modifiers}{lXc}{
\tableheader Terrain Type & \tableheader Examples & \tableheader Modifier\\
Desolate & Salt flats, sea of Silt & $-2$\\
Barren & Boulder fields, scrublands, stony barrens & $-1$\\
Infertile & Cities, rocky badlands & $+0$\\
Fertile & Mud flats, savannahs, swamps, verdant plains & $+1$\\
Abundant & Forests, gardens, Last Ocean & $+2$\\
}

\subsubsection{Defiling}
Defilers leave behind an ashen circle when casting spells. The radius is 1.5 m x spell slot level expended (a 0-level spell defiles a single 1.5 m square occupied by the caster). Creatures except the defiler caught within the defiling radius at casting time experience pain and suffer a $-1$ penalty to all attack rolls, weapon damage rolls, saving throws, skill checks, and ability checks for 1 round. Plant creatures also suffer 2 damage $\times$ spell slot level expended (a 0-level spell inflicts 1 damage).

Defiler's ash is black and totally devoid of life-giving properties. It is the telltale sign of wizardry. Nothing grows in a defiled area for years. Even if the defiler's ash moves with the wind, the ground remains a lifeless scar. A defiler cannot preserve, but a preserver can defile if desperate.

When defiling, a wizard can extend the casting time of her spells to 1 round and gain a +1 bonus to caster level. Her defiling radius increases by 1.5 m. Spells with a normal casting time of 1 round or longer require an extra round to be cast in this manner. Experienced defilers often increase their spellcasting power further through Raze feats (see \chapref{Feats}).