\PrestigeClass[\subsectionA][\subsubsection]{Spirit Initiate}
{
Hezzerat became a legend long ago. Now, as the ancient druid began to look deeper into the nature of his lands, he felt a compelling urge to become one with them. He spoke with the spirit that dwelled in the canyon he guarded, and learned that it was composed of a great many of his own, powerful predecessors.
}{Hezzerat's transformation}
{
Some of the most devoted druids in Athas' choose to take a path of self-sacrifice and abandonment, greatly increasing their bond with their spirit of the land, together with the help of psionics, and meld themselves into the land they protect.

As spirit initiates, they can combine their mastery of the Way and divine power into psionic enchantments that greatly enhance their abilities, and can counter defiling effects. Spirit initiates are often called to help other elemental beings in order to fight in the Unseen War.
}
{d6}
{an}
{
Spirit initiates are epic progressions of the druidic divine minds.
}
{
\textbf{Skills:} \skill{Concentration} 23 ranks, \skill{Knowledge} (psionic) 20 ranks, \skill{Knowledge} (nature) 20 ranks, \skill{Psicraft} 20 ranks, \skill{Spellcraft} 20 ranks.

\textbf{Feats:} \feat{Psionic Meditation}, \feat{Mind Over Body}, any two metamagic feats, and any two psionic feats.

\textbf{Spells:} Able to cast 9th-level divine spells.

\textbf{Psionics:} Able to manifest powers from all disciplines.

\textbf{Special:} Trackless step class feature.
}
{
\skill{Concentration} (Con),
\skill{Craft} (Int),
\skill{Diplomacy} (Cha),
\skill{Hide} (Dex),
\skill{Knowledge} (geography) (Int),
\skill{Knowledge} (nature) (Int),
\skill{Knowledge} (psionic) (Int),
\skill{Listen} (Wis),
\skill{Psicraft} (Int),
\skill{Search} (Int),
\skill{Sense Motive} (Wis),
\skill{Spellcraft} (Int),
\skill{Spot} (Wis),
and \skill{Survival} (Wis).
}
{6}
{\EpicTable}
{
 1 & +0 & +2 & +2 & +2 & Continued advancement, fast healing                    & 1 \\
 2 & +1 & +3 & +3 & +3 & Deflection, spell resistance                           & 1 \\
 3 & +2 & +3 & +3 & +3 & Blindsense, telepathy                                  & 2 \\
 4 & +3 & +4 & +4 & +4 & Increased size                                         & 2 \\
 5 & +3 & +4 & +4 & +4 & DR 10/cold metal and magic                             & 2 \\
 6 & +4 & +5 & +5 & +5 &                                                        & 3 \\
 7 & +5 & +5 & +5 & +5 & Increased size                                         & 3 \\
 8 & +6 & +6 & +6 & +6 & DR 15/cold metal and epic                              & 3 \\
 9 & +6 & +6 & +6 & +6 & Blindsight                                             & 4 \\
10 & +7 & +7 & +7 & +7 & Complete melding, divine rank, elemental manifestation & 4 \\
}
{
\textbf{Continued Advancement:} When a new spirit initiate level is attained, the character gains new spells per day as if she had also attained a level in any one divine spellcasting class she belonged to before she added the prestige class. She gains additional power points per day and access to new powers as if she had also gained a level in any one manifesting class she belonged to previously. She does not, however, gain any other benefit a character of either class would have gained (bonus metamagic, metapsionic, or item creation feats, psicrystal special abilities, and so on). This essentially means that she adds the level of spirit initiate to the level of whatever other divine spellcasting class and manifesting class the character has, then determines spells per day, caster level, power points per day, powers known, and manifester level accordingly.

If a character had more than one divine spellcasting class or more than one manifesting class before she became a spirit initiate, she must decide to which class she adds each level of spirit initiate for purpose of determining spells per day, caster level, power points per day, powers known, and manifester level.

\textbf{Psionic Enchantments:} A spirit initiate can cast psionic enchantments, epic magic that act as 10th-level spells and expends her psionic focus. She must choose and prepare her spells ahead of time. Each psionic enchantment requires a different preparation time.

To learn, prepare, or cast a psionic enchantment, the spirit initiate must have an Wisdom score equal to at least 20. The Difficulty Class for a saving throw against a spirit initiate's psionic enchantment is 20 + the spirit initiate's Wisdom modifier.

A spirit initiate can cast only a certain number of psionic enchantments per day. Her daily psionic enchantment allotment is given on \tabref{The Spirit Initiate}. Unlike spells, she does not receive bonus psionic enchantments per day.

\textbf{Fast Healing (Ex):} A spirit initiate gains fast healing. She heals a number of points of damage each round equal to her spirit initiate level.

\textbf{Deflection (Su):} At 2nd level, a spirit initiate gains a deflection bonus to AC equal to her class level + her Wisdom modifier.

\textbf{Spell Resistance (Su):} At 2nd level, a spirit initiate gains spell resistance equal to 12 + spirit initiate's HD.

\textbf{Blindsense (Ex):} At 3rd level, a spirit initiate gains the blindsense ability out to 9 meters. She does not need to make \skill{Spot} or \skill{Listen} checks to notice and locate creatures within range of her blindsense ability, provided that she has line of effect to that creature. Any opponent the spirit initiate cannot see has total concealment (50\% miss chance) against her, and the spirit initiate still has the normal miss chance when attacking foes that have concealment. Visibility still affects the spirit initiate's movement. A spirit initiate is still denied its Dexterity bonus to Armor Class against attacks from creatures she cannot see.

When she is in her guarded lands, the range of the blindsense extends over the entire guarded land area.

\textbf{Telepathy (Su):} At 3rd level, a spirit initiate gains the ability to communicate telepathically with any creature within 30 meters that has a language. When she is in her guarded lands, the range of this telepathy extends over the entire guarded land area and she can communicate with any intelligent creature within its borders, regardless of language.

\textbf{Increased Size:} At 4th level and 7th level, a spirit initiate increases in size by one category. At each size increase, the spirit initiate improves her Strength score by 8, and her Constitution score by 4. Small and Large spirit initiates increase the size by one category normally. Small spirit initiates that become Medium improve Strength as indicated, as this is not a normal monster progression. Colossal spirit initiates cannot increase further in size.

\textbf{Damage Reduction:} At 5th level, a spirit initiate gains damage reduction 10/cold metal and magic. So attacks from weapons that are not made of cold metal have their damage reduced, even if the weapon has an enhancement bonus or if it is made of common metal. Only cold metal weapons with an enhancement bonus can ignore this damage reduction. Damage reduction can reduce damage to 0 but not below 0. % Only attacks with cold metal weapons with an enhancement bonus of +1 or better can ignore this damage reduction.

At 8th level, this damage reduction improves to 15/cold metal and epic. Only attacks with cold metal weapons with an enhancement bonus of +6 or better can ignore this damage reduction.

\textbf{Blindsight (Ex):} At 9th level, a spirit initiate gains the blindsight ability out to 27 meters. Her senses become so acute that she can maneuver and fight flawlessly even in total darkness. Invisibility, darkness, and most kinds of concealment are irrelevant, though the spirit initiate must have line of effect to a creature or object to discern it.

When she is in her guarded lands, the range of the blindsight extends over the entire guarded land area.

\textbf{Complete Melding:} By obtaining the 10th level, the spirit initiate finishes melding into a spirit of the land, embodying all aspects of her guarded lands. A spirit initiate is now directly linked to her guarded lands. If her guarded lands are destroyed, so is she. All of her hit dice become d6. She gains flight speed of 21 meters, with perfect maneuverability. Her type changes to fey, and she gains the incorporeal subtype, which brings about the following alterations to her basic nature:
\begin{itemize*}
\item She loses her Strength score. She automatically fails Strength checks. If she can attack, she applies her Dexterity modifier to her base attack bonus instead of a Strength modifier.
\item She loses her weight and do not set off traps that are triggered by weight.
\item She gains immunity to all nonmagical attack forms.
\item She gains 50\% chance to ignore any damage from a corporeal source (except for positive energy, negative energy, force effects, or attacks made with \emph{ghost touch} weapons).
\item Her attacks ignore natural armor, armor, and shields, although deflection bonuses and force effects (such as \spell{mage armor}) work normally against it.
\item She cannot take any physical action that would move or manipulate an opponent or their equipment, nor is she subject to such actions.
\item She moves silently and cannot be heard with \skill{Listen} checks if she doesn't wish to be.
\item She cannot pass through a force effect.
\end{itemize*}

\textbf{Divine Rank:} At 10th level, a spirit initiate is considered a demigod. She can grant druid spells and perform a few deeds that are beyond mortal limits. She is immune to the effects of aging and never dies of ``natural causes.'' For more information, see \hyperref[Divine Rank]{Divine Rank}.
}

\textbf{Elemental Manifestation (Su):} At 10th level, when a spirit initiate is in her guarded lands, she gains the ability to manifest a material body as a standard action. While manifested, she loses the incorporeal subtype and her flight speed. She gains a Strength score depending on her size: Large spirits have a Strength score of 27, Huge spirits have Strength score of 35. She also gains two slam attacks that deal 2d8 points of bludgeoning damage, regardless of size, plus her Strength modifier.


\textit{Air Manifestation:} To manifest as air, a spirit initiate must have a windy valley, breezy seashore, or the like in her guarded lands. In this form, she gains flight speed of 42 meters with perfect maneuverability, the air subtype, and the following abilities.

\emph{Air Mastery (Ex):} Airborne creatures take a $-1$ penalty on attack and damage rolls against a spirit initiate.

\emph{Whirlwind (Su):} As an elder air elemental (DC 25 + her Strength modifier).


\textit{Earth Manifestation:} An earth manifestation simply requires any type of land. In this form, she gains land speed of 9 meters, the earth subtype, and the following abilities.

\emph{Earth Mastery (Ex):} A spirit initiate manifested as earth gains a +1 bonus on attack and damage rolls if both she and her foe are touching the ground. If an opponent is airborne or waterborne, she takes a $-4$ penalty on attack and damage rolls.

\emph{Push (Ex):} A spirit initiate manifested as earth can start a bull rush maneuver without provoking an attack of opportunity. The combat modifiers given in Earth Mastery, above, also apply to her opposed Strength checks.


\textit{Fire Manifestation:} A fire manifestation requires a volcanic region, hot spring, or the like on the spirit initiate's guarded lands. In this form, she gains land speed of 18 meters, the fire subtype, and the following abilities.

\emph{Fire Damage (Ex):} Each slam attack deals additional 4d8 points of fire damage.

\emph{Burn (Ex):} As an elder fire elemental (DC 25 + her Constitution modifier).


\textit{Water Manifestation:} To manifest as water, a spirit initiate must have a river, lake, pond, or other waterway in her guarded lands. In this form, she gains land speed of 6 meters, swim speed of 42 meters, the water subtype, and the following abilities.

\emph{Water Mastery (Ex):} A spirit initiate manifested as water gains a +1 bonus on attack and damage rolls if both she and her opponent are touching water. If the opponent or the spirit initiate is touching the ground, the spirit initiate takes a $-4$ penalty on attack and damage rolls.

\emph{Vortex (Su):} As an elder water elemental (DC 25 + her Strength modifier).
