\subsection{The Astral Plane}
The Astral Plane is the medium through which creatures move between planes, the void between the Outer Planes and the Gray, where they were build upon. The plane is a huge argent emptiness occasionally punctuated by large stars, which is why it is also called the Silvery Void. The Astral Plane is almost always deafening quiet and disturbingly still. The only changes one might find in their stay in the plane are tiny color pools and floating islands---chunks of rock and earth pulled from another plane.

The plane is home to creatures like the astral stalker^{MM3} and the astral kraken^{PH}, and it also harbors the githyanki, a race of reavers who travel through the plane in astral ships. They are the ancestors of the Athasian gith, and far more cunning and dangerous.

The Astral Plane is devoid of concepts of space or time. It is fueled by thoughts, emotions, perceptions, and dreams---a more esoteric plane, where the sensations and memories are carried by the wind. Entering the plane means that the Astral Plane translates the character and their equipment into an astral projection, because nothing physical actually enters the plane.

\textbf{Color Pools:} 

\Table{Color Pools}{Xl}{
  \tableheader Plane
& \tableheader Color \\

Ysgard & Indigo \\
Limbo & Jet \\
Pandemonium & Magenta \\
Abyss & Amethyst \\
Carceri & Olive \\
Hades & Rust \\
Gehenna & Russet \\
Baator & Ruby \\
Acheron & Flame \\
Mechanus & Diamond \\
Arcadia & Saffron \\
Celestia & Gold \\
Bytopia & Amber \\
Elysium & Opal \\
Beastlands & Emerald \\
Arborea & Sapphire \\
Outlands & Leather brown \\
}

It has the following traits.
\begin{itemize*}
\item \textbf{Subjective directional gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Timeless:} Age, hunger, thirst, poison, and natural healing don't function in the Astral Plane, though they resume functioning when the traveler leaves the Astral Plane.
\item \textbf{Mildly neutral-aligned.}
\item \textbf{Enhanced magic:} All spells and spell-like abilities used within the Astral Plane may be employed as if they were improved by the \feat{Quicken Spell} feat. Already quickened spells and spell-like abilities are unaffected, as are spells from magic items. Spells so quickened are still prepared and cast at their unmodified level. As with the \feat{Quicken Spell} feat, only one quickened spell can be cast per round.
\end{itemize*}
