\subsection{The Black}
The Black is a coterminous and coexistent plane that resides next to Athas. It is a reflection of the Prime Material Plane and shows what exists by way of negative space. For as long as Athasians have realized the power of the shadows the Black has been used, whether magically, psionically, or mundanely. The landscape of the Black is in constant flux, spells and psionic powers draw power from the planes, and due to the reflexive nature of the plane, changes on Athas cause changes in the Black.

The power and energy from the Black comes from its connection to the Material Plane of Athas. Shadows show what exist by absence. Shadows are negative space that shows existence through a negative. The Black exists where shadows are, and as its own plane. The Black contains not only the negative space from the reflections of existing objects, but also the potential of what all those things could be. Within the Black, all the things that could be are, but they are reflections, and have no substance, not existence, no life. When creatures used the Black to fuel their abilities, they are drawing on this potential and giving it a reality. The Black is not only the reflection of what is on Athas, but also the reflection of what could be. Powerful spellcasters have investigated the power of exploiting this potentiality to great effect. Rumors of a place beyond the Black, where not even reflections of reality exist are true. The Hollow is a plane outside of space and time. It is non-existence, and it is here that the Champions trapped Rajaat during the Rebellion.

Because of this, the landscape of the Black is constantly in motion, and never settled. It is at once a reflection of what is, and all the things that could be. The landscape resembles Athas, and there is a definite up and down, ground and sky, buildings, trees, rivers, and seas. However, all these things change and warp constantly. Gravity here exists, but only if one wishes it to.

Within the Black there are creatures that once lived on Athas. The halfling servants of the Warbringer were thrown into the Black during the Rebellion. To this day, they remain bodily within the Black, and are only able to interact with Athas through manipulating shadows. Also within the Black is the body of King Tithian of Tyr, his spirit trapped within the Cerulean Storm. When Rajaat was freed from the Hollow, he imprisoned Andropinis within the Black where he remains unable to escape from. Creatures native to the Black are few, but rumor has it that deep within the depths are possibilities of what could be, for both good and ill, and that these things sleep, unless someone awakens them. Terror could be unleashed on Athas if these things were given form outside the depths of the Black.

It has the following traits.
\begin{itemize*}
\item \textbf{Subjective directional gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Magically morphic.} Certain spells (those with the shadow descriptor, those that draw on the Black) modify the base material of the Black. The utility and power of these spells within the Black make them particularly useful for explorers and natives alike.
\item \textbf{Minor negative-dominant}: The dark nature of the Black brings numbing cold to all who visit. Living creatures take 1d6 points of damage per round. At 0 hit points or lower, they crumble into ash.
\item \textbf{Mildly neutral-aligned.}
\item \textbf{Enhanced magic:} Spells with the shadow descriptor are enhanced when within the Black. Such spells are cast as though they were prepared with the \feat{Maximize Spell} feat, though they don't require the higher spell slots.\\

Furthermore, specific spells become more powerful on the Black. The spells \spell{shadow conjuration} and \spell{shadow evocation} are 30\% as powerful as the conjurations and evocations they mimic (as opposed to 20\%). \spell{Greater shadow conjuration} and \spell{greater shadow evocation} are 70\% as powerful (not 60\%), and a \spell{shades} spell conjures at 90\% of the power of the original (not 80\%).

\item \textbf{Impeded magic:} Spells that use or generate light or fire may fizzle when cast within the Black. A spellcaster attempting a spell with the light or fire descriptor must succeed on a \skill{Spellcraft} check (DC 20 + the level of the spell). Spells that produce light are less effective in general, because all light sources have their ranges halved within the Black.
\end{itemize*}
