\section{Epic Feats}
\textbf{Acquiring Epic Feats:} Characters gain epic feats in the following ways:
\begin{itemize*}
\item At 21st level, and every three levels thereafter, the character may select an epic feat in place of a non-epic feat.
\item Character class that gains bonus epic feats according to the class description.
\end{itemize*}


\input{subsections/epic-levels/epic-feats/general-feats.tex}
\input{subsections/epic-levels/epic-feats/fighter-feats.tex}
\input{subsections/epic-levels/epic-feats/table-spell-feats.tex}
\input{subsections/epic-levels/epic-feats/psionic-feats.tex}
\input{subsections/epic-levels/epic-feats/divine-feats.tex}


\subsection{Metamagic Feats}
\GFeat[Epic, Metamagic]{Intensify Spell}
{\feat{Empower Spell}, \feat{Maximize Spell}, \skill{Spellcraft} 30 ranks, ability to cast 9th-level arcane or divine spells.}
{All variable, numeric effects of an intensified spell are maximized, then doubled. An intensified spell deals twice maximum damage, cures twice the maximum number of hit points, affects twice the maximum number of targets, and so forth, as appropriate. Saving throws and opposed rolls are not affected. An intensified spell uses up a spell slot seven levels higher than the spell's actual level. You can't combine the effects of this feat with any other feat that affects the variable, numeric effects of a spell.}


\subsection{Metapsionic Feats}
\GFeat[Epic, Metapsionic]{Intensify Power}
{\feat{Empower Power}, \feat{Maximize Power}, \skill{Psicraft} 30 ranks, access to six disciplines.}
{To use this feat, you must expend your psionic focus.

All variable, numeric effects of an intensified spell are maximized, then doubled. An intensified spell deals twice maximum damage, cures twice the maximum number of hit points, affects twice the maximum number of targets, and so forth, as appropriate. Saving throws and opposed rolls are not affected. You can't combine the effects of this feat with any other feat that affects the variable, numeric effects of a spell.

Using this feat increases the power point cost of the power by 35.}