\section{Psionic Enchantments}



\subsection{Cleric Psionic Enchantments}

\spellList{Air of Permanence}\textsuperscript{1}: Make an item immune to aging.

\spellList{Conversion}: Change target's alignment.

\spellList{Disruption}: Create interference between templars and target sorcerer-monarch.

\spellList{Hasten Crops}: Increase growth by a factor of 10.

\spellList{Insect Host}: Create a plague of insects.

\spellList{Miracle, Greater}: Request a deity's intercession.

\spellList{Rift}: Negative energy sphere boosts nearby undead.

\spellList{Silt Bridge}\textsuperscript{2}: Solidify huge portions of silt.

\spellList{Wall of Mountains}\textsuperscript{3}: Create a mountain range.

\noindent 1 Only air clerics.

\noindent 2 Only silt clerics.

\noindent 3 Only earth clerics.



\subsection{Druid Psionic Enchantments}

\spellList{Air of Permanence}: Make an item immune to aging.

\spellList{Hasten Crops}: Increase growth by a factor of 10.

\spellList{Insect Host}: Create a plague of insects.

\spellList{Prolific Forestation}: Create a grove of trees.

\spellList{Prolific Vegetation}: Create a shrubs and grass.

\spellList{Silt Bridge}: Solidify huge portions of silt.

\spellList{Wall of Mountains}: Create a mountain range.



\subsection{Wizard Psionic Enchantments}
\subsubsection{Abjuration}
\spellList{Dome of Invulnerability}: As \spell{globe of invulnerability}, but affects a larger area.

\spellList{Dimensional Lock, Greater}: As \spell{dimensional lock}, but affects a settlement.


\subsubsection{Conjuration}
\spellList{Mountain Fortress}: creates a mountain with a fortress on its top

\spellList{Prolific Forestation}: create a grove of trees

\spellList{Prolific Vegetation}: create shrubs and grass


\subsubsection{Divination}
\spellList{Foretell}: As \spell{scrying}, but over time.

\spellList{Lineage}: Know all personal history of the touched creature.


\subsubsection{Illusion}
\spellList{Umbra}: As \spell{shadow evocation}, but up to 9th level and 80\% real.


\subsubsection{Necromancy}
\spellList{Defiling Regeneration}: Creatures regenerate at the cost of nearby vegetation.

\spellList{Raise City}: raise all dead people from the ruins of a city

\spellList{Wizard Plague}: create a magical plague that forbids wizards from casting spells from the chosen school


\subsubsection{Enchantment}
\spellList{Cowardice}: Weaken the morale of a whole group.

\spellList{Dominate Monster, Greater}: As \spell{dominate monster}, but no save allowed.

\spellList{Dominate Monster, Mass}: As \spell{dominate monster}, but all within 9 m.

\spellList{Fanaticism}: As \spell{greater heroism}, but a whole group.

\spellList{Recruitment}: all living creatures within range become an army at your command


Evocation
Abrasion: Creatures in area take up to 1d3 damage per HD, may be unable to move.
Wall of Ash: Deals .

Conjuration ()
Rift: bring the Plane of Negative Energy closer to the Material Plane and buffs undead

Transmutation
Life Extension: Increase your maximum age by 77 years.

