\subsubsection{Crodlu}
\begin{MonsterStats}
{Large Animal}
{4d8+12 (30 hp)}
{+5}
{15 m (10 squares)}
{16 ($-1$ size, +5 Dex, +2 natural), touch 14, flat-footed 11}
{+3/+11}
{Claw +6 melee (1d6+4)}
{2 claws +6 melee (1d6+4) and bite +1 melee (1d8+2)}
{3 m/1.5 m}
{Improved grab, pounce, rake 1d6+2}
{Low-light vision}
{Fort +7, Ref +9, Will +3}
{Str 19, Dex 21, Con 17, Int 2, Wis 14, Cha 6}
{\skill{Jump} +22, \skill{Listen} +7, \skill{Move Silently} +9, \skill{Spot} +0}
{\feat{Alertness}, \feat{Endurance}, \feat{Run}\textsuperscript{B}}
{Scrub Plains}
{Herd (5--30)}
{2}
{None}
{Always neutral}
{5--8 HD (Large)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Crodlu are a species of flightless, scaled avian that roams the wilderness in herds. They have powerful hind legs, which were built for jumping great lengths. Crodlu have very poor eyesight, but make up for it with an excellent sense of smell. Crodlu have great endurance, almost better than a mul‘s, and can run at high speeds for long periods of time.

    Female crodlu only lay one egg each year. When the chick hatches it is able to run and fight within minutes, having a great appetite. When it comes to feeding, crodlu will eat anything, preferring to hunt live game when there is some around over eating just vegetables.

    Crodlu herds can get as big as 30 strong. The herd leader is usually the largest, and will have more of a reddish scaly hide.

    Crodlu make great mounts, but are hard to control and train as such most of the time unless they are caught as chicks and are trained as mounts as they are being raised.
}

Crodlu attack with their fore claws first, and then bite. Sometimes they will substitute hind claws for fore claw attacks if they happen to be holding something or are unable to use their fore claws.

\textbf{Improved Grab (Ex):} To use this ability, a crodlu must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can rake.

\textbf{Pounce (Ex):} If a crodlu charges, it can make a full attack, including two rake attacks.

\textbf{Rake (Ex):} Attack bonus +6 melee, damage 1d6+2.

\textbf{Skills:} Crodlu receive a +10 racial bonus on \skill{Jump} checks and a $-4$ penalty on \skill{Spot} checks.
