\subsubsection{Crodlu, Heavy}
\begin{MonsterStats}
{Large Animal}
{5d8+20 (42 hp)}
{+5}
{12 m (8 squares)}
{17 ($-1$ size, +4 Dex, +4 natural), touch 13, flat-footed 13}
{+3/+13}
{Claw +8 melee (1d6+6)}
{2 claws +8 melee (1d6+6) and bite +3 melee (1d8+3)}
{3 m/1.5 m}
{Improved grab, pounce, rake 1d6+3}
{Low-light vision}
{Fort +7, Ref +9, Will +3}
{Str 22, Dex 19, Con 19, Int 2, Wis 12, Cha 7}
{\skill{Jump} +20, \skill{Listen} +7, \skill{Move Silently} +8, \skill{Spot} $-1$}
{\feat{Alertness}, \feat{Endurance}, \feat{Run}\textsuperscript{B}}
{Sandy Wastes and Stony Barrens}
{Herd (5--30)}
{3}
{None}
{Always neutral}
{5--8 HD (Large)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    The heavy crodlu has been specifically bred for carrying heavier loads (or passengers) and occasionally for light skirmisher activity. It is a little larger and a fair deal stronger than its smaller cousin, but lacks the keener combat abilities of its warfaring big brother.

    Heavy crodlu possess the same wicked claws and sharp beak of its fellows and have a similar life cycle, but their herds were originally released into the wild by breeders. They have long since developed into an identifiable strain, but these herds remain valuable commodities nevertheless.
}

Heavy crodlu are fierce opponents if provoked, but centuries of breeding have rendered them more docile than their cousins, and they tend to become skittish if cornered. When pressed, however, they respond with a pair of ripping foreclaws and a savage bite. Raking strikes from their rear claws are also used, preferably as part of a pounce from a superior position.

\textbf{Improved Grab (Ex):} To use this ability, a heavy crodlu must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can rake.

\textbf{Pounce (Ex):} If a heavy crodlu charges, it can make a full attack, including two rake attacks.

\textbf{Rake (Ex):} Attack bonus +6 melee, damage 1d6+2.

\textbf{Skills:} Heavy crodlu receive a +10 racial bonus on \skill{Jump} checks and a $-4$ penalty on \skill{Spot} checks.
