\subsubsection{Inix}
\begin{MonsterStats}
{Large Animal}
{6d8+18 (45 hp)}
{+2}
{12 m (8 squares)}
{17 ($-1$ size, +2 Dex, +6 natural), touch 11, flat-footed 15}
{+4/+12}
{Bite +7 melee (1d8+6) or tail slap +7 melee (1d4+6)}
{Bite +7 melee (1d8+6) or tail slap +7 melee (1d4+6)}
{3 m/1.5 m (3 m reach with tail)}
{Improved grab, swallow whole}
{Improved carrying capacity, low-light vision}
{Fort +8, Ref +7, Will +3}
{Str 19, Dex 15, Con 16, Int 2, Wis 12, Cha 6}
{\skill{Listen} +8, \skill{Spot} +7}
{\feat{Alertness}, \feat{Combat Reflexes}, \feat{Dodge}}
{Deserts}
{Solitary or pair}
{3}
{None}
{Always neutral}
{7--12 HD (Huge)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Inixes are midway in size between a kank and a mekillot. Inixes weigh roughly two tonnes and can grow up to 5 meters long.

    Inixes make good mounts because of the amount of weight they can carry for their size, which is two times their normal capacity.
}

In combat inixes are fierce enemies. They usually attack with their tail first, taking advantage of its increased reach, then move in and try to bite, hoping to be able to grapple or swallow whole their victim.

\textbf{Improved Grab (Ex):} To use this ability, an inix must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can attempt to swallow the foe the following round.

\textbf{Swallow Whole (Ex):} An inix can try to swallow a grabbed opponent two or more sizes smaller than itself by making a successful grapple check. Once inside, the opponent takes 1d8+6 points of crushing damage plus 4 points of acid damage per round from the inix's stomach. A swallowed creature can cut its way out by using a light slashing or piercing weapon to deal 15 points of damage to the stomach (AC 13). Once the creature exits, muscular action closes the hole; another swallowed opponent must cut its own way out. A Large inix's interior can hold 1 Small, 2 Tiny, 4 Diminutive, or 8 Fine opponents.

\textbf{Improved Carrying Capacity:} An inix's carrying capacity is double the normal for a creature of its Strength. A light load for an inix is up to 348 kilograms; a medium load is up to 702 kilograms; a heavy load is up to 1,050 kilograms. An inix can drag 5,250 kilograms.
