\subsection{Magic Items On The Body}
Many magic items need to be donned by a character who wants to employ them or benefit from their abilities. It's possible for a creature with a humanoid-shaped body to wear as many as twelve magic items at the same time. However, each of those items must be worn on (or over) a particular part of the body.

A humanoid-shaped body can be decked out in magic gear consisting of one item from each of the following groups, keyed to which place on the body the item is worn.

\begin{itemize*}
\item One headband, hat, helmet, or phylactery on the head
\item One pair of eye lenses or goggles on or over the eyes
\item One amulet, brooch, medallion, necklace, periapt, or scarab around the neck
\item One vest, vestment, or shirt on the torso
\item One robe or suit of armor on the body (over a vest, vestment, or shirt)
\item One belt around the waist (over a robe or suit of armor)
\item One cloak, cape, or mantle around the shoulders (over a robe or suit of armor)
\item One pair of bracers or bracelets on the arms or wrists
\item One glove, pair of gloves, or pair of gauntlets on the hands
\item One ring on each hand (or two rings on one hand)
\item One pair of boots or shoes on the feet
\end{itemize*}

Of course, a character may carry or possess as many items of the same type as he wishes. However, additional items beyond those listed above have no effect.

Some items can be worn or carried without taking up space on a character's body. The description of an item indicates when an item has this property. 