\section{City-States}
The Tablelands have been defined by its city-states for thousands of years. They shelter most of the humanoid population, and are packed and busy with their markets. Each of city-state is different---in their laws, customs, architecture... But all of them conform to the needs of survival and the needs of their sorcerer-kings.

\textbf{Sorcerer-Monarchs:} Absolute dictators, epic psionic defilers. They are the top of the social order, revered as deities with clergymen called templars. Sorcerer-monarchs reign with fear of losing their city and their lives, so they became avert to each other and to preservers. Because of this fear, they start wars whenever there is an internal problem---so the population doesn't rise against them but focus on fighting another city-state.

\textbf{Templars:} Priests to sorcerer-monarchs and bureaucrats for their government. As city agents, their bureaus are filled with treachery and political intrigue between other agencies of the city's bureaucracy. They are also the guardians of reading and writing, executing on the spot anyone demonstrating these critical skills.

\textbf{Merchants:} As people who abandoned their citizenship, merchants have no obligation to the city-states but they also have no protection from them. Through their control over the goods that come in and out of any city-state, trading emporiums exert power over city-states only rivaled by the sorcerer-monarchs themselves. Merchants also found a way to bypass the literacy prohibition, as most merchants can read and write in the secret language of their merchant houses.

\input{subsections/athas/city-states/balic.tex}
\input{subsections/athas/city-states/draj.tex}
\input{subsections/athas/city-states/gulg.tex}
\input{subsections/athas/city-states/nibenay.tex}
\input{subsections/athas/city-states/raam.tex}
\input{subsections/athas/city-states/tyr.tex}
\input{subsections/athas/city-states/urik.tex}
