\section{The World of Athas}
Athas is a desert-sun-scorched and wind-scoured, parched and endless, but that does not mean that the landscape is monotonous. Far from it; over each hill, behind each dune, the terrain is more awesome, more spectacular, and more beautiful than any one has seen before. North or south, east or west, Athas contains natural wonders and dangers undreamed of on other worlds.

Storms blow in from the Sea of Silt, walls of pearly dust billow ten thousand feet into the air, then come roiling ashore like a mountain range crashing down about unwary travelers. There are hundreds of different kinds of terrain on Athas, from wind-scoured pebble flats to twisted badlands canyons to gleaming sands to jumbled boulder fields.

In this chapter, the world of Athas is examined from the point of view of the Tablelands, also known as the Tyr Region, the region that has influenced Athas (for good or bad) the most.

\subsection{Time}
Each year is made up of exactly 375 days: the exact time between highest suns. Athasians have no seasons that govern their thinking of time, for there is no marked difference in temperature or weather patterns. However, the year is divided into three equal phases: High Sun, Sun Descending, and Sun Ascending. Highest sun is the first day of the year, and lowest sun indicates the midpoint of the year (which, incidentally, occurs at midnight and is generally observed in night-time ceremonies).

\subsection{Marking the Years}
Every city-state and merchant house has its own calendar, but the most commonly used is the Calendar of Kings. In the Calendar of Kings, years are counted off using a pair of concurrently running cycles: one of eleven parts, the other of seven. The eleven-part, or Endlean cycle, is counted and spoken first, in the order presented below. The seven-part, or Seofean cycle, is counted and spoken second. The Endlean cycle is complete when Athas' two moons, Ral and Guthay, meet in the heavens, resulting in a major eclipse that occurs every 11 years. The Seofean cycle is more abstract, occurring after Agitation has led back to Fury in the cosmos.

Every 77 years the cycle repeats itself, ending with a year of Guthay's Agitation and starting again with a new year of Ral's Fury. Each 77-year cycle is called a King's Age. There have been 189 complete King's Ages since this calendar was adopted more than 14,500 years ago.

So, the first year of each King's Age is a year of Ral's Fury. The next year is a year of Friend's Contemplation, etc. The 76th year of each King's Age is a year of Enemy's Reverence, followed by the 77th year, a year of Guthay's Agitation.

\Table{}{C C}{
\tableheader Endlean Cycle & \tableheader Seofean Cycle\\
Ral & Fury\\
Friend & Contemplation\\
Desert & Vengeance\\
Priest & Slumber\\
Wind & Defiance\\
Dragon & Reverence\\
Mountain & Agitation\\
King &\\
Silt &\\
Enemy &\\
Guthay &\\
}

While each city-state has its own official calendar, the dynastic merchant houses have, over the centuries, come to use a standardized book of days. This has evolved slowly over time as the need to efficiently coordinate activities with trading partners grew. The calendar is generally referred to as the Merchant's Calendar. In the cities, it usually bears the name of the largest merchant house (which also generally receives the credit for inventing it).

The Merchant's Calendar divides the 375-day year into three 125-day seasons---High Sun, Sun Descending and Sun Ascending. Each season is divided into four 30-day months made up of six day weeks. A five day long festival week in the middle of each season lies outside the confines of the months.

The year begins on the day of Highest Sun, midway through the season of High Sun.

\Table{}{l l c X}{
\tableheader Season & \tableheader Month & \tableheader Days & \tableheader Star Sign\\
High Sun & Dominary & 30 & Balimarash the Caravan\\
High Sun & Sedulous & 30 & Fiddle the Beetle\\
Sun Descending & Fortuary & 30 & Hesper the Kenku\\
Sun Descending & Macro & 30 & Saurus the Lizard\\
Sun Descending & Dessalia & 5 & On the cusp\\
Sun Descending & Fifthover & 30 & Hortle the Spider\\
Sun Descending & Hexameron & 30 & Sylk the Wyrm\\
Sun Ascending & Morrow & 30 & Tasker the Scorpion\\
Sun Ascending & Octavus & 30 & Pyrus the Wheel\\
Sun Ascending & Assalia & 5 & On the cusp\\
Sun Ascending & Thaumast & 30 & The Dragon\\
Sun Ascending & Anabasis & 30 & Tyrospur the Lion\\
High Sun & Hoard & 30 & Scratch the Basilisk\\
High Sun & Flagstaad & 30 & Krawler the Kank\\
High Sun & Zenalia & 5 & On the cusp
}