\PrestigeClass{Arch Defiler}
{Power comes at a price. I am willing to pay it.}{Marakesh, human arch defiler}
{Arch defilers are defilers who seek to increase the power of their magic at the cost of a greater taint of defilement. So foul is the magic commanded by these defilers, that their very souls are scarred. Animals become nervous, people feel uncomfortable, and yet the arch defiler demands obedience. To command their foul magics, arch defilers need physical stamina to resist the vast energies they manipulate.}
{d4}
{an}
{Almost all arch defilers are wizards corrupted by their desire for power. Sometimes an adept becomes powerful enough to become one, but this is rare to say the best.}
{\textbf{Skills:} \skill{Knowledge} (arcana) 8 ranks, \skill{Spellcraft} 8 ranks.

\textbf{Feats:} \feat{Agonizing Radius}, \feat{Great Fortitude}, any metamagic feat.

\textbf{Spells:} Able to cast 3rd level arcane spells.

\textbf{Special:} Must be a defiler.}
{\skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Disguise} (Cha), \skill{Intimidate} (Cha), \skill{Knowledge} (all skills individually) (Int), \skill{Profession} (Wiz), \skill{Spellcraft} (Int).}
{2}
{\PrestigeSpellTable}{
	% 1 & +0 & +0 & +0 & +2 & Tainted aura, defiler feat & +1 level of existing arcane spellcasting class\\
	% 2 & +1 & +0 & +0 & +3 &  & +1 level of existing arcane spellcasting class\\
	% 3 & +1 & +1 & +1 & +3 & Casting time metamagic 1/day & +1 level of existing arcane spellcasting class\\
	% 4 & +2 & +1 & +1 & +4 &  & +1 level of existing arcane spellcasting class\\
	% 5 & +2 & +1 & +1 & +4 & Painful radius, defiler feat & +1 level of existing arcane spellcasting class\\
	% 6 & +3 & +2 & +2 & +5 &  & +1 level of existing arcane spellcasting class\\
	% 7 & +3 & +2 & +2 & +5 & Casting time metamagic 2/day & +1 level of existing arcane spellcasting class\\
	% 8 & +4 & +2 & +2 & +6 &  & +1 level of existing arcane spellcasting class\\
	% 9 & +4 & +3 & +3 & +6 & Defiler feat & +1 level of existing arcane spellcasting class\\
	% 10 & +5 & +3 & +3 & +7 & Metamagic raze & +1 level of existing arcane spellcasting class\\

	1 & +0 & +0 & +0 & +2 & Tainted aura, raze feat & +1 level of existing arcane spellcasting class\\
	2 & +1 & +0 & +0 & +3 & Casting time metamagic 1/day & +1 level of existing arcane spellcasting class\\
	3 & +1 & +1 & +1 & +3 & Painful radius, raze feat & +1 level of existing arcane spellcasting class\\
	4 & +2 & +1 & +1 & +4 & Casting time metamagic 2/day & +1 level of existing arcane spellcasting class\\
	5 & +2 & +1 & +1 & +4 & Metamagic raze, raze feat & +1 level of existing arcane spellcasting class\\
}
{
% You study how to extract every possible amount of energy from your surroundings, no matter what the cost. You understand the adverse effects of defiling and use them to the fullest.
\textbf{Weapon and Armor Proficiency:} Arch defilers gain no proficiency with any weapon or armor.

\textbf{Spellcasting:} When a new arch defiler level is gained, you gain new spells per day as if you had also gained a level in whatever arcane spellcasting class in which  you belonged to before you added the prestige class. You do not, however, gain any other benefit a character of that class would have gained. This essentially means that you add the level of arch defiler to the level of whatever other arcane spellcasting class you have, and then determines spells per day and caster level accordingly. If you had more than one arcane spellcasting class before you became an arch defiler, you must decide to which class you add each level of arch defiler for the purpose of determining spells per day.

\textbf{Tainted Aura (Su):} An arch defiler is tainted by his arcane ways in such a matter that it is noticeable. People feel uncomfortable and wary when he is present and animals whimper when you approach. He suffers a $-1$ circumstance penalty to \skill{Bluff}, \skill{Diplomacy}, \skill{Gather Information} and \skill{Handle Animal} checks for every level of arch defiler. Likewise, he receives a +2 circumstance bonus to \skill{Intimidate} checks for every level of arch defiler. The tainted aura has a range of 1.5 meter per arch defiler level.

\textbf{Raze Feat:} At 1st, 3rd and 5th levels, an arch defiler gains a bonus raze feat. He must qualify for any feat requirements.

\textbf{Casting Time Metamagic:} An arch defiler of 2nd level or higher can apply a metamagic feat he knows to a spell at casting time, once per day. This does not increase the spell's level or require a higher level spell slot. Casting time metamagic doubles the casting time of the spell (a casting time of 1 action becomes 1 full round). At 4th level, he can use casting time metamagic twice per day, but only once per spell. Only metamagic feats that would increase a spell slot by 3 or less may be applied with casting time metamagic.

\textbf{Painful Radius:} At 3rd level, the penalties suffered to attacks, saves and skill checks for being caught in an arch defiler's defiling radius increase by one. This effect stacks with the \feat{Agonizing Radius} feat, bringing the modifier to a total of $-3$.

\textbf{Metamagic Raze:} At 5th level, an arch defiler can gather energy during spell preparation to improve his metamagic capacity. Spell slot level adjustments from metamagic feats are reduced by one (to a minimum of one), but only once per spell. For each use of metamagic raze, he defiles a 1.5-meter-radius where the spell is prepared. Preparation of multiple spells increase the radius by 1.5 meter for each spell prepared with this ability.

% \subsection{Playing an Arch Defiler}
% Your years of reckless defiling and delving into forbidden secrets have taken a toll on your soul. Your presence has become uncomfortable for most creatures. So what if you're doomed to spend your last days on Athas as a lonely, and sometimes hunted, wanderer? The power and knowledge you seek is worth any price.

% \subsubsection{Combat}
% Spellcasting remains your greatest strength and progresses at its full rate as you advance. Thus, your place in combat is not likely to change much---if you are like most wizards, you will hang back from melee in order to blast opponents with the most potent evocation spells you have available.

% All of your abilities revolve around defiling to make your spells stronger, so make sure to have a good mix of Raze feats---always good in a straightforward fight against a physically powerful foe.

% \subsubsection{Advancement}
% Arch defilers come from a variety of backgrounds. Human wizards corrupted by their desire for power often become arch defilers. So do nomadic elven mages without concern for the environment they leave behind them in the disappearing horizon, or those who want to increase their spellcasting powers to gain status in their tribes. What they all have in common is a fascination with the interweaving of magic, life, and power. With that fascination comes a lust for more knowledge, a lust that quickly overpowers any concerns about morality.

% As an arch defiler, you spend much of your time seeking out ancient scrolls containing forbidden secrets, ruins with arcane inscriptions, undead wizards and the vanished arts they might have preserved. Between adventures, you pore over the lore you have uncovered, looking for to one day to become as powerful as a sorcerer-king, or better yet, the Dragon.

% \subsubsection{Resources}
% The one resource you covet above others is knowledge. If you have arch defilers in your acquaintance---or even other defilers or similar characters with arcane interests---the exchange of knowledge can be highly profitable for all of you, if you manage to trust such corrupt and amoral people like yourself. Besides, keeping in touch with your peers puts you in a good position to seize their knowledge should some sad fate befall them.

% \subsection{Arch Defilers on Athas}
% \Quote{I remember the first time I drew in the sweet power of magic. I felt it course through my veins as the land around me turned to ash. I felt powerful, almost complete. Now, I am powerful. Let others worry about the ash, I am as far above those concerns as I am above the common man.}{Friztroy Gelt, under interrogation by high templars of Hamanu for destruction of the western grain fields.}

% Arch defilers can be found anywhere. Some are loners, practicing their dark art in secrecy, while others seek employment and safety in organizations and groups without moral scruples. NPC arch defilers can typically be found in the ranks of merchant houses, raiding tribes, or operating on their own.
% \subsubsection{Organization}
% There is no general organization of arch defilers. A very few arch defiler cabals have been created, but they were quickly destroyed or disbanded since arch defilers, like most defilers, do not usually play well with others.
% \subsubsection{NPC Reactions}
% Arch defilers are typically greeted with nervousness, dislike, or outright disgust. Their taint might be invisible, but their corruption is sometimes abundantly clear even to casual acquaintances. As a result, most NPCs have an initial reaction of unfriendly when encountering an arch defiler, even if they can't put a finger on the reason for their dislike.

% Druids, good elemental clerics, and members of the Veiled Alliance are natural enemies of arch defilers, and will do almost anything to send them to a swift death.
}
% \subsubsection{Arch Defiler Lore}
% {}
% {arcana}
% {The arch defiler is an arcane caster who focuses on defiling as an energy source.}
% {The arch defiler embraces the taint of defiling so much his very presence becomes tainted with it.}
% {Arch defilers learn defiling secrets that improves their spellcasting, weakens their foes, and grants them unearthly knowledge.}

% Alternatively, similar information might be learned through bardic knowledge checks, or \skill{Gather Information} checks made with Veiled Alliance members.