\PrestigeClass{Cerebremancer}
{The thing is, even when I'm all dried up and exhausted from this psionic clash, I still can get power from the land and throw it into your face. But what about you, telepath? What will you do when I dry you up? Let's see who lasts longer.}{Omran, dwarf cerebremancer}
{Cerebremancers combine simulteaneously the arcane power of the wizards with the psionic power of the manifesters. They are the prestige class that made the biggest impact in the whole Athas, as all sorcerer-kings are members of this prestige class. The primary factor for entering this class is the lust for power, the desire to master all the most powerful abilities Athas has to offer with the least amount of effort.

Even though the prestige class has such prominent and evil members, cerebremancers can be both defiler and preservers. Cerebremancers preservers aspire to use their psionic abilities to restore Athas. And all cerebremancers seek the lore behind their abilities, and eventually how a power similar to theirs changed the world.
}
{d4}
{a}
{Cerebremancers must be wizards multiclass. The vast majority of the class combinations is wizard/psion, since both classes depend on a high Intelligence. Less frequently, you can encounter wizard/wilders and even more rarely wizard/psychic warriors.}
{
\textbf{Skills:} \skill{Knowledge} (arcana) 6 ranks, \skill{Knowledge} (psionics) 6 ranks.

\textbf{Spells:} Able to cast 2nd-level arcane spells.

\textbf{Psionics:} Able to manifest 2nd-level powers.
}
{
\skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Knowledge} (arcana) (Int), \skill{Knowledge} (psionics) (Int), \skill{Profession} (Wis), \skill{Psicraft} (Int), and \skill{Spellcraft} (Int).
}
{2}
{\PrestigeOnlySpellTable}{
1 & +0 & +0 & +0 & +2 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
2 & +1 & +0 & +0 & +3 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
3 & +1 & +1 & +1 & +3 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
4 & +2 & +1 & +1 & +4 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
5 & +2 & +1 & +1 & +4 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
6 & +3 & +2 & +2 & +5 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
7 & +3 & +2 & +2 & +5 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
8 & +4 & +2 & +2 & +6 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
9 & +4 & +3 & +3 & +6 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
10 & +5 & +3 & +3 & +7 & +1 level of existing arcane spellcasting class/+1 level of existing manifesting class\\
}
{
\textbf{Weapon and Armor Proficiency:} Cerebremancers gain no proficiency with any weapon or armor.

\textbf{Spellcasting/Manifesting:} When a new cerebremancer level is attained, the character gains new spells per day as if he had also attained a level in any one arcane spellcasting class he belonged to before he added the prestige class. He gains additional power points per day and access to new powers as if he had also gained a level in any one manifesting class he belonged to previously. He does not, however, gain any other benefit a character of either class would have gained (bonus metamagic, metapsionic, or item creation feats, psicrystal special abilities, and so on). This essentially means that he adds the level of cerebremancer to the level of whatever other arcane spellcasting class and manifesting class the character has, then determines spells per day, caster level, power points per day, powers known, and manifester level accordingly.

If a character had more than one arcane spellcasting class or more than one manifesting class before he became a cerebremancer, he must decide to which class he adds each level of cerebremancer for purpose of determining spells per day, caster level, power points per day, powers known, and manifester level.
}
{}
{arcana or psionics}
{Cerebremancers seek to master the arcane power and the Way at the same time.}
{With the range of possibilities of wizards and psions, there certainly isn't any cerebremancer equal to another.}
{Unlocking the combined power of wizardry and psionics is the easiest way to be targeted by all the templarate of the Tablelands. Sorcerer-kings desire no rivals.}