\PrestigeClass{Convict}
{I'm not here by my own will, but I'm enjoying killing you.}{Nurodar, mul convict}
{Whether convicted of a crime, or merely accused by a templar, the result is always the same-the accused is branded a criminal. The consequences are imprisonment and slavery. The unfortunate convict either spends the remainder of his life at hard labor, or battles for survival in the arena. For some, the arena is the better choice. Convicts have nothing to lose and only time to gain.}
{d8}
{a}
{Convicts are usually multiclass bard/gladiator or gladiator/rogues that were unfortunate enough to meet a templar. Although rarer, single-classed gladiators can become convicts if they find themselves on the wrong end of the templar justice.}
{
\textbf{Base Attack Bonus:} +4.

\textbf{Skills:} \skill{Bluff} 6 ranks, \skill{Perform} (arena fighting) 8 ranks. One of the following: \skill{Intimidate} 8 ranks, \skill{Open Lock} 5 ranks, or \skill{Sleight of Hand} 5 ranks.

\textbf{Feats:} \feat{Weapon Focus} (any dagger).

\textbf{Special:} Able to use the dirty trick gladiatorial performance ability.

\textbf{Special:} Must have been convicted of any crime by a templar.
}
{
\skill{Balance} (Dex), \skill{Bluff} (Cha), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Diplomacy} (Cha), \skill{Disable Device} (Int), \skill{Escape Artist} (Dex), \skill{Hide} (Dex), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Move Silently} (Dex), \skill{Open Lock} (Dex), \skill{Perform} (Cha), \skill{Profession} (Wis), \skill{Search} (Wis), \skill{Sense Motive} (Wis), \skill{Sleight of Hand} (Dex), and \skill{Tumble} (Dex).
}
{6}
{\PrestigeWarriorTable}{
1 & +1 & +2 & +2 & +0 & Gladiatorial performance, dirty trick, sneak attack +1d6 \\
2 & +2 & +3 & +3 & +0 & \feat{Improved Feint}, improviser, poison use \\
3 & +3 & +3 & +3 & +1 & Blood in the eyes, sneak attack +2d6 \\
4 & +4 & +4 & +4 & +1 & Dirty fighter \\
5 & +5 & +4 & +4 & +1 & Experienced scoundrel, sneak attack +3d6 \\
}
{
\textbf{Weapon and Armor Proficiency:} Convicts gain no proficiency with any weapon or armor.

\textbf{Gladiatorial Performance:} Gladiator levels stack with convict levels for the purpose of determining the number of daily uses of gladiatorial performance, but not any other gladiatorial performance-related effects.

As a convict attains higher levels, he gains access to new gladiatorial performance abilities. These follow the normal rules for gladiatorial performance.

\textit{Dirty Trick (Ex):} Add together the character's levels from all classes that grant dirty trick to determine the total bonus and penalty can gain or impose with each use. For example, a 4th-level rogue/2nd-level gladiator/5th-level convict could gain a +2 bonus or impose a $-2$ penalty.

\textit{Blood in the Eyes (Ex):} A convict of 3rd level or higher with 11 or more ranks in \skill{Perform} (arena fighting) can use his arena presence to frighten his enemies. He can make a special attempt to demoralize an opponent, adding his class level to his \skill{Intimidate} check. If the convict succeeds in demoralizing his opponent with this ability, he may treat the target as flat-footed for the purpose of dealing sneak attack damage.

\textbf{Sneak Attack:} This is exactly like the rogue ability of the same name. The extra damage dealt increases by +1d6 every other level (1st, 3rd, and 5th). If a convict gets a sneak attack bonus from another source the bonuses on damage stack.

\textbf{Improved Feint:} At 2nd level, a convict gains \feat{Improved Feint} as a bonus feat.

\textbf{Improviser (Ex):} At 2nd level, a convict's improvised weapon deals as much damage as his unarmed strike plus an extra 1d4 points. When a convict rolls a natural 1 on an attack roll while using an improvised weapon, that weapon breaks apart and becomes useless.

\textbf{Poison Use:} At 2nd level, convicts become trained in the use of poison and never risk accidentally poisoning themselves when applying poison to a blade.

\textbf{Dirty Fighter (Ex):} Beginning at 4th level, a convict may surprise an opponent whenever he uses a dirty trick. Whenever a convict imposes a penalty on an enemy with the dirty trick gladiatorial performance, he may use feint as a free action (see \skill{Bluff} skill).

\textbf{Experienced Scoundrel (Ex):} At 5th level, a convict may add +5 competence bonus to \skill{Bluff} and \skill{Sense Motive} checks made in combat. He may use dirty trick more than once against the same enemy in a single round. He may also repeat dirty tricks against the same opponent in the same encounter, but not in the same round.

}