\PrestigeOnlySpellTable{The Divine Mind}{
 1st & +0 & +0 & +0 & +2 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 2nd & +1 & +0 & +0 & +3 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 3rd & +1 & +1 & +1 & +3 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 4th & +2 & +1 & +1 & +4 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 5th & +2 & +1 & +1 & +4 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 6th & +3 & +2 & +2 & +5 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 7th & +3 & +2 & +2 & +5 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 8th & +4 & +2 & +2 & +6 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
 9th & +4 & +3 & +3 & +6 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
10th & +5 & +3 & +3 & +7 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
11th & +5 & +3 & +3 & +7 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
12th & +6 & +4 & +4 & +8 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
13th & +6 & +4 & +4 & +8 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
14th & +7 & +4 & +4 & +9 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
15th & +7 & +5 & +5 & +9 & +1 level of existing divine spellcasting class/+1 level of existing manifesting class\\
}
\PrestigeClass{Divine Mind}
{In order to spread the fiery chants, one needs to improve his inner flame and \emph{burn bright}!}{Hammu, half-elf divine mind}
{
The road of theology is paved in the search of answers to reconcile the entities of higher power with the self. Divine minds master both the psionic powers brought by their own minds as the divine spells given by their patrons. Clerics with this prestige class unlock the potential to become elemental creatures in the future, while druids with this prestige class unlock the potential to mend with a spirit of the land.
}
{d4}
{a}
{Divine minds must be manifesters multiclass. Most of the class combinations are cleric/psion or druid/psion, since those classes depend on a high Wisdom. Less frequently, you can encounter templar/psions.}
{
\textbf{Skills:} \skill{Knowledge} (nature) 4 ranks, \skill{Knowledge} (psionics) 9 ranks, \skill{Knowledge} (the planes) 4 ranks.

\textbf{Spells:} Able to cast 2nd-level divine spells.

\textbf{Psionics:} Able to manifest powers from 2 different disciplines.
}
{
\skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Knowledge} (nature), \skill{Knowledge} (psionics) (Int), \skill{Knowledge} (religion) (Int), \skill{Knowledge} (the planes) (Int), \skill{Profession} (Wis), \skill{Psicraft} (Int), and \skill{Spellcraft} (Int).
}
{2}
{}{}
{
\textbf{Weapon and Armor Proficiency:} Divine minds gain no proficiency with any weapon or armor.

\textbf{Spellcasting/Manifesting:} When a new divine mind level is attained, the character gains new spells per day as if he had also attained a level in any one divine spellcasting class he belonged to before he added the prestige class. He gains additional power points per day and access to new powers as if he had also gained a level in any one manifesting class he belonged to previously. He does not, however, gain any other benefit a character of either class would have gained (bonus metamagic, metapsionic, or item creation feats, psicrystal special abilities, and so on). This essentially means that he adds the level of divine mind to the level of whatever other divine spellcasting class and manifesting class the character has, then determines spells per day, caster level, power points per day, powers known, and manifester level accordingly.

If a character had more than one divine spellcasting class or more than one manifesting class before he became a divine mind, he must decide to which class he adds each level of divine mind for purpose of determining spells per day, caster level, power points per day, powers known, and manifester level.
}
