\PrestigeClass{Earth Defender}
{Arrogant aristocrats, witless farmers and vile defilers---they are all the same. They are my enemies, for they bring death to the fading life I have sworn to protect. Woe to these parasites if they cross my path!}{Nuan, human earth defender}
{Earth defenders are preservers concerned with protecting the environment at all costs. Some earth defenders choose to protect an area of land, while others devote their efforts to protect a species. The earth defender's charge is called a ward, and she is prepared to go to almost any length to protect it. Many earth defenders are fanatics. Their hatred against defilers or anything else that could harm their ward can be extreme. Death is the most usual punishment for threatening the earth defender's ward.}
{d8}
{an}
{
Earth defenders are single or multi-classed preserver wizards. Ranger/earth defenders often range across long distances, protecting members of endangered species wherever they journey. Druid/earth defenders, especially those who are grove masters, tend to guard a specific area.

Earth defenders are sworn enemies of defilers. NPC earth defenders are usually encountered protecting their chosen wards.
}
{
\textbf{Alignment:} Any nonlawful.

\textbf{Base Attack Bonus:} +3.

\textbf{Skills:} \skill{Hide} 6 ranks, \skill{Knowledge} (nature) 8 ranks, \skill{Spellcraft} 8 ranks, \skill{Survival} 6 ranks.

\textbf{Spells:} Able to cast 2nd level arcane spells.

\textbf{Special:} Must be a preserver.
}
{\skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Disguise} (Cha), \skill{Hide} (Dex), \skill{Intimidate} (Cha), \skill{Knowledge} (arcana) (Int), \skill{Knowledge} (dungeoneering) (Int), \skill{Knowledge} (geography) (Int), \skill{Knowledge} (nature) (Int), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Profession} (Wis), \skill{Spellcraft} (Int), \skill{Spot} (Wis), and \skill{Survival} (Wis).}
{6}
{\PrestigeSpellTable}{
1 & +0 & +0 & +2 & +0 & Skirmish +1d6, ward +1 & \\
2 & +1 & +0 & +3 & +0 & Nature's ally & +1 level of existing arcane spellcasting class \\
3 & +2 & +1 & +3 & +1 & Skirmish +1d6/+1 & +1 level of existing arcane spellcasting class \\
4 & +3 & +1 & +4 & +1 & Evasion & +1 level of existing arcane spellcasting class \\
5 & +3 & +1 & +4 & +1 & Skirmish +2d6/+1, ward +2 & \\
6 & +4 & +2 & +5 & +2 & Camouflage, armored mage & +1 level of existing arcane spellcasting class \\
7 & +5 & +2 & +5 & +2 & Skirmish +2d6/+2 & +1 level of existing arcane spellcasting class \\
8 & +6 & +2 & +6 & +2 & Arcane skirmish & +1 level of existing arcane spellcasting class \\
9 & +6 & +3 & +6 & +3 & Skirmish +3d6/+2, ward +3 & \\
10 & +7 & +3 & +7 & +3 & Hide in plain sight & +1 level of existing arcane spellcasting class \\
}
{
\textbf{Weapon and Armor Proficiencies:} Earth defenders are proficient with all simple  weapons, plus the handaxe, tortoise blade, atlatl, and shortbow. Earth defenders are proficient with light armor, but not shields.

\textbf{Skirmish (Ex):} An earth defender relies on mobility to deal extra damage and improve her defense. She deals an extra 1d6 points of damage on all attacks she makes during any round in which she moves at least 3 meters. The extra damage applies only to attacks taken during the earth defender's turn. This extra damage increases by 1d6 for every four levels gained above 1st (2d6 at 5th, 3d6 at 9th level).

The extra damage only applies against living creatures that have a discernible anatomy. Undead, constructs, oozes, plants, incorporeal creatures, and creatures immune to extra damage from critical hits are not vulnerable to this additional damage. The earth defender must be able to see the target well eough to pick out a vital spot and must be able to reach such a spot. Earth defenders can apply this extra damage to ranged attacks made while skirmishing, but only if the target is within 9 meters.

At 3rd level, an earth defender gains a +1 competence bonus to Armor Class during any round in which she moves at least 3 meters. The bonus applies as soon as the earth defender has moved 3 meters, and lasts until the start of her next turn. This bonus improves by 1 for every four levels gained above 3rd (+2 at 7th level).

An earth defender loses this ability when wearing medium or heavy armor or when carrying a medium or heavy load. If she gains the skirmish ability from another class, the bonuses stack.

\textbf{Ward (Ex):} At 1st level, an earth defender chooses a biome to guard from the ranger's favored terrains (see \tabref{Athasian Terrains})---except Obsidian Waste, since it is a lifeless place. She may add her class level as bonus on \skill{Knowledge} (geography) and \skill{Knowledge} (nature) checks about her ward and its species. Whenever she is actively defending her ward, she gains +1 competence in all saves. This bonus increases by +1 for every four levels gained about the 1st (+2 at 5th, +3 at 9th).

The earth defender chooses a new biome to guard at every four levels above the 1st (5th and 9th levels).

The earth defender must defend her wards, and the endangered species of plants and animals they host. This puts her in direct conflict with defilers. Whenever an earth defender encounters a defiler, she must make a DC 20 Will save or confront her hated enemy---even if it would be foolish or even deadly to do so.

\textbf{Nature's Ally (Ex):} Beginning at 2nd level, Spirits of the Land recognize the earth defender's dedication to nature and awards her. The earth defender adds all \emph{summon nature's ally} spells to her spell list, and she can use her spell slots to prepare \emph{summon nature's ally} spells. She does not need a spellbook to prepare these spells.

\textbf{Evasion (Ex):} At 4th level, an earth defender can avoid even magical and unusual attacks with great agility. If she makes a successful Reflex saving throw against an attack that normally deals half damage on a successful save, she instead takes no damage. Evasion can be used only if the earth defender is wearing light armor or no armor. A helpless earth defender does not gain the benefit of evasion.

\textbf{Camouflage (Ex):} Beginning at 6th level, an earth defender can use the \skill{Hide} skill in any sort of natural terrain, even if the terrain doesn't grant cover or concealment. She loses this benefit when wearing medium or heavy armor or when carrying a medium or heavy load.

\textbf{Armored Mage (Ex):} At 6h level, an earth defender ignores arcane spell failure chances when wearing light armor.

\textbf{Arcane Skirmish (Ex):} Beginning at 8th level, an earth defender may sacrifice her arcane powers to improve a skirmish attack.

Whenever she moves at least 3 meters, the earth defender may sacrifice one of her daily spell slots (of 1st level or higher), as a swift action. She gains a bonus on all her attack rolls and a bonus to AC both equal to the level of the spell sacrificed. These bonuses last until the start of her next turn.

For example, Nuan is a 8th level earth defender with able to cast 5th-level spells. On her turn, after moving 3 meters she chooses to sacrifice one of her 5th-level spells for the day, marking it off as if she had cast it. Until the end of her turn, she deals additional 2d6 damage from skirmish. Until the start of her next turn, she has +5 bonus on her attack rolls, and gains a total of +7 AC (+2 competence from skirmish and +5 from arcane skirmish).

\textbf{Hide in Plain Sight (Ex):} While in any sort of natural terrain, an earth defender of 10th level can use the \skill{Hide} skill even while being observed.

\subsubsection{Ex-Earth Defenders}
An earth defender who defiles, willfully allows damage to her ward, or refuses to help a fellow defender loses all earth defender abilites (except weapon and armor proficiencies). She may not progress any farther in levels as an earth defender. She regains her abilities and advancement potential if she atones for her violation (see the \spell{atonement} spell description), as appropriate.
}