\PrestigeSpellTable{The Elemental Singer}{
 1st & +0 & +0 & +0 & +2 & Elemental singing, inspire courage & +1 level of existing divine spellcasting class \\
 2nd & +1 & +0 & +0 & +3 &                                    & +1 level of existing divine spellcasting class \\
 3rd & +1 & +1 & +1 & +3 &                                    & +1 level of existing divine spellcasting class \\
 4th & +2 & +1 & +1 & +4 & Bonus domain spells                & +1 level of existing divine spellcasting class \\
 5th & +2 & +1 & +1 & +4 & Song of enduring                   & +1 level of existing divine spellcasting class \\
 6th & +3 & +2 & +2 & +5 &                                    & +1 level of existing divine spellcasting class \\
 7th & +3 & +2 & +2 & +5 & Bonus domain                       & +1 level of existing divine spellcasting class \\
 8th & +4 & +2 & +2 & +6 &                                    & +1 level of existing divine spellcasting class \\
 9th & +4 & +3 & +3 & +6 &                                    & +1 level of existing divine spellcasting class \\
10th & +5 & +3 & +3 & +7 & Sacred song                        & +1 level of existing divine spellcasting class \\
}
\PrestigeClass{Elemental Singer}
{Listen to the call of the wind, and all of its notes!}{Daaku, air singer}
{Element singers are elven clerics. They serve as advisors, healers, leaders, organizers of rituals of passage, and perform other duties for their tribe. Element singers are viewed with awe and respect due to their ability to commune with the elemental force they revere, and the positions they hold within their elven tribes. An elven tribe seldom has more than one or two element singers, and each tribe has its own distinct element traditions. Element singers who worship other elements usually find themselves ostracized and forced to leave their tribe.}
{d6}
{an}
{Element singers are always of elven blood. Most are full-blooded elves, but on rare occasions a half-elf cleric may aspire to the rank of element singer.}
{
\textbf{Race:} Elf or half-elf.

\textbf{Skills:} \skill{Perform} (sing) 5 ranks, \skill{Knowledge} (religion) 10 ranks.

\textbf{Spells:} Able to cast 4th-level divine spells.

\textbf{Special:} Must have an element as patron.
}
{
\skill{Concentration} (Con), \skill{Craft} (Int), \skill{Disguise} (Cha), \skill{Handle Animal} (Cha), \skill{Heal} (Wis), \skill{Knowledge} (nature) (Int), \skill{Knowledge} (history) (Int), \skill{Knowledge} (religion) (Int), \skill{Perform} (Cha), \skill{Profession} (Wis), \skill{Spellcraft} (Int), and \skill{Survival} (Wis).
}
{2}
{}{}
{
\textbf{Weapon and Armor Proficiencies:} Elemental singers gain no proficiency with any weapon or armor.

\textbf{Spellcasting:} When a new elemental singer level is gained, the character gains new spells per day as if she had also gained a level in whatever divine spellcasting class in which they could cast 3rd-level spells before they added the prestige class. She does not, however, gain any other benefit a character of that class would have gained. This essentially means that she adds the level of battle dancer to the level of whatever other divine spellcasting class she has, and then determines spells per day and caster level accordingly. If she had more than one divine spellcasting class before she became a battle dancer, she must decide to which class she adds each level of battle dancer for the purpose of determining spells per day.

\textbf{Elemental Singing:} Once per day per class level, an elemental singer can use her voice to product magical effects on those around her. Each ability requires a minimum elemental singer level, and some require a minimum number of ranks in \skill{Perform} (sing) to qualify.

If an elemental singer has bard levels, she can add her bard levels to her elemental singer levels to determine the number of daily uses of her elemental singing.

\textit{Inspire Courage (Su):} An elemental singer can use her elemental singing to inspire courage in her allies (including herself), bolstering them against fear and improving their combat abilities. To be affected, an ally must be able to hear the singer perform. The effect lasts for as long as the ally hears the singer perform and for 5 rounds thereafter. An affected ally receives a +1 morale bonus on saving throws against charm and fear effects and a +1 morale bonus on attack and weapon damage rolls. Inspire courage is a mind-affecting ability.

An elemental singer's ability to inspire courage doesn't normally improve with level. However, if an elemental singer already has this ability from another class (such as from bard levels), add together her class levels from all classes that grant this ability to determine the morale bonus granted by this ability. For example, a 2nd-level bard/5th-level fire cleric/6th-level elemental singer would grant a +2 morale bonus on the appropriate rolls.

\textit{Song of Enduring (Su):} An elemental singer of 5th level or higher with 10 or more ranks in \skill{Perform} (sing) can call upon the elemental healing magic on her allies. Each ally within 9 meters who can see and hear the elemental singer gains fast healing 3, and the mettle ability. If the ally makes a successful Fortitude or Will save against an attack that would normally have a lesser effect with a successful save (such as a spell with a saving throw entry of Will half or Fortitude partial), the effect is instead completely negated. Mettle only works as long as the ally is conscious. If an ally already has fast healing, this song improves it by 3. An elemental singer can keep up her song of enduring for one minute.

\textit{Sacred Song (Su):} An elemental singer of 10th level or higher with 20 or more ranks in \skill{Perform} (sing) can use chant holy words to her elemental patrons and call for blessings upon her allies. Each ally within 9 meters who can see and hear the elemental singer gains +4 sacred bonus to AC, +4 sacred bonus on saving throws, spell resistance equal to her ranks in \skill{Perform} (sing). The effect lasts for as long as the ally hears the song and 5 rounds thereafter.

\textbf{Bonus Domain Spells:} At 4th level, an elemental singer gains one new domain spell slot for the spell level she is capable of casting. Whenever she gains the access to a new spell level, she gains a new domain spell slot of that level.

\textbf{Bonus Domain:} At 7th level, an elemental singer may choose a bonus domain of her choice. The character can choose any domain made available by her element. The character gains the granted power associated with the domain she chooses, and can select the spells in that domain as her daily domain spells.

\subsubsection{Ex-Elemental Singers}
An elemental singer who defiles, worships a sorcerer-king, or refuses to answer a call for help from a member of her tribe loses all elemental singer abilities. She may not progress any farther in levels as an elemental singer. She regains her abilities and advancement potential if she atones for her violation (see the \spell{atonement} spell description), as appropriate.
}
