\PrestigeClass{Exterminator}
{I'll suck the life out of you and your damned plants, druid!}{Akrun, half-elf exterminator}
{Exterminators are defilers who use their defiling methods to purposefully destroy the ecosystem. Some of these defilers enjoy the rush of power that destroying plants give them; some are so consumed by hatred that they want to annihilate everything in their path. Others may be convinced that the evil plants of Athas need to be obliterated.}
{d6}
{an}
{Exterminators are usually evokers or necromancers, or defilers who enjoy the destruction of the flora. Without devoting time to improve his defiling, a wizard cannot become an exterminator.}
{
\textbf{Alignment:} Any nongood.

\textbf{Skills:} \skill{Craft} (poisonmaking) 5 ranks, \skill{Knowledge} (nature) 8 ranks, \skill{Spellcraft} 5 ranks.

\textbf{Feats:} \feat{Efficient Raze}, \feat{Exterminating Raze}.

\textbf{Spells:} Able to cast 3rd-level arcane spells.

\textbf{Special:} Must be a defiler.
}
{\skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Disguise} (Cha), \skill{Intimidate} (Cha), \skill{Knowledge} (arcana) (Int), \skill{Knowledge} (nature) (Int), \skill{Literacy} (N/A), \skill{Profession} (Wis), \skill{Spellcraft} (Int), and \skill{Survival} (Wis).}
{4}
{\PrestigeSpellTable}{
1 & +0 & +2 & +0 & +2 & Extended raze, poison use, \emph{revert growth} & +1 level of existing arcane spellcasting class \\
2 & +1 & +3 & +0 & +3 & Poison mastery & +1 level of existing arcane spellcasting class \\
3 & +2 & +3 & +1 & +3 & Razing sustenance & +1 level of existing arcane spellcasting class \\
4 & +3 & +4 & +1 & +4 & Arcane poison & +1 level of existing arcane spellcasting class \\
5 & +3 & +4 & +1 & +4 & \emph{Revert awakening} & +1 level of existing arcane spellcasting class \\
}
{
\textbf{Weapon and Armor Proficiencies:} Exterminators are proficient with all simple  weapons, plus the scythe. Exterminators are not proficient with any armor or shield.

\textbf{Extended Raze:} Because they love destroying plants so much and practice it so thoroughly, exterminators leave an increased razed area. Increase the defiling radius by 50\%, after applying all raze feats.

\textbf{Poison Use:} Exterminators are trained in the use of poison and never risk accidentally poisoning themselves when applying poison to a blade.

\textit{Revert Growth} \textbf{(Sp):} An exterminator can revert the effect of spells that rely on plant growth: \spell{entangle}, \spell{plant renewal}, \spell{plant growth}, \spell{spike growth}. In order to revert one of those spells, the exterminator must spend a spell slot of the same level or higher than the spell being reverted.

\textbf{Poison Mastery (Ex):} Starting at 2nd level, an exterminator may take 10 when crafing one chosen type of poison: contact, ingested, inhaled, or injury.

\textbf{Razing Sustenance (Su):} At 3rd level and higher, an exterminator gains his daily needs of food or water to survive whenever he defiles in an infertile terrain or better (see \chapref{Magic}).

\textbf{Arcane Poison (Ex):} Starting at 4th level, an exterminator may infuse poison with the effect of an arcane spell of 5th-level or lower that targets one or more creatures. This requires raw materials that cost a value equal to the spell level $\times$ exterminator's caster level $\times$ 25 cp. Crafting an arcane poison increases the craft time by one day, but only after the base poison has been completed (see \skill{Craft} skill).

When the target is inflicted with the poison, he is the target of the spell infused.

\textit{Revert Awakening} \textbf{(Sp):} At 5th level, an exterminator can revert the effect of spells that animate plants: \spell{awaken}, \spell{animate plants}, \spell{shambler}. In order to revert those spells, the exterminator must spend a spell slot of the same or higher level as the spell being reverted. If the spell being reverted required XP to cast, the exterminator must spend the same amount of XP to revert the spell.
}