\PrestigeClass{Horizon Walker}
{Been there, done that.}{Alahna, horizon walker}
{Horizon walkers are ever-travelers, adventuring to the most interesting places in Athas---and beyond. These travels make them adapt to any environment they find themselves, but also more distant as nothing can truly impress them.}
{d8}
{a}
{Rangers are predominately the class that makes the ranks of horizon walkers. But air clerics, bards, even barbarians and rogues occasionally adopt the prestige class. The one thing all have in common is their lust for new places.}
{
\textbf{Skills:} \skill{Knowledge} (geography) 8 ranks.

\textbf{Feats:} \feat{Endurance}.
}
{
\skill{Balance} (Dex), \skill{Climb} (Str), \skill{Diplomacy} (Cha), \skill{Handle Animal} (Cha), \skill{Hide} (Dex), \skill{Knowledge} (geography) (Int), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Profession} (Wis), \skill{Ride} (Dex), \skill{Speak Language} (N/A), \skill{Spot} (Wis), and \skill{Survival} (Wis).
}
{4}
{\PrestigeWarriorTable}{
1 & +1 & +2 & +0 & +0 & Terrain mastery\\
2 & +2 & +3 & +0 & +0 & Terrain mastery\\
3 & +3 & +3 & +1 & +1 & Terrain mastery\\
4 & +4 & +4 & +1 & +1 & Terrain mastery\\
5 & +5 & +4 & +1 & +1 & Terrain mastery\\
6 & +6 & +5 & +2 & +2 & Planar terrain mastery\\
7 & +7 & +5 & +2 & +2 & Planar terrain mastery\\
8 & +8 & +6 & +2 & +2 & Planar terrain mastery\\
9 & +9 & +6 & +3 & +3 & Planar terrain mastery\\
10 & +10 & +7 & +3 & +3 & Planar terrain mastery\\
}
{
\textbf{Weapon and Armor Proficiency:} Horizon walkers gain no proficiency with any weapon or armor.

\textbf{Terrain Mastery:} At each level, the Horizon Walker adds a new terrain environment to their repertoire from those given below. Terrain mastery gives a horizon walker a bonus on checks involving a skill useful in that terrain, or some other appropriate benefit. A horizon walker also knows how to fight dangerous creatures typically found in that terrain, gaining a +1 insight bonus on attack rolls and damage rolls against creatures with that terrain mentioned in the Environment entry of their descriptions. The horizon walker only gains the bonus if the creature description specifically lists the terrain type.

Horizon walkers take their terrain mastery with them wherever they go. They retain their terrain mastery bonuses on skill checks, attack rolls, and damage rolls whether they're actually in the relevant terrain or not.

\textbf{Planar Terrain Mastery:} Planar terrain mastery functions just like terrain mastery, except that the horizon walker can choose one of the planar categories at each level. The horizon walker can take a non-planar terrain type instead, if she wishes.

\subsubsection{Terrain Mastery Benefits}
\textbf{Aquatic:} You gain a +4 competence bonus on Swim checks, or a +3-meter bonus to your swim speed if you have one. You gain a +1 insight bonus on attack and damage rolls against aquatic creatures.

\textbf{Desert:} You resist effects that tire you. You are immune to fatigue, and anything that would cause you to become exhausted makes you fatigued instead. You gain a +1 insight bonus on attack and damage rolls against desert creatures.

\textbf{Forest:} You have a +4 competence bonus on Hide checks. You gain a +1 insight bonus on attack and damage rolls against forest creatures.

\textbf{Hills:} You gain a +4 competence bonus on Listen checks. You gain a +1 insight bonus on attack and damage rolls against hills creatures.

\textbf{Marsh:} You have a +4 competence bonus on Move Silently checks. You gain a +1 insight bonus on attack and damage rolls against marsh creatures.

\textbf{Mountains:} You gain a +4 competence bonus on Climb checks, or a +3-meter bonus to your climb speed if you have one. You gain a +1 insight bonus on attack and damage rolls against mountain creatures.

\textbf{Plains:} You have a +4 competence bonus on Spot checks. You gain a +1 insight bonus on attack and damage rolls against plains creatures.

\textbf{Underground:} You have 18-meter darkvision, or 36-meter darkvision if you already had darkvision from another source. You gain a +1 insight bonus on attack and damage rolls against underground creatures.

\textbf{Fiery (Planar):} This kind of planar terrain mastery provides you with resistance to fire 20. You gain a +1 insight bonus on attack and damage rolls against outsiders and elementals with the fire subtype.

\textbf{Weightless (Planar):} You gain a +9-meter bonus to your fly speed on planes with no gravity or subjective gravity. You gain a +1 insight on attack and damage rolls against creatures native to the Astral Plane, the Elemental Plane of Air, and the Ethereal Plane.

\textbf{Cold (Planar):} This kind of planar terrain mastery provides you with resistance to cold 20. You gain a +1 insight bonus on attack and damage rolls against outsiders and elementals with the cold subtype.

\textbf{Shifting (Planar):} You instinctively anticipate shifts in the reality of the plane that bring you closer to your destination, giving you the spell-like ability to use dimension door (as the spell cast at your character level) once every 1d4 rounds. You gain a +1 insight bonus on attack and damage rolls against outsiders and elementals native to a shifting plane.

\textbf{Cavernous (Planar):} You gain tremorsense with a 9-meter range.
}
{}
{geography or the planes}
{Horizon walkers cannot stay in one place for long. They always have something to show from the places they visit.}
{Those walkers have adaptations for each environment they visited.}
{They don't travel only within Athas but go beyond, to other planes. And they get strange powers for traveling to those planes.}