\PrestigeClass{Jaguar Knight}
{The draji might be mekillots in their skulls, but in their hearts they are jaguars.}{Chao Chin, nibenese entrepreneur}
{The jaguar knights are Draj's finest elite warriors. They undergo intense training, learning to put fear into their opponents before they strike. Their skills as battlefield warriors are unrivaled in Draj, as they are immune to fear and can wade through vast amounts of foes, cleaving their way. Jaguar knights are flawless in their own and every other Draji's eyes---resistant against cowardly mental attacks and powerful enough to strike down any foe foolish enough to stand in their way. The ferocity of the jaguar stirs in the heart of the jaguar knight, and his scream leaves enemies trembling before they die.

Jaguar knights are proud warriors. They frown upon cowardice and believe mercy is for the weak. Combatants who do not stare their enemy in the eye are shown no respect. Jaguar knights seldom get along with rogues and bards who rely upon stealth and tricks such as poison to overcome their enemies. Nor do jaguar knights trust wizards or wielders of the Way, but they do recognize divine spellcasting for its healing properties that allow them to recover quickly to be engaged in battle again sooner.}
{d10}
{a}
{Jaguar knights usually come from the ranks of fighters, gladiators, rangers or the psychic warrior class. Occasionally a particularly determined member of another class becomes a jaguar knight, but these characters are rare.}
{
\textbf{Base Attack Bonus:} +7.

\textbf{Feats:} \feat{Iron Will}, \feat{Power Attack}, \feat{Cleave}, \feat{Great Cleave}.

\textbf{Special:} Must have been trained in the Draji army.
}
{
\skill{Climb} (Str), \skill{Craft} (Int), \skill{Handle Animal} (Cha), \skill{Intimidate} (Cha), \skill{Jump} (Str), and \skill{Knowledge} (warcraft) (Int).
}
{2}
{\PrestigeWarriorTable}{
1 & +1 & +2 & +0 & +2 & Know no fear\\
2 & +2 & +3 & +0 & +3 & Supreme cleave\\
3 & +3 & +3 & +1 & +3 & Slippery mind\\
4 & +4 & +4 & +1 & +4 & Jaguar roar\\
5 & +5 & +4 & +1 & +4 & Improved power attack\\
}
{
\textbf{Weapon and Armor Proficiencies:} The jaguar knight is proficient with all simple and martial weapons, all types of armor (light, medium, heavy), and shields (including tower shields).

\textbf{Know No Fear:} Jaguar knights are immune to fear-effects.

\textbf{Supreme Cleave:} The jaguar knight may take his 5 foot step before executing his \feat{Cleave} or \feat{Great Cleave} attack.

\textbf{Slippery Mind (Ex):} At 3rd level, as part of their intense training involves sharpening their mental defense capabilities against the attacks of telepaths, and the result of this painful exercise is an ability to shrug off mental attacks. If a jaguar knight is affected by an enchantment spell or effect and fails his saving throw, he can attempt it again 1 round later at the same DC. He gets only this one extra chance to succeed on his saving throw.

\textbf{Jaguar Roar:} At 4th level, a jaguar knight gains the \feat{Jaguar Roar} feat even if he does not meet the prerequisites. If the jaguar knight already possesses the \feat{Jaguar Roar} feat, the save DC increases by 2.

\textbf{Improved Power Attack:} The testament of the master warrior in Draj, the jaguar strike is legendary. A jaguar knight deals +50\% the normal damage from his use of the \feat{Power Attack} feat. In other words, when using the \feat{Power Attack} feat, a jaguar knight wielding a two-handed weapon gains a +3 bonus on damage rolls (instead of a +2 bonus) for each $-1$ penalty he applies to his attack rolls.
% When using the \feat{Power Attack} feat, the jaguar knight multiplies the number subtracted from his base attack by 1.5, and adds this number (rounded down) to his damage roll. For instance, if he subtracts 4 points from his base attack, he adds 6 points to damage.
}
{}
{local [Draj] or warcraft}
{}
{}
{}