\PrestigeClass{Jazst}
{Don't die yet, we have a crowd to please.}{Sandsinger, elf jazst}
{Jazst are widely traveled theatrical performers in the Athasian arenas. Jazst are always free, and the only gladiatorial combatants that travel freely between the arenas of major cities. Jazst are usually early warm-up acts that amuse the eager crowds.}
{d10}
{a}
{Jazsts come mostly from gladiator backgrounds, although there are quite some fighters and rangers. Most multiclass are bard/gladiators that use their poison to weaken their foes while dancing.}
{
\textbf{Base Attack Bonus:} +5.

\textbf{Skills:} \skill{Jump} 5 ranks, \skill{Perform} (dance) 8 ranks, \skill{Tumble} 5 ranks.

\textbf{Feats:} \feat{Dodge}, \feat{Mobility}, \feat{Weapon Focus} (armor spikes).
}
{\skill{Balance} (Dex), \skill{Bluff} (Cha), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Diplomacy} (Cha), \skill{Disguise} (Cha), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Perform} (Cha), \skill{Sense Motive} (Wis), \skill{Survival} (Wis), and \skill{Tumble} (Dex).
}
{4}
{\PrestigeWarriorTable}{
1 & +1 & +0 & +2 & +0 & Jazst performance, jazst blades, taunt, skirmish +1d6 \\
2 & +2 & +0 & +3 & +0 & Principle of the razor \\
3 & +3 & +1 & +3 & +1 & Flexibility adjustment, skirmish +1d6/+1 \\
4 & +4 & +1 & +4 & +1 & Fast movement \\
5 & +5 & +1 & +4 & +1 & Skirmish +2d6/+1 \\
6 & +6 & +2 & +5 & +2 & Pounce, movement mastery \\
7 & +7 & +2 & +5 & +2 & Skirmish +2d6/+2 \\
8 & +8 & +2 & +6 & +2 & Flexibility adjustment \\
9 & +9 & +3 & +6 & +3 & Skirmish +3d6/+2 \\
10 & +10 & +3 & +7 & +3 & Dance of whirling blades \\
}
{
\textbf{Weapon and Armor Proficiency:} Jahzts gain no proficiency with any weapon or armor.

\textbf{Jazst Performance:} Once per day per class level, a jazst can use her dancing to improve her martial abilities. Each ability requires a minimum jazst level, and some require a minimum number of ranks in \skill{Perform} (dance) to qualify.

If a jazst has gladiator levels, she can add her gladiator levels to her jazst levels to determine the number of daily uses of her jazst performance and the number of targets of her taunt ability.

\textit{Taunt (Ex):} A jazst can taunt one opponent to fly into a rage. The opponent to be taunted must be within 9 meters, able to see and hear the jazst, and must have an Intelligence of 3 or higher. The jazst must also be able to see the creature. For every three levels a jazst attains beyond the 1st, she can target one additional creature with a single use of this ability.

A jazst makes a \skill{Perform} (dance) check. Her check result is the DC for each affected creature's Will save against the effect. If a creature's saving throw succeeds, the jazst cannot attempt to taunt that creature again for 24 hours. If its saving throw fails, the creature flies into a blind rage. While enraged, a target takes $-2$ penalty on attack rolls and AC. The rage lasts until either the jazst or her target become unconscious.

Taunt is a mind-affecting ability.

\textit{Principle of the Razor (Ex):} A jazst of 2nd or higher level with 10 or more ranks in \skill{Perform} (dance) can use her blades to deal deep cuts, that weaken her foes and are difficult to heal. If she hits an attack with skirmish, she can trade +1d6 damage from her skirmish damage to deal 1 point of Strength damage. Ability points lost to damage return on their own at the rate of 1 point per day for each damaged ability. She can only use this ability with slashing weapons.

\textit{Pounce (Ex):} A jazst of 6th or higher level with 14 or more ranks in \skill{Perform} (dance) can throw herself with pure savagery. As a swift action, she gains the pounce ability until the end of turn, allowing the jazst to make a full attack at the end of a charge.

\textit{Dance of Whirling Blades (Ex):} A jazst of 10th level with 18 or more ranks in \skill{Perform} (dance) can leap into the air, spinning toward her intended victim. If she cover at least 3 meters of horizontal distance with her jump, and she end her jump in a square from which she threatens her target, she can double the attacks she makes at the end of the charge. She takes an additional $-2$ penalty on AC for one round. Once she uses this ability, the jazst must spend one round recovering, if she plans to use it again in the same encounter.

\textbf{Jazst Blades (Ex):} A jahzt learns to improve their armor with long, slim, razor-like weapons they carry mounted on their legs and arms. These specialized weapons deal 1d10 slashing damage. They otherwise follow the same rules of armor spikes. 

\textbf{Skirmish (Ex):} A jazst relies on mobility to deal extra damage and improve her defense. She deals an extra 1d6 points of damage on all attacks she makes during any round in which she moves at least 3 meters. The extra damage applies only to attacks taken during the jazst's turn. This extra damage increases by 1d6 for every four levels gained above 1st (2d6 at 5th, 3d6 at 9th level).

The extra damage only applies against living creatures that have a discernible anatomy. Undead, constructs, oozes, plants, incorporeal creatures, and creatures immune to extra damage from critical hits are not vulnerable to this additional damage. The jazst must be able to see the target well eough to pick out a vital spot and must be able to reach such a spot. Earth defenders can apply this extra damage to ranged attacks made while skirmishing, but only if the target is within 9 meters.

At 3rd level, a jazst gains a +1 competence bonus to Armor Class during any round in which she moves at least 3 meters. The bonus applies as soon as the jazst has moved 3 meters, and lasts until the start of her next turn. This bonus improves by 1 for every four levels gained above 3rd (+2 at 7th level).

A jazst loses this ability when wearing medium or heavy armor or when carrying a medium or heavy load. If she gains the skirmish ability from another class, the bonuses stack.

\textbf{Flexibility Adjustment (Ex):} At 3rd level, a jazst can adjust her armor to improve her reflex capabilities. She increases the maximum Dexterity bonux and reduces the armor check penalty by 1 whenever she is wearing any armor she is proficient with. At 8th level, these improvements increase by 1. If she has flexibility adjustment from other sources (such as gladiator levels), these bonuses stack.

\textbf{Fast Movement (Ex):} At 4th level, jazst's land speed is faster than the norm for her race by +3 meters. This benefit applies only when she is wearing no armor, light armor, or medium armor and not carrying a heavy load. Apply this bonus before modifying the jazst's speed because of any load carried or armor worn. If a jazst gains fast movement from another class, such as barbarian, the bonuses stack.

\textbf{Movement Mastery (Ex):} At 6th level, a jazst is so certain of her movements that he is unaffected by adverse conditions. When making a \skill{Jump}, \skill{Perform} (dance), or \skill{Tumble} check, he may take 10 even if stress and distraction would normally prevent her from doing so.

}