\PrestigeClass{Loremaster}
{Oh my... `Rajaat'? Quite dangerous to ask around about this, you know? But let see my tables...}{Erkaar, elf loremaster}
{Loremasters are spellcasters who specialize on knowledge and secrets over material treasures. They enhance themselves by uncovering forgotten secrets in their studies. They usually are the guardians of ancient lore, working on a king's library, as a tribe's sage, or even as information brokers.}
{d4}
{a}
{Usually loremasters are wizards (preservers or defilers) that seek to better understand their magic, its consequences, and its connections with the history of Athas. Clerics find themselves meditating on the elements and their planes, and how to find balance between the arcane and the divine. Templars seek to understand their connection with the sorcerer-kings, and how psionics rules the society.}
{
\textbf{Skills:} \skill{Knowledge} (any two) 10 ranks in each.

\textbf{Feats:} Any three metamagic or item creation feats, plus \feat{Skill Focus} (\skill{Knowledge} [any individual \skill{Knowledge} skill]).

\textbf{Spells:} Able to cast seven different divination spells, one of which must be 3rd level or higher.
}
{
\skill{Appraise} (Int), \skill{Concentration} (Con), \skill{Craft} (alchemy) (Int), \skill{Decipher Script} (Int), \skill{Gather Information} (Cha), \skill{Handle Animal} (Cha), \skill{Heal} (Wis), \skill{Knowledge} (all skills taken individually) (Int), \skill{Perform} (Cha), \skill{Profession} (Wis), \skill{Speak Language} (None), \skill{Spellcraft} (Int), \skill{Use Magic Device} (Cha), and \skill{Use Psionic Device} (Cha).
}
{4}
{\PrestigeSpellTable}{
1 & +0 & +0 & +0 & +2 & Secret & +1 level of existing class\\
2 & +1 & +0 & +0 & +3 & Lore & +1 level of existing class\\
3 & +1 & +1 & +1 & +3 & Secret & +1 level of existing class\\
4 & +2 & +1 & +1 & +4 & Bonus language & +1 level of existing class\\
5 & +2 & +1 & +1 & +4 & Secret & +1 level of existing class\\
6 & +3 & +2 & +2 & +5 & Greater lore & +1 level of existing class\\
7 & +3 & +2 & +2 & +5 & Secret & +1 level of existing class\\
8 & +4 & +2 & +2 & +6 & Bonus language & +1 level of existing class\\
9 & +4 & +3 & +3 & +6 & Secret & +1 level of existing class\\
10 & +5 & +3 & +3 & +7 & True lore & +1 level of existing class\\
}
{
\textbf{Weapon and Armor Proficiency:} Loremasters gain no proficiency with any weapon or armor.

\textbf{Spellcasting:} When a new loremaster level is gained, the character gains new spells per day (and spells known, if applicable) as if she had also gained a level in a spellcasting class she belonged to before she added the prestige class. She does not, however, gain any other benefit a character of that class would have gained. This essentially means that she adds the level of loremaster to the level of some other spellcasting class the character has, then determines spells per day, spells known, and caster level accordingly.

\textbf{Secret:} At 1st level and every two levels higher than 1st (3rd, 5th, 7th, and 9th), the loremaster chooses one secret from the table below. Her loremaster level plus Intelligence modifier determines the secrets from which she can choose. She can't choose the same secret twice.

\Table{Loremaster Secrets}{y{.9cm} y{3cm} X}{
\tableheader Level + Int Modifier & \tableheader Secret & \tableheader Effect\\
1 & Instant mastery & 4 ranks of a skill in which the character has no ranks\\
2 & Secret health & +3 hit points\\
3 & Secrets of inner strength & +2 bonus on Will saves\\
4 & The lore of true stamina & +2 bonus on Fortitude saves\\
5 & Secret knowledge of avoidance & +2 bonus on Reflex saves\\
6 & Weapon trick & +1 bonus on attack rolls\\
7 & Dodge trick & +1 dodge bonus to AC\\
8 & Applicable knowledge & Any one feat\\
9 & Newfound arcana & 1 bonus 1st-level spell slot\\
10 & More newfound arcana & 1 bonus 2nd-level spell slot\\
}

\textbf{Lore:} At 2nd level, a loremaster gains the ability to know legends or information regarding various topics, just as a bard can with bardic knowledge. The loremaster adds her level and her Intelligence modifier to the lore check, which functions otherwise exactly like a bardic knowledge check.

\textbf{Bonus Languages:} A loremaster can choose any new language at 4th and 8th level.

\textbf{Greater Lore (Ex):} At 6th level, a loremaster gains the ability to understand magic items, as with the \spell{identify} spell.

\textbf{True Lore (Ex):} At 10th level, once per day a loremaster can use her knowledge to gain the effect of a \spell{legend lore} spell or an \spell{analyze dweomer} spell.
}
{}
{history}
{Loremasters are sages who uncover powerful secrets in their studies.}
{As sages, they remember important people and events as a bard does. But without all that singing and dancing.}
{They study to the point of gaining access to knowledge only possible through wizardry.}