\PrestigeClass{Master Scout}
{Stay away from the cacti... \textbf{STAY AWAY} from the cacti.}{Badu, caravan scout}
{Caravan masters, army commanders, raiding parties, adventuring groups, and anyone else traversing the hostile wilderness of Athas, all need the services of the master scout. Experienced wanderers and trackers who know every path and rock provide a safety and advantage valued by those who have come to know their services.}
{d8}
{a}
{Rangers are natural candidates for the master scout class, with their extensive knowledge of the wastes and its creatures. Barbarians also make good scouts due to their fast movement. Thri-kreen, elves and other races with inborn speed and endurance make excellent master scouts, though few can compare with the flight capabilities of aarakocra scouts. Halfling master scouts use their natural aptitude for stealth to compensate for their lack of overland speed. Master scouts are usually mercenaries for hire, many of whom cater to adventurers, or they are members of slave, elf or halfling tribes.}
{
\textbf{Skills:} \skill{Knowledge} (geography) 8 ranks, \skill{Knowledge} (nature) 8 ranks, \skill{Survival} 8 ranks.

\textbf{Feats:} \feat{Track}, \feat{Wastelander}.
}
{
\skill{Balance} (Dex), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Handle Animal} (Cha), \skill{Hide} (Dex), \skill{Jump} (Str), \skill{Knowledge} (nature) (Int), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Spot} (Wis), \skill{Survival} (Wis) and \skill{Use Rope} (Dex).
}
{8}
{\PrestigeWarriorTable}{
 1st & +0 & +2 & +2 & +0 & Blaze trail, flawless stride, hard march \\
 2nd & +1 & +3 & +3 & +0 & Skirmish (+1d6) \\
 3rd & +2 & +3 & +3 & +1 & Swift tracker, wasteland sense \\
 4th & +3 & +4 & +4 & +1 & Favored terrain, skirmish (+1d6/+1 AC) \\
 5th & +3 & +4 & +4 & +1 & Uncanny stealth (normal speed) \\
 6th & +4 & +5 & +5 & +2 & Skirmish (+2d6/+1 AC) \\
 7th & +5 & +5 & +5 & +2 & Running tracker \\
 8th & +6 & +6 & +6 & +2 & Skirmish (+2d6/+2 AC) \\
 9th & +6 & +6 & +6 & +3 & Favored terrain \\
10th & +7 & +7 & +7 & +3 & Skirmish (+3d6/+2 AC), uncanny stealth (running)\\
}
{
\textbf{Weapon and Armor proficiencies:} Master scouts are proficient in light armor and simple weapons.

\textbf{Blaze Trail (Ex):} The master scout is skilled at finding the best route through unfamiliar or obstructed areas and can guide others as well. Add 1.5 meter to the master scout's base speed. Up to one additional creature per master scout level can benefit from Blaze Trail. In Favored Terrains, the master scout may add an additional 1.5 meter to his own and his party's speed, due to familiarity with these terrains and areas.

% \Figure{t}{images/silhouette.png}

\textbf{Flawless Stride (Ex):} Starting at 6th level, a master scout can move through any sort of terrain that slows movement (such as undergrowth, rubble, and similar terrain) at his normal speed and without taking damage or suffering any other impairment.

This ability does not let him move more quickly through terrain that requires a \skill{Climb} or \skill{Swim} check to navigate, nor can he move more quickly through terrain or undergrowth that has been magically manipulated to impede motion.

A master scout loses this benefit when wearing medium or heavy armor or when carrying a medium or heavy load.

\textbf{Hard March (Ex):} Due to his knowledge and experience of travel, add the master scout's Wisdom modifier (if positive) to Fortitude saves for enduring a forced march. Up to one additional creature per master scout level can benefit from hard march.

\textbf{Skirmish (Ex):} Beginning at 2nd level, a master scout relies on mobility to deal extra damage and improve his defense. He deals an extra 1d6 points of damage on all attacks he makes during any round in which he moves at least 3 meters. The extra damage applies only to attacks taken during the master scout's turn. This extra damage increases by 1d6 for every four levels gained above 2nd (2d6 at 6th, 3d6 at 10th level).

The extra damage only applies against living creatures that have a discernible anatomy. Undead, constructs, oozes, plants, incorporeal creatures, and creatures immune to extra damage from critical hits are not vulnerable to this additional damage. The master scout must be able to see the target well enough to pick out a vital spot and must be able to reach such a spot. Master scouts can apply this extra damage to ranged attacks made while skirmishing, but only if the target is within 9 meters.

At 3rd level, a master scout gains a +1 competence bonus to Armor Class during any round in which he moves at least 3 meters. The bonus applies as soon as the master scout has moved 3 meters, and lasts until the start of his next turn. This bonus improves by 1 for every four levels gained above 4th (+2 at 8th level).

A master scout loses this ability when wearing medium or heavy armor or when carrying a medium or heavy load.

If he gains the skirmish ability from another source, the bonuses stack.

\PrestigeOnlySpellTable{The Mystic Theurge}{
 1st & +0 & +0 & +0 & +2 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 2nd & +1 & +0 & +0 & +3 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 3rd & +1 & +1 & +1 & +3 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 4th & +2 & +1 & +1 & +4 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 5th & +2 & +1 & +1 & +4 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 6th & +3 & +2 & +2 & +5 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 7th & +3 & +2 & +2 & +5 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 8th & +4 & +2 & +2 & +6 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 9th & +4 & +3 & +3 & +6 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
10th & +5 & +3 & +3 & +7 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
11th & +5 & +3 & +3 & +7 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
12th & +6 & +4 & +4 & +8 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
13th & +6 & +4 & +4 & +8 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
14th & +7 & +4 & +4 & +9 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
15th & +7 & +5 & +5 & +9 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
}

\textbf{Swift Tracker (Ex):} At 3rd level, a master scout can move at his normal speed while following tracks without taking the normal $-5$ penalty. He takes only a $-10$ penalty (instead of the normal $-20$) when moving at up to twice normal speed while tracking.

\textbf{Wasteland Sense (Ex):} Starting at 3rd level, a master scout can add his Constitution bonus (if any) as bonus on his Armor Class. This bonus does not apply to touch attacks. He also adds this bonus on Reflex saves made to avoid traps and natural hazards. He loses this bonus when he is wearing medium or heavy armor, when wearing tower shields, when immobilized or helpless, or when carrying a medium or heavy load.

\textbf{Uncanny Stealth:} Master scouts learn to move quickly yet quietly. At 5th level, he no longer suffers the $-5$ penalty on \skill{Hide} and \skill{Move Silently} checks while moving at normal speed.

At 10th level, a master scouts suffers only a $-10$ penalty on \skill{Hide} and \skill{Move Silently} checks while running or charging (instead of the normal $-20$ penalty).

\textbf{Favored Terrain:} At 4th and 8th level, a master scout gains a favored terrain, as per the ranger class feature. This benefit scales with previously chosen favored terrains.

\textbf{Running Tracker (Ex):} At 7th level, the master scout can use the \skill{Survival} skill to track while running or charging.

}
% {}
% {nature}
% {Master scouts take many names in each language, but all agree that they are instrumental for crossing the wastelands.}
% {Master scouts move very quickly even tracking or while being stealthy.}
% {Moving through the wastelands in small groups with master scouts may cut the time of travel by almost half when they are in their favorite terrain.}

% Members with connections with a merchant house should have little problem contacting master scouts through house agents (\skill{Gather Information} DC 10).
