\PrestigeClass{Mystic Theurge}
{All of this may seem like a desert to you, lifeless. But take a closer look. Each rock is a house. Each cavern is a city. Our very ground is a huge metropolis for all living things. This is why I preserve. This is what is worth preserving.}{Arlaam, halfing mystic theurge}
{Athas is a world changed deeply by the use of arcane magic. While most would rather stay in the arcane (or divine) path, mystic theurges try to draw power from the elements and from Athas itself. Their knowledge is not only theoretical, but pratical, as they master both types of spells simultaneously. A mystic theurge does not hinder its spell capabilities from any of their sources, being able to cast most of the spells in this book.}
{d4}
{a}
{Since mystic theurges can cast both arcane and divine spells, all of its members are multiclass spellcasters. Preservers multiclass with either cleric or druid in order to further their ability to protect Athas. While defilers multiclass with cleric or templar, so they can improve their firepower to corrupt all they can.}
{
\textbf{Skills:} \skill{Knowledge} (arcana) 6 ranks, \skill{Knowledge} (religion) 6 ranks.

\textbf{Spells:} Able to cast 2nd-level divine spells and 2nd-level arcane spells.
}
{
\skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Knowledge} (arcana) (Int), \skill{Knowledge} (religion) (Int), \skill{Profession} (Wis), \skill{Sense Motive} (Wis), and \skill{Spellcraft} (Int).
}
{2}
{\PrestigeOnlySpellTable}{
 1st & +0 & +0 & +0 & +2 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 2nd & +1 & +0 & +0 & +3 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 3rd & +1 & +1 & +1 & +3 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 4th & +2 & +1 & +1 & +4 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 5th & +2 & +1 & +1 & +4 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 6th & +3 & +2 & +2 & +5 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 7th & +3 & +2 & +2 & +5 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 8th & +4 & +2 & +2 & +6 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
 9th & +4 & +3 & +3 & +6 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
10th & +5 & +3 & +3 & +7 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
11th & +5 & +3 & +3 & +7 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
12th & +6 & +4 & +4 & +8 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
13th & +6 & +4 & +4 & +8 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
14th & +7 & +4 & +4 & +9 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
15th & +7 & +5 & +5 & +9 & +1 level of existing arcane spellcasting class/+1 level of existing divine spellcasting class\\
}
{
\textbf{Weapon and Armor Proficiency:} Mystic theurges gain no proficiency with any weapon or armor.

\textbf{Spellcasting:} When a new mystic theurge level is gained, the character gains new spells per day as if he had also gained a level in any one arcane spellcasting class he belonged to before he added the prestige class and any one divine spellcasting class he belonged to previously. He does not, however, gain any other benefit a character of that class would have gained. This essentially means that he adds the level of mystic theurge to the level of whatever other arcane spellcasting class and divine spellcasting class the character has, then determines spells per day and caster level accordingly. If a character had more than one arcane spellcasting class or more than one divine spellcasting class before he became a mystic theurge, he must decide to which class he adds each level of mystic theurge for the purpose of determining spells per day.
}
% {}
% {arcane or religion}
% {Mystic theurges are wizards who trained in divine arts.}
% {There are as many different mystic theurges as there are giant faces. You get them preservers, defilers, templars...}
% {While they seem as powerful as either wizards or clerics, they give up all other abilities so they can focus on just spellcasting.}