\PrestigeClass{Psiologist}
{The Way is hard for those without the Will to follow it to the end.}{Urmexca, Draji psiologist}
{Many are those who are trained in the use of the Way, but few dedicate themselves completely to its comprehension. The psiologist studies extensively in the psionic academies and schools to unlock a mastery over the Way that other never dream of. Intense contemplation on the uses of his powers and on the understanding of his Will are paramount to this end. He firmly believes that psionics is superior to magic, or any other physical training, if its user is knowledgeable enough in the Way and has the Will to back it up. The psiologist even considers himself superior to other, more mundane users of the Way.}
{d4}
{a}
{Only manifesters who have given a priority to their psionic development are likely to be drawn to becoming psiologists. Thus, almost all psiologists come from the ranks of psions.}
{
\textbf{Alignment:} Any lawful.

\textbf{Skills:} \skill{Knowledge} (psionics) 8 ranks, \skill{Psicraft} 8 ranks.

\textbf{Feats:} \feat{Psionic Meditation}, any two metapsionic feats.

\textbf{Special:} Manifester level 5th.

\textbf{Special:} Must be a member of a psionic school.
}
{
\skill{Autohypnosis} (Wis), \skill{Concentration} (Con), \skill{Heal} (Wis), \skill{Knowledge} (all skills, taken individually) (Int), \skill{Performance} (Cha), \skill{Psicraft} (Int), and \skill{Use Psionic Device} (Cha).
}
{2}
{\PrestigePowerTable}{
 1st & +0 & +0 & +0 & +2 & Bonus feat, greater Will     & +1 level of existing manifesting class\\
 2nd & +1 & +0 & +0 & +3 & Improved science, mettle     & +1 level of existing manifesting class\\
 3rd & +1 & +1 & +1 & +3 & Improved meditation          & +1 level of existing manifesting class\\
 4th & +2 & +1 & +1 & +4 & Improved science             & +1 level of existing manifesting class\\
 5th & +2 & +1 & +1 & +4 & Bonus feat, mental mastery   & +1 level of existing manifesting class\\
 6th & +3 & +2 & +2 & +5 & Improved science             & +1 level of existing manifesting class\\
 7th & +3 & +2 & +2 & +5 & Metascience manipulation     & +1 level of existing manifesting class\\
 8th & +4 & +2 & +2 & +6 & Improved science             & +1 level of existing manifesting class\\
 9th & +4 & +3 & +3 & +6 & Metascience thesis           & +1 level of existing manifesting class\\
10th & +5 & +3 & +3 & +7 & Bonus feat, improved science & +1 level of existing manifesting class\\
}
{
\textbf{Weapon and Armor Proficiency:} Psiologists gain no proficiency with any weapon or armor.

\textbf{Manifesting:} At every level a psiologist gains additional power points per day and access to new powers as if he had also gained a level in whatever manifesting class he belonged to before he added the prestige class. He does not, however, gain any other benefit a character of that class would have gained (bonus feats, metapsionic or item creation feats, psicrystal special abilities, and so on). This essentially means that he adds the level of psiologist to the level of whatever manifesting class the character has, then determines power points per day, powers known, and manifester level accordingly.

If a character had more than one manifesting class before he became a psiologist, he must decide to which class he adds the new level of psiologist for the purpose of determining power points per day, powers known, and manifester level.


\textbf{Bonus Feats:} A psiologist gains a bonus feat at 1st level, 5th level, and 10th level. This feat must be a psionic feat, a metapsionic feat, or a psionic item creation feat.

\textbf{Greater Will (Su):} A psiologist grows stronger in the Will than other characters. Each psiologist level gives him 2 extra power points.

\textbf{Improved Science (Su):} At 2nd level and every two levels thereafter, a psiologist chooses one known psionic power to improve. He adds +1 bonus to power checks related to this psionic power. He may select the same power multiple times.

\textbf{Mettle (Su):} At 2nd level, a psiologist gains the ability to resist magical compulsions and other unusual attacks with uncommon willpower and stamina. If she makes a successful Fortitude or Will save against an attack that would normally have a lesser effect with a successful save (such as a spell with a saving throw entry of ``Will half'' or ``Fortitude partial''), the effect is instead completely negated. This ability only works as long as she is conscious, however.

\textbf{Improved Meditation (Su):} At 3rd level, a psiologist can gain psionic focus with a swift action (see \skill{Concentration} skill).

\textbf{Mental Mastery (Ex):} At 5th level, a psiologist has reached inner knowledge to focus on what matters. When making a \skill{Autohypnosis}, \skill{Concentration}, or \skill{Psicraft} check, she may take 10 even if stress or distraction would normally prevent her from doing so.

\textbf{Metascience Manipulation (Su):} At 7th level, a psiologist may replace the metapsionic power point cost by an increase in the power check DC. For every 5 extra power points, the power check DC increases by 1. A psiologist can only apply this manipulation to a psionic power selected as improved science.

\textbf{Metascience Thesis (Su):} At 9th level, a psiologist reduces the metapsionic power point cost. Any psionic power selected as improved science can have a power point reduction to metapsionic cost equal to 5 $\times$ bonus added by improved science. This is applied before metascience manipulation. For example, a 9th-level psiologist who selected \psionic{death field} three times wants to manifest a \psionicref{death field}{quickened death field}. She reduces the original \feat{Quicken Power} additional cost of 30 power points to 15. She manipulates the remaining cost, so the power check DC increases from 28 to 31 with no additional power point cost.

\textbf{Code of Conduct:} A psiologist must not use armor. He may use one magical weapon, one wondrous item, and two rings. Psiologists believe in the superiority of psionics over any physical or magical discipline.

\subsubsection{Ex-Psiologist}
A psiologist who uses armor, or exceeds his limit of magical items loses all class features and may not progress in levels as a psiologist.
}
