\PrestigeClass{Arena Champion}
{You fought like the Dragon.}{Jarek, half-elf arena champion}
{Arena champions are gladiatorial combatants who aspire to greatness in their blood sports. They dream of performing in arenas filled with thousands of frenzied spectators. Risking their lives for fame, wealth and adoration, arena champions are the heroes to commoners of all ages. Many hail from local neighborhoods or nearby communities.}
{d12}
{an}
{Gladiators make up the majority of arena champions, since their abilities already so closely mimic those of the prestige class. Most of the rest are fighters, along with the occasional psychic warrior or barbarian with a knack for flare and extravagance.}
{
\textbf{Base Attack Bonus:} +7.

\textbf{Skills:} \skill{Perform} (arena fighting) 10 ranks.

\textbf{Feats:} \feat{Endurance}, \feat{Extra Performance}, \feat{Weapon Focus}, \feat{Weapon Specialization}.
}
{\skill{Balance} (Dex), \skill{Bluff} (Cha), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Perform} (Cha), \skill{Sense Motive} (Wis), and \skill{Tumble} (Dex).
}
{4}
{\PrestigeWarriorTable}{
1 & +1 & +2 & +0 & +0 & Gladiatorial performance, \feat{Leadership}, improviser\\
2 & +2 & +3 & +0 & +0 & Crowd support +1 (10), reputation +1\\
3 & +3 & +3 & +1 & +1 & Armor optimization, \feat{Greater Weapon Focus}\\
4 & +4 & +4 & +1 & +1 & Signature move +2 \\
5 & +5 & +4 & +1 & +1 & Crowd support +2 (50), reputation +2\\
6 & +6 & +5 & +2 & +2 & Second wind\\
7 & +7 & +5 & +2 & +2 & Signature move +4 \\
8 & +8 & +6 & +2 & +2 & Armor optimization, crowd support +3 (100), reputation +3\\
9 & +9 & +6 & +3 & +3 & Roar of the crowd \\
10 & +10 & +7 & +3 & +3 & Legend, finishing move \\
}
{
\textbf{Weapon and Armor Proficiency:} Arena champions gain no proficiency with any weapon or armor.

\textbf{Gladiatorial Performance:} Gladiator levels stack with arena champion levels for the purpose of determining which gladiatorial performance abilities an arena champion has access to.

\textbf{Leadership:} An arena champion gains the \feat{Leadership} feat as a bonus feat.

\textbf{Improviser (Ex):} An arena champion's improvised weapon deals as much damage as his unarmed strike plus an extra 1d4 points. When an arena champion rolls a natural 1 on an attack roll while using an improvised weapon, that weapon breaks apart and becomes useless.

\textbf{Crowd Support (Ex):} At 2nd level, an arena champion enjoys a +1 morale bonus to attack and damage rolls whenever there are ten or more non-combatant spectators present. 

At 5th level, this bonus can increase by 1 (+2 total), if amount of spectators is at least fifty.

At 8th level, this bonus can increase by 2 (+3 total), but the minimum amount of spectators must be one hundred for the bonus to take effect.

\textbf{Reputation:} At 2nd level, an arena champion receives a +1 circumstance bonus to non-combat uses of the \skill{Bluff}, \skill{Diplomacy}, \skill{Gather Information} and \skill{Intimidate} skills. These benefits do not apply when dealing with the devoted fans of rival gladiators. The arena champion also gets a +1 bonus to his \feat{Leadership} score.

These bonuses increase to +2 at 5th level, and to +3 at 8th level.

\textbf{Armor Optimization (Ex):} At 3rd level, an arena champion gains an understanding of how his armor can better serve him. He increases the armor bonus to AC and reduces the armor check penalty by 1 whenever he is wearing any armor he is proficient with. At 8th level, these improvements increase by 1. If he has armor optimization from other sources (such as gladiator levels), these bonuses stack.

\textbf{Greater Weapon Focus:} At 3rd level, an arena champion gains the \feat{Greater Weapon Focus} feat with a chosen weapon. The weapon must be one for which he already has selected the \feat{Weapon Focus} and \feat{Weapon Specialization} feats.

\textbf{Signature Move (Ex):} Arena champions develop a signature move at 4th level. The exact technical nature of the move is up to the individual arena champion to develop, and it grants one of the following benefits:
\begin{itemize*}
\item +2 competence bonus on opposed rolls for disarm attempts.
\item +2 competence bonus on opposed rolls for trip attempts.
\item +2 competence bonus on damage rolls for sunder attempts.
\item +2 competence bonus on opposed Bluff and Sense Motive checks in combat.
\item +2 dodge bonus to AC when using total defense, or +1 dodge bonus to AC when fighting defensively.
\end{itemize*}

At 7th level, the benefit associated with the arena champion's chosen signature move is doubled. For example, a +2 competence bonus on opposed rolls for disarm attempts increases to +4. Alternatively, he may select a second signature move instead, to expand his repertoire.

\textbf{Second Wind (Ex):} At 6th level, an arena champion can dig his resolve and endurance to find an extra burst of vitality. He can use a standard action to heal a number of hit points equal to his Constitution modifier $\times$ his arena champion levels. He can use this ability only once per encounter.

\textbf{Roar of the Crowd (Ex):} At 8th level, an arena champion can use the cheering of the crowd to his advantage. In any round when he successfully deals damage to an opponent, he gains a +1 morale bonus on the next attack roll he makes in the same round.

\textbf{Legend:} At 10th level, an arena champion becomes a legend known to all. Treat general NPC initial attitudes as one category better. This benefit does not extend to the devoted fans of rival gladiators.

\textbf{Finishing Move (Ex):} At 10th level, if an attack reduces an opponent below 0 hit points, an arena champion can attempt a coup de grace as a free action.
}