\PrestigeClass{Dune Trader}
{Don't trust anything with pointy ears. It will either cheat you or try to eat you.}{Marek, human trader}
{Wagons pulled by mekillots and kanks travel along dusty roads, carrying slaves, weapons, food and other goods between the city-states and the villages of the wastes. Caravans of all sizes trek across the Tablelands and beyond, owned by powerful Merchant Houses. Trade ensures the survival of many small villages and is vital to the economy of the city-states of the sorcerer-kings. Dune traders are agents for the merchant houses. Some even aspire to become invited family members of the ancient merchant dynasties.}
{d6}
{a}
{Because of the requirements for entry, the dune trader can appeal to a wide range of characters. Rogues, bards, rangers, and other skill-focused characters are the most likely to enter the prestige class, but the entry requirements are well within the reach of intelligent members of any class.}
{
\textbf{Skills:} \skill{Appraise} 5 ranks, \skill{Bluff} 5 ranks, \skill{Diplomacy} 7 ranks, \skill{Profession} (merchant) 3 ranks, \skill{Sense Motive} 5 ranks.

\textbf{Feats:} \feat{Trader}.

\textbf{Special:} Must be accepted into a merchant house.
}
{
\skill{Appraise} (Int), \skill{Bluff} (Cha), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Diplomacy} (Cha), \skill{Disguise} (Cha), \skill{Forgery} (Int), \skill{Gather Information} (Cha), \skill{Hide} (Dex), \skill{Intimidate} (Cha), \skill{Listen} (Wis), \skill{Literacy} (N/A), \skill{Move Silently} (Dex), \skill{Open Lock} (Dex), \skill{Profession} (Wis), \skill{Ride} (Dex), \skill{Search} (Int), \skill{Sense Motive} (Wis), \skill{Sleight of Hand} (Dex), \skill{Speak Language} (N/A), \skill{Spot} (Wis), and \skill{Survival} (Wis).
}
{8}
{\PrestigeWarriorTable}{
1  & +0 & +0 & +0 & +2 & Smooth talk, poison use\\
2  & +1 & +0 & +0 & +3 & Contact (1), open arms\\
3  & +2 & +1 & +1 & +3 & Agent +2, master linguist\\
4  & +3 & +1 & +1 & +4 & Contact (2), dazzle\\
5  & +3 & +1 & +1 & +4 & Fast talk, \feat{Leadership}\\
6  & +4 & +2 & +2 & +5 & Contact (3), skill mastery\\
7  & +5 & +2 & +2 & +5 & Agent +4, slippery mind\\
8  & +6 & +2 & +2 & +6 & Contact (4), taunt\\
9  & +6 & +3 & +3 & +6 & Allies\\
10 & +7 & +3 & +3 & +7 & Contact (5), force of personality\\
}
{
\textbf{Weapon and Armor Proficiency:} Dune traders gain no proficiency with any weapon or armor.

\textbf{Smooth Talk (Ex):} A dune trader can retry \skill{Bluff} and \skill{Diplomacy} checks at a $-5$ penalty, but only once per check.

\textbf{Poison Use:} Dune traders are trained in the use of poison and never risk accidentally poisoning themselves when applying poison to a blade.

\textbf{Open Arms:} Beginning at 2nd level, a dune trader becomes skilled at initiating peaceful (and not so peaceful) negotiations. The dune trader adds a competence bonus equal to one-half of his dune trader level (rounded down) on all \skill{Diplomacy} checks.

\textbf{Contact:} At 2nd level and every even-numbered level thereafter, a dune trader gains the trust of a non-player character he can rely on when the time comes. A dune trader can ask for a favor once per week per contact. Contacts come in three varieties, one of which he must choose: influence contacts, skill contacts, and trade contacts (see \hyperref[sec:contacts]{Contacts}).

\textbf{Agent (Ex):} At 3rd level, a dune trader becomes an agent of his merchant house. Agents of the major houses listed below gain a +2 circumstance bonus to a skill embedded in the merchant house's culture and organization. Agents of other, smaller houses gain a +1 circumstance bonus to a skill of their choice.

\textit{House Inika:} \skill{Gather Information}.

\textit{House M'ke:} \skill{Sense Motive}.

\textit{House Shom:} \skill{Bluff}.

\textit{House Stel:} \skill{Knowledge} (warcraft).

\textit{House Tsalaxa:} \skill{Intimidate}.

\textit{House Vordon:} \skill{Appraise}.

\textit{House Wavir:} \skill{Diplomacy}.

\textit{Other Houses:} Skill of choice.

At 7th level, major house bonus increase to +4, and small house bonus incresce to +2.

\textbf{Master Linguist (Ex):} At 3rd level, a dune trader becomes a master linguist. Whenever he encounters a new language, either spoken or written, that he does not know, he can make an Intelligence check (for a spoken language) or a \skill{Decipher Script} check (for a written language) to determine if he can understand it.

The DC for the check is DC 15 if the language is commonly spoken, or DC 25 if the language is ancient or unique. Success means he can glean enough meaning from a conversation or document to ascertain the basic message, but this ability in no way simulates actually being able to converse or fluently read and write in a given language. A single check covers roughly one minute of a spoken language or one page of a written language.

\textbf{Dazzle (Ex):} At 4th level, a dune trader gains the ability to dazzle a creature through sheer force of personality, a winning smile, and fast-talking. The creature to be fascinated must be within 27 meters, able to see, hear and understand the dune trader, and able to pay attention to him. The dune trader must also be able to see the creature. The distraction of nearby combat or other dangers prevents the ability from working.

As a move action, the dune trader makes an opposed \skill{Bluff} check. If he succeeds on the check, the creature receives a $-1$ penalty on attack rolls, ability checks, skill checks, and saving throws for a number of rounds equal to his dune trader level.

At 7th and 10th level, a dune trader can target one additional creature with a single use of this ability.

This is a mind-affecting, language-dependent ability.

\textbf{Fast Talk (Ex):} Beginning at 5th level, a dune trader may make a rushed \skill{Diplomacy} check as a full-round action with a $-5$ penalty instead of the normal $-10$ penalty.

\textbf{Leadership:} At 5th level, a dune trader gains the \feat{Leadership} feat as a bonus feat.

\textbf{Skill Mastery:} At 6th level, the dune trader becomes so certain in the use of certain skills that he can use them reliably even under adverse conditions. Upon gaining this ability, he selects a number of skills equal to 3 + his Intelligence modifier. When making a skill check with one of these skills, he may take 10 even if stress and distractions would normally prevent him from doing so.

\textbf{Slippery Mind (Ex):} If a 7th level dune trader is affected by an enchantment spell or effect and fails his saving throw, he can attempt it again 1 round later at the same DC. He gets only this one extra chance to succeed on her saving throw.

\textbf{Taunt (Ex):} At 8th level, a dune trader gains the ability to temporarily rattle a creature through the use of insults and goading. As a move action, he may taunt a target able to see, hear and understand him, with an Intelligence score of 3 or higher. The opponent resists the taunt by making a Will saving throw (DC 10 + his dune trader level + his Cha modifier). If the save fails, he is the only creature it can make melee attacks against for 1 round.

This is a mind-affecting, language-dependent ability.

\textbf{Allies:} Beginning at 9th level, a dune trader gains the favor of an organization, tribe, planar creature or a powerful individual---in the most extreme case, a sorcerer-king. The frequency and extent of favors a trader may call upon will vary (for example, spending the night under the protected tents of an Elven tribe is a small favor, while asking for a caravan raid in which several tribe members will perish is a large favor). The DM determines how often the trader can call upon his allies for aid without losing their favor. The maximum monetary value of the favor cannot exceed 1,000 cp.

\textbf{Force of Personality (Su):} Starting at 10th level, a dune trader can channel his mental strength for physical needs. He adds his Intelligence bonus (if any) to his initiative checks and Reflex saves, and his Charisma bonus (if any) to his Concentration checks and Fortitude saves.
}