\PrestigeClass{War Mind}
{Through physical training alone, you may become a fantastic soldier, but nothing more. Through history lessons, you may become a superb sage, but nothing more. Through physical training and history lessons is that we may become masters in the art of war. }{Erthan, dwarf war mind}
{War minds are expert fighters who claim to possess unequaled knowledge in the art of war. Through inner contemplation and martial studies, war minds grow their craft of arms and war.}
{d10}
{a}
{Wild talents who begin their careers as fighters or barbarians are the most likely to pick this prestige class. Even psions may take some training in any warrior class for the express purpose of eventually being able to study as a war mind.}
{
\textbf{Alignment:} Any nonchaotic.

\textbf{Base Attack Bonus:} +3.

\textbf{Skills:} \skill{Knowledge} (history) 2 ranks, \skill{Knowledge} (psionics) 8 ranks.

\textbf{Psionics:} Must have a power point reserve of at least 1 power point.

\textbf{Special:} Must have had some instruction by another war mind, or belong to the House of the Mind.
}
{\skill{Autohypnosis} (Wis), \skill{Concentration} (Con), \skill{Intimidate} (Cha), \skill{Knowledge} (history) (Int), \skill{Knowledge} (psionics) (Int), and \skill{Psicraft} (Int).}
{2}
{\PsychicTable}{
 1st &  +1 & +2 & +2 & +0 & Chain of personal superiority +2 & 10 &  2 & 1 \\
 2nd &  +2 & +3 & +3 & +0 & Chain of defensive posture +2    & 15 &  3 & 2 \\
 3rd &  +3 & +3 & +3 & +1 & Damage Reduction 1/--            & 20 &  4 & 2 \\
 4th &  +4 & +4 & +4 & +1 &                                  & 25 &  5 & 2 \\
 5th &  +5 & +4 & +4 & +1 & Sweeping strike                  & 30 &  6 & 3 \\
 6th &  +6 & +5 & +5 & +2 & Damage Reduction 2/--            & 35 &  7 & 3 \\
 7th &  +7 & +5 & +5 & +2 & Chain of personal superiority +4 & 40 &  8 & 3 \\
 8th &  +8 & +6 & +6 & +2 & Chain of defensive posture +4    & 45 &  9 & 4 \\
 9th &  +9 & +6 & +6 & +3 & Damage Reduction 3/--            & 50 & 10 & 4 \\
10th & +10 & +7 & +7 & +3 & Chain of overwhelming force      & 55 & 11 & 4 \\
}
{
\textbf{Weapon and Armor Proficiency:} War minds gain no proficiency with any weapon or armor.

\textbf{Power Points per Day:} A war mind can manifest powers. His ability to manifest powers is limited by the power points he has available. His base daily allotment of power points is given on \tabref{The War Mind}. In addition, he receives bonus power points per day if he has a high ability score. A war mind gain bonus power points with Constitution, Intelligence, and Wisdom. His race may also provide bonus power points per day, as may certain feats and items. If a war mind has power points from a different class, those points are pooled together and usable to manifest powers from either class. Bonus power points from having a high ability score can be gained only for the character's highest psionic class.

\textbf{Discipline:} Every war mind must decide at 1st level which psionic discipline he will specialize in. Choosing a discipline provides a war mind with access to the powers restricted to that discipline. However, choosing a discipline also means that the war mind cannot learn powers that are restricted to other disciplines. He can't even use such powers by employing psionic items.

Beginning at 2nd level and every three levels thereafter, the war mind gains access to a new discipline and may learn powers of this new discipline.

\textbf{Powers Known:} A war mind begins play knowing two powers of his choice. Each time he achieves a new level, he unlocks the knowledge of a new power.

Choose the powers known from the list of powers of your chosen discipline. You cannot choose powers from discipline lists other than your own discipline list. You must fulfill the power prerequisites (if any) to learn a power---these are powers that you must know before learning that power. The number of times a war mind can manifest powers in a day is limited only by his daily power points.

A war mind simply knows his powers; they are ingrained in his mind. He does not need to prepare them (in the way that some spellcasters prepare their spells), though he must get a good night's sleep each day to regain all his spent power points. To learn or manifest a power, a war mind must have a key ability score of at least 10 + the power's level. The key ability depends on the discipline of the power.

The Difficulty Class for saving throws against war mind powers is 10 + the power's level + the war mind's key ability modifier. The key ability depends on the discipline of the power being manifested.

\textbf{Chain of Personal Superiority (Ex):} At 1st level, a war mind learns the first principle of warfare for the individual combatant: the ability to both deal punishment and take it. Calling upon inner reserves of knowledge and dedication, a war mind can provide himself with a +2 insight bonus to Strength and Constitution for up to 1 minute. A war mind can use this power three times per day. Activating this power is a free action. At 7th level, the insight bonus to Strength and Constitution improves to +4.

\textbf{Chain of Defensive Posture (Ex):} At 2nd level, a war mind learns the second principle of warfare for the individual combatant: the ability to avoid the enemy's counterattacks if that enemy is not immediately overwhelmed. Calling upon inner reserves of knowledge and dedication, a war mind can provide himself with a +2 insight bonus to Armor Class for up to 1 minute. A war mind can use this power three times per day. Activating this power is a free action. At 8th level, the insight bonus to Armor Class improves to +4.

\textbf{Damage Reduction (Ex):} At 3rd level, a war mind learns the third principle of warfare for the individual combatant: to unleash in oneself the spirit of the enduring body. The spirit of the ideal body transforms a war mind, granting him damage reduction 1/--. At 6th level, his damage reduction improves to 2/--. At 9th level, his damage reduction improves to 3/--.

\textbf{Sweeping Strike (Ex):} At 5th level, a war mind gains the ability to make great, sweeping swings with a melee weapon. On each melee attack a war mind makes, he can choose squares he threatens that are adjacent to each other, and his attacks apply to creatures in those two squares equally. A war mind can use this ability on any attack, even an attack of opportunity or a cleave attempt.

A war mind cannot use this ability if he has moved more than 3 meters since the end of his last turn. If a war mind drops one or both of his foes with a sweeping strike, he can attempt a cleave normally; however, he makes only one cleave attempt per sweeping strike, even if he drops more than one foe.

\textbf{Chain of Overwhelming Force (Su):} At 10th level, a war mind learns the fourth principle of warfare for the individual combatant: to discover the underlying violence of the world and deliver it in a perfectly executed attack.

The war mind taps into this underlying energy and apply it to a single attack, dealing an extra 10d6 points of damage. A war mind can use this power once per day. Activating this power is a free action. If the attack misses, the power is wasted.
}
