\PrestigeClass{Poisonmaster}
{That wasn't tea... and that wasn't cinnamon. Oh, dear.}{Salima, elven poisonmaster}
{All experienced bards know how to apply poisons to a blade and spike a drink, but some go on to study poisons in depth, seeking out ancient recipes and secrets of poison lore. Some pursue poisons with a passion, others for more sinister reasons. Whether it is the thrill of trying out a new poison on a new victim, or inhaling the fumes of the boiling brew, these bards more often than not develop some form of peculiarities as their experimenting with poisons over time deteriorate their nerves and minds.}
{d6}
{a}
{Bards make up the majority of poisonmasters, with multiclass rangers and rogues forming the bulk of the rest. These three classes rely most often on poisons. Sometimes a multiclassed assassin expands his deadly repertoire by manipulating poisons to more potent effects.}
{
\textbf{Skills:} \skill{Craft} (poisonmaking) 8 ranks, \skill{Craft} (alchemy) 4 ranks, \skill{Heal} 4 ranks.

\textbf{Feats:} \feat{Skill Focus} (\skill{Craft} [poisonmaking]).

\textbf{Special:} Must be trained in the use of poison.
}
{
\skill{Appraise} (Int), \skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Diplomacy} (Cha), \skill{Disguise} (Cha), \skill{Gather Information} (Cha), \skill{Heal} (Wis), \skill{Hide} (Dex), \skill{Intimidate} (Cha), \skill{Knowledge} (nature) (Int), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Perform} (Cha), \skill{Profession} (Wis), \skill{Sense Motive} (Wis), \skill{Sleight of Hand} (Dex), and \skill{Spot} (Wis).
}
{6}
{\PrestigeWarriorTable}{
1 & +0 & +2 & +2 & +2 & Dosage, identify poison \\
2 & +1 & +3 & +3 & +3 & Poison secret \\
3 & +2 & +3 & +3 & +3 & Extend poison \\
4 & +3 & +4 & +4 & +4 & Poison secret, mental resistance \\
5 & +3 & +4 & +4 & +4 & Damage reduction 3/--, empower poison \\
6 & +4 & +5 & +5 & +5 & Poison secret, poison mastery \\
7 & +5 & +5 & +5 & +5 & Poisoner's fortitude, maximize poison \\
8 & +6 & +6 & +6 & +6 & Poison secret, \emph{mind blank} \\
9 & +6 & +6 & +6 & +6 & Quicken poison \\
10 & +7 & +7 & +7 & +7 & Damage reduction 6/--, poison secret, tough body \\
}
{
\textbf{Weapon and Armor Proficiency:} Poisonmasters gain proficiency with all simple weapons, light armor, but no shields.

\textbf{Dosage (Ex):} Poisonmasters know the exact amount of poison needed for an application, making sure no excessive poison is used. Each dose of poison created by a poisonmaster can be applied twice.

\textbf{Identify Poison (Ex):} Poisonmasters can safely identify any poison through an appropriate method (smell, taste, alchemical test) without risking harm.

\textbf{Poison Secret (Ex):} At 2nd level and every two levels thereafter, a poisonmaster can select one of the following bardic secrets: poisondealer, scorpion's touch, smokestick application, poisonbane, poison resistance. Some of these secrets may be selected more than once. See the bard class for details.

\textbf{Extend Poison (Ex):} Beginning at 3rd level, a poisonmaster can alter the onset time of any poison they manufacture by up to one hour. This can be applied to either or both primary and secondary damage. This increases the poison's base price by 25\%.

\textbf{Mental Resistance (Su):} At 4th level, a poisonmaster has advantage on saves made against telepathic powers and enchantment (charm) spells.

\textbf{Damage Reduction (Ex):} Beginning at 5th level, a poisonmaster's nervous system suffers from their experimentations with poisons, making you slightly resistant to physical attacks. Subtract 3 points from the damage the poisonmaster takes each time he is dealt damage. At 10th level, this damage reduction rises to 6/--. Damage reduction can reduce damage to 0 but not below 0.

\textbf{Empower Poison (Ex):} Beginning at 5th level, a poisonmaster can alter the strength of any poison with numeric variables they manufacture. All variable, numeric effects of an empowered poison are increased by one-half. This can be applied to either or both primary and secondary damage. Empower poison increases a poison's base price by 50\%.

\textbf{Poison Mastery (Ex):} Starting at 6th level, a poisonmaster may take 20 when crafing poisons without any risk of ruining raw materials.

\textbf{Poisoner's Fortitude (Ex):} At 7th level, a poisonmaster gets a +4 bonus to Fortitude saves from physiological changes due to poison, but suffers mental side effects, reducing their Wisdom by 2.

\textbf{Maximize Poison (Ex):} Beginning at 7th level, a poisonmaster can maximize the strength of any poison with numeric variables they manufacture. For example, a poison that inflicts 2d6 Str damage inflicts 12 points of Str damage. Maximize poison increases a poison's base price by 75\%.

\textit{Mind Blank (Sp):} At 8th level, a poisonmaster's mind becomes completely sealed against involuntary intrusion as per the \spell{mind blank} spell. This ability is always considered active and supersedes mental resistance.

\textbf{Quicken Poison (Ex):} Beginning at 9th level, a poisonmaster can reduce the time between a poison's initial and secondary damage from 1 minute to 1 round. Quicken poison increases a poison's base price by 100\%.

\textbf{Tough Body (Ex):} At 10th level, a poisonmaster becomes immune to all nonmagical diseases and poisons.
}