\PrestigeClass{Psiologist}
{The Way is hard for those without the Will to follow it to the end.}{Urmexca, Draji psiologist}
{Many are those who are trained in the use of the Way, but few dedicate themselves completely to its comprehension. The psiologist studies extensively in the psionic academies and schools to unlock a mastery over the Way that other never dream of. By learning from the various existing traditions of the Way, he can benefit from the wisdom of hundreds of great masters. Intense contemplation on the uses of his powers and on the understanding of his Will are paramount to this end. He firmly believes that psionics is superior to magic, or any other physical training, if its user is knowledgeable enough in the Way and has the Will to back it up. The psiologist even considers himself superior to other, more mundane users of the Way.}
{d4}
{a}
{Only manifesters who have given a priority to their psionic development are likely to be drawn to becoming psiologists. Thus, almost all psiologists come from the ranks of psions or psionicists (NPC psionic class), and a few wilders who trained in the academies after developing their powers on their own. Psychic warriors and soulknives rarely have the intellectual focus required to become psiologists.}
{
\textbf{Alignment:} Any lawful.

\textbf{Skills:} \skill{Knowledge} (psionics) 12 ranks, \skill{Psicraft} 12 ranks.

\textbf{Feats:} \feat{Psionic Affinity}, \feat{Skill Focus} (\skill{Knowledge} [psionics]), \feat{Skill Focus} (\skill{Psicraft}), any two metapsionic feats.

\textbf{Psionics:} Able to manifest 5th-level powers.

\textbf{Special:} Must have trained in at least three different psionic academies or schools and must still be a member in good standing in one of them.
}
{
\skill{Autohypnosis} (Wis), \skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Diplomacy} (Cha), \skill{Knowledge} (all skills, taken individually) (Int), \skill{Psicraft} (Int), \skill{Sense Motive} (Wis), and \skill{Use Psionic Device} (Cha).
}
{2}
{\PrestigePowerTable}{
 1st & +0 & +0 & +0 & +2 & Psiologism                & +1 level of existing manifesting class\\
 2nd & +1 & +0 & +0 & +3 & Psionic acumen +1         & +1 level of existing manifesting class\\
 3rd & +1 & +1 & +1 & +3 & Psionic rationalization 1 & +1 level of existing manifesting class\\
 4th & +2 & +1 & +1 & +4 & Forethought 1/day         & +1 level of existing manifesting class\\
 5th & +2 & +1 & +1 & +4 & Psionic acumen +2         & +1 level of existing manifesting class\\
 6th & +3 & +2 & +2 & +5 & Forethought 2/day         & +1 level of existing manifesting class\\
 7th & +3 & +2 & +2 & +5 & Psionic rationalization 2 & +1 level of existing manifesting class\\
 8th & +4 & +2 & +2 & +6 & Discipline insight        & +1 level of existing manifesting class\\
 9th & +4 & +3 & +3 & +6 & Psionic acumen +3         & +1 level of existing manifesting class\\
10th & +5 & +3 & +3 & +7 & Schoolmaster              & +1 level of existing manifesting class\\
}
{
\textbf{Weapon and Armor Proficiency:} Psiologists gain no proficiency with any weapon or armor.

\textbf{Manifesting:} At every level a psiologist gains additional power points per day and access to new powers as if he had also gained a level in whatever manifesting class he belonged to before he added the prestige class. He does not, however, gain any other benefit a character of that class would have gained (bonus feats, metapsionic or item creation feats, psicrystal special abilities, and so on). This essentially means that he adds the level of psiologist to the level of whatever manifesting class the character has, then determines power points per day, powers known, and manifester level accordingly.

If a character had more than one manifesting class before he became a psiologist, he must decide to which class he adds the new level of psiologist for the purpose of determining power points per day, powers known, and manifester level.

\textbf{Psiologism (Ex):} The time you spend learning and discovering the intricacies of the Way provides you with an ever-growing knowledge and mastery of the things of the mind. You gain a competence bonus equal to one-half your psiologist level on all \skill{Concentration}, \skill{Knowledge} (psionics) and \skill{Psicraft} checks.

\textbf{Psionic Acumen (Su):} At 2nd level, you develop ways to strengthen your powers farther than other users of the Way. You can now augment any power you know for a total of 1 power point more than your manifester level. At 5th and 9th level, you add an additional power point to the limit of power points you can spend for augmenting powers you know. This benefit cannot be used while you are wild surging, since it is by controlling consciously your use of the Will that you achieve this result.

\textbf{Psionic Rationalization (Su):} At 3rd level, your understanding of the Way shows itself as you can enhance your powers while making less use of your Will. When using a metapsionic feat, you reduce the increased power point cost by 1. At 7th level, you can reduce the cost by an additional point. The cost cannot be reduced below its original cost by the use of this ability.

\textbf{Forethought (Su):} Upon achieving 4th level, your control of the Way becomes such that you can manifest a power as if you were using the \feat{Quicken Power} feat once per day. Later at 6th level, you may use this ability twice per day, instead.

\textbf{Discipline Insight (Su):} At 8th level, you master a single discipline that you choose. Your knowledge and understanding of this chosen discipline is so great that you can, once per day, manifest a power from that discipline as if you had two additional manifester levels. This benefit cannot be used while you are wild surging, since it is by controlling consciously your use of the Will that you achieve this result. If you are already a psion, then you must choose your chosen psion discipline when using this ability.

\textbf{Schoolmaster (Su):} At 10th level, you are able to manifest powers from your chosen discipline for the maximum effect possible. Once per day, you can manifest a power from that discipline that is both empowered and maximized, without any extra power point cost. The chosen discipline for the schoolmaster ability must be the same one as was chosen for discipline insight.
}