\PrestigeClass{Restorationist}
{Athas is a blasted wasteland scarred by ancient wars and the defiling magic of the sorcerer-kings. But before the wars, before the sorcerer-kings, Athas was a verdant paradise. There has to be a way to restore Athas to her former splendor, and I intend to find it.}{Diadinatius, half-elf restorationist}
{Restorationists are preservers whose main goal is to return Athas to its former state of verdant vegetation and plentiful water. Wholly subsumed to their task, restorationists often tutor others in ecologically sound land management. A restorationist seldom takes lives unnecessarily, eats meat only when fruit and other plants that can return something to the land are unavailable, and searches for magic in her travels that can revitalize Athas.}
{d4}
{a}
{Restorationists are preserver wizards of any race. Multi-classed druid/wizards who become restorationists are perhaps the most knowledgeable when it comes to nurturing the land. Multi-classed ranger/wizards are particularly adept at surviving in the wilderness during long travels.}
{
\textbf{Alignment:} Any nonevil.

\textbf{Skills:} \skill{Knowledge} (nature) 8 ranks, \skill{Profession} (herbalist) 4 ranks, \skill{Spellcraft} 8 ranks.

\textbf{Spells:} Able to cast 3rd-level arcane spells.

\textbf{Special:} Must be a preserver.
}
{\skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Diplomacy} (Cha),  \skill{Disguise} (Cha), \skill{Knowledge} (all skills taken individually) (Int), \skill{Literacy} (N/A), \skill{Profession} (Wis), \skill{Speak Language} (N/A), \skill{Spellcraft} (Int), and \skill{Survival} (Wis).}
{4}
{\PrestigeSpellTable}{
1st & +0 & +0 & +0 & +2 & Careful casting, \emph{speak with plants} & +1 level of existing arcane spellcasting class \\
2nd & +1 & +0 & +0 & +3 & \feat{Brew Potion}, gentle & +1 level of existing arcane spellcasting class \\
3rd & +1 & +1 & +1 & +3 & Plant domain & +1 level of existing arcane spellcasting class \\
4th & +2 & +1 & +1 & +4 & Brew greater potion & +1 level of existing arcane spellcasting class \\
5th & +2 & +1 & +1 & +4 & Timeless body & +1 level of existing arcane spellcasting class \\
}
{
\textbf{Weapon and Armor Proficiencies:} Restorationists gain no proficiency with any weapon or armor.

\textbf{Careful Casting:} A restorationist always takes extra time when tapping into a plant's life energy and carefully replace the life-force after extracting the small amount of energy he needs. At 1st level, a restorationist increases the casting time of each spell following \tabref{Careful Casting}. Spells that take 1 immediate action to cast are unaffected.

\Table{Careful Casting}{XX}{
\tableheader Original Casting Time & \tableheader New Casting Time\\
1 swift action & 1 move action \\
1 standard action & 1 full round \\
1 full round or longer & Double the time \\
}

This allows the restorationist to extract the arcane energy from the environment with more care. He treats terrain as one step better (see \chapref{Magic}).

\textit{Speak with Plants} \textbf{(Sp):} At will, a restorationist can use \spell{speak with plants} as the spell.

\textbf{Brew Potion:} At 2nd level, a restorationist gains \feat{Brew Potion} as a bonus feat.

\textbf{Gentle (Ex):} Beginning at 2nd level, a restorationist may add his class level in his \skill{Diplomacy} checks. These wizards are not hated and reviled like others because they are the most careful not to let anyone know that they are spellcasters. Nobles and commoners alike come to them for advice on growing more abundant crops, and they are respected for their knowledge.

\textbf{Plant Domain:} At 3rd level, a restorationist gains access to the Plant domain. They gain its granted power---Rebuke or command plant creatures as an evil cleric rebukes or commands undead. He can use this ability a total number of times per day equal to 3 + your Charisma modifier.

In order to learn a spell from the Plant domain, a restorationist must find or purchase a scroll of that spell and pay the usual price to scribe the spell into their spellbook. 

When preparing spells, they can select one spell slot per spell level---and only one slot per spell level---to memorize a Plant domain spell. A restorationist can never prepare more than one domain spell of each level.

\textbf{Brew Greater Potion (Ex):} At 4th level, a restorationist can brew potions of spells 5th-level or lower.

\textbf{Timeless Body (Ex):} At 5th level, the restorationist no longer suffers ability penalties for aging and cannot be magically aged. Any penalties she may have already suffered remain in place. Bonuses still accrue, and the restorationist eventually dies of old age.

\subsubsection{Ex-Restorationists}
A restorationist who pulls energy from any one group of plants or area (approximately 3-meter square) more than once per day, defiles, or willfully allows damage to happen to plants loses all class features and may not progress in levels as restorationist. He regain his abilities if he atones (see \spell{atonement} spell).
}