\PrestigeClass{Sensei}
{Physical perfection is useless without mental perfection.}{Talanoa, Nibenese sensei}
{The most powerful characters on Athas combine the study of psionics with the study of another discipline. Dragons study sorcery in conjunction with the Way, while elemental clerics harness the power of their minds to the power of their worship. The sensei combines an intensive physical training program with the Way, seeking to become the perfect weapon.

Sensei are very rare in the Tyr region, since their art is extraordinarily demanding. Few people are even aware that they exist. Each sensei charts his own course in life; there is no organization or school that binds them together.}
{d8}
{a}
{The few known sensei are usually humans, half-elves, elves and muls, since they are usually the only races with both the physical and mental requisites. Sensei from other races are unknown in the Tyr Region. Some may be assassins, others gladiators, and others wandering champions who fight against injustice.}
{
\textbf{Base Attack Bonus:} +3.

\textbf{Skills:} \skill{Autohypnosis} 5 ranks, \skill{Concentration} 8 ranks, \skill{Knowledge} (psionics) 6 ranks, \skill{Jump} 5 ranks, \skill{Tumble} 4 ranks.

\textbf{Feats:} \feat{Endurance}, \feat{Improved Unarmed Strike}, \feat{Psionic Meditation}, \feat{Weapon Focus}.

\textbf{Special:} Manifester level 3rd.
}
{
\skill{Autohypnosis} (Wis), \skill{Balance} (Dex), \skill{Concentration} (Con), \skill{Diplomacy} (Cha), \skill{Heal} (Wis), \skill{Jump} (Str), \skill{Knowledge} (psionics) (Int), \skill{Perform} (Cha), \skill{Psicraft} (Int), \skill{Sense Motive} (Wis), \skill{Swim} (Str), and \skill{Tumble} (Dex).
}
{4}
{\PrestigeMonkTable}{
 1 &  +1 & +2 & +2 & +2 & +1 & 1d6  & Bonus feat, unarmed strike       & \\
 2 &  +2 & +3 & +3 & +3 & +1 & 1d6  & Mettle, versatile focus          & +1 level of existing manifesting class\\
 3 &  +3 & +3 & +3 & +3 & +1 & 1d8  & Disciplined mind, purity of body & +1 level of existing manifesting class\\
 4 &  +4 & +4 & +4 & +4 & +2 & 1d8  & Improved meditation              & +1 level of existing manifesting class\\
 5 &  +5 & +4 & +4 & +4 & +2 & 1d8  & Bonus feat, mental mastery       & \\
 6 &  +6 & +5 & +5 & +5 & +2 & 1d10 & Disciplined mind                 & +1 level of existing manifesting class\\
 7 &  +7 & +5 & +5 & +5 & +2 & 1d10 & Diamond body                     & +1 level of existing manifesting class\\
 8 &  +8 & +6 & +6 & +6 & +3 & 1d10 & Improved mettle                  & +1 level of existing manifesting class\\
 9 &  +9 & +6 & +6 & +6 & +3 & 2d6  & Bonus feat, disciplined mind     & \\
10 & +10 & +7 & +7 & +7 & +3 & 2d6  & Diamond soul                     & +1 level of existing manifesting class\\
11 & +11 & +7 & +7 & +7 & +3 & 2d6  & Timeless body                    & +1 level of existing manifesting class\\
12 & +12 & +8 & +8 & +8 & +4 & 2d8  & Disciplined mind, perfect self   & +1 level of existing manifesting class\\
}
{
\textbf{Weapon and Armor Proficiency:} Sensei are proficient with all simple weapons, gythka, and chatkcha. Sensei gain no proficiency with any armor.

\textbf{Manifesting:} When a new sensei level is gained---except 1st and every four levels thereafter (5th and 9th)---the character gains additional power points per day and access to new powers as if she had also gained a level in whatever manifesting class she belonged to before she added the prestige class. She does not, however, gain any other benefit a character of that class would have gained (bonus feats, metapsionic or item creation feats, psicrystal special abilities, and so on). This essentially means that she adds the level of sensei to the level of whatever manifesting class the character has, then determines power points per day, powers known, and manifester level accordingly.

If a character had more than one manifesting class before she became a sensei, she must decide to which class she adds the new level of sensei for the purpose of determining power points per day, powers known, and manifester level.

\textbf{AC Bonus:} When unarmored and unencumbered, the sensei adds her Wisdom bonus (if any) to her AC. In addition, a sensei gains a +1 bonus to AC. This bonus increases by 1 for every four sensei levels (+2 at 4th, +3 at 8th, and +4 at 12th level).

These bonuses to AC apply even against touch attacks or when the sensei is flat-footed. She loses these bonuses when she is immobilized or helpless, when she wears any armor, when she carries a shield, or when she carries a medium or heavy load.

\textbf{Unarmed Strike:} A sensei's attacks may be with either fist interchangeably or even from elbows, knees, and feet. This means that a sensei may even make unarmed strikes with her hands full. There is no such thing as an off-hand attack for a sensei striking unarmed. A sensei may thus apply her full Strength bonus on damage rolls for all her unarmed strikes.

Usually a sensei's unarmed strikes deal lethal damage, but she can choose to deal nonlethal damage instead with no penalty on her attack roll. She has the same choice to deal lethal or nonlethal damage while grappling.

A sensei's unarmed strike is treated both as a manufactured weapon and a natural weapon for the purpose of powers, spells, and effects that enhance or improve either manufactured weapons or natural weapons.

A sensei also deals more damage with her unarmed strikes than a normal person would, as shown on \tabref{The Sensei}. The unarmed damage on \tabref{The Sensei} is for Medium monks. A Small sensei deals less damage than the amount given there with her unarmed attacks, while a Large sensei deals more damage; see \tabref{Small or Large Sensei Unarmed Damage}.

\Table{Small or Large Sensei Unarmed Damage}{lCC}{
& \multicolumn{2}{c}{Unarmed Damage}\\
\cmidrule[0.5pt]{2-3}
\tableheader Level & \tableheader Small & \tableheader Large \\
1st--2nd & 1d4 & 1d8 \\
3rd--5th & 1d6 & 2d6 \\
6th--8th & 1d8 & 2d8 \\
9th--11th & 1d10 & 3d6 \\
12th & 2d6 & 3d8 \\
}

\textbf{Bonus Feat:} At 1st level and every four levels thereafter (5th and 9th), a sensei gets a bonus feat. This feat must be a psionic feat or a psionic item creation feat. She must still meet the prerequisites for the feat.

\textbf{Mettle (Su):} At 2nd level, a sensei gains the ability to resist magical compulsions and other unusual attacks with uncommon willpower and stamina. If she makes a successful Fortitude or Will save against an attack that would normally have a lesser effect with a successful save (such as a spell with a saving throw entry of ``Will half'' or ``Fortitude partial''), the effect is instead completely negated. This ability only works as long as she is conscious, however.

\textbf{Versatile Focus (Ex):} At 2nd level, a sensei gains the benefit of \feat{Weapon Focus} for any weapon she is proficient with.

\textbf{Disciplined Mind (Ex):} At 3rd level, a sensei chooses a discipline between Psychometabolism and Psychokinesis. She learns a new power from her chosen discipline at 3rd level and every three levels thereafter (6th, 9th and 12th). This new power must be of a level the sensei can manifest.

\textbf{Purity of Body (Ex):} At 3rd level, a sensei gains immunity to all diseases except for supernatural and magical diseases.

\textbf{Improved Meditation (Su):} At 4th level, a sensei can gain psionic focus with a swift action (see \skill{Concentration} skill).

\textbf{Mental Mastery (Ex):} At 5th level, a sensei has reached inner knowledge to focus on what matters. When making a \skill{Autohypnosis}, \skill{Concentration}, or \skill{Psicraft} check, she may take 10 even if stress or distraction would normally prevent her from doing so.

\textbf{Diamond Body (Su):} At 7th level, a sensei gains immunity to poisons of all kinds.

\textbf{Improved Mettle (Su):} This ability, gained at 8th level, works like mettle. If she makes a successful Fortitude or Will save against an attack that would normally have a lesser effect with a successful save, the effect is instead completely negated. What's more, she takes only the lesser effect even if she fails her saving throw.

\textbf{Diamond Soul (Ex):} At 10th level, a sensei gains power resistance equal to 10 + her sensei level + her Wisdom bonus.

\textbf{Timeless Body (Ex):} Upon attaining 11th level, a sensei no longer takes penalties to her ability scores for aging and cannot be magically aged. Any such penalties that she has already taken, however, remain in place. Bonuses still accrue, and the sensei still dies of old age when her time is up.

\textbf{Perfect Self:} At 12th level, a sensei becomes a psionic creature. Her type changes to outsider. Additionally, the sensei gains damage reduction 10/magic. Unlike other outsiders, the sensei can still be brought back from the dead as if she were a member of her previous creature type.

\textbf{Code of Conduct:} A sensei must not use armor or any magical device to improve her Armor Class. She must not use magical weapons, either. Sensei belive on their own abilities and disdain the use of such crutches in the practice of their art.

\subsubsection{Ex-Sensei}
A sensei who uses a magical weapon or who uses any armor or magical device to improve her AC loses all class features and powers and may not progress in levels as a sensei. %She regains her abilities if she atones for her violations (see \spell{atonement} spell).

A sensei faces a special restriction in multiclassing. A sensei who gains a level in a class other than sensei may never again raise her sensei level, though she retains all her sensei abilities.
}