\PrestigeClass{Shadow Wizard}
{Why do you fear the darkness? You do not fear the light.}{Carrakachan, half-elf shadow wizard}
{Shadow wizards are arcane spellcasters who have tapped into a different source of spell energy: The Black. Sometimes referred to as Black Wizards, these mages have been around for centuries, but never in great numbers. Shadow wizards often appear cold and distant, wrapped in cloaks that conceal their true appearances. The more the shadow wizard uses his source of power, the darkness of the Black taints him, spreading across his body. Their alien appearances often turn shadow wizards into mysterious loners.}
{d4}
{a}
{The majority of shadow wizards are human, but a number of shadow wizards are half-elves. These outcasts often lead solitary lives, allowing them to practice their art unnoticed. The claustrophobic nature of the Black is unappealing to aarakocra. Shadow wizards usually avoid the Veiled Alliance and templar factions, fearing their reactions. Occasionally, two shadow wizards can be found together, one as mentor and the other as apprentice.}
{
\textbf{Alignment:} Any neutral.

\textbf{Skills:} \skill{Knowledge} (arcana) 8 ranks, \skill{Knowledge} (the planes) 8 ranks.

\textbf{Spells:} Ability to cast 3rd-level arcane spells; ability to cast at least one light spell of 1st-level or higher.
}
{
\skill{Autohypnosis} (Wis), \skill{Craft} (Int), \skill{Knowledge} (arcane) (Int), \skill{Knowledge} (the planes) (Int), \skill{Literacy} (N/A), \skill{Profession} (Wis), \skill{Spellcraft} (Int), and \skill{Survival} (Wis).
}
{2}
{\PrestigeSpellTable}{
 1st & +0 & +2 & +0 & +2 & \emph{Inflict wounds} (light), shadow casting           & +1 level of existing arcane spellcasting class\\
 2nd & +1 & +3 & +0 & +3 & Speak with shadows, shadow taint $-1$                   & +1 level of existing arcane spellcasting class\\
 3rd & +1 & +3 & +1 & +3 & \emph{Inflict wounds} (moderate)                        & +1 level of existing arcane spellcasting class\\
 4th & +2 & +4 & +1 & +4 & Fortification 25\%, shadow taint $-2$                   & +1 level of existing arcane spellcasting class\\
 5th & +2 & +4 & +1 & +4 & \emph{Inflict wounds} (serious)                         & +1 level of existing arcane spellcasting class\\
 6th & +3 & +5 & +2 & +5 & Negative energy resistance, \hskip2cm shadow taint $-3$ & +1 level of existing arcane spellcasting class\\
 7th & +3 & +5 & +2 & +5 & \emph{Inflict wounds} (critical)                        & +1 level of existing arcane spellcasting class\\
 8th & +4 & +6 & +2 & +6 & Shadow taint $-4$                                       & +1 level of existing arcane spellcasting class\\
 9th & +4 & +6 & +3 & +6 & Fortification 50\%                                      & +1 level of existing arcane spellcasting class\\
10th & +5 & +7 & +3 & +7 & Shadow apotheosis                                       & +1 level of existing arcane spellcasting class\\
}
{
\textbf{Weapon and Armor Proficiency:} Shadow wizards gain no proficiency with any weapon or armor.

\textbf{Spellcasting:} When a new shadow wizard level is gained, the character gains new spells per day as if he had also gained a level in whatever arcane spellcasting class in which they could cast 3rd-level spells before they added the prestige class. They do not, however, gain any other benefit a character of that class would have gained. This essentially means that he adds the level of shadow wizard to the level of whatever other arcane spellcasting class he has, and then determines spells per day and caster level accordingly. If he had more than one arcane spellcasting class before he became a shadow wizard, he must decide to which class he adds each level of shadow wizard for the purpose of determining spells per day.

\textit{Inflict Wounds} \textbf{(Sp):} The Black taints the shadow wizard. For every level gained, 5\% of his body becomes enveloped in shadow, starting with one of his hands. The hand functions as normal, but is cold to the touch and appears jet black. At 1st level, shadow wizard can use \spell{inflict light wounds} as the spell. He may use this ability a number of times per day equal to his class level.

At every two levels beyond the 1st, the ability to channel negative energy becomes stronger. At 3rd level, he uses \spell{inflict moderate wounds}, instead. At 5th level, he uses \spell{inflict serious wounds}, instead. At 7th level, he uses \spell{inflict critical wounds}, instead.

\textbf{Shadow Casting:} A shadow wizard gets his arcane powers from the Black, not from the usual plant life that most wizards use. This connection is unstable, and a shadow wizard must roll every encounter to determine the strength of his connection. Roll a d10 to see the modifier on his caster level and his spells' DC.

\Table{}{CXC}{
\tableheader d10 & \tableheader Connection Strength & \tableheader Modifier\\
1 & Minimal & $-2$\\
2--4 & Poor & $-1$\\
5--7 & Normal & +0\\
8--9 & Good & +1\\
10 & Superb & +2\\
}

If there are no shadows within 3 meters from the shadow wizard, such as in total darkness, he is cut off from the Black. He must use the normal methods, but he treats the terrain as one step worse (see \chapref{Magic}). The shadow wizard also must make a DC 15 Fortitude save or take 1d4 damage of negative energy from the temperature shock.

\textbf{Speak with Shadows (Ex):} At 2nd level, a shadow wizard gains the ability to speak and understand shadows. They may not heed him, but they will understand him and he them.

\textbf{Shadow Taint (Ex):} Beginning at 2nd level, a shadow wizard becomes increasingly more bizarre and the air becomes strangely cold around him. When his shadow tain is concealed, he takes a $-1$ penalty in \skill{Bluff}, \skill{Diplomacy}, \skill{Disguise}, and \skill{Gather Information}. This penalty increases every two levels thereafter, up to $-4$ at 8th level.

Living creatures with an Intelligence score of 3 or higher who see the shadow taint for the first time must make a Will save DC 10 + shadow wizard class level, or become panicked for 1d4 rounds. Black-touched creatures and creatures from the Black are immune to this effect.

\textbf{Fortification:} Starting at 4th level, a shadow wizard gains 25\% resistance to critical hits and sneak attacks; this is equivalent to the light fortification armor special ability. At 9th level, this fortification increases to 50\%.

\textbf{Negative Energy Resistance:} At 6th level, a shadow wizard gains +4 bonus on saving throws made to resist negative energy effects, including energy drain, some ability drain, and \emph{inflict} spells.

\textbf{Shadow Apotheosis (Ex):} At 10th level, a shadow wizard becomes perfectly atunned with the Black. The shadow wizard's type changes to outsider. Additionally, he gains immunity to negative energy. Unlike other outsiders, a shadow wizard can be raised and resurrected.

}