\PrestigeClass{Wanderer}
{Villagers, gather around! Listen to my watery tales and fill your bottles! I've traveled far and wide, and bring news of freedom!}{Aajik, water cleric}
{Wanderers are clerics that travel from settlement to settlement to preach, share prophecies, heal the wounded, and teach. They bring the news from distant lands to the nomads and small towns throughout Athas. They are usually loners that need to learn how to survive on their own.}
{d6}
{a}
{Wanderers are the most common type of cleric in Athas. Earth wanderers help tend the crops and teach agricultural techniques. Air wanderers are the most common type, since their element focus on freedom. They reveal future success of crops or the fate of the village. Fire clerics slay incoming raiders and lurking creatures. Water clerics replenish water supplies and heal more serious wounds and diseases.

Paraelemental wanderers are seeking places to grow their patron element, or spreading their element's word in a village that is near their path.}
{
\textbf{Alignment:} Any chaotic.

\textbf{Skills:} \skill{Knowledge} (religion) 6 ranks, \skill{Survival} 3 ranks.

\textbf{Spells:} Able to cast 2nd-level divine spells.

\textbf{Special:} Must have an element or paraelement as patron.
}
{\skill{Autohypnosis} (Wis), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Diplomacy} (Cha), \skill{Gather Information} (Cha), \skill{Heal} (Wis), \skill{Knowledge} (geography) (Int), \skill{Knowledge} (nature) (Int), \skill{Knowledge} (religion) (Int), \skill{Profession} (Wis), \skill{Ride} (Dex), \skill{Spellcraft} (Int), \skill{Spot} (Wis), and \skill{Survival} (Wis).
}
{4}
{\PrestigeSpellTable}{
1st & +0 & +0 & +0 & +2 & Turn/rebuke undead, lore & +1 level of existing divine spellcasting class\\
2nd & +1 & +0 & +0 & +3 &                          & +1 level of existing divine spellcasting class \\
3rd & +2 & +1 & +1 & +3 & Travel domain            & +1 level of existing divine spellcasting class\\
}
{
\textbf{Spellcasting:} When a new wanderer level is gained, the character gains new spells per day (and spells known, if applicable) as if they had also gained a level in whatever divine spellcasting class they belonged to before they added the prestige class. They do not, however, gain any other benefit a character of that class would have gained (favored enemy, wild shape ability, and so on). This essentially means that they add the level of wanderer to the level of whatever other divine spellcasting class the character has, then determine spells per day and spells known.

If a character had more than one divine spellcasting class in which they would cast 2nd-level divine spells before they became a wanderer, the player must decide which class to ssign each level of wanderer for the purpose of determining spells per day.

\textbf{Turn/rebuke undead:} A wanderer adds their wanderer class levels to his cleric levels for all purposes related to turning or rebuking undead.

\textbf{Lore:} A wanderer may ancient lore, just like a bard can with bardic knowledge. The wanderer adds their wanderer level, cleric level, and their Wisdom modifier to the lore check, which functions otherwise exactly like a bardic knowledge check.

If the wanderer has a lore check from another class, instead they can boost the check. They can expend one daily turn or rebuke attempt to add their wanderer level and Wisdom modifier to the lore check.

\textbf{Travel Domain:} At 3rd level, a wanderer gains access to the Travel domain. They gain the granted power associated with the domain, and can choose the spells in that domain as their daily domain spells.

\textbf{Code of Conduct:} A wanderer must never spend more than three days in the same place, unless there is a dire danger that only his presence can prevent.

\subsubsection{Ex-Wanderers}
A wanderer who ceases to be chaotic or who settles in a single place loses all class features and may not progress in levels as a wanderer. They regain their abilities if they atone for their violation (see the \spell{atonement} spell).
}
% {}
% {local or religion}
% {Wanderers are travelers that help tiny communities in the harsh desert.}
% {Loners that can help lost travelers and little villages in need, with news from outside. Their call is to always travel.}
% {Each wanderer is a different from the next. All of them help villages, but some only if the village helps them in their current quest. Paraelemental wanderers are always looking for a next spot to grow their element, while elemental wanderers spread the message of preservation.}