\PrestigeClass{War Mind}
{Through physical training alone, you may become a fantastic soldier, but nothing more. Through history lessons, you may become a superb sage, but nothing more. Through physical training and history lessons is that we may become masters in the art of war. }{Erthan, dwarf war mind}
{War minds are expert fighters who claim to possess unequaled knowledge in the art of war. Through inner contemplation and martial studies, war minds grow their craft of arms and war.}
{d10}
{a}
{Psychic warriors are most likely to take this prestige class, but even those who begin their careers as fighters or barbarians may pick some training in a psionic class for the express purpose of eventually being able to study as a war mind.}
{
\textbf{Alignment:} Any nonchaotic.

\textbf{Base Attack Bonus:} +3.

\textbf{Skills:} \skill{Knowledge} (history) 2 ranks, \skill{Knowledge} (psionics) 8 ranks.

\textbf{Psionics:} Must have a power point reserve of at least 1 power point.

\textbf{Special:} Must have had some instruction by another war mind.
}
{\skill{Autohypnosis} (Wis), \skill{Concentration} (Con), \skill{Intimidate} (Cha), \skill{Knowledge} (history) (Int), \skill{Knowledge} (psionics) (Int), and \skill{Psicraft} (Int).}
{2}
{\PsychicTable}{
 1 &  +1 & +2 & +2 & +0 & Chain of personal superiority +2 &  2 & 1 & 1st\\
 2 &  +2 & +3 & +3 & +0 & Chain of defensive posture +2    &  5 & 2 & 1st\\
 3 &  +3 & +3 & +3 & +1 & Enduring body (DR 1/--)          &  9 & 2 & 1st\\
 4 &  +4 & +4 & +4 & +1 &                                  & 14 & 3 & 2nd\\
 5 &  +5 & +4 & +4 & +1 & Sweeping strike                  & 20 & 3 & 2nd\\
 6 &  +6 & +5 & +5 & +2 & Enduring body (DR 2/--)          & 28 & 4 & 3rd\\
 7 &  +7 & +5 & +5 & +2 & Chain of personal superiority +4 & 37 & 4 & 3rd\\
 8 &  +8 & +6 & +6 & +2 & Chain of defensive posture +4    & 47 & 5 & 4th\\
 9 &  +9 & +6 & +6 & +3 & Enduring body (DR 3/--)          & 58 & 5 & 4th\\
10 & +10 & +7 & +7 & +3 & Chain of overwhelming force      & 70 & 6 & 5th\\
11 & +11 & +7 & +7 & +3 &                                  & 84 & 6 & 5th\\
12 & +12 & +8 & +8 & +4 & Enduring body (DR 4/--)          & 99 & 7 & 6th\\
}
{
\textbf{Weapon and Armor Proficiency:} War minds gain no proficiency with any weapon or armor.

\textbf{Power Points/Day:} A war mind can manifest powers. His ability to manifest powers is limited by the power points he has available. His base daily allotment of power points is given on \tabref{The War Mind}. In addition, he receives bonus power points per day if he has a high Wisdom score. His race may also provide bonus power points per day, as may certain feats and items. If a war mind has power points from a different class, those points are pooled together and usable to manifest powers from either class. Bonus power points from having a high ability score can be gained only for the character's highest psionic class.

\textbf{Powers Known:} A war mind chooses his powers from the psychic warrior power list. At 1st level, a war mind knows one psychic warrior power of your choice. At every even-numbered level higher than 1st, he learns one new power. A war mind can manifest any power that has a power point cost equal to or lower than his manifester level. The total number of powers a war mind can manifest per day is limited only by his daily power points.

A war mind simply knows his powers; they are ingrained in his mind. He does not need to prepare them (in the way that some spellcasters prepare their spells), though he must get a good night's sleep each day to regain all his spent power points.

The Difficulty Class for saving throws against war mind powers is 10 + the power's level + the war mind's Wisdom modifier.

\textbf{Maximum Power Level Known:} A war mind gains the ability to learn one 1st-level power when he takes his first level in the prestige class. As he attains each even-numbered level beyond 2nd, a war mind gains the ability to master more complex powers.

To learn or manifest a power, a war mind must have a Wisdom score of at least 10 + the power's level.

\textbf{Chain of Personal Superiority (Ex):} At 1st level, a war mind learns the first principle of warfare for the individual combatant: the ability to both deal punishment and take it. Calling upon inner reserves of knowledge and dedication, a war mind can provide himself with a +2 insight bonus to Strength and Constitution for up to 1 minute. A war mind can use this power three times per day. Activating this power is a free action. At 7th level, the insight bonus to Strength and Constitution improves to +4.

\textbf{Chain of Defensive Posture (Ex):} At 2nd level, a war mind learns the second principle of warfare for the individual combatant: the ability to avoid the enemy's counterattacks if that enemy is not immediately overwhelmed. Calling upon inner reserves of knowledge and dedication, a war mind can provide himself with a +2 insight bonus to Armor Class for up to 1 minute. A war mind can use this power three times per day. Activating this power is a free action. At 8th level, the insight bonus to Armor Class improves to +4.

\textbf{Enduring Body (Ex):} At 3rd level, a war mind learns the third principle of warfare for the individual combatant: to unleash in oneself the spirit of the enduring body. The spirit of the ideal body transforms a war mind, granting him damage reduction 1/--. At 6th level, his damage reduction improves to 2/--. At 9th level, his damage reduction improves to 3/--.

\textbf{Sweeping Strike (Ex):} At 5th level, a war mind gains the ability to make great, sweeping swings with a melee weapon. On each melee attack a war mind makes, he can choose squares he threatens that are adjacent to each other, and his attacks apply to creatures in those two squares equally. A war mind can use this ability on any attack, even an attack of opportunity or a cleave attempt.

A war mind cannot use this ability if he has moved more than 3 meters since the end of his last turn. If a war mind drops one or both of his foes with a sweeping strike, he can attempt a cleave normally; however, he makes only one cleave attempt per sweeping strike, even if he drops more than one foe.

\textbf{Chain of Overwhelming Force (Su):} At 10th level, a war mind learns the fourth principle of warfare for the individual combatant: to discover the underlying violence of the world and deliver it in a perfectly executed attack.

The war mind taps into this underlying energy and apply it to a single attack, dealing an extra 10d6 points of damage. A war mind can use this power once per day. Activating this power is a free action. If the attack misses, the power is wasted.
}