\subsection{Power Centers}
Any settlement has a number of figures or groups who hold power and influence over it. The bigger a settlement gets, more power centers dispute influence over it. Villages may have only a single leader, while city-states have their sorcerer-monarchs, merchant houses, nobles, and bureaucrats.

\Table{Number of Power Centers}{lClC}{
  \tableheader Town Size
& \tableheader Power Centers
& \tableheader Town Size
& \tableheader Power Centers \\
Small tribe & 1 & Small city  & 4 \\
Large tribe & 1 & Large city  & 5 \\
Village     & 1 & Metropolis  & 6 \\
Small town  & 2 & Megalopolis & 7 \\
Large town  & 3 & & \\
}

\subsubsection{Power Center Type}
Each power center is defined by its type, and a single settlement can have any number of power centers of the same type. Two power centers of the same type just represent different groups.

\Table{Power Center Type}{cXcX}{
  \tableheader d\%
& \tableheader Power Center Type
& \tableheader d\%
& \tableheader Power Center Type \\
01--12  & Aristocratic  &  % nobility
45--56  & Plutocratic   \\ % merchants
13--20  & Bureaucratic  &  % offices
57--68  & Psiocratic    \\ % psions
21--28  & Democratic    &  % elected
69--80  & Stratocratic  \\ % military
29--35  & Gerontocratic &  % older folk
81--92  & Theocratic    \\ % clerics
36--44  & Mageocratic   &  % wizards
93--100 & Monstrous     \\
}

\textbf{Aristocratic:} A group of nobles holds influence over the settlement, with their hereditary titles and powerful connections.

\textbf{Bureaucratic:} A group of government offices hold power through intricate rules. The most common example of this is the Templarate.

\textbf{Democratic:} Elected officials influence the whole community, even if they were elected by a few. It can be an elected mayor, or a legislative position as Balic's Chamber of Patricians.

\textbf{Gerontocratic:} A group of older people holds power. It can be a council of elders deemed wiser than the rest, or a group of old nobles who gathered most influence over time.

\textbf{Mageocratic:} A group of wizards (either defilers or preservers) holds influence because of their arcane capabilities. It can be a single wizard leading a village, or royal defilers, or the Veiled Alliance.

\textbf{Plutocratic:} A group of wealthy people hold power because of their money. The most common example of this in Athas is Dynastic Merchant Houses, as they hold influence in every city-state.

\textbf{Psiocratic:} A group of psions holds influence because of their psionic capabilities. It can be a single psion leading a village, or Saragar's Mind Lords.

\textbf{Stratocratic:} A military group hold influence because of their martial power. It can be the leader of the guard holding influence in the city's politics, or raiders demanding tribute.

\textbf{Theocratic:} Clerics or druids influencing the community with their faith. It can be an earth cleric leading a slave tribe, or a druid circle dictating how and when crops should planted.

\textbf{Monstrous:} A monstrous influence impact the lives of the community. It can be the Dragon demanding their levy, or a gith tribe enforcing a tribute to the village, or belgoi \emph{dominating} the minds of citizen.


\subsubsection{Alignment of Power Centers}
Power centers have alignments as if they are characters. Their alignment tell how the power centers act and influence the community. Most power centers are lawful, due to their internal rules and laws.

\Table{Power Center Alignment}{cXcX}{
  \tableheader d\%
& \tableheader Alignment
& \tableheader d\%
& \tableheader Alignment \\
01--20 & Lawful Good &
89--96 & Neutral Evil \\
21--50 & Lawful Neutral &
  97   & Chaotic Good \\
51--70 & Lawful Evil &
98--99 & Chaotic Neutral \\
71--78 & Neutral Good &
 100   & Chaotic Evil \\
79--88 & True Neutral &&\\
}

\textbf{Lawful Good:} A community with a lawful good power center usually has a codified set of laws, and most people willingly obey those laws.

\textbf{Lawful Neutral:} A community with a lawful neutral power center has a codified set of laws that are followed to the letter. Those in power usually insist that visitors (as well as residents) obey all local rules and regulations.

\textbf{Lawful Evil:} A community with a lawful evil power center usually has a codified set of laws, which most people obey out of fear of harsh punishment.

\textbf{Neutral Good:} A neutral good power center rarely influences the residents of the community other than to help them when they are in need.

\textbf{True Neutral:} This sort of power center rarely influences the community. Those in power prefer to pursue their private goals.

\textbf{Neutral Evil:} The residents of a community with a neutral evil power center are usually oppressed and subjugated, facing a dire future.

\textbf{Chaotic Good:} This sort of power center influences the community by helping the needy and opposing restrictions on freedom.

\textbf{Chaotic Neutral:} This sort of power center is unpredictable, influencing the community in different ways at different times.

\textbf{Chaotic Evil:} The residents of a community with a chaotic evil power center live in abject fear because of the unpredictable and horrific situations continually placed upon them.
