\Table{Specific Armors}{LR}{
  \tableheader Armor
& \tableheader Price \\
Drakehide Plate        & 3,300 cp \\
Banded Mail of Luck    & 18,900 cp \\
Breastplate of Command & 25,400 cp \\
De'utko Armor          & 87,250 cp \\
Adamantine Breastplate & 10,002 gp \\
Dwarven Plate          & 15,015 gp \\
}

\subsubsection{Specific Armors}
The following specific suits of armor usually are preconstructed with exactly the qualities described here.

\textbf{Adamantine Breastplate:} This nonmagical breastplate is made of adamantine, giving its wearer damage reduction of 2/--.

No aura (nonmagical); Price 10,002 gp.

\textbf{Banded Mail of Luck:} Ten 100-cp gems adorn this \emph{+3 banded mail}. Once per week, the armor allows its wearer to require that an attack roll made against him be rerolled. He must take whatever consequences come from the second roll. The wearer's player must decide whether to have the attack roll rerolled before damage is rolled.

Strong enchantment; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{bless}; Price 18,900 cp; Cost 10,150 cp + 700 XP.

\textbf{Breastplate of Command:} This finely crafted \emph{+2 breastplate} radiates a powerful aura of magic. When worn, the armor bestows a dignified and commanding aura upon its owner. The wearer gains a +2 competence bonus on all Charisma checks, including turning checks and Charisma-based skill checks. The wearer also gains a +2 competence bonus to his \feat{Leadership} score. Friendly troops within 102 meters of the user become braver than normal. Since the effect arises in great part from the distinctiveness of the armor, the wearer cannot hide or conceal herself in any way and still have the effect function.

Strong enchantment; CL 15th; \feat{Craft Magic Arms and Armor}, \spell{mass charm monster}; Price 25,400 cp; Cost 10,975 cp + 850 XP.

\textbf{De'utko Armor:} This elven suit of armor, whose name means ``sleepless'' in their tongue, is fashioned from the chitinuous shells of slain thri-kreen by the tribe's best artisan. It is etched with markings symbolizing the glory of the hunt and slaying of the hated insect-men. Only kreen slayers don this armor, using its powers to aid in hunting and protecting their tribes for long periods of time without fear of letting their guards down in face of the sleepless mantis warrior.

This \emph{+2 improved silent moves chitin armor} renders the wearer immune to all spells and effects that restrict his movement, as if he were under the effect of a \spell{freedom of movement} spell. He also receives the benefit of the thri-kreen's sleep immunity racial ability for a number of days equal to 7 + his Constitution modifier, after which time 8 hours of uninterrupted sleep are needed before gaining the benefits of this ability again. A spellcasting or manifesting wearer must rest as usual each time he wants to prepare new spells or regain spent power points.

Strong abjuration; CL 17th; \feat{Craft Magic Arms and Armor}, creator must be an elf, \spell{freedom of movement}, \spell{silence}, \spell{wakefulness}; Price 87,250 cp; Cost 53,250 cp + 2,720 XP.

\textbf{Drakehide Plate:} This suit of full plate is made of drakehide, rather than metal, so druids can wear it. It is otherwise identical to masterwork full plate.

No aura (nonmagical); Price 3,300 cp.

\textbf{Dwarven Plate:} This full plate is made of adamantine, giving its wearer damage reduction of 3/--.

No aura (nonmagical); Price 15,015 gp.
