\subsection{Bull Rush}
You can make a bull rush as a standard action (an attack) or as part of a charge. When you make a bull rush, you attempt to push an opponent straight back instead of damaging him. You can only bull rush an opponent who is one size category larger than you, the same size, or smaller.

\textbf{Initiating a Bull Rush:} First, you move into the defender's space. Doing this provokes an attack of opportunity from each opponent that threatens you, including the defender. (If you have the \feat{Improved Bull Rush} feat, you don't provoke an attack of opportunity from the defender.) Any attack of opportunity made by anyone other than the defender against you during a bull rush has a 25\% chance of accidentally targeting the defender instead, and any attack of opportunity by anyone other than you against the defender likewise has a 25\% chance of accidentally targeting you. (When someone makes an attack of opportunity, make the attack roll and then roll to see whether the attack went astray.)

Second, you and the defender make opposed Strength checks. You each add a +4 bonus for each size category you are larger than Medium or a $-4$ penalty for each size category you are smaller than Medium. You get advantage on your check if you are charging. The defender gets advantage on his roll if he has more than two legs or is otherwise exceptionally stable.

\textbf{Bull Rush Results:} If you beat the defender's Strength check result, you push him back 1.5 meter. If you wish to move with the defender, you can push him back an additional 1.5 meter for each 5 points by which your check result is greater than the defender's check result. You can't, however, exceed your normal movement limit. (Note: The defender provokes attacks of opportunity if he is moved. So do you, if you move with him. The two of you do not provoke attacks of opportunity from each other, however.)

If you fail to beat the defender's Strength check result, you move 1.5 meter straight back to where you were before you moved into his space. If that space is occupied, you fall prone in that space.