\subsection{Two-Weapon Fighting}
If you wield a second weapon in your off hand, you can get one extra attack per round with that weapon. You suffer a $-6$ penalty with your regular attack or attacks with your primary hand and a $-10$ penalty to the attack with your off hand when you fight this way. You can reduce these penalties in two ways:

\begin{itemize*}
\item If your off-hand weapon is light, the penalties are reduced by 2 each. (An unarmed strike is always considered light.)
\item The \feat{Two-Weapon Fighting} feat lessens the primary hand penalty by 2, and the off-hand penalty by 6.
\end{itemize*}

\tabref{Two-Weapon Fighting Penalties} summarizes the interaction of all these factors.

\Table{Two-Weapon Fighting Penalties}{p{38mm}CC}{
\tableheader Circumstances & \tableheader Primary Hand & \tableheader Off Hand \\
Normal penalties & $-6$ & $-10$ \\
Off-hand weapon is light & $-4$ & $-8$ \\
\feat{Two-Weapon Fighting} feat & $-4$ & $-4$ \\
Off-hand weapon is light and \feat{Two-Weapon Fighting} feat & $-2$ & $-2$ \\
}

\textbf{Double Weapons:} You can use a double weapon to make an extra attack with the off-hand end of the weapon as if you were fighting with two weapons. The penalties apply as if the off-hand end of the weapon were a light weapon.

\textbf{Thrown Weapons:} The same rules apply when you throw a weapon from each hand. Treat a dart or shuriken as a light weapon when used in this manner, and treat a bolas, javelin, net, or sling as a one-handed weapon.

\textbf{Shield Bash Attacks:} You can bash an opponent with a light shield or heavy shield, using it as an off-hand weapon. See \tabref{Martial Weapons} for the damage dealt by a shield bash. Used this way, a shield is a martial bludgeoning weapon. For the purpose of penalties on attack rolls, treat a heavy shield as a one-handed weapon and a light shield as a light weapon. If you use your shield as a weapon, you lose its AC bonus until your next action (usually until the next round). An enhancement bonus on a shield does not improve the effectiveness of a shield bash made with it, but the shield can be made into a magic weapon in its own right.

\textbf{Shield Spikes:} When added to your shield, these spikes turn it into a martial piercing weapon that increases the damage dealt by a shield bash as if the shield were designed for a creature one size category larger than you. You can’t put spikes on a buckler or a tower shield. Otherwise, attacking with a spiked shield is like making a shield bash attack.

An enhancement bonus on a spiked shield does not improve the effectiveness of a shield bash made with it, but a spiked shield can be made into a magic weapon in its own right.