\subsubsection{Magic Weapon Special Ability Descriptions}
In addition to enhancement bonuses, weapons can have one or more of the special abilities detailed below. A weapon with a special ability must have at least a +1 enhancement bonus.

\textbf{Anarchic:} An anarchic weapon is chaotically aligned and infused with the power of chaos. It makes the weapon chaos-aligned and thus bypasses the corresponding damage reduction. It deals an extra 2d6 points of damage against all of lawful alignment. It bestows one negative level on any lawful creature attempting to wield it. The negative level remains as long as the weapon is in hand and disappears when the weapon is no longer wielded. This negative level never results in actual level loss, but it cannot be overcome in any way (including \spell{restoration} spells) while the weapon is wielded. Bows, crossbows, and slings so crafted bestow the chaotic power upon their ammunition.

Moderate evocation [chaotic]; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{chaos hammer}, creator must be chaotic; Price +2 bonus.

\textbf{Axiomatic:} An axiomatic weapon is lawfully aligned and infused with the power of law. It makes the weapon law-aligned and thus bypasses the corresponding damage reduction. It deals an extra 2d6 points of damage against all of chaotic alignment. It bestows one negative level on any chaotic creature attempting to wield it. The negative level remains as long as the weapon is in hand and disappears when the weapon is no longer wielded. This negative level never results in actual level loss, but it cannot be overcome in any way (including \spell{restoration} spells) while the weapon is wielded. Bows, crossbows, and slings so crafted bestow the lawful power upon their ammunition.

Moderate evocation [lawful]; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{order's wrath}, creator must be lawful; Price +2 bonus.

\textbf{Baleful Shriek:} Upon command, a baleful shriek weapon hums with an aura of sonic energy that deals an extra 1d6 points of sonic damage on a successful attack. The weapon emits a shrieks when thrown, forcing all enemies of the wielder within 6 meters of the weapon's path to succeed on a DC 16 Will save or become shaken for 1 round. When dealing a critical hit the weapon emits a pain-wracked scream, forcing the opponent struck to succeed on a DC 16 Will save or cower for 1 round. Except for the sonic damage, these are mind-affecting fear effects. Only thrown weapons can be so enchanted.

Moderate evocation and necromancy; CL 9th; \feat{Craft Magic Arms and Armor}, heightened 4th-level \spell{cause fear} or heightened 4th-level \spell{doom}, \spell{shout} or \spell{sound burst}; Price +3 bonus.

\textbf{Bloodlust:} When you drop an opponent with a bloodlust weapon during a rage (such as the barbarian ability or the spell), you gain a +2 morale bonus to your Strength score until the end of your rage. You can only gain an increase in Strength once each round, no matter how many opponents you drop during a round, although this Strength bonus stacks with itself over the course of multiple rounds. Only melee weapons can be so enchanted.

Faint enchantment; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{rage}; Price +1 bonus.

\textbf{Bodyfeeder:} All feeder weapons have a special ability that functions only upon scoring a successful critical hit. A bodyfeeder weapon grants its wielder temporary hit points equal to the total damage dealt by a successful critical hit. These temporary hit points last for 10 minutes. Thus, if the wielder of a bodyfeeder weapon successfully scores a critical hit while the wielder still enjoys temporary hit points from a previous critical hit, the wielder gains only the better of the two values: either his current number of temporary hit points, or the new influx of temporary hit points, whichever is higher.

Strong necromancy; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{vampiric touch}; Price +3 bonus.

\textbf{Brilliant Energy:} A brilliant energy weapon has its significant portion transformed into light, although this does not modify the item's weight. It always gives off light as a torch (6-meter radius). A brilliant energy weapon ignores nonliving matter. Armor and shield bonuses to AC (including any enhancement bonuses to that armor) do not count against it because the weapon passes through armor. (Dexterity, deflection, dodge, natural armor, and other such bonuses still apply.) A brilliant energy weapon cannot harm undead, constructs, and objects. This property can only be applied to melee weapons, thrown weapons, and ammunition.

Strong transmutation; CL 16th; \feat{Craft Magic Arms and Armor}, \spell{gaseous form}, \spell{continual flame}; Price +4 bonus.

\textbf{Chitin-Rot:} A chitin-rot weapon always uses sap from the Forest Ridge's trees in its fabrication and always seems slick with humidity, even in the hottest environment. Its wounds cause the exoskeleton of creatures such as insects and kreen to become dull and streaked with gray striations of fungal infection, effectively weakening it as if suffering from the chitin-rot disease.

Any such creature succesfully hit by a chitin-rot weapon must make a DC 16 Fortitude save or suffer a $-2$ cumulative penalty to its natural armor, down to a minimum of 0. The penalty for this effect decreases naturally at a rate of 1 point per day. Any effect that heals ability damage may also be used to reduce or eliminate the penalty by the same amount. Bows, crossbows, and slings so crafted bestow the chitin-rot ability upon their ammunition.

Moderate necromancy; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{contagion}; Price +1 bonus.

\textbf{Cleansing Flame:} Cleansing flame weapons were used during the Preserver Jihad to quickly destroy the defiler minions of Rajaat's armies.

A cleansing flame weapon functions as a flaming weapon against most creatures, but against defilers, templars whose sorcerer-kings are defilers, creatures with the defiled template, items created through defiling magic, creatures with the evil subtype, and undead, the flames become extremely deadly. These targets must make a DC 23 Fortitude save or immediately be destroyed and turned to ash by the heat of the flames.

Creatures killed by this spell have their remains consumed (but not their equipment and possessions) utterly. The only way to restore life to creatures killed in this way is to use \spell{true resurrection}, a carefully worded \spell{wish} spell followed by \spell{resurrection}, or \spell{miracle}, or the \psionic{reality revision} power.

If a creature from the above list attempts to wield a cleansing flame weapon, he is affected as if he had been struck by it, needing to succeed on a Fortitude save each round that he holds the weapon to avoid fiery destruction. Only melee weapons can be so enchanted.

Moderate evocation; CL 17th; \feat{Craft Magic Arms and Armor}, \spell{cleansing flame}; Price +5 bonus.

\textbf{Coup de Grace:} Coup de grace weapons are exceptionally dangerous. On a successful critical hit, the foe must succeed on a DC 27 Will save or be paralyzed for 1 round. While this ability does work on creatures that are immune to extra damage from critical hits, it does not work on creatures without an Intelligence score. Bows, crossbows, and slings bestow this ability on their ammunition.

Strong enchantment; CL 19th; \feat{Craft Magic Arms and Armor}, \spell{dominate monster}; Price +5 bonus.

\textbf{Dancing:} As a standard action, a dancing weapon can be loosed to attack on its own. It fights for 4 rounds using the base attack bonus of the one who loosed it and then drops. While dancing, it cannot make attacks of opportunity, and the person who activated it is not considered armed with the weapon. In all other respects, it is considered wielded or attended by the creature for all maneuvers and effects that target items. While dancing, it takes up the same space as the activating character and can attack adjacent foes (weapons with reach can attack opponents up to 3 meters away). The dancing weapon accompanies the person who activated it everywhere, whether she moves by physical or magical means. If the wielder who loosed it has an unoccupied hand, she can grasp it while it is attacking on its own as a free action; when so retrieved the weapon can't dance (attack on its own) again for 4 rounds.

Strong transmutation; CL 15th; \feat{Craft Magic Arms and Armor}, \spell{animate objects}; Price +4 bonus.

\textbf{Defending:} A defending weapon allows the wielder to transfer some or all of the sword's enhancement bonus to his AC as a bonus that stacks with all others. As a free action, the wielder chooses how to allocate the weapon's enhancement bonus at the start of his turn before using the weapon, and the effect to AC lasts until his next turn.

Moderate abjuration; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{shield} or \spell{shield of faith}; Price +1 bonus.

\textbf{Dislocator:} The wielder of this kind of weapon can attempt to dislocate a designated foe up to three times per day. On a successful hit, the foe must succeed on a DC 17 Will save or be teleported 1-150 kilometers in a random direction. If the weapon misses, the use is wasted. Bows, crossbows, and slings bestow this ability on their ammunition.

Strong conjuration; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{teleport}; Price +3 bonus.

\textbf{Disruption:} A weapon of disruption is the bane of all undead. Any undead creature struck in combat must succeed on a DC 14 Will save or be destroyed. A weapon of disruption must be a bludgeoning weapon. (If you roll this property randomly for a piercing or slashing weapon, reroll.)

Strong conjuration; CL 14th; \feat{Craft Magic Arms and Armor}, \spell{heal}; Price +2 bonus.

\textbf{Distance:} This property can only be placed on a ranged weapon. A weapon of distance has double the range increment of other weapons of its kind.

Moderate divination; CL 6th; \feat{Craft Magic Arms and Armor}, \spell{clairaudience/clairvoyance}; Price +1 bonus.

\textbf{Doom:} Doom weapons were used during the Preserver Jihad and the Cleansing Wars to bring down powerful opponents on both sides.

A doom weapon is keyed to a particular individual. During the crafting of this weapon, something valuable to the individual to be exterminated must be incorporated into the crafting process of the weapon.

Against the particular creature it was crafted to slay, the effective enhancement bonus of the weapon is +2 better than its normal enhancement bonus. On a critical hit the target must make a DC 23 Fortitude save or die instantly. This ability is a death effect. On a successful save the target is nevertheless dealt an extra 3d6+17 points of damage. Only melee weapons can be so enchanted.

Strong necromancy; CL 17th; \feat{Craft Magic Arms and Armor}, heightened 9th-level \spell{finger of death}; Price +3 bonus.

\textbf{Expiation:} An expiation weapon is a device created to purge the land of those who will continue to help it towards desolation and eventual destruction. The majority of these weapons were created at the end of the Preserver Jihad and the beginning of the Cleansing Wars; many were lost during battles, their powers forgotten by all but the most erudite. Some parts of these weapons are always crafted to resemble natural creatures or plants.

Against defilers, the effective enhancement bonus of the weapon is +2 better than its normal enhancement bonus. It deals an extra 2d6 points of damage against these foes. Also, upon a successful hit, the defender must succeed at a DC 17 Will save or be unable to cast spells, use spell-like abilities, or activate spell completion or spell trigger items for 2d4 rounds. Expiation effects are only found on melee weapons.

Moderate divination; CL 9th; \feat{Craft Magic Arms and Armor}, \spell{defiler scent}; Price +2 bonus.

\textbf{Flaming:} Upon command, a flaming weapon is sheathed in fire. The fire does not harm the wielder. The effect remains until another command is given. A flaming weapon deals an extra 1d6 points of fire damage on a successful hit. Bows, crossbows, and slings so crafted bestow the fire energy upon their ammunition.

Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor} and \spell{flame blade}, \spell{flame strike}, or \spell{fireball}; Price +1 bonus.

\textbf{Flaming Burst:} A flaming burst weapon functions as a flaming weapon that also explodes with flame upon striking a successful critical hit. The fire does not harm the wielder. In addition to the extra fire damage from the flaming ability (see above), a flaming burst weapon deals an extra 1d10 points of fire damage on a successful critical hit. If the weapon's critical multiplier is $\times3$, add an extra 2d10 points of fire damage instead, and if the multiplier is $\times4$, add an extra 3d10 points of fire damage. Bows, crossbows, and slings so crafted bestow the fire energy upon their ammunition.

Even if the flaming ability is not active, the weapon still deals its extra fire damage on a successful critical hit.

Strong evocation; CL 12th; \feat{Craft Magic Arms and Armor} and \spell{flame blade}, \spell{flame strike}, or \spell{fireball}; Price +2 bonus.

\textbf{Frost:} Upon command, a frost weapon is sheathed in icy cold. The cold does not harm the wielder. The effect remains until another command is given. A frost weapon deals an extra 1d6 points of cold damage on a successful hit. Bows, crossbows, and slings so crafted bestow the cold energy upon their ammunition.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{chill metal} or \spell{ice storm}; Price +1 bonus.

\textbf{Ghost Touch:} A ghost touch weapon deals damage normally against incorporeal creatures, regardless of its bonus. (An incorporeal creature's 50\% chance to avoid damage does not apply to attacks with ghost touch weapons.) The weapon can be picked up and moved by an incorporeal creature at any time. A manifesting ghost can wield the weapon against corporeal foes. Essentially, a ghost touch weapon counts as either corporeal or incorporeal at any given time, whichever is more beneficial to the wielder.

Moderate conjuration; CL 9th; \feat{Craft Magic Arms and Armor}, \spell{plane shift}; Price +1 bonus.

\textbf{Great Dislocator:} The wielder of this kind of weapon can attempt to greatly dislocate a designated foe up to three times per day. On a successful hit, the foe must succeed on a DC 20 Will save or be cast into a random alternate plane of existence. If the weapon misses, the use is wasted. Bows, crossbows, and slings bestow this ability upon their ammunition.

Strong conjuration; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{plane shift}; Price +4 bonus.

\textbf{Holy:} A holy weapon is imbued with holy power. This power makes the weapon good-aligned and thus bypasses the corresponding damage reduction. It deals an extra 2d6 points of damage against all of evil alignment. It bestows one negative level on any evil creature attempting to wield it. The negative level remains as long as the weapon is in hand and disappears when the weapon is no longer wielded. This negative level never results in actual level loss, but it cannot be overcome in any way (including \spell{restoration} spells) while the weapon is wielded. Bows, crossbows, and slings so crafted bestow the holy power upon their ammunition.

Moderate evocation [good]; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{holy smite}, creator must be good; Price +2 bonus.

\textbf{Icy Burst:} An icy burst weapon functions as a frost weapon that also explodes with frost upon striking a successful critical hit. The frost does not harm the wielder. In addition to the extra damage from the frost ability, an icy burst weapon deals an extra 1d10 points of cold damage on a successful critical hit. If the weapon's critical multiplier is $\times3$, add an extra 2d10 points of cold damage instead, and if the multiplier is $\times4$, add an extra 3d10 points. Bows, crossbows, and slings so crafted bestow the cold energy upon their ammunition.

Even if the frost ability is not active, the weapon still deals its extra cold damage on a successful critical hit.

Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{chill metal} or \spell{ice storm}; Price +2 bonus.

\textbf{Keen:} This ability doubles the threat range of a weapon. Only piercing or slashing weapons can be keen. (If you roll this property randomly for an inappropriate weapon, reroll.) This benefit doesn't stack with any other effect that expands the threat range of a weapon (such as the \spell{keen edge} spell or the \feat{Improved Critical} feat).

Moderate transmutation; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{keen edge}; Price +1 bonus.

\textbf{Malison:} A malison weapon deals wounds that are fouled by sorcery. All damage dealt by the weapon, calculated using the weapon type’s base damage plus the wielder’s Strength modifiers and before adding any magical bonuses or other damage-dealing effects, including feats, spells or powers, cannot be cured by any means until the damaged individual has received a \spell{remove curse} spell (or some other effect that neutralizes a curse). The remaining damage dealt by the weapon, effects or as a result of this damage is considered of its usual type.

If a creature is slain by a malison weapon, it can’t be raised from the dead unless a \spell{remove curse} spell (or similar effect) is first cast on the body, or a \spell{true resurrection} spell is used. Only melee weapons can be so enchanted.

Strong necromancy; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{bestow curse}; Price +4 bonus.

\textbf{Manifester:} This kind of weapon generates 5 power points once per day that the wearer can use when manifesting a power he knows. These power points must all be used on the same power. As usual, a psionic character cannot pay a power's cost with power points from more than one source, so the power points in the weapon must be used for discrete manifestations.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{dweomer of transference}, knowledge of any 3rd-level power; Price +16,000 cp.

\textbf{Merciful:} The weapon deals an extra 1d6 points of damage, and all damage it deals is nonlethal damage. On command, the weapon suppresses this ability until commanded to resume it. Bows, crossbows, and slings so crafted bestow the merciful effect upon their ammunition.

Faint conjuration; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{cure light wounds}; Price +1 bonus.

\textbf{Mighty Cleaving:} A mighty cleaving weapon allows a wielder with the Cleave feat to make one additional cleave attempt in a round.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{divine power}; Price +1 bonus.

\textbf{Parching:} A parching weapon drains the water from creatures hit. A creature is dealt an extra 1d6 points of nonlethal damage and is considered fatigued as if suffering from thirst. It must drink the necessary amount of water or, failing that, make a Fortitude save (DC 10, +1 for each previous check) each following hour or sustain 1d6 points of nonlethal damage. Further hits to the same creature deal the nonlethal damage and increase the DC of the subsequent Fortitude check(s) by a cumulative +2 per additional hit. Only melee weapons can be so enchanted.

Moderate evocation; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{sunstroke}; Price +1 bonus.

\textbf{Penetration:} A penetration weapon is the bane of all kreen and insects. It deals +2d6 points of bonus damage on a successful hit against creatures possessing an exoskeleton or natural armor specified as being chitinous in nature. This enchantment is only found on piercing weapons. Bows and crossbows so crafted bestow the penetration effect upon their ammunition.

Moderate transmutation; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{keen edge}; Price +2 bonus.

\textbf{Power Storing:} A power storing weapon allows a manifester to store a single targeted power of up to 5 power points in the weapon. (The power must have a manifesting time of 1 standard action.) Any time the weapon strikes a creature and the creature takes damage from it, the weapon can immediately manifest the power on that creature as a swift action if the wielder desires. (This ability is an exception to the rule that manifesting a power from an item takes at least as long as manifesting that power normally.) Once the power is manifested, the weapon is empty, and a manifester can imbed any other targeted power of up to 5 power points into it. The weapon telepathically whispers to the wearer the name of the power currently stored within it. A randomly generated power storing weapon has a 50\% chance to have a power stored in it already.

Strong evocation; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{dweomer of transference}, creator must be a manifester of at least 12th level; Price +1 bonus.

\textbf{Psychic:} A psychic weapon's power depends on its wielder. In the hands of a nonpsionic creature, the weapon possesses the qualities of a nonmagical, nonpsionic masterwork weapon. When wielded by a psionic creature, this weapon has an enhancement bonus based on the wielder's current power point reserve, as shown on the following table. The weapon's enhancement bonus decreases as the wielder spends power points, and it increases whenever the wielder gains enough power points (by any means) to put his power point reserve into the next higher category.

\Table{}{r{1cm}lClr{1cm}}{
& \tableheader Power Point Reserve & \tableheader Enhancement Bonus & \\
& 1--4 & +1 & \\
& 5--29 & +2 & \\
& 30--79 & +3 & \\
& 80--129 & +4 & \\
& 130 or higher & +5 & \\
}

Strong evocation; CL 17th; \feat{Craft Magic Arms and Armor}, \spell{wish} or \spell{miracle}; Price +35,000 cp.

\textbf{Returning:} This special ability can only be placed on a weapon that can be thrown. A returning weapon flies through the air back to the creature that threw it. It returns to the thrower just before the creature's next turn (and is therefore ready to use again in that turn).

Catching a returning weapon when it comes back is a free action. If the character can't catch it, or if the character has moved since throwing it, the weapon drops to the ground in the square from which it was thrown.

Moderate transmutation; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{telekinesis}; Price +1 bonus.

\textbf{Rumbling:} Upon command, a rumbling weapon creates a continuous rumble like that of an approaching storm. A rumbling weapon deals an extra 1d8 points of sonic damage on a successful hit. The sonic energy does not harm the wielder. The effect remains until dismissed by another command. In addition to the sonic damage, a rumbling weapon deals an extra 1d8 points of sonic damage on a successful critical hit. If the weapon’s critical multiplier is $\times3$, add an extra 2d8 points of sonic damage instead, and if the multiplier is $\times4$, add an extra 3d8 points of sonic damage. Subjects dealt a critical hit by a rumbling weapon must make a DC 19 Fortitude save or be stunned for 1 round. Bows, crossbows, and slings so crafted bestow this enchantment upon their ammunition.

Strong evocation; CL 11th; \feat{Craft Magic Arms and Armor}, heightened 6th-level \spell{sound burst}; Price +3 bonus.

\textbf{Seeking:} Only ranged weapons can have the seeking ability. The weapon veers toward its target, negating any miss chances that would otherwise apply, such as from concealment. (The wielder still has to aim the weapon at the right square. Arrows mistakenly shot into an empty space, for example, do not veer and hit invisible enemies, even if they are nearby.)

Strong divination; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{true seeing}; Price +1 bonus.

\textbf{Shattering:} A shattering weapon increases the wielder’s ability to sunder objects, and he is considered to have the \feat{Improved Sunder} feat regardless of whether or not he meets the feat’s prerequisites. When making a sundering attempt, a successful opposed attack roll on the part of the wielder causes the struck object, which can be up to the size category of the shattering weapon, to shatter and be destroyed. If a sunder attempt is made against the shattering weapon, then the attacker’s weapon is also treated as being dealt a sundering attempt and thus is subject to destruction if the shattering weapon’s wielder  succeeds on the opposed attack roll. Only bludgeoning or slashing weapons can be shattering. A shattering weapon’s shattering ability only works against objects made of bone, stone, or wood; the wielder is still considered to have the \feat{Improved Sunder} feat against objects made from other materials, however.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{shatter}; Price +2 bonus.

\textbf{Shock:} Upon command, a shock weapon is sheathed in crackling electricity. The electricity does not harm the wielder. The effect remains until another command is given. A shock weapon deals an extra 1d6 points of electricity damage on a successful hit. Bows, crossbows, and slings so crafted bestow the electricity energy upon their ammunition.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{call lightning} or \spell{lightning bolt}; Price +1 bonus.

\textbf{Shocking Burst:} A shocking burst weapon functions as a shock weapon that also explodes with electricity upon striking a successful critical hit. The electricity does not harm the wielder. In addition to the extra electricity damage from the shock ability, a shocking burst weapon deals an extra 1d10 points of electricity damage on a successful critical hit. If the weapon's critical multiplier is $\times3$, add an extra 2d10 points of electricity damage instead, and if the multiplier is $\times4$, add an extra 3d10 points. Bows, crossbows, and slings so crafted bestow the electricity energy upon their ammunition.

Even if the shock ability is not active, the weapon still deals its extra electricity damage on a successful critical hit.

Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{call lightning} or \spell{lightning bolt}; Price +2 bonus.

\textbf{Silencing:} Silencing weapons were created to rid the land of the preservers opposing Rajaat’s forces. The majority of these weapons were created at the beginning of the Preserver Jihad, but many were lost during the many battles, their powers forgotten by all but the most erudite. Some part of these weapons always depict anguished humanoid visages prevented from screaming by various means.

Against preservers the effective enhancement bonus of the weapon is +2 better than its normal enhancement bonus. It deals an extra 2d6 points of damage against these foes. Also, upon a successful hit, the defender must succeed at a DC 17 Will save or be unable to cast spells, use spell-like abilities, or activate spell completion or spell trigger items for 2d4 rounds. Silencing effects are only found on melee weapons.

Moderate abjuration; CL 9th; \feat{Craft Magic Arms and Armor}, \spell{dispel magic}; Price +2 bonus.

\textbf{Soul-bleeder:} This ability causes a weapon to have a special bond with the Gray, creating wounds that drain the strength from living creatures. Each hit from a soul-bleeder weapon inflicts 1 point of Strength damage to a living creature hit in addition to normal damage. The Strength damage lasts for 5 minutes unless cured by other means, and is considered temporary ability damage caused by a necromantic source for all other purposes. The soul-bleeding ability is only found on melee weapons.

A soul-bleeder weapon made of Gray-forged steel instead deals 1d4 points of Strength damage in addition to normal damage upon a successful hit.

Faint necromancy; CL 5th; \feat{Craft Magical Arms and Armor}, \spell{ray of enfeeblement}; Price +1 bonus.

\textbf{Speed:} When making a full attack action, the wielder of a speed weapon may make one extra attack with it. The attack uses the wielder's full base attack bonus, plus any modifiers appropriate to the situation. (This benefit is not cumulative with similar effects, such as a \spell{haste} spell.)

Moderate transmutation; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{haste}; Price +3 bonus.

\textbf{Spell Storing:} A spell storing weapon allows a spellcaster to store a single targeted spell of up to 3rd level in the weapon. (The spell must have a casting time of 1 standard action.) Any time the weapon strikes a creature and the creature takes damage from it, the weapon can immediately cast the spell on that creature as a free action if the wielder desires. (This special ability is an exception to the general rule that casting a spell from an item takes at least as long as casting that spell normally.) Once the spell has been cast from the weapon, a spellcaster can cast any other targeted spell of up to 3rd level into it. The weapon magically imparts to the wielder the name of the spell currently stored within it. A randomly rolled spell storing weapon has a 50\% chance to have a spell stored in it already.

Strong evocation (plus aura of stored spell); CL 12th; \feat{Craft Magic Arms and Armor}, creator must be a caster of at least 12th level; Price +1 bonus.

\textbf{Thundering:} A thundering weapon creates a cacophonous roar like thunder upon striking a successful critical hit. The sonic energy does not harm the wielder. A thundering weapon deals an extra 1d8 points of sonic damage on a successful critical hit. If the weapon's critical multiplier is $\times3$, add an extra 2d8 points of sonic damage instead, and if the multiplier is $\times4$, add an extra 3d8 points of sonic damage. Bows, crossbows, and slings so crafted bestow the sonic energy upon their ammunition. Subjects dealt a critical hit by a thundering weapon must make a DC 14 Fortitude save or be deafened permanently.

Faint necromancy; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{blindness/deafness}; Price +1 bonus.

\textbf{Throwing:} This ability can only be placed on a melee weapon. A melee weapon crafted with this ability gains a range increment of 3 meters and can be thrown by a wielder proficient in its normal use.

Faint transmutation; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{magic stone}; Price +1 bonus.

\textbf{Unholy:} An unholy weapon is imbued with unholy power. This power makes the weapon evil-aligned and thus bypasses the corresponding damage reduction. It deals an extra 2d6 points of damage against all of good alignment. It bestows one negative level on any good creature attempting to wield it. The negative level remains as long as the weapon is in hand and disappears when the weapon is no longer wielded. This negative level never results in actual level loss, but it cannot be overcome in any way (including \spell{restoration} spells) while the weapon is wielded. Bows, crossbows, and slings so crafted bestow the unholy power upon their ammunition.

Moderate evocation [evil]; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{unholy blight}, creator must be evil; Price +2 bonus.

\textbf{Vicious:} When a vicious weapon strikes an opponent, it creates a flash of disruptive energy that resonates between the opponent and the wielder. This energy deals an extra 2d6 points of damage to the opponent and 1d6 points of damage to the wielder. Only melee weapons can be vicious.

Moderate necromancy; CL 9th; \feat{Craft Magic Arms and Armor}, \spell{enervation}; Price +1 bonus.

\textbf{Vorpal:} This potent and feared ability allows the weapon to sever the heads of those it strikes. Upon a roll of natural 20 (followed by a successful roll to confirm the critical hit), the weapon severs the opponent's head (if it has one) from its body. Some creatures, such as many aberrations and all oozes, have no heads. Others, such as golems and undead creatures other than vampires, are not affected by the loss of their heads. Most other creatures, however, die when their heads are cut off. A vorpal weapon must be a slashing weapon. (If you roll this property randomly for an inappropriate weapon, reroll.)

Strong necromancy and transmutation; CL 18th; \feat{Craft Magic Arms and Armor}, \spell{circle of death}, \spell{keen edge}; Price +5 bonus.

\textbf{Wounding:} A wounding weapon deals 1 point of Constitution damage from blood loss when it hits a creature. A critical hit does not multiply the Constitution damage. Creatures immune to critical hits (such as plants and constructs) are immune to the Constitution damage dealt by this weapon.

Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{mage's sword}; Price +2 bonus.