\subsubsection{Specific Weapons}
The following specific weapons usually are preconstructed with exactly the qualities described here.

\textbf{Adamantine Battleaxe:} This nonmagical axe is made out of adamantine. As a masterwork weapon, it has a +1 enhancement bonus on attack rolls.

No aura (nonmagical); Price 301,000 cp.

\textbf{Adamantine Dagger:} This nonmagical dagger is made out of adamantine. As a masterwork weapon, it has a +1 enhancement bonus on attack rolls.

No aura (nonmagical); Price 300,200 cp.

\textbf{Assassin's Dagger:} This wicked-looking, curved \emph{+2 bone dagger} provides a +1 bonus to the DC of a Fortitude save forced by the death attack of an assassin.

Moderate necromancy; CL 9th; \feat{Craft Magic Arms and Armor}, \spell{slay living}; Price 18,302 cp; Cost 9,302 cp + 720 XP.

\textbf{Dagger of Venom:} This black \emph{+1 wood dagger} has a serrated edge. It allows the wielder to use a \spell{poison} effect (as the spell, save DC 14) upon a creature struck by the blade once per day. The wielder can decide to use the power after he has struck. Doing so is a free action, but the \spell{poison} effect must be invoked in the same round that the dagger strikes.

Faint necromancy; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{poison}; Price 8,302 cp; Cost 4,302 cp + 320 XP.

% \textbf{Dwarven Thrower:} This weapon commonly functions as a \emph{+2  warhammer}. In the hands of a dwarf, the warhammer gains an additional +1 enhancement bonus (for a total enhancement bonus of +3) and gains the returning special ability. It can be hurled with a 9-meter range increment. When hurled, it deals an extra 2d8 points of damage against giants or an extra 1d8 points of damage against any other target.

% Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor}, creator must be a dwarf of at least 10th level; Price 60,312 cp; Cost 30,312 cp + 2,400 XP.

\textbf{Flame Tongue:} This is a \emph{+1 flaming burst metal longsword}. Once per day, the sword can blast forth a fiery ray at any target within 9 meters as a ranged touch attack. The ray deals 4d6 points of fire damage on a successful hit.

Moderate evocation; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{scorching ray}, and \spell{flame blade}, \spell{flame strike}, or \spell{fireball}; Price 22,200 cp; Cost 12,000 cp + 816 XP.

\textbf{Frost Brand:} This \emph{+3 frost stone greatsword} sheds light as a torch when the temperature drops below -18$^\circ$C. At such times it cannot be concealed when drawn, nor can its light be shut off. Its wielder is protected from fire; the sword absorbs the first 10 points of fire damage each round that the wielder would otherwise take.

A frost brand extinguishes all nonmagical fires in its area. As a standard action, it can also dispel lasting fire spells, but not instantaneous effects, though you must succeed on a dispel check (1d20 +14) against each spell to dispel it. The DC to dispel such spells is 11 + the caster level of the fire spell.

Strong evocation; CL 14th; \feat{Craft Magic Arms and Armor}, \spell{ice storm}, \spell{dispel magic}, \spell{protection from energy}; Price 54,450 cp; Cost 27,350 cp and 5 bits + 2,179 XP.

% \textbf{Holy Avenger:} This \emph{+2 cold iron longsword} becomes a \emph{+5 holy cold iron longsword} in the hands of a paladin.

% It provides spell resistance of 5 + the paladin's level to the wielder and anyone adjacent to her. It also enables the wielder to use greater dispel magic (once per round as a standard action) at the class level of the paladin. (Only the area dispel is possible, not the targeted dispel or counterspell versions of greater dispel magic.)

% Strong abjuration; CL 18th; \feat{Craft Magic Arms and Armor}, holy aura, creator must be good; Price 120,630 cp; Cost 60,630 cp + 4,800 XP.

\textbf{Javelin of Lightning:} This javelin becomes a 5d6 \spell{lightning bolt} when thrown (Reflex DC 14 half). It is consumed in the attack.

Faint evocation; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{lightning bolt}; Price 1,500 cp; Cost 750 cp + 30 XP.

\textbf{Life-Drinker:} This \emph{+1 stone greataxe} is favored by undead and constructs, who do not suffer its drawback. A life-drinker bestows two negative levels on its target whenever it deals damage, just as if its target had been struck by an undead creature. One day after being struck, subjects must make a DC 16 Fortitude save for each negative level or lose a character level.

Each time a life-drinker deals damage to a foe, it also bestows one negative level on the wielder. Any negative level gained by the wielder in this fashion lasts for 1 hour.

Strong necromancy; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{enervation}; Price 40,310 cp; Cost 20,310 cp + 1,600 XP.

\textbf{Luck Blade:} This \emph{+2 wood short sword} gives its possessor a +1 luck bonus on all saving throws. Its possessor also gains the power of good fortune, usable once per day. This extraordinary ability allows its possessor to reroll one roll that she just made. She must take the result of the reroll, even if it's worse than the original roll. In addition, a \emph{luck blade} may contain up to three \emph{wishes} (when randomly rolled, a \emph{luck blade} holds 1d4-1 \emph{wishes}, minimum 0). When the last \emph{wish} is used, the sword remains a \emph{+2 short sword}, still grants the +1 luck bonus, and still grants its reroll power.

Strong evocation; CL 17th; \feat{Craft Magic Arms and Armor}, \spell{wish} or \spell{miracle}; Price 22,060 cp (0 \emph{wishes}), 62,360 cp (1 \emph{wish}), 102,660 cp (2 \emph{wishes}), 142,960 cp (3 \emph{wishes}); Cost 11,030 cp + 882 XP (0 \emph{wishes}), 31,180 cp + 2,494 XP (1 \emph{wish}); 51,330 cp + 4,106 XP (2 \emph{wishes}), 71,480 cp + 5,718 XP (3 \emph{wishes}).

\textbf{Mace of Smiting:} This \emph{+3 adamantine heavy mace} has a +5 enhancement bonus against constructs, and any critical hit dealt to a construct completely destroys it (no saving throw). A critical hit dealt to an outsider deals $\times4$ damage rather than $\times2$.

Moderate transmutation; CL 11th; \feat{Craft Magic Arms and Armor}, \spell{disintegrate}; Price 373,500 cp; Cost 337,500 cp + 2,880 XP.

\textbf{Mace of Terror:} On command, this \emph{+2 heavy mace} causes the wielder's clothes and appearance to transform into an illusion of darkest horror such that living creatures in a 9-meter cone become panicked as if by a \spell{fear} spell (Will DC 16 partial). They take a $-2$ morale penalty on saving throws, and they flee from the wielder. The wielder may use this ability up to three times per day.

Strong necromancy; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{fear}; Price 39,047 cp; Cost 19,771 cp + 1,542 XP.

\textbf{Masterwork Cold Iron Longsword:} This nonmagical longsword is crafted out of cold iron. As a masterwork weapon, it has a +1 enhancement bonus on attack rolls.

No aura (nonmagical); Price 1800 cp.

\textbf{Nine Lives Stealer:} This longsword always performs as a \emph{+2 bone longsword}, but it also has the power to draw the life force from an opponent. It can do this nine times before the ability is lost. At that point, the sword becomes a simple \emph{+2 bone longsword} (with a hint of evil about it). A critical hit must be dealt for the sword's death-dealing ability to function, and this weapon has no effect on creatures not subject to critical hits. The victim is entitled to a DC 20 Fortitude save to avoid death. If the save is successful, the sword's death-dealing ability does not function, no use of the ability is expended, and normal critical damage is determined. This sword is evil, and any good character attempting to wield it gains two negative levels. These negative levels remain as long as the sword is in hand and disappear when the sword is no longer wielded. These negative levels never result in actual level loss, but they cannot be overcome in any way (including restoration spells) while the sword is wielded.

Strong necromancy [evil]; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{finger of death}; Price 23,052 cp and 5 bits; Cost 11,536 cp + 922 XP.

\textbf{Oathbow:} Of elven make, this white \emph{+2 composite longbow} (+2 Str bonus) whispers ``Swift defeat to my enemies'' in Elven when nocked and pulled. Once per day, if the firer swears aloud to slay her target (a free action), the bow's whisper becomes the low shout ``Swift death to those who have wronged me.'' Against such a sworn enemy, the bow has a +5 enhancement bonus, and arrows launched from it deal an additional 2d6 points of damage (and $\times4$ on a critical hit instead of the normal $\times3$). However, the bow is treated as only a masterwork weapon against all foes other than the sworn enemy, and the wielder takes a $-1$ penalty on attack rolls with any weapon other than the oathbow. These bonuses and penalties last for seven days or until the sworn enemy is slain or destroyed by the wielder of the oathbow, whichever comes first.

The oathbow may only have one sworn enemy at a time. Once the wielder swears to slay a target, he cannot make a new oath until he has slain that target or seven days have passed. Even if the wielder slays the sworn enemy on the same day that he makes the oath, he cannot activate the oathbow's special power again until 24 hours have passed from the time he made the oath.

Strong evocation; CL 15th; \feat{Craft Magic Arms and Armor}, creator must be an elf; Price 25,600 cp; Cost 13,100 cp + 1,000 XP.

\textbf{Rapier of Puncturing:} Three times per day, this \emph{+2 wounding bone rapier} allows the wielder to make a touch attack with the weapon that deals 1d6 points of Constitution damage by draining blood. Creatures immune to critical hits are immune to the Constitution damage dealt by this weapon.

Strong necromancy; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{harm}; Price 50,310 cp; Cost 25,310 cp + 2,000 XP.

\textbf{Screaming Bolt:} One of these \emph{+2 bolts} screams when fired, forcing all enemies of the wielder within 20 feet of the path of the bolt to succeed on a DC 14 Will save or become shaken. This is a mind-affecting fear effect.

Faint enchantment; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{doom}; Price 267 cp; Cost 128 cp and 5 bits + 10 XP.

\textbf{Shatterspike:} Wielders without the \feat{Improved Sunder} feat use \emph{Shatterspike} as a \emph{+1 longsword} only; wielders with the \feat{Improved Sunder} feat add a +4 bonus (including the sword's +1 enhancement bonus) to the opposed roll when attempting to strike a foe's weapon. If successful, \emph{Shatterspike} deals 1d8+4 points of damage plus the wielder's Strength modifier to the target weapon (the target weapon's hardness must still be overcome with each hit). \emph{Shatterspike} can damage weapons with an enhancement bonus of +4 or lower.

Strong evocation; CL 13th; Str 13, \feat{Craft Magic Arms and Armor}, \feat{Power Attack}, \feat{Improved Sunder}, \spell{shatter}; Price 5,800 cp; Cost 3,800 cp + 160 XP; Weight 4 lb.

% Shifter's Sorrow
% This +1/+1 two-bladed sword has blades of alchemical silver. The weapon deals an extra 2d6 points of damage against any creature with the shapechanger subtype. When a shapechanger or a creature in an alternate form (such as a druid using wild shape) is struck by the weapon, it must make a DC 15 Will save or return to its natural form.

% Strong transmutation; CL 15th; Craft Arms and Armor, baleful polymorph; Price 12,780 cp; Cost 6,780 cp + 480 XP; Weight 10 lb.

\textbf{Silver Dagger, Masterwork:} This masterwork alchemical silver dagger is nonmagical. As a masterwork weapon, it has a +1 enhancement bonus on attack rolls.

No aura (nonmagical); Price 322 cp.

\textbf{Slaying Arrow:} This \emph{+1 arrow} is keyed to a particular type or subtype of creature. If it strikes such a creature, the target must make a DC 20 Fortitude save or die (or, in the case of unliving targets, be destroyed) instantly. Note that even creatures normally exempt from Fortitude saves (undead and constructs) are subject to this attack. When keyed to a living creature, this is a death effect (and thus death ward protects a target). To determine the type or subtype of creature the arrow is keyed to, roll on the table below.

A \emph{greater slaying arrow} functions just like a normal \emph{slaying arrow}, but the DC to avoid the death effect is 23.

Strong necromancy; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{finger of death} (\emph{slaying arrow}) or heightened 9th-level \spell{finger of death} (\emph{greater slaying arrow}); Price 2,282 cp (\emph{slaying arrow}) or 4,057 cp (\emph{greater slaying arrow}); Cost 1,144 cp 5 sp + 91 XP (\emph{slaying arrow}) or 2,032 cp + 162 XP (\emph{greater slaying arrow}).

% d%	Designated
% Type or Subtype	d%	Designated
% Type or Subtype	d%	Designated
% Type or Subtype
% 01-05	Aberrations	46	Humanoids, gnome	77	Outsiders, earth
% 06-09	Animals	47-49	Humanoids, goblinoid	78-80	Outsiders, evil
% 10-16	Constructs	50	Humanoids, halfling	81	Outsiders, fire
% 17-22	Dragons	51-54	Humanoids, human	82-84	Outsiders, good
% 23-27	Elementals	55-57	Humanoids, reptilian	85-87	Outsiders, lawful
% 28-32	Fey	58-60	Humanoids, orc	88	Outsiders, water
% 33-39	Giants	61-65	Magical beasts	89-90	Plants
% 40	Humanoids, aquatic	66-70	Monstrous humanoids	91-98	Undead
% 41-42	Humanoids, dwarf	71-72	Oozes	99-100	Vermin
% 43-44	Humanoids, elf	73	Outsiders, air		
% 45	Humanoids, gnoll	74-76	Outsiders, chaotic		

\textbf{Sleep Arrow:} This \emph{+1 arrow} is painted white and has white fletching. If it strikes a foe so that it would normally deal damage, it instead bursts into magical energy that deals nonlethal damage (in the same amount as would be lethal damage) and forces the target to make a DC 11 Will save or fall asleep.

Faint enchantment; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{sleep}; Price 132 cp; Cost 69 cp 5 bits + 5 XP.

\textbf{Sun Blade:} This sword is the size of a bastard sword. However, a \emph{sun blade} is wielded as if it were a short sword with respect to weight and ease of use. (In other words, the weapon appears to all viewers to be a bastard sword, and deals bastard sword damage, but the wielder feels and reacts as if the weapon were a short sword.) Any individual able to use either a bastard sword or a short sword with proficiency is proficient in the use of a \emph{sun blade}. Likewise, \feat{Weapon Focus} and \feat{Weapon Specialization} in short sword and bastard sword apply equally, but the benefits of those feats do not stack.

In normal combat, the glowing golden blade of the weapon is equal to a \emph{+2 bastard sword}. Against evil creatures, its enhancement bonus is +4. Against Negative Energy Plane creatures or undead creatures, the sword deals double damage (and $\times3$ on a critical hit instead of the usual $\times2$).

The blade also has a special \emph{sunlight} power. Once per day, the wielder can swing the blade vigorously above her head while speaking a command word. The \emph{sun blade} then sheds a bright yellow radiance that is like full daylight. The radiance begins shining in a 3-meter radius around the sword wielder and extends outward at 1.5 meter per round for 10 rounds thereafter, to create a globe of light with a 18-meter radius. When the wielder stops swinging, the radiance fades to a dim glow that persists for another minute before disappearing entirely. All \emph{sun blades} are of good alignment, and any evil creature attempting to wield one gains one negative level. The negative level remains as long as the sword is in hand and disappears when the sword is no longer wielded. This negative level never results in actual level loss, but it cannot be overcome in any way (including restoration spells) while the sword is wielded.

Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{daylight}, creator must be good; Price 53,800 cp; Cost 28,800 cp + 2,000 XP.

\textbf{Sword of Life Stealing:} This black iron \emph{+2 longsword} bestows a negative level when it deals a critical hit. The sword wielder gains 1d6 temporary hit points each time a negative level is bestowed on another. These temporary hit points last for 24 hours. One day after being struck, subjects must make a DC 16 Fortitude save for each negative level or lose a character level.

Strong necromancy; CL 17th; \feat{Craft Magic Arms and Armor}, \spell{enervation}; Price 27,200 cp; Cost 14,342 cp and 5 sp + 1,029 XP.

\textbf{Sword of the Planes:} This longsword has an enhancement bonus of +1 on the Material Plane, but on any Elemental Plane its enhancement bonus increases to +2. (The +2 enhancement bonus also applies on the Material Plane when the weapon is used against elementals.) It operates as a \emph{+3 longsword} on the Astral Plane or the Ethereal Plane or when used against opponents native to either of those planes. On any other plane, or against any outsider, it functions as a \emph{+4 longsword}.

Strong evocation; CL 15th; \feat{Craft Magic Arms and Armor}, \spell{plane shift}; Price 23,800 cp; Cost 12,642 cp and 5 sp + 893 XP.

\textbf{Sword of Subtlety:} A \emph{+1 short sword} with a thin, dull gray blade, this weapon provides a +4 bonus on its wielder's attack and damage rolls when he is making a sneak attack with it.

Moderate illusion; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{blur}; Price 23,300 cp; Cost 12,145 cp + 892 XP.

% Sylvan Scimitar
% This +3 scimitar, when used outdoors in a temperate climate, grants its wielder the use of the Cleave feat and deals an extra 1d6 points of damage.

% Moderate evocation; CL 11th; \feat{Craft Magic Arms and Armor}, divine power or creator must be a 7th-level druid; Price 47,315gp; Cost 23,657 cp and 5 sp + 1,893 XP.

% \textbf{Trident of Fish Command:} The magical properties of this +1 trident with a 6-foot-long haft enable its wielder to charm up to 14 HD of aquatic animals (Will DC 16 negates, animals get a +5 bonus if currently under attack by the wielder or his allies), no two of which can be more than 9 meters apart. The wielder can use this effect up to three times per day. The wielder can communicate with the animals as if using a speak with animals spell. Animals making their saving throw are free of control, but they will not approach within 10 feet of the trident. The trident can be used up to three times per day.

% Moderate enchantment; CL 7th; \feat{Craft Magic Arms and Armor}, speak with animals; Price 18,650 cp; Cost 9,325 cp + 746 XP.

% \textbf{Trident of Warning:} A weapon of this type enables its wielder to determine the location, depth, kind, and number of aquatic predators within 680 feet. A trident of warning must be grasped and pointed in order for the character using it to gain such information, and it requires 1 round to scan a hemisphere with a radius of 680 feet. The weapon is otherwise a +2 trident.

% Moderate divination; CL 7th; \feat{Craft Magic Arms and Armor}, locate creature; Price 10,115 cp; Cost 5,057 cp and 5 sp + 405 XP.