\subsubsection{Gorak}
\begin{MonsterStats}
{Small Animal}
{1d8+1 (5 hp)}
{+3}
{12 m (8 squares)}
{15 (+1 size, +3 Dex, +1 natural), touch 14, flat-footed 12}
{+0/$-5$}
{Claw +1 melee (1d4--1)}
{2 claws +1 melee (1d4--1) and bite --5 melee (1d4--1)}
{1.5 m/1.5 m}
{Hypnotism}
{Low-light vision}
{Fort +3, Ref +5, Will +0}
{Str 8, Dex 17, Con 13, Int 1, Wis 10, Cha 6}
{\skill{Listen} +2, \skill{Spot} +4}
{\feat{Weapon Focus} (claw)}
{Any waste}
{Herd (5--30)}
{\onehalf}
{None}
{Always neutral}
{2 HD}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Goraks are herd animals, used by many in the Tablelands as sources of food. Many herds roam free, while some have been domesticated. Quick and agile, goraks group together to attack prey. They are known for their good eyesight as well as their keen sense of smell. Domesticated herds have been known to number as many as 50 beasts but wild herds rarely boast more than 20 individuals because of the scarcity of food throughout most of Athas. The herd will be led by the largest male (known as the alpha), a position that comes under challenge frequently. If food becomes scarce for some reason, the alpha male culls the herd of other males.

    Herds do not accept goraks from outside the herd and attack and kill outsiders on first contact. Typically, goraks are 1 meter in length and weigh 75 kilograms. Their skin ranges in color from red-brown to sandy-beige and they have a colorful fanlike dorsal fin that they extend to cool their bodies in the hot Athasian sun. A second, less colorful fin surrounds their heads.
}

Goraks will group together to attack a single target, using their hypnotic trance to dazzle their prey while their sharp claws rip the target to shreds. When excited or threatened, goraks emit a loud hissing noise as a warning and extend their fins in an attempt to appear larger and more threatening. When extended, the patterns on the dorsal fin can induce a trance in the gorak‘s target.

\textbf{Hypnotism (Ex):} The gorak‘s colorful dorsal fin can mesmerize creatures. Each target must make a Will save (DC 10) or be affected as by the spell \spell{hypnotism}, except the duration is 1d4 rounds, and the number of Hit Dice affected is 2d4. The save DC is Wisdom-based.

\textbf{Skills:} Because of their unusually large eyes, goraks receive a +2 bonus to \skill{Spot} checks.
