\subsection{Cost and Maintenance}
All powers have a Cost line and a Maintenance Cost line, indicating the power's initial power point expenditure and the continuous cost.

The psionic character class tables show how many power points a character has access to each day, depending on level.

A power's cost and maintenance are determined by its level, as shown below. Every power's cost and maintenance are noted in its description for ease of reference.

\Table{Power Points by Power Level}{l *{9}{C}}
{
\textbf{Power Level} & 1st & 2nd & 3rd & 4th & 5th & 6th & 7th & 8th & 9th\\
% \textbf{Power Point Cost} & 1 & 3 & 5 & 7 & 9 & 11 & 13 & 15 & 17\\
\textbf{Power Point Cost} & 5 & 10 & 15 & 20 & 25 & 30 & 35 & 40 & 45\\
\textbf{Power Point Maintenance} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9\\
}

A power lasts for as long as the manifester pays its maintenance cost. Maintenance cost is spent at the beginning of the manifester's turn. The first time interval is already paid with the initial cost. If the manifester doesn't pay the maintenance cost, the power ceases to function harmlessly. Some powers have maintenance cost in minutes and hours, indicating how many power points the manifester must spend for each minute and hour, respectively.

\textbf{None (Instantaneous):} Powers without maintenance cost happens instantaneously. The psionic energy comes and goes the instant the power is manifested, though the consequences might be long-lasting.

% \textbf{Power Point Limit:} Some powers allow you to spend more than their base cost to achieve an improved effect, or augment the power. The maximum number of points you can spend on a power (for any reason) is equal to your manifester level.

\textbf{XP Cost (XP):} On the same line that the power point cost of a power is indicated, the power's experience point cost, if any, is noted. Particularly powerful effects entail an experience point cost to you. No spell or power can restore XP lost in this manner. You cannot spend so much XP that you lose a level, so you cannot manifest a power with an XP cost unless you have enough XP to spare. However, you can, on gaining enough XP to attain a new level, use those XP for manifesting a power rather than keeping them and advancing a level. The XP are expended when you manifest the power, whether or not the manifestation succeeds.