\subsection{Display}
When a power is manifested, a display may accompany the primary effect. This secondary effect may be auditory, material, mental, olfactory, or visual. No power's display is significant enough to create consequences for the psionic creatures, allies, or opponents during combat. The secondary effect for a power occurs only if the power's description indicates it. If multiple powers with similar displays are in effect simultaneously, the displays do not necessary become more intense. Instead, the overall display remains much the same, though with minute spikes in intensity. A \skill{Psicraft} check (DC 10 + 1 per additional power in use) reveals the exact number of simultaneous powers in play.

\textbf{Dispense with Displays:} Despite the fact that almost every power has a display, a psionic character can always choose to manifest the power without the flashy accompaniment. To manifest a power without any display (no matter how many displays it might have), a manifester must make a \skill{Concentration} check (DC 15 + the level of the power). This check is part of the action of manifesting the power. If the check is unsuccessful, the power manifests normally with its display.

Even if a manifester manifests a power without a display, he is still subject to attacks of opportunity in appropriate circumstances. (Of course, another \skill{Concentration} check can be made as normal to either manifest defensively or maintain the power if attacked.)

\textit{Auditory:} A bass-pitched hum issues from the manifester's vicinity or in the vicinity of the power's subject (manifester's choice), eerily akin to many deep-pitched voices. The sound grows in a second from hardly noticeable to as loud as a shout strident enough to be heard within 30 meters. At the manifester's option, the instantaneous sound can be so soft that it can be heard only within 4.5 meters with a successful DC 10 \skill{Listen} check. Some powers describe unique auditory displays.

\textit{Material:} The subject or the area is briefly slicked with a translucent, shimmering substance. The glistening substance evaporates after 1 round regardless of the power's duration. Sophisticated psions recognize the material as ectoplasmic seepage from the Astral Plane; this substance is completely inert.

\textit{Mental:} A subtle chime rings once in the minds of creatures within 4.5 meters of either the manifester or the subject (at the manifester's option). At the manifester's option, the chime can ring continuously for the power's duration. Some powers describe unique mental displays.

\textit{Olfactory:} An odd but familiar odor brings to mind a brief mental flash of a long-buried memory. The scent is difficult to pin down, and no two individuals ever describe it the same way. The odor originates from the manifester and spreads to a distance of 6 meters, then fades in less than a second (or lasts for the duration, at the manifester's option).

\textit{Visual:} The manifester's eyes burn like points of silver fire while the power remains in effect. A rainbow-flash of light sweeps away from the manifester to a distance of 1.5 meter and then dissipates, unless a unique visual display is described. This is the case when the Display entry includes ``see text,'' which means that a visual effect is described somewhere in the text of the power.