\subsection{Duration}
A power's Duration line tells you how long the psionic energy of the power lasts.

Timed Durations: Many durations are measured in rounds, minutes, hours, or some other increment. When the time is up, the psionic energy sustaining the effect fades, and the power ends. If a power's duration is variable it is rolled secretly.

\textbf{Instantaneous:} The psionic energy comes and goes the instant the power is manifested, though the consequences might be long-lasting.

\textbf{Permanent:} The energy remains as long as the effect does. This means the power is vulnerable to dispel psionics.

\textbf{Concentration:} The power lasts as long as you concentrate on it. Concentrating to maintain a power is a standard action that does not provoke attacks of opportunity. Anything that could break your concentration when manifesting a power can also break your concentration while you're maintaining one, causing the power to end. You can't manifest a power while concentrating on another one. Some powers may last for a short time after you cease concentrating. In such a case, the power keeps going for the given length of time after you stop concentrating, but no longer. Otherwise, you must concentrate to maintain the power, but you can't maintain it for more than a stated duration in any event. If a target moves out of range, the power reacts as if your concentration had been broken.

\textbf{Subjects, Effects, and Areas:} If the power affects creatures directly the result travels with the subjects for the power's duration. If the power creates an effect, the effect lasts for the duration. The effect might move or remain still. Such an effect can be destroyed prior to when its duration ends. If the power affects an area then the power stays with that area for its duration. Creatures become subject to the power when they enter the area and are no longer subject to it when they leave.

\textbf{Touch Powers and Holding the Charge:} In most cases, if you don't discharge a touch power on the round you manifest it, you can hold the charge (postpone the discharge of the power) indefinitely. You can make touch attacks round after round. If you touch anything with your hand while holding a charge, the power discharges. If you manifest another power, the touch power dissipates.

Some touch powers allow you to touch multiple targets as part of the power. You can't hold the charge of such a power; you must touch all the targets of the power in the same round that you finish manifesting the power. You can touch one friend (or yourself) as a standard action or as many as six friends as a full round action.

\textbf{Discharge:} Occasionally a power lasts for a set duration or until triggered or discharged.

\textbf{(D) Dismissible:} If the Duration line ends with ``(D),'' you can dismiss the power at will. You must be within range of the power's effect and must mentally will the dismissal, which causes the same display as when you first manifested the power. Dismissing a power is a standard action that does not provoke attacks of opportunity. A power that depends on concentration is dismissible by its very nature, and dismissing it does not take an action or cause a display, since all you have to do to end the power is to stop concentrating on your turn.