\section{Dynastic Merchant Houses}

\textbf{Entry Requirements:} \skill{Appraise} 3 ranks, \skill{Diplomacy} 5 ranks, \skill{Gather Information} 5 ranks, \skill{Sense Motive} 5 ranks; accept the Merchants' Code (see below).

It would be a terrible mistake to assume that all power on Athas rests in the hands of the sorcerer-kings. Power can be held in many ways, and many hands besides those of the cities' rulers may possess it.

The merchant houses supply the lifeblood of Athas---foodstuffs that feed isolated city‐states, construction materials to build the palaces of sorcerer-kings and decadent nobles, slaves to toil in fields or fight and die in gladiator pits, and many other vital items.

\subsubsection{Merchants' Code}
All mercantile houses follow a strict code of behavior, known as the Merchants' Code. Anyone wishing to join a merchant house must accept all aspects of this code and abide by them or face immediate expulsion. The code varies from house to house, but in most cases it conforms to the following principles:

\begin{enumerate*}
\item Recognition that by joining a merchant house, an agent forsakes citizenship in any city or membership in any tribe.
\item An oath of allegiance to the merchant house.
\item A promise to perform in the best interests of the merchant house in return for a salary.
\item A promise to deal honestly with stranger, friend, and foe alike.
\item A promise not to flaunt any wealth gained through employment with the house.
\item A promise to uphold the laws of the city in which the agent is stationed, and to do nothing to bring down the wrath of the sorcerer-king or his agents upon the house.
\item A promise to cooperate with other merchants to make life very expensive for any person who unjustly imprisons, blackmails, or otherwise harasses any merchant.
\end{enumerate*}

\subsubsection{Dynastic Merchant Houses Benefits}
Being a member of any merchant house gives access to some common benefits.

\textbf{Economics:} Agents of a Merchant House may buy their House's specialty goods for 80\% of their listed market price.

\textbf{Services:} Merchant Houses often acquire hirelings for their caravans. Agents may get access to experts among the hirelings to appraise, disguise, and negotiate. These experts have a relevant skill modifier of +10. Experts with modifiers of +15 or higher are also available at half the price.

\textbf{Information:} Checking with the leader of the local headquarters is equivalent to a \skill{Gather Information} check on the PCs' behalf. A typical House local leader has a \skill{Gather Information} modifier of +15.

\textbf{Access:} Agents have access to a place to stay in each city-state, and in each of the House's facilities.

\subsubsection{Dynastic Merchant Houses in the Game}
Senior members of a Merchant House make good patrons and allies. They might seek to hire the PCs for almost any kind of mission or even recruit them if they display useful skills. As a twist, you can use a templar to send the PCs on various missions, revealing only later (or not at all) that the PCs' contact is actually an undercover agent from a Merchant House. Allow the PCs to take advantage of the hirelings, special transportations, and other perks of joining a Merchant House. Over time, introduce the costs associated with those advantages: internal and interhouse rivalries, political machinations, and the feeling of being just a small cog in a vast economic enterprise.

\input{subsections/organizations/dynastic-merchant-houses/house-inika.tex}
\input{subsections/organizations/dynastic-merchant-houses/house-m-ke.tex}
\input{subsections/organizations/dynastic-merchant-houses/house-shom.tex}

\subsection{House Stel}
\subsection{House Tsalaxa}
\subsection{House Vordon}
\subsection{House Wavir}