\section{Elvish Tribes}

\textbf{Entry Requirements:} Must be an elf.

Elvish tribes are notoriously nomads, typically running as a group towards new grounds to hunt, trade, or raid. Outsiders often view their culture as savage and barbaric. They don't use any type of mount, as elves reject the idea of depending on others for transportation. The tribe takes care of one as long as they can keep up with the tribe, otherwise they are left behind.

\subsubsection{Elvish Tribes Benefits}
\textbf{Economics:} Elvish merchants are willing to go one step lower when bargaining (see \skill{Diplomacy}) when selling goods to fellow tribe members.

\textbf{Services:} With the exception of basic needs, services are always paid and tribe members do not get a discount. All elvish tribes have access to merchants, scouts, and thieves. Some tribes may have access to more specific experts.

\textbf{Information:} All tribes excel with their information network, since they are nomads with very little military power. Being a member of the tribe gives access to part of these secrets. Elvish sages have a \skill{Knowledge} modifier of +15, or a \skill{Gather Information} modifier of +20.

\textbf{Access:} Most tribes are nomads, so tribe members will always have protection and every basic need covered while traveling with the tribe.

\subsubsection{Elvish Tribes in the Game}
There are two major types of elvish tribes: minor merchant houses and herdsmen. Minor merchant houses might hire the PCs for protection, but they do not have the wealth required for riskier tasks. Their main quests are spying on other houses. Herdsmen interact mostly with the natural dangers of the wasteland and the occasional merchant house with which they trade livestock and its derivatives.

There are exceptions for these types: the Silver Hands who control a fixed settlement, and the Shadows who are mostly assassins for hire.

\subsection{Clearwater Tribe}
\textbf{Area of Operation:} The whole Tablelands, with a permanent market in Tyr.

\textbf{Tribe Size:} Around 5,000 split between a dozen clans.

The Clearwaters are traders first and foremost, but they choose well what they sell. Even though their merchandise vary as much as their customers, from ordinary items to magical items, they are known to sell shoddy items to those they fell deserve it. Contraband (e.g., books and spell components) is sold only under the most secure conditions, after the tribe's many troubles with templars.

\subsubsection{Brief History}
These elves claim their tribe comes from the Blue Age, but their appearance in the Tablelands is dated to 800 years ago, from west of the Ringing Mountains. First established a market near Tyr, where they were successful in avoid direct confrontation with the city's templars. Later, they ventured south to Gulg, where they were not as successful, vanishing from the city for many years.

After almost a hundred years missing, the Clearwater tribe has returned to roaming the Tablelands, stopping occasionally near any settlement loaded with valuable goods and spell components.

\subsubsection{Clearwater Tribe in Athas}
After a devastating battle against the gith from the Mekillot Mountains during the tribe's exploration of the Tablelands, they found an unlikely alliance with the dwarves from North Ledopolus. The Clearwaters have settled near the dwarven village and started trading with them, starting their close relationship that continues to this day as some dwarves still travel with the tribe to sell their stonework and weapons.

The Clearwaters have a mixed relationship with city-states. They have had trouble with Gulg in the past, but started trading in the city again after the current high templar reached its current status. Even with all their caution, there still was trouble with Draj recently---two Clearwater warriors were found dead. As a result, the Clearwater are avoiding the city-state.

The Clearwaters maintain a permanent market in the city-state of Tyr, close to the city's center. Popular wisdom says that anything that can be bought is found in the city's Elven Market, which is closer to the truth than the city-state's templars are willing to admit.

\subsubsection{Clearwater Tribe Society}
The Clearwaters are divided between twelve clans, who have distinct roles within the tribe. This is reflected in the rarity of interclan marriage. The resulting children from such marriages choose which of the clans they wish to join by the age of ten.

Clearwater chiefs are chosen among the clan elders. These chiefs are absolute only in battle, when orders are obeyed instantly and to the letter. In peacetime, chiefs have the clan elders as advisers and act only on consensus.

% \subsubsection{Clearwater Tribe Clans}
% The Clearwaters are split among twelve clans, each with their own culture and trade specialties.

% \textbf{Fireshapers:} Spellcasting clan, with mainly wizards and clerics. The ten highest-ranking warriors fight with ancient steel \emph{flame tongue} sword, while the highest-ranking warrior bears the sacred \emph{sun sword}---the clan's most. The dwarven hero Tolkas of Ledopolus wields a \emph{flame tongue}, but neither he or the Fireshapers say what he did to deserve it.

% Fireshapers sell weapons, fine clothing, and spell components.

% \textbf{Graffyons:} Warrior house, with many elite fighters. By tradition, the Graffyons do not cast spells---any clan member who shows this capability is allowed to join another clan to better nurture their skill.

% Graffyons trade in weapons and mounts.

% \textbf{Graystars:} They serve as wasteland scouts for the Clearwater tribe. They only spend short periods of time with the tribe, before wandering into the desert again. While in the desert, they occasionally raid caravans or other elvish tribes.

% Graystars sell survival gear made from animals they hunted, or booty gathered in the desert.

% \textbf{Lightning:} Spellcasting clan specialized in weather and earth spells. They rarely use weapons, preferring magic items for protection or wands for aggression. The clan has a single \emph{rod of wonder}, which they hold in similar fashion as the Fireshapers' \emph{sun sword}.

% The Lightning clan trade in spell components and magic items.

% \textbf{Onyx:} The stealth branch of the tribe, serving as spies and assassins for the Clearwaters. Clan members are known for their magical onyx daggers, which are used for special missions.

% Onyx trade only on the black market.

% \textbf{Sandrunners:} Urban scouts and minstrels. They are a constant presence at Clearwater feasts and celebrations, even performed before sorcerer-kings on rare occasions.

% Sandrunners trade in jewelry, wines, and musical instruments. Magical instruments are also sold by the clan, although some customers claim that their magic ceases as soon as the tribe leaves the area.

% \textbf{Silverleaves:} Bureaucratic house, with mostly traders and accountants. Their manifesters and spellcasters are trained in detection and stealth, as they guard the elven market.

% Silverleaves are the most skilled merchants of the tribe. They deal in virtually any item, licit or illicit.

% \textbf{Songweavers:} Artisan house, they are the most skilled crafters of the Clearwaters. Songweavers design and produce their own armor, weapons, and magical items. Their art always fetches high prices, since all their craft is considered masterwork.

% Songweavers trade in artwork, fine jewelry, clothing. Many items are magical besides being masterworks.

% \textbf{Steeljaw:} Blacksmith clan, they supply the tribe with weapons and armor. All members of this clan are combat-oriented, even spellcasters and manifesters.

% Steeljaws rarely trade with outsiders.

% \textbf{Wavedivers:} Spellcasting clan specialized in water spells. Wavediver clerics create water for the tribe when supplies run low.

% Wavedivers sell water and magical items to find it.

% \textbf{Windriders:}

\subsection{Night Runners}
\textbf{Area of Operation:}

\subsection{Shadows}
\subsection{Silt Stalkers}
\subsection{Silver Hands}
\subsection{Sky Singers}
\subsection{Swiftwing Tribe}
\subsection{Water Hunters}
\subsection{Wind Dancers}
