\section{Veiled Alliance}

\textbf{Entry Requirements:} Must be non-evil; wizards must be preservers; vow fulfillment of the duties:
\begin{itemize*}
	\item Obey the Five Aims (see below).
	\item Obey Council's orders.
	\item Hold regular meetings in different locations.
	\item Cautiously seek new members.
	\item Never resign, and enforce requital on those who do.
\end{itemize*}

The Veiled Alliance serves as a secret support network to help preservers survive across Athas, no matter their enemies. They help any preserver, not only members of the Alliance.

\textbf{The Green Test:} In order to accept wizards as members, they must cast an arcane spell in a verdant environment without destroying the plant matter around them.



\subsubsection{The Five Aims}
The Five Aims have a rank of priority, listed below.

\begin{enumerate*}
	\item \textbf{Protect the Alliance:} This usually means ``keep it a secret,'' since that is the way that kept the Alliance alive all these years. 
	\item \textbf{Protect Preservers:} The oldest aim of the Alliance. Even non-members should be protected.
	\item \textbf{Protect Auxiliaries:} Those who help the Alliance but don't have arcane capabilities must also be protected.
	\item \textbf{Oppose Defilers:} The Alliance is practical about this, as defilers compete for land, spell components, and magical treasure.
	\item \textbf{Undermine the Sorcerer-Kings:} The sorcerer-kings are the only ones with enough power and will to eradicate the Alliance.
\end{enumerate*}



\subsubsection{Veiled Alliance Benefits}
Being a member of the Veiled Alliance gives access to some common benefits.

\textbf{Economics:} Preservers can find any material component if they wait long enough. Magical weapons and armor are often sold at a 10\% discount for members.

\textbf{Services:} The Veiled Alliance offers a number of services to help preservers in danger: hideaways, non-magical transportation, forgery of new identities, training novice preservers, rescue of imprisoned preservers or auxiliaries.

\textbf{Information:} Even though they are not often around, asking for information from senior members is equivalent to a \skill{Knowledge} check on the PCs' behalf. A senior member has a \skill{Knowledge} modifier of +20, but it may take days for the request to get through the Alliance's network.

\textbf{Access:} Members of the Veiled Alliance have access to a place to stay in each city-state, and in each of the Alliance's headquarters.



\subsubsection{Veiled Alliance in the Game}
The Veiled Alliance usually is the one to initiate contact with the PCs, a fact that helps to conceal the existence of the organization, even if characters have previously explored UnderTyr, Magehome, or any other location where Veiled Alliance member are expected to be encountered.

Being a part of a Veiled Alliance chapter offers great opportunities for adventure. The more missions the PCs undertake, the greater their prominence, allowing them to make important decisions and perhaps eventually rise to a position of leadership.



\subsection{Structure}
The Veiled Alliance is an acephalous ecoterrorist group. Instead of a single-minded group across Athas, each city-state holds a different Alliance (usually called \emph{chapter}). Those groups do not cooperate, nor do they share leaders. Each chapter may have their own goals, but all pledged allegiance the Five Aims.

Within each city-state, its chapter is structured with a overseeing Council, that acts as a central leadership, and several cells, with little knowledge of the bigger scope of the organization. This way, no member outside the Council can betray much under interrogation.

\textbf{The Council:} The Council is composed of one leader and three lieutenants. Leaders of the Council are usually members from the high society. They hold both huge arcane power and huge influential power. All members of the city's Alliance pay close attention to their usual pronouncements. Their orders are sent down to all cells. Each lieutenant is in charge of a branch of cells. While they have autonomy in their own cells operations, the leader's orders are final.

\textbf{The Cells:} Each cell is composed of 3--6 members, occasionally more. They receive a rank depending on how many steps a Council message takes to reach, i.e. a first-rank cell is directly linked to the Council, while a second-rank cell receives the messages from a first-rank cell. They are linked to a higher rank via a regular contact and to another cell of the same rank with an emergency contact. The members who hold contact to their higher rank do not necessarily lead the cells, as cells have autonomy for their internal affairs. 



\subsection{Methods}
The Veiled Alliance has two major common enemies: defilers and sorcerer-kings. They use different tactics for each of those.

\textbf{Defilers:} When it comes to defilers, the Veiled Alliance uses one of the following tactics:
\begin{enumerate*}
	\item \textit{Whispering Campaigns:} The Alliance uses the common hatred of wizards towards specific defilers, whom they expose through rumors, hoping that the mob will do its justice.
	\item \textit{Theft:} One of their preferred ways of dealing with defilers, they steal their magical items and spellbooks.
	\item \textit{Vandalism:} When they can't steal, they destroy a defiler's lair.
	\item \textit{Conversion:} If a defiler is at the beginning of their career, the wisest Alliance members lure the defiler to the wilderness in hopes of converting his heart to preserving.
	\item \textit{Ambush:} Powerful defilers sometimes are taken down by luring them into a prepared location.
	\item \textit{Duel:} Lawful members challenge those powerful defilers on a duel to the death. Defilers who refuse the challenge become fair game for ambush.
\end{enumerate*}

\textbf{Sorcerer-Kings:} The Veiled Alliance is still in war against the sorcerer-kings and their templars, and they use the following fighting methods:
\begin{enumerate*}
	\item \textit{Propaganda:} Rumors of slave uprisings, betrayed templars, and covert resistance.
	\item \textit{Sabotage:} Shipments missing, templar headquarters collapsing, slave pits gates unlocking.
	\item \textit{Betrayal:} Revealing important state secrets to their enemies, such as army deployments on hostile territory.
\end{enumerate*}



\subsection{Chapters}
Each city-state chapter has its own idiosyncrasies, summarized below.


\subsubsection{Balic}
\textbf{Chapter Age:} About 100 years old.

\textbf{Contact:} Theatrical performances at the various amphitheaters around.

\textbf{Initiation:} After the "Green Test", candidate-wizards must do a mission that hurts Andropinis, however little.

\textbf{Headquarters:} Villa of Zaethus Nauripides, near the city gate.

Balikites honor the city's tradition of voting, by running elections every three years for the chapter's leader and lieutenants and every member votes, no matter the cell. For the last four elections, the Balic's Alliance voted for Ramphion, a bard, as their leader. Son of a templar reformer who died because of the many hateful edicts he repealed, his father's death moved him to create an award-winning drama called Hero's Burial. He was recruited by the Veiled Alliance soon after the play's win.


\subsubsection{Draj}
\textbf{Chapter Age:} About 65 years old.

\textbf{Contact:} A tent selling spell components, in the market near the Two Moon City.

\textbf{Initiation:} After the "Green Test", candidate-wizards must do a rescue mission for preservers and auxiliaries kept in the Draji detention pens.

\textbf{Headquarters:} Beneath the shell of Tectuktitlay's Temple of Two Moons, in an ancient forgotten pyramid.

The late leader (and founder) of the chapter, Diatlaxi, was austere and no member has satisfied his stringent tests of morality. Some of his austerity is deep into the chapter's culture: unlike the other chapters, the Draji Alliance leave any defiler's corpse in the open, as an example. Being the youngest chapter, their plots against templars and the sorcerer-king are still crude. While they successfully promoted rivalries among the templars, most of those would probably have occurred anyway.


\subsubsection{Gulg}
\textbf{Chapter Age:} About 200 years old.

\textbf{Contact:} Wait at a spell component harvesting points in the forest, or a suspicious house with concealed wards and glyphs. Bring a token gift.

\textbf{Initiation:} After the "Green Test", candidate-wizards must hunt the member who recruited them.

\textbf{Headquarters:} Inside a dead baobab tree, within an unnamed Queen's Grove guarded by a thri-kreen druid.

Gulg's chapter does not see the city-state's sorcerer-queen as a great danger, but as a benevolent dictator. The number of defilers in the Gulg was greatly reduced by Nibenay's crusade against them. Because of these factors, the goal of the Alliance in Gulg is to restore Athas to its former verdant glory. This has caused other chapters, specially Raam's, to think of them as cowards. Raam's rivalry goes back to its foundation, since they were both founded by the same Clennay the Impetuous.


\subsubsection{Nibenay}
\textbf{Chapter Age:} 300--350 years old.

\textbf{Contact:} In dance festivals, the Veiled Alliance has members observing the defilers who cast the illusions.

\textbf{Initiation:} After the "Green Test", candidate-wizards must either retrieve magical items from known defilers or learn anything on a templar from Naggaramakam.

\textbf{Headquarters:} Beneath an area of rolling hills, about 800 meters north of the city, adjacent to the Plain of Burning Water.

The Nibanese chapter finds the Shadow King virtually impossible to fight, but their opposition to defilers has become true fanaticism---they regard defilers as an offense against the universe. They developed its particular hatred of defilers after Thagya Phon rose to leadership 20 years ago. When he returned from a desert sojourn with his family, he told the Alliance a defiler's tribe attacked them and killed his wife. Since then, the Alliance has achieved significant success in its crusade.


\subsubsection{Raam}
\textbf{Chapter Age:} About 200 years old.

\textbf{Contact:} Ask for a job as corpse hauler, at the crematory in the city's outskirts.

\textbf{Initiation:} After the "Green Test", lower-leveled candidate-wizards must retrieve unusual spell components or expose the identity of a previously unknown kuotagha. High-leveled candidates must retrieve a completely new spell for the chapter, without help from anyone in the Alliance.

\textbf{Headquarters:} The underground of the city's crematory.

Raamite chapter has completely restructured its internal organization under the current leadership of Nanda Shatri. The chapter holds a military hierarchy with the chapter's leader as their Commander. The council is effectively formed by the Commander, the Sub-Commander, and the Secretary. Below them, there are four Sectorates, responsible for each corner of the city. Sectorates command five officers (for research, security, finance, training, and information), and each officer commands a varying number of lieutenants.

With the money that the crematory generates, which is owned by Shatri, the Alliance has increased its influence at every level of the government (mostly through bribes). They also allocate resources for spell research---as Shatri wants to learn the spell to become an avangion (see \chapref{Epic Levels}).


\subsubsection{Tyr}
\textbf{Chapter Age:} 400--500 years old.

\textbf{Contact:} Drunken Giant wine shop, at the Elven Market.

\textbf{Initiation:} After the "Green Test", candidate-wizards must go to UnderTyr and enter an ancient temple guarded by ``crimson knights'', who turn evil-doers back.

\textbf{Headquarters:} The marble ruin of Kalla-Kouro, in the northwest Warrens.

Tyr's chapter is the oldest chapter in the Veiled Alliance, and during the King Kalak's reign survival was their most notable success. This survival was greatly influenced by the 300 years of leadership of Acritus the Transmuter. He diligently followed the Five Aims and the requital. Having such a long livespan, Acritus has many legends around his name: some say he studied psionics with Kalak himself, which would explain his keen understanding of the late king's mentality; others say Acritus \spellref{polymorph}{polymorphed} a volunteer or prisoner on two different occasions to escape death; another legend tells that a dynasty of wizards have used the Acritus name after the original died after a normal lifespan.


\subsubsection{Urik}
\textbf{Chapter Age:} 400--500 years old.

\textbf{Contact:} At the Three Sisters Observatory, or in the Potter's Court.

\textbf{Initiation:} After the "Green Test", candidate-wizards must either answer a series of questions to assess their ability to reason (Leoricius' faction), or do a task with an unexpected problem (i.e. deliver an item to someone who will not appear) to assess their ability to think quickly (Thania's faction).

\textbf{Headquarters:} Three Sisters Observatory, and a small shop in the Potter's Court.

After Hamanu's merciless hunt of the Alliance, Morlak restored the Urikite chapter and focused them to overthrow the sorcerer-king. But, after his disappearance, the Alliance has split into two factions. His bodyguard, Leoricius, leads one of the factions over the Observatory, maintaining Morlak's goal. Thania, the half-elf, accused him of murdering Morlak, and now leads the other faction from the Potter's Court, with the goal of remaining out of Hamanu's sight and focusing on covert actions.

