\subsection{Creating Staffs}
To create a magic staff, a character needs a supply of materials, the most obvious being a staff or the pieces of the staff to be assembled.

The cost for the materials is subsumed in the cost for creating the staff---375 gp $\times$ the level of the highest-level spell $\times$ the level of the caster, plus 75\% of the value of the next most costly ability (281.25 gp $\times$ the level of the spell $\times$ the level of the caster), plus one-half of the value of any other abilities (187.5 gp $\times$ the level of the spell $\times$ the level of the caster). Staffs are always fully charged (50 charges) when created.

If desired, a spell can be placed into the staff at only half the normal cost, but then activating that particular spell costs 2 charges from the staff. The caster level of all spells in a staff must be the same, and no staff can have a caster level of less than 8th, even if all the spells in the staff are low-level spells.

The creator must have prepared the spells to be stored (or must know the spell, in the case of a templar) and must provide any focus the spells require as well as material and XP component costs sufficient to activate the spell a maximum number of times (50 divided by the number of charges one use of the spell expends). This is in addition to the XP cost for making the staff itself. Material components are consumed when he begins working, but focuses are not. (A focus used in creating a staff can be reused.) The act of working on the staff triggers the prepared spells, making them unavailable for casting during each day of the staff's creation. (That is, those spell slots are expended from his currently prepared spells, just as if they had been cast.)

Creating a few staffs may entail other prerequisites beyond spellcasting. See the individual descriptions for details.

Crafting a staff requires one day for each 1,000 gp of the base price.

\textbf{Item Creation Feat Required:} \feat{Craft Staff}.
