\subsection{Creating Magic Weapons}
To create a magic weapon, a character needs a heat source and some iron, wood, or leatherworking tools. She also needs a supply of materials, the most obvious being the weapon or the pieces of the weapon to be assembled. Only a masterwork weapon can become a magic weapon, and the masterwork cost is added to the total cost to determine final market value. Additional magic supplies costs for the materials are subsumed in the cost for creating the magic weapon---half the base price given on Table: Weapons, according to the weapon's total effective bonus.

Creating a magic weapon has a special prerequisite: The creator's caster level must be at least three times the enhancement bonus of the weapon. If an item has both an enhancement bonus and a special ability the higher of the two caster level requirements must be met.

A magic weapon must have at least a +1 enhancement bonus to have any of the abilities listed on Table: Melee Weapon Special Abilities or Table: Ranged Weapon Special Abilities.

If spells are involved in the prerequisites for making the weapon, the creator must have prepared the spells to be cast (or must know the spells, in the case of a templar) but need not provide any material components or focuses the spells require, nor are any XP costs inherent in a prerequisite spell incurred in the creation of the item. The act of working on the weapon triggers the prepared spells, making them unavailable for casting during each day of the weapon's creation. (That is, those spell slots are expended from his currently prepared spells, just as if they had been cast.)

At the time of creation, the creator must decide if the weapon glows or not as a side-effect of the magic imbued within it. This decision does not affect the price or the creation time, but once the item is finished, the decision is binding.

Creating magic double-headed weapons is treated as creating two weapons when determining cost, time, XP, and special abilities.

Creating some weapons may entail other prerequisites beyond or other than spellcasting. See the individual descriptions for details.

Crafting a magic weapon requires one day for each 1,000 gp value of the base price.

\textbf{Item Creation Feat Required:} \feat{Craft Magic Arms and Armor}.
