\subsection{Creating Potions}
The creator of a potion needs a level working surface and at least a few containers in which to mix liquids, as well as a source of heat to boil the brew. In addition, he needs ingredients. The costs for materials and ingredients are subsumed in the cost for brewing the potion---25 gp $\times$ the level of the spell $\times$ the level of the caster.

All ingredients and materials used to brew a potion must be fresh and unused. The character must pay the full cost for brewing each potion. (Economies of scale do not apply.)

The imbiber of the potion is both the caster and the target. Spells with a range of personal cannot be made into potions.

The creator must have prepared the spell to be placed in the potion (or must know the spell, in the case of a templar) and must provide any material component or focus the spell requires.

If casting the spell would reduce the caster's XP total, he pays the XP cost upon beginning the brew in addition to the XP cost for making the potion itself. Material components are consumed when he begins working, but a focus is not. (A focus used in brewing a potion can be reused.) The act of brewing triggers the prepared spell, making it unavailable for casting until the character has rested and regained spells. (That is, that spell slot is expended from his currently prepared spells, just as if it had been cast.) Brewing a potion requires one day.

\textbf{Item Creation Feat Required:} \feat{Brew Potion}.

\Table{Potion Base Prices (By Brewer's Class)}{c*3C}{
  \tableheader Spell Level
& \tableheader Clr, Drd, Wiz
& \tableheader Tmp
& \tableheader Rgr\footnotemark[1] \\
0   & 25 gp  & 25 gp  & --- \\
1st & 50 gp  & 50 gp  & 100 gp \\
2nd & 300 gp & 400 gp & 400 gp \\
3rd & 750 gp & 900 gp & 750 gp \\
\TableNote{4}{1 Caster level is half class level.}\\
\TableNote{4}{Prices assume that the potion was made at the minimum caster level.}\\
}


\Table{Base Cost to Brew a Potion (By Brewer's Class)}{c*3C}{
  \tableheader Spell Level
& \tableheader Clr, Drd, Wiz
& \tableheader Tmp
& \tableheader Rgr\footnotemark[1] \\

0   & 12 gp 5 sp +1 XP & 12 gp 5 sp +1 XP & --- \\
1st & 25 gp +2 XP      & 25 gp +2 XP      & 50 gp +4 XP \\
2nd & 150 gp +12 XP    & 200 gp +16 XP    & 200 gp +16 XP \\
3rd & 375 gp +30 XP    & 450 gp +36 XP    & 375 gp +30 XP \\

\TableNote{4}{1 Caster level is half class level.}\\
\TableNote{4}{Costs assume that the creator makes the potion at the minimum caster level.}\\
}
