\subsectionA{Elemental Plane of Water}
The Elemental Plane of Water is a sea of green and blue. Lacking a floor or a surface, it is an entirely fluid environment lit by a diffuse glow. It is one of the more hospitable of the Elemental Planes once a traveler figures out how to breathe.

The eternal oceans of this plane vary between ice cold and boiling hot, between saline and fresh. The water is constantly in motion, wracked by currents and tides. The plane's permanent settlements form around bits of coral and other drifting things suspended within this endless liquid. These settlements drift on the tides of the Elemental Plane of Water.

Armies of the Elemental Plane of Water are strange and surprisingly plentiful. Within the waves that are water elementals ride fearsome aquatic creatures, from sharks to kraken. The armies of the plane are aware when an intruder lurks, and if one is injured in battle, the scent of blood will travel for miles, attracting more and more creatures to devour the interloper.

The Elemental Plane of Water has the following traits.
\begin{itemize*}
\item \textbf{Subjective Directional Gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Water-Dominant.}
\item \textbf{Enhanced Magic:} Spells and spell-like abilities that use or create water are both extended and enlarged (as if the \feat{Extend Spell} and \feat{Enlarge Spell} metamagic feats had been used on them, but the spells don't require higher-level slots). Spells and spell-like abilities that are already extended or enlarged are unaffected by this benefit.
\item \textbf{Impeded Magic:} Spells and spell-like abilities with the fire descriptor (including spells of the Fire domain) are impeded.
\end{itemize*}
