\subsectionA{Negative Energy Plane}
To an observer, there's little to see on the Negative Energy Plane. It is a dark, empty place, an eternal pit where a traveler can fall until the plane itself steals away all light and life. The Negative Energy Plane is the most hostile of the Inner Planes, and the most uncaring and intolerant of life. Only creatures immune to its life-draining energies can survive there.

\subsubsection{Negative Energy Plane Traits}
\begin{itemize*}
\item \textbf{Subjective Directional Gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Major Negative-Dominant:} Each round, those within must make a DC 25 Fortitude save or gain a negative level. A creature whose negative levels equal its current levels or Hit Dice is slain, becoming a wraith. The \spell{death ward} spell protects a traveler from the damage and energy drain of the plane.

Some areas within the plane have only the minor negative-dominant trait, and these islands tend to be inhabited. On those areas, living creatures take 1d6 points of damage per round. At 0 hit points or lower, they crumble into ash.
\item \textbf{Enhanced Magic:} Spells and spell-like abilities that use negative energy are maximized (as if the \feat{Maximize Spell} metamagic feat had been used on them, but the spells don't require higher-level slots). Spells and spell-like abilities that are already maximized are unaffected by this benefit. Class abilities that use negative energy, such as rebuking and controlling undead, gain a +10 bonus on the roll to determine Hit Dice affected.
\item \textbf{Impeded Magic:} Spells and spell-like abilities that use positive energy, including \spellref{cure light wounds}{cure} spells, are impeded. Characters on this plane take a $-10$ penalty on Fortitude saving throws made to remove negative levels bestowed by an energy drain attack.
\end{itemize*}
