\subsectionA{Paraelemental Plane of Sun}
The Paraelemental Plane of Sun is a vast plane of cloudless sky and an enormous sun, with heat and light radiating on all. There is no protection from the heat, nor do the denizens of the plane care to have it.

Settlements on the plane are cities of light, radiating like the sun on solidified rays of solar energy. While different colors exist, the structures tend to mimic the sun and have a dark red coloring. Every so often a building will have prisms, scattering the light into more colors than a traveler could imagine. Visitors will want protection from the exposure to so much light and heat.

The Armies of the Sun are blinding forces that radiate not only their anger and power, but also cast out any shadows or darkness. They travel fast and strike hard, vanishing in the blink of an eye, leaving their victims blind and burned.

The Paraelemental Plane of Sun has the following traits.
\begin{itemize*}
\item \textbf{Subjective Directional Gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Air-Dominant.}
\item \textbf{Fire-Dominant:} Unprotected wood, paper, cloth, and other flammable materials catch fire almost immediately, and those wearing unprotected flammable clothing catch on fire. In addition, individuals take 3d10 points of fire damage every round. Those that are made of water take double damage each round.
\item \textbf{Enhanced Magic:} Spells and spell-like abilities with the air or fire descriptor are both maximized and enlarged (as if the Maximize Spell and Enlarge had been used on them, but the spells don't require higher-level slots). Spells and spell-like abilities that are already maximized or enlarged are unaffected by this benefit.
\item \textbf{Impeded Magic:} Spells and spell-like abilities that use or create water, darkness or shadows (including spells of the Water domain and spells that summon water elementals or outsiders with the water or shadow or Black subtype) are impeded.
\end{itemize*}
