\subsectionA{Paraelemental Plane of Rain}
The Paraelemental Plane of Rain is an endless expanse of clouds, lightning and, of course, rain. The plane is not uniform, so pockets of peaceful light drizzle give way to raging storms that blow with the force of a hurricane. The Paraelemental Plane of Rain also has varying temperatures, so that one place will have warm, tropical rains, while others will have storms that are the rarest of all on Athas: blizzards.

Settlements in the plane are made of clouds and ice, hardened into vast castles and cities. Lightning jumps from structure to structure, and the sound of thunder, both from the storms and from the voices of the inhabitance, echo for hundreds of miles. A sadness seems to infect the plane, as well as an anger that burst like a thunderclap.

The forces of the Plane of Rain are the weakest of all the Paraelemental planes. Due to the weakened condition of Athas and their connection to the planes, Rain has suffered. However, weakest does not mean weak, and to withstand the force unleashed by the denizens of the planes when off to war is to be electrified, deafened, and then to have your flesh ripped by your bones from the onslaught of hailstones. Travelers should be prepared to make their stay as short as possible.

\subsubsection{Paraelemental Plane of Rain Traits}
\begin{itemize*}
\item \textbf{Subjective Directional Gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Air-Dominant.}
\item \textbf{Enhanced Magic:} Spells and spell-like abilities that use, manipulate, or create air or water (including spells of the Air or water domains) are both empowered and enlarged (as if the \feat{Empower Spell} and \feat{Enlarge Spell} metamagic feats had been used on them, but the spells don't require higher-level slots).
\item \textbf{Impeded Magic:} Spells and spell-like abilities that use or create earth or fire (including spells of the Earth and Fire domains and spells that summon earth or fire elementals or outsiders with the earth or fire subtype) are impeded.
\end{itemize*}
