\subsectionA{Paraelemental Plane of Magma}
The Paraelemental Plane of Magma is a vast expanse of flowing lava. Different pockets of alternating temperatures make some places within the plane harder or softer. Occasionally, a pocket of toxic fumes will exist. Travelers on the planes who are not native will be burned to cinders then crushed under the weight of all that liquid stone.

Cities within the plane are made of obsidian and basalt. The hellish landscape leaves little room for error for those traveling here. Passions erupt like volcanoes, and violence spews forth in pyroclastic shows of force and magic.
 
The armies of the plane are fearsome. They drip with molten rock burning and crushing all those in their way. They are highly aggressive and militaristic. Those who fail their lords are consumed, and their remains return to the plane that gave them life. Those traveling here would be best served to make the trip a short one. If they don't, the inhabitants of the plane will.

\subsubsection{Paraelemental Plane of Magma Traits}
\begin{itemize*}
\item \textbf{Heavy Gravity:} Strength-based and Dexterity-based skill checks incur a $-2$ circumstance penalty, as do all attack rolls. All item weights are effectively doubled, which might affect a character's speed. Weapon ranges are halved. Characters who fall on a heavy gravity plane take 1d10 points of damage for each 3 meters fallen, to a maximum of 20d10 points of damage.
\item \textbf{Earth-Dominant.}
\item \textbf{Fire-Dominant:} Unprotected wood, paper, cloth, and other flammable materials catch fire almost immediately, and those wearing unprotected flammable clothing catch on fire. In addition, individuals take 3d10 points of fire damage every round. Those that are made of water take double damage each round.
\item \textbf{Enhanced Magic.} Spells and spell-like abilities with the fire or earth descriptor are both maximized and enlarged (as if the \feat{Maximize Spell} and \feat{Enlarge Spell} had been used on them, but the spells don't require higher-level slots). Spells and spell-like abilities that are already maximized or enlarged are unaffected by this benefit.
\item \textbf{Impeded Magic.} Spells and spell-like abilities that use or create water (including spells of the Water domain and spells that summon water elementals or outsiders with the water subtype) are impeded.
\end{itemize*}
