\subsectionA{Positive Energy Plane}
The Positive Energy Plane has no surface and is akin to the Elemental Plane of Air with its wide-open nature. However, every bit of this plane glows brightly with innate power. This power is dangerous to mortal forms, which are not made to handle it. Despite the beneficial effects of the plane, it is one of the most hostile of the Inner Planes. An unprotected character on this plane swells with power as positive energy is force-fed into her. Then, her mortal frame unable to contain that power, she immolates as if she were a small planet caught at the edge of a supernova. Visits to the Positive Energy Plane are brief, and even then travelers must be heavily protected.

\subsubsection{Positive Energy Plane Traits}
\begin{itemize*}
\item \textbf{Subjective Directional Gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Major Positive-Dominant:} A creature on the Positive Energy Plane must make a DC 15 Fortitude save to avoid being blinded for 10 rounds by the brilliance of the surroundings. Simply being on the plane grants fast healing 5 as an extraordinary ability. In addition, those at full hit points gain 5 additional temporary hit points per round. These temporary hit points fade 1d20 rounds after the creature leaves the Positive Energy Plane. However, a creature must make a DC 20 Fortitude save each round that its temporary hit points exceed its normal hit point total. Failing the saving throw results in the creature exploding in a riot of energy, killing it.

Some regions of the plane have the minor positive-dominant trait instead, and those islands tend to be inhabited. All individuals in those regions gain fast healing 2 as an extraordinary ability.
\item \textbf{Enhanced Magic:} Spells and spell-like abilities that use positive energy, including \spellref{cure light wounds}{cure} spells, are maximized (as if the \feat{Maximize Spell} metamagic feat had been used on them, but the spells don't require higher-level slots). Spells and spell-like abilities that are already maximized are unaffected by this benefit. Class abilities that use positive energy, such as turning and destroying undead, gain a +10 bonus on the roll to determine Hit Dice affected. (Undead are almost impossible to find on this plane, however.)
\item \textbf{Impeded Magic:} Spells and spell-like abilities that use negative energy (including \spellref{inflict light wounds}{inflict} spells) are impeded.
\end{itemize*}
