\section{Creating a Party}
When players create characters, they should work with you and each other to determine their history, and to give the characters a reason to be together from the very beginning. How do they know each other? Why are they working together? Consider the following possibilities.

\textbf{Slavery:} The player characters share the fate of shackles and servitude. They can be gladiators fighting for their lives in the arenas, laborers toiling in the Smoking Crown mines, or as builders constructing the grand monuments of the sorcerer-kings. Were they born in captivity? Were they captured and sold into slavery, or were they sentenced for their crimes?

\textbf{Rebellion:} King Kalak of Tyr was overthrown by an unlikely band of heroes, which liberated all slaves in the city, and fought off the advancing army of Hamanu of Urik come to claim Tyr's iron mines. Today the city faces many challenges. Did the player characters participate in the rebellion? Which side were they on? Were they freed from captivity? Did they fight in the war against Urik?

\textbf{King's Service:} The sorcerer-kings rule their domains with an iron fist, and their enforcers are feared and loathed. Political intrigue, corruption, assassinations and intimidation accompany those employed in the king's service. Player characters can assume the roles of templars, royal defilers, myrmeleons and other agents of the king, or as mercenaries employed by such individuals.

\textbf{Dune Traders:} Caravans trek across the deserts and fierce rivalries exist between new and established trade houses. Either through business operations of their own, or by working for a merchant house, the player characters are involved with trade. Are the characters mercenaries? Do they work for a small or large house? Do they follow the Merchant Code, and where do their allegiances truly lie?

\textbf{Wastelanders:} Those who eke a living in the Athasian wilderness must protect themselves from the dreaded sun, forage for food and defend scarce water supplies. Nomadic elves and herders, ex-slaves and raiders, and savage humanoids all fight for survival in the wastelands.