\section{Demographics}



\Table{Town Examples}{lRX}{
  \tableheader Town Size
& \tableheader Population\footnotemark[1]
& \tableheader Examples \\

Small tribe &           20--60 & Sortar's camp \\
Large tribe &          61--200 & Tenpug's band \\
Village     &       201--1,000 & Winter Nest \\
Small town  &     1,001--5,000 & Pterran Vale \\
Large town  &    5,001--10,000 &  \\
Small city  &   10,001--50,000 & City-states \\
Large city  &  50,001--100,000 &  \\
Metropolis  & 100,001--300,000 &  \\
Megalopolis & 300,001 or more  &  \\
}

\textbf{Agriculture:} A big enough settlement needs a spellcaster whose job is to cast \spell{plant growth} on the city's crops. One such spellcaster is expected for every 2,000 people. It can be a earth cleric up to 8th-level, a ranger 11th-level or higher, or a druid 12th-level or higher.

Clerics of 9th-level or higher are called to help with planar duties from their elemental masters, rangers need to be of high enough level to be able cast the spell, while druids are required to wander until they reach the 12th-level.

\textbf{Health:} It is expected to exist a cleric or druid that can cast \spell{remove disease} for every 15,000 people. For smaller communities, there is one priest to attend to a large number of villages and tribes. For large settlements, their priests would attend to the city and its satellite towns.

\textbf{Safety:} For every 400 people in the community (rounded down), the community has one full-time guard. In city-states, these guards are mostly low-level templars and fighters. In smaller communities, guards are mostly fighters and scouts.

In addition, for every 20 people in the community, an able-bodied member of the local militia or a conscript soldier can be brought into service within just a few hours. In tribes, every adult member is called to defend their tribe. 

\subsubsection{Community Population and Wealth}
\subsubsection{NPCs in the Community}
\textbf{Highest-Level NPC in the Community for Each Class:} Use the following tables to determine the highest-level character in a given class for a given community. Determine the appropriate community modifier by consulting the first table below; then refer to the second table, roll the dice indicated for the class, and apply the modifier to get a result.

A result of 0 or lower for character level means that no characters of that kind can be found in the community. The maximum level for any class is 20th.


\Table{Community Modifiers}{lLL}{
  \tableheader Community Size
& \tableheader Community Modifier
& \tableheader Example \\
Small tribe & $-3$                                  & Sortar's camp \\
Large tribe & $-2$                                  & Tenpug's band \\
Village     & $-1$                                  & Winter Nest \\
Small town  & +0                                    & Pterran Vale \\
Large town  & +1                                    &  \\
Small city  & +2 (roll twice)\footnotemark[1]       & City-states \\
Large city  & +4 (roll thrice)\footnotemark[1]      &  \\
Metropolis  & +8 (roll four times)\footnotemark[1]  &  \\
Megalopolis & +16 (roll five times)\footnotemark[1] &  \\
\TableNote{2}{1 Cities this large can have more than one high-level NPC per class, each of whom generates lower-level characters of the same class.}\\
}

\Table{Highest-Level Locals}{lX}{
  \tableheader Class
& \tableheader Character Level \\

Barbarian & 1d4 (2) + community modifier\footnotemark[1] \\
Bard      & 1d6 (3) + community modifier \\
Cleric    & 1d6 (3) + community modifier \\
Druid     & 1d3 (2) + community modifier \\
Fighter   & 1d8 (4) + community modifier \\ 
Gladiator & 1d8 (4) + community modifier \\
Psion     & 1d4 (4) + community modifier\footnotemark[2] \\
Ranger    & 1d3 (2) + community modifier\footnotemark[3] \\
Scout     & 1d8 (4) + community modifier \\
Templar   & ---\footnotemark[2] \\
Thief     & 1d8 (4) + community modifier \\
Wizard    & 1d4 (2) + community modifier\footnotemark[2] \\

\TableNote{2}{1 In raiding tribes, level is 1d8 (4) + community modifier.}\\
\TableNote{2}{2 In city states, level is 20.}\\
\TableNote{2}{3 In hunting clans, level is 1d8 (4) + community modifier.}\\
}
