\section{Traps}

\textbf{Types of Traps:} A trap can be either mechanical or magic in nature. Mechanical traps include pits, arrow traps, falling blocks, water-filled rooms, whirling blades, and anything else that depends on a mechanism to operate. A mechanical trap can be constructed by a PC through successful use of the \skill{Craft} (trapmaking) skill (see Designing a Trap, below, and the skill description).

Magic traps are further divided into spell traps and magic device traps. Magic device traps initiate spell effects when activated, just as wands, rods, rings, and other magic items do. Creating a magic device trap requires the \feat{Craft Wondrous Item} feat (see Designing a Trap and the feat description).

Spell traps are simply spells that themselves function as traps. Creating a spell trap requires the services of a character who can cast the needed spell or spells, who is usually either the character creating the trap or an NPC spellcaster hired for the purpose.

\subsection{Mechanical Traps}
Dungeons are frequently equipped with deadly mechanical (nonmagical) traps. A trap typically is defined by its location and triggering conditions, how hard it is to spot before it goes off, how much damage it deals, and whether or not the heroes receive a saving throw to mitigate its effects. Traps that attack with arrows, sweeping blades, and other types of weaponry make normal attack rolls, with a specific attack bonus dictated by the trap’s design.

Creatures who succeed on a DC 20 \skill{Search} check detect a simple mechanical trap before it is triggered. (A simple trap is a snare, a trap triggered by a tripwire, or a large trap such as a pit.)

A character with the trapfinding class feature who succeeds on a DC 21 (or higher) \skill{Search} check detects a well-hidden or complex mechanical trap before it is triggered. Complex traps are denoted by their triggering mechanisms and involve pressure plates, mechanisms linked to doors, changes in weight, disturbances in the air, vibrations, and other sorts of unusual triggers.

\subsection{Magic Traps}
Many spells can be used to create dangerous traps. Unless the spell or item description states otherwise, assume the following to be true.

\begin{itemize*}
\item A successful \skill{Search} check (DC 25 + spell level) made by a rogue (and only a rogue) detects a magic trap before it goes off. Other characters have no chance to find a magic trap with a \skill{Search} check.
\item Magic traps permit a saving throw in order to avoid the effect (DC 10 + spell level $\times$ 1.5).
\item Magic traps may be disarmed by a rogue (and only a rogue) with a successful \skill{Disable Device} check (DC 25 + spell level).
\end{itemize*}

\input{subsections/campaign/traps/elements-of-a-trap.tex}
\input{subsections/campaign/traps/sample-traps.tex}
\input{subsections/campaign/traps/designing-a-trap.tex}
