\section{Region of Origin}

In Athas, where you character comes from can help dictate his speech, clothing, world view, and values. In the context of the game, these cultural differences are expressed in the choices of class, skills, feats, and prestige classes that characters from different regions make.

This section describes the most common choices of game-related options for several known regions of Athas. These choices are not meant to be restrictive, since exceptions always exist to such general rules. They simply offer guidelines for making a character seem like a true representative of his native culture.

\subsection{Balic}
The city-state of Balic sits at the eastern tip of the Balican Peninsula, the piece of land which splits the Estuary of the Forked Tongue into its northern and southern branches. Balic is currently ruled by a triumvirate made up of its largest merchant houses.

\textbf{Classes:} \class{Bard}, \class{Gladiator}, \class{Templar}.

\textbf{Skills:} \skill{Perform} (any).

\textbf{Feats:} \feat{Performance Artist}.

\textbf{Prestige Classes:} \class{Dune Trader}, \class{Master Shipfloater}, \class{Shadow Dancer}, \class{Shadow Templar}, \class{Shadow Wizard}.

\subsection{Barrier Wastes}
The Barrier Wastes is the desolate area that cuts across a massive portion of the Jagged Cliffs region, and it is home to the Bandit States, a collection of violent humanoid raiding tribes.

\textbf{Classes:} \class{Barbarian}, \class{Fighter}.

\textbf{Skills:} \skill{Intimidate}, \skill{Survival}.

\textbf{Feats:} \feat{Intimidating Presence}, \feat{Wastelander}.

\textbf{Prestige Classes:} \class{Master Scout}, \class{Kik}, \class{Savage}.

\subsection{Draj}
Draj is a warrior city-state mostly human but intermingled with the other common races, situated on a vast mud flat east of Raam.

\textbf{Classes:} \class{Fighter}, \class{Gladiator}, \class{Templar}.

\textbf{Skills:} \skill{Intimidate}, \skill{Knowledge} (nature).

\textbf{Feats:} \feat{Astrologer}, \feat{Mekillothead}.

\textbf{Prestige Classes:} \class{Arrow Knight}, \class{Cerulean}, \class{Dune Trader}, \class{Jaguar Knight}, \class{Moon Priest}.

\subsection{Eldaarich}
Eldaarich occupies a small island in the Sea of Silt, just off the mainland. This human city-state is ruled by the mad Daskinor and his ruthless red guards.

\textbf{Classes:} \class{Gladiator}, \class{Templar}.

\textbf{Skills:} \skill{Intimidate}, \skill{Sense Motive}.

\textbf{Feats:} \feat{Grovel}, \feat{Paranoid}, \feat{Reign of Terror}.

\textbf{Prestige Classes:} \class{Browncloak}, \class{Executioner}, \class{Red Guard}.


\subsection{Forest Ridge}
The Forest Ridge stretches all along the western side of the Ringing Mountains, hugging the spine of the range from north to south. This is where most halflings come from.

\textbf{Classes:} \class{Druid}, \class{Ranger}.

\textbf{Skills:} \skill{Knowledge} (nature), \skill{Survival}.

\textbf{Feats:} \feat{Cannibalism Ritual}, \feat{Jungle Fighter}, \feat{Nature's Child}.

\textbf{Prestige Classes:} \class{Elite Sniper}, \class{Grove Master}.


\subsection{Gulg}
The predominantly human city-state of Gulg sits inside the southern portion of the Crescent Forest, almost directly east of Tyr.

\textbf{Classes:} \class{Gladiator}, \class{Templar}, \class{Ranger}.

\textbf{Skills:} \skill{Knowledge} (nature), \skill{Survival}.

\textbf{Feats:} \feat{Jungle Fighter}, \feat{Nature's Child}.

\textbf{Prestige Classes:} \class{Ambofari}, \class{Dune Trader}, \class{Hunter Noble}, \class{Elite Judaga}, \class{Master Scout}, \class{Oba's Servant}.


\subsection{Jagged Cliffs}
One of the mist isolated places in Athas, the Jagged Cliffs are home to the rhul-thaun, descendants of the rhulisti, and the distant relatives of the modern halflings, and keepers of the life-shaping arts.

\textbf{Classes:} \class{Fighter}, \class{Ranger}.

\textbf{Skills:} \skill{Climb}, \skill{Craft} (life-shaped), \skill{Knowledge} (life-shaping).

\textbf{Feats:} \feat{Cliff Combat}, \feat{Vertical Orientation}.

\textbf{Prestige Classes:} \class{Cliffclimber}, \class{Life-Shaper}, \class{Windrider}.


\subsection{Kurn}
Kurn lies in a fertile valley hidden among the White Mountains themselves. The mostly human residents of Kurn are among the most sophisticated and cultured people of Athas.

\textbf{Classes:} \class{Cleric} (air), \class{Templar}, \class{Wizard}.

\textbf{Skills:} \skill{Bluff}, \skill{Knowledge} (arcana).

\textbf{Feats:} \feat{Companion}.

\textbf{Prestige Classes:} \class{Dune Trader}, \class{Double Templar}, \class{Kurnan Maker}, \class{Kurnan Spymaster}, \class{Loremaster}.

\subsection{Nibenay}
The city-state of Nibenay is located east of Tyr at the northern tip of the Crescent Forest and it is famous for its artisans and musicians.

\textbf{Classes:} \class{Bard}, \class{Gladiator}, \class{Templar}.

\textbf{Skills:} \skill{Craft} (any), \skill{Knowledge} (nature), \skill{Perform} (any).

\textbf{Feats:} \feat{Artisan}, \feat{Astrologer}, \feat{Performance Artist}.

\textbf{Prestige Classes:} \class{Dune Trader}, \class{Mystic Dancer}, \class{Wife of Nibenay}.

\subsection{Raam}
The city-state of Raam is located east of Urik and is one of the largest and most chaotic cities in the Tablelands. It also has one of the most mixed populations.

\textbf{Classes:} \class{Gladiator}, \class{Templar}, \class{Psion}.

\textbf{Skills:} \skill{Craft} (any), \skill{Intimidate}.

\textbf{Feats:} \feat{Artisan}, \feat{Mansabdar}, \feat{Tarandan Method}.

\textbf{Prestige Classes:} \class{Dune Trader}, \class{Kuotagha}, \class{Servant of Badna}, \class{Psiologist}.

\subsection{Saragar}
Home to the Last Sea of Athas, Saragar is the legendary region where the Green Age still exists. Their residents are mostly human and elves and psionics is everyday life.

\textbf{Classes:} \class{Druid}, \class{Psion}, \class{Psychic Warrior}, \class{Wilder}.

\textbf{Skills:} \skill{Autohypnosis}, \skill{Knowledge} (psionics).

\textbf{Feats:} \feat{Psionic Schooling}.

\textbf{Prestige Classes:} \class{Metamind}, \class{Psion Uncarnate}.


\subsection{Sea of Silt}
An endless plain of pearly powder, The Silt Sea is home to powerful, aggressive, and primitive giants. Most humanoids use it as a way of transportation using specially crafted vehicles.

\textbf{Classes:} \class{Barbarian}, \class{Cleric} (silt), \class{Ranger}.

\textbf{Skills:} \skill{Knowledge} (nature), \skill{Survival}.

\textbf{Feats:} \feat{Giant Killer}.

\textbf{Prestige Classes:} \class{Elementalist}, \class{Master Shipfloater}.


\subsection{Trembling Plains}
The Trembling Plains are named for the enormous herds of mekillot that stampede across the plains during early Fruitbirth season, shaking the ground. It is home to humans, dwarves and half-elves known as Eloy.

\textbf{Classes:} \class{Fighter}, \class{Ranger}.

\textbf{Skills:} \skill{Survival}.

\textbf{Feats:} \feat{Elfish Eloy}, \feat{Longshanks}, \feat{Wind Racer}.

\textbf{Prestige Classes:} \class{Wind Walker}.


\subsection{Tyr}
Located in a fertile valley in the foothills of the Ringing Mountains, Tyr was the first city-state to successfully revolt against its sorcerer-king and to unban preserving magic.

\textbf{Classes:} \class{Gladiator}, \class{Wizard}, \class{Templar}.

\textbf{Skills:} \skill{Craft} (any), \skill{Diplomacy}.

\textbf{Feats:} \feat{Companion}, \feat{Freedom}, \feat{Metalsmith}.

\textbf{Prestige Classes:} \class{Arena Champion}, \class{Dune Trader}, \class{Templar Knight}.

\subsection{Urik}
Located northeast of Tyr, between the Dragon's Bowl and the Smoking Crown Mountains, the city-state of Urik is to fighters what Draj is to barbarians and cerulean wizards.

\textbf{Classes:} \class{Fighter}, \class{Gladiator}, \class{Psychic Warrior}, \class{Templar}.

\textbf{Skills:} \skill{Concentration}, \skill{Craft} (any), \skill{Knowledge} (warcraft).

\textbf{Feats:} \feat{Artisan}, \feat{Disciplined}.

\textbf{Prestige Classes:} \class{Dune Trader}, \class{Templar Knight}, \class{War Mind}, \class{Yellow Robe}.
