\section{Rogue}
\Quote{Marek, always helpful, said that the UnderTyr catacombs are supposed to be haunted. Think I'll go make some inquiries about where a 'heretic' like me can get some holy earth. Always go prepared...}{Janos, human rogue}

Dark Sun offers a world of intrigue, manipulation, secret deals, and subtle treachery—in short, a rogue's playground. Rather than eking out their living at the
borders of society, many Athasian rogues dominate the action in many of the most powerful political factions in the Seven Cities: the Noble Houses, the templars, and the Merchant Houses. Often rogues themselves, the wealthy and powerful deploy lesser rogues as pawns in their endless games of acquisition, espionage, and deceit.

Individual rogues run the gamut of Athasian society, from the street rats of the cities to the vagabonds of the outlands, to the prosperous and respectable dune traders, to the low‐ranking templars that search their caravans at the gates. Accomplished rogues are often sought by the nobility as agents, and can earn both wealth and honor in such positions --- or earn a quick death should they be caught contemplating treachery against their masters.

\subsection{Making a Rogue}

A rogue can't stand up face to face with a mul warrior as well as a fighter or gladiator can. With his cunning and your various skills, however, he excels at taking the slightest opportunity and turning to his advantage. His ability to slip under the notice of an observer makes him a capable lone hunter, but his greatest strength are found through interaction with allies and foes, inside or outside, a battle—he can use his enemy`s slightest distraction to deliver a lethal blow, or ensure his party`s safe passage through a templar patrol.

\textbf{Races:} Elves, half‐elves, and humans take to the rogue's skills and lifestyle with the greatest ease. Halflings, dwarves, and muls, while not commonly rogues, adapt to the class remarkably well when they take to it. Thri‐kreen, pterrans, and aarakocra are usually quite adverse to the rogue class, and tend to do poorly. Half‐
giant rogues are unheard of except as fictional figures in comical tales around the fireside.

\textbf{Alignment:} Athasian rogues follow opportunity rather than ideals, but as many of them are lawful as chaotic. Lawful rogues tend to seek security and advancement in the service of nobles or in the ranks of the templars.

\subsection{Game Rule Information}
\textbf{Hit Die:} d6.

\subsection{Class Skills}
\textbf{Class Skills:} Appraise (Int), Balance (Dex), Bluff (Cha), Climb (Str), Craft (Int), Decipher Script (Int), Diplomacy (Cha), Disable Device (Int), Disguise (Cha), Escape Artist (Dex), Forgery (Int), Gather Information (Cha), Hide (Dex), Intimidate (Cha), Jump (Str), Knowledge (local) (Int), Listen (Wis), Move Silently (Dex), Open Lock (Dex), Perform (Cha), Profession (Wis), Search (Int), Sense Motive (Wis), Sleight of Hand (Dex), Spot (Wis), Tumble (Dex), Use Magic Device (Cha), Use Psionic Device (Cha), and Use Rope (Dex).
\textbf{Skill Points per Level:} 8 + Int modifier ($\times4$ at 1st level).

\subection{Class Features}

\textbf{Class Skills:} Use Psionic Device is a class skill for Athasian rogues. Swim is a cross‐class skill for Athasian rogues.

\textbf{Weapon and Armor Proficiency:} In addition to those presented on the Player's Handbook, Athasian rogues are proficient with the bard's friend, blowgun, garrote, small
macahuitl, tonfa, widow's knife, and wrist razor.

\textbf{Special Abilities:} In addition to those presented on the Player's Handbook, Athasian rogues may choose from the following abilities.