\section{General Feats}

\Feat{Ancestral Knowledge}
{You know legends and facts about long past events that have been shrouded by the sands of time.}
{Int 13, \skill{Knowledge} (history) 10 ranks.}
{Choose one of the following time periods: Blue Age, Green Age, or Cleansing Wars. You gain a +10 bonus on \skill{Knowledge} (history) checks or bardic knowledge checks to gain information about the chosen category.}{}
{You can take this feat more than once, but the bonus doesn't stack. Each time you take this feat, you choose another time period.}

\Feat{Arena Clamor}
{With your savage blows, you can make your companions give their best.}
{Cha 13, \feat{Improved Critical}, Perform 5 ranks.}
{Whenever you confirm a critical hit, all allies within a 60‐foot radius who have line of sight on you receive a +2 morale bonus on attack rolls for 1 round. This is a mind‐affecting effect. This effect is not cumulative. Characters cannot be affected more than once in this way in the same combat.}{}{}

\Feat{Armor Proficiency (Heavy)}
{}
{Armor Proficiency (light), Armor Proficiency (medium).}
{See Armor Proficiency (light).}
{See Armor Proficiency (light).}
{Fighters, psychic warriors, and clerics automatically have Armor Proficiency (heavy) as a bonus feat. They need not select it.}

\Feat{Armor Proficiency (Light)}
{}{}
{When you wear a type of armor with which you are proficient, the armor check penalty for that armor applies only to \skill{Balance}, \skill{Climb}, \skill{Escape Artist}, \skill{Hide}, \skill{Jump}, \skill{Move Silently}, \skill{Sleight of Hand}, and \skill{Tumble} checks.}
{A character who is wearing armor with which she is not proficient applies its armor check penalty to attack rolls and to all skill checks that involve moving, including Ride.}
{All characters except wizards, and psions automatically have Armor Proficiency (light) as a bonus feat. They need not select it.}

\Feat{Armor Proficiency (Medium)}
{}
{Armor Proficiency (light).}
{See Armor Proficiency (light).}
{See Armor Proficiency (light).}
{Fighters, barbarians, gladiators, psychic warriors, clerics, druids, and templars automatically have Armor Proficiency (medium) as a bonus feat. They need not select it.}

\GFeat{Augment Summoning}
{\feat{Spell Focus} (conjuration).}
{Each creature you conjure with any summon spell gains a +4 enhancement bonus to Strength and Constitution for the duration of the spell that summoned it.}

\Feat{Brutal Attack}
{Your decisive attacks are especially frightening for those who watch.}
{Cha 13, \feat{Improved Critical}, \skill{Perform} 5 ranks.}
{Whenever you confirm a critical hit, all enemies within a 10‐foot radius who have line of sight on you must make a Will save (DC 10 + \onehalf your character level + your Cha modifier) or become shaken for a
number of rounds equal to your Cha modifier. This is a mind‐affecting fear effect.

Whether or not the save is successful, that creature cannot be affected again by the same character's brutal
attack for 24 hours.}{}{}

\Feat{Bug Trainer}
{You can train vermin creatures, such as kanks and cilops.}
{\skill{Handle Animal} 5 ranks, \skill{Knowledge} (nature) 5 ranks.}
{You can use the \skill{Handle Animal} skill for vermin as though they were animals with an Intelligence score of 1.}
{You can use the \skill{Handle Animal} skill only on creatures with an Intelligence score of 1 or 2.}
{}

\GFeat{Combat Casting}{}
{You get a +4 bonus on Concentration checks made to cast a spell or use a spell-like ability while on the defensive or while you are grappling or pinned.}

\Feat{Cornered Fighter}
{You fight better when you freedom is put at risk.}
{Base attack bonus +5.}
{You receive a +2 bonus on attack rolls and a +2 bonus to AC when fighting against opponents who flank you.}
{}{}

\Feat{Defender of the Land}
{You share power with the spirit from your guarded land, to nurture and protect the land to which the spirit is tied.}
{Wild shape class feature.}
{You receive a +1 caster level on spells you cast against defilers and your spells damage is increased by 1 per die against defilers.}
{}{}

\Feat{Diehard}
{}
{\feat{Endurance}.}
{When reduced to between $-1$ and $-9$ hit points, you automatically become stable. You don't have to roll d\% to see if you lose 1 hit point each round.

When reduced to negative hit points, you may choose to act as if you were disabled, rather than dying. You must make this decision as soon as you are reduced to negative hit points (even if it isn't your turn). If you do not choose to act as if you were disabled, you immediately fall unconscious.

When using this feat, you can take either a single move or standard action each turn, but not both, and you cannot take a full round action. You can take a move action without further injuring yourself, but if you perform any standard action (or any other action deemed as strenuous, including some free actions, swift actions, or immediate actions, such as casting a quickened spell) you take 1 point of damage after completing the act. If you reach $-10$ hit points, you immediately die.}
{A character without this feat who is reduced to between $-1$ and $-9$ hit points is unconscious and dying.}
{}

\Feat{Dissimulated}
{Your ability to speak what others want to hear increases the credibility of your words.}
{Int 13, Cha 13, \skill{Bluff} 5 ranks.}
{In addition to your Charisma modifier, you can add your Intelligence modifier to your \skill{Bluff} checks.}
{}{}

\Feat{Drake's Child}
{You are what is known as a drake's child, an individual who shows both exceptional strength and wisdom.}
{Str 13, Wis 13.}
{You get a +1 bonus to Will saves and a +1 bonus to Fortitude saves. You gain an additional +1 bonus to saving throws against ability drain, ability damage, energy drain, and death effects.}
{}{}

\Feat{Elemental Cleansing}
{Undead you turn or rebuke suffer elemental damage.}
{Ability to turn or rebuke undead.}
{Any undead that you successfully turn or rebuke takes 2d6 points of energy damage in addition to the normal turning or rebuking effect. The type of damage dealt is the one associated with your patron element.}{}{}

\Feat{Endurance}
{}
{You gain a +4 bonus on the following checks and saves: Swim checks made to resist nonlethal damage, Constitution checks made to continue running, Constitution checks made to avoid nonlethal damage from a forced march, Constitution checks made to hold your breath, Constitution checks made to avoid nonlethal damage from starvation or thirst, Fortitude saves made to avoid nonlethal damage from hot or cold environments, and Fortitude saves made to resist damage from suffocation. Also, you may sleep in light or medium armor without becoming fatigued.}
{A character without this feat who sleeps in medium or heavier armor is automatically fatigued the next day.}{}
{A ranger automatically gains Endurance as a bonus feat at 3rd level. He need not select it.}

\GFeat{Eschew Materials}{}
{You can cast any spell that has a material component costing 1 gp or less without needing that component. (The casting of the spell still provokes attacks of opportunity as normal.) If the spell requires a material component that costs more than 1 gp, you must have the material component at hand to cast the spell, just as normal.}

\Feat{Extra Turning}
{}
{Ability to turn or rebuke creatures.}
{Each time you take this feat, you can use your ability to turn or rebuke creatures four more times per day than normal.

If you have the ability to turn or rebuke more than one kind of creature each of your turning or rebuking abilities gains four additional uses per day.}
{Without this feat, a character can typically turn or rebuke undead (or other creatures) a number of times per day equal to 3 + his or her Charisma modifier.}
{You can gain Extra Turning multiple times. Its effects stack. Each time you take the feat, you can use each of your turning or rebuking abilities four additional times per day.}

\Feat{Faithful Follower}
{You overcome your fears while being led.}{}
{You receive a +5 morale bonus on saving throws against fear effects whenever you are within 20 feet of an ally with the \feat{Leadership} feat.}{}{}

\Feat{Favorite}
{You have gained the graces of your sorcerer‐monarch, receiving extra benefits.}
{\feat{Secular Authority}, \skill{Diplomacy} 10 ranks.}
{You can use your secular authority ability four more times per day than normal. Furthermore, whenever you contest or are contested in the use of secular authority, you receive a +2 bonus on your opposed \skill{Diplomacy} check.}
{Without this feat, a templar can typically use secular authority only once per day per templar level.}
{You can gain Favorite multiple times. Its effects stack. Each time you take the feat, you can use secular authority four additional times per day.}

\Feat{Fearsome}
{Your might frightens your foes.}
{Str 15.}
{You can use your Strength modifier instead of your Charisma modifier on Intimidate checks. Additionally, you receive a +2 bonus on Intimidate checks.}{}{}

\Feat{Gladiatorial Entertainer}
{You can make gladiatorial performances more often than normal.}
{Gladiatorial performance class feature.}
{Each time you take this feat, you can use your gladiatorial performance ability four more times per day than normal.}
{}
{You can gain Gladiatorial Entertainer multiple times. Its effects stack. Each time you take the feat, you can use gladiatorial performance four additional times per day.}

\Feat{Greasing the Wheels}
{You can circumvent various official obstacles when a person in a position of trust or authority is willing to accept ``presents.''}
{Cha 13, \skill{Diplomacy} 7 ranks, \skill{Knowledge} (local) 5 ranks.}
{This feat grants a new use for the \skill{Diplomacy} skill. You must share a language with a creature in order to use this option. This option cannot be used during combat.

\textit{Bribery Etiquette:} You can discern the timing of the offer, the amount that will most likely garner the wanted reaction, and the best way to disguise the bribe so that it doesn’t draw attention from unwanted witnesses. An insulted character will have his attitude changed one step for the worse and might report you to the proper authorities (this can be negated by a successful \skill{Diplomacy} check, albeit with a $-10$ penalty).

To bribe a character, you must give him a number of ceramic pieces (in coins, items or other valuables) as
shown below.

\Table{}{X c}{
\tableheader Bribery Target & \tableheader Cp Needed\\
Bouncer & 4 Cp\\
Informant & 5 Cp\\
Templar or guard, low-level (1--4) & 12 Cp\\
Templar or guard, mid-level (5--8) & 20 Cp\\
Templar or guard, high-level (9+) & 30 Cp
}

Several factors can affect the amount needed to bribe a character, but the DM may modify these values as he sees fit.

\Table{}{X c}{
\tableheader Background & \tableheader Cp Modifier\\
Renown & $-2$\\
Illegal profession & +5\\
PC is wanted & $\times2$\\
Slave & +2\\
Noble & $-2$\\
Templar & $-5$
}
}{}{}

\GFeat{Great Fortitude}{}
{You get a +2 bonus on all Fortitude saving throws.}

\Feat{Greater Spell Focus}
{Choose a school of magic to which you already have applied the \feat{Spell Focus} feat.}{}
{Add +1 to the Difficulty Class for all saving throws against spells from the school of magic you select. This bonus stacks with the bonus from \feat{Spell Focus}.}{}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new school of magic to which you already have applied the \feat{Spell Focus} feat.}{}

\GFeat{Greater Spell Penetration}
{\feat{Spell Penetration}.}
{You get a +2 bonus on caster level checks (1d20 + caster level) made to overcome a creature's spell resistance. This bonus stacks with the one from Spell Penetration.}

\Feat{Hard as Rock}
{You are resolute while fighting and particularly tough to kill.}
{Con 15, \feat{Diehard}, \feat{Great Fortitude}.}
{You are immune to death from massive damage. Furthermore, you have a 30\% chance per round of becoming stable on your own when you are dying and a 30\% chance per hour of regaining consciousness.}
{The chance of becoming stable on your own is 10\% per round and regaining consciousness is 10\% per hour.}{}

\Feat{Improved Counterspell}
{}{}
{When counterspelling, you may use a spell of the same school that is one or more spell levels higher than the target spell.}
{Without this feat, you may counter a spell only with the same spell or with a spell specifically designated as countering the target spell.}{}

\Feat{Improved Familiar}
{This feat allows spellcasters to acquire a new familiar from a nonstandard list, but only when they could normally acquire a new familiar.}
{Ability to acquire a new familiar, sufficiently high level (see below).}
{When choosing a familiar, the creatures listed below are also available to the spellcaster. The spellcaster may choose a familiar with an alignment up to one step away on each of the alignment axes (lawful through chaotic, good through evil).

\Table{}{p{2cm} X Z{1.2cm}}{
\tableheader Familiar & \tableheader Condition & \tableheader Arcane Spellcaster Level\\
Black/Gray Touched & Ability to channel energy from the Black or the Grey & 3rd\\
Boneclaw, lesser &  Neutral Alignment & 3rd\\
Pterrax & Reptilian subtype or ability to manifest psionic powers & 3rd\\
Elemental incarnation & Matching subtype or patron element, or preserver & 5th\\
Paraelemental incarnation & Matching subtype or patron element, or defiler & 5th\\
Tagster & Preserver & 5th\\
Dagorran & Neutral alignment & 5th\\
Elemental, Small & Matching subtype or patron element, or preserver & 5th\\
Paraelemental, Small & Matching subtype or patron element, or defiler & 5th\\
Boneclaw, greater & Neutral alignment or ability to manifest psionic powers & 7th\\
Tigone & Neutral alignment or preserver & 7th\\
Tembo & Defiler or ability to manifest psionic powers & 7th\\
Wall walker & Neutral alignment or defiler & 7th\\
Psionocus & Ability to manifest psionic powers (The master must first create the psionocus.) & 7th
}

Apply the Elemental incarnation or Paraelemental incarnation template to a familiar from the standard list.

Improved familiars otherwise use the rules for regular familiars, with two exceptions: If the creature's type is something other than animal, its type does not change; and improved familiars do not gain the ability to speak with other creatures of their kind (although many of them already have the ability to communicate).}{}{}

\Feat{Improved Sigil}
{You templar sigil has been imbued with special powers.}
{Sigil ability, \skill{Diplomacy} 9 ranks.}
{Choose two 1st‐level divine spells on your spell list. You can use them once per day as a spell-like ability. You must grasp and hold your sigil to use this ability. The save DC for these spell‐like abilities is 11 + your Charisma modifier.}{}{}

\GFeat{Improved Turning}
{Ability to turn or rebuke creatures.}
{You turn or rebuke creatures as if you were one level higher than you are in the class that grants you the ability.}

\Feat{Improviser}
{You are adept at using makeshift weapons.}
{Wis 13, base attack bonus +3.}
{Whenever using improvised weapons in combat, you suffer a $-1$ penalty on attack rolls made with them.}
{Whenever using improvised weapons in combat, you suffer a $-4$ penalty on attack rolls made with them.}{}

\Feat{Innate Hunter}
{You are an excellent hunter, capable to find sustenance even in the most desolate areas.}
{\feat{Track}, \skill{Survival} 5 ranks.}
{You receive a +4 insight bonus on \skill{Survival} checks involving hunting. You also receive a +1 insight bonus on attack rolls when fighting with creatures with the animal type.}{}{}

\GFeat{Iron Will}{}
{You get a +2 bonus on all Will saving throws.}

\Feat{Kiltektet}
{The Kiltektet is a group consisting mostly, but not solely, of kreen dedicated to hunting for knowledge and spreading it.}{}
{All Knowledge skills are class skills for you.}{}{}

\GFeat{Leadership}
{Character level 6th.}
{Having this feat enables the character to attract loyal companions and devoted followers, subordinates who assist her. See the table below for what sort of cohort and how many followers the character can recruit.

\Table{Leadership}{p{2cm} C *{6}{Z{.4cm}}}{
\rowcolor{white}
\multirow{2}{2cm}{\tableheader Leadership Score} & \multirow{2}{*}{\tableheader Cohort Level} & \multicolumn{6}{c}{\tableheader Number of Followers by Level}\\
\cmidrule[0.5pt]{3-8}
& & 1st & 2nd & 3rd & 4th & 5th & 6th\\
1 or lower & --- & --- & --- & --- & --- & --- & ---\\
2 & 1st & --- & --- & --- & --- & --- & ---\\
3 & 2nd & --- & --- & --- & --- & --- & ---\\
4 & 3rd & --- & --- & --- & --- & --- & ---\\
5 & 3rd & --- & --- & --- & --- & --- & ---\\
6 & 4th & --- & --- & --- & --- & --- & ---\\
7 & 5th & --- & --- & --- & --- & --- & ---\\
8 & 5th & --- & --- & --- & --- & --- & ---\\
9 & 6th & --- & --- & --- & --- & --- & ---\\
10 & 7th & 5 & --- & --- & --- & --- & ---\\
11 & 7th & 6 & --- & --- & --- & --- & ---\\
12 & 8th & 8 & --- & --- & --- & --- & ---\\
13 & 9th & 10 & 1 & --- & --- & --- & ---\\
14 & 10th & 15 & 1 & --- & --- & --- & ---\\
15 & 10th & 20 & 2 & 1 & --- & --- & ---\\
16 & 11th & 25 & 2 & 1 & --- & --- & ---\\
17 & 12th & 30 & 3 & 1 & 1 & --- & ---\\
18 & 12th & 35 & 3 & 1 & 1 & --- & ---\\
19 & 13th & 40 & 4 & 2 & 1 & 1 & ---\\
20 & 14th & 50 & 5 & 3 & 2 & 1 & ---\\
21 & 15th & 60 & 6 & 3 & 2 & 1 & 1\\
22 & 15th & 75 & 7 & 4 & 2 & 2 & 1\\
23 & 16th & 90 & 9 & 5 & 3 & 2 & 1\\
24 & 17th & 110 & 11 & 6 & 3 & 2 & 1\\
25 or higher & 17th & 135 & 13 & 7 & 4 & 2 & 2
}

\textit{Leadership Score:} A character's base Leadership score equals his level plus any Charisma modifier. In order to take into account negative Charisma modifiers, this table allows for very low Leadership scores, but the character must still be 6th level or higher in order to gain the Leadership feat. Outside factors can affect a character's Leadership score, as detailed above.

\textit{Cohort Level:} The character can attract a cohort of up to this level. Regardless of a character's Leadership score, he can only recruit a cohort who is two or more levels lower than himself. The cohort should be equipped with gear appropriate for its level. A character can try to attract a cohort of a particular race, class, and alignment. The cohort's alignment may not be opposed to the leader's alignment on either the law-vs-chaos or good-vs-evil axis, and the leader takes a Leadership penalty if he recruits a cohort of an alignment different from his own.

Cohorts earn XP as follows:

\begin{enumerate*}
\item The cohort does not count as a party member when determining the party's XP.
\item Divide the cohort's level by the level of the PC with whom he or she is associated (the character with the Leadership feat who attracted the cohort).
\item Multiply this result by the total XP awarded to the PC and add that number of experience points to the cohort's total.
\end{enumerate*}

If a cohort gains enough XP to bring it to a level one lower than the associated PC's character level, the cohort does not gain the new level---its new XP total is 1 less than the amount needed attain the next level.

\textit{Number of Followers by Level:} The character can lead up to the indicated number of characters of each level. Followers are similar to cohorts, except they're generally low-level NPCs. Because they're generally five or more levels behind the character they follow, they're rarely effective in combat.

Followers don't earn experience and thus don't gain levels. However, when a character with Leadership attains a new level, the player consults the table above to determine if she has acquired more followers, some of which may be higher level than the existing followers. (You don't consult the table to see if your cohort gains levels, however, because cohorts earn experience on their own.)

\textit{Leadership Modifiers:} Several factors can affect a character's Leadership score, causing it to vary from the base score (character level + Cha modifier). A character's reputation (from the point of view of the cohort or follower he is trying to attract) raises or lowers his Leadership score, see Table: Reputation.

\Table{Reputation}{X c}{
\tableheader Leader's Reputation & \tableheader Modifier\\
Great renown & +2\\
Fairness and generosity & +1\\
Special power & +1\\
Failure & $-1$\\
Aloofness & $-1$\\
Cruelty & $-2$
}

Other modifiers may apply when the character tries to attract a cohort, see \tabref{Attracting Cohorts}.

\Table{Attracting Cohorts}{X c}{
\tableheader The Leader… & \tableheader Modifier\\
Has a familiar, special mount, or animal companion & $-2$\\
Recruits a cohort of a different alignment & $-1$\\
Caused the death of a cohort & $-2$ per cohort killed
}

Followers have different priorities from cohorts. When the character tries to attract a new follower, use any of the modifiers that apply on \tabref{Attracting Followers}.

\Table{Attracting Followers}{X c}{
\tableheader The Leader… & \tableheader Modifier\\
Has a stronghold, base of operations, guildhouse, or the like & +2\\
Moves around a lot & $-1$\\
Caused the death of other followers & $-1$
}}

\GFeat{Lightning Reflexes}{}
{You get a +2 bonus on all Reflex saving throws.}

\Feat{Linguist}
{You have an ear for language.}{}
{Speak Language is a class skill to you. You can also speak 2 additional languages.}{}
{This feat must be selected at 1st level.}

\Feat{Martial Weapon Proficiency}
{Choose a type of martial weapon. You understand how to use that type of martial weapon in combat.}
{}
{You make attack rolls with the selected weapon normally.}
{When using a weapon with which you are not proficient, you take a $-4$ penalty on attack rolls.}
{Barbarians, fighters, gladiators, psychic warriors, and rangers are proficient with all martial weapons. They need not select this feat.

You can gain Martial Weapon Proficiency multiple times. Each time you take the feat, it applies to a new type of weapon.

A Hamanu's templar, because of the the War domain, automatically gains the Martial Weapon Proficiency feat related to his sorcerer-monarchs's favored weapon as a bonus feat, the longsword. He need not select it.}

\Feat{Mastyrial Blood}
{You have an uncanny resistance against toxic substances.}
{Con 13.}
{You receive a +4 bonus on saving throws against poison.}{}
{This feat must be selected at 1st level.}

\GFeat{Natural Spell}
{Wis 13, wild shape ability.}
{You can complete the verbal and somatic components of spells while in a wild shape. You substitute various noises and gestures for the normal verbal and somatic components of a spell.

You can also use any material components or focuses you possess, even if such items are melded within your current form. This feat does not permit the use of magic items while you are in a form that could not ordinarily use them, and you do not gain the ability to speak while in a wild shape.}

\Feat{Path Dexter}
{Preservers tend to lean towards spells of protective nature and those that increase knowledge.}
{Preserver.}
{Choose two spells at every spell level. These spells must be selected from the abjuration and/or divination schools. You gain +1 caster level when casting the chosen spells.}{}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new set of spells from the abjuration and/or divination schools.
This feat can be selected only by preservers.}

\Feat{Path Sinister}
{Defilers tend to lean towards spells of a darker nature.}
{Defiler.}
{Choose two spells at every spell level. These spells must be selected from the evocation and/or necromancy schools. You gain +1 caster level when casting the chosen spells.}{}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new set of spells from the evocation and/or necromancy schools.}

\Feat{Protective}
{You know that your gear could save your life, and you will do anything to protect it.}{}
{Gear on your person gains a +4 bonus to saving throws. If an item takes damage while you're holding it in your hands, you may make a Reflex save DC 10 + the amount of damage the item takes (after subtracting hardness) to transfer the damage to yourself.}{}{}

\Feat{Psionic Mimicry}
{Due to your study of psionic powers, you can pass off your spells as such.}
{\skill{Bluff} 8 ranks, \skill{Knowledge} (psionics) 4 ranks, \skill{Psicraft} 4 ranks.}
{You can disguise your spells as psionic powers by making a successful \skill{Bluff} check (DC 10 + spell level). An onlooker suspecting the nature of your spellcasting can attempt to identify a spell being cast using the \skill{Spellcraft} skill, but your check DC increases by 2.}{}{}

\Feat{Psionic Schooling}
{In your homeland, all who show some skill in the Way may receive training as a psion.}{}
{Psion, psychic warrior, or wilder is now a favored class for you (pick one), in addition to any other favored class you already possess. It does not count when determining multiclass XP penalties.}
{A character can have one favored class.}
{This feat must be selected at 1st level.}

\Feat{Raised by Beasts}
{Abandoned when you were very young, you were raised by wild animals.}{}
{Choose a kind of animal (amphibian, avian, mammal, fish, or reptile). You receive the wild empathy ability with animals of that kind. You also receive a +2 insight bonus on all Handle Animal checks with animals of that kind.}{}
{This feat must be selected at 1st level.}

\Feat{Run}
{}{}
{When running, you move five times your normal speed (if wearing medium, light, or no armor and carrying no more than a medium load) or four times your speed (if wearing heavy armor or carrying a heavy load). If you make a jump after a running start (see the Jump skill description), you gain a +4 bonus on your Jump check. While running, you retain your Dexterity bonus to AC.}
{You move four times your speed while running (if wearing medium, light, or no armor and carrying no more than a medium load) or three times your speed (if wearing heavy armor or carrying a heavy load), and you lose your Dexterity bonus to AC.}{}

\Feat{Secular Authority}
{You can use your authority within your city‐state to order slaves to do your bidding, requisition troops, enter the homes of freemen and nobles, and have them arrested.}
{Cha 13, \skill{Diplomacy} 6 ranks, \feat{Negotiator}, accepted into city‐state's templarate.}
{This feat grants four new uses for the \skill{Diplomacy} skill. None of them functions during combat.

\textit{Requisition:} You can draw upon the resources of your city, gaining the use of any slave, overriding the wishes of its owner.

\textit{Intrude:} You can, at any time, search the home, person or possessions of a slave. You may search and impound any evidence of wrongdoing, if found. Your authority does not extend to confiscating items for personal use.

\textit{Accuse:} You may have a slave imprisoned indefinitely, awaiting the gathering of evidence against him. You may only imprison one suspect in such a manner.

\textit{Judge:} You may pass judgment on a slave. This includes setting fines, prison sentences, death sentences or anything else you wish, within the laws of your city‐state.

As you gain more ranks in the \skill{Diplomacy} ranks, you gain the authority to take these actions against progressively higher social rankings, as described on the table below.

\Table{Secular Authority abilities}{c X}{
\tableheader Ranks & \tableheader Ability\\
2 & Requisition slave\\
3 & Intrude on slave\\
4 & Accuse slave\\
5 & Requisition troops\\
6 & Intrude on freeman\\
7 & Judge slave\\
8 & Accuse freeman\\
9 & Requisition gear\\
10 & Intrude on noble\\
11 & Judge freeman\\
12 & Accuse noble\\
13 & Requisition spellcaster/manifester\\
14 & Intrude on templar\\
15 & Judge noble\\
16 & Accuse templar\\
17 & Requisition property\\
18+ & Judge templar
}

Failure to comply with these demands is usually sanctioned with fines, imprisonment, outlaw status, and possibly execution. Any of this ability can be contested by another person with the Secular Authority feat, and move to have the action reversed with an opposed \skill{Diplomacy} check. If the challenger wins the opposed roll, the defending templar’s action is reversed (for example an imprisoned freeman is set free). If the defender wins the opposed roll nothing happens. Secular Authority can be contested in a particular case only once. A defending character who loses the opposed roll may not contest the result. Nor can he use Secular Authority to repeat the action that was contested against the same target.

You may use Secular Authority once per day for every four levels you have attained (but see Special), but only
within your city‐state.}
{}
{A templar automatically gains Secular Authority as a bonus feat. He need not select it. A templar may use Secular Authority a number of times per day equal to his templar level, plus one more time per day for every four levels he has in classes other than templar.}

\Feat{Shield Proficiency}
{}{}
{You can use a shield and take only the standard penalties.}
{When you are using a shield with which you are not proficient, you take the shield's armor check penalty on attack rolls and on all skill checks that involve moving, including Ride checks.}
{Barbarians, clerics, druids, fighters, gladiators, psychic warriors, rangers, and templars automatically have Shield Proficiency as a bonus feat. They need not select it.}

\Feat{Simple Weapon Proficiency}
{}{}
{You make attack rolls with simple weapons normally.}
{When using a weapon with which you are not proficient, you take a $-4$ penalty on attack rolls.}
{All characters except for druids, psions, and wizards are automatically proficient with all simple weapons. They need not select this feat.}

\Feat{Sniper}
{You are better at hiding when firing missile weapons and trying to stay hidden.}
{Dex 13, \skill{Hide} 1 rank.}
{You receive a +5 competence bonus to \skill{Hide} checks when firing missiles while trying to stay hidden.}{}{}

\Feat{Skill Focus}
{Choose a skill.}{}
{You get a +3 bonus on all checks involving that skill.}{}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new skill.}

\Feat{Spell Focus}
{Choose a school of magic.}{}
{Add +1 to the Difficulty Class for all saving throws against spells from the school of magic you select.}{}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a new school of magic.}

\Feat[Special]{Spell Mastery}{}
{Wizard level 1st.}
{Each time you take this feat, choose a number of spells equal to your Intelligence modifier that you already know. From that point on, you can prepare these spells without referring to a spellbook.}
{Without this feat, you must use a spellbook to prepare all your spells, except read magic.}{}

\GFeat{Spell Penetration}{}
{You get a +2 bonus on caster level checks (1d20 + caster level) made to overcome a creature's spell resistance.}

\Feat{Toughness}
{}{}
{You gain +3 hit points.}{}
{A character may gain this feat multiple times. Its effects stack.}

\Feat{Tower Shield Proficiency}
{}
{\feat{Shield Proficiency}.}
{You can use a tower shield and suffer only the standard penalties.}
{A character who is using a shield with which he or she is not proficient takes the shield's armor check penalty on attack rolls and on all skill checks that involve moving, including Ride.}
{Fighters automatically have Tower Shield Proficiency as a bonus feat. They need not select it.}

\Feat{Track}
{}{}
{To find tracks or to follow them for 1 mile requires a successful Survival check. You must make another Survival check every time the tracks become difficult to follow.

You move at half your normal speed (or at your normal speed with a $-5$ penalty on the check, or at up to twice your normal speed with a $-20$ penalty on the check). The DC depends on the surface and the prevailing conditions, as given on \tabref{Track DC}.


\Table{Track DC}{X Z{1.4cm} X Z{1.4cm}}{
\tableheader Surface & \tableheader Survival DC & \tableheader Surface & \tableheader Survival DC\\
Very soft ground & 5 & Firm ground & 15\\
Soft ground & 10 & Hard ground & 20
}

\textit{Very Soft Ground:} Any surface (fresh snow, thick dust, wet mud) that holds deep, clear impressions of footprints.

\textit{Soft Ground:} Any surface soft enough to yield to pressure, but firmer than wet mud or fresh snow, in which a creature leaves frequent but shallow footprints.

\textit{Firm Ground:} Most normal outdoor surfaces (such as lawns, fields, woods, and the like) or exceptionally soft or dirty indoor surfaces (thick rugs and very dirty or dusty floors). The creature might leave some traces (broken branches or tufts of hair), but it leaves only occasional or partial footprints.

\textit{Hard Ground:} Any surface that doesn't hold footprints at all, such as bare rock or an indoor floor. Most streambeds fall into this category, since any footprints left behind are obscured or washed away. The creature leaves only traces (scuff marks or displaced pebbles).

Several modifiers may apply to the \skill{Survival} check, as given on \tabref{Track DC Modifiers}.

\Table{Track DC Modifiers}{X Z{1.4cm}}{
\tableheader Condition & \tableheader Survival DC Modifier\\
Every three creatures in the group being tracked & $-1$\\
Size of creature or creatures being tracked & \\
~ Fine & +8\\
~ Diminutive & +4\\
~ Tiny & +2\\
~ Small & +1\\
~ Medium & 0\\
~ Large & $-1$\\
~ Huge & $-2$\\
~ Gargantuan & $-4$\\
~ Colossal & $-8$\\
Every 24 hours since the trail was made & +1\\
Every hour of rain since the trail was made & +1\\
Fresh snow cover since the trail was made & +10\\
Poor visibility (Apply only the largest modifier from this category.) & \\
~ Overcast or moonless night & +6\\
~ Moonlight & +3\\
~ Fog or precipitation & +3\\
Tracked party hides trail (and moves at half speed) & +5
}

For a group of mixed sizes, apply only the modifier for the largest size category.

If you fail a \skill{Survival} check, you can retry after 1 hour (outdoors) or 10 minutes (indoors) of searching.}
{Without this feat, you can use the \skill{Survival} skill to find tracks, but you can follow them only if the DC for the task is 10 or lower. Alternatively, you can use the \skill{Search} skill to find a footprint or similar sign of a creature's passage using the DCs given above, but you can't use Search to follow tracks, even if someone else has already found them.}
{A ranger automatically has Track as a bonus feat. He need not select it.

This feat does not allow you to find or follow the tracks made by a subject of a pass without trace spell.}

\Feat{Wastelander}
{You are an experienced survivor of the wastes.}{}
{You get a +1 bonus to Fortitude saves and a +2 bonus to \skill{Survival} checks.}{}{}
