\section{Item Creation Feats}

\GFeat[Item Creation]{Brew Potion}
{Caster level 3rd.}
{You can create a potion of any 3rd-level or lower spell that you know and that targets one or more creatures. Brewing a potion takes one day. When you create a potion, you set the caster level, which must be sufficient to cast the spell in question and no higher than your own level. The base price of a potion is its spell level $\times$ its caster level $\times$ 50 gp. To brew a potion, you must spend 1/25 of this base price in XP and use up raw materials costing one half this base price.

When you create a potion, you make any choices that you would normally make when casting the spell. Whoever drinks the potion is the target of the spell.

Any potion that stores a spell with a costly material component or an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must expend the material component or pay the XP when creating the potion.}

\GFeat[Item Creation]{Craft Magic Arms And Armor}
{Caster level 5th.}
{You can create any magic weapon, armor, or shield whose prerequisites you meet. Enhancing a weapon, suit of armor, or shield takes one day for each 1,000 gp in the price of its magical features. To enhance a weapon, suit of armor, or shield, you must spend 1/25 of its features’ total price in XP and use up raw materials costing one-half of this total price.

The weapon, armor, or shield to be enhanced must be a masterwork item that you provide. Its cost is not included in the above cost.

You can also mend a broken magic weapon, suit of armor, or shield if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to craft that item in the first place.}

\GFeat[Item Creation]{Craft Rod}
{Caster level 9th.}
{You can create any rod whose prerequisites you meet. Crafting a rod takes one day for each 1,000 gp in its base price. To craft a rod, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price.

Some rods incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the rod’s base price.}

\GFeat[Item Creation]{Craft Staff}
{Caster level 12th.}
{You can create any staff whose prerequisites you meet.

Crafting a staff takes one day for each 1,000 gp in its base price. To craft a staff, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price. A newly created staff has 50 charges.

Some staffs incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the staff’s base price.}

\GFeat[Item Creation]{Craft Wand}
{Caster level 5th.}
{You can create a wand of any 4th-level or lower spell that you know. Crafting a wand takes one day for each 1,000 gp in its base price. The base price of a wand is its caster level $\times$ the spell level $\times$ 750 gp. To craft a wand, you must spend 1/25 of this base price in XP and use up raw materials costing one-half of this base price. A newly created wand has 50 charges.

Any wand that stores a spell with a costly material component or an XP cost also carries a commensurate cost. In addition to the cost derived from the base price, you must expend fifty copies of the material component or pay fifty times the XP cost.}

\GFeat[Item Creation]{Craft Wondrous Item}
{Caster level 3rd.}
{You can create any wondrous item whose prerequisites you meet. Enchanting a wondrous item takes one day for each 1,000 gp in its price. To enchant a wondrous item, you must spend 1/25 of the item’s price in XP and use up raw materials costing half of this price.

You can also mend a broken wondrous item if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to craft that item in the first place.

Some wondrous items incur extra costs in material components or XP, as noted in their descriptions. These costs are in addition to those derived from the item’s base price. You must pay such a cost to create an item or to mend a broken one.}

\GFeat[Item Creation]{Forge Ring}
{Caster level 12th.}
{You can create any ring whose prerequisites you meet. Crafting a ring takes one day for each 1,000 gp in its base price. To craft a ring, you must spend 1/25 of its base price in XP and use up raw materials costing one-half of its base price.

You can also mend a broken ring if it is one that you could make. Doing so costs half the XP, half the raw materials, and half the time it would take to forge that ring in the first place.

Some magic rings incur extra costs in material components or XP, as noted in their descriptions. You must pay such a cost to forge such a ring or to mend a broken one.}

\GFeat[Item Creation]{Scribe Scroll}
{Caster level 1st.}
{You can create a scroll of any spell that you know. Scribing a scroll takes one day for each 1,000 gp in its base price. The base price of a scroll is its spell level $\times$ its caster level $\times$ 25 gp. To scribe a scroll, you must spend 1/25 of this base price in XP and use up raw materials costing one-half of this base price.

Any scroll that stores a spell with a costly material component or an XP cost also carries a commensurate cost. In addition to the costs derived from the base price, you must expend the material component or pay the XP when scribing the scroll.}