\Feat[Metapsionic]{Burrowing Power}
{Your powers sometimes bypass barriers.}{}
{To use this feat, you must expend your psionic focus. You can attempt to manifest your powers against targets that are sheltered behind a wall or force effect. Your power briefly skips through the Astral Plane to bypass the barrier.

The strength and thickness of the barrier determine your chance of success. To successfully bypass the barrier with your power, you make a Psicraft check against a DC equal to 10 + the hardness of the barrier + 1 per foot of thickness (minimum 1). Assign a hardness of 20 to barriers without a hardness rating, such as force effects (or a wall of ectoplasm). Force walls or walls of ectoplasm are assumed to have less than 1 foot of thickness unless noted otherwise.

If a power requires line of sight (which includes most powers that affect a target or targets instead of an area), you cannot manifest it as a burrowing power unless you can somehow see the target, such as with clairvoyant sense.

Using this feat increases the power point cost of the power by 2. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Chain Power}
{You can manifest powers that arc to hit other targets in addition to the primary target.}
{}
{To use this feat, you must expend your psionic focus. You can chain any power that affects a single target and that deals either acid, cold, electricity, fire, or sonic damage. After the primary target is struck, the power can arc to a number of secondary targets equal to your manifester level (maximum twenty). The secondary arcs each strike one target and deal half as much damage as the primary one did (round down).

Each target gets to make a saving throw, if one is allowed by the power. You choose secondary targets as you like, but they must all be within 30 feet of the primary target, and no target can be struck more than once. You can choose to affect fewer secondary targets than the maximum (to avoid allies in the area, for example).

Using this feat increases the power point cost of the power by 6. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Delay Power}
{You can manifest powers that go off up to 5 rounds later.}
{To use this feat, you must expend your psionic focus. You can manifest a power as a delayed power. A delayed power doesn’t activate immediately. When you manifest the power, you choose one of three trigger mechanisms: (1) The power activates when you take a standard action to activate it; (2) It activates when a creature enters the area that the power will affect (only powers that affect areas can use this trigger condition); or (3) It activates on your turn after 5 rounds pass. If you choose one of the first two triggers and the conditions are not met within 5 rounds, the power activates automatically on the fifth round.

Only area and personal powers can be delayed.

Any decisions you would make about the delayed power, including attack rolls, designating targets, or determining or shaping an area, are decided when the power is manifested. Any effects resolved by those affected by the power, including saving throws, are decided when the delay period ends.

A delayed power can be dispelled normally during the delay, and can be detected normally in the area or on the target by the use of powers that can detect psionic effects.

Using this feat increases the power point cost of the power by 2. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Empower Power}
{You can manifest powers to greater effect.}
{}
{To use this feat, you must expend your psionic focus.

You can empower a power. All variable, numeric effects of an empowered power are increased by one-half. An empowered power deals half again as much damage as normal, cures half again as many hit points, affects half again as many targets, and so forth, as appropriate. Augmented powers can also be empowered (multiply 1½ times the damage total of the augmented power). Saving throws and opposed checks (such as the one you make when you manifest dispel psionics) are not affected, nor are powers without random variables.

Using this feat increases the power point cost of the power by 2. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Enlarge Power}
{You can manifest powers farther than normal.}
{}
{To use this feat, you must expend your psionic focus. You can alter a power with a range of close, medium, or long to increase its range by 100\%. An enlarged power with a range of close has a range of 50 feet + 5 feet per level, a medium-range power has a range of 200 feet + 20 feet per level, and a long-range power has a range of 800 feet + 80 feet per level.

Powers whose ranges are not defined by distance, as well as powers whose ranges are not close, medium, or long, are not affected.

Using this feat does not increase the power point cost of the power.}{}{}

\Feat[Metapsionic]{Extend Power}
{You can manifest powers that last longer than normal.}
{}
{To use this feat, you must expend your psionic focus.

You can manifest an extended power. An extended power lasts twice as long as normal. A power with a duration of concentration, instantaneous, or permanent is not affected by this feat.

Using this feat increases the power point cost of the power by 2. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Maximize Power}
{You can manifest powers to maximum effect.}
{}
{To use this feat, you must expend your psionic focus.

You can maximize a power. All variable, numeric effects of a power modified by this feat are maximized. A maximized power deals maximum damage, cures the maximum number of hit points, affects the maximum number of targets, and so on, as appropriate. Saving throws and opposed checks are not affected, nor are powers without random variables.

Augmented powers can be maximized; a maximized augmented power deals the maximum damage (or cures the maximum hit points, and so on) of the augmented power.

An empowered and maximized power gains the separate benefits of each feat: the maximum result plus one-half the normally rolled result.

Using this feat increases the power point cost of the power by 4. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Opportunity Power}
{You can make power-enhanced attacks of opportunity.}
{}
{To use this feat, you must expend your psionic focus. When you make an attack of opportunity, you can use any power you know with a range of touch, if you have at least one hand free.

Manifesting this power is an immediate action.

You cannot use this feat with a touch power whose manifesting time is longer than 1 full-round action.

Using this feat increases the power point cost of the power by 6. The power’s total cost cannot exceed your manifester level.}
{Attacks of opportunity can be made only with melee weapons.}{}

\Feat[Metapsionic]{Quicken Power}
{You can manifest a power with a moment’s thought.}
{}
{To use this feat, you must expend your psionic focus. You can quicken a power. You can perform another action, even manifest another power, in the same round that you manifest a quickened power. You can manifest only one quickened power per round. A power whose manifesting time is longer than 1 round cannot be quickened.

Using this feat increases the power point cost of the power by 6. The power’s total cost cannot exceed your manifester level.

Manifesting a quickened power does not provoke attacks of opportunity.}{}{}

\Feat[Metapsionic]{Split Psionic Ray}
{You can affect two targets with a single ray.}
{Any other metapsionic feat.}
{To use this feat, you must expend your psionic focus. You can split psionic rays you manifest. The split ray affects any two targets that are both within the power’s range and within 30 feet of each other. If the ray deals damage, each target takes as much damage as a single target would take.

Using this feat increases the power point cost of the power by 2.}{}{}

\Feat[Metapsionic]{Twin Power}
{You can manifest a power simultaneously with another power just like it.}
{}
{To use this feat, you must expend your psionic focus. You can twin a power. Manifesting a power altered by this feat causes the power to take effect twice on the area or target, as if you were simultaneously manifesting the same power two times on the same location or target. Any variables in the power (such as duration, number of targets, and so on) are the same for both of the resulting powers. The target experiences all the effects of both powers individually and receives a saving throw (if applicable) for each. In some cases, such as a twinned psionic charm, failing both saving throws results in redundant effects (although, in this example, any ally of the target would have to succeed on two dispel attempts to free the target from the charm effect).

Using this feat increases the power point cost of the power by 6. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Unconditional Power}
{Disabling conditions do not hold you back.}
{}
{To use this feat, you must expend your psionic focus. Your mental strength is enough to overcome some otherwise disabling conditions. You can manifest an unconditional power when you are dazed, confused, nauseated, or stunned.

Only personal powers and powers that affect your person can be manifested as unconditional powers.

Using this feat increases the power point cost of the power by 8. The power’s total cost cannot exceed your manifester level.}{}{}

\Feat[Metapsionic]{Widen Power}
{You can increase the area of your powers.}
{}
{To use this feat, you must expend your psionic focus. You can alter a burst, emanation, line, or spread-shaped power to increase its area. (Powers that do not have an area of one of these four sorts are not affected by this feat.) Any numeric measurements of the power’s area increase by 100\%.

Using this feat increases the power point cost of the power by 4. The power’s total cost cannot exceed your manifester level.}{}{}