\section{Skill Feats}

\GFeat[Skill]{Acrobatic}{}
{You get a +2 bonus on all \skill{Jump} checks and \skill{Tumble} checks.}

\GFeat[Skill]{Agile}{}
{You get a +2 bonus on all \skill{Balance} checks and \skill{Escape Artist} checks.}

\Feat[Skill]{Alertness}{}{}
{You get a +2 bonus on all \skill{Listen} checks and \skill{Spot} checks.}
{}
{The master of a familiar gains the benefit of the Alertness feat whenever the familiar is within arm’s reach.}

\GFeat[Skill]{Animal Affinity}{}
{You get a +2 bonus on all \skill{Handle Animal} checks and \skill{Ride} checks.}

\GFeat[Skill]{Athletic}{}
{You get a +2 bonus on all \skill{Climb} checks and \skill{Swim} checks.}

\GFeat[Skill]{Autonomous}{}
{You get a +2 bonus on all \skill{Autohypnosis} checks and \skill{Knowledge} (psionics) checks.}

\GFeat[Skill]{Deceitful}{}
{You get a +2 bonus on all \skill{Disguise} checks and \skill{Forgery} checks.}

\GFeat[Skill]{Deft Hands}{}
{You get a +2 bonus on all \skill{Sleight of Hand} checks and \skill{Use Rope} checks.}

\GFeat[Skill]{Diligent}{}
{You get a +2 bonus on all \skill{Appraise} checks and Decipher \skill{Script} checks.}

\GFeat[Skill]{Field Officer}{}
{You get a +2 bonus on all \skill{Diplomacy} checks and \skill{Knowledge} (warcraft) checks.}

\GFeat[Skill]{Investigator}{}
{You get a +2 bonus on all \skill{Gather Information} checks and \skill{Search} checks.}

\GFeat[Skill]{Magical Aptitude}{}
{You get a +2 bonus on all \skill{Spellcraft} checks and \skill{Use Magic Device} checks.}

\GFeat[Skill]{Negotiator}{}
{You get a +2 bonus on all \skill{Diplomacy} checks and \skill{Sense Motive} checks.}

\GFeat[Skill]{Nimble Fingers}{}
{You get a +2 bonus on all \skill{Disable Device} checks and \skill{Open Lock} checks.}

\GFeat[Skill]{Persuasive}{}
{You get a +2 bonus on all \skill{Bluff} checks and \skill{Intimidate} checks.}

\GFeat[Skill]{Psionic Affinity}{}
{You get a +2 bonus on all \skill{Psicraft} checks and \skill{Use Psionic Device} checks.}

\GFeat[Skill]{Self-Sufficient}{}
{You get a +2 bonus on all \skill{Heal} checks and \skill{Survival} checks.}

\GFeat[Skill]{Stealthy}{}
{You get a +2 bonus on all \skill{Hide} checks and \skill{Move Silently} checks.}

\GFeat[Skill]{Trader}{}
{You get a +2 bonus on all \skill{Appraise} checks and \skill{Bluff} checks.}