\PrestigeClass{Arrow Knight}
{The thing with stealing from the draji, my father used to say, is that if they spot you they will come charging at you with bloodlust in their eyes. Keeping a crodlu nearby can save your life, son, for you can always outride them... Then he met an arrow knight and now he can't say anything at all.}{Gorgathor, human rogue}
{The arrow knights form Draj's corps of elite archers. Ranked third among the special warrior forces of Draj, these archers' might with the bow is perhaps unrivaled in the Tablelands. Although they form an elite group, the arrow knights are the least respected of Draj's three elite warrior forces. As ranged attackers, they do not gain the honor that Draji culture places on hand to hand combat. However, their place in the Draji military earns them some measure of respect, and their military role's importance is unquestioned. To other tablelanders, Draji arrow knights are feared for their determination, precision and bloodlust.

Arrow knights get along well with other warriors, but they are fiercely determined to prove their worth when it comes to eagle and jaguar knights. NPC arrow knights are usually encountered in Draj, its client villages and military installations, or traveling with the army. Arrow knights rarely leave Draj on their own, but those few who do usually make a name for themselves as mercenaries.}
{d10}
{an}
{Arrow knights come exclusively from the ranks of single or multi-classed fighters. They are unequaled with the bow, spending countless hours on the archery fields every day. Draji muls, dwarves, half-elves and humans make up the arrow knight corps, though members of other races might be accepted into their ranks if they can prove their skill and battle spirit. In very rare instances, non-draji have been accepted as an arrow knight, but these are exceptions rather than the norm.}
{
\textbf{Base Attack Bonus:} +5.

\textbf{Feats:} \feat{Point Blank Shot}, \feat{Weapon Focus} (any bow), \feat{Weapon Specialization} (any bow).

\textbf{Special:} Must have been trained in the Draji army.
}
{\skill{Climb} (Str), \skill{Craft} (Int), \skill{Handle Animal} (Cha), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Knowledge} (warcraft) (Int), \skill{Spot} (Wis).}
{2}
{\PrestigeWarriorTable}{
1 & +1 & +0 & +2 & +0 & Close combat shot, draji training \\
2 & +2 & +0 & +3 & +0 & Bonus feat \\
3 & +3 & +1 & +3 & +1 & Long shot \\
4 & +4 & +1 & +4 & +1 & Bonus feat \\
5 & +5 & +1 & +4 & +1 & Lethal shot \\
}
{
\textbf{Weapon and Armor Proficiencies:} The Arrow Knight is proficient with all simple and martial weapons, light armor, and shields (but not tower shields).

\textbf{Close Combat Shot (Ex):} An arrow knight can attack with a ranged weapon while in a threatened square and not provoke an attack of opportunity.

\textbf{Draji Training:} Arrow knights go through rigorous training. Arrow knight levels stack with fighter levels to fulfill feat requirements. %Before moving on to long range archery, they must first master short range shooting. At 1st level, they receive a +1 bonus to attack and damage rolls within 30 feet when using a bow, in addition to the benefits granted by the \feat{Point Blank Shot} feat.

\textbf{Bonus Feat:} At 2nd and 4th level, an arrow knight may choose one fighter feat. The arrow knight must still meet all the prerequisites for the bonus feat.

\textbf{Long Shot (Ex):} Mastering long range archery makes an army archer even more deadly. While a company of archers is almost bound to hit something when they all fire at once, a company of experienced arrow knights will hit much more. From 2nd level, archer knights take half the normal penalty on ranged attacks per range increment ($-1$ per range increment, rather than $-2$) when using a bow.

% \textbf{Deadly Aim:} At 3rd level, an arrow knight's precision increases at all ranges. The critical threat range for bows doubles (i.e. from 20/x3 to 19--20/x3).

% \textbf{Spot Weakness:} The arrow knight can use a move action to study a target and identify a weak spot. The arrow knight's single next attack with a bow against that target ignores half of her armor and natural armor bonuses (both rounded down).

\textbf{Lethal Shot (Ex):} Executing a lethal shot is a standard action. A successful attack roll inflicts a nasty wound that in addition to normal damage will continue to bleed for ten rounds if left unattended, inflicting one point of damage per round of bleeding. A \skill{Heal} check DC 15 or application of a cure spell will stop the bleeding immediately. Creatures immune to bleeding effects, critical hits or sneak attacks are also immune to lethal shot.
}
{}
{warcraft}
{Arrow knights are elite archers from Draj.}
{Arrow knights are amongst the best special forces on Athas. Their bloodlust in battle is unrivaled, as is their precision. Some bleed their foes to death instead of killing them on sight.}
{Despite being one of the best ranged special forces in Athas, arrow knights are the least privileged special force since Draji culture prefers hand to hand combat.}

Since much of the lore around arrow knights involves Draji culture, a successful check of \skill{Knowledge} (local [Draj]) can give the same information.