\PrestigeClass{Arena Champion}
{You fought like the Dragon.}{Jarek, half-elf arena champion}
{Arena champions are gladiatorial combatants who aspire to greatness in their blood sports. They dream of performing in arenas filled with thousands of frenzied spectators. Risking their lives for fame, wealth and adoration, arena champions are the heroes to commoners of all ages. Many hail from local neighborhoods or nearby communities.}
{d12}
{an}
{Gladiators make up the majority of arena champions, since their abilities already so closely mimic those of the prestige class. Most of the rest are fighters, along with the occasional psychic warrior or barbarian with a knack for flare and extravagance.}
{
\textbf{Base Attack Bonus:} +5.

\textbf{Skills:} \skill{Perform} (any) 6 ranks.

\textbf{Feats:} \feat{Weapon Focus} (any weapon), \feat{Toughness}.}
{\skill{Balance} (Dex), \skill{Bluff} (Cha), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Perform} (Cha), \skill{Profession} (Wis), \skill{Sense Motive} (Wis), \skill{Tumble} (Dex).}
{4}
{\MiniWarriorTable}{
1 & +1 & +2 & +0 & +0 & Crowd support +1 (10)\\
2 & +2 & +3 & +0 & +0 & Reputation\\
3 & +3 & +3 & +1 & +1 & Weapon mastery\\
4 & +4 & +4 & +1 & +1 & Signature move\\
5 & +5 & +4 & +1 & +1 & Crowd support +2 (50)\\
6 & +6 & +5 & +2 & +2 & Fame\\
7 & +7 & +5 & +2 & +2 & Improved signature move\\
8 & +8 & +6 & +2 & +2 & Roar of the crowd\\
9 & +9 & +6 & +3 & +3 & Crowd support +3 (100)\\
10 & +10 & +7 & +3 & +3 & Legend, finishing move
}
\textbf{Weapon and Armor Proficiency:} Arena champions gain no proficiency with any weapon or armor.

\textbf{Gladiatorial Performance:} Your gladiator levels stack with your arena champion levels for the purpose of determining your gladiatorial performance special abilities.

\textbf{Crowd Support (Ex):} The crowd may love or loathe you, but regardless their presence motivates you, who enjoys a +1 morale bonus to attack and damage rolls whenever there are ten or more non‐combatant spectators present. At 5th and 9th level this bonus increases, but the minimum amount of spectators must be fifty and one hundred respectively for the bonuses to take effect.

\textbf{Reputation:} You enjoy respect and admiration. You receive a +1 circumstance bonus to non‐combat uses of the \skill{Bluff}, \skill{Diplomacy}, \skill{Gather Information} and \skill{Intimidate} skills. These benefits do not apply when dealing with the devoted fans of rival gladiators. If you have or select the \feat{Leadership} feat, you get a +1 bonus to your leadership score.

\textbf{Weapon Mastery:} You get a +2 bonus to damage rolls with a chosen weapon. The weapon must be one for which you already have selected the \feat{Weapon Focus} feat.

\textbf{Signature Move (Ex):} You have developed a signature move. The exact technical nature of the move is up to the individual arena champion to develop, and it grants one of the following benefits:
\begin{itemize*}
\item A +2 competence bonus on opposed rolls for disarm attempts.
\item A +2 competence bonus on opposed rolls for trip attempts.
\item A +2 competence bonus on damage rolls for sunder attempts.
\item A +2 competence bonus on opposed Bluff and Sense Motive checks in combat.
\item A +1 dodge bonus to AC when fighting defensively or using total defense.
\end{itemize*}

\textbf{Fame:} As your reputation grows, so does your ability to influence others. Your bonuses to non‐combat uses of the \skill{Bluff}, \skill{Diplomacy}, \skill{Gather Information} and \skill{Intimidate} skills increase to +2, and the bonus to your leadership score increases to +2.

\textbf{Improved Signature Move (Ex):} Through specialization the benefit associated with your chosen signature move is doubled, for example, a +2 competence bonus on opposed rolls for disarm attempts increases to +4.

Alternatively, you may select a second signature move instead to expand your repertoire.

\textbf{Roar of the Crowd (Ex):} At 8th level, you can use the cheering of the crowd to your advantage. In any round when you successfully deal damage to an opponent, you gain a +1 morale bonus on the next attack roll you make in the same round.

\textbf{Legend:} You are a legend known to all. Treat general NPC initial attitudes as one category better. This benefit does not extend to the devoted fans of rival gladiators. Your bonus to your leadership score increases to +3.

\textbf{Finishing Move (Ex):} If an attack reduces an opponent below 0 hit points, you can attempt a coup de grace as a free action.

\subsection{Arena Champion Lore}
Characters with ranks in \skill{Knowledge} (history) or \skill{Knowledge} (local) can research arena champions to learn more about them. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 15:} Arena champions make the best fights in an arena. Always bet on them.

\textbf{DC 20:} Not every arena champion is a pompous gladiator---some of them are also raging barbarians or powerful fighters. They simply want the prestige and fame the profession brings.

\textbf{DC 30:} Characters who achieve this level of success can learn important details about specific arena champions in your campaign, including a notable individual, the area in which he operates, and the kinds of activities he undertakes.

Because arena champions have great reputations and a vast number of fans, the easiest way to find one is to contact the local arena manager or gladiatorial match agent and inquire about individuals with unique fighting talents.