\PrestigeClass{Assassin}
{Oh, don't worry. It's not the stab that will kill you. Nor will it be the poison taking effect right now. What killed you, mage, was only your Alliance. You should have chosen better friends.}{Kalar, half-elf assassin}
{Assassins are stealthy warriors specialized in dealing a single fatal attack after studying the target. The methods they take before dealing this attack vary from assassin to assassin. They may be master infiltrators, attacking the target while disguised. Many are killers for hire, and most are spies for the sorcerer-monarchs. They train in the use of poison and the forbidden arcane arts in order to finish their jobs effectively.}
{d6}
{an}
{The assassins are predominantly bards and rogues that enjoy killing, one way or another. Rangers become assassins specialized on targets of a race or killing in a terrain.}
{
\textbf{Alignment:} Any evil.

\textbf{Skills:} \skill{Disguise} 4 ranks, \skill{Hide} 8 ranks, \skill{Move Silently} 8 ranks.

\textbf{Special:} The character must kill someone for no other reason than to join the assassins.
}
{
\skill{Balance} (Dex), \skill{Bluff} (Cha), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Diplomacy} (Cha), \skill{Disable Device} (Int), \skill{Disguise} (Cha), \skill{Escape Artist} (Dex), \skill{Forgery} (Int), \skill{Gather Information} (Cha), \skill{Hide} (Dex), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Open Lock} (Dex), \skill{Search} (Int), \skill{Sense Motive} (Wis), \skill{Sleight of Hand} (Dex), \skill{Spot} (Wis), \skill{Swim} (Str), \skill{Tumble} (Dex), \skill{Use Magic Device} (Cha), and \skill{Use Rope} (Dex).
}
{4}
{\HalfSpellcasterTable[.6cm]}{
1 & +0 & +0 & +2 & +0 & Sneak attack +1d6, death attack, poison use, spells & 0 &&&\\
2 & +1 & +0 & +3 & +0 & +1 save against poison, uncanny dodge & 1 &&&\\
3 & +2 & +1 & +3 & +1 & Sneak attack +2d6 & 2 & 0 &&\\
4 & +3 & +1 & +4 & +1 & +2 save against poison & 3 & 1 &&\\
5 & +3 & +1 & +4 & +1 & Improved uncanny dodge, sneak attack +3d6 & 3 & 2 & 0 &\\
6 & +4 & +2 & +5 & +2 & +3 save against poison & 3 & 3 & 1 &\\
7 & +5 & +2 & +5 & +2 & Sneak attack +4d6 & 3 & 3 & 2 & 0\\
8 & +6 & +2 & +6 & +2 & +4 save against poison, hide in plain sight & 3 & 3 & 3 & 1\\
9 & +6 & +3 & +6 & +3 & Sneak attack +5d6 & 3 & 3 & 3 & 2\\
10 & +7 & +3 & +7 & +3 & +5 save against poison & 3 & 3 & 3 & 3	\\
}
{
\textbf{Weapon and Armor Proficiency:} Assassins are proficient with the crossbow (hand, light, or heavy), dagger (any type), dart, rapier, sap, shortbow (normal and composite), and short sword. Assassins are proficient with light armor but not with shields.

\textbf{Sneak Attack:} This is exactly like the rogue ability of the same name. The extra damage dealt increases by +1d6 every other level (1st, 3rd, 5th, 7th, and 9th). If an assassin gets a sneak attack bonus from another source the bonuses on damage stack.

\textbf{Death Attack:} If an assassin studies his victim for 3 rounds and then makes a sneak attack with a melee weapon that successfully deals damage, the sneak attack has the additional effect of possibly either paralyzing or killing the target (assassin's choice). While studying the victim, the assassin can undertake other actions so long as his attention stays focused on the target and the target does not detect the assassin or recognize the assassin as an enemy. If the victim of such an attack fails a Fortitude save (DC 10 + the assassin's class level + the assassin's Int modifier) against the kill effect, she dies. If the saving throw fails against the paralysis effect, the victim is rendered helpless and unable to act for 1d6 rounds plus 1 round per level of the assassin. If the victim's saving throw succeeds, the attack is just a normal sneak attack. Once the assassin has completed the 3 rounds of study, he must make the death attack within the next 3 rounds.

If a death attack is attempted and fails (the victim makes her save) or if the assassin does not launch the attack within 3 rounds of completing the study, 3 new rounds of study are required before he can attempt another death attack.

\textbf{Poison Use:} Assassins are trained in the use of poison and never risk accidentally poisoning themselves when applying poison to a blade.

\textbf{Spells:} Beginning at 1st level, an assassin gains the ability to cast a number of arcane spells. To cast a spell, an assassin must have an Intelligence score of at least 10 + the spell's level, so an assassin with an Intelligence of 10 or lower cannot cast these spells. Assassin bonus spells are based on Intelligence, and saving throws against these spells have a DC of 10 + spell level + the assassin's Intelligence bonus. When the assassin gets 0 spells per day of a given spell level he gains only the bonus spells he would be entitled to based on his Intelligence score for that spell level.

An assassin casts arcane spells, which are drawn from the assassin spell list (shown below). He can cast any spell he knows without preparing it ahead of time. Every assassin spell has a verbal component. An assassin can cast assassin spells while wearing light armor without incurring the normal arcane spell failure chance. However, like any other arcane spellcaster, an assassin wearing medium or heavy armor or using a shield incurs a chance of arcane spell failure if the spell in question has a somatic component (most do).

\Table{Assassin Spells Known}{b{1cm} C C C C}{
\tableheader Level & \multicolumn{4}{c}{\tableheader Spells Known}\\
\cmidrule[0.5pt]{2-5}
& \tableheader 1st & \tableheader 2nd & \tableheader 3rd & \tableheader 4th\\
1 & 2 &&&\\
2 & 3 &&&\\
3 & 3 & 2 &&\\
4 & 4 & 3 &&\\
5 & 4 & 3 & 2 &\\
6 & 4 & 4 & 3 &\\
7 & 4 & 4 & 3 & 2\\
8 & 4 & 4 & 4 & 3\\
9 & 4 & 4 & 4 & 3\\
10 & 4 & 4 & 4 & 4\\
}

An assassin can only learn spells of a certain level if he has at least one spell slot per day at that level. This means that when the number of slots available at that level is zero, he needs to have sufficient Intelligence to have a bonus spell at that level in order to know any spells of that level.

Upon reaching 6th level, at every even-numbered level after that (8th and 10th), an assassin can choose to learn a new spell in place of one he already knows. The new spell's level must be the same as that of the spell being exchanged, and it must be at least two levels lower than the highest-level assassin spell the assassin can cast. An assassin may swap only a single spell at any given level, and must choose whether or not to swap the spell at the same time that he gains new spells known for that level.

As noted above, an assassin need not prepare his spells in advance. He can cast any spell he knows at any time, assuming he has not yet used up his allotment of spells per day for the spell’s level.

\textbf{Save Bonus against Poison:} The assassin gains a natural saving throw bonus to all poisons gained at 2nd level that increases by +1 for every two additional levels the assassin gains.

\textbf{Uncanny Dodge (Ex):} Starting at 2nd level, an assassin retains his Dexterity bonus to AC (if any) regardless of being caught flat-footed or struck by an invisible attacker. (He still loses any Dexterity bonus to AC if immobilized.)

If a character gains uncanny dodge from a second class the character automatically gains improved uncanny dodge (see below).

\textbf{Improved Uncanny Dodge (Ex):} At 5th level, an assassin can no longer be flanked, since he can react to opponents on opposite sides of him as easily as he can react to a single attacker. This defense denies rogues the ability to use flank attacks to sneak attack the assassin. The exception to this defense is that a rogue at least four levels higher than the assassin can flank him (and thus sneak attack him).

If a character gains uncanny dodge (see above) from a second class the character automatically gains improved uncanny dodge, and the levels from those classes stack to determine the minimum rogue level required to flank the character.

\textbf{Hide in Plain Sight (Su):} At 8th level, an assassin can use the \skill{Hide} skill even while being observed. As long as he is within 10 feet of some sort of shadow, an assassin can hide himself from view in the open without having anything to actually hide behind. He cannot, however, hide in his own shadow.

\subsubsection{Assassin Spell List}
Assassins choose their spells from the following list:

\textbf{1st Level:} \spell{disguise self}, \spell{detect poison}, \spell{feather fall}, \spell{ghost sound}, \spell{jump}, \spell{obscuring mist}, \spell{slave scent}, \spell{sleep}, \spell{true strike}.

\textbf{2nd Level:} \spell{alter self}, \spell{cat's grace}, \spell{darkness}, \spell{death mark}, \spell{fox's cunning}, \spell{illusory script}, \spell{invisibility}, \spell{pass without trace}, \spell{spider climb}, \spell{undetectable alignment}.

\textbf{3rd Level:} \spell{boneclaw's cut}, \spell{death whip} \spell{deep slumber}, \spell{deeper darkness}, \spell{false life}, \spell{magic circle against good}, \spell{misdirection}, \spell{nondetection}.

\textbf{4th Level:} \spell{clairaudience/clairvoyance}, \spell{claws of the tembo}, \spell{dimension door}, \spell{freedom of movement}, \spell{glibness}, \spell{greater invisibility}, \spell{locate creature}, \spell{mage seeker}, \spell{modify memory}, \spell{poison}, \spell{rangeblade}, \spell{scapegoat}.
}
{}
{local}
{Assassins are spies that kill anyone for more than the right amount of money.}
{Assassins specialize in dealing a single fatal attack. Their victims are known for being poisoned.}
{Besides poison and their death attack, assassins can cast spells that enhance their abilities.}