\PrestigeClass{Black Cassock}
{Craftsmen! By decree of the king, you are ordered to follow us to the Ziggurat. Take with you tools of your crafts and come along quietly. Disobedience will be punished.}{Dote Atravian, black cassock}
{The templars of Tyr experienced their reign of terror coming to an end marked by the death of King Kalak, the Tyrant of Tyr. Without their spells, many templars fell prey to the mobs of angry and newly released slaves. Some fled the city, whereas others sought shelter under the new King Tithian’s hand. Tithian, himself a former high templar, made sure his enemies were removed, then invested the remaining templars into important positions. The templars remain a thorn in the eye of Sadira and Rikus, but Tyr’s heroes realize the city cannot be administrated without the bureaucratic ex-templars of Kalak. As for the templars, they are desperately clinging to what power they can get hold of, seeking individual alliances with other factions in the city. Fear and hatred remain against the now spelless templars. Wherever they go, the black cassocks must keep one hand on their swords.}
{d8}
{a}
{Black cassocks can be of any race and gender. Rumors speculate that templars from other city-states might have infiltrated the ranks of the Tyrian templarate, but no templar agents of other sorcerer-kings have been unmasked that the public knows of. Black cassocks are usually encountered in Tyr or the nearby mountain ranges. Templars administer the city of Tyr and its iron mines. They rarely venture alone and avoid the Warrens and Shadow Square unless ordered to go there. Some ex-templars have sought refuge in the ruins below the surface, eking a living among the undead and other dread denizens in Undertyr.}
{
\textbf{Skills:} \skill{Diplomacy} 8 ranks.

\textbf{Special:} Must be accepted into the templarate of Tyr.
}
{\skill{Appraise} (Int), \skill{Bluff} (Cha), \skill{Climb} (Str), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Diplomacy} (Cha), \skill{Disguise} (Cha), \skill{Gather Information} (Cha), \skill{Heal} (Wis), \skill{Intimidate} (Cha), \skill{Jump} (Str), \skill{Knowledge} (any) (Int), \skill{Literacy} (N/A), \skill{Profession} (Wis), \skill{Sense Motive} (Wis), \skill{Speak Language} (N/A) and \skill{Spellcraft} (Int).}
{4}
{\PrestigeSpellTable}{
1st & +0 & +2 & +0 & +2 & Secular authority, rebuke undead & +1 level of existing divine spellcasting class\\
2nd & +1 & +3 & +0 & +3 & Bureau specialization & +1 level of existing divine spellcasting class\\
3rd & +2 & +3 & +1 & +3 & King’s gift & +1 level of existing divine spellcasting class\\
4th & +3 & +4 & +1 & +4 &  & +1 level of existing divine spellcasting class\\
5th & +3 & +4 & +1 & +4 &  & +1 level of existing divine spellcasting class\\
6th & +4 & +5 & +2 & +5 & Bureau mastery & +1 level of existing divine spellcasting class\\
7th & +5 & +5 & +2 & +5 & King’s pet & +1 level of existing divine spellcasting class\\
8th & +6 & +6 & +2 & +6 &  & +1 level of existing divine spellcasting class\\
9th & +6 & +6 & +3 & +6 &  & +1 level of existing divine spellcasting class\\
10th & +7 & +7 & +3 & +7 & King’s favorite & +1 level of existing divine spellcasting class\\
}

\textbf{Weapon and Armor Proficiencies:} Black cassocks gain no proficiency with any weapon or armor.

\textbf{Secular Authority:} Black cassock gains the \feat{Secular Authority} feat.

\textbf{King’s Gift:} A black cassock receives a steel weapon from his king, signifying his rank.

\textbf{Bureau Specialization (Ex):} The templarate has many bureaus, each charged with an area of responsibility. The black cassock gets a +3 bonus to a class skill of his choice.

\textbf{Bureau Mastery (Ex):} The black cassock has survived long enough to have learnt the inner workings of a bureau. The bonus granted from bureau specialization increases to +6.

\textbf{King’s Pet:} The black cassock receives a permanent magical or psionic item from the king as recognition of her rank and service. The maximum value of this item is 8,000 Cp.

\textbf{King’s Favorite:} The black cassock is a personal favorite of the king and is rewarded with a gift---a potent permanent magical or psionic item. The maximum value of this item is 40,000 Cp.

\subsubsection{Ex-Templars}
A black cassock who abandons his sorcerer-monarch, or whose sorcerer-monarch dies, loses all templar spellcasting abilities. If the black cassock later becomes the templar of another sorcerer-monarch, he immediately regains his full templar spellcasting abilities.

\subsection{Black Cassock Lore}
Characters with ranks in \skill{Knowledge} (local [Tyr]) can research black cassocks to learn more about them. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 15:}

\textbf{DC 20:}

\textbf{DC 30:}