\PrestigeClass{Browncloak}
{}{}
{Dating back to the early Cleansing Wars, the Shtas are the most ancient of Daskinor's Orders still in operation, and may be the most ancient existing templar organization on Athas. Regardless of their past glories, the Shtas today are little more than puppets of the Red Guards; their outlying posts such as South Guard completely depend on provisions and equipment that the Red Guard provide, or refuse to provide, at their whim. Shtas soldiers are demoralized and unequipped, and at South Guard, face overwhelming foes, harsh weather, and must keep charge of angry foreign slaves that outnumber them eight to one.

Shtas Officers, the Browncloaks, provide the honeyed voices to recruit foolish Eldaarish youths to service in the Shtas. Other Browncloaks become responsible for putting and keeping these fools in harm's way. Browncloaks prevent desertion by a combination of patriotism, coercion, terror, a generous supply of psychoactive addictive substances.

Since Shtas posts are typically undermanned, Shtas soldiers cannot be allowed to quit fighting merely because they've had a limb or a head torn off. Shtas officers are especially adept at animating and commanding the dead corpses of soldiers under their command. Some Shtas officers would prefer to dispense with the living soldiers altogether, since zombies are so much more obedient, and never complain about the quantity or quality of rations. Alas, the laws of Eldaarich give the Shtas no rights to keep the bodies of dead humanoids. Naturally, the Browncloaks violate this law whenever they can get away with it.}
{d8}
{a}
{Browncloaks are exclusively evil templars from Eldaarich. But they may come as multiclass bards or rogues, or even evil clerics.}
{
\textbf{Alignment:} Any evil.

\textbf{Skills:} \skill{Bluff} 7 ranks, \skill{Diplomacy} 7 ranks.

\textbf{Spells:} Able to spontaneously cast 2nd level divine spells.

\textbf{Special:} Rebuke undead, promotion to officer in the Shtas Order.
}
{\skill{Bluff} (Cha), \skill{Craft} (Int), \skill{Diplomacy} (Cha), \skill{Heal} (Wis), \skill{Intimidate} (Cha), \skill{Knowledge} (local) (Int), \skill{Knowledge} (religion) (Int), \skill{Ride} (Dex), \skill{Psicraft} (Int), \skill{Sense Motive} (Wis), \skill{Spellcraft} (Int).}
{4}
{\PrestigeSpellTable}{
1 & +0 & +2 & +0 & +2 & Manipulator, poison use, rebuke undead & +1 level of existing divine spellcasting class\\
2 & +1 & +3 & +0 & +3 & Medicinal purposes & +1 level of existing divine spellcasting class\\
3 & +2 & +3 & +1 & +3 & Patch together & +1 level of existing divine spellcasting class\\
4 & +3 & +4 & +1 & +4 & Dreadful leadership & +1 level of existing divine spellcasting class\\
5 & +3 & +4 & +1 & +4 & --- & +1 level of existing divine spellcasting class\\
6 & +4 & +5 & +2 & +5 & War caster & +1 level of existing divine spellcasting class\\
7 & +5 & +5 & +2 & +5 & --- & +1 level of existing divine spellcasting class\\
8 & +6 & +6 & +2 & +6 & --- & +1 level of existing divine spellcasting class\\
9 & +6 & +6 & +3 & +6 & Quicken undeath & +1 level of existing divine spellcasting class\\
10 & +7 & +7 & +3 & +7 & Call on the Founders & +1 level of existing divine spellcasting class\\
}
{
\textbf{Weapon and Armor Proficiencies:} Browncloaks are proficient with all martial weapons, whip, bolas, lasso. Browncloaks are proficient with all armors, all shields, including tower shields.

\textbf{Spells per Day:} When a new browncloak level is gained, the character gains new spells per day (and spells known, if applicable) as if he had also gained a level in whatever divine spellcasting class in which he could cast 2nd-level spells before he added the prestige class level. He does not, however, gain any other benefit a character of that class would have gained. If a character had more than one divine spellcasting class in which he could cast 2nd-level spells spontaneously before he became an browncloak, he must decide to which class he adds each level of browncloak for the purpose of determining spells per day.

\textbf{Manipulator (Ex):} From duping potential recruits to bullying terrified troops, the browncloaks is a skilled manipulator, gaining +2 bonus on \skill{Bluff}, \skill{Diplomacy}, and \skill{Intimidate} checks.

\textbf{Rebuke Undead (Su):} Browncloaks gain +3 to their effective cleric level when rebuking undead, and browncloak levels stack with templar levels for purposes of rebuking undead. This effectively puts the browncloak at a par with evil clerics for purposes of rebuking undead.

\textbf{Poison Use:} Browncloaks can apply poisons without chance of accidentally poisoning themselves.

\textbf{Medicinal Purposes (Ex):} At 2nd level, a browncloak gains the ability to learn the \skill{Craft} (alchemy) skill, and gains +4 bonus on \skill{Craft} (alchemy) checks to prepare drugs that are psychoactive, addictive, or both.

\textbf{Patch Together (Sp):} At 3rd level and higher, a browncloak may try to heal a creature with a \skill{Heal} check (DC 10). Patching a wounded creature takes 1 full round and converts 1d6 points of damage into an equal amount of nonlethal damage. If the \skill{Heal} check fails, no damage is converted and the target suffers 1d4 points of damage. A browncloak may only use this ability in the same creature once per day.

\textbf{Dreadful Leadership (Ex):} At 4th level, a browncloak gains the \feat{Leadership} feat, gaining command of the number of Shtas soldier followers indicated by his Leadership score. If the browncloak already has the \feat{Leadership} feat, then he gains +2 to his Leadership score. The browncloak's followers may be living or undead, if a living follower dies and the browncloak animates the follower.

\textbf{War Caster (Ex):} At 6th level, a browncloak becomes disciplined and coolheaded in the heat of battle. He can take 10 on \skill{Concentration} checks to cast spells defensively. He also gains a +2 bonus to Will saves against charm and compulsion effects.

\textbf{Quicken Undeath (Sp):} Beginning at 9th Level, the browncloak can cast \spell{animate dead} as a swift action. The browncloak uses the normal spell slot to cast the spell.

\textbf{Call on the Founders (Ex):} At 10th level, the browncloak is initiated into the dark secrets of the organization's inner circle. This initiation involves meeting the persons that founded the Shtas organization thousands of years ago. ``The Founders,'' as these persons are known, served Daskinor long ago, and are now Athasian Wraiths.

Once per week, the browncloak may summon two Athasian wraiths from the Temple of the Founders in Eldaarich. The browncloak cannot command or rebuke these Wraiths when they arrive, since the Founders are the browncloak's superior officers. The Founders will do what needs to be done to protect what they see as Eldaarich's interests, by possessing bodies and fighting enemies, but when the battle is over, if they perceive that the browncloak has been negligent or incompetent in his command, the Founders will seize the browncloak and take him back to the Temple of the Founders for judgment.
}
{}
{local [Eldaarich]}
{}
{}
{}