\PrestigeClass{Cerulean}
{I am the eye of the storm.}{Krekara, aarakocra cerulean}
{Ceruleans are mages who have discovered how to draw energy for their spells from the Cerulean storm. They are explorers and researchers who have discovered a new power source and seek to exploit it. For whatever reason, cerulean wizards are not content to practice magic as the generations before them have done. Whether they sought more power, an end to the destruction of the world’s plant life, an outlet for their creativity or simply craved new knowledge; the cerulean wizards have found a new way to use magic. A minority of others have been lured to power by Tithian, the one-time king of Tyr who is trapped within the storm and seeks a means to escape.}
{d4}
{a}
{Most races that take to wizardry can become cerulean wizards. Aarakocra have an affinity for high, cold places, and thus find the class to be of particular interest, although they are somewhat reluctant to use the storm’s destructive power. Ceruleans tend to avoid the Veiled Alliance and the agents of the sorcerer-kings. Both parties fear the ceruleans can cause disaster by their tampering with the forces of the Cerulean Storm. NPC ceruleans usually have various agendas. Some seek to release Tithian from his captivity in the Cerulean Storm. Ceruleans can often be found where Tyr Storms frequently wreak havoc, especially in and around Draj.}
{
\textbf{Skills:} \skill{Concentration} 8 ranks, \skill{Craft} (optics) 2 ranks, \skill{Spellcraft} 5 ranks.

\textbf{Feats:} \feat{Empower Spell}.

\textbf{Spells:} Able to cast 3rd level arcane spells.

\textbf{Special:} The character must craft a blue lens focus (see below).
}
{\skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Decipher Script} (Int), \skill{Disguise} (Cha), \skill{Knowledge} (all skills, taken individually) (Int), \skill{Profession} (Wis), \skill{Spellcraft} (Int) and \skill{Survival} (Wis).}
{2}
{\PrestigeSpellTable}{
1 & +0 & +0 & +0 & +2 & Cerulean casting, blue lens focus +1 & +1 level of existing arcane spellcasting class\\
2 & +1 & +0 & +0 & +3 & --- & +1 level of existing arcane spellcasting class\\
3 & +1 & +1 & +1 & +3 & Empower 1/day & +1 level of existing arcane spellcasting class\\
4 & +2 & +1 & +1 & +4 & --- & +1 level of existing arcane spellcasting class\\
5 & +2 & +1 & +1 & +4 & Cerulean blast & +1 level of existing arcane spellcasting class\\
6 & +3 & +2 & +2 & +5 & --- & +1 level of existing arcane spellcasting class\\
7 & +3 & +2 & +2 & +5 & Empower 2/day & +1 level of existing arcane spellcasting class\\
8 & +4 & +2 & +2 & +6 & --- & +1 level of existing arcane spellcasting class\\
9 & +4 & +3 & +3 & +6 & Control weather & +1 level of existing arcane spellcasting class\\
10 & +5 & +3 & +3 & +7 & --- & +1 level of existing arcane spellcasting class\\
}
{
\textbf{Weapon and Armor Proficiencies:} Ceruleans gain no proficiency with any weapon or armor.

\textbf{Cerulean Casting:} Ceruleans have discovered how to draw energy from the Cerulean storm to fuel their spells. They can choose whether to utilize plant energy or cerulean energy when casting spells. Cerulean energy has no impact on the environment.

\textbf{Blue Lens Focus:} The cerulean can channel the energy of the Cerulean Storm through a Blue Lens to substitute material components for arcane spells. However, drawing upon the power of the Cerulean Storm is not without its perils. Depending upon the value of the material component to be substituted, the cerulean suffers an amount of damage that cannot be redirected, absorbed or otherwise avoided. This damage is applied immediately after a spell is cast.

\Table{}{p{1cm} X R p{1cm}}{
& \tableheader Component cost & \tableheader Damage &\\
& 1 Cp or less & 0 & \\
& 1-50 Cp & 5 & \\
& 51-300 Cp & 11 & \\
& 301-750 Cp & 17 & \\
& 750+ Cp & 23 & 
}

Crafting a blue lens requires raw materials worth 50 ceramics. The \skill{Craft} (optics) DC is 20. The lens has 5 hit points and hardness 1. It uses the cerulean’s save values.

\textbf{Empower (Su):} At 3rd level the cerulean can channel energy through the blue lens at the listed amount of times per day to apply the metamagic feat \feat{Empower Spell} to a spell without using a higher level spell slot. This can only be applied to spells with the cold, electricity, fire, sonic or acid descriptors.

\textbf{Cerulean Blast (Su):} At 5th level the cerulean can use the blue lens to unleash blasts of energy from the Cerulean storm as a standard action. This energy blast can target living creatures or objects. The blast is a ranged touch attack with close range (25 feet + 5 feet/2 levels of cerulean) that deals 1d4 points of electricity damage per level of cerulean. A successful Reflex save (DC of 10 + the cerulean’s class level) halves the damage. However, the energy blast has its price. The cerulean suffers 2 points of temporary Wisdom damage each time he uses it.

\textbf{Control Weather (Sp):} At 9th level the cerulean can use the blue lens to summon or eradicate small Tyr Storms. The cerulean can cast \spell{control weather} as per the spell once per day.
}
{}
{arcane}
{}
{}
{}