\PrestigeClass{Elite Sniper}
{The path is clear...}{Last words of Badu, caravan scout}
{In the jungles of the Forest Ridge, unseen halfling snipers with blowguns are the worst predators one can encounter. Out in the open desert landscape, elven snipers wielding the longbow quickly dispatch the commanders of their enemies, turning the tides of raider attacks to the elves' advantage. In the cities, urban snipers attacking from rooftops and through windows are deadly opponents. Elite snipers come from mixed races and backgrounds, but all are dangerous adversaries.}
{d8}
{an}
{Tales of halfling snipers are among the common Athasian legends. Any traveler to the Forest Ridge should rightfully fear the cannibals that move without a sound and strike without being seen. Halfling elite snipers are usually ranger/fighters who choose the ranged combat style. Elven elite snipers are usually fighter/rogues who benefit from additional sneak attack damage.}
{
\textbf{Base Attack Bonus:} +5.

\textbf{Skills:} \skill{Hide} 8 ranks, \skill{Spot} 8 ranks.

\textbf{Feats:} \feat{Point Blank Shot}, \feat{Precise Shot}, \feat{Sniper}, \feat{Weapon Focus} (any ranged weapon).
}
{\skill{Balance} (Dex), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Heal} (Wis), \skill{Hide} (Dex), \skill{Jump} (Str), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Spot} (Wis), \skill{Tumble} (Dex), and \skill{Use Rope} (Dex).}
{4}
{\PrestigeWarriorTable}{
1st & +1 & +0 & +2 & +0 & Improved sniping, poison use, ranged sneak attack +1d6\\
2nd & +2 & +0 & +3 & +0 & Aim\\
3rd & +3 & +1 & +3 & +1 & Ranged sneak attack +2d6\\
4th & +4 & +1 & +4 & +1 & Hide in plain sight\\
5th & +5 & +1 & +4 & +1 & Critical aim, ranged sneak attack +3d6\\
6th & +6 & +2 & +5 & +2 & Hawkeye\\
7th & +7 & +2 & +5 & +2 & Ranged sneak attack +4d6\\
8th & +8 & +2 & +6 & +2 & Marksman\\
9th & +9 & +3 & +6 & +3 & Ranged sneak attack +5d6\\
10th & +10 & +3 & +7 & +3 & Vanish, improved aim\\
}
{
\textbf{Weapon and Armor Proficiencies:} Elite snipers are proficient in light armor. They gain no additional weapon proficiencies.

\textbf{Improved Sniping (Ex):} An elite sniper can add her elite sniper level as a bonus to \skill{Hide} checks made after a ranged attack.

\textbf{Poison Use:} Elite snipers are trained in the use of poisons, and do not risk accidentally poisoning themselves when applying poison to their weapons.

\textbf{Ranged Sneak Attack (Ex):} Any time an elite sniper's target would be denied its Dexterity bonus to AC (whether the target actually has a Dexterity bonus or not), the elite sniper's ranged attack deals an extra 1d6 points of damage. This damage increases by 1d6 every two elite sniper levels after the 1st (3rd, 5th, 7th, and 9th). Should an elite sniper score a critical hit with a ranged sneak attack, this extra damage is not multiplied. This bonus damage is not applied to melee attacks (even if she uses a ranged weapon for the attack), it is only applied to ranged attacks.

An elite sniper can sneak attack only living creatures with discernible anatomies---undead, constructs, oozes, plants, and incorporeal creatures lack vital areas to attack. Any creature that is immune to critical hits is not vulnerable to sneak attacks. The elite sniper must be able to see the target well enough to pick out a vital spot and must be able to reach such a spot. An elite sniper cannot sneak attack while striking a creature with concealment or striking the limbs of a creature whose vitals are beyond reach\

If an elite sniper gets a sneak attack bonus from another source (such as rogue levels), the extra damage stacks.

\textbf{Aim (Ex):} At 2nd level, an elite sniper can take full-round action to make a \skill{Spot} check (CD = target's AC) to improve her next attack against a specific foe. Her next attack against the target ignore armor bonus and natural armor bonus.

\textbf{Hide in Plain Sight (Ex):} While in any sort of natural terrain, an elite sniper of 4th level or higher can use the \skill{Hide} skill even while being observed.

\textbf{Critical Aim (Ex):} At 5th level, an elite sniper gains the \feat{Improved Critical} feat for any ranged weapons with which she has \feat{Weapon Focus}.

\textbf{Hawkeye (Ex):} An elite sniper of 6th level or higher can take 10 when making a \skill{Spot} check even if stress and distraction would normally prevent her from doing so.

\textbf{Marksman (Ex):} An elite sniper of 8th level or higher can make ranged sneak attacks (and sneak attacks, if she has the ability) at a range of up to 18 meters.

\textbf{Vanish (Psi):} At 10th level, the elite sniper can make a \skill{Hide} check to stay hidden after using a full attack action, as a free action. It follows the same rules as Sniping, otherwise---including the bonus from improved sniping.

\textbf{Improved Aim (Ex):} At 10th level, an elite sniper may use aim as a move action.
}
{}
{warcraft}
{}
{}
{}