\PrestigeClass{Master Shipfloater}
{You can rest assured. I will stand by my post until we are there.}{Saeltus, Balikite master shipfloater}
{Master shipfloaters form the core of those who sail the psionic silt skimmers, specializing in the control of the obsidian engines that power them.}
{d4}
{a}
{Psions make up the majority of those who become master shipfloaters, if they travel enough on the silt to warrant the taking of these levels. While psions like the contemplative state one must be in to control the skimmer, those who prefer more action like psychic warriors will find that sitting hours before an obsidian engine to be quite monotonous.}
{
\textbf{Skills:} \skill{Concentration} 8 ranks, \skill{Psicraft} 6 ranks.

\textbf{Feats:} \feat{Shipfloater}, \feat{Skill Focus} (Concentration).

\textbf{Psionics:} Able to manifest 3rd-level powers, with at least one from the psychokinesis discipline.
}
{\skill{Concentration} (Con), \skill{Craft} (Int), \skill{Knowledge} (any) (Int), \skill{Listen} (Wis), \skill{Psicraft} (Int), \skill{Profession} (Wis), \skill{Search} (Int), and \skill{Spot} (Wis).}
{2}
{\PrestigePowerTable}{
1 & +0 & +0 & +0 & +2 & Adept steersman & +1 level of existing manifesting class\\
2 & +1 & +0 & +0 & +3 & Stay in control &\\
3 & +1 & +1 & +1 & +3 & Accomplished steersman & +1 level of existing manifesting class\\
}
{
\textbf{Manifesting:} When a master shipfloater reaches 1st and 3rd level, you gain additional power points per day and access to new powers as if you had also gained a level in whatever manifesting class you belonged to before you added the prestige class. You do not, however, gain any other benefit a character of the class would have gained (bonus feats, metapsionic, psionic or item creation feats, psicrystal special abilities, and so on). This essentially means that you add the level of master shipfloater to the level of whatever manifesting class you have, then determines power points per day, powers known, and manifester level accordingly. If you had more than one manifesting class before you became a master shipfloater, you must decide to which class you add the new level of master shipfloater for the purpose of determining power points per day, powers known, and manifester level.

\textbf{Adept Steersman (Ex):} The master shipfloater knows from experience how to better transfer his psychic energies through an obsidian engine. You gain a bonus equal to twice your master shipfloater level to your \skill{Concentration} check to control the obsidian engine under safe circumstances. The master shipfloater also gains a +2 bonus to its Constitution check to resist taking nonlethal damage by making a forced march while in control of an obsidian engine.

\textbf{Stay In Control (Ex):} At 2nd level, you become so in touch with an obsidian engine that you can control it as a free action. You must stay psionically focused and remain in touch with the engine as normal.

\textbf{Accomplished Steersman (Ex):} By 3rd level, you can use your psychic energies to control and power an obsidian engine far better than other users. From now on, you can take 10 to make your \skill{Concentration} check each round the vessel is in danger of sinking, or if you are personally attacked.
}
{}
{geography or psionics}
{}
{}
{}