\PrestigeClass{Master Scout}
{Stay away from the cacti... STAY AWAY from the cacti.}{Badu, caravan scout}
{Caravan masters, army commanders, raiding parties, adventuring groups, and anyone else traversing the hostile wilderness of Athas, all need the services of the master scout. Experienced wanderers and trackers who know every path and rock provide a safety and advantage valued by those who have come to know their services.}
{d8}
{a}
{Rangers are natural candidates for the master scout class, with their extensive knowledge of the wastes and its creatures. Barbarians also make good scouts due to their fast movement. Thri-kreen, elves and other races with inborn speed and endurance make excellent master scouts, though few can compare with the flight capabilities of aarakocra scouts. Halfling master scouts use their natural aptitude for stealth to compensate for their lack of overland speed. Master scouts are usually mercenaries for hire, many of whom cater to adventurers, or they are members of slave, elf or halfling tribes.}
{
\textbf{Skills:} \skill{Survival} 8 ranks.

\textbf{Feats:} \feat{Track}, \feat{Wastelander}.

\textbf{Special:} Must have the Favored Terrain feature.
}
{
\skill{Balance} (Dex), \skill{Climb} (Str), \skill{Craft} (Int), \skill{Handle Animal} (Cha), \skill{Hide} (Dex), \skill{Jump} (Str), \skill{Knowledge} (nature) (Int), \skill{Listen} (Wis), \skill{Move Silently} (Dex), \skill{Spot} (Wis), \skill{Survival} (Wis) and \skill{Use Rope} (Dex).
}
{6}
{\PrestigeWarriorTable}{
1 & +1 & +2 & +2 & +0 & Blaze trail, hard march\\
2 & +2 & +3 & +3 & +0 & Stealth walk\\
3 & +3 & +3 & +3 & +1 & Swift tracker, favored terrain\\
4 & +4 & +4 & +4 & +1 & Stealth run\\
5 & +5 & +4 & +4 & +1 & Master tracker, resilient\\
}
{
\textbf{Weapon and Armor proficiencies:} Master scouts are proficient in light armor and simple weapons.

\textbf{Blaze Trail:} The master scout is skilled at finding the best route through unfamiliar or obstructed areas and can guide others as well. Add 5 feet to the master scout’s base speed. Up to one additional creature per master scout level can benefit from Blaze Trail. In Favored Terrains, the master scout may add an additional 5 feet to his own and his party’s speed, due to familiarity with these terrains and areas.

\textbf{Hard March:} Due to his knowledge and experience of travel, add the master scout’s Wisdom modifier (if positive) to Fortitude saves for enduring a forced march. Up to one additional creature per master scout level can benefit from Hard March.

\textbf{Stealth Walk:} The master scout no longer suffers a $-5$ penalty to \skill{Move Silently} checks for moving at normal speed. When moving at twice his normal speed, the penalty to \skill{Move Silently} is only $-10$ (instead of the normal $-20$).

\textbf{Swift Tracker:} The master scout can move at his normal speed while following tracks without taking the normal $-5$ penalty. He takes only a $-10$ penalty (instead of the normal $-20$) when moving at up to twice normal speed while tracking.

\textbf{Favored Terrain:} As per the ranger class feature. This benefit scales with previously chosen favored terrains.

\textbf{Stealth Run:} The master scout may \skill{Move Silently} with no penalty while moving at twice his normal speed.

\textbf{Master Tracker:} The master scout may \feat{Track} with no penalty while moving at twice his normal speed.

\textbf{Resilient:} The master scout has survived the Athasian wilderness and has become resilient from experience. He gains a bonus feat chosen from the following list: \feat{Endurance}, \feat{Great Fortitude}, \feat{Iron Will}, \feat{Lightning Reflexes}, \feat{Toughness}.
}
{}
{nature}
{}
{}
{}