\PrestigeClass{Moon Priest}
{You will know fear!}{Talixomac, moon priest}
{The moon priests are the high templars and administrators of Draj. They represent the upper hierarchy of the templarate, those who have attained great influence and political power in Draj. Dressed in blue robes, with a yellow moon in front and in the back of their robes, the Moon Priests are responsible for the administration of the Temples of Ral and Guthay, as well as being the lead organizers of the sacrifices on the Great Pyramid. The moon priests wield considerable power in Draj. Their ability to judge and sentence slaves and sometimes even nobles makes them a force to be reckoned with. For more than a thousand years, the moon priests have served Tectuktitlay, the king of Draj. With a new king in Draj, the moon priests have lost their spellcasting capabilities, but their mastery of rituals tied to their worship of the moons still grant them substantial powers. Also, their knowledge of the inner workings of Draj make the moon priests invaluable in administering the city.

Moon priests are mysterious and powerful individuals. Despite having lost their spells, the arrogance and superiority of their rank is obvious. The Draji still turn to their moon priests for spiritual guidance and the moon priests know to take full advantage of the obedience of their people. Outside of Draj, the moon priests' influence is much less, and it is very rare indeed to find a moon priest outside of Draj, unless it is in one of Draj's client villages.}
{d8}
{a}
{Moon priests are mostly humans, dwarves, muls and half-elves. Pureblooded elves are rare due to their reputation for roguish ways and pterrans and aarakocra have yet to reach Draj in substantial numbers. Half-giant and halfling moon priests are exceedingly rare.}
{
\textbf{Feats:} \feat{Astrologer}, \feat{Mekillothead}, \feat{Secular Authority}.

\textbf{Skills:} \skill{Diplomacy} 8 ranks, \skill{Intimidate} 5 ranks, \skill{Profession} (astrologer) 5 ranks.

\textbf{Special:} Acceptance into the templarate of Draj.
}
{
\skill{Appraise} (Int), \skill{Bluff} (Cha), \skill{Concentration} (Con), \skill{Craft} (Int), \skill{Diplomacy} (Cha), \skill{Forgery} (Int), \skill{Gather Information} (Cha), \skill{Heal} (Wis), \skill{Intimidate} (Cha), \skill{Knowledge} (all skills, taken individually) (Int), \skill{Literacy} (N/A), \skill{Profession} (Wis), \skill{Sense Motive} (Wis), \skill{Speak Language} (N/A) and \skill{Spellcraft} (Int).
}
{2}
{\PrestigeSpellTable}{
1 & +0 & +2 & +0 & +2 & Moon priest's authority & +1 level of existing divine spellcasting class\\
2 & +1 & +3 & +0 & +3 & Guthay's revelation & +1 level of existing divine spellcasting class\\
3 & +2 & +3 & +1 & +3 && +1 level of existing divine spellcasting class\\
4 & +3 & +4 & +1 & +4 & Ral's convergence & +1 level of existing divine spellcasting class\\
5 & +3 & +4 & +1 & +4 && +1 level of existing divine spellcasting class\\
6 & +4 & +5 & +2 & +5 & Jaguar presence & +1 level of existing divine spellcasting class\\
7 & +5 & +5 & +2 & +5 && +1 level of existing divine spellcasting class\\
8 & +6 & +6 & +2 & +6 & Feathered serpent & +1 level of existing divine spellcasting class\\
9 & +6 & +6 & +3 & +6 && +1 level of existing divine spellcasting class\\
10 & +7 & +7 & +3 & +7 & Eclipse & +1 level of existing divine spellcasting class\\
}
{
\textbf{Weapon and Armor Proficiencies:} Moon priests gain no proficiency in any additional weapons. They are proficient in light and medium armors and shields (except tower shields).

\textbf{Moon Priest's Authority (Ex):} The moon priests are feared and respected and they are accompanied by an air of authority wherever they walk. Moon priests receive a +2 bonus to \skill{Intimidate} checks. Moon priest levels stack with templar levels for determining the amount of times per day a character can use the \feat{Secular Authority} feat.

\textbf{Guthay's Revelation (Sp):} Through mysterious rituals conducted by the moon priests, the elite templars of Draj gain the supernatural ability to see what the eyes of ordinary men may not. The moon priest can use see \spell{invisibility} once per day as the spell.

\textbf{Ral's Convergence (Su):} The moon priests know better than anyone else how the moons influence life on Athas. Their study of the moons and the rituals they conduct eventually grant them the power to alter their own fate for better or for worse. Once per day, the moon priest may reroll one d20 roll that he has just made. He must keep the result of the second roll, even if it's worse than the original roll.

\textbf{Jaguar Presence (Sp):} A 6th level moon priest has mastered horrifying rituals, and he may inspire fear in others merely by looking in their direction. Jaguar Presence functions exactly like the \spell{fear} spell. The DC is 14 + the moon priest's Charisma modifier. A moon priest may use this spell-like ability 3/day.

\textbf{Feathered Serpent (Su):} The quatl, or feathered serpent, holds a key role in Draji mythology. Some scholars claim there exists a link between the silk worm and the quatl of legend, and elven tales would have it that the silk wyrms are born on the face of the moon of Guthay. Regardless of fact or fiction, at 8th level, the moon priest has mastered rituals that allow him to sprout massive feathered wings from his back once per day. With these wings, the moon priest may fly at his normal land speed with average maneuverability. If the moon priest would suffer from reduced land speed from wearing medium and heavy armor, or due to carrying capacity, his flying speed is also reduced. The wings disappear after 1 hour.

\textbf{Eclipse (Su):} Only a select few of the most powerful moon priests of all times have mastered the ritual of the Eclipse. Wrapped in secrets and elusive nature, the ritual is in itself is practically impossible to extract from the minds of those who have mastered it. Their minds and very existence are cloaked by the shroud of the moons. 10 level moon priests are treated as if they
had \spell{mindblank} permanently cast on them. If Eclipse is dispelled, the moon priest can reactivate it as a free action.

\subsubsection{Ex-Templars}
A moon priest who abandons his sorcerer-monarch, or whose sorcerer-monarch dies, loses all templar spellcasting abilities. If the moon priest later becomes the templar of another sorcerer-monarch, he immediately regains his full templar spellcasting abilities.
}
{}
{local [Draj] or religion}
{They represent the upper hierarchy of the templarate.}
{Some moon priests can sprout colorful wings from their backs, like a quatl.}
{While the moon priests have impressive abilities, they can no longer cast any spells.}