\Chapter{Introduction}
{For thousands of years, the Tablelands have remained untouched: its politics frozen in a delicate stalemate, its life in a balance even more delicate. It is true that the Dragon Kings amused themselves with their petty wars, rattling sabers to punctuate the passing of ages. It is true that, occasionally, another city would be swallowed by the wastes.

But there were no surprises. The Dragon Kings steered everything from their omnipotent perches, content in their superiority, but ever thirsting for challenge. All that has changed. The Tablelands have been thrown into turmoil, the likes of which have not been seen since times forgotten. The Dragon Kings have been thrown into confusion, grasping for the tedium they so recently lamented.

And yet I fear the worst is yet to come. Change is in the air, and change has never come gently to Athas.}{Oronis, sorcerer-king of Kurn}

% \Figure*{b}{images/raiders-2.png}

\Capitalize{D}{ark} Sun 3.5 is a new edition of the {\tableheader Dark Sun} campaign setting, written as a revision of athas.org's {\tableheader Dark Sun} 3 rulebook and the \emph{Athasian Emporium}. This rulebook condenses all d20 System information available under OGL, including psionic rules, but it also changes the system a bit. In addition, you might find useful to download the \emph{Terrors of Athas} (ToA), \emph{Terrors of the Dead Lands} (TotDL), and \emph{Faces of the Forgotten North} (FFN), since this book does not contain information on monsters.

This document is intended for an audience already familiar with the {\tableheader Dark Sun} campaign setting, and does not attempt to detail the world of Athas in full. For more information on Athas, visit \url{www.athas.org}---the official {\tableheader Dark Sun} website. In addition to the latest version of this document, you may find other {\tableheader Dark Sun} material available as free downloads.

All {\tableheader Dark Sun} products published by TSR may be purchased from RPGNow! as PDF downloads.

\input{sections/introduction/this-is-athas.tex}
% \Figure*{b}{images/adventurer-2.png}



\section{Where to Begin}
Players should begin by creating their {\tableheader Dark Sun} character after reading the first seven chapters of this book. Players may also want to read the timeline in order to understand the history of Athas. Remember to discuss with your DM before creating your character to find out what options and other books are allowed in his campaign.

The DM should start with \chapref{Life on Athas} and read material relevant to the locations, \chapref{Campaigns} for guidelines and tips when running your campaign, and \chapref{Others Ages of Play} to understand more about the era of play on which your campaign will focus.


\subsection{What You Need to Play}
This book contains revisions on the material from the three core rulebooks for {\tableheader Dungeons \& Dragons v3.5} and the \emph{Expanded Psionics Handbook} released under Open Game License (OGL). Throughout this book, superscript abbreviations are often used to denote game elements that appear in certain supplements: \emph{Complete Adventurer} (CAd), \emph{Complete Arcane} (CAr), \emph{Complete Champion} (CC), \emph{Complete Divine} (CD), \emph{Complete Mage} (CM), \emph{Complete Psionics} (CP), \emph{Complete Scoundrel} (CS), \emph{Complete Warrior} (CW), \emph{Player's Handbook II} (PH2). Having any of all of these supplements will enhance your enjoyment of this book, but they are not required.


\subsection{What Changed?}
Many new options were added to previous base classes, and some have been completely rewritten. Getting inspiration on the {\tableheader Dungeons \& Dragons 5e}, advantage and disadvantage were added to the system as well as multiclass prerequisites for base classes. Spell lists, domains, and magical items were changed. For a summary of all the changes between the d20 System rules under OGL and this book, see \apxref{Changes from d20 System}.

% There are changes between the original \url{www.athas.org} rulebook and this revision, with some prestige classes being excluded, and others being reworked. New feats were also added and some of the previous ones were reworked. For a summary of all the changes between the \url{www.athas.org} rulebook and this book, see \apxref{Changes from Dark Sun 3}.

\input{sections/introduction/the-core-mechanic.tex}



\section{Abilities}
Each character in {\tableheader Dark Sun} has six abilities: Strength (abbreviated Str), Dexterity (Dex), Constitution (Con), Intelligence (Int), Wisdom (Wis), and Charisma (Cha). Each of your abilities above average gives you a bonus on certain die rolls, and abilities below average give you a penalty on other die rolls.


\BigTable{Ability Modifiers and Bonus Spells}{cc *{10}C}{
  & & \multicolumn{10}{c}{\tableheader Bonus Spells (by spell level)} \\
  \cmidrule[0.5pt]{3-12}
  \tableheader Score
& \tableheader Modifier
& \tableheader 0
& \tableheader 1st
& \tableheader 2nd
& \tableheader 3rd
& \tableheader 4th
& \tableheader 5th
& \tableheader 6th
& \tableheader 7th
& \tableheader 8th
& \tableheader 9th \\
  1 & $-5$ & \cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}\\
  2--3 & $-4$ & \cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}\\
  4--5 & $-3$ & \cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}\\
  6--7 & $-2$ & \cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}&\cellcolor{TableColor}\\
  8--9 & $-1$ &\multicolumn{10}{c}{\multirow{-5}{*}{\bfseries Can't cast spells tied to this ability}}\\
  10--11 & 0 &&&&&&&&&&\\
  12--13 & +1 && 1 &&&&&&&&\\
  14--15 & +2 && 1 & 1 &&&&&&&\\
  16--17 & +3 && 1 & 1 & 1 &&&&&&\\
  18--19 & +4 && 1 & 1 & 1 & 1 &&&&&\\
  20--21 & +5 && 2 & 1 & 1 & 1 & 1 &&&&\\
  22--23 & +6 && 2 & 2 & 1 & 1 & 1 & 1 &&&\\
  24--25 & +7 && 2 & 2 & 2 & 1 & 1 & 1 & 1 &&\\
  26--27 & +8 && 2 & 2 & 2 & 2 & 1 & 1 & 1 & 1 &\\
  28--29 & +9 && 3 & 2 & 2 & 2 & 2 & 1 & 1 & 1 & 1 \\
  30--31 & +10 && 3 & 3 & 2 & 2 & 2 & 2 & 1 & 1 & 1 \\
  32--33 & +11 && 3 & 3 & 3 & 2 & 2 & 2 & 2 & 1 & 1 \\
  34--35 & +12 && 3 & 3 & 3 & 3 & 2 & 2 & 2 & 2 & 1 \\
  36--37 & +13 && 4 & 3 & 3 & 3 & 3 & 2 & 2 & 2 & 2 \\
  38--39 & +14 && 4 & 4 & 3 & 3 & 3 & 3 & 2 & 2 & 2 \\
  40--41 & +15 && 4 & 4 & 4 & 3 & 3 & 3 & 3 & 2 & 2
}

\BigTable{Ability Scores and Bonus Power Points}{l *{20}{C}}{
  & \multicolumn{20}{c}{\tableheader Bonus Power Points (by class level)} \\
  \cmidrule[0.5pt]{2-21}
  \tableheader Score
& \tableheader 1st
& \tableheader 2nd
& \tableheader 3rd
& \tableheader 4th
& \tableheader 5th
& \tableheader 6th
& \tableheader 7th
& \tableheader 8th
& \tableheader 9th
& \tableheader 10th
& \tableheader 11th
& \tableheader 12th
& \tableheader 13th
& \tableheader 14th
& \tableheader 15th
& \tableheader 16th
& \tableheader 17th
& \tableheader 18th
& \tableheader 19th
& \tableheader 20th \\
10--11 &&&&&&&&&&&&&&&&&&&&\\
12--13 &   &  1 &  1 &  2 &  2 &  3 &  3 &  4 &  4 &  5 &  5 &  6 &  6 &   7 &   7 &   8 &   8 &   9 &   9 &  10 \\
14--15 & 1 &  2 &  3 &  4 &  5 &  6 &  7 &  8 &  9 & 10 & 11 & 12 & 13 &  14 &  15 &  16 &  17 &  18 &  19 &  20 \\
16--17 & 1 &  3 &  4 &  6 &  7 &  9 & 10 & 12 & 13 & 15 & 16 & 18 & 19 &  21 &  22 &  24 &  25 &  27 &  28 &  30 \\
18--19 & 2 &  4 &  6 &  8 & 10 & 12 & 14 & 16 & 18 & 20 & 22 & 24 & 26 &  28 &  30 &  32 &  34 &  36 &  38 &  40 \\
20--21 & 2 &  5 &  7 & 10 & 12 & 15 & 17 & 20 & 22 & 25 & 27 & 30 & 32 &  35 &  37 &  40 &  42 &  45 &  47 &  50 \\
22--23 & 3 &  6 &  9 & 12 & 15 & 18 & 21 & 24 & 27 & 30 & 33 & 36 & 39 &  42 &  45 &  48 &  51 &  54 &  57 &  60 \\
24--25 & 3 &  7 & 10 & 14 & 17 & 21 & 24 & 28 & 31 & 35 & 38 & 42 & 45 &  49 &  52 &  56 &  59 &  63 &  66 &  70 \\
26--27 & 4 &  8 & 12 & 16 & 20 & 24 & 28 & 32 & 36 & 40 & 44 & 48 & 52 &  56 &  60 &  64 &  68 &  72 &  76 &  80 \\
28--29 & 4 &  9 & 13 & 18 & 22 & 27 & 31 & 36 & 40 & 45 & 49 & 54 & 58 &  63 &  67 &  72 &  76 &  81 &  85 &  90 \\
30--31 & 5 & 10 & 15 & 20 & 25 & 30 & 35 & 40 & 45 & 50 & 55 & 60 & 65 &  70 &  75 &  80 &  85 &  90 &  95 & 100 \\
32--33 & 5 & 11 & 16 & 22 & 27 & 33 & 38 & 44 & 49 & 55 & 60 & 66 & 71 &  77 &  82 &  88 &  93 &  99 & 104 & 110 \\
34--35 & 6 & 12 & 18 & 24 & 30 & 36 & 42 & 48 & 54 & 60 & 66 & 72 & 78 &  84 &  90 &  96 & 102 & 108 & 114 & 120 \\
36--37 & 6 & 13 & 19 & 26 & 32 & 39 & 45 & 52 & 58 & 65 & 71 & 78 & 84 &  91 &  97 & 104 & 110 & 117 & 123 & 130 \\
38--39 & 7 & 14 & 21 & 28 & 35 & 42 & 49 & 56 & 63 & 70 & 77 & 84 & 91 &  98 & 105 & 112 & 119 & 126 & 133 & 140 \\
40--41 & 7 & 15 & 22 & 30 & 37 & 45 & 52 & 60 & 67 & 75 & 82 & 90 & 97 & 105 & 112 & 120 & 127 & 135 & 142 & 150 \\
}


\subsection{Ability Scores}
% Previous editions used a rolling method that produced, on average, higher stats. This was supposed to convey that Athas was a much harsher world than normal {\tableheader Dungeons \& Dragons} campaign worlds, and that its denizens had adapted to compensate. However, the meaning of an attribute has changed in 3rd edition, and attributes start having a positive effect much sooner than they did in 2nd edition. Whereas many stats didn't start having a positive effect until they were at least 14, now as low as 12 have a positive effect. Using higher overall attributes for characters in {\tableheader Dark Sun} actually makes it easier for characters to survive and overcome obstacles that should be challenging, which would mean that the effective difficulty of a campaign would actually be lower using this stat generation method.

% \subsubsection{Creating Ability Scores}
To create an ability score for your character, roll 5d6. Disregard the two lowest dice rolls and sum the rest. The result is a number between 3 (horrible) and 18 (tremendous). The average ability score for the typical commoner is 10 or 11, but your character is not typical. The most common ability scores for player characters (PCs) are 13 and 14.

Make this roll six times, recording each result on a piece of paper. Once you have six scores, assign each score to one of the six abilities.

% \textbf{Point Buy:} All abilities scores start at 8. Take a number of points according to the type of your campaign to spread out among all abilities. For ability scores of 14 or lower, you buy additional points on a 1-for-1 basis. For ability scores higher than 14, it costs a little more.

% \Table{}{CC CC}{
%   \tableheader Ability Score
% & \tableheader Point Cost
% & \tableheader Ability Score
% & \tableheader Point Cost \\
%    9 & 1 & 14 & 6 \\
%   10 & 2 & 15 & 8 \\
%   11 & 3 & 16 & 10 \\
%   12 & 4 & 17 & 13 \\
%   13 & 5 & 18 & 16 \\
% }

% \Table{}{X r}{
%   \tableheader Type of Campaign
% & \tableheader Points Allowed \\
%   Low-powered campaign  & 15 points \\
%   Challenging campaign  & 22 points \\
%   Normal campaign       & 25 points \\
%   Tougher campaign      & 28 points \\
%   High-powered campaign & 32 points \\
% }

\subsubsection{Ability Modifiers}
Each ability, after changes made because of race, has a modifier ranging from $-5$ to +5. \tabref{Ability Modifiers and Bonus Spells} shows the modifier for each score. It also shows bonus spells, which you'll need to know about if your character is a spellcaster.

The modifier is the number you apply to the die roll when your character tries to do something related to that ability. You also use the modifier with some numbers that aren't die rolls. A positive modifier is called a bonus, and a negative modifier is called a penalty.

\subsubsection{Abilities, Spellcasters and \hskip4em Manifesters}
The ability that governs bonus spells depends on what type of spellcaster your character is: Intelligence for wizards; Wisdom for clerics, druids, and rangers; or Charisma for templars. In addition to having a high ability score, a spellcaster must be of high enough class level to be able to cast spells of a given spell level.

Psions also depend on abilities for additional power for each discipline: Intelligence for metacreativity and psychokinesis, Wisdom for clairscience and telepathy, and Constitution for psychometabolism and psychoportation. The modifier for this ability is referred to as your key ability modifier. If your character's key ability score is 9 or lower, you can't manifest powers from that discipline.
% Psionic classes also depend on abilities for additional power: Intelligence for psions, Wisdom for psychic warriors, and Charisma for wilders. The modifier for this ability is referred to as your key ability modifier. If your character's key ability score is 9 or lower, you can't manifest powers from that psionic class.

Just as a high Intelligence score grants bonus spells to a wizard and a high Wisdom score grants bonus spells to a cleric, a character who manifests powers (psions) gains bonus power points according to each of the following ability scores: Constitution, Intelligence, and Wisdom scores. Refer to \tabref{Ability Scores and Bonus Power Points}.

\textbf{How To Determine Bonus Power Points:} Your key ability score grants you additional power points equal to your key ability modifier $\times$ your manifester level $\times$ \onehalf. \tabref{Ability Scores and Bonus Power Points} shows these calculations for class levels 1st through 20th and key ability scores from 10 to 41.


\subsection{The Abilities}
Each ability partially describes your character and affects some of his or her actions.

\subsubsection{Strength (Str)}
Strength measures your character's muscle and physical power. This ability is especially important for gladiators, fighters, barbarians, and rangers because it helps them prevail in combat. Strength also limits the amount of equipment your character can carry.

You apply your character's Strength modifier to:
\begin{itemize*}
\item Melee attack rolls.
\item Damage rolls when using a melee weapon or a thrown weapon (including a sling). (Exceptions: Off-hand attacks receive only one-half the character's Strength bonus, while two-handed attacks receive one and a half times the Strength bonus. A Strength penalty, but not a bonus, applies to attacks made with a bow that is not a composite bow.)
\item \skill{Climb}, \skill{Jump}, and \skill{Swim} checks. These are the skills that have Strength as their key ability.
\item Strength checks (for breaking down doors and the like).
\end{itemize*}

\subsubsection{Dexterity (Dex)}
Dexterity measures hand-eye coordination, agility, reflexes, and balance. This ability is the most important one for thieves, scouts, and bards, but it's also high on the list for characters who typically wear light or medium armor (gladiators, rangers, and barbarians) or no armor at all (psions and wizards), and for anyone who wants to be a skilled archer.

You apply your character's Dexterity modifier to:
\begin{itemize*}
\item Ranged attack rolls, including those for attacks made with bows, crossbows, throwing axes, and other ranged weapons.
\item Armor Class (AC), provided that the character can react to the attack.
\item Reflex saving throws, for avoiding fireballs and other attacks that you can escape by moving quickly.
\item \skill{Balance}, \skill{Escape Artist}, \skill{Hide}, \skill{Move Silently}, \skill{Open Lock}, \skill{Ride}, \skill{Sleight of Hand}, \skill{Tumble}, and \skill{Use Rope} checks. These are the skills that have Dexterity as their key ability.
\end{itemize*}

\subsubsection{Constitution (Con)}
Constitution represents your character's health and stamina. A Constitution bonus increases a character's hit points, so the ability is important for all classes.

You apply your character's Constitution modifier to:
\begin{itemize*}
\item Each roll of a Hit Die (though a penalty can never drop a result below 1---that is, a character always gains at least 1 hit point each time he or she advances in level).
\item Fortitude saving throws, for resisting poison and similar threats.
\item \skill{Concentration} checks. Concentration is a skill, important to spellcasters, that has Constitution as its key ability.
\end{itemize*}

The minimum Constitution score needed for a psion to manifest a psychometabolism or psychoportation power is 10 + the power's level.

If a character's Constitution score changes enough to alter his or her Constitution modifier, the character's hit points also increase or decrease accordingly.

\subsubsection{Intelligence (Int)}
Intelligence determines how well your character learns and reasons. This ability is important for wizards because it affects how many spells they can cast, how hard their spells are to resist, and how powerful their spells can be. It's also important for any character who wants to have a wide assortment of skills.

You apply your character's Intelligence modifier to:
\begin{itemize*}
\item The number of languages your character knows at the start of the game.
\item The number of skill points gained each level. (But your character always gets at least 1 skill point per level.)
\item \skill{Appraise}, \skill{Craft}, \skill{Decipher Script}, \skill{Disable Device}, \skill{Forgery}, \skill{Knowledge}, \skill{Search}, and \skill{Spellcraft} checks. These are the skills that have Intelligence as their key ability.
\end{itemize*}

A wizard gains bonus spells based on her Intelligence score. The minimum Intelligence score needed to cast a wizard spell is 10 + the spell's level.

A psion gains bonus power points based on his Intelligence score. The minimum Intelligence score needed to manifest a metacreativity or psychokinesis power is 10 + the power's level.

An animal has an Intelligence score of 1 or 2. A creature of human-like intelligence has a score of at least 3.

\subsubsection{Wisdom (Wis)}
Wisdom describes a character's willpower, common sense, perception, and intuition. While Intelligence represents one's ability to analyze information, Wisdom represents being in tune with and aware of one's surroundings. Wisdom is the most important ability for clerics, druids, and templars, and it is also important for psions and rangers. If you want your character to have acute senses, put a high score in Wisdom. Every creature has a Wisdom score.

You apply your character's Wisdom modifier to:
\begin{itemize*}
\item Will saving throws (for negating the effect of charm person and other spells).
\item \skill{Heal}, \skill{Listen}, \skill{Profession}, \skill{Sense Motive}, \skill{Spot}, and \skill{Survival} checks. These are the skills that have Wisdom as their key ability.
\end{itemize*}

Clerics, druids, and rangers get bonus spells based on their Wisdom scores. The minimum Wisdom score needed to cast a cleric, druid, or ranger spell is 10 + the spell's level.

The minimum Wisdom score needed to manifest a clairsentience or telepathy power is 10 + the power's level.

\subsubsection{Charisma (Cha)}
Charisma measures a character's force of personality, persuasiveness, personal magnetism, ability to lead, and physical attractiveness. This ability represents actual strength of personality, not merely how one is perceived by others in a social setting. Charisma is important for clerics and templars, since it affects their ability to turn undead. Every creature has a Charisma score.

You apply your character's Charisma modifier to:
\begin{itemize*}
\item \skill{Bluff}, \skill{Diplomacy}, \skill{Disguise}, \skill{Gather Information}, \skill{Handle Animal}, \skill{Intimidate}, \skill{Perform}, and \skill{Use Magic Device} checks. These are the skills that have Charisma as their key ability.
\item Checks that represent attempts to influence others.
\item Turning checks for clerics and templars attempting to turn zombies, vampires, and other undead.
\end{itemize*}

Templars get bonus spells based on their Charisma scores. The minimum Charisma score needed to cast a templar spell is 10 + the spell's level.

\subsubsection{Changing Ability Scores}
When an ability score changes, all attributes associated with that score change accordingly. A character does not retroactively get additional skill points for previous levels if she increases her intelligence.
