\Chapter{Character Classes}
{From the lowliest slave to the highest templar, our fates are decided for us. The slave at the hands of the master, and the templar at the will of the king. Pray to Ral and Guthay that your children are born when the stars align to favor them. Few are those privileged to choose their own path of life, and cursed are those for they are bound by choice and have but themselves to blame for their misfortune. The bard addicted to his alchemical mixtures, the templar imprisoned for his crimes, and the gladiator sacrificed for the thrill of the fight. It is the choices that define who you are and how you die, regardless of who makes them.}{The Oracle, Blue Shrine Scrolls}

\section{The Classes}
\Capitalize{Y}{ou} may notice that there are some classes not described here. Some of these are core classes that have been deemed inappropriate to the feel of the {\tableheader Dark Sun} campaign setting. Others are classes from previous editions of {\tableheader Dark Sun} that don't fit in the 3e.

\textbf{Monk:} There are several monasteries on Athas, though little evidence in previous material supports the martial artist variety of monk. Monks are too few in number to warrant a core class.

\textbf{Paladin:} The idea of doing good for its own sake runs contrary to the tone and theme of the setting. There are no gods to reward selfless acts, and no grand traditions of chivalry and nobility to promote. In essence, Athas is a world where evil behavior is the norm.

\textbf{Sorcerer:} Mechanically, a sorcerer's spontaneous casting and a psion's manifesting are similar, thus including the sorcerer removes some of the uniqueness of the psion. Some also feel that an arcane spellcaster without a spellbook violates the flavor of the setting.

\textbf{Soulknife:} There is no precedent of a concept such as the soulknife in any previous material. However, in a metal-poor, high psionic world, the ability to manifest a weapon using the mind has its place. There would probably not be enough soulknives to warrant a core class, which would need to be shoehorned into the existing campaign world.

\textbf{Trader:} The trader class, present in previous editions of the setting is not included here because it's benefits and traits are nearly all encompassed in the standard set of 3rd edition skills. Reproducing the class is easily done using a standard skill-focused class, like the rogue or bard, or using the expert NPC class.

Some DMs choose to run {\tableheader Dark Sun} as a low-magic, low treasure campaign. In such games, the monk and soulknife could become unbalanced because of their lack of dependence on treasure.

DMs are free to include any of the above core classes in their games, but these classes will not appear in any official releases.

\subsection{Changes from Previous Version}
This book brings revisions to some of the base classes, in order to address the power gap in high levels---specially with respect to how the spells and psionic powers impact the adventure. This means that some classes have more class features. The number of power points available each level was also changed for all psionic classes.

\subsection{The Power Point Reserve}
Psionic characters fuel their abilities through a pool, or reserve, of power points. Your power point reserve is equal to your base power points gained from your class, bonus power points from a high key ability score (see \chapref{Introduction}), and any additional bonus power points from sources such as your character race and feat selections.


\Table{}{lX}{
%   \tableheader Class
% & \tableheader Description\\

\multicolumn{2}{l}{\textbf{Warriors}}\\
Barbarian       & Brute that rages in battle \\
Fighter         & Formal soldier dedicated to war \\
Gladiator       & Survivor of the many arenas in Athas \\
Ranger          & Wanderer of the wastes \\

\cmidrule[0pt]{1-2}
&\\
\cmidrule[0pt]{1-2}
\multicolumn{2}{l}{\textbf{Rogues}}\\
Bard            & Minstrel that serves as assassin and merchant \\
Scout           & Survivalist focused on fast reconnaissance \\
Thief           & Rogues specialized against unprepared foes \\

&\\
\cmidrule[0pt]{1-2}
\multicolumn{2}{l}{\textbf{Power-Wielders}}\\
Cleric          & Elemental priest devoted to preservation \\
Druid           & Protector of the land with shape-shifting abilities \\
Psion           & Student of the Way \\
% Psychic warrior & Warrior that applies the Way in combat \\
Templar         & Disciples and enforcers of sorcerer-kings \\
% Wilder          & Psionicist with overflowing Will \\
Wizard          & Arcanist that gathers energy from plant-life \\
}

\subsection{Level-Dependent Benefits}
Besides the bonuses given by their character classes, all characters gain additional feats and increase their abilities from advancing in level as seen in \tabref{Level-Dependent Benefits}. This does not count a race's level adjustment---only character classes.

\textbf{Feat:} Every character gets their first feat at 1st level. At 3rd level and every other 3 levels, characters gain another feat. More information on feats on \chapref{Feats}.

\textbf{Ability Score Increase:} At 4th level and every 4 levels thereafter, the player chooses one of their character's ability scores to increase by 1 point. This improvement is permanent.

\textbf{Class Skill Max Ranks:} The maximum number of ranks a character can have in a class skill is equal to their character level +3.

\textbf{Cross-Class Skill Max Ranks:} For cross-class skills, the maximum number of ranks is one-half the maximum for a class skill.

\Table{Level-Dependent Benefits}{lccCC}{
  \multirow[b]{2}{13mm}{\hskip-1mm \tableheader Character Level}
& \multirow[b]{2}{5mm}{\centering \tableheader Feat}
& \multirow[b]{2}{16mm}{\centering \tableheader Ability Score\\Increase}
& \multicolumn{2}{c}{\tableheader Max Ranks}\\
\cmidrule[0.5pt]{4-5}
&&& \tableheader Class Skill & \tableheader Cross-Class Skill\\

 1st & 1st &     &  4 & 2          \\
 2nd &     &     &  5 & 2\onehalf  \\
 3rd & 2nd &     &  6 & 3          \\
 4th &     & 1st &  7 & 3\onehalf  \\
 5th &     &     &  8 & 4          \\
 6th & 3rd &     &  9 & 4\onehalf  \\
 7th &     &     & 10 & 5          \\
 8th &     & 2nd & 11 & 5\onehalf  \\
 9th & 4th &     & 12 & 6          \\
10th &     &     & 13 & 6\onehalf  \\
11th &     &     & 14 & 7          \\
12th & 5th & 3rd & 15 & 7\onehalf  \\
13th &     &     & 16 & 8          \\
14th &     &     & 17 & 8\onehalf  \\
15th & 6th &     & 18 & 9          \\
16th &     & 4th & 19 & 9\onehalf  \\
17th &     &     & 20 & 10         \\
18th & 7th &     & 21 & 10\onehalf \\
19th &     &     & 22 & 11         \\
20th &     & 5th & 23 & 11\onehalf \\
}


% \Figure[\columnwidth-7mm]{b}{images/cleric-4.png}

% \subsection{Other Sources}
% In addition to the many options presented here, a few more base classes should be considered for {\tableheader Dark Sun} characters. This edition made a revision in most of the base classes. Because of this, some minor changes are suggested for each class.

% \textbf{Scout} (\emph{Complete Adventurer}): Scout brings a mix of ranger and rogue that is adequate for the setting, being part of the core components of any caravan. When using this class, change the rate of bonus feats to: at 4th level and every three levels thereafter (7th, 10th, 13th, 16th, and 19th level).

% \textbf{Lurk} (\emph{Complete Psionic}): This psionic rogue is as prevalent as any psychic warrior. When using this class, change the number of power points per day to match a psychic warrior of the same level.


\clearpage
\input{sections/classes/barbarian.tex}
\input{sections/classes/bard.tex}
\input{sections/classes/cleric.tex}
\input{sections/classes/druid.tex}
\input{sections/classes/fighter.tex}
\input{sections/classes/new-gladiator.tex}
\input{sections/classes/new-psion.tex}
\input{sections/classes/ranger.tex}
\input{sections/classes/scout.tex}
\input{sections/classes/templar.tex}
\input{sections/classes/rogue.tex}
\input{sections/classes/wizard.tex}
\input{sections/classes/multiclass-characters.tex}
\input{sections/classes/alternative-class-features.tex}
