\Chapter{Skills}
{You can learn much from observing another being. The way the gith hunches before it leaps at you, or how the aarakocra circles before it dives. The way the halfling inhales and pauses briefly before shooting his poisoned needles, or how the Urikite trader licks his lips before making his final offer. But appearances can deceive. No two creatures are alike. Remember that when the gith hunches before casting a defiler spell, or the Urikite trader moistens his lips and spits a needle at you.}{The Oracle, Blue Shrine Scrolls}
\section{Skill Summary}
\Capitalize{I}{f} you buy a class skill, your character gets 1 rank (equal to a +1 bonus on checks with that skill) for each skill point. If you buy other classes' skills (cross-class skills), you get \onehalf rank per skill point.

Your maximum rank in a class skill is your character level + 3.

Your maximum rank in a cross-class skill is one-half of this number (do not round up or down).

\subsection{Using Skills}
To make a skill check, roll:

{
	\centering
	\vskip1em
	{\Large 1d20 + \textit{skill modifier}}
	\vskip.3em
	\Cell{\small\textit{Skill modifier} = skill rank + ability modifier\\\small + miscellaneous modifiers.}
	\vskip1em
}

This roll works just like an attack roll or a saving throw---the higher the roll, the better. Either you're trying to match or exceed a certain Difficulty Class (DC), or you're trying to beat another character's check result.

\textbf{Skill Ranks:} A character's number of ranks in a skill is based on how many skill points a character has invested in a skill. Many skills can be used even if the character has no ranks in them; doing this is called making an untrained skill check.

\textbf{Ability Modifier:} The ability modifier used in a skill check is the modifier for the skill's key ability (the ability associated with the skill's use). The key ability of each skill is noted in its description.

\textbf{Miscellaneous Modifiers:} Miscellaneous modifiers include racial bonuses, armor check penalties, and bonuses provided by feats, among others.

\subsection{Acquiring Skill Ranks}
Each skill point you spend on a class skill gets you 1 rank in that skill. Class skills are the skills found on your character's class skill list. Each skill point you spend on a cross-class skill gets your character \onehalf rank in that skill. Cross-class skills are skills not found on your character's class skill list. (Half ranks do not improve your skill check, but two \onehalf ranks make 1 rank.) You can't save skill points to spend later.

The maximum rank in a class skill is the character's level + 3. If it's a cross-class skill, the maximum rank is half of that number (do not round up or down).

Regardless of whether a skill is purchased as a class skill or a cross-class skill, if it is a class skill for any of your classes, your maximum rank equals your total character level + 3.

\input{sections/skills/using-skills.tex}
\input{sections/skills/skill-descriptions.tex}