\Chapter{Feats}
{Turning from political histories to folklore, who has not heard a bard's sonorous voice sing the marvels of the world before ours? The lyrics speak of a land of plenty, with grass on every hill and water in every draw. Fields of barley and whey stretched for miles, and there were so many sheep that the herds could not be counted. Proud forests of oak and maple covered the wild lands, and men were the masters of the beasts.

These ballads sing the praises of warriors who fought not for food or entertainment, but for honor, glory, and lady love. The kings in these songs were noble warriors who fought terrible beasts and waged righteous wars in defense of their subjects. Clearly, they were men who placed the needs of their domains above their own desires and cravings.}
{The Wanderer's Journal}

\section{Prerequisites}
Some feats have prerequisites. Your character must have the indicated ability score, class feature, feat, skill, base attack bonus, or other quality designated in order to select or use that feat. A character can gain a feat at the same level at which he or she gains the prerequisite.

A character can't use a feat if he or she has lost a prerequisite.

\section{Types Of Feats}
Some feats are general, meaning that no special rules govern them as a group. Others are item creation feats, which allow spellcasters to create magic items of all sorts. A metamagic feat lets a spellcaster prepare and cast a spell with greater effect, albeit as if the spell were a higher spell level than it actually is.

\subsection{Fighter Bonus Feats}
Any feat designated as a fighter feat can be selected as a fighter's bonus feat. This designation does not restrict characters of other classes from selecting these feats, assuming that they meet any prerequisites.

\subsection{Racial Feats}
Feats designated as racial feats require the character to be of a specific race in order to select the feat. These feats share no other special properties and are considered to be a subset of a larger category of feats (e.g., general, psionic, or tactical).

\subsection{Regional Feats}
Regional feats are feats that require that a character belongs to a certain culture, either a race or a specified area. These feats can only be selected at 1st level. A character can only take one single regional feat. This is because most regional feats are more powerful when compared to other feats.

\subsection{Psionic Feats}
Psionic feats are available only to characters and creatures with the ability to manifest powers. (In other words, they either have a power point reserve or have psi-like abilities.)

Because psionic feats are supernatural abilities---a departure from the general rule that feats do not grant supernatural abilities---they cannot be disrupted in combat (as powers can be) and generally do not provoke attacks of opportunity (except as noted in their descriptions). Supernatural abilities are not subject to power resistance and cannot be dispelled; however, they do not function in areas where psionics is suppressed, such as a null psionics field. Leaving such an area immediately allows psionic feats to be used.

Many psionic feats can be used only when you are psionically focused; others require you to expend your psionic focus to gain their benefit. Expending your psionic focus does not require an action; it is part of another action (such as using a feat). When you expend your psionic focus, it applies only to the action for which you expended it.

\subsection{Divine Feats}
Divine feats are available only to characters with the ability to turn or rebuke undead. Using a divine feat costs at least one turn attempt from the character's number of attempts each day. If you don't have any turn or rebuke attempts left, you can't use a divine feat.

As psionic feats, divine feats are also supernatural abilities. Activating a divine feat does not provoke attacks of opportunity, unless otherwise noted. You can activate only one divine feat (or turn/rebuke once) per round.

\subsection{Raze Feats}
Raze feats are feats that require an arcane spellcaster to be a defiler. They can only be applied when defiling.

Multiple raze feats can be applied at the same time. For example, a defiler who has \feat{Distance Raze}, \feat{Destructive Raze} and \feat{Fast Raze} can benefit from all of them when casting a single spell. A wizard's bonus feats can be used to acquire Raze feats if the wizard fulfills the feat prerequisites.

\subsection{Metamagic Feats}
As a spellcaster's knowledge of magic grows, she can learn to cast spells in ways slightly different from the ways in which the spells were originally designed or learned. Preparing and casting a spell in such a way is harder than normal but, thanks to metamagic feats, at least it is possible. Spells modified by a metamagic feat use a spell slot higher than normal. This does not change the level of the spell, so the DC for saving throws against it does not go up.

\textbf{Wizards and Divine Spellcasters:} Wizards and divine spellcasters must prepare their spells in advance. During preparation, the character chooses which spells to prepare with metamagic feats (and thus which ones take up higher-level spell slots than normal).

\textbf{Templars:} Templars choose spells as they cast them. They can choose when they cast their spells whether to apply their metamagic feats to improve them. As with other spellcasters, the improved spell uses up a higher-level spell slot. But because the templar has not prepared the spell in a metamagic form in advance, he must apply the metamagic feat on the spot. Therefore, such a character must also take more time to cast a metamagic spell (one enhanced by a metamagic feat) than he does to cast a regular spell. If the spell's normal casting time is 1 standard action, casting a metamagic version is a full-round action for a templar. (This isn't the same as a 1-round casting time.)

For a spell with a longer casting time, it takes an extra full-round action to cast the spell.

\textbf{Spontaneous Casting and Metamagic Feats:} A cleric spontaneously casting a cure or inflict spell can cast a metamagic version of it instead. Extra time is also required in this case. Casting a 1-action metamagic spell spontaneously is a full-round action, and a spell with a longer casting time takes an extra full-round action to cast.

\textbf{Effects of Metamagic Feats on a Spell:} In all ways, a metamagic spell operates at its original spell level, even though it is prepared and cast as a higher-level spell. Saving throw modifications are not changed unless stated otherwise in the feat description.

The modifications made by these feats only apply to spells cast directly by the feat user. A spellcaster can't use a metamagic feat to alter a spell being cast from a wand, scroll, or other device.

Metamagic feats that eliminate components of a spell don't eliminate the attack of opportunity provoked by casting a spell while threatened. However, casting a spell modified by \feat{Quicken Spell} does not provoke an attack of opportunity.

Metamagic feats cannot be used with all spells. See the specific feat descriptions for the spells that a particular feat can't modify.

\textbf{Multiple Metamagic Feats on a Spell:} A spellcaster can apply multiple metamagic feats to a single spell. Changes to its level are cumulative. You can't apply the same metamagic feat more than once to a single spell.

\textbf{Magic Items and Metamagic Spells:} With the right item creation feat, you can store a metamagic version of a spell in a scroll, potion, or wand. Level limits for potions and wands apply to the spell's higher spell level (after the application of the metamagic feat). A character doesn't need the metamagic feat to activate an item storing a metamagic version of a spell.

\textbf{Counterspelling Metamagic Spells:} Whether or not a spell has been enhanced by a metamagic feat does not affect its vulnerability to counterspelling or its ability to counterspell another spell.

\subsection{Metapsionic Feats}
As a manifester's knowledge of psionics grows, he can learn to manifest powers in ways slightly different from how the powers were originally designed or learned. Of course, manifesting a power while using a metapsionic feat is more expensive than manifesting the power normally.

\textbf{Manifesting Time:} Powers manifested using metapsionic feats take the same time as manifesting the powers normally unless the feat description specifically says otherwise.

\textbf{Manifestation Cost:} To use a metapsionic feat, a psionic character must both expend his psionic focus (see the \skill{Concentration} skill description) and pay an increased power point cost as given in the feat description.

\textbf{Limits on Use:} As with all powers, you cannot spend more power points on a power than your manifester level. Metapsionic feats merely let you manifest powers in different ways; they do not let you violate this rule.

\textbf{Effects of Metapsionic Feats on a Power:} In all ways, a metapsionic power operates at its original power level, even though it costs additional power points. The modifications to a power made by a metapsionic feat have only their noted effect on the power. A manifester can't use a metapsionic feat to alter a power being cast from a power stone, dorje, or other device.

Manifesting a power modified by the \feat{Quicken Power} feat does not provoke attacks of opportunity.

Some metapsionic feats apply only to certain powers, as described in each specific feat entry.

\textbf{Psionic Items and Metapsionic Powers:} With the right psionic item creation feat, you can store a metapsionic power in a power stone, psionic tattoo, or dorje. Level limits for psionic tattoos apply to the power's higher metapsionic level.

A character doesn't need the appropriate metapsionic feat to activate an item in which a metapsionic power is stored, but does need the metapsionic feat to create such an item.

\subsection{Item Creation Feats}
An item creation feat lets a spellcaster create a magic item of a certain type. Regardless of the type of items they involve, the various item creation feats all have certain features in common.

\textbf{XP Cost:} Experience that the spellcaster would normally keep is expended when making a magic item. The XP cost equals 1/25 of the cost of the item in gold pieces. A character cannot spend so much XP on an item that he or she loses a level. However, upon gaining enough XP to attain a new level, he or she can immediately expend XP on creating an item rather than keeping the XP to advance a level.

\textbf{Raw Materials Cost:} The cost of creating a magic item equals one-half the sale cost of the item.

Using an item creation feat also requires access to a laboratory or magical workshop, special tools, and so on. A character generally has access to what he or she needs unless unusual circumstances apply.

\textbf{Time:} The time to create a magic item depends on the feat and the cost of the item. The minimum time is one day.

\textbf{Item Cost:} \feat{Brew Potion}, \feat{Craft Wand}, and \feat{Scribe Scroll} create items that directly reproduce spell effects, and the power of these items depends on their caster level---that is, a spell from such an item has the power it would have if cast by a spellcaster of that level. The price of these items (and thus the XP cost and the cost of the raw materials) also depends on the caster level. The caster level must be high enough that the spellcaster creating the item can cast the spell at that level. To find the final price in each case, multiply the caster level by the spell level, then multiply the result by a constant, as shown below:

\textit{Scrolls:} Base price = spell level $\times$ caster level $\times$ 25 cp.

\textit{Potions:} Base price = spell level $\times$ caster level $\times$ 50 cp.

\textit{Wands:} Base price = spell level $\times$ caster level $\times$ 750 cp.

A 0-level spell is considered to have a spell level of \onehalf for the purpose of this calculation.

\textbf{Extra Costs:} Any potion, scroll, or wand that stores a spell with a costly material component or an XP cost also carries a commensurate cost. For potions and scrolls, the creator must expend the material component or pay the XP cost when creating the item.

For a wand, the creator must expend fifty copies of the material component or pay fifty times the XP cost.

Some magic items similarly incur extra costs in material components or XP, as noted in their descriptions.


\subsection{Psionic Item Creation Feats}
Manifesters can use their personal power to create lasting psionic items. Doing so, however, is draining. A manifester must put a little of himself or herself into every psionic item he or she creates.

A psionic item creation feat lets a manifester create a psionic item of a certain type. Regardless of the type of items they involve, the various item creation feats all have certain features in common.

\textbf{XP Cost:} Power and energy that the manifester would normally keep is expended when making a psionic item. The experience point cost of using a psionic item creation feat equals 1/25 the cost of the item in gold pieces. A character cannot spend so much XP on an item that he or she loses a level. However, upon gaining enough XP to attain a new level, he or she can immediately expend XP on creating an item rather than keeping the XP to advance a level.

\textbf{Raw Materials Cost:} Creating a psionic item requires costly components, most of which are consumed in the process. The cost of these materials equals onehalf the cost of the item.

Using a psionic item creation feat also requires access to a laboratory or psionic workshop, special tools, and other equipment. A character generally has access to what he or she needs unless unusual circumstances apply (such as if he's traveling far from home).

\textbf{Time:} The time to create a psionic item depends on the feat and the cost of the item. The minimum time is one day.

% \textbf{Item Cost:} Craft Dorje, Imprint Stone, and Scribe Tattoo create items that directly reproduce the effects of powers, and the strength of these items depends on their manifester level---that is, a power from such an item has the strength it would have if manifested by a manifester of that level. Often, that is the minimum manifester level necessary to manifest the power. (Randomly discovered items usually follow this rule.) However, when making such an item, the item's strength can be set higher than the minimum. Any time a character creates an item using a power augmented by spending additional power points, the character's effective manifester level for the purpose of calculating the item's cost increases by 1 for each 1 additional power point spent. (Augmentation is a feature of many powers that allows the power to be amplified in various ways if additional power points are spent.) All other level-dependent parameters of the power forged into the item are set according to the effective manifester level.

% The price of psionic items (and thus the XP cost and the cost of the raw materials) depends on the level of the power and a character's manifester level. The character's manifester level must be high enough that the item creator can manifest the power at the chosen level. To find the final price in each case, multiply the character's manifester level by the power level, then multiply the result by a constant, as shown below.

\textbf{Item Cost:} \feat{Scribe Tattoo} create items that directly reproduce the effects of powers, and the strength of these items depends on the effective level of the power: power level + the power check DC modifier. Often, that is the minimum power check modifier necessary to manifest the power. (Randomly discovered items usually follow this rule.) However, when making such an item, the item's strength can be set higher than the minimum. Any time a character creates an item using a power augmented by spending additional power points, the power check DC modifier may increase depending on the psionic power. (Augmentation is a feature of many powers that allows the power to be amplified in various ways if additional power points are spent.) All other level-dependent parameters of the power forged into the item are set according to the effective manifester level.

The price of psionic items (and thus the XP cost and the cost of the raw materials) depends on the effective level of the power and a character's manifester level. The character's manifester level must be high enough that the item creator can manifest the power. To find the final price in each case, multiply the character's manifester level by the effective power level, then multiply the result by a constant, as shown below.

\textit{Psionic Tattoos:} Base price = (power level + power check DC modifier) $\times$ manifester level $\times$ 4,000 cp.

\textbf{Extra Costs:} Any psionic tattoo that stores a power with an XP cost also carries a commensurate cost, the creator must pay the XP cost when creating the item.

Some psionic items similarly incur extra costs in XP, as noted in their descriptions.


\section{Feat Descriptions}
Here is the format for feat descriptions.

\subsubsection{Feat Name {\large[Type Of Feat]}}
\textbf{Prerequisite:} A minimum ability score, another feat or feats, a minimum base attack bonus, a minimum number of ranks in one or more skills, or a class level that a character must have in order to acquire this feat. This entry is absent if a feat has no prerequisite. A feat may have more than one prerequisite.

\textbf{Benefit:} What the feat enables the character (``you'' in the feat description) to do. If a character has the same feat more than once, its benefits do not stack unless indicated otherwise in the description.

In general, having a feat twice is the same as having it once.

\textbf{Normal:} What a character who does not have this feat is limited to or restricted from doing. If not having the feat causes no particular drawback, this entry is absent.

\textbf{Special:} Additional facts about the feat that may be helpful when you decide whether to acquire the feat.

\input{sections/feats/table-general-feats.tex}
\vskip3cm
\input{sections/feats/general-feats.tex}
\input{sections/feats/table-skill-feats.tex}
\input{sections/feats/skill-feats.tex}
\input{sections/feats/racial-feats.tex}
% \input{sections/feats/regional-feats.tex}
\input{sections/feats/table-fighter-feats.tex}
\input{sections/feats/fighter-feats.tex}
\input{sections/feats/table-psionic-feats.tex}
\input{sections/feats/psionic-feats.tex}
\input{sections/feats/table-spell-feats.tex}
\input{sections/feats/divine-feats.tex}
\input{sections/feats/raze-feats.tex}
\input{sections/feats/metamagic-feats.tex}
\input{sections/feats/metapsionic-feats.tex}
\input{sections/feats/item-creation-feats.tex}
