\Chapter{Prestige Classes}
{There are many paths to power, but all power comes at a price. Fame or infamy follows those who make great sacrifices and who reach grand achievements. Would you be called tyrant or savior, I wonder. Perhaps you would prefer to be addressed as Mighty One, or plain and simply by your birthname? Will the bards speak of you as delusional or omnipotent? It all depends on the eye that sees. The hero of one is villain to another. But all beings of power share one trait---each has its own secrets. Remnants of the past, stories of the now, or visions of the future---secrets are the source of power. And the keepers of the greatest secrets are the most dangerous of all beings, for they will use any means to prevent others from unveiling them.}{The Oracle, Blue Shrine Scrolls}

\Capitalize{P}{restige} classes offer a new form of multiclassing. Unlike the basic classes, characters must meet Requirements before they can take their first level of a prestige class. The rules for level advancement apply to this system, meaning the first step of advancement is always choosing a class. If a character does not meet the Requirements for a prestige class before that first step, that character cannot take the first level of that prestige class. Taking a prestige class does not incur the experience point penalties normally associated with multiclassing.

% The prestige classes in this chapter are designed for characters in an Athasian campaign. They make use of defiling rules, the characters classes described in Chapter 2, or allow characters to further develop their elemental powers.

In addition to the prestige classes presented in this chapter, characters in a {\tableheader Dark Sun} campaign can adopt any prestige classes---with the DM's permission---from other sources as well. This chapter is not a comprehensive guide to the prestige classes on Athas. Check the \href{http://athas.org/products/prc1}{Prestige Class Appendix I} and \href{http://athas.org/products/prc2}{Prestige Class Appendix II} for more Athasian prestige classes.

Besides athasian prestige classes, the DM may also use the following prestige classes from Wizards of the Coast supplements:

\begin{itemize*}
\item Anarchic Initiate (Complete Psionic)
\item Argent Savant (Complete Arcane)
\item Avenging Executioner (Complete Scoundrel)
\item Beastmaster (Complete Adventurer)
\item Blighter (Complete Divine)
\item Blood Magus (Complete Arcane)
\item Bloodhound (Complete Adventurer)
\item Cloaked Dancer (Complete Scoundrel)
\item Combat Trapsmiths (Complete Scoundrel)
\item Contemplative (Complete Divine)
\item Dervish (Complete Warrior)
\item Divine Oracle (Complete Divine)
\item Ebon Saint (Complete Psionic)
\item Ectopic Adept (Complete Psionic)
\item Elemental Savant (Complete Arcane)
\item Exemplar (Complete Adventurer)
\item Exotic Weapon Master (Complete Warrior)
\item Fist of the Forest (Complete Champion)
\item Forest Reeve (Complete Champion)
\item Frenzied Berserker (Complete Warrior)
\item Highland Stalker (Complete Adventurer)
\item Holt Warden (Complete Champion)
\item Hulking Hurler (Complete Warrior)
\item Illumine Soul (Complete Psionic)
\item Invisible Blade (Complete Warrior)
\item Justiciar (Complete Warrior)
\item Master of Many Forms (Complete Adventurer)
\item Master Specialist (Complete Mage)
\item Master Thrower (Complete Warrior)
\item Mindbender (Complete Arcane)
\item Nature's Warrior (Complete Warrior)
\item Nightmare Spinner (Complete Mage)
\item Occult Slayer (Complete Warrior)
\item Psibond Agents (Complete Scoundrel)
\item Reaping Mauler (Complete Warrior)
\item Seeker of the Song (Complete Arcane)
\item Shadowmind (Complete Adventurer)
\item Spymaster (Complete Adventurer)
\item Storm Disciple (Complete Psionic)
\item Streetfighter (Complete Adventurer)
\item Tempest (Complete Adventurer)
\item Thief-Acrobat (Complete Adventurer)
\item Unseen Seer (Complete Mage)
\item War Chanter (Complete Warrior)
\item Warshaper (Complete Warrior)
\item Wild Plains Outrider (Complete Adventurer)
\end{itemize*}

\subsection{Definitions of Terms}
Here are definitions of some terms used in this section.

\textbf{Base Class:} One of the standard classes.

\textbf{Caster Level:} Generally equal to the number of class levels (see below) in a spellcasting class. Some prestige classes add caster levels to an existing class.

\textbf{Character Level:} The total level of the character, which is the sum of all class levels held by that character.

\textbf{Class Level:} The level of a character in a particular class. For a character with levels in only one class, class level and character level are the same.

\input{sections/prestige-classes/arcane-trickster.tex} %srd
\input{sections/prestige-classes/arch-defiler.tex}
\input{sections/prestige-classes/archmage.tex} %srd
\input{sections/prestige-classes/new-arena-champion.tex}
\input{sections/prestige-classes/arrow-knight.tex}
\input{sections/prestige-classes/assassin.tex} %srd
\input{sections/prestige-classes/battle-dancer.tex}
\input{sections/prestige-classes/beastmaster-psionicist.tex}
% \input{sections/prestige-classes/browncloak.tex}
\input{sections/prestige-classes/cerebremancer.tex} %xph
\input{sections/prestige-classes/cerulean.tex}
\input{sections/prestige-classes/chasseur.tex}
\input{sections/prestige-classes/convict.tex}
% \input{sections/prestige-classes/duelist.tex} %srd
\input{sections/prestige-classes/new-dune-trader.tex}
\input{sections/prestige-classes/earth-defender.tex}
\input{sections/prestige-classes/elemental-champion.tex}
\input{sections/prestige-classes/elemental-singer.tex}
\input{sections/prestige-classes/elite-sniper.tex}
\input{sections/prestige-classes/elocater.tex} %xph
% \input{sections/prestige-classes/executioner.tex}
\input{sections/prestige-classes/exterminator.tex}
\input{sections/prestige-classes/grove-master.tex}
\input{sections/prestige-classes/hierophant.tex} %srd
\input{sections/prestige-classes/horizon-walker.tex} %srd
\input{sections/prestige-classes/jaguar-knight.tex}
\input{sections/prestige-classes/loremaster.tex} %srd
\input{sections/prestige-classes/master-scout.tex}
% \input{sections/prestige-classes/master-shipfloater.tex}
\input{sections/prestige-classes/metamind.tex} %xph
% \input{sections/prestige-classes/moon-priest.tex}
\input{sections/prestige-classes/mystic-theurge.tex} %srd
\input{sections/prestige-classes/poisonmaster.tex}
\input{sections/prestige-classes/psiologist.tex}
\input{sections/prestige-classes/psion-uncarnate.tex} %xph
\input{sections/prestige-classes/restorationist.tex}
\input{sections/prestige-classes/shadowdancer.tex} %srd
\input{sections/prestige-classes/shadow-wizard.tex}
\input{sections/prestige-classes/templar-knight.tex}
\input{sections/prestige-classes/thaumaturgist.tex} %srd
\input{sections/prestige-classes/wanderer.tex} %
\input{sections/prestige-classes/war-mind.tex} %xph