\Chapter{Spells}
{Magic is arguably the mightiest force in Athas. Those wielding it call fire storms out of a calm sky, change one object into another, or kill enemies with a mere gesture. They dictate the wills of entire mobs, make the dead walk, and have even been known to stop time. Magic can expose traitors, destroy rivals, and exact unquestioning obedience from subjects. It can also conceal secret activities, uncover the king's spies, be used to assassinate royal officers, and foster general rebellion.}{The Wanderer's Journal}

An M or F appearing at the end of a spell's name in the spell lists denotes a spell with a material or focus component, respectively, that is not normally included in a spell component pouch. An X denotes a spell with an XP component paid by the caster.

\textbf{Order of Presentation:} In the spell lists and the spell descriptions that follow them, the spells are presented in alphabetical order by name except for those belonging to certain spell chains.

When a spell's name begins with ``lesser,'' ``greater,'' or ``mass,'' the spell description is alphabetized under the second word of the spell name instead.

\textbf{Hit Dice:} The term ``Hit Dice'' is used synonymously with ``character levels'' for effects that affect a number of Hit Dice of creatures. Creatures with Hit Dice only from their race, not from classes, have character levels equal to their Hit Dice.

\textbf{Caster Level:} A spell's power often depends on caster level, which is defined as the caster's class level for the purpose of casting a particular spell. A creature with no classes has a caster level equal to its Hit Dice unless otherwise specified. The word ``level'' in the spell lists that follow always refers to caster level.

\textbf{Creatures and Characters:} The words ``creature'' and ``character'' are used synonymously in the spell descriptions.

\input{sections/spells/cleric-spells.tex}
\input{sections/spells/cleric-domains.tex}
\input{sections/spells/druid-spells.tex}
\input{sections/spells/ranger-spells.tex}
\input{sections/spells/templar-spells.tex}
\input{sections/spells/templar-domains.tex}
\input{sections/spells/wizard-spells.tex}
\input{sections/spells/spells.tex}