\Chapter{Powers}
{Geryas drifted in the cloudy realm of his own mind, contemplating the sun-like nexus of energy that glowed at the core of his being. He perceived his sentience as a shower of golden sparks that whirled and darted around the nexus, and the various disciplines of the Way as colorful spheres of light that danced and bobbed in the gray vapor. He selected a large scarlet orb---his psychokinetic powers---and concentrated on it.

Geryas's body sat cross-legged on a rocky shelf overlooking the Sea of Silt. His eyes stared blankly ahead. As he touched the red sphere with his consciousness. his body began to levitate, rising from the rocky crag. Without stirring from his lotus position, Geryas began to imagine flight. The golden sparks to surrounded the red sphere, exploring it.


When Geryas opened his eyes at last, he was far above the Sea of Silt, the air whistling past his ears as he flew forward. At last, he thought, \emph{telekinetic flight}.}
{}

\Capitalize{T}{his} chapter begins with the power lists for all psion's disciplines. An \textsuperscript{A} appearing at the end of a power's name in the power lists denotes an augmentable power. A \textsuperscript{P} denotes a power with prerequisites the manifester must fulfill before learning it. An \textsuperscript{X} denotes a power with an XP component paid by the manifester.

\textbf{Power Chains:} Some powers reference other powers that they are based upon. Only information in a power later in the power chain that is different from the base power is covered in the power being described. Header entries and other information that are the same as the base power are not repeated. The same holds true for powers that are the equivalents of spells, only the way the power varies from the spell is noted, such as power point cost.

\textbf{Order of Presentation:} In the power lists and the power descriptions that follow them, the powers are presented in alphabetical order by name---except for those belonging to certain power chains and those that are psionic equivalents of spells. When a power's name begins with ``lesser,'' ``greater,'' ``mass,'' or a similar kind of qualifier, the power description is alphabetized under the second word of the power description instead. When the effect of a power is essentially the same as that of a spell, the power's name is simply ``Psionic'' followed by the name of the spell, and it is alphabetized according to the spell name.

% \textbf{Manifester Level:} A power's effect often depends on the manifester level, which is the manifester's psionic class level. A creature with no classes has a manifester level equal to its Hit Dice unless otherwise specified. The word ``level'' in the power lists always refers to manifester level.
\textbf{Manifester Level:} A few powers require a specific manifester level, which is the manifester's psionic class level. A creature with no classes has a manifester level equal to its Hit Dice unless otherwise specified. The word ``level'' in the power lists always refers to manifester level.

\textbf{Creatures and Characters:} ``Creatures'' and ``characters'' are used synonymously in the power descriptions.

\textbf{Prerequisites:} Some powers require previous knowledge of another power. The manifester must fulfill all prerequisites before learning the power.

\textbf{Augment:} Many powers vary in strength depending on how many power points you put into them. The more power points you spend, the more powerful the manifestation. %However, you can spend only a total number of points on a power equal to your manifester level, unless you have an ability that increases your effective manifester level.

Many powers can be augmented in more than one way. When the Augment section contains numbered paragraphs, you need to spend power points separately for each of the numbered options. When a paragraph in the Augment section begins with ``In addition,'' you gain the indicated benefit according to how many power points you have already decided to spend on manifesting the power.

% \input{sections/powers/psion-powers.tex}
% \input{sections/powers/psion-discipline-powers.tex}
% \input{sections/powers/war-mind-powers.tex}
\input{sections/powers/new-psion-powers.tex}
\input{sections/powers/new-psion-discipline-powers.tex}


\clearpage
\section{Power Descriptions}
The powers herein are presented in alphabetical order (with the exception of those whose names begin with ``greater,'' ``lesser,'' or ``mass''; see Order of Presentation).

\input{sections/powers/powers.tex}
