\Chapter{Campaigns}
{Bards tell tales of the fall of King Kalak of Tyr, the great rebellion and liberation of the slaves, and the war against Urik. It is the life of Rikus the gladiator and his fellow comrades. Elders speak of ancient ruins where undead walk at night, where powerful defilers seek secrets so terrible the Sorcerer-Kings tremble. Travelers dream of hidden cities in the Silt Sea, of forgotten cities to the North closed off to the world around them, and of strange halfling cities, beyond which are the vast Hinterlands of the kreen. Some whisper of sighting strange beings, a forewarning of invasions of kreen, undead or dray. Athas calls for new heroes and villains. Who will rise to answer the call?}{The Oracle, Blue Shrine Scrolls}

The world of Athas has a slightly different flavor from traditional high fantasy. With a combination of survival against, ecological disaster, resource depletion, survival of the fittest, slavery and poverty, and the wide-spread use of psionic abilities, it has the potential to handle a wide range of adventures. The world has been scarred and forever changed by the abuse of magic and a terrible war that lasted over a millennia. In the aftermath, a handful of individuals with powers akin to gods in other settings and other powerful groups fight to gain power and influence.

% encounters
% >encounter level
% >skill encounter
% >
% dungeons
% urban adventures
% >demographics
\section{Urban Adventures}
\subsection{Demographics}

\Table{Town Sizes}{lr{21mm}r{13mm}X}{
  \tableheader Town Size
& \tableheader Population\footnotemark[1]
& \tableheader CP Limit
& \tableheader Examples \\

Small tribe &           20--60 &      30 cp & Sortar's camp \\
Large tribe &          61--200 &      70 cp & Tenpug's band \\
Village     &       201--1,000 &     150 cp & Winter Nest \\
Small town  &     1,001--5,000 &     400 cp & Pterran Vale \\
Large town  &    5,001--10,000 &   1,000 cp &  \\
Small city  &   10,001--50,000 &   5,000 cp & City-states \\
Large city  &  50,001--100,000 &  25,000 cp &  \\
Metropolis  & 100,001--300,000 &  75,000 cp &  \\
Megalopolis & 300,001 or more  & 250,000 cp &  \\
}

\Table{NPCs Needed per Population}{Xcl}{
  \tableheader Class
& \tableheader Levels
& \tableheader For Every... \\

\multicolumn{2}{l}{\TableSubheader{Agriculture}} & 2,000 people\\
Earth cleric  & 5th to 8th     & \\
Ranger        & 11th or higher & \\
Druid         & 12th or higher & \\

\multicolumn{2}{l}{\TableSubheader{Health}} & 15,000 people\\
Cleric & 5th or higher  & \\
Druid  & 12th or higher & \\
}

\textbf{Agriculture:} A big enough settlement needs a spellcaster whose job is to cast \spell{plant growth} on the city's crops. One such spellcaster is required for every 2,000 people---it can be a earth cleric of 5th- to 8th-level, a ranger 11th-level or higher, or a druid 12th-level or higher.

Clerics of 9th-level or higher are called to help with planar duties from their elemental masters, rangers need to be of high enough level to be able cast the spell, while druids are required to wander until they reach the 12th-level.

\textbf{Health:} It is expected to exist a cleric or druid that can cast \spell{remove disease} for every 15,000 people. For smaller communities, there is one priest to attend to a big number of villages and tribes. For big cities, their priests would attend to the city and its satellite towns.

\subsubsection{Community Population and Wealth}
\subsubsection{NPCs in the Community}
\textbf{Highest-Level NPC in the Community for Each Class:} Use the following tables to determine the highest-level character in a given class for a given community. Determine the appropriate community modifier by consulting the first table below; then refer to the second table, roll the dice indicated for the class, and apply the modifier to get a result.

A result of 0 or lower for character level means that no characters of that kind can be found in the community. The maximum level for any class is 20th.


\Table{Community Modifiers}{lX}{
  \tableheader Community Size
& \tableheader Community Modifier \\
Small tribe & $-3$ \\
Large tribe & $-2$ \\
Village     & $-1$ \\
Small town  & +0 \\
Large town  & +1 \\
Small city  & +2 (roll twice)\footnotemark[1] \\
Large city  & +4 (roll thrice)\footnotemark[1] \\
Metropolis  & +8 (roll four times)\footnotemark[1] \\
Megalopolis & +16 (roll five times)\footnotemark[1] \\
\TableNote{2}{1 Cities this large can have more than one high-level NPC per class, each of whom generates lower-level characters of the same class.}\\
}

\Table{Highest-Level Locals}{lX}{
  \tableheader Class
& \tableheader Character Level \\

Barbarian & 1d4 (2) + community modifier\footnotemark[1] \\
Bard      & 1d6 (3) + community modifier \\
Cleric    & 1d6 (3) + community modifier \\
Druid     & 1d3 (2) + community modifier \\
Fighter   & 1d8 (4) + community modifier \\ 
Gladiator & 1d8 (4) + community modifier \\
Psion     & 1d4 (4) + community modifier\footnotemark[2] \\
Ranger    & 1d3 (2) + community modifier\footnotemark[3] \\
Rogue     & 1d8 (4) + community modifier \\
Templar   & ---\footnotemark[2] \\
Wizard    & 1d4 (2) + community modifier\footnotemark[2] \\

\TableNote{2}{1 In raiding tribes, level is 1d8 (4) + community modifier.}\\
\TableNote{2}{2 In city states, level is 20.}\\
\TableNote{2}{3 In hunting clans, level is 1d8 (4) + community modifier.}\\
}

% >war
% NPCs
% >cohorts
% >followers
% >roles in society

\input{sections/campaign/variant-rules.tex}