\Chapter{Life on Athas}
{Almost all the Tyr Region is a desert wasteland, though it is beautiful and spectacular in its own fashion. Over each hill, behind each sand dune, the terrain appears more awesome than the land before. In my travels, I have often been overwhelmed by the sheer magnitude of this land, cowed by its indifferent brutality, even frightened by the unrestrained might of its elements---but I have never been bored.

Can I impart the grandeur and majesty of this area with mere words? I wonder. I can describe the queasy feeling of sliding down the glassy slopes of the Smoking Crown, or make your eyes sting with tales of walking the salt flats on a windy day. My words are but transparent reflections of this magnificent land, but perhaps they can be of use.}
{The Wanderer's Journal}

\Capitalize{A}{thas} is still a largely unknown world. Millennia of misinformation, wars, and natural barriers have created isolated pockets of civilization between large expanses of desert terrain.

The known world is currently divided into the Silt Sea, the Tablelands (also known as the Tyr Region), the Ringing Mountains, and the Hinterlands. The Tyr Region is defined as the area bordered by the Sea of Silt on the east, the Hinterlands to the west, and the Endless Sand Dunes to the south.

Outside of those regions, the Jagged Cliffs, the Deadlands, and the Valley of the Cerulean Storm wait to be discovered, charted, and plundered. The surface of Athas stretches from horizon to horizon, a patchwork of fields and forests, oceans (of water and sand) and mountains, deserts, swamps, jungles, and more. Beneath the crimson sun, Athas' varied environments give way one to another across the Tablelands. Mountains rise, valleys fall, and desert surrounds the land.

\input{sections/athas/the-world-of-athas.tex}

\newcommand{\City}[5]{
    \section{#1}
    \textbf{Population:} #2

    \textbf{Exports:} #3

    \textbf{Languages:} #4

    #5

    \CityDescription
}
\newcommand{\SubCity}[5]{
    \subsectionA{#1}
    \textbf{Population:} #2

    \textbf{Exports:} #3

    \textbf{Languages:} #4

    #5

    \CityDescription[\subsubsection]
}
\newcommand{\CityDescription}[7][\subsection]{
    #1{Life and Society}
    #2
    #1{Government and Politics}
    #3
    #1{Power Groups}
    #4
    \ifx&#5&\else
    #1{Major Settlements}
    #5
    \fi

    \ifx&#6&\else
    #1{Important Sites}
    #6
    \fi
    #1{Adventure Ideas}
    \begin{itemize*}
    #7
    \end{itemize*}
}

\input{sections/athas/city-states.tex}
\input{sections/athas/beyond-the-tablelands.tex}
\input{sections/athas/other-races.tex}
