\Chapter{Planes of Existence}
{Scampering blazes dove in to the rolling mass of ooze that issued from the plane of magma, but the attack was in vain. The hungry paraelementals devoured them, using the energy to stoke their liquid ovens. A mighty creature of earth rose from the ground and roared its defiance at the wave of lava that threatened to overwhelm it. Mighty fists of granite and obsidian smashed in to the magma bank, scattering its molten form. What remained reformed and threw itself over the earth elemental, swallowing it in its glowing cocoon. It grew from the feast, and dared the remaining fire elementals to throw themselves in to its gaping maw.}
{Tales of an Unseen War}

\Capitalize{P}{lanes} of existence make up the cosmology of any campaign setting. These planes correspond to entire universes with their own laws of physics and idiosyncrasies. They can be dangerous, wondrous, and specially strange.

The spells required to reach other planes are all 6th level or higher, making planar adventures more recommended for high-level characters. These adventures require not only the characters to be able to reach the planes, but they also must survive the unusual environments in those planes.

\input{sections/planes/what-is-a-plane.tex}
\input{sections/planes/planar-traits.tex}
\input{sections/planes/how-planes-interact.tex}
\input{sections/planes/athasian-cosmology.tex}
\input{sections/planes/transitive-planes.tex}
\input{sections/planes/inner-planes.tex}
\input{sections/planes/outer-planes.tex}
