\Chapter{Other Ages of Play}
{Little is known of Athas' true past. Every time I find another piece to the puzzle, more questions arise. The truth remains hidden and forever will be. There are records of great wars where entire races were hunted down and destroyed, and I have found images of beings unlike those that walk the sands today. Who were the Warbringer and his Champions, what was their motivation? One tablet speaks of a great cataclysm when a gate to the paraelemental plane of Magma was opened, but who did this, for what purpose, and could this be the source of the obsidian plains to the south? And what of our planet? Was Athas once covered in forests or even water, as some sources suggest? The only ones who could know are those who were there, and they are all either dead or mad.}
{The Oracle, Blue Shrine Scrolls}

\Capitalize{A}{s} the Dungeon Master, you are free to set your {\tableheader Dark Sun} campaign in any time period. However, the core rulebook focuses in two ages in particular, the Dragon Age, and the Age of Heroes. The information presented in this chapter is intended to give you enough of a backdrop to comfortably set adventures in any of Athas' other ages.

Take note that information concerning the history of Athas is scarce. Furthermore, it tends to be ambiguous, sometimes even contradictory. Separating fact from myth when history is recorded by individuals of power with their own agendas and views can sometimes be difficult, if not impossible.

The sections entitled ``A brief overview'' below could have been recovered from crystal orbs stored in the Blue Shrine, from writings in New Kurn's Great Library, or even from a rhulisti recorder unearthed during an aftershock. Knowledge of who, how and for what purpose the information was gathered remains shrouded in mystery. One theory is that they have belonged to the Wanderer or a sage. Whoever left them behind is now long gone...

\input{sections/other-ages-to-play/the-blue-age.tex}
\input{sections/other-ages-to-play/the-green-age.tex}
\input{sections/other-ages-to-play/the-blood-age.tex}
\input{sections/other-ages-to-play/the-dragon-age.tex}
