\Chapter{Epic Levels}
{
`Three thousand, one hundred and fifty-seven years in this place! What am I doing here? What do I hope to accomplish when it's done? I already know the damage this can inflict on the land, so why do I keep trying to perfect it? What if all of this set me back one step towards returning Athas to its former glory, but later on it will be two steps forwards it? I am willing to make this sacrifice. It will all be worthy.'

Then, with renewed energy, he went back once again to the final piece of the puzzle. An epiphany suddenly struck him: `Yes, the path is all too clear to me now.' He left his chambers, never looking back. After a while, the deformed creature emerged from the porous rock tower. He knew Athas would never be the same again.
}{}

Epic characters in {\tableheader Dark Sun} earn the power to drastically change their environment, for better or for worse. They can become the leaders of mighty armies, cruel tyrants ruling with iron fists, beings of pure psionic
energy, elemental champions battling for their patron's superiority, or become a force of hope and renewal for Athas' abused landscape.

Differently from other {\tableheader D\&D} settings, it is very hard to become epic in Athas without ever being noticed by the general populace, and worst, it is harder yet to go unnoticed by those who hold the reins of power. It is almost impossible to do so without attracting at least some (unwelcome) attention.

\subsection{Epic Characters in Your Game}
Athas is a harsh world, where survival itself is not a mundane task, let alone living enough to be able to thrive. Advancing into epic levels is extremely difficult, since victims of their own success. Powerful forces, such as the sorcerer-kings or the mysterious Order constantly look for potential threats and eliminate them before they have a
chance to fight back. Sometimes it is even impossible to become one, unless a character starts preparing years, maybe decades, in advance.

The most powerful epic creatures in Athas must be able to wield both magic and psionics, since only the clarity of mind resulting in practicing the Way would prepare their minds for the traumatic metamorphosis they must go through in order to become truly advanced beings.

\section{Epic Level Basics}
Epic characters---those whose character level is 21st or higher---are handled slightly differently from nonepic characters. While epic characters continue to receive most of the benefits of gaining levels, some benefits are replaced by alternative gains. A class can be advanced beyond 20th level. A ten-level prestige class can progress beyond 10th level, but only if the character level is already 20th or higher. A class with fewer than ten levels cannot progress beyond the maximum for that class, regardless of character level.

If your group is using the traditional leveling system via XP, you can use \tabref{Traditional Experience and Wealth}. In this table there is the expected wealth of player characters. Use this as a guide to balance adventures, i.e., do not assume a 23rd-level character should have a 762,000 cp item.


\Table{Traditional Experience and Wealth}{lRRR}{
\tableheader ECL & \tableheader Total XP & \tableheader XP for next level & \tableheader Wealth\\
20 & 285,000 & 30,000 &   378,000 cp\\
21 & 315,000 & 31,500 &   474,000 cp\\
22 & 346,500 & 33,000 &   570,000 cp\\
23 & 379,500 & 34,500 &   762,000 cp\\
24 & 414,000 & 36,000 &   954,000 cp\\
25 & 450,000 & 37,500 & 1,146,000 cp\\
26 & 487,500 & 39,000 & 1,530,000 cp\\
27 & 526,500 & 40,500 & 1,914,000 cp\\
28 & 567,000 & 42,000 & 2,298,000 cp\\
29 & 609,000 & 43,500 & 3,066,000 cp\\
30 & 652,500 &        & 3,834,000 cp\\
}


\input{subsections/epic-levels/epic-level-basics/level-dependent-benefits.tex}

\subsection{Adding a Second Class}
When a single-class epic character gains a level, they may choose to increase the level of their current class or pick up a new class at 1st level. The standard rules for multiclass characters still apply.

\input{subsections/epic-levels/epic-level-basics/divine-rank.tex}

\subsection{Psionic Enchantment}
Beyond the horizons of routine magic are whole seas of power that cannot be tapped naturally. The unaided mind, regardless of intelligence, cannot comprehend, let alone command, such tremendous energy. But psionics can ``tune'' the mind for greater mastery of magic. The combination produces the most powerful magic available in a {\tableheader Dark Sun} campaign.

In psionic enchantment, psionics is a means toward an end, a catalyst in the magical process. Spells beyond 9th-level are too difficult for the unaided mind to comprehend. Only through psionic disciplines can the mind handle this magic.

In game terms, psionic enchantments are new spells for the highest-level spellcasting characters who are also manifesters. Psionic enchantments are 10th-level spells that become available for spellcasters that have reached the 21st level of a spellcasting class and are capable of manifesting 9th-level powers. Casting a psionic enchantment requires spending 50 power points, besides the spell slot of 10th-level.

Characters without manifesting abilities do not have access to the spell slots. Specialist wizards do not gain additional spell slots for psionic enchantments---these spell slots do not work with the normal arcane regimes and cannot be manipulated in the same way.

\section{Epic Class Progressions}
Because the \chapref{Character Classes} contains information on advancement only up to 20th level in any given class, this chapter expands each class's progression up to the 30th level.

\input{subsections/epic-levels/epic-class-progressions/epic-barbarian.tex}
\input{subsections/epic-levels/epic-class-progressions/epic-bard.tex}
\input{subsections/epic-levels/epic-class-progressions/epic-cleric.tex}


\SpellcasterTable[11]{3mm}{The Epic Druid}{
\SpellHeader{10} \\
21 & +15/+10/+5        & +12 & +7  & +12 & Wild shape (7/day, Diminutive)    & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 0 \\
22 & +16/+11/+6/+1     & +13 & +7  & +13 & Guardian telepathy                & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 0 \\
23 & +17/+12/+7/+2     & +13 & +7  & +13 & Guardian call                     & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 1 \\
24 & +18/+13/+8/+3     & +14 & +8  & +14 & Wild shape (8/day, magical beast) & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 1 \\
25 & +18/+13/+8/+3     & +14 & +8  & +14 & Wild shape (Gargantuan)           & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 1 \\
26 & +19/+14/+9/+4     & +15 & +8  & +15 & Guardian dome                     & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 1 \\
27 & +20/+15/+10/+5    & +15 & +9  & +15 & Wild shape (9/day)                & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 2 \\
28 & +21/+16/+11/+6/+1 & +16 & +9  & +16 & Guardian sacrifice                & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 2 \\
29 & +21/+16/+11/+6/+1 & +16 & +9  & +16 & Wild shape (Colossal)             & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 2 \\
30 & +22/+17/+12/+7/+2 & +17 & +10 & +17 & Wild shape (10/day, aberration)   & 6 & 5 & 5 & 5 & 4 & 4 & 3 & 3 & 2 & 2 & 2 \\
}

\subsectionA{Epic Druid}

\textbf{Hit Die:} d8.

\textbf{Skill Points per Level:} 2 + Int modifier.

\textbf{Spells:} An epic druid gain access to psionic enchantments: 10th-level spells that need profound psionic knowledge. In order to cast those psionic enchantments, the epic druid must have Intelligence and Wisdom scores both equal to at least 20, and be capable of manifesting 9th-level powers. Casting a psionic enchantment requires spending 50 power points, besides the spell slot of 10th-level. The Difficulty Class for a saving throw against a psionic enchantment is 20 + the epic druid's Wisdom modifier.

\textbf{Wild Shape (Su):} At 21st level, the epic druid can use this ability to take the form of an animal one additional time per day. An epic druid can use this ability more times per day at 24th and every three levels thereafter (27th and 30th level).

In addition, she gains the ability to take the shape of a Diminutive animal at 21st level, a Gargantuan animal at 25th level, and a Colossal animal at 29th level.

At 24th level, an epic druid becomes able to use wild shape to change into a magical beast with the same size restrictions as for animal forms.

At 30th level, an epic druid becomes able to use wild shape to change into an aberration with the same size restrictions as for animal forms. This transformation uses two wild shape daily uses.

\textbf{Guardian Telepathy (Su):} At 22nd level, an epic druid can communicate telepathically with any creature within her guarded lands. This ability has no range limit, and language does not interfere with this communication. The epic druid does not need to be on her guarded lands to communicate.

\textbf{Guardian Call (Su):} At 23rd level, an epic druid can call upon an entire species within her guarded lands. The epic druid must first wild shape into the desired creature and use her telepathy to call for all members of the same species. All able creatures will move to her location at their best speed. The number of creatures cannot be decrease---it's all who live on her guarded lands or nothing. The called creatures will obey all of the epic druid's commands, provided she stays with them in wild shape. Once she returns to her original form, all creatures return to their homes.

\textbf{Guardian Dome (Su):} At 26th level, an epic druid can create an impenetrable dome around her guarded lands. The dome rises 300 meters above the highest point of the guarded lands. The dome is impossible to cross with the following exceptions: creatures designated by the epic druid or creatures with more Hit Dice than the epic druid can cross the dome. The dome prohibits passage in both directions---those inside cannot get out and those without cannot get in.

The nature of the dome is up to the epic druid's imagination---an array of spinning blades, a field of pure force, a curtain of flame and magma, etc.

\textbf{Guardian Sacrifice (Su):} At 28th level, an epic druid senses precisely where a defiler casts a spell within her guarded lands she knows the location of the act---even if she is not in the area. She can protect her lands through sacrificing part of her own life force. This nullifies a wizard's defiling radius and any effects it entails, such as penalties to attacks and saving throws, and damage to plants. It also nullifies the benefits of any raze feats used in the casting of the defiling spell. She loses 1 hit point per 3 meter of defiling radius nullified.



\subsectionA{Epic Fighter}

\textbf{Hit Die:} d10.

\textbf{Skill Points per Level:} 4 + Int modifier.

\textbf{Martial Prowess:} At 21st level and every two epic fighter levels thereafter (23th, 25th, 27th, and 29th level), an epic fighter learns a new technique. This technique can be chosen from the normal fighter list or the following list:

\textit{Aura of Courage (Su):} An epic fighter is immune to fear (magical or otherwise). Each ally within 3 meters of him gains a +4 morale bonus on saving throws against fear effects. This ability functions while the epic fighter is conscious, but not if he is unconscious or dead.

\textit{Devastating Blow (Ex):} As a standard action, an epic fighter may make a single melee attack with a two-handed weapon at a $-5$ penalty. If the attack hits, it is treated as a critical threat.


\textbf{Bonus Feat:} At 22nd and every even-numbered level thereafter, an epic fighter gains a bonus feat. These bonus feat must be selected from the normal fighter bonus feat list or epic fighter feats.



\WarriorTable{The Epic Fighter}{
21 & +21/+16/+11/+6/+1   & +12 & +7  & +7  & Martial prowess \\
22 & +22/+17/+12/+7/+2   & +13 & +7  & +7  & Bonus feat      \\
23 & +23/+18/+13/+8/+3   & +13 & +7  & +7  & Martial prowess \\
24 & +24/+19/+14/+9/+4   & +14 & +8  & +8  & Bonus feat      \\
25 & +25/+20/+15/+10/+5  & +14 & +8  & +8  & Martial prowess \\
26 & +26/+21/+16/+11/+6  & +15 & +8  & +8  & Bonus feat      \\
27 & +27/+22/+17/+12/+7  & +15 & +9  & +9  & Martial prowess \\
28 & +28/+23/+18/+13/+8  & +16 & +9  & +9  & Bonus feat      \\
29 & +29/+24/+19/+14/+9  & +16 & +9  & +9  & Martial prowess \\
30 & +30/+25/+20/+15/+10 & +17 & +10 & +10 & Bonus feat      \\
}

\subsectionA{Epic Gladiator}

\textbf{Hit Die:} d8.

\textbf{Skill Points per Level:} 4 + Int modifier.

\textbf{Martial Prowess:} At 22nd level and every three epic gladiator levels thereafter (25th and 28th level), an epic gladiator learns a new technique. This technique can be chosen from the normal gladiator list or the following list:

\WarriorTable{The Epic Gladiator}{
21 & +21/+16/+11/+6/+1   & +12 & +7  & +7  & ?                                         \\
22 & +22/+17/+12/+7/+2   & +13 & +7  & +7  & Exotic weapon, martial prowess       \\
23 & +23/+18/+13/+8/+3   & +13 & +7  & +7  &                                           \\
24 & +24/+19/+14/+9/+4   & +14 & +8  & +8  & ?                                         \\
25 & +25/+20/+15/+10/+5  & +14 & +8  & +8  & Armor optimization 5, martial prowess, dirty trick $\pm$10/$\pm$12 \\
26 & +26/+21/+16/+11/+6  & +15 & +8  & +8  & Exotic weapon                             \\
27 & +27/+22/+17/+12/+7  & +15 & +9  & +9  & ?                                         \\
28 & +28/+23/+18/+13/+8  & +16 & +9  & +9  & Martial prowess                      \\
29 & +29/+24/+19/+14/+9  & +16 & +9  & +9  &                                           \\
30 & +30/+25/+20/+15/+10 & +17 & +10 & +10 & Armor optimization 6, exotic weapon, ?    \\
}

\subsectionA{Epic Psion}

\PsychicTable{The Epic Psion}{
21 & +15/+10/+5        & +7  & +7  & +12 &            &  84 & 26 & 6 \\
22 & +16/+11/+6/+1     & +7  & +7  & +13 &            &  86 & 27 & 6 \\
23 & +17/+12/+7/+2     & +7  & +7  & +13 &            &  88 & 28 & 6 \\
24 & +18/+13/+8/+3     & +8  & +8  & +14 &            &  90 & 29 & 6 \\
25 & +18/+13/+8/+3     & +8  & +8  & +14 & Bonus feat &  92 & 30 & 6 \\
26 & +19/+14/+9/+4     & +8  & +8  & +15 &            &  94 & 31 & 6 \\
27 & +20/+15/+10/+5    & +9  & +9  & +15 &            &  96 & 32 & 6 \\
28 & +21/+16/+11/+6/+1 & +9  & +9  & +16 &            &  98 & 33 & 6 \\
29 & +21/+16/+11/+6/+1 & +9  & +9  & +16 &            & 100 & 34 & 6 \\
30 & +22/+17/+12/+7/+2 & +10 & +10 & +17 & Bonus feat & 102 & 35 & 6 \\
}

% \subsectionA{Epic Psychic Warrior}

% \PsychicTable{The Epic Psychic Warrior}{
% 21 & +15/+10/+5        & +12 & +7  & +7  &            & 200 & 21 & 6th\\
% 22 & +16/+11/+6/+1     & +13 & +7  & +7  &            & 200 & 22 & 6th\\
% 23 & +17/+12/+7/+2     & +13 & +7  & +7  & Bonus feat & 200 & 23 & 6th\\
% 24 & +18/+13/+8/+3     & +14 & +8  & +8  &            & 200 & 24 & 6th\\
% 25 & +18/+13/+8/+3     & +14 & +8  & +8  &            & 200 & 25 & 6th\\
% 26 & +19/+14/+9/+4     & +15 & +8  & +8  & Bonus feat & 200 & 26 & 6th\\
% 27 & +20/+15/+10/+5    & +15 & +9  & +9  &            & 200 & 27 & 6th\\
% 28 & +21/+16/+11/+6/+1 & +16 & +9  & +9  &            & 200 & 28 & 6th\\
% 29 & +21/+16/+11/+6/+1 & +16 & +9  & +9  & Bonus feat & 200 & 29 & 6th\\
% 30 & +22/+17/+12/+7/+2 & +17 & +10 & +10 &            & 200 & 30 & 6th\\
% }

\input{subsections/epic-levels/epic-class-progressions/epic-ranger.tex}
\input{subsections/epic-levels/epic-class-progressions/epic-scout.tex}
\input{subsections/epic-levels/epic-class-progressions/epic-thief.tex}



% \subsectionA{Epic Wilder}

% \PsychicTable{The Epic Wilder}{
% 21 & +15/+10/+5        & +7  & +7  & +12 & Volatile mind (5 power points)  & 260 & 11 & 9th \\
% 22 & +16/+11/+6/+1     & +7  & +7  & +13 &                                 & 260 & 12 & 9th \\
% 23 & +17/+12/+7/+2     & +7  & +7  & +13 & Wild surge +7                   & 260 & 12 & 9th \\
% 24 & +18/+13/+8/+3     & +8  & +8  & +14 &                                 & 260 & 13 & 9th \\
% 25 & +18/+13/+8/+3     & +8  & +8  & +14 & Volatile mind (6 power points)  & 260 & 13 & 9th \\
% 26 & +19/+14/+9/+4     & +8  & +8  & +15 &                                 & 260 & 14 & 9th \\
% 27 & +20/+15/+10/+5    & +9  & +9  & +15 & Wild surge +8                   & 260 & 14 & 9th \\
% 28 & +21/+16/+11/+6/+1 & +9  & +9  & +16 & Surging euphoria +4             & 260 & 15 & 9th \\
% 29 & +21/+16/+11/+6/+1 & +9  & +9  & +16 & Volatile mind (7 power points)  & 260 & 15 & 9th \\
% 30 & +22/+17/+12/+7/+2 & +10 & +10 & +17 &                                 & 260 & 16 & 9th \\
% }

\subsectionA{Epic Wizard}
\SpellcasterTable[11]{3mm}{The Epic Wizard}{
\SpellHeader{10} \\
21 & +10/+5     & +7  & +7  & +12 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 1 \\
22 & +11/+6/+1  & +7  & +7  & +13 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 1 \\
23 & +11/+6/+1  & +7  & +7  & +13 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 2 \\
24 & +12/+7/+2  & +8  & +8  & +14 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 2 \\
25 & +12/+7/+2  & +8  & +8  & +14 & Bonus feat & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 2 \\
26 & +13/+8/+3  & +8  & +8  & +15 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 3 \\
27 & +13/+8/+3  & +9  & +9  & +15 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 3 \\
28 & +14/+9/+4  & +9  & +9  & +16 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 3 \\
29 & +14/+9/+4  & +9  & +9  & +16 &            & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 \\
30 & +15/+10/+5 & +10 & +10 & +17 & Bonus feat & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 \\
}

\clearpage
\section{Epic Feats}
\textbf{Acquiring Epic Feats:} Characters gain epic feats in the following ways:
\begin{itemize*}
\item At 21st level, and every three levels thereafter, the character may select an epic feat in place of a non-epic feat.
\item Each character class gains bonus epic feats according to the class description.
\end{itemize*}





\subsection{General Feats}
\GFeat[Epic]{Augmented Poison}
{Int 21, \skill{Craft} (poisonmaking) 24 ranks.}
{Whenever creating a poison, you can make it more potent than normal by adding +20 to the DC required to create it and multiplying its price by 5. You increase its damage by 100\%.}

\GFeat[Epic]{Bane Of Enemies}
{\skill{Survival} 24 ranks, five or more favored enemies.}
{Any weapon you wield against one of your favored enemies is treated as a bane weapon for that creature type (thus, its enhancement bonus is increased by +2 and it deals +2d6 points of damage). This ability doesn't stack with similar abilities.}

\GFeat[Epic]{Chaotic Rage}
{Rage 5/day, chaotic alignment.}
{Any weapon you wield while in a rage is treated as an anarchic weapon (it is chaos-aligned and deals an extra 2d6 points of damage against creatures of lawful alignment). This ability does not stack with similar abilities.}

\Feat[Epic]{Efficient Item Creation}
{}
{Item creation feat to be selected, \skill{Knowledge} (arcana) 24 ranks or \skill{Knowledge} (psionics) 24 ranks, \skill{Spellcraft} 24 ranks.}
{Select an item creation feat. Creating a magic item using that feat requires one day per 10,000 cp of the item's market price, with a minimum of one day.}
{Without this feat, creating a magic item requires one day for each 1,000 cp of the item's market price.}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different item creation feat.}

\Feat[Epic]{Energy Resistance}
{}{}
{Choose a type of energy (acid, cold, electricity, fire, or sonic). You gain resistance 10 to that type of energy, or your existing resistance to that type of energy increases by 10. This feat does not stack with energy resistance granted by magic items or nonpermanent magical effects.}
{}{You can gain this feat multiple times. If the same type of energy is chosen, the effects stack.}

\GFeat[Epic]{Epic Dodge}
{Dex 25, \feat{Dodge}, \skill{Tumble} 30 ranks, improved evasion, defensive roll class feature.}
{Once per round, when struck by an attack from an opponent you have designated as the object of your dodge, you may automatically avoid all damage from the attack.}

\GFeat[Epic]{Epic Endurance}
{Con 25, \feat{Endurance}.}
{Whenever you make a check for performing a physical action that extends over a period of time, you get a +10 bonus on the check.}

\GFeat[Epic]{Epic Initiative}
{\feat{Improved Initiative}.}
{You get a +8 bonus on initiative checks. This bonus overlaps (does not stack with) the bonus from Improved Initiative.}

\Feat[Epic]{Epic Skill Focus}
{}
{\feat{Skill Focus} in the selected skill, 20 ranks in the selected skill.}
{You gain a +10 bonus on all checks with that skill.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different skill.}

\Feat[Epic]{Epic Speed}
{}
{Dex 21, \feat{Run}.}
{Your speed increases by 9 meters. This is considered an enhancement bonus.}
{}{This feat only functions when you are wearing medium armor, light armor, or no armor.}

\Feat[Epic]{Epic Spell Focus}
{}
{\feat{Greater Spell Focus} in school, \feat{Spell Focus} in school, ability to cast at least one 9th-level spell of the school to be chosen.}
{Add +1 to the Difficulty Class for all saving throws against spells from the school of magic you select to focus on. This stacks with the bonuses from \feat{Spell Focus} and \feat{Greater Spell Focus}.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different school of magic.}

\GFeat[Epic]{Epic Spell Penetration}
{\feat{Greater Spell Penetration}, \feat{Spell Penetration}.}
{You get a +2 bonus on caster level checks to beat a creature's spell resistance. This stacks with the bonuses from \feat{Spell Penetration} and \feat{Greater Spell Penetration}.}

\GFeat[Epic]{Epic Toughness}
{}
{You gain +30 hit points.}

\Feat[Epic]{Extended Life Span}
{}{}
{Add one-half the maximum result of your race's maximum age modifier to your normal middle age, old, and venerable age categories. Calculate your maximum age using the new venerable number. This feat can't lower your current age category.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Extra Chance}
{}
{Chance 2/day.}
{You gain one additional daily use of chance.}
{}{You can gain this feat multiple times. Its effects stack.}


\Feat[Epic]{Fast Healing}
{}
{Con 25.}
{You gain fast healing 3, or your existing fast healing increases by 3.}
{}{You can gain this feat multiple times. Its effects stack.}





\FeatTable{General}{
\feat{Augmented Poison} & Int 21, \skill{Craft} (poisonmaking) 24 ranks & Double the poison damage \\
\feat{Bane Of Enemies} & \skill{Survival} 24 ranks, five or more favored enemies & Weapons are treated as bane against favored enemies \\
\feat{Chaotic Rage} & Rage 5/day, chaotic alignment & Weapons are treated as anarchic while raging \\
\feat{Efficient Item Creation}\footnotemark[1] & Item creation feat to be selected, \skill{Knowledge} (arcana) 24 ranks or \skill{Knowledge} (psionics) 24 ranks, \skill{Spellcraft} 24 ranks & Craft magic items  required 1 day per 10,000 cp \\
\feat{Energy Resistance}\footnotemark[2] && Gain energy resistance 10 \\
\feat{Epic Dodge} & Dex 25, \feat{Dodge}, \skill{Tumble} 30 ranks, improved evasion, defensive roll class feature & Once per round avoid all damage from one attack \\
\feat{Epic Endurance} & Con 25, \feat{Endurance} & Gain +10 on checks to resist nonlethal damage \\
\feat{Epic Initiative} & \feat{Improved Initiative} & Gain +8 on initiative checks \\
\feat{Epic Skill Focus}\footnotemark[1] & \feat{Skill Focus} in the selected skill, 20 ranks in the selected skill & +10 bonus on checks of selected skill \\
\feat{Epic Speed} & Dex 21, \feat{Run} & Speed +9 m while not in heavy armor \\
\feat{Epic Spell Focus}\footnotemark[1] & \feat{Greater Spell Focus} in school, \feat{Spell Focus} in school, ability to cast at least one 9th-level spell of the school & +1 bonus to DC on spells of chosen school \\
\feat{Epic Spell Penetration} & \feat{Greater Spell Penetration}, \feat{Spell Penetration} & +2 bonus on caster level check to defeat spell resistence\\
\feat{Epic Toughness} && +30 hit points\\
\feat{Extended Life Span}\footnotemark[1] && Increase the threshold for each of your age categories\\
\feat{Extra Chance}\footnotemark[1] & Chance 2/day & One additional chance per day\\
\feat{Fast Healing}\footnotemark[1] & Con 25 & Fast healing 3\\
\feat{Great Charisma}\footnotemark[1] && Increase your Charisma by 1\\
\feat{Great Constitution}\footnotemark[1] && Increase your Constitution by 1\\
\feat{Great Dexterity}\footnotemark[1] && Increase your Dexterity by 1\\
\feat{Great Intelligence}\footnotemark[1] && Increase your Intelligence by 1\\
\feat{Great Strength}\footnotemark[1] && Increase your Strength by 1\\
\feat{Great Wisdom}\footnotemark[1] && Increase your Wisdom by 1\\
\feat{Improved Armor Optimization}\footnotemark[1] & Armor optimization 4 or more & Increase armor optimization improvement by 1 \\
\feat{Improved Favored Enemy}\footnotemark[1] & Five or more favored enemies & Improve all favored enemy bonus by +1 \\
\feat{Improved Favored Terrain}\footnotemark[1] & Four or more favored terrain & Improve all favored terrain bonus by +1 \\
\feat{Improved Inspiration}\footnotemark[1] & Cha 25, \skill{Perform} 30 ranks, bardic music class feature & Improve all bardic music bonus by +1\\
\feat{Improved Metamagic} & Four metamagic feats, \skill{Spellcraft} 30 ranks & Reduce metamagic spell slot modifier by 1\\
\feat{Ignore Material Components} & \feat{Eschew Materials}, \skill{Spellcraft} 25 ranks, ability to cast 9th-level arcane or divine spells & Cast spells without any material components\\
\feat{Legendary Acrobat} & \skill{Balance} 24 ranks, \skill{Tumble} 24 ranks & Ignore penalties for accelerated \skill{Balance} and \skill{Tumble} checks\\
\feat{Legendary Climber} & Dex 21, \skill{Balance} 12 ranks, \skill{Climb} 24 ranks & Ignore penalties for accelerated climbing\\
\feat{Legendary Leaper} & \skill{Jump} 24 ranks & Move only 1.5 meter to make running jump\\
\feat{Legendary Poisoner} & \skill{Craft} (poisonmaking) 24 ranks & +2 DC to all poisons you apply\\
\feat{Legendary Rider} & \skill{Ride} 24 ranks & No penalty riding bareback and no checks to control mount in combat\\
\feat{Legendary Tracker} & Wis 25, \feat{Track}, \skill{Knowledge} (nature) 30 ranks, \skill{Survival} 30 ranks & Track across water, underwater or through the air \\
\feat{Perfect Health} & Con 25, \feat{Great Fortitude} & Become immune to diseases and poisons\\
\feat{Poison Penetration} & Int 21, \skill{Craft} (poisonmaking) 24 ranks & Your poisons affect creatures with poison immunity\\
\feat{Polyglot} & Int 25, \skill{Speak Language} (five languages) & Speak all languages\\

\TableNote{3}{1 You can take this feat multiple times. Its effects do not stack.}\\
\TableNote{3}{2 You can take this feat multiple times. Its effects stack.}\\
}





\Feat[Epic]{Great Charisma}
{}{}
{Your Charisma increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Constitution}
{}{}
{Your Constitution increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Dexterity}
{}{}
{Your Dexterity increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Intelligence}
{}{}
{Your Intelligence increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Strength}
{}{}
{Your Strength increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Wisdom}
{}{}
{Your Wisdom increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Improved Armor Optimization}
{}
{Armor optimization 4 or more.}
{Your armor optimization improvement increases by 1.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Improved Favored Enemy}
{}
{Five or more favored enemies.}
{Add +1 to the bonus on \skill{Bluff}, \skill{Listen}, \skill{Sense Motive}, \skill{Spot}, and \skill{Survival} checks and damage rolls against all your favored enemies.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Improved Favored Terrain}
{}
{Four or more favored enemies.}
{Add +1 to the bonus on \skill{Hide}, \skill{Listen}, \skill{Move Silently}, \skill{Search}, \skill{Spot}, and \skill{Survival} checks and initiative checks within your favored terrains. Likewise, add +1 to the bonus on \skill{Knowledge} (geography) and \skill{Knowledge} (nature) checks about your favored terrains.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Improved Inspiration}
{}
{Cha 25, \skill{Perform} 30 ranks, bardic music class feature.}
{All competence bonuses, dodge bonuses, and morale bonuses granted by your bardic music ability increase by +1. If you have the inspire greatness bardic music ability, it grants one additional bonus HD.}
{}{You can gain this feat multiple times. Its effects stack.}

\GFeat[Epic]{Improved Metamagic}
{Four metamagic feats, \skill{Spellcraft} 30 ranks.}
{The spell slot modifier of all your metamagic feats is reduced by one level, to a minimum of +1. This feat has no effect on metamagic feats whose spell slot modifier is +1 or less.}

\GFeat[Epic]{Ignore Material Components}
{\feat{Eschew Materials}, \skill{Spellcraft} 25 ranks, ability to cast 9th-level arcane or divine spells.}
{You may cast spells without any material components. This feat does not affect the need for a focus or divine focus.}

\Feat[Epic]{Legendary Acrobat}
{}
{\skill{Balance} 24 ranks, \skill{Tumble} 24 ranks.}
{You can ignore any check penalties applied for accelerated movement while balancing, for accelerated tumbling, or for running while balancing on a narrow surface or while tumbling.}
{Without this feat, you take a $-5$ penalty on \skill{Balance} checks and a $-10$ penalty on \skill{Tumble} checks when attempting to move your full speed as a move action, or a $-20$ penalty on \skill{Balance} or \skill{Tumble} checks when attempting to run while balancing on a narrow surface or while tumbling.}{}

\Feat[Epic]{Legendary Climber}
{}
{Dex 21, \skill{Balance} 12 ranks, \skill{Climb} 24 ranks.}
{You can ignore any check penalties applied for accelerated climbing or rapid climbing.}
{Without this feat, you take a $-5$ penalty on \skill{Climb} checks when attempting to cover your full speed in climbing distance in a round, or a $-20$ penalty when attempting to cover twice your speed in climbing distance in a round.}{}

\Feat[Epic]{Legendary Leaper}
{}
{\skill{Jump} 24 ranks.}
{You need only move 1.5 meter in a straight line to make a running jump.}
{Without this feat, you must move at least 6 meters in a straight line before attempting a running jump.}{}

\GFeat[Epic]{Legendary Poisoner}
{\skill{Craft} (poisonmaking) 24 ranks.}
{Add 2 to the save DC of all poisons applied by you.}

\Feat[Epic]{Legendary Rider}
{}
{\skill{Ride} 24 ranks.}
{You don't take a penalty on \skill{Ride} checks when riding a mount without a saddle (bareback). You never need to make a \skill{Ride} check to control a mount in combat (and even controlling a mount not trained for combat doesn't require an action).}
{Without this feat, you take a -5 penalty on \skill{Ride} checks without a saddle, and must make a \skill{Ride} check to control a mount in combat (and controlling a mount not trained for combat requires a move action).}{}

\GFeat[Epic]{Legendary Tracker}
{Wis 25, \feat{Track}, \skill{Knowledge} (nature) 30 ranks, \skill{Survival} 30 ranks.}
{You can track creatures across water, under-water, or through the air. This adds the surfaces of water, underwater, and air to the list of surfaces found under the \feat{Track} feat.}

\Table{}{XC}{
  \tableheader Surface
& \tableheader DC\\
Water      & 60  \\
Underwater & 80  \\
Air        & 120 \\
}

\GFeat[Epic]{Perfect Health}
{Con 25, \feat{Great Fortitude}.}
{You are immune to all nonmagical diseases, as well as to all poisons whose Fortitude save DC is 25 or less.}

\GFeat[Epic]{Poison Penetration}
{Int 21, \skill{Craft} (poisonmaking) 24 ranks.}
{Whenever you attack a creature with immunity to poison, you deal \onehalf of the damage it would otherwise deal as if it didn't have immunity.}

\GFeat[Epic]{Polyglot}
{Int 25, \skill{Speak Language} (five languages).}
{You can speak all languages. If you are literate, you can also read and write all languages (not including magical script).}




\FeatTable{Fighter}{
\feat{Armor Skin}\footnotemark[2] && Gain +1 natural armor \\
\feat{Damage Reduction}\footnotemark[2] & Con 21 & Gain RD 3/-- \\
\feat{Distant Shot} & Dex 25, \feat{Far Shot}, \feat{Point Blank Shot}, \skill{Spot} 20 ranks & Throw or fire ranged weapon without penalty for range\\
\feat{Epic Feint} & \skill{Bluff} 24 ranks, \feat{Improved Feint} & Ignore penalties against nonhumanoid opponents\\
\feat{Epic Manyshot} & Dex 19, base attack bonus +21, \feat{Manyshot}, \feat{Point Blank Shot}, \feat{Rapid Shot} & Shoot as many arrows as your BAB allows\\
\feat{Epic Weapon Focus}\footnotemark[1] & \feat{Weapon Focus} with weapon, \feat{Greater Weapon Focus} with weapon, fighter level 21st & +2 bonus on attack rolls with chosen weapon\\
~ \feat{Epic Weapon Specialization}\footnotemark[1] & \feat{Epic Weapon Focus} with weapon, \feat{Greater Weapon Focus} with weapon, \feat{Greater Weapon Specialization} with weapon, \feat{Weapon Focus} with weapon, \feat{Weapon Specialization} with weapon, fighter level 24th & +4 bonus on damage rolls with chosen weapon\\
\feat{Exceptional Deflection} & Dex 21, Wis 19, \feat{Deflect Arrows}, \feat{Improved Unarmed Strike} & Deflect any ranged attacks\\
\feat{Exotic Mastery} & \feat{Exotic Weapon Proficiency} with five or more weapons & Become proficient in all exotic weapons\\
\feat{Improved Combat Reflexes} & Dex 21, \feat{Combat Reflexes} & No limit for attacks of opportunity\\
\feat{Improved Whirlwind Attack} & Int 13, Dex 23, \feat{Combat Expertise}, \feat{Dodge}, \feat{Mobility}, \feat{Spring Attack}, \feat{Whirlwind Attack} & Make whirlwind attack as standard action\\
\feat{Infinite Deflection} & Dex 25, \feat{Combat Reflexes}, \feat{Deflect Arrows}, \feat{Improved Unarmed Strike} & No limit to number of deflections\\
\feat{Instant Reload}\footnotemark[1] & \feat{Quick Draw}, \feat{Rapid Reload} with crossbow type chosen, \feat{Weapon Focus} with crossbow type chosen & Fire at your full normal attack rate\\
\feat{Legendary Wrestler} & Str 21, Dex 21, \feat{Improved Unarmed Strike}, \feat{Improved Grapple} & +10 on grapple checks\\
\feat{Overwhelming Critical}\footnotemark[1] & Str 23, \feat{Cleave}, \feat{Great Cleave}, \feat{Improved Critical} with weapon, \feat{Power Attack}, \feat{Weapon Focus} with weapon & +1d6 bonus damage on a critical hit\\
~ \feat{Devastating Critical}\footnotemark[1] & Str 25, \feat{Cleave}, \feat{Great Cleave}, \feat{Improved Critical} with weapon, \feat{Overwhelming Critical} with weapon, \feat{Power Attack}, \feat{Weapon Focus} with weapon & Target must make a Fort save or die after a critical hit\\
\feat{Perfect Multiweapon Fighting} & Dex 25, \feat{Greater Multiweapon Fighting}, \feat{Improved Multiweapon Fighting}, \feat{Multiweapon Fighting} & Make as many attacks with each of your off-hands as with your primary\\
\feat{Perfect Two-Weapon Fighting} & Dex 25, \feat{Greater Two-Weapon Fighting}, \feat{Improved Two-Weapon Fighting}, \feat{Two-Weapon Fighting} & Make as many attacks with your off-hand as with your primary\\
\feat{Storm of Throws} & Dex 23, \feat{Point Blank Shot}, \feat{Quick Draw}, \feat{Rapid Shot} & Throw light weapons at each opponent within 9 meters\\
\feat{Swarm of Arrows}\footnotemark[1] & Dex 23, \feat{Point Blank Shot}, \feat{Rapid Shot}, \feat{Weapon Focus} with a bow type & Fire an arrow at each\\
\feat{Uncanny Accuracy} & Dex 21, base attack bonus +11, \feat{Point Blank Shot}, \feat{Precise Shot}, \feat{Improved Precise Shot}, \skill{Spot} 20 ranks & Ignore miss chance from total concealment\\

\TableNote{3}{1 You can take this feat multiple times. Its effects do not stack.}\\
\TableNote{3}{2 You can take this feat multiple times. Its effects stack.}\\
}

\subsection{Fighter Feats}
\Feat[Epic, Fighter]{Armor Skin}
{}{}
{You gain a +1 natural armor bonus to Armor Class, or your existing natural armor bonus increases by 1.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic, Fighter]{Damage Reduction}
{}
{Con 21.}
{You gain damage reduction 3/--. This does not stack with damage reduction granted by magic items or nonpermanent magical effects, but it does stack with any damage reduction granted by permanent magical effects, class features, or this feat itself.}
{}{You can gain this feat multiple times. Each time you gain the feat, your damage reduction increases by 3.}

\Feat[Epic, Fighter]{Devastating Critical}
{}
{Str 25, \feat{Cleave}, \feat{Great Cleave}, \feat{Improved Critical} with weapon, \feat{Overwhelming Critical} with weapon, \feat{Power Attack}, \feat{Weapon Focus} with weapon.}
{Whenever you score a critical hit with the chosen weapon, the target must make a Fortitude save (DC 10 + \onehalf your level + your Strength modifier) or die instantly. (Creatures immune to critical hits can't be affected by this feat.)}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different type of weapon.}

\GFeat[Epic, Fighter]{Distant Shot}
{Dex 25, \feat{Far Shot}, \feat{Point Blank Shot}, \skill{Spot} 20 ranks.}
{You may throw or fire a ranged weapon at any target within line of sight, with no penalty for range.}

\GFeat[Epic, Fighter]{Epic Feint}
{\skill{Bluff} 24 ranks, \feat{Improved Feint}.}
{You can ignore any check penalties applied to feinting against nonhumanoid opponents.}

\Feat[Epic, Fighter]{Epic Manyshot}
{}
{Dex 19, base attack bonus +21, \feat{Manyshot}, \feat{Point Blank Shot}, \feat{Rapid Shot}.}
{As \feat{Manyshot}, but the number of arrows you can fire is limited only by your base attack bonus (two arrows, plus one arrow for every 5 points of base attack bonus above +6).}
{With the \feat{Manyshot} feat, you are limited to a maximum of four arrows fired (when your base attack bonus is +16 or higher).}
{Regardless of the number of arrows you fire, you only apply precision-based damage (such as sneak attack damage or the ranger's favored enemy bonus) once. If you score a critical hit, only one of the arrows deals critical damage (your choice); all others deal normal damage.}

\Feat[Epic, Fighter]{Epic Weapon Focus}
{}
{\feat{Weapon Focus} with weapon, \feat{Greater Weapon Focus} with weapon, fighter level 21st.}
{Add a +2 bonus to all attack rolls you make using the selected weapon.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different type of weapon.}

\Feat[Epic, Fighter]{Epic Weapon Specialization}
{}
{\feat{Epic Weapon Focus} with weapon, \feat{Greater Weapon Focus} with weapon, \feat{Greater Weapon Specialization} with weapon, \feat{Weapon Focus} with weapon, \feat{Weapon Specialization} with weapon, fighter level 24th.}
{Add +4 to all damage you deal using the selected weapon.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat it applies to a different type of weapon.}

\GFeat[Epic, Fighter]{Exceptional Deflection}
{Dex 21, Wis 19, \feat{Deflect Arrows}, \feat{Improved Unarmed Strike}.}
{You can deflect any ranged attacks (including spells that require ranged touch attacks) as if they were arrows.}

\GFeat[Epic, Fighter]{Exotic Mastery}
{\feat{Exotic Weapon Proficiency} with five or more weapons.}
{You are proficient with all exotic weapons.}

\GFeat[Epic, Fighter]{Improved Combat Reflexes}
{Dex 21, \feat{Combat Reflexes}.}
{There is no limit to the number of attacks of opportunity you can make in one round. (you still can't make more than one attack of opportunity for a given opportunity.)}

\Feat[Epic, Fighter]{Improved Whirlwind Attack}
{}
{Int 13, Dex 23, \feat{Combat Expertise}, \feat{Dodge}, \feat{Mobility}, \feat{Spring Attack}, \feat{Whirlwind Attack}.}
{As a standard action, you can make one melee attack for every five points of your base attack bonus.

You cannot attack any one opponent more than once as part of this action. These attacks (as well as all other attacks made until the start of your next turn) suffer a $-4$ penalty.

When using the Improved Whirlwind Attack feat, you also forfeit any bonus or extra attacks granted by other spells or abilities (such as the \feat{Cleave} feat or the \spell{haste} spell).

Since these attacks are made as part of a standard action, you can't make a 1.5-meter step between any two of the attacks.}
{Without this feat, using the Whirlwind Attack feat requires a full attack action, and you can take a 1.5-meter step between any two of the attacks.}
{}

\GFeat[Epic, Fighter]{Infinite Deflection}
{Dex 25, \feat{Combat Reflexes}, \feat{Deflect Arrows}, \feat{Improved Unarmed Strike}.}
{You may perform any number of deflections each round, as the \feat{Deflect Arrows} feat.}

\Feat[Epic, Fighter]{Instant Reload}
{}
{\feat{Quick Draw}, \feat{Rapid Reload} with crossbow type chosen, \feat{Weapon Focus} with crossbow type chosen.}
{You may fire the selected type of crossbow at your full normal attack rate. Reloading the crossbow does not provoke attacks of opportunity.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different type of crossbow.}

\GFeat[Epic, Fighter]{Legendary Wrestler}
{Str 21, Dex 21, \feat{Improved Unarmed Strike}, \skill{Escape Artist} 15 ranks.}
{You gain a +10 bonus on all grapple checks.}


\Feat[Epic, Fighter]{Overwhelming Critical}
{}
{Str 23, \feat{Cleave}, \feat{Great Cleave}, \feat{Improved Critical} with weapon, \feat{Power Attack}, \feat{Weapon Focus} with weapon.}
{When using the weapon you have selected, you deal an extra 1d6 points of bonus damage on a successful critical hit. If the weapon's critical multiplier is $\times$3, add +2d6 points of bonus damage instead, and if the multiplier is $\times$4, add +3d6 points of bonus damage instead. Creatures immune to critical hits can't be affected by this feat.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take this feat, it applies to a different type of weapon.}


\Feat[Epic, Fighter]{Perfect Multiweapon Fighting}
{}
{Dex 25, three or more hands, \feat{Greater Multiweapon Fighting}, \feat{Multiweapon Fighting}.}
{You can make as many attacks with each extra weapon as with your primary weapon, using the same base attack bonus. You still take the normal penalties for fighting with two weapons.}
{Without this feat, you can make only one attack per round with each extra weapon (or two attacks per round with each weapon if you have \feat{Multiweapon Fighting}, or three attacks per round with each extra weapon if you have \feat{Greater Multiweapon Fighting}). Each attack after the first extra attack has a cumulative $-5$ penalty.}
{This feat replaces the \feat{Perfect Two-Weapon Fighting} feat for creatures with more than two arms.}

\Feat[Epic, Fighter]{Perfect Two-Weapon Fighting}
{}
{Dex 25, \feat{Greater Two-Weapon Fighting}, \feat{Improved Two-Weapon Fighting}, \feat{Two-Weapon Fighting}.}
{You can make as many attacks with your off-hand weapon as with your primary weapon, using the same base attack bonus. You still take the normal penalties for fighting with two weapons.}
{Without this feat, you can only get a single attack with an off-hand weapon (or two attacks with an off-hand weapon if you have \feat{Improved Two-Weapon Fighting}, or three attacks with an off-hand weapon if you have \feat{Greater Two-Weapon Fighting}).}
{A 21st level ranger who has chosen the two-weapon combat style is treated as having Perfect Two-Weapon Fighting, even if he does not have the prerequisites for it, but only when he is wearing light or no armor.}

\GFeat[Epic, Fighter]{Storm of Throws}
{Dex 23, \feat{Point Blank Shot}, \feat{Quick Draw}, \feat{Rapid Shot}.}
{As a full-round action, you may throw a light weapon at your full base attack bonus at each opponent within 9 meters. All light weapons thrown need not be the same type.}

\GFeat[Epic, Fighter]{Swarm of Arrows}
{Dex 23, \feat{Point Blank Shot}, \feat{Rapid Shot}, \feat{Weapon Focus} with bow.}
{As a full-round action, you may fire an arrow at your full base attack bonus at each opponent within 9 meters.}

\Feat[Epic, Fighter]{Uncanny Accuracy}
{}
{Dex 21, base attack bonus +11, \feat{Point Blank Shot}, \feat{Precise Shot}, \feat{Improved Precise Shot}, \skill{Spot} 20 ranks.}
{Your ranged attacks ignore the miss chance granted to targets by total concealment. You must aim your attacks at the correct square to take advantage of this feat.}
{Without this feat, you suffer a 50\% miss chance when making a ranged attack against a target with total concealment.}
{A 21st level ranger who has chosen the archery combat style is treated as having Uncanny Accuracy, even if he does not have the prerequisites for it, but only when he is wearing light or no armor.}




\FeatTable{Psionic}{
	
}
\FeatTable{Divine}{
	
}
\FeatTable{Metamagic}{
	
}


\subsection{Psionic Feats}
\Feat[Epic, Psionic]{Epic Psionic Meditation}
{}
{Wis 21, \feat{Psionic Meditation}, \skill{Concentration} 24 ranks.}
{You can become psionically focused as a free action, but only once per round.}
{Without this feat, you must take a full-round action to become psionically focused (or a move action if you have \feat{Psionic Meditation}).}
{}

\GFeat[Epic, Psionic]{Improved Metapsionics}
{Character level 21st, four metapsionic feats, \skill{Psicraft} 30 ranks.}
{Metapsionic powers you manifest cost 10 power points less than normal (to a minimum of 5 power point).

This feat has no effect on metapsionic powers that inflate the cost by only 10 power points.}




\subsection{Divine Feats}
\GFeat[Divine, Epic]{Undead Mastery}
{Cha 21, ability to rebuke or command undead.}
{You may command up to ten times your level in HD of undead.}

\GFeat[Divine, Epic]{Zone Of Animation}
{Cha 25, Undead Mastery, ability to rebuke or command undead.}
{You can use a rebuke or command undead attempt to animate corpses within range of your rebuke or command attempt. You animate a total number of HD of undead equal to the number of undead that would be commanded by your result (though you can’t animate more undead than there are available corpses within range). You can’t animate more undead with any single attempt than the maximum number you can command (including any undead already under your command). These undead are automatically under your command, though your normal limit of commanded undead still applies. If the corpses are relatively fresh, the animated undead are zombies. Otherwise, they are skeletons.}




\subsection{Metamagic Feats}
\GFeat[Epic, Metamagic]{Intensify Spell}
{\feat{Empower Spell}, \feat{Maximize Spell}, \skill{Spellcraft} 30 ranks, ability to cast 9th-level arcane or divine spells.}
{All variable, numeric effects of an intensified spell are maximized, then doubled. An intensified spell deals twice maximum damage, cures twice the maximum number of hit points, affects twice the maximum number of targets, and so forth, as appropriate. Saving throws and opposed rolls are not affected. An intensified spell uses up a spell slot seven levels higher than the spell's actual level. You can't combine the effects of this feat with any other feat that affects the variable, numeric effects of a spell.}


\clearpage
\input{sections/epic-levels/epic-prestige-classes.tex}

\clearpage

