\Capitalize{A}{thas} is a world of many races, from the gith who wander the deserts, to the tareks, too stubborn to know when they have died. Giants terrorize the Silt Sea, while belgoi steal grown men in the night. The magic of the Pristine Tower produces the New Races; most never see a second generation. Despite the variety of intelligent life, only a few races have the numbers to significantly impact the politics of the Tablelands.

Though the races of the {\tableheader Dark Sun} campaign setting resemble those of other campaign worlds, it is frequently in name only. The insular elves roam the Tablelands, trusted by no one but their own tribe-mates. Halflings are feral creatures, possessed of a taste for human flesh. Hairless dwarves work endlessly, their entire perception of the world filtered through the lens of a single, all-consuming task. Unsleeping thri-kreen roam the wastes, always hunting their next meal.

\section{Racial Characteristics}

\subsection{Ability Adjustments}

Find your character's race on \tabref{Athasian Racial Ability Adjustments} and apply the adjustments to your character's ability scores. If these changes put your score above 18 or below 3, that's okay, except in the case of Intelligence, which does not go below 3 for characters.

\subsection{Level Adjustment}

To determine the effective character level (ECL) of a character, add its race's level adjustment (LA) to its character class levels.

Use ECL instead of character level to determine how many experience points a character needs to reach its next level. Also use ECL to determine starting wealth for a character.

\subsection{Favored Class}

Each race's favored class is also given on \tabref{Athasian Racial Ability Adjustments}. A character's favored class doesn't count against him or her when determining experience point penalties for multiclassing.

\BigTablePair{Athasian Racial Ability Adjustments}{l l C p{6cm} p{2cm} l}{
\tableheader Race & \tableheader Type (Subtype) & \tableheader LA & \tableheader Ability Adjustments & \tableheader Favored Class & \tableheader Languages \\
Human & Humanoid (human) & --- & --- & Any & Common \\
Aarakocra & Monstrous Humanoid & +1 & $-2$ Strength, +4 Dexterity, $-2$ Charisma & Cleric & Auran, Common \\
Dwarf & Humanoid (dwarf) & --- & +2 Constitution, $-2$ Charisma & Fighter & Common, Dwarven \\
Elf & Humanoid (elf) & --- & +2 Dexterity, $-2$ Constitution & Rogue & Common, Elven \\
Half-elf & Humanoid (elf) & --- & +2 Dexterity, $-2$ Charisma & Any & Common, Elven \\
Half-giant & Giant & +2 & +8 Strength, $-2$ Dexterity, +4 Constitution, \newline $-4$ Intelligence, $-4$ Wisdom, $-4$ Charisma & Barbarian & Common \\
Halfling & Humanoid (halfling) & --- & $-2$ Strength, +2 Dexterity & Ranger & Halfling \\
Mul & Humanoid (dwarf) & +1 & +4 Strength, +2 Constitution, $-2$ Charisma & Gladiator & Common \\
Pterran & Humanoid (pterran) & --- & $-2$ Dexterity, +2 Wisdom, +2 Charisma & Druid, ranger,\newline or telepath & Saurian \\
Thri-kreen & Monstrous Humanoid & +2 & +2 Strength, +4 Dexterity, $-2$ Intelligence, \newline +2 Wisdom, $-4$ Charisma & Psychic warrior & Kreen}

\subsection{Race And Languages}

Only races that live in the reach of the city-states know how to speak Common. A aarakocra, dwarf, elf, half-elf, halfling, pterran, or thri-kreen also speaks a racial language, as appropriate. A character who has an Intelligence bonus at 1st level speaks other languages as well, one extra language per point of Intelligence bonus as a starting character.

\textbf{Literacy}: The ability to read has been outlawed for thousands of years by the sorcerer-kings. All characters in a {\tableheader Dark Sun} campaign start without the ability to read or write.

\textbf{Class-Related Languages}: Clerics, druids, templars, and wizards can choose certain languages as bonus languages even if they're not on the lists found in the race descriptions. These class-related languages are as follows:

\textit{Cleric}: Aquan, Auran, Ignan, Terran.

\textit{Druid}: Sylvan.

\textit{Templar}: Templar's City-State language.

\textit{Wizard}: Draconic.

\input{sections/2.1-humans.tex}
\input{sections/2.2-aarakocra.tex}
\input{sections/2.3-dwarves.tex}
\input{sections/2.4-elves.tex}
\input{sections/2.5-half-elves.tex}
\input{sections/2.6-half-giants.tex}
\input{sections/2.7-halflings.tex}
\input{sections/2.8-muls.tex}
\input{sections/2.9-pterrans.tex}
\input{sections/2.10-thri-kreen.tex}

\section{Other Races}
Athas is a place where members of different races are usually found in the same city-state, usually because they are going to be used in gladiatorial games as an exotic attraction, or to become slaves due to their physical might. Even though they are not usually concentrated on a specific area, these races are significant players in the Tablelands. It is only fitting then, that belgoi, gith, jozhals, ssurrans, tareks, taris, yuan-tis, and a variety of other creatures commonly viewed as monsters might appear as player characters in a {\tableheader Dark Sun} campaign.

All the rules you need to play a character belonging to one of these races can be found in Terrors of Athas, Expanded Psionics Handbook, and the Dungeon Master's Guide. Cultural information about several monstrous races appears in Chapter 7: Life on Athas.

\input{sections/2.11-vital-statistics.tex}
\input{sections/2.12-region-of-origin.tex}