\section{The Classes}

\Capitalize{Y}{ou} may notice that there are some classes not described here. Some of these are core classes that have been deemed inappropriate to the feel of the Dark Sun campaign setting. Others are classes from previous editions of Dark Sun that don't fit in the 3e.

\textbf{Monk:} There are several monasteries on Athas, though little evidence in previous material supports the martial artist variety of monk. Monks are too few in number to warrant a core class.

\textbf{Paladin:} The idea of doing good for its own sake runs contrary to the tone and theme of the setting. There are no gods to reward selfless acts, and no grand traditions of chivalry and nobility to promote. In essence, Athas is a world where evil behavior is the norm.

\textbf{Sorcerer:} Mechanically, a sorcerer's spontaneous casting and a psion's manifesting are similar, thus including the sorcerer removes some of the uniqueness of the psion. Some also feel that an arcane spellcaster without a spellbook violates the flavor of the setting.

\textbf{Soulknife:} There is no precedent of a concept such as the soulknife in any previous material. However, in a metal‐poor, high psionic world, the ability to manifest a weapon using the mind has its place. There would probably not be enough soulknives to warrant a core class, which would need to be shoehorned into the existing campaign world.

\textbf{Trader:} The trader class, present in previous editions of the setting is not included here because it's benefits and traits are nearly all encompassed in the standard set of 3rd edition skills. Reproducing the class is easily done using a standard skill‐focused class, like the rogue or bard, or using the expert NPC class.

Some DMs choose to run Dark Sun as a low‐magic, low treasure campaign. In such games, the monk and soulknife could become unbalanced because of their lack of dependence on treasure.

DMs are free to include any of the above core classes in their games, but these classes will not appear in any official releases.

\input{sections/4.1-barbarian.tex}
\input{sections/4.2-bard.tex}
\input{sections/4.3-cleric.tex}
\input{sections/4.4-druid.tex}
\input{sections/4.5-fighter.tex}
\input{sections/4.6-gladiator.tex}
\input{sections/4.7-psion.tex}
\input{sections/4.8-psychic-warrior.tex}
\input{sections/4.9-ranger.tex}
\input{sections/4.10-rogue.tex}