\section{Skill Summary}
\Capitalize{I}{f} you buy a class skill, your character gets 1 rank (equal to a +1 bonus on checks with that skill) for each skill point. If you buy other classes’ skills (cross-class skills), you get ½ rank per skill point.

Your maximum rank in a class skill is your character level + 3.

Your maximum rank in a cross-class skill is one-half of this number (do not round up or down).

\subsection{Using Skills}
To make a skill check, roll:

{
	\centering
 1d20 + {\bfseries skill modifier}
 
}


\textit{Skill modifier =} skill rank + ability modifier + miscellaneous modifiers.

This roll works just like an attack roll or a saving throw— the higher the roll, the better. Either you’re trying to match or exceed a certain Difficulty Class (DC), or you’re trying to beat another character’s check result.

\textit{Skill Ranks}: A character’s number of ranks in a skill is based on how many skill points a character has invested in a skill. Many skills can be used even if the character has no ranks in them; doing this is called making an untrained skill check.

\textit{Ability Modifier}: The ability modifier used in a skill check is the modifier for the skill’s key ability (the ability associated with the skill’s use). The key ability of each skill is noted in its description.

\textit{Miscellaneous Modifiers}: Miscellaneous modifiers include racial bonuses, armor check penalties, and bonuses provided by feats, among others.

\subsection{Acquiring Skill Ranks}

Each skill point you spend on a class skill gets you 1 rank in that skill. Class skills are the skills found on your character’s class skill list. Each skill point you spend on a cross-class skill gets your character ½ rank in that skill. Cross-class skills are skills not found on your character’s class skill list. (Half ranks do not improve your skill check, but two ½ ranks make 1 rank.) You can’t save skill points to spend later.

The maximum rank in a class skill is the character’s level + 3. If it’s a cross-class skill, the maximum rank is half of that number (do not round up or down).

Regardless of whether a skill is purchased as a class skill or a cross-class skill, if it is a class skill for any of your classes, your maximum rank equals your total character level + 3.