\Chapter{Equipment}
{I have heard tales that suits of clothing fashioned from metal have even been found from time to time. It is generally agreed that these were worn by warriors to protect against the blows of enemy weapons. I can only speculate that the climate must have been far cooler in those ancient days. Any fool that would wear such clothing now would die faster from heat stroke than he would have from the weapons of his foes. Still, the idea that there was once enough metal in the world to allow such a garment to have been manufactured astounds me.

There are even rumors that mounds of steel, silver, and gold lie hidden in the deepest tunnels of certain forlorn cities. I have never seen such a thing myself, but if such treasures exist, they will reward those who find them most handsomely. Those who control such stores of metal can buy food, power, influence, and sometimes even the sorcerer-king's protection.}
{The Wanderer's Journal}

Dark Sun characters must be well equipped in order to endure the rigors of Athas. This chapter covers a variety of topics related to mundane equipment that every hero needs to survive and prosper.

\section{Equipping a Character}
The world of Athas has a very specific feel to it; many things that are taken for granted in other campaign worlds, like the availability of metal and water, are very different on this heat-wracked planet. To maintain this feel, the equipment available to characters should reflect these differences.

\section{Wealth and Money}
\subsection{Coins}
All prices in Dark Sun are given in terms of ceramic pieces, the most common coin. Ceramics are made from glazed clay and baked in batches once a year in a secure process supervised by the high templar that supervises the city's treasury. Bits are literally one‐tenth parts of a ceramic piece---the ceramic pieces break easily into ten bits. Some cities' ceramic pieces have small holes that can be threaded onto a bracelet or necklace. The lowest unit of Athasian trade is the lead bead (bd).

Each of the city-states of the Tablelands produces its own currency. All cities use ceramic pieces as the most common coin, but also mint silver coins and, in some cases, rare and highly prized gold coins.

\Table[\scriptsize]{Currency Conversions}{l C C C C}{
& \multicolumn{4}{c}{\tableheader Exchange Value}\\
& \tableheader bd & \tableheader bit & \tableheader cp & \tableheader sp\\
Lead bead (bd) & 1 & 1/10 & 1/100 & 1/1,000\\
Ceramic bit (bit) & 10 & 1 & 1/10 & 1/100\\
Ceramic piece (cp) & 100 & 10 & 1 & 1/10\\
Silver piece (sp) & 1,000 & 100 & 10 & 1\\
Gold piece (gp) & 10,000 & 1000 & 100 & 10\\
}

\subsubsection{Moneychangers}
Adventurers that travel between cities will need to change their currency for local currency at each city they visit. With a couple of exceptions, the city-states have moneychangers available for incoming visitors. Located near the city gates and in large market places, moneychangers denote their business by hanging a large purple banner from their shop. The banners are always purple, but the moneychangers in each city-state display a different emblem on the banner, based on their city's standard.

Moneychangers charge each customer a fee to change coins. The fees differ by city and are summarized on \tabref{Moneychangers}.

\Table{Moneychangers}{C C}{
\tableheader City & \tableheader Exchange Rate\\
Balic & 6\%\\
Draj & 8\%\\
Gulg & 10\%\\
Kurn & 16\%\\
Nibenay & 14\%\\
Raam & 12\%\\
Tyr & 12\%\\
Urik & 9\%\\
}

These fees are averages and may vary slightly. There are of course many unscrupulous money merchants who will charge as much as they can get away with. Moneychangers in Kurn are rare but a couple do exist. Since metal coins from any city-state are readily accepted by local merchants and no corresponding Kurnish coins exist there is little need to exchange such coins. There are, however, a few moneychangers willing to exchange ceramic pieces.

There are two cities that do not have moneychangers. Visitors to Celik have no need of a moneychangers, as merchants in that city take coins of all types. Nor are there any moneychangers in Eldaarich. Since Eldaarich has been shut off from the rest of the land for so long, visitors needing to exchange money have been nonexistent, so no moneychangers have set up business.

\subsection{Trade}
In general, the Athasian economy in the cities is relatively stable thanks to the Merchant Houses. Under normal conditions, supply is ample thanks to the caravans traveling back and forth between the cities. However, for smaller communities and trade outposts the price situation on certain goods can sway drastically. A raider attack or sandstorm can result in lack of necessities such as food and water, for which people will pay almost any amount of coin. Coins are not the only means of exchange. Barter and trade in commodities is widespread.

Dune traders commonly exchange trade goods without using currency, instead relying on a basic bartering system.


\Table{Trade Goods}{l X}{
\tableheader Cost & \tableheader Item\\
2 bits & One pound of salt\\
3 bits & One pound of grain or faro\\
5 bits & One pound of lead\\
1 cp & One pound of nuts, or one pound of kank nectar\\
4 cp & One square yard of cotton (cloth)\\
5 cp & One pound of obsidian\\
10 cp & One square yard of silk, or one tun of water, or one erdlu\\
50 cp & One pound of copper, or one herding kank, or one aprig\\
100 cp & One pound of iron, or one male carru, or one inix\\
200 cp & One mekillot\\
300 cp & One female carru\\
500 cp & One pound of silver\\
5,000 cp & One pound of gold\\
}

\subsection{Selling Loot}
In general, a character can sell something for half its listed price.

Trade goods are the exception to the half-price rule. A trade good, in this sense, is a valuable good that can be easily exchanged almost as if it were cash itself.

\section{Weapons}
Characters in a Dark Sun game use a variety of weapons: some with direct counterparts in the real world, some without.

\input{subsections/8.2-weapon-categories.tex}
\input{sections/8-weapon-table.tex}

\section{Weapon Qualities}
Here is the format for weapon entries (given as column headings on Table: Weapons).

\textbf{Cost:} This value is the weapon’s cost in gold pieces (gp) or silver pieces (sp). The cost includes miscellaneous gear that goes with the weapon.

This cost is the same for a Small or Medium version of the weapon. A Large version costs twice the listed price.

\textbf{Damage:} The Damage columns give the damage dealt by the weapon on a successful hit. The column labeled ``Dmg (S)'' is for Small weapons. The column labeled "Dmg (M)" is for Medium weapons. If two damage ranges are given then the weapon is a double weapon. Use the second damage figure given for the double weapon’s extra attack. Table: Larger and Smaller Weapon Damage gives weapon damage values for weapons of various sizes.

\textbf{Critical:} The entry in this column notes how the weapon is used with the rules for critical hits. When your character scores a critical hit, roll the damage two, three, or four times, as indicated by its critical multiplier (using all applicable modifiers on each roll), and add all the results together.

\textit{Exception:} Extra damage over and above a weapon’s normal damage is not multiplied when you score a critical hit.

\textit{×2:} The weapon deals double damage on a critical hit.

\textit{×3:} The weapon deals triple damage on a critical hit.

\textit{×3/×4:} One head of this double weapon deals triple damage on a critical hit. The other head deals quadruple damage on a critical hit.

\textit{×4:} The weapon deals quadruple damage on a critical hit.

\textit{19-20/×2:} The weapon scores a threat on a natural roll of 19 or 20 (instead of just 20) and deals double damage on a critical hit. (The weapon has a threat range of 19-20.)

\textit{18-20/×2:} The weapon scores a threat on a natural roll of 18, 19, or 20 (instead of just 20) and deals double damage on a critical hit. (The weapon has a threat range of 18-20.)

\textbf{Range Increment:} Any attack at less than this distance is not penalized for range. However, each full range increment imposes a cumulative -2 penalty on the attack roll. A thrown weapon has a maximum range of five range increments. A projectile weapon can shoot out to ten range increments.

\textbf{Weight:} This column gives the weight of a Medium version of the weapon. Halve this number for Small weapons and double it for Large weapons.

\textbf{Type:} Weapons are classified according to the type of damage they deal: bludgeoning, piercing, or slashing. Some monsters may be resistant or immune to attacks from certain types of weapons.

Some weapons deal damage of multiple types. If a weapon is of two types, the damage it deals is not half one type and half another; all of it is both types. Therefore, a creature would have to be immune to both types of damage to ignore any of the damage from such a weapon.

In other cases, a weapon can deal either of two types of damage. In a situation when the damage type is significant, the wielder can choose which type of damage to deal with such a weapon.

\textbf{Special:} Some weapons have special features. See the weapon descriptions for details.

