\section{Armor}
In general, magic armor protects the wearer to a greater extent than nonmagical armor. Magic armor bonuses are enhancement bonuses, never rise above +5, and stack with regular armor bonuses (and with shield and magic shield enhancement bonuses). All magic armor is also masterwork armor, reducing armor check penalties by 1.

In addition to an enhancement bonus, armor may have special abilities. Special abilities usually count as additional bonuses for determining the market value of an item, but do not improve AC. A suit of armor cannot have an effective bonus (enhancement plus special ability bonus equivalents) higher than +10. A suit of armor with a special ability must have at least a +1 enhancement bonus.

A suit of armor or a shield may be made of an unusual material. Roll d\%: 01--95 indicates that the item is of a standard sort, and 96--100 indicates that it is made of a special material.

Armor is always created so that even if the type of armor comes with boots or gauntlets, these pieces can be switched for other magic boots or gauntlets.

\textbf{Caster Level for Armor and Shields:} The caster level of a magic shield or magic armor with a special ability is given in the item description. For an item with only an enhancement bonus, the caster level is three times the enhancement bonus. If an item has both an enhancement bonus and a special ability, the higher of the two caster level requirements must be met.

\textbf{Shields:} Shield enhancement bonuses stack with armor enhancement bonuses. Shield enhancement bonuses do not act as attack or damage bonuses when the shield is used in a bash. The bashing special ability, however, does grant a +1 bonus on attack and damage rolls.

A shield could be built that also acted as a magic weapon, but the cost of the enhancement bonus on attack rolls would need to be added into the cost of the shield and its enhancement bonus to AC.

As with armor, special abilities built into the shield add to the market value in the form of additions to the bonus of the shield, although they do not improve AC. A shield cannot have an effective bonus (enhancement plus special ability bonus equivalents) higher than +10. A shield with a special ability must have at least a +1 enhancement bonus.

\textbf{Shield Hardness and Hit Points:} Each +1 of enhancement bonus adds 2 to a shield's hardness and +10 to its hit points.

\textbf{Activation:} Usually a character benefits from magic armor and shields in exactly the way a character benefits from nonmagical armor and shields—by wearing them. If armor or a shield has a special ability that the user needs to activate then the user usually needs to utter the command word (a standard action).

\textbf{Armor for Unusual Creatures:} The cost of armor for nonhumanoid creatures, as well as for creatures who are neither Small nor Medium, varies. The cost of the masterwork quality and any magical enhancement remains the same.

\input{subsections/magic-items/armor/magic-armor-and-shield-special-ability-descriptions.tex}