\input{subsections/magic-items/creating-items-of-power/table-summary-magic-item-creation-costs.tex}
\section{Creating Items of Power}
To create magic items and psionic items, spellcasters and manifesters use special feats. They invest time, money, and their own personal energy (in the form of experience points) in an item's creation.

Note that all items have prerequisites in their descriptions. These prerequisites must be met for the item to be created. Most of the time, they take the form of spells that must be known by the item's creator (although access through another magic item or spellcaster is allowed).

While item creation costs are handled in detail below, note that normally the two primary factors are the caster level of the creator and the level of the spell or spells put into the item. A creator can create an item at a lower caster level than her own, but never lower than the minimum level needed to cast the needed spell. Using metamagic feats, a caster can place spells in items at a higher level than normal.

Magic supplies for items are always half of the base price in gp and 1/25 of the base price in XP. For many items, the market price equals the base price.

Armor, shields, weapons, and items with a value independent of their magically enhanced properties add their item cost to the market price. The item cost does not influence the base price (which determines the cost of magic supplies and the experience point cost), but it does increase the final market price.

In addition, some items cast or replicate spells with costly material components or with XP components. For these items, the market price equals the base price plus an extra price for the spell component costs. Each XP in the component costs adds 5 gp to the market price. The cost to create these items is the magic supplies cost and the base XP cost (both determined by the base price) plus the costs for the components. Descriptions of these items include an entry that gives the total cost of creating the item.

The creator also needs a fairly quiet, comfortable, and well-lit place in which to work. Any place suitable for preparing spells is suitable for making items. Creating an item requires one day per 1,000 gp in the item's base price, with a minimum of at least one day. Potions are an exception to this rule; they always take just one day to brew. The character must spend the gold and XP at the beginning of the construction process.

The caster works for 8 hours each day. He cannot rush the process by working longer each day. But the days need not be consecutive, and the caster can use the rest of his time as he sees fit.

A character can work on only one item at a time. If a character starts work on a new item, all materials used and XP spent on the under-construction item are wasted.

The secrets of creating artifacts are long lost.

\input{subsections/magic-items/creating-items-of-power/table-estimating-item-of-power-values.tex}
\input{subsections/magic-items/creating-items-of-power/item-of-power-values.tex}

\subsection{Masterwork Items}
Masterwork items are extraordinarily well-made items. They are more expensive, but they benefit the user with improved quality. They are not magical in any way. However, only masterwork items may be enhanced to become magic armor and weapons. (Items that are not weapons or armor may or may not be masterwork items.)

\input{subsections/magic-items/creating-items-of-power/creating-magic-armor.tex}
\input{subsections/magic-items/creating-items-of-power/creating-magic-weapons.tex}
\input{subsections/magic-items/creating-items-of-power/creating-potions.tex}
\input{subsections/magic-items/creating-items-of-power/creating-rings.tex}
\input{subsections/magic-items/creating-items-of-power/creating-rods.tex}
\input{subsections/magic-items/creating-items-of-power/creating-scrolls.tex}
\input{subsections/magic-items/creating-items-of-power/creating-staffs.tex}
\input{subsections/magic-items/creating-items-of-power/creating-wands.tex}
\input{subsections/magic-items/creating-items-of-power/creating-wondrous-items.tex}
\input{subsections/magic-items/creating-items-of-power/creating-intelligent-items.tex}
\input{subsections/magic-items/creating-items-of-power/creating-psionic-tattoos.tex}

\subsection{Adding New Abilities}
A creator can add new magical abilities to a magic item with no restrictions. The cost to do this is the same as if the item was not magical. Thus, a \emph{+1 longsword} can be made into a \emph{+2 vorpal longsword}, with the cost to create it being equal to that of a \emph{+2 vorpal sword} minus the cost of a \emph{+1 sword}.

If the item is one that occupies a specific place on a character's body the cost of adding any additional ability to that item increases by 50\%. For example, if a character adds the power to confer invisibility to her \emph{ring of protection +2}, the cost of adding this ability is the same as for creating a ring of invisibility multiplied by 1.5.

\subsection{Body Slot Affinities}
Each location on the body, or body slot, has one or more affinities: a word or phrase that describes the general function or nature of magic items designed for that body slot. Body slot affinities are deliberately broad, abstract categorizations, because a hard-and-fast rule can't cover the great variety among wondrous items.

\Table{Body Slot Affinities}{LL}{
  \tableheader Body Slot
& \tableheader Affinity\\
Headband, helmet                                     & Mental improvement, ranged attacks \\
Hat                                                  & Interaction \\
Phylactery                                           & Morale, alignment \\
Eye lenses, goggles                                  & Vision \\
Cloak, cape, mantle                                  & Transformation, protection \\
Amulet, brooch, medallion, necklace, periapt, scarab & Protection, discernment \\
Robe                                                 & Multiple effects \\
Shirt                                                & Physical improvement \\
Vest, vestment                                       & Class ability improvement \\
Bracers                                              & Combat \\
Bracelets                                            & Allies \\
Gloves                                               & Quickness \\
Gauntlets                                            & Destructive power \\
Belt                                                 & Physical improvement \\
Boots                                                & Movement \\
}

You can use the affinities in the \tabref{Body Slot Affinities} to guide your decisions on which magic items should be allowed in which body slots. And when you design your own magic items, the affinities give you some guidance for what form a particular item should take.

Some body slots have different affinities for different specific items.

Wondrous items that don't match the affinity for a particular body slot should cost 50\% more than wondrous items that match the affinity.

