\section{Cursed Items}
Cursed items are magic items with some sort of potentially negative impact. Sometimes they're directly bad for the user; sometimes they're just inconvenient. Occasionally they mix bad with good, forcing characters to make difficult choices.

\Table{Cursed Item Common Curses}{CX}{
  \tableheader d\%
& \tableheader Curse \\
01--15  & Delusion \\
16--35  & Opposite effect or target \\
36--45  & Intermittent functioning \\
46--60  & Requirement \\
61--75  & Drawback \\
76--90  & Completely different effect \\
91--100 & Substitute specific cursed item \\
}

\textbf{Delusion:} The user believes the item is what it appears to be, yet it actually has no magical power other than to deceive. The user is mentally fooled into thinking the item is functioning and cannot be convinced otherwise without the help of a remove curse spell.

\textbf{Opposite Effect or Target:} These cursed items malfunction, so that either they do the opposite of what the creator intended, or they target the user instead of someone else. The interesting point to keep in mind here is that these items aren't always bad to have. Opposite-effect items include weapons that impose penalties on attack and damage rolls rather than bonuses. Just as a character shouldn't necessarily immediately know what the enhancement bonus of a noncursed magic item is, she shouldn't immediately know that a weapon is cursed. Once she knows, however, the item can be discarded unless some sort of compulsion is placed upon it that compels the wielder to keep and use it. In such cases, a remove curse spell is generally needed to get rid of the item.

\textbf{Intermittent Functioning:} The three varieties of intermittent functioning items all function perfectly as described---at least some of the time. The three varieties are unreliable, dependent, and uncontrolled items.

\textbf{Unreliable:} Each time the item is activated, there is a 5\% chance (01--05 on d\%) that it does not function.

\textit{Dependent:} The item only functions in certain situations. To determine what the situation is, either select a situation or roll on the following table.

\Table{Dependent Curse Condition}{cL}{
  \tableheader d\%
& \tableheader Situation \\
01--03 & Temperature below freezing \\
04--05 & Temperature above freezing \\
06--10 & During the day \\
11--15 & During the night \\
16--20 & In direct sunlight \\
21--25 & Out of direct sunlight \\
26--34 & Underwater \\
35--37 & Out of water \\
38--45 & Underground \\
46--55 & Aboveground \\
56--60 & Within 3 meters of a random creature type \\
61--64 & Within 3 meters of a random race or kind of creature \\
65--72 & Within 3 meters of an arcane spellcaster \\
73--80 & Within 3 meters of a divine spellcaster \\
81--85 & In the hands of a nonspellcaster \\
86--90 & In the hands of a spellcaster \\
91--95 & In the hands of a creature of a particular alignment \\
  96   & In the hands of a creature of particular gender \\
97--99 & On nonholy days or during particular astrological events \\
  100  & More than 150 kilometers from a particular site \\
}

\textit{Uncontrolled:} An uncontrolled item occasionally activates at random times. Roll d\% every day. On a result of 01--05 the item activates at some random point during that day.

\textit{Requirement:} In a sense, a command word is a requirement. Nevertheless, some items have much more stringent requirements that must be met for them to be usable. To keep an item with this kind of curse functioning, one or more of the following conditions must be met.

\begin{itemize*}
\item Character must eat twice as much as normal.
\item Character must sleep twice as much as normal.
\item Character must undergo a specific quest (one time only, and then item functions normally thereafter).
\item Character must sacrifice (destroy) 100 gp worth of valuables per day.
\item Character must sacrifice (destroy) 2,000 gp worth of magic items each week.
\item Character must swear fealty to a particular noble or his family.
\item Character must discard all other magic items.
\item Character must worship a particular deity.
\item Character must change her name to a specific name. (The item only works for characters of that name.)
\item Character must add a specific class at the next opportunity if not of that class already.
\item Character must have a minimum number of ranks in a particular skill.
\item Character must sacrifice some part of her life energy (2 points of Constitution) one time. If the character gets the Constitution points back (such as from a \spell{restoration} spell), the item ceases functioning. (The item does not cease functioning if the character receives a Constitution increase caused by level gain, a wish, or the use of a magic item.)
\item Item must be cleansed with holy water each day.
\item Item must be used to kill a living creature each day.
\item Item must be bathed in volcanic lava once per month.
\item Item must be used at least once a day, or it won't function again for its current possessor.
\item Item must draw blood when wielded (weapons only). It can't be put away or exchanged for another weapon until it has scored a hit.
\item Item must have a particular spell cast upon it each day (such as \spell{bless}, \spell{atonement}, or \spell{animate objects}).
\end{itemize*}

Requirements are so dependent upon suitability to the item that they should never be determined randomly. An item with a requirement that is also intelligent often imposes its requirement through its personality. If the requirement is not met, the item ceases to function. If it is met, usually the item functions for one day before the requirement must be met again (although some requirements are one time only, others monthly, and still others continuous).

\textbf{Drawback:} Items with drawbacks are usually still beneficial to the possessor but they also carry some negative aspect. Although sometimes drawbacks occur only when the item is used (or held, in the case of some items such as weapons), usually the drawback remains with the character for as long as she has the item.

Roll on the table below to generate a drawback that (unless otherwise indicated) remains in effect as long as the item is in the character's possession.

\Table{Cursed Item Drawback}{cL}{
  \tableheader d\%
& \tableheader Drawback \\
01--04 & Character's hair grows 2 centimeters longer. Only happens once. \\
05--09 & Character either shrinks 1 centimeter (01--50 on d\%) or grows that much taller (51--100). Only happens once. \\
10--13 & Temperature around item is 5°C cooler than normal. \\
14--17 & Temperature around item is 5°C warmer than normal. \\
18--21 & Character's hair color changes. \\
22--25 & Character's skin color changes. \\
26--29 & Character now bears some identifying mark (tattoo, weird glow, or the like). \\
30--32 & Character's gender changes. \\
33--34 & Character's race or kind changes. \\
  35   & Character is afflicted with a random disease that cannot be cured. \\
36--39 & Item continually emits a disturbing sound (moaning, weeping, screaming, cursing, insults). \\
  40   & Item looks ridiculous (garishly colored, silly shape, glows bright pink, ...). \\
41--45 & Character becomes selfishly possessive about the item. \\
46--49 & Character becomes paranoid about losing the item and afraid of damage occurring to it. \\
50--51 & Character's alignment changes. \\
52--54 & Character must attack nearest creature (5\% chance [01--05 on d\%] each day). \\
55--57 & Character is stunned for 1d4 rounds once item function is finished (or randomly, 1/day). \\
58--60 & Character's vision is blurry ($-2$ penalty on attack rolls, saves, and skill checks requiring vision). \\
61--64 & Character gains one negative level. \\
  65   & Character gains two negative levels. \\
66--70 & Character must make a Will save each day or take 1 point of Intelligence damage. \\
71--75 & Character must make a Will save each day or take 1 point of Wisdom damage. \\
76--80 & Character must make a Will save each day or take 1 point of Charisma damage. \\
81--85 & Character must make a Fortitude save each day or take 1 point of Constitution damage. \\
86--90 & Character must make a Fortitude save each day or take 1 point of Strength damage. \\
91--95 & Character must make a Fortitude save each day or take 1 point of Dexterity damage. \\
  96   & Character is \spellref{polymorph}{polymorphed} into a specific creature (5\% chance [01--05 on d\%] each day). \\
  97   & Character cannot cast arcane spells. \\
  98   & Character cannot cast divine spells. \\
  99   & Character cannot cast any spells. \\
  100  & Either pick one of the above that's appropriate or create a drawback specifically for that item. \\
}

\input{subsections/magic-items/cursed-items/specific-cursed-items.tex}
