\section{Handling Magic Items}

\subsection{Identifying Items}
\textbf{Trial and Error:} Close study of an item might provide some information. A DC 15 (or maybe 20) \skill{Search} check should reveal a clue for how the item works, such as a tiny command word etched inside a ring or feather motifs that hint the ability to fly.

You might also permit a character to attempt a DC 30 \skill{Spellcraft} check or \skill{Knowledge} (arcana) check to determine if she can attune herself with the item's power or if she remembers reading of it once in her studies.

\textbf{Spells:} The easiest way to discern whether an object is magical is to use \spell{detect magic}. A character can focus on an item to determine the school of the spells embedded within it and the strength of the aura it gives off. The \spell{identify} and \spell{analyze dweomer} spells provide much more information.

\subsubsection{Magic Items and \emph{Detect Magic}}
When \spell{detect magic} identifies a magic item's school of magic, this information refers to the school of the spell placed within the potion, scroll, or wand, or the prerequisite given for the item. The description of each item provides its aura strength and the school it belongs to.

If more than one spell is given as a prerequisite, use the highest-level spell. If no spells are included in the prerequisites, use the following default guidelines.

\Table{}{lX}{
\tableheader Item Nature & \tableheader School \\
Armor and protection items & Abjuration \\
Weapons or offensive items & Evocation \\
Bonus to ability score, on skill check, etc. & Transmutation \\
}

% \subsubsection{Psionic Items and \emph{Detect Psionics}}
% When \psionic{detect psionics} identifies a magic item's school of magic, this information refers to the school of the spell placed within the potion, scroll, or wand, or the prerequisite given for the item. The description of each item provides its aura strength and the school it belongs to.

% If more than one spell is given as a prerequisite, use the highest-level spell. If no spells are included in the prerequisites, use the following default guidelines.

% \Table{}{lX}{
% \tableheader Item Nature & \tableheader School \\
% Armor and protection items & Abjuration \\
% Weapons or offensive items & Evocation \\
% Bonus to ability score, on skill check, etc. & Transmutation \\
% }

\input{subsections/magic-items/handling-magic-items/using-items.tex}
\input{subsections/magic-items/handling-magic-items/size-and-magic-items.tex}
\input{subsections/magic-items/handling-magic-items/magic-items-on-the-body.tex}

\subsection{Saving Throws Against Magic Item Powers}
Magic items produce spells or spell-like effects. For a saving throw against a spell or spell-like effect from a magic item, the DC is 10 + the level of the spell or effect + the ability modifier of the minimum ability score needed to cast that level of spell. Another way to figure the same number is to multiply the power's level by 1\onehalf and add 10 to the result.

Staffs are an exception to the rule. Treat the saving throw as if the wielder cast the spell, including caster level and all modifiers to save DC.

Most item descriptions give saving throw DCs for various effects, particularly when the effect has no exact spell equivalent (making its level otherwise difficult to determine quickly).

\subsection{Damaging Items of Power}
An item of power doesn't need to make a saving throw unless it is unattended, it is specifically targeted by the effect, or its wielder rolls a natural 1 on his save. Items of power should always get a saving throw against spells that might deal damage to them---even against attacks from which a mundane item would normally get no chance to save. Items of power use the same saving throw bonus for all saves, no matter what the type (Fortitude, Reflex, or Will). An item of power's saving throw bonus equals 2 + \onehalf its caster/manifester level (round down). The only exceptions to this are intelligent items, which make Will saves based on their own Wisdom scores.

Items of power, unless otherwise noted, take damage as mundane items of the same sort. A damaged magic item continues to function, but if it is destroyed, all its power is lost.

\subsection{Repairing Items of Power}
Some items of power take damage over the course of an adventure. It costs no more to repair a item of power with the \skill{Craft} skill than it does to repair its nonmagical counterpart. The \spell{make whole} spell also repairs a damaged---but not completely broken---item of power.

% \subsection{Intelligent Items}
% Some magic items, particularly weapons, have an intelligence all their own. Only permanent magic items (as opposed to those with a single use or those with charges) can be intelligent. (This means that potions, scrolls, and wands, among other items, are never intelligent.)

% In general, less than 1\% of magic items have intelligence.

\subsection{Cursed Items}
Some items are cursed---incorrectly made, or corrupted by outside forces. Cursed items might be particularly dangerous to the user, or they might be normal items with a minor flaw, an inconvenient requirement, or an unpredictable nature. Randomly generated items are cursed 5\% of the time.

\subsection{Charges, Doses, And Multiple Uses}
Many items, particularly wands and staffs, are limited in power by the number of charges they hold. Normally, charged items have 50 charges at most. If such an item is found as a random part of a treasure, roll d\% and divide by 2 to determine the number of charges left (round down, minimum 1). If the item has a maximum number of charges other than 50, roll randomly to determine how many charges are left.

Prices listed are always for fully charged items. (When an item is created, it is fully charged.) For an item that's worthless when its charges run out (which is the case for almost all charged items), the value of the partially used item is proportional to the number of charges left. For an item that has usefulness in addition to its charges, only part of the item's value is based on the number of charges left.