\subsectionA{Potions and Oils}
A potion is a magic liquid that produces its effect when imbibed. Magic oils are similar to potions, except that oils are applied externally rather than imbibed. A potion or oil can be used only once. It can duplicate the effect of a spell of up to 3rd level that has a casting time of less than 1 minute.

Potions are like spells cast upon the imbiber. The character taking the potion doesn't get to make any decisions about the effect---the caster who brewed the potion has already done so. The drinker of a potion is both the effective target and the caster of the effect (though the potion indicates the caster level, the drinker still controls the effect).

The person applying an oil is the effective caster, but the object is the target.

\textbf{Physical Description:} A typical potion or oil consists of 30 mililiters of liquid held in a ceramic or glass vial fitted with a tight stopper. The stoppered container is usually no more than 1 inch wide and 2 inches high. The vial has AC 13, 1 hit point, hardness 1, and a break DC of 12. Vials hold 30 mililiters of liquid.

\textbf{Identifying Potions:} In addition to the standard methods of identification, PCs can sample from each container they find to attempt to determine the nature of the liquid inside. An experienced character learns to identify potions by memory---for example, the last time she tasted a liquid that reminded her of almonds, it turned out to be a potion of cure moderate wounds.

\textbf{Activation:} Drinking a potion or applying an oil requires no special skill. The user merely removes the stopper and swallows the potion or smears on the oil. The following rules govern potion and oil use.

Drinking a potion or using an oil on an item of gear is a standard action. The potion or oil takes effect immediately. Using a potion or oil provokes attacks of opportunity. A successful attack (including grappling attacks) against the character forces a Concentration check (as for casting a spell). If the character fails this check, she cannot drink the potion. An enemy may direct an attack of opportunity against the potion or oil container rather than against the character. A successful attack of this sort can destroy the container.

A creature must be able to swallow a potion or smear on an oil. Because of this, incorporeal creatures cannot use potions or oils.

Any corporeal creature can imbibe a potion. The potion must be swallowed. Any corporeal creature can use an oil.

A character can carefully administer a potion to an unconscious creature as a full-round action, trickling the liquid down the creature's throat. Likewise, it takes a full-round action to apply an oil to an unconscious creature.

\subsubsection{Potion Descriptions}
The caster level for a standard potion is the minimum caster level needed to cast the spell (unless otherwise specified).

\Table{Potions and Oils I}{Xr{15mm}} {
\tableheader Potion or Oil & \tableheader Market Price \\
\spell{cure light wounds} (potion)                & 50 cp \\
\spell{endure elements} (potion)                  & 50 cp \\
\spell{hide from animals} (potion)                & 50 cp \\
\spell{hide from undead} (potion)                 & 50 cp \\
\spell{jump} (potion)                             & 50 cp \\
\spell{mage armor} (potion)                       & 50 cp \\
\spell{magic fang} (potion)                       & 50 cp \\
\spell{magic stone} (oil)                         & 50 cp \\
\spell{magic weapon} (oil)                        & 50 cp \\
\spell{pass without trace} (potion)               & 50 cp \\
 \emph{protection from (alignment)} (potion)      & 50 cp \\
\spell{remove fear} (potion)                      & 50 cp \\
\spell{sanctuary} (potion)                        & 50 cp \\
\spell{shield of faith} +2 (potion)               & 50 cp \\
\spell{shillelagh} (oil)                          & 50 cp \\
\spell{bless weapon} (oil)                        & 100 cp \\
\spell{enlarge person} (potion)                   & 250 cp \\
\spell{reduce person} (potion)                    & 250 cp \\
\spell{aid} (potion)                              & 300 cp \\
\spell{barkskin} +2 (potion)                      & 300 cp \\
\spell{bear's endurance} (potion)                 & 300 cp \\
\spell{blur} (potion)                             & 300 cp \\
\spell{bull's strength} (potion)                  & 300 cp \\
\spell{cat's grace} (potion)                      & 300 cp \\
\spell{cure moderate wounds} (potion)             & 300 cp \\
\spell{darkness} (oil)                            & 300 cp \\
\spell{darkvision} (potion)                       & 300 cp \\
\spell{delay poison} (potion)                     & 300 cp \\
\spell{eagle's splendor} (potion)                 & 300 cp \\
\spell{fox's cunning} (potion)                    & 300 cp \\
\spell{invisibility} (potion or oil)              & 300 cp \\
\spell{lesser restoration} (potion)               & 300 cp \\
\spell{levitate} (potion or oil)                  & 300 cp \\
\spell{misdirection} (potion)                     & 300 cp \\
\spell{owl's wisdom} (potion)                     & 300 cp \\
\spell{protection from arrows} 10/magic (potion)  & 300 cp \\
\spell{remove paralysis} (potion)                 & 300 cp \\
\spell{resist energy} (type) 10 (potion)          & 300 cp \\
\spell{shield of faith} +3 (potion)               & 300 cp \\
\spell{spider climb} (potion)                     & 300 cp \\
\spell{undetectable alignment} (potion)           & 300 cp \\
\spell{barkskin} +3 (potion)                      & 600 cp \\
\spell{shield of faith} +4 (potion)               & 600 cp \\
\spell{resist energy} (type) 20 (potion)          & 700 cp \\
}

\Table{Potions and Oils II}{Xr{15mm}} {
\tableheader Potion or Oil & \tableheader Market Price \\
\spell{cure serious wounds} (potion)              & 750 cp \\
\spell{daylight} (oil)                            & 750 cp \\
\spell{displacement} (potion)                     & 750 cp \\
\spell{flame arrow} (oil)                         & 750 cp \\
\spell{fly} (potion)                              & 750 cp \\
\spell{gaseous form} (potion)                     & 750 cp \\
\spell{greater magic fang} +1 (potion)            & 750 cp \\
\spell{greater magic weapon} +1 (oil)             & 750 cp \\
\spell{haste} (potion)                            & 750 cp \\
\spell{heroism} (potion)                          & 750 cp \\
\spell{keen edge} (oil)                           & 750 cp \\
 \emph{magic circle against (alignment)} (potion) & 750 cp \\
\spell{magic vestment} +1 (oil)                   & 750 cp \\
\spell{neutralize poison} (potion)                & 750 cp \\
\spell{nondetection} (potion)                     & 750 cp \\
\spell{protection from energy} (type) (potion)    & 750 cp \\
\spell{rage} (potion)                             & 750 cp \\
\spell{remove blindness/deafness} (potion)        & 750 cp \\
\spell{remove curse} (potion)                     & 750 cp \\
\spell{remove disease} (potion)                   & 750 cp \\
\spell{tongues} (potion)                          & 750 cp \\
\spell{water breathing} (potion)                  & 750 cp \\
\spell{water walk} (potion)                       & 750 cp \\
\spell{barkskin} +4 (potion)                      & 900 cp \\
\spell{shield of faith} +5 (potion)               & 900 cp \\
\spell{good hope} (potion)                        & 1,050 cp \\
\spell{resist energy} (type) 30 (potion)          & 1,100 cp \\
\spell{barkskin} +5 (potion)                      & 1,200 cp \\
\spell{greater magic fang} +2 (potion)            & 1,200 cp \\
\spell{greater magic weapon} +2 (oil)             & 1,200 cp \\
\spell{magic vestment} +2 (oil)                   & 1,200 cp \\
\spell{protection from arrows} 15/magic (potion)  & 1,500 cp \\
\spell{greater magic fang} +3 (potion)            & 1,800 cp \\
\spell{greater magic weapon} +3 (oil)             & 1,800 cp \\
\spell{magic vestment} +3 (oil)                   & 1,800 cp \\
\spell{greater magic fang} +4 (potion)            & 2,400 cp \\
\spell{greater magic weapon} +4 (oil)             & 2,400 cp \\
\spell{magic vestment} +4 (oil)                   & 2,400 cp \\
\spell{greater magic fang} +5 (potion)            & 3,000 cp \\
\spell{greater magic weapon} +5 (oil)             & 3,000 cp \\
\spell{magic vestment} +5 (oil)                   & 3,000 cp \\
}
