\subsectionA{Scrolls}
A scroll is a spell (or collection of spells) that has been stored in written form. A spell on a scroll can be used only once. The writing vanishes from the scroll when the spell is activated. Using a scroll is basically like casting a spell.

\textbf{Physical Description:} A scroll is a heavy sheet of fine vellum or high-quality paper. An area about 20 centimeters wide and 30 centimeters long is sufficient to hold one spell. The sheet is reinforced at the top and bottom with strips of leather slightly longer than the sheet is wide. A scroll holding more than one spell has the same width (about 20 centimeters) but is an extra 30 centimeters long for each extra spell. Scrolls that hold three or more spells are usually fitted with reinforcing rods at each end rather than simple strips of leather. A scroll has AC 9, 1 hit point, hardness 0, and a break DC of 8.

To protect it from wrinkling or tearing, a scroll is rolled up from both ends to form a double cylinder. (This also helps the user unroll the scroll quickly.) The scroll is placed in a tube of ivory, jade, leather, metal, or wood. Most scroll cases are inscribed with magic symbols which often identify the owner or the spells stored on the scrolls inside. The symbols often hide magic traps.

\textbf{Activation:} To activate a scroll, a spellcaster must read the spell written on it. Doing so involves several steps and conditions.

\textit{Decipher the Writing:} The writing on a scroll must be deciphered before a character can use it or know exactly what spell it contains. This requires a \spell{read magic} spell or a successful \skill{Spellcraft} check (DC 20 + spell level).

Deciphering a scroll to determine its contents does not activate its magic unless it is a specially prepared cursed scroll. A character can decipher the writing on a scroll in advance so that he or she can proceed directly to the next step when the time comes to use the scroll.

\textit{Activate the Spell:} Activating a scroll requires reading the spell from the scroll. The character must be able to see and read the writing on the scroll. Activating a scroll spell requires no material components or focus. (The creator of the scroll provided these when scribing the scroll.) Note that some spells are effective only when cast on an item or items. In such a case, the scroll user must provide the item when activating the spell. Activating a scroll spell is subject to disruption just as casting a normally prepared spell would be. Using a scroll is like casting a spell for purposes of arcane spell failure chance.

To have any chance of activating a scroll spell, the scroll user must meet the following requirements.

\begin{itemize*}
\item The spell must be of the correct type (arcane or divine). Arcane spellcasters (assassins and wizards) can only use scrolls containing arcane spells, and divine spellcasters (clerics, druids, and rangers) can only use scrolls containing divine spells. (The type of scroll a character creates is also determined by his or her class.)
\item The user must have the spell on his or her class list.
\item The user must have the requisite ability score.
\end{itemize*}

If the user meets all the requirements noted above, and her caster level is at least equal to the spell's caster level, she can automatically activate the spell without a check. If she meets all three requirements but her own caster level is lower than the scroll spell's caster level, then she has to make a caster level check (DC = scroll's caster level + 1) to cast the spell successfully. If she fails, she must make a DC 5 Wisdom check to avoid a mishap (see Scroll Mishaps, below). A natural roll of 1 always fails, whatever the modifiers.

\textit{Determine Effect:} A spell successfully activated from a scroll works exactly like a spell prepared and cast the normal way. Assume the scroll spell's caster level is always the minimum level required to cast the spell for the character who scribed the scroll (usually twice the spell's level, minus 1), unless the caster specifically desires otherwise.

The writing for an activated spell disappears from the scroll.

\textit{Scroll Mishaps:} When a mishap occurs, the spell on the scroll has a reversed or harmful effect. Possible mishaps are given below.

\begin{itemize*}
\item A surge of uncontrolled magical energy deals 1d6 points of damage per spell level to the scroll user.
\item Spell strikes the scroll user or an ally instead of the intended target, or a random target nearby if the scroll user was the intended recipient.
\item Spell takes effect at some random location within spell range.
\item Spell's effect on the target is contrary to the spell's normal effect.
\item The scroll user suffers some minor but bizarre effect related to the spell in some way. Most such effects should last only as long as the original spell's duration, or 2d10 minutes for instantaneous spells.
\item Some innocuous item or items appear in the spell's area.
\item Spell has delayed effect. Sometime within the next 1d12 hours, the spell activates. If the scroll user was the intended recipient, the spell takes effect normally. If the user was not the intended recipient, the spell goes off in the general direction of the original recipient or target, up to the spell's maximum range, if the target has moved away.
\end{itemize*}

Several arcane spells are different in level for wizards than they are for assassins. Such spells appear on the table at the level appropriate to a wizard (considered the default because assassins typically don't involve themselves in scribing scrolls).

Likewise, some divine spells are different in level for clerics and druids than they are for rangers. Such spells appear at the level appropriate to a cleric or druid (considered the default because rangers typically don't involve themselves in scribing scrolls).
% Several divine spells are different in level for clerics and druids than they are for rangers. Such spells appear at the level appropriate to a cleric or druid (considered the default because rangers typically don't involve themselves in scribing scrolls).

If a divine spell is cast at different levels by clerics and druids, it appears at the level appropriate to a cleric (considered the default choice between clerics and druids).

Many spells are either arcane or divine, depending on the class of the caster. Such spells appear on both lists at the level appropriate to the class of the arcane or divine caster.


\Table{Arcane Spells I}{Xr{15mm}}{
\multicolumn{2}{c}{\tableheader 0-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell       & \tableheader Market Price\\
\spell{acid splash}      & 12 cp 5 bits\\
\spell{arcane mark}      & 12 cp 5 bits\\
\spell{dancing lights}   & 12 cp 5 bits\\
\spell{daze}             & 12 cp 5 bits\\
\spell{detect magic}     & 12 cp 5 bits\\
\spell{detect poison}    & 12 cp 5 bits\\
\spell{disrupt undead}   & 12 cp 5 bits\\
\spell{flare}            & 12 cp 5 bits\\
\spell{ghost sound}      & 12 cp 5 bits\\
\spell{light}            & 12 cp 5 bits\\
\spell{mage hand}        & 12 cp 5 bits\\
\spell{mending}          & 12 cp 5 bits\\
\spell{message}          & 12 cp 5 bits\\
\spell{open/close}       & 12 cp 5 bits\\
\spell{prestidigitation} & 12 cp 5 bits\\
\spell{ray of frost}     & 12 cp 5 bits\\
\spell{read magic}       & 12 cp 5 bits\\
\spell{resistance}       & 12 cp 5 bits\\
\spell{slave scent}      & 12 cp 5 bits\\
\spell{touch of fatigue} & 12 cp 5 bits\\

\cmidrule[0pt]{1-2}
\multicolumn{2}{c}{\tableheader 1st-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                          & \tableheader Market Price\\
\spell{alarm}                               & 25 cp\\
\spell{animate rope}                        & 25 cp\\
\spell{burning hands}                       & 25 cp\\
\spell{cause fear}                          & 25 cp\\
\spell{charm person}                        & 25 cp\\
\spell{chill touch}                         & 25 cp\\
\spell{color spray}                         & 25 cp\\
\spell{comprehend languages}                & 25 cp\\
\spell{cooling canopy}                      & 25 cp\\
\spell{detect poison}\footnotemark[1]       & 25 cp\\
\spell{detect secret doors}                 & 25 cp\\
\spell{detect undead}                       & 25 cp\\
\spell{disguise self}                       & 25 cp\\
\spell{endure elements}                     & 25 cp\\
\spell{enlarge person}                      & 25 cp\\
\spell{erase}                               & 25 cp\\
\spell{expeditious retreat}                 & 25 cp\\
\spell{feather fall}                        & 25 cp\\
\spell{floating disk}                       & 25 cp\\
\spell{ghost sound}\footnotemark[1]         & 25 cp\\
\spell{grease}                              & 25 cp\\
\spell{hold portal}                         & 25 cp\\
\spell{hypnotism}                           & 25 cp\\
\spell{identify}                            & 125 cp\\
\spell{illusory talent}                     & 25 cp\\
\spell{jump}                                & 25 cp\\
\spell{mage armor}                          & 25 cp\\
\spell{magic aura}                          & 25 cp\\
\spell{magic missile}                       & 25 cp\\
\spell{magic weapon}                        & 25 cp\\
\spell{mount}                               & 25 cp\\
\spell{obscuring mist}                      & 25 cp\\
\spell{protection from chaos}/\spellref{protection from evil}{evil}/\spellref{protection from good}{good}/\spellref{protection from law}{law}
& 25 cp\\
\spell{ray of enfeeblement}                 & 25 cp\\
\spell{reduce person}                       & 25 cp\\
\spell{shield}                              & 25 cp\\
\spell{shocking grasp}                      & 25 cp\\
\spell{silent image}                        & 25 cp\\
\spell{slave scent}\footnotemark[1]         & 25 cp\\
\spell{sleep}                               & 25 cp\\
\spell{summon monster I}                    & 25 cp\\
\spell{true strike}                         & 25 cp\\
\spell{unseen servant}                      & 25 cp\\
\spell{ventriloquism}                       & 25 cp\\


\cmidrule[0pt]{1-2}
\multicolumn{2}{c}{\tableheader 2nd-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                             & \tableheader Market Price\\
\spell{acid arrow}                             & 150 cp \\
\spell{alter self}                             & 150 cp \\
\spell{arcane lock}                            & 175 cp \\
\spell{backlash}                               & 150 cp \\
\spell{bear's endurance}                       & 150 cp \\
\spell{blindness/deafness}                     & 150 cp \\
\spell{blur}                                   & 150 cp \\
\spell{boneharden}                             & 150 cp \\
}

\Table{Arcane Spells II}{Xr{15mm}}{
\multicolumn{2}{c}{\tableheader 2nd-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                             & \tableheader Market Price\\
\spell{bull's strength}                        & 150 cp \\
\spell{cat's grace}                            & 150 cp \\
\spell{cerulean shock}                         & 150 cp \\
\spell{command undead}                         & 150 cp \\
\spell{continual flame}                        & 200 cp \\
\spell{darkness}                               & 150 cp \\
\spell{darkvision}                             & 150 cp \\
\spell{daze monster}                           & 150 cp \\
\spell{death mark}                             & 150 cp \\
\spell{detect thoughts}                        & 150 cp \\
\spell{eagle's splendor}                       & 150 cp \\
\spell{eye of the storm}                       & 150 cp \\
\spell{false life}                             & 150 cp \\
\spell{flaming sphere}                         & 150 cp \\
\spell{fog cloud}                              & 150 cp \\
\spell{footsteps of the quarry}                & 150 cp \\
\spell{fox's cunning}                          & 150 cp \\
\spell{ghoul touch}                            & 150 cp \\
\spell{glitterdust}                            & 150 cp \\
\spell{gust of wind}                           & 150 cp \\
\spell{hideous laughter}                       & 150 cp \\
\spell{hypnotic pattern}                       & 150 cp \\
\spell{illusory script}\footnotemark[1]        & 200 cp \\
\spell{invisibility}                           & 150 cp \\
\spell{knock}                                  & 150 cp \\
\spell{levitate}                               & 150 cp \\
\spell{locate object}                          & 150 cp \\
\spell{magic mouth}                            & 160 cp \\
\spell{minor image}                            & 150 cp \\
\spell{mirror image}                           & 150 cp \\
\spell{misdirection}                           & 150 cp \\
\spell{obscure object}                         & 150 cp \\
\spell{owl's wisdom}                           & 150 cp \\
\spell{pass without trace}                     & 150 cp \\
\spell{phantom trap}                           & 200 cp \\
\spell{protection from arrows}                 & 150 cp \\
\spell{pyrotechnics}                           & 150 cp \\
\spell{resist energy}                          & 150 cp \\
\spell{rope trick}                             & 150 cp \\
\spell{sandstone}                              & 150 cp \\
\spell{scare}                                  & 150 cp \\
\spell{scorching ray}                          & 150 cp \\
\spell{see invisibility}                       & 150 cp \\
\spell{shatter}                                & 150 cp \\
\spell{spectral hand}                          & 150 cp \\
\spell{spider climb}                           & 150 cp \\
\spell{sting of the gold scorpion}             & 150 cp \\
\spell{summon monster II}                      & 150 cp \\
\spell{summon swarm}                           & 150 cp \\
\spell{touch of idiocy}                        & 150 cp \\
\spell{undetectable alignment}\footnotemark[1] & 150 cp \\
\spell{wakefulness}                            & 150 cp \\
\spell{web}                                    & 150 cp \\
\spell{whispering wind}                        & 150 cp \\

\cmidrule[0pt]{1-2}
\multicolumn{2}{c}{\tableheader 3rd-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                               & \tableheader Market Price\\
\spell{arcane sight}                             & 375 cp \\
\spell{blink}                                    & 375 cp \\
\spell{boneclaw's cut}                           & 375 cp \\
\spell{clairaudience/clairvoyance}               & 375 cp \\
\spell{clear-river}                              & 375 cp \\
\spell{conservation}                             & 375 cp \\
\spell{daylight}                                 & 375 cp \\
\spell{dedication}                               & 375 cp \\
\spell{deep slumber}                             & 375 cp \\
\spell{deeper darkness}\footnotemark[1]          & 375 cp \\
\spell{dispel magic}                             & 375 cp \\
\spell{displacement}                             & 375 cp \\
\spell{explosive runes}                          & 375 cp \\
\spell{false life}\footnotemark[1]               & 375 cp \\
\spell{fireball}                                 & 375 cp \\
\spell{flame arrow}                              & 375 cp \\
\spell{fly}                                      & 375 cp \\
\spell{gaseous form}                             & 375 cp \\
\spell{gentle repose}                            & 375 cp \\
\spell{halt undead}                              & 375 cp \\
}

\Table{Arcane Spells III}{Xr{15mm}}{
\multicolumn{2}{c}{\tableheader 3rd-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                             & \tableheader Market Price\\
\spell{haste}                                    & 375 cp \\
\spell{heroism}                                  & 375 cp \\
\spell{hold person}                              & 375 cp \\
\spell{illusory script}                          & 425 cp \\
\spell{invisibility sphere}                      & 375 cp \\
\spell{keen edge}                                & 375 cp \\
\spell{lightning bolt}                           & 375 cp \\
\spell{magic circle against chaos}/\spellref{magic circle against evil}{evil}/\spellref{magic circle against good}{good}/\spellref{magic circle against law}{law}
	& 375 cp \\
\spell{magic weapon, greater}                    & 375 cp \\
\spell{major image}                              & 375 cp \\
\spell{misdirection}\footnotemark[1]             & 375 cp \\
\spell{nondetection}                             & 425 cp \\
\spell{phantom steed}                            & 375 cp \\
\spell{protection from energy}                   & 375 cp \\
\spell{rage}                                     & 375 cp \\
\spell{ray of exhaustion}                        & 375 cp \\
\spell{secret page}                              & 375 cp \\
\spell{sepia snake sigil}                        & 875 cp \\
\spell{shrink item}                              & 375 cp \\
\spell{sleet storm}                              & 375 cp \\
\spell{slow}                                     & 375 cp \\
\spell{stinking cloud}                           & 375 cp \\
\spell{suggestion}                               & 375 cp \\
\spell{summon monster III}                       & 375 cp \\
\spell{tiny hut}                                 & 375 cp \\
\spell{tongues}                                  & 375 cp \\
\spell{vampiric touch}                           & 375 cp \\
\spell{wind wall}                                & 375 cp \\
\spell{worm's breath}                            & 375 cp \\
\spell{zombie berry}                             & 375 cp \\

\cmidrule[0pt]{1-2}
\multicolumn{2}{c}{\tableheader 4th-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                                       & \tableheader Market Price\\
\spell{animate dead}                                     & 1,050 cp \\
\spell{arcane eye}                                       & 700 cp \\
\spell{bestow curse}                                     & 700 cp \\
\spell{black tentacles}                                  & 700 cp \\
\spell{charm monster}                                    & 700 cp \\
\spell{clairaudience/clairvoyance}\footnotemark[1]       & 700 cp \\
\spell{claws of the tembo}                               & 700 cp \\
\spell{confusion}                                        & 700 cp \\
\spell{contagion}                                        & 700 cp \\
\spell{crushing despair}                                 & 700 cp \\
\spell{detect scrying}                                   & 700 cp \\
\spell{dimension door}                                   & 700 cp \\
\spell{dimensional anchor}                               & 700 cp \\
\spell{dweomer fo transference}                          & 700 cp \\
\spell{enervation}                                       & 700 cp \\
\spell{fear}                                             & 700 cp \\
\spell{fire shield}                                      & 700 cp \\
\spell{fire trap}                                        & 725 cp \\
\spell{freedom of movement}\footnotemark[1]              & 700 cp \\
\spell{ghostfire}                                        & 700 cp \\
\spell{glibness}\footnotemark[1]                         & 700 cp \\
\spell{gloomcloud}                                       & 700 cp \\
\spell{greater invisibility}                             & 700 cp \\
\spell{hallucinatory terrain}                            & 700 cp \\
\spell{ice storm}                                        & 700 cp \\
\spell{illusory wall}                                    & 700 cp \\
\spell{lesser geas}                                      & 700 cp \\
\spell{lesser globe of invulnerability}                  & 700 cp \\
\spell{locate creature}                                  & 700 cp \\
\spell{mage seeker}                                      & 700 cp \\
\spell{mass enlarge person}                              & 700 cp \\
\spell{mass reduce person}                               & 700 cp \\
\spell{minor creation}                                   & 700 cp \\
\spell{mnemonic enhancer}                                & 700 cp \\
\spell{phantasmal killer}                                & 700 cp \\
\spell{poison}\footnotemark[1]                           & 700 cp \\
\spell{polymorph}                                        & 700 cp \\
\spell{rainbow pattern}                                  & 700 cp \\
\spell{rangeblade}\footnotemark[1]                       & 700 cp \\
\spell{remove curse}                                     & 700 cp \\
\spell{resilient sphere}                                 & 700 cp \\
\spell{sand spray}                                       & 700 cp \\
\spell{scapegoat}\footnotemark[1]                        & 700 cp \\
\spell{scrying}                                          & 700 cp \\
}

\Table{Arcane Spells IV}{Xr{15mm}}{
\multicolumn{2}{c}{\tableheader 4th-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                                         & \tableheader Market Price\\
\spell{secure shelter}                                   & 700 cp \\
\spell{shadow conjuration}                               & 700 cp \\
\spell{shout}                                            & 700 cp \\
\spell{solid fog}                                        & 700 cp \\
\spell{stone shape}                                      & 700 cp \\
\spell{stoneskin}                                        & 950 cp \\
\spell{summon monster IV}                                & 700 cp \\
\spell{touch the Black}                                  & 700 cp \\
\spell{wall of fire}                                     & 700 cp \\
\spell{wall of ice}                                      & 700 cp \\

\cmidrule[0pt]{1-2}
\multicolumn{2}{c}{\tableheader 5th-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell               & \tableheader Market Price\\
\spell{animal growth}            & 1,125 cp \\
\spell{baleful polymorph}        & 1,125 cp \\
\spell{blight}                   & 1,125 cp \\
\spell{break enchantment}        & 1,125 cp \\
\spell{cerulean hail}            & 1,125 cp \\
\spell{cloudkill}                & 1,125 cp \\
\spell{cone of cold}             & 1,125 cp \\
\spell{contact other plane}      & 1,125 cp \\
\spell{dismissal}                & 1,125 cp \\
\spell{dominate person}          & 1,125 cp \\
\spell{dream}                    & 1,125 cp \\
\spell{fabricate}                & 1,125 cp \\
\spell{false vision}             & 1,375 cp \\
\spell{feeblemind}               & 1,125 cp \\
\spell{hold monster}             & 1,125 cp \\
\spell{interposing hand}         & 1,125 cp \\
\spell{mage's faithful hound}    & 1,125 cp \\
\spell{mage's private sanctum}   & 1,125 cp \\
\spell{magic jar}                & 1,125 cp \\
\spell{major creation}           & 1,125 cp \\
\spell{mind fog}                 & 1,125 cp \\
\spell{mirage arcana}            & 1,125 cp \\
\spell{nightmare}                & 1,125 cp \\
\spell{overland flight}          & 1,125 cp \\
\spell{passwall}                 & 1,125 cp \\
\spell{permanency}               & 10,125 cp\footnotemark[2] \\
\spell{persistent image}         & 1,125 cp \\
\spell{lesser planar binding}    & 1,125 cp \\
\spell{prying eyes}              & 1,125 cp \\
\spell{psychic turmoil}          & 1,125 cp \\
\spell{quietstorm}               & 1,125 cp \\
\spell{ragestorm}                & 1,125 cp \\
\spell{rangeblade}               & 1,125 cp \\
\spell{sand trap}                & 1,125 cp \\
\spell{sandflow}                 & 1,125 cp \\
\spell{secret chest}             & 1,125 cp \\
\spell{seeming}                  & 1,125 cp \\
\spell{sending}                  & 1,125 cp \\
\spell{shadow evocation}         & 1,125 cp \\
\spell{skyfire}                  & 1,125 cp \\
\spell{sparkrain}                & 1,125 cp \\
\spell{summon monster V}         & 1,125 cp \\
\spell{symbol of pain}           & 2,125 cp \\
\spell{symbol of sleep}          & 2,125 cp \\
\spell{telekinesis}              & 1,125 cp \\
\spell{telepathic bond}          & 1,125 cp \\
\spell{teleport}                 & 1,125 cp \\
\spell{transmute mud to rock}    & 1,125 cp \\
\spell{transmute rock to mud}    & 1,125 cp \\
\spell{wall of force}            & 1,125 cp \\
\spell{wall of stone}            & 1,125 cp \\
\spell{waves of fatigue}         & 1,125 cp \\

\cmidrule[0pt]{1-2}
\multicolumn{2}{c}{\tableheader 6th-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                 & \tableheader Market Price\\
\spell{acid fog}                   & 1,650 cp \\
\spell{analyze dweomer}            & 1,650 cp \\
\spell{antimagic field}            & 1,650 cp \\
\spell{banish Tyr-storm}           & 1,650 cp \\
\spell{braxatskin}                 & 1,650 cp \\
\spell{chain lightning}            & 1,650 cp \\
\spell{circle of death}            & 2,150 cp \\
\spell{cleansing flame}            & 1,650 cp \\
\spell{contingency}                & 1,650 cp \\
\spell{control tides}              & 1,650 cp \\
}

\Table{Arcane Spells V}{Xr{15mm}}{
\multicolumn{2}{c}{\tableheader 6th-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                 & \tableheader Market Price\\
\spell{create undead}              & 2,350 cp \\
\spell{disintegrate}               & 1,650 cp \\
\spell{eyebite}                    & 1,650 cp \\
\spell{flesh to stone}             & 1,650 cp \\
\spell{forceful hand}              & 1,650 cp \\
\spell{freezing sphere}            & 1,650 cp \\
\spell{geas/quest}                 & 1,650 cp \\
\spell{globe of invulnerability}   & 1,650 cp \\
\spell{greater dispel magic}       & 1,650 cp \\
\spell{greater heroism}            & 1,650 cp \\
\spell{groundflame}                & 1,650 cp \\
\spell{guards and wards}           & 1,650 cp \\
\spell{hardening}                  & 1,650 cp \\
\spell{legend lore}                & 1,900 cp \\
\spell{mage's lucubration}         & 1,650 cp \\
\spell{mass bear's endurance}      & 1,650 cp \\
\spell{mass bull's strength}       & 1,650 cp \\
\spell{mass cat's grace}           & 1,650 cp \\
\spell{mass eagle's splendor}      & 1,650 cp \\
\spell{mass fox's cunning}         & 1,650 cp \\
\spell{mass owl's wisdom}          & 1,650 cp \\
\spell{mass suggestion}            & 1,650 cp \\
\spell{mental pinnacle}            & 1,650 cp \\
\spell{mislead}                    & 1,650 cp \\
\spell{move earth}                 & 1,650 cp \\
\spell{permanent image}            & 1,650 cp \\
\spell{planar binding}             & 1,650 cp \\
\spell{probe thoughts}             & 1,650 cp \\
\spell{programmed image}           & 1,675 cp \\
\spell{repulsion}                  & 1,650 cp \\
\spell{shadow walk}                & 1,650 cp \\
\spell{shining sands}              & 1,650 cp \\
\spell{shroud of darkness}         & 1,650 cp \\
\spell{stone to flesh}             & 1,650 cp \\
\spell{summon monster VI}          & 1,650 cp \\
\spell{summon Tyr-storm}           & 1,650 cp \\
\spell{symbol of fear}             & 2,650 cp \\
\spell{symbol of persuasion}       & 6,650 cp \\
\spell{transformation}             & 1,950 cp \\
\spell{true seeing}                & 1,900 cp \\
\spell{undeath to death}           & 2,150 cp \\
\spell{veil}                       & 1,650 cp \\
\spell{wall of iron}               & 6,650 cp \\

\multicolumn{2}{c}{\tableheader 7th-Level Arcane Spells}\\
\cmidrule[0pt]{1-2}
\tableheader Spell                 & \tableheader Market Price\\
\spell{banishment}                   & 2,275 cp \\
\spell{control undead}               & 2,275 cp \\
\spell{control weather}              & 2,275 cp \\
\spell{delayed blast fireball}       & 2,275 cp \\
\spell{ethereal jaunt}               & 2,275 cp \\
\spell{finger of death}              & 2,275 cp \\
\spell{forcecage}                    & 3,775 cp \\
\spell{grasping hand}                & 2,275 cp \\
\spell{Gray beckoning}               & 2,275 cp \\
\spell{greater arcane sight}         & 2,275 cp \\
\spell{greater scrying}              & 2,275 cp \\
\spell{greater shadow conjuration}   & 2,275 cp \\
\spell{greater teleport}             & 2,275 cp \\
\spell{infestation}                  & 2,275 cp \\
\spell{insanity}                     & 2,275 cp \\
\spell{instant summons}              & 3,275 cp \\
\spell{limited wish}                 & 3,775 cp\footnotemark[3] \\
\spell{mage's magnificent mansion}   & 2,275 cp \\
\spell{mage's sword}                 & 2,275 cp \\
\spell{mass hold person}             & 2,275 cp \\
\spell{mass invisibility}            & 2,275 cp \\
\spell{phase door}                   & 2,275 cp \\
\spell{plane shift}                  & 2,275 cp \\
\spell{power word blind}             & 2,275 cp \\
\spell{prismatic spray}              & 2,275 cp \\
\spell{project image}                & 2,280 cp \\
\spell{reverse gravity}              & 2,275 cp \\
\spell{sequester}                    & 2,275 cp \\
\spell{simulacrum}                   & 7,275 cp\footnotemark[4] \\
\spell{spell turning}                & 2,275 cp \\
\spell{statue}                       & 2,275 cp \\
}


\Table{Arcane Spells VI}{Xr{15mm}}{
\multicolumn{2}{c}{\tableheader 7th-Level Arcane Spells}\\
\spell{symbol of stunning}           & 7,275 cp \\
\spell{summon monster VII}           & 2,275 cp \\
\spell{symbol of weakness}           & 7,275 cp \\
\spell{teleport object}              & 2,275 cp \\
\spell{vision}                       & 2,775 cp \\
\spell{waves of exhaustion}          & 2,275 cp \\
}
