\subsectionA{Staffs}
A staff is a long shaft of wood that stores several spells. Unlike wands, which can contain a wide variety of spells, each staff is of a certain kind and holds specific spells. A staff has 50 charges when created.

\textbf{Physical Description:} A typical staff is 1.2 meter to 2.1 meters long and 5 centimeters to 7 centimeters thick, weighing about 2.5 kilograms. Most staffs are wood, but a rare few are bone, metal, or even glass. (These are extremely exotic.) Staffs often have a gem or some device at their tip or are shod in metal at one or both ends. Staffs are often decorated with carvings or runes. A typical staff is like a walking stick, quarterstaff, or cudgel. It has AC 7, 10 hit points, hardness 5, and a break DC of 24.

\textbf{Activation:} Staffs use the spell trigger activation method, so casting a spell from a staff is usually a standard action that doesn't provoke attacks of opportunity. (If the spell being cast, however, has a longer casting time than 1 standard action, it takes that long to cast the spell from a staff.) To activate a staff, a character must hold it forth in at least one hand (or whatever passes for a hand, for nonhumanoid creatures).

\Table{Staffs}{Xr{15mm}}{
\tableheader Staff & \tableheader Market Price\\
Charming         & 16,500 cp \\
Fire             & 28,500 cp \\
Swarming insects & 24,750 cp \\
Healing          & 27,750 cp \\
Size alteration  & 29,000 cp \\
Trickster        & 33,200 cp \\
Concurrence      & 39,000 cp \\
Illumination     & 48,250 cp \\
Desert Travel    & 52,000 cp \\
Pain             & 54,750 cp \\
Frost            & 56,250 cp \\
Defense          & 58,250 cp \\
Abjuration       & 65,000 cp \\
Conjuration      & 65,000 cp \\
Enchantment      & 65,000 cp \\
Evocation        & 65,000 cp \\
Illusion         & 65,000 cp \\
Necromancy       & 65,000 cp \\
Transmutation    & 65,000 cp \\
Divination       & 73,500 cp \\
Earth and stone  & 80,500 cp \\
Woodlands        & 101,250 cp \\
Life             & 155,750 cp \\
Passage          & 170,500 cp \\
Power            & 211,000 cp \\
}

\subsubsection{Staff Descriptions}
Staffs use the wielder's ability score and relevant feats to set the DC for saves against their spells. Unlike with other sorts of magic items, the wielder can use his caster level when activating the power of a staff if it's higher than the caster level of the staff.

This means that staffs are far more potent in the hands of a powerful spellcaster. Because they use the wielder's ability score to set the save DC for the spell, spells from a staff are often harder to resist than ones from other magic items, which use the minimum ability score required to cast the spell. Not only are aspects of the spell dependant on caster level (range, duration, and so on) potentially higher, but spells from a staff are harder to dispel and have a better chance of overcoming a target's spell resistance.

Furthermore, a staff can hold a spell of any level, unlike a wand, which is limited to spells of 4th level or lower. The minimum caster level of a staff is 8th. Standard staffs are described below.

\textbf{Abjuration:} Usually carved from the heartwood of an ancient oak or other large tree, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{shield} (1 charge)
\item \spell{resist energy} (1 charge)
\item \spell{dispel magic} (1 charge)
\item \spell{lesser globe of invulnerability} (2 charges)
\item \spell{dismissal} (2 charges)
\item \spell{repulsion} (3 charges)
\end{itemize*}

Strong abjuration; CL 13th; \feat{Craft Staff}, \spell{dismissal}, \spell{dispel magic}, \spell{lesser globe of invulnerability}, \spell{resist energy}, \spell{repulsion}, \spell{shield}; Price 65,000 cp.

\textbf{Charming:} Made of twisting wood ornately shaped and carved, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{charm person} (1 charge)
\item \spell{charm monster} (2 charges)
\end{itemize*}

Moderate enchantment; CL 8th; \feat{Craft Staff}, \spell{charm person}, \spell{charm monster}; Price 16,500 cp.

\textbf{Concurrence:} Made from the fine grained, straight wood of a kaor tree that has been blessed by a druid, this staff allows the use of the following spells:
\begin{itemize*}
\item \spell{sleep} (1 charge)
\item \spell{hold person} (1 charge)
\item \spell{tiny hut} (1 charge)
\item \spell{resilient sphere} (2 charges)
\item \spell{polymorph} (2 charges)
\end{itemize*}

Moderate varied; CL 8th; \feat{Craft Staff}, \spell{hold person}, \spell{polymorph}, \spell{resilient sphere}, \spell{sleep}, \spell{tiny hut}; Price 39,000 cp.

\textbf{Conjuration:} This staff is usually made of ash or walnut and bears ornate carvings of many different kinds of creatures. It allows use of the following spells:
\begin{itemize*}
\item \spell{unseen servant} (1 charge)
\item \spell{summon swarm} (1 charge)
\item \spell{stinking cloud} (1 charge)
\item \spell{minor creation} (2 charges)
\item \spell{cloudkill} (2 charges)
\item \spell{summon monster VI} (3 charges)
\end{itemize*}

Strong conjuration; CL 13th; \feat{Craft Staff}, \spell{cloudkill}, \spell{stinking cloud}, \spell{summon monster VI}, \spell{summon swarm}, \spell{unseen servant}; Price 65,000 cp.

\textbf{Defense:} The staff of defense is a simple-looking staff that throbs with power when held defensively. It allows use of the following spells:
\begin{itemize*}
\item \spell{shield} (1 charge)
\item \spell{shield of faith} (1 charge)
\item \spell{shield other} (1 charge)
\item \spell{shield of law} (3 charges)
\end{itemize*}

Strong abjuration; CL 15th; \feat{Craft Staff}, \spell{shield}, \spell{shield of faith}, \spell{shield of law}, \spell{shield other}, creator must be lawful; Price 58,250 cp.

\textbf{Desert Travel:} Crafted from the wood of a wanderer's staff, a straight and tall species of trees that grows in the Ringing Mountains, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{cooling canopy} (1 charge)
\item \spell{create element} (water) (1 charge)
\item \spell{purify food and drink} (1 charge)
\item \spell{summon nature's ally VI} (water elemental or rain paraelemental beast only) (2 charges)
\end{itemize*}

The staff may be used as a weapon, functioning as a \emph{+2 quarterstaff}. The \emph{staff of desert travel} also allows its wielder to \spell{detect animals or plants} and \spell{know direction} at will, with no charge cost. These two attributes continue to function even after all the staff's charges are expended.

Moderate varied; CL 13th; \feat{Craft Staff}, \feat{Craft Magic Arms and Armor}, \spell{create element}, \spell{cooling canopy}, \spell{detect animals or plants}, \spell{know direction}, \spell{purify food and drink}, \spell{summon nature's ally VI}; Price 52,000 cp.

\textbf{Divination:} Made from a supple length of willow, often with a forked tip, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{detect secret doors} (1 charge)
\item \spell{locate object} (1 charge)
\item \spell{tongues} (1 charge)
\item \spell{locate creature} (2 charges)
\item \spell{prying eyes} (2 charges)
\item \spell{true seeing} (3 charges)
\end{itemize*}

Strong divination; CL 13th; \feat{Craft Staff}, \spell{detect secret doors}, \spell{locate creature}, \spell{locate object}, \spell{prying eyes}, \spell{tongues}, \spell{true seeing}; Price 73,500 cp.

\textbf{Earth and Stone:} This staff is topped with a fist-sized emerald that gleams with smoldering power. It allows the use of the following spells:
\begin{itemize*}
\item \spell{passwall} (1 charge)
\item \spell{move earth} (1 charge)
\end{itemize*}

Moderate transmutation; CL 11th; \feat{Craft Staff}, \spell{move earth}, \spell{passwall}; Price 80,500 cp.

\textbf{Enchantment:} Often made from applewood and topped with a clear crystal, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{sleep} (1 charge)
\item \spell{hideous laughter} (1 charge)
\item \spell{suggestion} (1 charge)
\item \spell{crushing despair} (2 charges)
\item \spell{mind fog} (2 charges)
\item \spell{mass suggestion} (3 charges)
\end{itemize*}

Strong enchantment; CL 13th; \feat{Craft Staff}, \spell{crushing despair}, \spell{mass suggestion}, \spell{mind fog}, \spell{sleep}, \spell{suggestion}, \spell{hideous laughter}; Price 65,000 cp.

\textbf{Evocation:} Usually very smooth and carved from hickory, willow, or yew, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{magic missile} (1 charge)
\item \spell{shatter} (1 charge)
\item \spell{fireball} (1 charge)
\item \spell{ice storm} (2 charges)
\item \spell{wall of force} (2 charges)
\item \spell{chain lightning} (3 charges)
\end{itemize*}

Strong evocation; CL 13th; \feat{Craft Staff}, \spell{chain lightning}, \spell{fireball}, \spell{ice storm}, \spell{magic missile}, \spell{shatter}, \spell{wall of force}; Price 65,000 cp.

\textbf{Fire:} Crafted from bronzewood with brass bindings, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{burning hands} (1 charge)
\item \spell{fireball} (1 charge)
\item \spell{wall of fire} (2 charges)
\end{itemize*}

Moderate evocation; CL 8th; \feat{Craft Staff}, \spell{burning hands}, \spell{fireball}, \spell{wall of fire}; Price 28,500 cp.

\textbf{Frost:} Tipped on either end with a glistening diamond, this rune-covered staff allows use of the following spells:
\begin{itemize*}
\item \spell{ice storm} (1 charge)
\item \spell{wall of ice} (1 charge)
\item \spell{cone of cold} (2 charge)
\end{itemize*}

Moderate evocation; CL 10th; \feat{Craft Staff}, \spell{cone of cold}, \spell{ice storm}, \spell{wall of ice}; Price 56,250 cp.

\textbf{Healing:} This white ash staff, with inlaid silver runes, allows use of the following spells:
\begin{itemize*}
\item \spell{lesser restoration} (1 charge)
\item \spell{cure serious wounds} (1 charge)
\item \spell{remove blindness/deafness} (2 charges)
\item \spell{remove disease} (3 charges)
\end{itemize*}

Moderate conjuration; CL 8th; \feat{Craft Staff}, \spell{cure serious wounds}, \spell{lesser restoration}, \spell{remove blindness/deafness}, \spell{remove disease}; Price 27,750 cp.

\textbf{Illusion:} This staff is made from ebony or other dark wood and carved into an intricately twisted, fluted, or spiral shape. It allows use of the following spells:
\begin{itemize*}
\item \spell{disguise self} (1 charge)
\item \spell{mirror image} (1 charge)
\item \spell{major image} (1 charge)
\item \spell{rainbow pattern} (2 charges)
\item \spell{persistent image} (2 charges)
\item \spell{mislead} (3 charges)
\end{itemize*}

Strong illusion; CL 13th; \feat{Craft Staff}, \spell{disguise self}, \spell{major image}, \spell{mirror image}, \spell{persistent image}, \spell{project image}, \spell{rainbow pattern}; Price 65,000 cp.

\textbf{Illumination:} This staff is usually sheathed in silver and decorated with sunbursts. It allows use of the following spells:
\begin{itemize*}
\item \spell{dancing lights} (1 charge)
\item \spell{flare} (1 charge)
\item \spell{daylight} (2 charges)
\item \spell{sunburst} (3 charges)
\end{itemize*}

Strong evocation; CL 15th; \feat{Craft Staff}, \spell{dancing lights}, \spell{daylight}, \spell{flare}, \spell{sunburst}; Price 48,250 cp.

\textbf{Life:} Made of thick oak shod in gold, this staff allows use of the following spells:
\begin{itemize*}
\item \spell{heal} (1 charge)
\item \spell{resurrection} (5 charges)
\end{itemize*}

Moderate conjuration; CL 13th; \feat{Craft Staff}, \spell{heal}, \spell{resurrection}; Price 155,750 cp.

\textbf{Necromancy:} This staff is made from ebony or other dark wood and carved with the images of bones and skulls. It allows use of the following spells:
\begin{itemize*}
\item \spell{cause fear} (1 charge)
\item \spell{ghoul touch} (1 charge)
\item \spell{halt undead} (1 charge)
\item \spell{enervation} (2 charges)
\item \spell{waves of fatigue} (2 charges)
\item \spell{circle of death} (3 charges)
\end{itemize*}

Strong necromancy; CL 13th; \feat{Craft Staff}, \spell{cause fear}, \spell{circle of death}, \spell{enervation}, \spell{ghoul touch}, \spell{halt undead}, \spell{waves of fatigue}; Price 65,000 cp.

\textbf{Pain:} This weapon is typically used by the templars of Athas to motivate slaves under their control by inflict pain upon them. It allows use of the following spells:
\begin{itemize*}
\item \spell{hold person} (1 charge)
\item \spell{image of the sorcerer-king} (1 charge)
\item \spell{psychic turmoil} (1 charge)
\item \spell{greater psychic turmoil} (2 charges)
\end{itemize*}

The wielder of a \emph{staff of pain} can channel power points to it to inflict pain to any living creature he touches with the staff (by making a melee touch attack). This attack deals 2d6 points of nonlethal damage for each 2 power points spent, up to a maximum of 14d6 points of nonlethal damage by spending 14 power points. The wielder cannot spend more power points than his manifester level. Each use of this touch consumes 3 charges of the staff.

Strong varied; CL 14th; \feat{Craft Staff}, \spell{dweomer of transference}, \spell{greater psychic turmoil}, \spell{hold person}, \spell{image of the sorcerer-king}, \spell{inflict critical wounds}, \spell{psychic turmoil}; Price 54,750 cp.

\textbf{Passage:} This potent item allows use of the following spells:
\begin{itemize*}
\item \spell{dimension door} (1 charge)
\item \spell{passwall} (1 charge)
\item \spell{phase door} (2 charges)
\item \spell{greater teleport} (2 charges)
\item \spell{astral projection} (2 charges)
\end{itemize*}

Strong varied; CL 17th; \feat{Craft Staff}, \spell{astral projection}, \spell{dimension door}, \spell{greater teleport}, \spell{passwall}, \spell{phase door}; Price 170,500 cp.

\textbf{Power:} The \emph{staff of power} is a very potent magic item, with offensive and defensive abilities. It is usually topped with a glistening gem, its shaft straight and smooth. It has the following powers:
\begin{itemize*}
\item \spell{magic missile} (1 charge)
\item \spell{ray of enfeeblement} (heightened to 5th level) (1 charge)
\item \spell{continual flame} (1 charge)
\item \spell{levitate} (1 charge)
\item \spell{lightning bolt} (heightened to 5th level) (1 charge)
\item \spell{fireball} (heightened to 5th level) (1 charge)
\item \spell{cone of cold} (2 charges)
\item \spell{hold monster} (2 charges)
\item \spell{wall of force} (in a 3-m-diameter hemisphere around the caster only) (2 charges)
\item \spell{globe of invulnerability} (2 charges)
\end{itemize*}

The wielder of a \emph{staff of power} gains a +2 luck bonus to AC and saving throws. The staff is also a \emph{+2 quarterstaff}, and its wielder may use it to smite opponents. If 1 charge is expended (as a free action), the staff causes double damage ($\times$3 on a critical hit) for 1 round.

A \emph{staff of power} can be used for a retributive strike, requiring it to be broken by its wielder. (If this breaking of the staff is purposeful and declared by the wielder, it can be performed as a standard action that does not require the wielder to make a Strength check.) All charges currently in the staff are instantly released in a 9-meter radius. All within 2 squares of the broken staff take points of damage equal to 8 $\times$ the number of charges in the staff, those 3 or 4 squares away take 6 $\times$ the number of charges in damage, and those 5 or 6 squares distant take 4 $\times$ the number of charges in damage. All those affected can make DC 17 Reflex saves to reduce the damage by half.

The character breaking the staff has a 50\% chance of traveling to another plane of existence, but if he does not, the explosive release of spell energy destroys him. Only certain items, including the staff of the magi and the \emph{staff of power}, are capable of being used for a retributive strike.

After all charges are used up from the staff, it remains a \emph{+2 quarterstaff}. (Once empty of charges, it cannot be used for a retributive strike.)

Strong varied; CL 15th; \feat{Craft Staff}, \feat{Craft Magic Arms and Armor}, \spell{magic missile}, heightened \spell{ray of enfeeblement}, \spell{continual flame}, \spell{levitate}, heightened \spell{fireball}, heightened \spell{lightning bolt}, \spell{cone of cold}, \spell{hold monster}, \spell{wall of force}, \spell{globe of invulnerability}; Price 211,000 cp.

\textbf{Size Alteration:} Stout and sturdy, this staff of dark wood allows use of the following spells:
\begin{itemize*}
\item \spell{enlarge person} (1 charge)
\item \spell{reduce person} (1 charge)
\item \spell{shrink item} (1 charge)
\item \spell{mass enlarge person} (1 charge)
\item \spell{mass reduce person} (1 charge)
\end{itemize*}

Faint conjuration; CL 8th; \feat{Craft Staff}, \spell{enlarge person}, \spell{mass enlarge person}, \spell{reduce person}, \spell{mass reduce person}, \spell{shrink item}; Price 29,000 cp.

\textbf{Swarming Insects:} Made of twisted dark wood with dark spots resembling crawling insects (which occasionally seem to move), this staff allows use of the following spells:
\begin{itemize*}
\item \spell{summon swarm} (1 charge)
\item \spell{insect plague} (3 charges)
\end{itemize*}

Moderate conjuration; CL 9th; \feat{Craft Staff}, \spell{insect plague}, \spell{summon swarm}; Price 24,750 cp.

\textbf{Transmutation:} This staff is generally carved from or decorated with petrified wood and allows use of the following spells:
\begin{itemize*}
\item \spell{expeditious retreat} (1 charge)
\item \spell{alter self} (1 charge)
\item \spell{blink} (1 charge)
\item \spell{polymorph} (2 charges)
\item \spell{baleful polymorph} (2 charges)
\item \spell{disintegrate} (3 charges)
\end{itemize*}

Strong transmutation; CL 13th; \feat{Craft Staff}, \spell{alter self}, \spell{baleful polymorph}, \spell{blink}, \spell{disintegrate}, \spell{expeditious retreat}, \spell{polymorph}; Price 65,000 cp.

\textbf{Trickster:} Mostly seen in the hands of elven wizards, this one-meter long bone staff is crafted from drake ivory and covered with elaborate carvings depicting laughing and smiling male and female elven faces intertwined with smaller, full-body reliefs of elves dancing, running, or embracing in positions of physical pleasure. The staff is adorned with small, embedded obsidian spheres that spiral around its haft. Legend has it that the first of these items was crafted by the elven defiler and trickster Daaku, renowned for his audacious and daring schemes and exploits, sometime before his mysterious disappearance after making enemies of the Shadows tribe.

This staff allows use of the following spells:
\begin{itemize*}
\item \spell{magic aura} (1 charge)
\item \spell{disguise self} (1 charge)
\item \spell{expeditious retreat} (1 charge)
\item \spell{greater invisibility} (2 charges)
\item \spell{dimension door} (2 charges)
\end{itemize*}

This staff also grants its wielder a +5 bonus to \skill{Bluff} checks and the ability to use \spell{ghost sound}, as a spell-like ability at caster level 9th, at will. These two attributes continue to function even after all the charges have been expended.

Moderate varied; CL 9th; \feat{Craft Staff}, \spell{dimension door}, \spell{disguise self}, \spell{expeditious retreat}, \spell{ghost sound}, \spell{greater invisibility}, \spell{magic aura}; Price 33,200 cp.

\textbf{Woodlands:} Appearing to have grown naturally into its shape, this oak, ash, or yew staff allows use of the following spells:
\begin{itemize*}
\item \spell{charm animal} (1 charge)
\item \spell{speak with animals} (1 charge)
\item \spell{barkskin} (2 charges)
\item \spell{wall of thorns} (3 charges)
\item \spell{summon nature's ally VI} (3 charges)
\item \spell{animate plants} (4 charges)
\end{itemize*}

The staff may be used as a weapon, functioning as a \emph{+2 quarterstaff}. The staff of the woodlands also allows its wielder to \spell{pass without trace} at will, with no charge cost. These two attributes continue to function after all the charges are expended.

Moderate varied; CL 13th; \feat{Craft Staff}, \feat{Craft Magic Arms and Armor}, \spell{animate plants}, \spell{barkskin}, \spell{charm animal}, \spell{pass without trace}, \spell{speak with animals}, \spell{summon nature's ally VI}, \spell{wall of thorns}; Price 101,250 cp. 
