\section{The Athasian Cosmology}
\begin{figure}[t!]
\centering
\begin{tikzpicture}[blend mode=multiply, baseline=0]
\contourlength{.5mm}
\begin{scope}[blend group=normal, scale=1.25, every node/.style={scale=1.25}, local bounding box=scope1]
\draw[line width=0.2mm, color=black, draw, fill=black!20] ( 2.65, 2.65) arc (45:135:3.75) -- (0,0) --cycle;
\draw[line width=0.2mm, color=black, draw, fill=black!20] (-2.65,-2.65) arc (225:315:3.75) -- (0,0) --cycle;
\draw[line width=0.2mm, color=black, draw,fill=white] ( 2.12,  2.12) arc(45:135:3) -- (0,0) --cycle;
\draw[line width=0.2mm, color=black, draw,fill=white] (-2.12, -2.12) arc(225:315:3) -- (0,0) --cycle;
\draw[line width=0.2mm, color=black, pattern=crosshatch dots, pattern color=black!20]  ( 2.12,  2.12) arc(45:135:3) -- (0,0) --cycle;
\draw[line width=0.2mm, color=black, pattern=north west lines, pattern color=black!20] (-2.12, -2.12) arc(225:315:3) -- (0,0) --cycle;
\node[line width=0.2mm, color=black, circle, draw, fill=black!40, minimum size=45mm, inner sep=0pt, outer sep=0pt] at (0,0) {};
\node[color=richblack] at (0,-1.5) {\tableheader The Gray};
\node[line width=0.2mm, color=black, circle, draw, fill=white, minimum size=30mm, inner sep=0pt, outer sep=0pt] at (0,.6) {};
% \draw[color=black, postaction={decorate,decoration={text along path,text align=center,text={|\tableheader|Material Plane}}}] ( -1.03, 0) arc (210:330:1.2);
\node[color=richblack] at (0, -0.3) {\tableheader Material Plane};
\node[line width=0.2mm, color=black, circle, draw, fill=black, minimum size=14mm, inner sep=0pt, outer sep=0pt] at (0,.6) {\color{white}\tableheader The Black};
\node[color=richblack] at (0, 2.5) {\tableheader \contour{white}{Ethereal Plane}};
\node[color=richblack] at (0,-2.55) {\tableheader \contour{white}{Astral Plane}};
\node[color=richblack] at (0, 3.3) {\tableheader Inner Planes};
\node[color=richblack] at (0,-3.3) {\tableheader Outer Planes};
\end{scope}
\end{tikzpicture}
\end{figure}

The Athasian cosmology is structured as follows.
\begin{itemize*}
\item The Material Plane at its center.
\item The Gray is coexistent with the Material Plane, the Ethereal Plane, and the Astral Plane. It serves a buffer that inhibits planar travel to and from the Athasian Material Plane. This buffer is larger in the direction of the Astral Plane (and the Outer Planes) than in the direction of the Ethereal Plane (and the Inner Planes).
\item The Black is coexistent with the Material Plane.
% \item The Hollow is coterminous with the Black, and as far away from the Material Plane as possible.
\item The Ethereal Plane is coexistent with the Inner Planes and the Gray.
\item The ten Inner Planes are surrounded by the Ethereal Plane. They are coexistent with the Ethereal Plane, and coterminous with each other. Each of the Inner Planes has the appropriate elemental trait. Elemental conduits link the Inner Planes and the Material Plane allowing the clerics to gather their divine energy.
\item The Astral Plane is coexistent with the Outer Planes and the Gray. Color pools connect the Astral Plane to each of the Outer Planes and the Gray.
% \item The Outer Planes are arranged in a great wheel. Each Outer Plane is coterminous to the planes on either side of it but separate from the other Outer Planes. The exception is the \emph{Concordant Domain of the Outlands}, which is coterminous to every other Outer Plane and thus serves as a central hub for dealings between outsiders.

% The Outer Planes are coexistent with the Astral Plane. They are separate from the Ethereal Plane, so certain spells (\spell{ethereal jaunt}, for example) aren't available to a caster on the Outer Planes. Each Outer Planes is made up of related layers, and the most common access to an Outer Plane is through the top layer of each plane. The good-aligned planes, also called the celestial planes or the upper planes, are linked by the path of the \emph{River Oceanus}. The evil-aligned planes, also called the infernal planes or the lower planes, are linked by the path of the \emph{River Styx}.

\item The Outer Planes are coexistent with the Astral Plane. They are separate from the Ethereal Plane, so certain spells (\spell{ethereal jaunt}, for example) aren't available to a caster on the Outer Planes. They are thoroughly explained in the \emph{Manual of the Planes}.
\end{itemize*}

A large number of finite demiplanes connect all over the place. Individual conduits, freestanding portals, and vortices are also common.

\subsection{Arcane Spells in Other Planes}
Most planes do not have any plant life from which Athasian wizards draw their magic. In those planes, magic items still function normally, as the energy powering the effect is contained within the item.

Planes with plant life that allow normal arcane casting:
\begin{itemize*}
\item \textbf{The Material Plane:} Actual plant life can be used to cast spells.
\item \textbf{The Black:} Shadows of plant life can be used to gather energy for spells.
\item \textbf{The Elemental Plane of Earth:} Exotic plants living underground can be used to draw magic.
\end{itemize*}

\subsubsection{Arcane Spells in the Astral Plane}
There are two ways of entering the Astral Plane: creating a projection yourself while on another plane, or moving your physical reality there. The manner of arrival will impact a wizard's ability to cast spells in the Astral Plane.

\textbf{Astral Projection:} Using the \spell{astral projection} spell or similar spell or power may allow the wizard to gather energy from the feeling of casting that spell---not the reality of gathering energy. That happens at the plane the wizard is in. If the wizard is \spellref{astral projection}{astral projecting} from any plane with plant life, they will use that location's terrain type modifiers.

\textbf{Physical Transportation:} Physically entering the plane can be accomplished via spells, such as the \spell{plane shift} spell, or via the color pools linking the Outer Planes to the Astral Plane. This planar travel does not allow casting arcane spells in the Astral Plane, as the plane does not have the plant life required for it. It is called the Silver Void for a reason.


\subsectionA{Prime Material Plane}
The physical world, where Athas is. The Prime Material Plane is the most familiar place for characters in {\tableheader Dark Sun}---most never leave it. The few outsiders on the Material Plane tend to be uncomfortable, since they have a physical reality and the Material Plane does not have any alignment trait. Elementals are quite at home in Athas, however, as they find plenty of locations to thrive (even water elementals).

\textbf{Planar Interference:} The Gray acts as a metaphysical interference for planar travelers getting into or out of Athas. Whenever a casting spell or manifesting a power that reaches planes other than the Gray, the character must make a planar interference check with a d\% (see \tabref{Planar Interference Check}) adding their caster level or manifester level to the result. A character must also make this check when trying to reach the Prime Material Plane from planes other than the Gray.

\Table{Planar Interference Check}{lCC}{
& \multicolumn{2}{c}{\tableheader Target Plane}\\
\cmidrule[.5pt]{2-3}
  \tableheader Result
& \tableheader Ethereal/Inner Plane
& \tableheader Astral/Outer Plane \\
Lost in the Gray & 01--08  & 01--15  \\
Failure          & 09--65  & 16--95  \\
Success          & 66--100 & 96--100 \\
}

\textit{Clerics and Planar Interference:} When clerics cast spells to reach their patron's plane of existence, they do not need to make a check. They also do not need to make this check when reaching the Prime Material Plane from their patron's plane. Elemental conduits guide them directly to their plane. They still need to make this check for any other plane, however.

\subsubsection{Prime Material Plane Traits}
\begin{itemize*}
\item \textbf{Normal Gravity.}
\item \textbf{Normal Time.}
\item \textbf{Infinite Size.}
\item \textbf{No Elemental or Energy Traits.}
\item \textbf{Mildly neutral-aligned.}
\item \textbf{Impeded Magic and Psionics:} Spells and powers that provide access or travel to other planes are much more difficult, since the Gray acts as an interference zone for those effects. The only exception being a cleric reaching out to or from their patron's Inner Plane.
\item \textbf{Alterable Morphic.}
\end{itemize*}
