\section{How Planes Interact}

\textbf{Separate Planes:} Two planes that are separate do not overlap or directly connect to each other. They are like planets in different orbits. The only way to get from one separate plane to the other is to go through a third plane.

\textbf{Coterminous Planes:} Planes that touch at specific points are coterminous. Where they touch, a connection exists, and travelers can leave one reality behind and enter the other.

\textbf{Coexistent Planes:} If a link between two planes can be created at any point, the two planes are coexistent. These planes overlap each other completely. A coexistent plane can be reached from anywhere on the plane it overlaps. When moving on a coexistent plane, it is often possible to see into or interact with the plane it coexists with.

\subsection{Layered Planes}
Infinities may be broken into smaller infinities, and planes into smaller, related planes. These layers are effectively separate planes of existence, and each layer can have its own planar traits. Layers are connected to each other through a variety of planar gates, natural vortices, paths, and shifting borders.

Access to a layered plane from elsewhere usually happens on a specific layer: the first layer of the plane, which can be either the top layer or the bottom layer, depending on the specific plane. Most fixed access points (such as portals and natural vortices) reach this layer, which makes it the gateway for other layers of the plane. The \spell{plane shift} spell also deposits the spellcaster on the first layer of the plane.
