\section{Outer Planes}
If the Inner Planes are the raw matter and energy that makes up the multiverse, the Outer Planes are the direction, thought and purpose for such construction. 
These are the planes where the ancient gods once thrived. The Outer Planes are so far from the Prime Material Plane that any of the existing gods cannot interact with Athas anymore. The bigger buffer the Gray has between Athas and the Astral Plane is enough to impede the formation of conduits connecting the Prime Material Plane to the Outer Planes.

% Accordingly, many sages refer to the Outer Planes as divine planes, spiritual planes, or godly planes, for the Outer Planes are best known as the homes of deities. Gods may live elsewhere, but they thrive on the Outer Planes. Other creatures inhabit the Outer Planes too, some that are the servants of deities and others that fiercely guard their independence.

To the novice traveler, the Outer Planes seem more hospitable and familiar to natives of the Material Plane than either the Transitive Planes or the Inner Planes. The notion is deceptive. While the landscape might look like that of the Material Plane, it can change at the whim of the powerful forces that live on the Outer Planes. The desires of the godly forces that dwell on these planes can remake them completely, effectively erasing and rebuilding existence itself to better fulfill their own needs.

\textbf{Traveling:} Each of the Outer Planes borders two others, forming the Great Wheel that encircles the Gray. It is possible to move between the Outer Planes of the Great Wheel through the Astral or through physical movement as one plane gives way to another near the coterminous border regions. These borders are loosely defined and always in a state of flux, so creatures sometimes move between planes without intending to.

\subsubsection{Godhood}
The Outer Planes are also the homes of powerful deities. These deities may exist on other planes, but the Outer Planes are ideal for them. The Outer Planes are divinely morphic, so deities can alter the landscape itself within a limited area. And deities benefit from inhabiting planes that match their alignment.

The basic categories of godhood are:

\textbf{Quasi-Deity/Hero-Deity:} Quasi-deities and hero-deities are only slightly ``divine,'' but they still possess a portion of deity-level power or attract worshipers. They lack the ability to manipulate the area around them. As a result, they tend to wander or occupy small realms on the Outer Planes that are constructed with brute labor, not divine power.

\textbf{Demideity:} This is the weakest category of fully divine deities. Indeed, some demideities were once legendary mortals who were rewarded with (or seized for themselves) the mantle of godhood. They are the most mortal-seeming of the deities. They also lack the power to manipulate the divinely morphic area around them. They also wander, construct their homes conventionally, or rely on more powerful deities to manipulate the planar landscape for them.

\textbf{Lesser Deity:} The deities in this category have several domains they grant their clerics and an area of responsibility called a portfolio that they oversee. Lesser deities tend to handle relatively ``small'' matters, and they often work for and with more powerful deities. They can begin to alter the Outer Plane where they live, changing how travelers reach their realms. Within a two-kilometer radius, a lesser deity can determine the nature of any planar connections. The deity can decide, for example, whether the area can be accessed from the Astral Plane. In addition, a lesser deity can mandate that planar portals only appear at a specific location and that creatures cannot be summoned from within the area.

\textbf{Intermediate Deity:} These deities are more powerful than the lesser deities and command more important portfolios. can make more dramatic and far-reaching effects. They can affect everything within a fifteen-kilometer radius just as a lesser deity can, plus an intermediate deity can apply the enhanced magic or impeded magic trait to up to four groups (selected by school, domain, or descriptor) of spells.

Many deities apply the enhanced magic trait to their domain spells, making them maximized (as the \feat{Maximize Spell} feat) within the boundaries of their realm. The impeded magic trait doesn't affect the intermediate deity's spells and spell-like abilities, but the deity can take advantage of enhanced magic within the realm.

In addition, the intermediate deity can erect buildings as desired and alter terrain within ten miles to become any terrain type found on the Material Plane.

\textbf{Greater Deity:} These are the most powerful deities that adventurers encounter. They have the most important portfolios and often have other deities reporting to them. Some lead entire groups of deities (called pantheons). A greater deity affects everything just as an intermediate deity does, but out to a two-hundred-kilometer radius. Within this area, the greater deity can also do anyone of the following:

\begin{itemize*}
\item Change or apply an elemental or energy trait of the area.
\item Change or apply a time trait within the area.
\item Change or apply a gravity trait within the area.
\item Apply the limited magic trait against a particular school, domain, or spell descriptor within the area. The greater deity's own spells and spell-like abilities are not limited by these restrictions.
\end{itemize*}

Using power to divinely morph a plane in such dramatic fashion is time-consuming and involves a great deal of the deity's divine power. As a result, a greater deity often uses major trait changes to cement his or her hold over a realm. Such places are not given up lightly.

\input{subsections/planes/outer-planes/ysgard.tex}
\input{subsections/planes/outer-planes/limbo.tex}
\input{subsections/planes/outer-planes/pandemonium.tex}
\input{subsections/planes/outer-planes/abyss.tex}
\input{subsections/planes/outer-planes/carceri.tex}
\input{subsections/planes/outer-planes/hades.tex}
% \input{subsections/planes/outer-planes/gehenna.tex}
% \input{subsections/planes/outer-planes/baator.tex}
% \input{subsections/planes/outer-planes/acheron.tex}
% \input{subsections/planes/outer-planes/mechanus.tex}
% \input{subsections/planes/outer-planes/arcadia.tex}
% \input{subsections/planes/outer-planes/celestia.tex}
% \input{subsections/planes/outer-planes/bytopia.tex}
% \input{subsections/planes/outer-planes/elysium.tex}
% \input{subsections/planes/outer-planes/beastlands.tex}
% \input{subsections/planes/outer-planes/arborea.tex}
% \input{subsections/planes/outer-planes/outlands.tex}
