\section{What Is A Plane?}
The planes of existence are different realities with interwoven connections. Except for rare linking points, each plane is effectively its own universe with its own natural laws.

The planes break down into a number of general types: the Material Plane, the Transitive Planes, the Inner Planes, the Outer Planes, and the demiplanes.

\textbf{Material Plane:} The Material Plane tends to be the most Earthlike of all planes and operates under the same set of natural laws that our own real world does. This is the default plane for most adventures.

\textbf{Transitive Planes:} These planes have one important common characteristic: Each is used to get from one place to another. The Astral Plane is a conduit to the Outer Planes, the Ethereal Plane connects to the Inner Planes, the Gray connects the Material Plane to the Astral and Ethereal planes, the Black serve as means of transportation within the Material Plane and to the Hollow. The Gray and the Black have the strongest regular interaction with the Material Plane and are often accessed by using various spells. All transitive planes have native inhabitants as well.

\textbf{Inner Planes:} These eight planes are manifestations of the basic building blocks of the universe. Each is made up of a single type of element that overwhelms all others. The natives of a particular Inner Plane are made of the same element as the plane itself.

\textbf{Outer Planes:} The deities live on the Outer Planes, as do creatures such as celestials, demons, and devils. Each of the Outer Planes has an alignment, representing a particular moral or ethical outlook, and the natives of each plane tend to behave in agreement with that plane's alignment. The Outer Planes are also the final resting place of souls from the Material Plane, whether that final rest takes the form of calm introspection or eternal damnation.

\textbf{Demiplanes:} This catch-all category covers all extradimensional spaces that function like planes but have measurable size and limited access. Other kinds of planes are theoretically infinite in size, but a demiplane might be only a few hundred feet across. The Hollow is one of such demiplanes.
