\subsectionA{Shadows}
\textbf{Area of Operation:} The whole Tablelands.

\textbf{Tribe Size:} Unknowable.

The Shadows is a mysterious, vast, and unthinkably old organization. They deal with all kinds of illegal activities, e.g. espionage, assassination, theft, and extortion, but also trade of contraband and forbidden items.

\subsubsection{Brief History}
The origins of the Shadows has not been exactly dated, but the oldest known reference comes from the ancient epic ``The Saga of the Fall of Kaday,'' in which the powerful defiler Kaday is undone by an ex-lover with the aid of black-clad elves. Each settlement has a tale about the tribe, always with a different role for the tribe. The only thing that stays the same in every tale is the exquisite sense of justice. Orders followed to the letter, even if the outcome is far out of proportion of the original request.

\subsubsection{The Shadows in Athas}
Every city in the Tablelands has a tale about the Shadows because every city has a Shadow cell, known as a ``talon,'' responsible for all activities in the vicinity. For outsiders, Shadows seem to only operate as thieves and spies, as their mercenary and spellcasting sections are often disguised as independent agents. But while this is their view, the reality is that the tribe has also traders. When Shadows need to operate within another elvish tribe domain, such as an elvish market, they usually do so by an agreement with the host tribe.

Hiring the Shadows to steal treasure can cost up to 100 gp, \emph{before} the job is done. After the job is done, the tribe demands up to \onehalf the value of the stolen treasure. The Shadows are relentless against cheaters, not only getting back the treasure but also stealing a ``compensation fee'' from the cheater.

Price for any job depends on the Shadows' sense of justice. It goes up for any target considered poor or innocent, and it goes down for rich targets. Their raiders are known to charge almost nothing for lucrative targets, while their merchants disfavor evil clients. But up to a point, as their spies can even take revenge if they feel the information is gained for evil purposes or to harm innocents.

\subsubsection{The Shadows Society}
The Shadows are no longer a single tribe or family, but a secret elvish society. They operate much like the Veiled Alliance, with a different cell in each city. They have a strict hierarchy with each cell having a leader, called ``talon-master,'' ruling over numerous sub-commanders, called ``shadow-masters''. Once per decade, all talon-masters meet in a secret location to elect the Grand Shadow Master, who leads the tribe for the next ten years. While each cell has autonomy, the Grand Master can remove any talon-master from office, so his edicts are usually followed.

While each city has a different internal organization, shadow-masters are usually divided between a mercenary, spellcasting, thieving, espionage, and merchant sections.
