\subsectionA{Silt Stalkers}
\textbf{Area of Operation:} Eastern side of the Ivory Triangle, extending to the shore.

\textbf{Tribe Size:} 850 members.

Silt Stalkers are a raiding tribe operating in the eastern coast of the Sea of Silt. They plunder small villages, outposts, and caravans. Since they started acting, all major houses stopped sending caravans east of the Windbreak Mountains.

\subsubsection{Brief History}
The Silt Stalkers started as a small raiding tribe, but they have quickly grown into a mighty force recognized by all major players in the Ivory Triangle. In the last months, the tribe's master defiler has taken interest in the ruins of Giustenal. She has been urging the tribe chief for more aggressive acts ever since she returned from the ruins.

\subsubsection{Silt Stalkers in Athas}
The tribe does not have allies. Everyone and everything within their area of operation is a potential target. Their main targets are gith and belgoi tribes, located in the Blackspine Mountains. Occasional raids are bound to slave villages and the few outposts in the region.

The merchant houses of Fyra, Inika, Shom, and Wavir are constantly harassed. The tribe periodically raids Fort Harbeth, Fort Inix, Outpost 19, Fort Fyra, and the Cromlin village. This caused House Shom to increase the number of troops in Cromlin.

The elves of the Sky Singer tribe are special targets to the Silt Stalkers, since the Sky Singers are preservers seeking the same treasures in Giustenal.

\subsubsection{Silt Stalkers Society}
Silt Stalkers are divided between three clans. Defilers and thieves are the members of the Fire Dagger clan, focusing in assassination and specialized skills. Fire Bow clan is focused in wilderness skills, with scouts and elemental fire singers. The Fire Sword clan is the tribe's vanguard, using elvish longswords as its name implies.

The tribe chief maintains his position with death-fights. This is the only tribal law that must be obeyed by everyone, even the chief. A refused challenge will result in lost honor, position, or even life. The only rules in a death-fight are: (i) the fight continues until one or both are dead; and (ii) death must be delivered by a physical elvish weapon. Magic and psionics can be used through out the fight, but not as the killing blow. Eevuu has been challenged three times, but still remains chief of the Silt Stalkers.
