\subsectionA{Silver Hands}
\textbf{Area of Operation:} Silver Spring.

\textbf{Tribe Size:} 100 members.

The most different of the elvish tribes, Silver Hands have settled down in a small oasis. Silver Spring is now an almost mandatory stopping point for travelers in the main trade route between Urik and Tyr. Stopping there will teach that the silver in their names comes from the coins they crave.

\subsubsection{Brief History}
Silver Hands were raiders first, roaming the Great Road that connects Urik to the south of the Tablelands. Upon reaching the oasis, the chief saw the opportunity to use the location to rob unaware travelers. As time passed by, the Silver Hands methods changed from the simple raids and thefts to ruling of the Silver Spring. They started to think more like other races, on how to better protect the tribe and their end goal, profit. As the tribe changed, so did the settlement---the simple camp turned into a mud-bricked fort, and now into an even bigger stone fort protects the oasis.

\subsubsection{Silver Hands in Athas}
Settled in the middle of the trade route between Tyr and Urik, the Silver Hands is seen as a necessary evil for the merchant houses. The settlement is now a fortified trading post with  caravans paying the price of two silver pieces per creature---person or animal. All able members of the tribe try to sell or trade any trinket for far more than it is worth, or collect minor fees for the privilege of resting within the tribe's fortified wall. Those who try to resupply in the compound's market find that everything is extremely expensive, and most items have subpar quality.

Being a constant presence in the region, Silver Hands had to deal themselves with raiders. They agreed to allow the Black Sand Raiders to use the oasis in exchange of the raiders not plunder and destroy the elvish compound. The Silver Hands serve as scouts for the slave tribe, warning them of choice caravans and signs of danger.

\subsubsection{Silver Hands Society}
The Silver Hands is less structured than other elvish tribes. They have no clans--all members are Silver Hands elves. They also only have three official posts: chief, protector of the wall, and keeper of the silver. Chief Toramund believes that sharing all wealth that comes his way with the entire tribe will decrease the likelihood of them holding back any wealth they obtain.

While the money with a steady pace comes to the Silver Hands, goods are not as constant. From time to time, the tribe sends small trading parties to Fort Iron and the trading village of Ablath, to gather resources when supplies are low. The tribe also has a routine of sending scouts to watch for caravans and dangers in the nearby wilderness.
