\subsectionA{Sky Singers}
\textbf{Area of Operation:} The Ivory Triangle, with a permanent market in Nibenay.

\textbf{Tribe Size:} Approximately 3,500 split between three clans.

Sky Singers operate as a minor merchant house for all intents and purposes. They trade and purchase goods from outlying settlements to bring to market in the city-states. Each clan is coordinated with this simple vision in mind: increase the tribe's profit via legitimate means.

\subsubsection{Brief History}
The Sky Singer tribe is a relatively new faction in Athas. They started trading more than a hundred years ago, and since then they use it as the tribe's primary means of sustenance. Only in desperate times, the tribe turns to raiding to survive---the only memory of such decision is in the ``Song of Temtaa.'' In the last few years, they erected an elvish market in Nibenay and with it trade flourished, making the now permanent market their main source of income.

\subsubsection{Sky Singers in Athas}
Sky Singers are a constant presence in the Ivory Triangle, trading mainly in Nibenay and Gulg, but also in their surrounding settlements. Being an elvish merchant house, they attract hatred from certain Dynastic Merchant Houses, specially House Stel from Urik. They are in open conflict against each other, while House Stel tries to increase its market share in Nibenay. The central motive behind this feud is livestock. Sky Singers are able to bring animals faster and in larger numbers, and their expertise in the field makes their animals healthier and more robust.

A healthy competition is held between Sky Singers and Clearwaters, as the tribes are now competing for the same markets, resources, and trade routes. Currently there is no sign of escalation between both tribes, but that can change at any moment. Silt Stalkers raid recurrently Sky Singers' caravans, with increasingly amounts of success.

\subsubsection{Sky Singers Society}
Three clans compose the Sky Singer tribe: Dayjumpers with 1,500 members, and Dawnchasers and Twilightcatchers with the rest. Dawnchasers operate as herders, handling not only the tribe's animals but also livestock sold at the markets. Dayjumpers are mainly traders and bureaucrats who deal with city-states' laws and customs, staying behind to maintain their markets while the rest of the tribe travels. Twilightcatchers are focused on the arcane arts, dealing with spell components, magic items, and scrolls of all descriptions.

The advisers consist of the leader of each clan, the flame singer, the elder wizard, the commander of the guard, and the nine trade masters. While clan leaders keep their posts for 12 years, the other advisers are the paragons of the tribe: the best cleric, wizard, warrior, and traders the tribe has. Their seats change as other elves show better skills.
