\subsectionA{Swiftwing Tribe}
\textbf{Area of Operation:} The Ivory Triangle.

\textbf{Tribe Size:} Unknown (estimated to be in some hundreds).

Swiftwings are nomadic raiders who terrorize the Tyr Region, with no one save from their raids---not even other elvish tribes. As a nomadic tribe, most of the tribe's sustenance comes from hunting, gathering, and herding. Raiding is done to complement what they can't gather and for profit by doing what no other raider in the wastelands does: the Swiftwing tribe find time to trade their goods, specially forbidden goods. While still learning the trade practices, they are quickly adjusting to the market.

\subsubsection{Brief History}
The Swiftwings are remnants of the older Red Sand tribe, from which they broke off over 500 years ago. They wandered the Alluvial Sand Wastes until a flock of birds guided them to the Dragon's Bowl---giving them their current name, Swiftwings. They started raiding caravans since then. This lifestyle brought new enemies to the tribe, from Silver Spring to Gulg, merchants hired anyone to destroy them---including the Red Sands.

The tribe was convinced to turn south. After raiding so much loot to slow their tribe, they arrived at Balic. They started an elvish market to reduce their cargo, but it proved to be profitable enough to make them rethink their ways.

\subsubsection{Swiftwing Tribe in Athas}
The tribe never stopped raiding, and they still are a constant menace in the Ivory Triangle. But since the Swiftwings started trading, they do so with the same chaotic glee normally reserved for raids.

The tribe can be reasoned with, and over time has allied with other forces in the region. Swiftwing tribe is currently protecting House Wavir against other raiders near the Mekillot Mountains.

\subsubsection{Swiftwing Tribe Society}
The Swiftwing tribe is led by a chief and the ``Learned Ones''---a council of advisors. The Learned Ones are chosen by consensus, when the attitude of those around them match their own sense of accomplishment and self-confidence. The chief is chosen from among the Learned Ones, also by consensus. When a chief has a dispute with a Learned One about a decision and neither party wants to compromise, the council will convene to settle the issue. A chief who disagrees with the consensus is removed, and a new chief is chosen.

For a tribe member, participating in raids is the best way to gain status. Each act of bravery is rewarded with a bead, with a different color for each act. Black beads represent killing an enemy warrior. Red beads represent slaying an enemy while unarmed and unarmored. Green beads for defeating a manifester or spellcaster. White beads for finding a particularly rich caravan to raid. Defeating a known defiler is the highest status for the Swiftwings, and such warrior tattoos themselves with a nine-pointed star.
