\subsectionA{Water Hunters}
\textbf{Area of Operation:} Northeast of Tyr, near the Utbo Grove.

\textbf{Tribe Size:} 100 members.

Hunter-gatherers and herders make up the Water Hunters. They embrace the old elvish ways with zealous fervor, declaring the other tribes heretics of elvish nature. They follow Coraanu Star Racer, a mythic elf that legends tell stories of how he taught all tribes how to run, fight, steal, and sing.

\subsubsection{Brief History}
For the last 20 years, the tribe chief has struggled to keep his elves true to the traditions. Too many tribes have deviated from the elvish ways. They have become merchants, mercenaries, or even settled down.

In the recent months, they discovered a new outpost near their sacred grove. Once they learned the outpost belongs to House Stel, whose city has a practice of slaughtering elves, they attacked the outpost. None survived. Two months later, they engaged in skirmishes with additional troops sent to reestablish the outpost. This time, defilers, psions, and templars were among the troops. Even though they took significant damage, the Water Hunters managed to destroy the second outpost.

\subsubsection{Water Hunters in Athas}
The Water Hunters live a mostly secluded way, hunting for prey by the Ringing Mountains. They are primarily hunters and herders, but hey occasionally raid caravans near outposts and near Urik. The elves defend their hunting ground ferociously against those who enter indiscriminately.

The tribe's sacred grove is near the Hidden Village, a slave tribe. Water Hunters sent an ultimatum: move or prepare for war. Their leader refused either action, and demanded a meeting with the Water Hunter chief. After engaging in a series of contests, the human successfully proved his equality among elves. The two tribes are in good terms ever since.

House Stel has been effectively at war with the Water Hunters, as they too have received the same ultimatum. The merchant house has dedicated a sizeable amount of funds towards eliminating the Water Hunters.

\subsubsection{Water Hunters Society}
The two forces that drive the Water Hunters tribe are tradition and devotion to the elemental water. Every decade when spring bubbles beneath an ancient kaor tree, the tribe gathers in the Utbo grove for the election of a new leader. Water Hunters wait for the water elementals that dwell in the underground spring to choose the new leader. If no elemental appears, the old chief continues to rule for another 10 years.

Three clans form the tribe, the Raindancers, the Poolrunners, and the Lakesingers. But they are not specialized as the other elvish tribes, each clan hunts, herds, and gathers for the benefit of the entire tribe. Tradition tells that each member is free to follow any course they wish---provided they don't violate tradition or anger water elementals.

The tribe's best hunters also gain as much prestige as chiefs and religious leaders, also acting as leaders. Their prestige is shown by the number of bone trophies adorning their skins and head rings. The masters of hunt demand obedience and cooperation when stalking prey, even though chiefs don't exercise constant control over the tribe.

They do not live in the Utbo grove, but they do consider it to be part of their territory. Being nomads, most of the tribe are not stationed there. However, a select number of members are trained as druids. They have the duty to tend and guard the Utbo grove, while the tribe roams the wastelands.
