\subsectionA{Wind Dancers}
\textbf{Area of Operation:} The Great Alluvial Sand Wastes.

\textbf{Tribe Size:} 400 members.

Wind Dancers have become raiders by necessity, as disaster struck the tribe twice.

\subsubsection{Brief History}
Originally herders, the Wind Dancers tended to a huge kank herd, moving from Balic to Tyr, until a disease affected the tribe's herd. This disease passed to the elves themselves, who started to die or become incapacitated, with fewer than 50 strong enough to tend to the tribe's needs. At the height of the Wind Dancers' vulnerability, a thri-kreen hunting pack attacked. Between the disease and the kreen, the tribe lost all their kanks and only 400 members survived.

\subsubsection{Wind Dancers in Athas}
Any outsider is a potential target for the Wind Dancers, as they search for plunder from Tyr to the Lost Oasis. House Wavir and House Inika have increased security of their caravans, while the tribe raids targets close to the Ringing Mountains, such as House Wavir's Outpost 10. While they are on the run, they have come to conflict with gith, thri-kreen, and even slave tribes. They do anything to take what they need to survive, from anyone.

There is an exception to this generalized aggression: outcast elves. The Wind Dancers have dwindled in numbers, so the tribe's chief, Santhaal, has focused on making the tribe prosper by any means. These outcast elves are given a chance to join the tribe, if they swear loyalty to Santhaal. As expected for elvish tribes, they go through tests of loyalty as initiation rituals.

\subsubsection{Wind Dancers Society}
Only two clans remain from the original five clans that made up the tribe, the Airhunters and the Breezechasers. Surviving members of the other clans were assimilated into the remaining ones by order of Santhaal. As far as the chief is concerned, the clans must be as one if the tribe is going to survive.

The adviser council is composed only of warriors, since they are now constantly functioning in a state of emergency. Even the element singer and the master wizard have militaristic approach to life. This mentality is shown when raiding, as the raiding parties (consisting of 50 elves) have even children among their ranks. Every single elf able to help the tribe must do so.
