\section{Weapons}
Characters in a {\tableheader Dark Sun} game use a variety of weapons: some with direct counterparts in the real world, some without.

\input{subsections/equipment/weapons/weapon-categories.tex}
\input{subsections/equipment/weapons/weapon-table.tex}

\subsection{Weapon Qualities}
Here is the format for weapon entries (given as column headings on each weapon table).

\textbf{Cost:} This value is the weapon's cost in gold pieces (gp), silver pieces (sp), ceramic pieces (cp) or ceramic bits (bits). The cost includes miscellaneous gear that goes with the weapon.

This cost is the same for a Small or Medium version of the weapon. A Large version costs twice the listed price.

\textbf{Damage:} The Damage columns give the damage dealt by the weapon on a successful hit. There are three columns for different weapon sizes: ``S'' for Small weapons, ``M'' for Medium weapons, and ``L'' for Large weapons. If two damage ranges are given then the weapon is a double weapon. Use the second damage figure given for the double weapon's extra attack. \tabref{Larger and Smaller Weapon Damage} gives weapon damage values for weapons of various sizes.

\textbf{Critical:} The entry in this column notes how the weapon is used with the rules for critical hits. When your character scores a critical hit, roll the damage two, three, or four times, as indicated by its critical multiplier (using all applicable modifiers on each roll), and add all the results together.

\textit{Exception:} Extra damage over and above a weapon's normal damage is not multiplied when you score a critical hit.

\textit{\multiplied2:} The weapon deals double damage on a critical hit.

\textit{\multiplied3:} The weapon deals triple damage on a critical hit.

\textit{\multiplied4:} The weapon deals quadruple damage on a critical hit.

\textit{19--20/\multiplied2:} The weapon scores a threat on a natural roll of 19 or 20 (instead of just 20) and deals double damage on a critical hit. (The weapon has a threat range of 19--20.)

\textit{18--20/\multiplied2:} The weapon scores a threat on a natural roll of 18, 19, or 20 (instead of just 20) and deals double damage on a critical hit. (The weapon has a threat range of 18--20.)

\textbf{Range Increment:} Any attack at less than this distance is not penalized for range. However, each full range increment imposes a cumulative $-2$ penalty on the attack roll. A thrown weapon has a maximum range of five range increments. A projectile weapon can shoot out to ten range increments.

\textbf{Weight:} There are three columns for the weight of a weapon: ``S'' for Small weapons, ``M'' for Medium weapons, and ``L'' for Large weapons.

\textbf{Type:} Weapons are classified according to the type of damage they deal: bludgeoning, piercing, or slashing. Some monsters may be resistant or immune to attacks from certain types of weapons.

Some weapons deal damage of multiple types. If a weapon is of two types, the damage it deals is not half one type and half another; all of it is both types. Therefore, a creature would have to be immune to both types of damage to ignore any of the damage from such a weapon.

In other cases, a weapon can deal either of two types of damage. In a situation when the damage type is significant, the wielder can choose which type of damage to deal with such a weapon.

\textbf{Special:} Some weapons have special features. See the weapon descriptions for details.

\input{subsections/equipment/weapons/weapon-descriptions.tex}

\subsection{Masterwork Weapons}
A masterwork weapon is a finely crafted version of a normal weapon. Wielding it provides a +1 enhancement bonus on attack rolls.

You can't add the masterwork quality to a weapon after it is created; it must be crafted as a masterwork weapon (see the \skill{Craft} skill). The masterwork quality adds 300 cp to the cost of a normal weapon (or 6 cp to the cost of a single unit of ammunition). Adding the masterwork quality to a double weapon costs twice the normal increase (+600 cp).

Masterwork ammunition is damaged (effectively destroyed) when used. The enhancement bonus of masterwork ammunition does not stack with any enhancement bonus of the projectile weapon firing it.

All magic weapons are automatically considered to be of masterwork quality. The enhancement bonus granted by the masterwork quality doesn't stack with the enhancement bonus provided by the weapon's magic.

Even though some types of armor and shields can be used as weapons, you can't create a masterwork version of such an item that confers an enhancement bonus on attack rolls. Instead, masterwork armor and shields have lessened armor check penalties.
