\section{Psion Discipline Powers}



\subsection{Egoist Discipline Powers {\normalsize(Psychometabolism; Con)}}
\begin{enumerate*}
\item \psionicList{Adapt Body}\textsuperscript{A}: Your body automatically adapts to hostile environments.

      \psionicList{Body Equilibrium}:

      \psionicList{Carapace}: Gain +11 natural armor bonus and $-4$ Dexterity penalty.

      \psionicList{Catfall}: Instantly save yourself from a fall. %XPH

      \psionicList{Cell Adjustment}: Each round heal up to 4 hp or remove one disease.

      \psionicList{Double Pain}: Target perceives all damage as doubled for one minute.

      \psionicList{Photosynthesis}: Stand in the sun to heal hit points.

      \psionicList{Sleep, Psionic}: Puts one creature into magical slumber.

\item \psionicList{Adrenaline Control}: Increase Strength, Dexterity, or Constitution by 1d6.

      \psionicList{Biofeedback}: Gain RD 2/--, and +2 bonus on AC.

      \psionicList{Disguise Self, Psionic}\textsuperscript{P}: Changes your appearance.

      \psionicList{Chameleon}: Gain +10 enhancement bonus on \skill{Hide} checks. %XPH

      \psionicList{Empathic Transfer}\textsuperscript{A}: Transfer another's wounds to yourself. %XPH

      \psionicList{Expansion}\textsuperscript{A}: Become one size category larger. %XPH

      \psionicList{Haste, Personal}: Move faster, +1 on attacks, AC, Reflex saves.

      \psionicList{Reduction}\textsuperscript{A}: You grow smaller. %XPH

      \psionicList{Spider Climb, Psionic}: Grants ability to walk on walls and ceilings.

      \psionicList{Sustenance}\textsuperscript{A}: Go without food and water for one day. %XPH

\item \psionicList{Aging}: Victim ages 2d4 years.

      \psionicList{Animal Affinity}: Gain low-light vision and characteristics of an animal.

      \psionicList{Displacement, Psionic}: Attacks miss subject 50\%.

      \psionicList{Graft Weapon}: Your hand is replaced seamlessly by your weapon. %XPH

      \psionicList{Life Draining}\textsuperscript{A}: Touch deals 1d6 damage/round; caster gains damage as hp.

\item \psionicList{Ectoplasmic Form}: You gain benefits of being insubstantial and can fly slowly. %XPH

      \psionicList{Energy Adaptation}\textsuperscript{A}: Your body converts energy to harmless light.

      \psionicList{Flesh Armor}: Turn your skin into armor.

\item \psionicList{Immovability}: You are almost impossible to move and gain DR 5/--.

      \psionicList{Metamorphosis}\textsuperscript{P}: Assume shape of creature or object. %XPH

      \psionicList{Shadow Body}: You become a living shadow (not the creature). %XPH

\item \psionicList{Heal, Personal}\textsuperscript{AP}: Cures 120 points of damage, all diseases and mental conditions.

      \psionicList{Suspend Life}\textsuperscript{A}: Put yourself into a state akin to suspended animation. %XPH

\item \psionicList{Regenerate, Psionic}\textsuperscript{P}: Subject's severed limbs grow back, cures 6d12 damage.

\item \psionicList{Death Field}: Sacrifice hit points to deal damage in a 18-meter radius.

\item \psionicList{Elemental Composition}\textsuperscript{P}:
\end{enumerate*}



\subsection{Kineticist Discipline Powers {\normalsize(Psychokinesis; Int)}}
\begin{enumerate*}
\item \psionicList{Compact}: Reduce the size of a volume of any material to 10\% of its original volume.

      \psionicList{Control Sound}: Alter existing sounds.

      \psionicList{Deflect}\textsuperscript{P}: Deflect a single thrown weapon or fired projectile.

      \psionicList{Molecular Agitation}: You heat a creature or object.

      \psionicList{Magnetize}\textsuperscript{A}: Make a metal object attract or be attracted to other metal objects.

      \psionicList{Soften}: Decrease an object's base hardness by 1 per round.

      \psionicList{Telekinesis, Psionic}\textsuperscript{A}: Moves object, attacks creature, or hurls object or creature.

\item \psionicList{Concentrate Water}\textsuperscript{P}: Collect all moisture within 9-meter-radius.

      \psionicList{Control Flames}\textsuperscript{P}: Take control of nearby open flame.

      \psionicList{Control Light}: Adjust ambient light levels.

      \psionicList{Create Sound}\textsuperscript{P}: Create the sound you desire.
      
\item \psionicList{Animate Objects, Psionic}\textsuperscript{AP}: Objects attack your foes.

      \psionicList{Ballistic Attack}\textsuperscript{P}: Attack with small objects.

      \psionicList{Levitate, Psionic}\textsuperscript{P}: You move up and down at your direction.

      \psionicList{Mass Manipulation}\textsuperscript{P}: Change an object's weight from 50\% up to 200\% its normal value.

      \psionicList{Project Force}\textsuperscript{AP}: Punch someone from afar.

      \psionicList{Static Discharge}\textsuperscript{P}: Accumulate static electricity and discharge it on a creature afterwards.

\item \psionicList{Control Body}\textsuperscript{P}: Take rudimentary control of your foe's limbs.

      \psionicList{Create Object}\textsuperscript{P}: Assemble matter from the surrounding area to create a solid object.

      \psionicList{Fly, Psionic}\textsuperscript{P}: You fly at speed of 18 m.

      \psionicList{Inertial Barrier}\textsuperscript{P}: Create a sphere that protects you against fire, missile attacks, and more.

      \psionicList{Molecular Manipulation}\textsuperscript{P}: Decrease an object's hit points to the point of breaking.

      \psionicList{Opposite Reaction}\textsuperscript{P}: Project a force blast in the opposite direction of an incoming physical missile attack.

\item \psionicList{Control Wind}\textsuperscript{P}:

      \psionicList{Detonate}\textsuperscript{P}: Explode small objects or destroy one construct or undead creature.

      \psionicList{Molecular Bonding}\textsuperscript{P}: Join two surfaces together.

      \psionicList{Wall of Force, Psionic}\textsuperscript{P}: Wall is immune to damage.

\item \psionicList{Kinetic Control}: Gain a kinetic storage that absorbs physical damage, and expend it later.

      \psionicList{Molecular Rearrangement}\textsuperscript{P}: Change one object's fundamental properties.

\item \psionicList{Disintegrate, Psionic}\textsuperscript{AP}: Turn one creature or object to dust.

\item \psionicList{Momentum Theft}\textsuperscript{P}: Remove all speed from a target creature or object.

\item \psionicList{Megakinesis}\textsuperscript{AP}: As \psionic{psionic telekinesis}, but you can move objects 100$\times$ heavier.
\end{enumerate*}



\subsection{Nomad Discipline Powers {\normalsize(Psychoportation; Con)}}
\begin{enumerate*}
\item \psionicList{Astral Projection}: Create a clone in the Astral Plane.

      \psionicList{Spacetime Anchor}: You cannot be \emph{teleported} against your will.

\item \psionicList{Dimensional Anchor, Psionic}\textsuperscript{P}: Bars extradimensional movement.

      \psionicList{Duo-Dimension}: You become two-dimensional.

\item \psionicList{Dimension Blade}\textsuperscript{P}: Transform a melee weapon into a super sharp blade.

      \psionicList{Pocket Dimension}: Create a small extradimensional storage area.

      \psionicList{Shadow Walk, Psionic}\textsuperscript{A}: Step into shadow to travel rapidly.

      \psionicList{Time Hop, Personal}: You hop forward up to 3 rounds in the future.

\item \psionicList{Astral Caravan}: You lead a group to a planar destination.

      \psionicList{Dimension Door, Psionic}: Teleports you short distance. %XPH

      \psionicList{Spatial Distortion}: Change dimensions on a volume to become larger or smaller.

\item \psionicList{Teleport, Psionic}\textsuperscript{A}: Instantly transports you as far as 90,000 km.

      \psionicList{Teleport Other}\textsuperscript{AP}: As \psionic{psionic teleport}, but affects another creature.

      \psionicList{Wormhole}\textsuperscript{AP}: Create a door between any two known points.

\item \psionicList{Banishment, Psionic}: Teleport a creature to a pocket dimension.

      \psionicList{Blink, Psionic}\textsuperscript{P}: You randomly vanish and reappear.


\item \psionicList{Decerebrate}\textsuperscript{P}: Remove portion of subject's brain stem.

      \psionicList{Phase}: Become ethereal for a short period.

      \psionicList{Summon Planar Creature}\textsuperscript{AP}: Transport one creature from another plane to you.

      \psionicList{Time Travel}\textsuperscript{AP}: Jump to the past or to the future.

\item \psionicList{Phase Object}: Make an object ethereal for a short period.

      \psionicList{Summon Planar Energy}\textsuperscript{AP}: Transport harmful energy from an Inner Plane.

      \psionicList{Time Dilation}\textsuperscript{P}: Speed up or slow down the timestream itself.

\item \psionicList{Planar Transportation}\textsuperscript{AP}: Switch a 9-meter-cube from one plane for a portion of another plane.

      \psionicList{Time Duplicate}\textsuperscript{P}: Borrow a future self to aid you.
\end{enumerate*}



\subsection{Seer Discipline Powers {\normalsize(Clairsentience; Wis)}}
\begin{enumerate*}
\item \psionicList{Detect Poison, Psionic}: Detects poison in one creature or object.

      \psionicList{Know Direction and Location}: You discover where you are and what direction you face.

      \psionicList{Detect Remote Viewing}: You know when others spy on you remotely.

\item \psionicList{Detect Magic, Psionic}: Detects spells and magic items within 6 m.

      \psionicList{Sensitivity to Psychic Impressions}: You can find out about an area's past.

      \psionicList{Watcher's Ward}: You are aware of creatures entering warded area.

\item \psionicList{Clairaudience}: Hear at a distance.

      \psionicList{Danger Sense}\textsuperscript{A}: Gain the uncanny dodge ability.

      \psionicList{Detect Moisture}\textsuperscript{A}: Reveals moisture within 18 m.

      \psionicList{Detect Spirits}: Sense incorporeal creatures within 12 m.

      \psionicList{Environment}: Sense the environment around a known item.

      \psionicList{Synesthete}: You receive one kind of sense when another sense is stimulated.

      \psionicList{Trail of Destruction}\textsuperscript{P}: Detect past use of defiling magic in the area.

      \psionicList{Ubiquitous Vision}: You have all-around vision.

\item \psionicList{Anchored Navigation}\textsuperscript{A}: Establish a mishap-free teleport beacon.

      \psionicList{Aura Sight}: Reveal alignment, type, and hit dice of creatures in sight.

      \psionicList{Clairvoyance}: See at a distance.

      \psionicList{Combat Mind}\textsuperscript{A}: You improve your allies' initiative count by 1.

      \psionicList{Weather Prediction}\textsuperscript{P}: Predicts weather for next 24 hours.

\item \psionicList{Arcane Sight, Psionic}\textsuperscript{P}: Magical auras become visible to you.

      \psionicList{Object Reading}: Learn details about an object's previous owner.

      \psionicList{Safe Path}\textsuperscript{AP}: Gain +2 AC bonus, +4 bonus in saving throws and some skill checks.

      \psionicList{Second Chance}: Gain a reroll. %XPH

\item \psionicList{Bone Reading}\textsuperscript{P}: Learn details about a deceased creature.

      \psionicList{Precognition}: Forsee some hours into your future to give you an edge.

\item \psionicList{Fate of One}\textsuperscript{P}: Reroll any roll you just failed. %XPH

      \psionicList{Predestination}\textsuperscript{AP}: Predict the destiny of a single creature.

\item \psionicList{Spirit Lore}\textsuperscript{P}: Commune with spirits to ask one question/round.

      \psionicList{True Seeing, Psionic}\textsuperscript{P}: Lets you see all things as they really are.

\item \psionicList{Cosmic Awareness}\textsuperscript{AP}: You perceive all things in range.
\end{enumerate*}



\subsection{Shaper Discipline Powers {\normalsize(Metacreativity; Int)}}
\begin{enumerate*}
\item \psionicList{Cannibalize}\textsuperscript{P}: Convert your Constitution score into power points.

      \psionicList{Heighten Senses}\textsuperscript{AP}: You gain scent and +6 enhancement bonus in \skill{Spot} and \skill{Listen}.

\item \psionicList{Detect Psionics}\textsuperscript{P}: You detect the presence of psionics.

      \psionicList{Teleport Trigger}\textsuperscript{P}: Predetermined event triggers \psionic{psionic teleport}.

\item \psionicList{Dispel Psionics}\textsuperscript{P}: Cancels psionic powers and effects.

      \psionicList{Trace Teleport}\textsuperscript{AP}: Learn destination of subject's \emph{teleport}.

\item \psionicList{Freedom of Movement, Psionic}\textsuperscript{P}: You cannot be held or otherwise rendered immobile.

      \psionicList{Psychic Noise}\textsuperscript{P}: Double power point expenditure in a 15-meter radius.

\item \psionicList{Antimagic Field, Psionic}\textsuperscript{P}: Suppress all magic in a 9-meter radius.

      \psionicList{Astral Construct}\textsuperscript{AP}: Creates astral construct to fight for you. %XPH

      \psionicList{Dimensional Screen}\textsuperscript{P}: Wrap yourself with a \psionic{psionic dimension door}.

      \psionicList{Metaconcert}\textsuperscript{AP}: Mental concert of two or more increases the total power of the participants.

      \psionicList{Power Leech}\textsuperscript{AP}: Drain power points while you maintain concentration.

\item \psionicList{Null Psionics Field}\textsuperscript{P}: Create a field where psionic power does not function. %XPH

\item \psionicList{Psychic Chirurgery}\textsuperscript{PX}: You repair psychic damage or impart knowledge of new powers. %XPH

      \psionicList{Reddopsi}\textsuperscript{P}: Powers targeting you rebound on manifester. %XPH

      \psionicList{Teleport Object, Psionic}\textsuperscript{AP}: As \psionic{psionic teleport}, but affects a touched object.

\item \psionicList{Bend Reality}\textsuperscript{PX}: Alters reality within power limits. %XPH

      \psionicList{Schism}\textsuperscript{P}: Your partitioned mind can manifest lower level powers. %XPH

      \psionicList{Summon Object}\textsuperscript{P}: Bring a distant object to you.

\item \psionicList{Apopsi}\textsuperscript{PX}: You delete target's psionic powers. %XPH

      \psionicList{Reality Revision}\textsuperscript{PX}: As \psionic{bend reality}, but fewer limits. %XPH

      \psionicList{Revivify}\textsuperscript{APX}: Return the dead to life before the psyche leaves the corpse.
\end{enumerate*}



\subsection{Telepath Discipline Powers {\normalsize(Telepathy; Wis)}}
\begin{enumerate*}
\item \psionicList{Conceal Thoughts}: Protects you mind against telepathic powers.

      \psionicList{Contact}: Establish mental connection with the target's mind.

      \psionicList{Psychic Crush}\textsuperscript{A}: Telepathic attack. Deal 2d8 points of damage.

      \psionicList{Send Thoughts}\textsuperscript{P}: Make a one-way communication with the target.

\item \psionicList{Awe}\textsuperscript{P}: Subject fears you.

      \psionicList{Charm, Psionic}\textsuperscript{AP}: Makes one person your friend.

      \psionicList{Invisibility, Psionic}\textsuperscript{AP}: Trick a \emph{contacted} mind to make a creature invisible.

      \psionicList{Mind Thrust}\textsuperscript{AP}: Telepathic attack. Lock one of the target's known psionic powers for 2d6 days.

      \psionicList{Read Thoughts}\textsuperscript{P}: Read someone's surface thoughts.

      \psionicList{Sense Link}\textsuperscript{AP}: You sense what the subject senses (single sense).

\item \psionicList{Ego Whip}\textsuperscript{AP}: Telepathic attack. Leave target shaken for 1d4 rounds. Spellcasters cannot cast spells above 3rd level.

      \psionicList{Ejection}: Force unwanted \emph{contacts} out of your mind, with risk of side effects.

      \psionicList{Life Dectection}\textsuperscript{A}: Detect presence of thinking creatures in a 54-meter cone.

      \psionicList{Psychic Messenger}: Create a image of yourself to deliver a message within 300 km.

      \psionicList{Read Thoughts}: Detect surface thoughts of a \emph{contacted} mind.

      \psionicList{Suggestion, Psionic}\textsuperscript{AP}: Compels subject to follow stated course of action.

\item \psionicList{Attraction}\textsuperscript{P}: Subject has attraction you specify.

      \psionicList{Aversion}\textsuperscript{P}: Subject has aversion you specify.

      \psionicList{Mind Bar}: You become immune to possession and gain +15 bonus on Will saves against spells and powers.

      \psionicList{Mindlink}\textsuperscript{P}: You forge a limited mental bond with a \emph{contacted} creature.

      \psionicList{Modify Memory, Psionic}\textsuperscript{P}: Changes 5 minutes of subject's memories.

      \psionicList{Psionic Blast}\textsuperscript{AP}: Telepathic attack. Deal 80\% of the target's hit points as non-lethal damage.

\item \psionicList{Dominate, Psionic}\textsuperscript{AP}: Control target telepathically.

      \psionicList{Id Insinuation}\textsuperscript{AP}: Telepathic attack. Daze target for 1d4 rounds.

      \psionicList{Inflict Pain}\textsuperscript{AP}: Telepathic stab gives your foe $-4$ on attack rolls, or $-2$ if he makes the save.

      \psionicList{Probe}\textsuperscript{P}: Telepathically ask one question/round to a target.

      \psionicList{Superior Invisibility}\textsuperscript{P}: As \psionic{psionic invisibility}, but creatures have no sound or smell.

\item \psionicList{Mindflame}\textsuperscript{P}: Project a cone of mental force that can damage lesser minds.

      \psionicList{Mind Switch}\textsuperscript{APX}: You switch minds with another.

\item \psionicList{Mind Blank, Personal}\textsuperscript{P}: You are immune to scrying and mental effects for one day.

\item \psionicList{Mind Blank, Psionic}\textsuperscript{P}: Subject immune to mental/emotional effects and scrying effects for one day.

\item \psionicList{Mind Switch, True}\textsuperscript{PX}: A permanent mind swap.
\end{enumerate*}