\section{Psion Discipline Powers}



\subsection{Egoist Discipline Powers {\normalsize(Psychometabolism)}}
\begin{enumerate*}
\item \psionicList{Thicken Skin}\textsuperscript{A}: Gain +1 enhancement bonus to your AC for 10 min./level.
\item \psionicList{Animal Affinity}\textsuperscript{A}: Gain +4 enhancement to one ability.

\psionicList{Chameleon}: Gain +10 enhancement bonus on \skill{Hide} checks.

\psionicList{Empathic Transfer}\textsuperscript{A}: Transfer another's wounds to yourself.

\psionicList{Share Strength}\textsuperscript{A}: Temporarily transfer your Strength to another. %

\item \psionicList{Aging}\textsuperscript{A}: Make subject older. %

\psionicList{Death Field}\textsuperscript{A}: Release an energy burst from the Gray that drains vital energy. %

\psionicList{Ectoplasmic Form}: You gain benefits of being insubstantial and can fly slowly.

\psionicList{Hustle}: Instantly gain a move action.

\item \psionicList{Accelerate}\textsuperscript{A}: Move faster, +1 on attack rolls, AC, and Reflex saves. %

\psionicList{Metamorphosis}: Assume shape of creature or object.

\psionicList{Psychic Vampire}: Touch attack drains 2 power points/level from foe.

\item \psionicList{Revivify, Psionic}\textsuperscript{AX}: Return the dead to life before the psyche leaves the corpse.

\psionicList{Psychofeedback}: Boost Strength, Dexterity, or Constitution at the expense of one or more other scores.

\psionicList{Restore Extremity}: Return a lost digit, limb, or other appendage to subject.

\item \psionicList{Restoration, Psionic}: Restores level and ability score drains.
\item \psionicList{Complete Healing}\textsuperscript{A}: Heals all damage. %

\psionicList{Fission}: You briefly duplicate yourself.

\psionicList{Poison Simulation}\textsuperscript{A}: Coat surface with potent poisons. %

\item \psionicList{Fusion}\textsuperscript{X}: You combine your abilities and form with another.
\item \psionicList{Metamorphosis, Greater}\textsuperscript{X}: Assume shape of any nonunique creature or object each round.
\end{enumerate*}



\subsection{Kineticist Discipline Powers {\normalsize(Psychokinesis)}}
\begin{enumerate*}
\item \psionicList{Control Object}: Telekinetically animate a small object.
\item \psionicList{Control Air}\textsuperscript{A}: You have control over wind speed and direction.

\psionicList{Energy Missile}\textsuperscript{A}: Deal 3d6 energy damage to up to five subjects.

\item \psionicList{Energy Cone}\textsuperscript{A}: Deal 5d6 energy damage in 18-m cone.
\item \psionicList{Control Body}\textsuperscript{A}: Take rudimentary control of your foe's limbs.

\psionicList{Energy Ball}\textsuperscript{A}: Deal 7d6 energy damage in 6-m radius.

\psionicList{Inertial Barrier}: Gain DR 5/--.

\item \psionicList{Energy Current}\textsuperscript{A}: Deal 9d6 damage to one foe and half to another foe as long as you concentrate.

\psionicList{Fiery Discorporation}\textsuperscript{A}: Cheat death by discorporating into nearby fire for one day.

\item \psionicList{Dispelling Buffer}: Subject is buffered from one \psionic{dispel psionics} effect.

\psionicList{Null Psionics Field}: Create a field where psionic power does not function.

\item \psionicList{Reddopsi}: Powers targeting you rebound on manifester.
\item \psionicList{Telekinetic Sphere, Psionic}: Mobile force globe encapsulates creature and moves it.
\item \psionicList{Tornado Blast}\textsuperscript{A}: Vortex of air subjects your foes to 17d6 damage and moves them.
\end{enumerate*}



\subsection{Nomad Discipline Powers {\normalsize(Psychoportation)}}
\begin{enumerate*}
\item \psionicList{Burst}: Gain +3 m to speed this round.

\psionicList{Detect Teleportation}\textsuperscript{A}: Know when teleportation powers are used in close range.

\item \psionicList{Dimension Swap}\textsuperscript{A}: You and ally or two allies switch positions.

\psionicList{Levitate, Psionic}: Subject moves up and down at your direction.

\item \psionicList{Astral Caravan}\textsuperscript{A}: You lead \psionic{astral traveler}-enabled group to a planar destination.
\item \psionicList{Dimensional Anchor, Psionic}: Bars extra dimensional movement.

\psionicList{Dismissal, Psionic}: Forces a creature to return to its native plane.

\psionicList{Fly, Psionic}: You fly at a speed of 18 m.

\item \psionicList{Baleful Teleport}\textsuperscript{A}: Destructive teleport deals 9d6 damage.

\psionicList{Teleport, Psionic}: Instantly transports you as far as 100 miles/level.

\psionicList{Teleport Trigger}: Predetermined event triggers teleport.

\item \psionicList{Banishment, Psionic}\textsuperscript{A}: Banishes extraplanar creatures.
\item \psionicList{Dream Travel}\textsuperscript{A}: Travel to other places through dreams.

\psionicList{Ethereal Jaunt, Psionic}: Become ethereal for 1 round/level.

\psionicList{Teleport Object, Psionic}: As \psionic{psionic teleport}, but affects a touched object. %

\item \psionicList{Time Hop, Mass}\textsuperscript{A}: Willing subjects hop forward in time.
\item \psionicList{Teleportation Circle, Psionic}: Circle teleports any creatures inside to designated spot.

\psionicList{Time Regression}\textsuperscript{X}: Relive the last round.
\end{enumerate*}



\subsection{Seer Discipline Powers {\normalsize(Clairsentience)}}
\begin{enumerate*}
\item \psionicList{Destiny Dissonance}: Your dissonant touch sickens a foe.

\psionicList{Precognition}: Gain +2 insight bonus to one roll.

\item \psionicList{Clairvoyant Sense}: See and hear a distant location.

\psionicList{Locate, Psionic}\textsuperscript{A}: Indicates direction to familiar objects and creatures. %

\psionicList{Object Reading}\textsuperscript{A}: Learn details about an object's previous owner.

\psionicList{Sensitivity to Psychic Impressions}: You can find out about an area's past.

\item Detect Moisture\textsuperscript{A}: Reveals moisture within 18 m. %

\psionicList{Escape Detection}: You become difficult to detect with clairsentience powers.

\psionicList{Fate Link}\textsuperscript{A}: You link the fates of two targets.

\psionicList{Truthear}: Receive +20 insight bonus to \skill{Sense Motive} checks. %

\item \psionicList{Anchored Navigation}\textsuperscript{A}: Establish a mishap-free teleport beacon.

\psionicList{Remote Viewing}\textsuperscript{X}: See, hear, and potentially interact with 
subjects at a distance.
\item \psionicList{Clairtangent Hand}\textsuperscript{A}: Emulate \psionic{far hand} at a distance.

\psionicList{Second Chance}: Gain a reroll.

\item \psionicList{Precognition, Greater}: Gain +4 insight bonus to one roll.
\item \psionicList{Fate of One}: Reroll any roll you just failed.
\item \psionicList{Hypercognition}: You can deduce almost anything.
\item \psionicList{Cosmic Awareness}: You perceive all things in range. %

\psionicList{Metafaculty}\textsuperscript{X}: You learn details about any one creature.
\end{enumerate*}



\subsection{Shaper Discipline Powers {\normalsize(Metacreativity)}}
\begin{enumerate*}
\item \psionicList{Astral Construct}\textsuperscript{A}: Creates astral construct to fight for you.

\psionicList{Minor Creation, Psionic}: Creates one cloth or wood object.

\item \psionicList{Psionic Repair Damage}\textsuperscript{A}: Repairs construct of 3d8 hit points +1 hp/level.
\item \psionicList{Concealing Amorpha, Greater}: Quasi-real membrane grants you total concealment.

\psionicList{Ectoplasmic Cocoon}\textsuperscript{A}: You encapsulate a foe so it can't move.

\item \psionicList{Fabricate, Psionic}: Transforms raw goods to finished items.

\psionicList{Quintessence}: You collapse a bit of time into a physical substance.

\item \psionicList{Hail of Crystals}\textsuperscript{A}: A crystal explodes in an area, dealing 9d4 slashing damage.

\psionicList{Pocket Dimension}\textsuperscript{A}: Create a small storage area in an extradimensional space. %

\item \psionicList{Crystallize}: Turn subject permanently to crystal.

\psionicList{Fabricate, Greater Psionic}: Transforms a lot of raw goods to finished items.

\item \psionicList{Ectoplasmic Cocoon, Mass}\textsuperscript{A}: You encapsulate all foes in a 6-m radius.
\item \psionicList{Astral Seed}: You plant the seed of your rebirth from the Astral Plane.
\item \psionicList{Genesis}\textsuperscript{X}: You instigate a new demiplane on the Astral Plane.

\psionicList{True Creation}\textsuperscript{X}: As \psionic{psionic major creation}, except items are completely real.
\end{enumerate*}



\subsection{Telepath Discipline Powers {\normalsize(Telepathy)}}
\begin{enumerate*}
\item \psionicList{Charm, Psionic}\textsuperscript{A}: Makes one person your friend.

\psionicList{Mindlink}\textsuperscript{A}: You forge a limited mental bond with another creature.

\item \psionicList{Aversion}\textsuperscript{A}: Subject has aversion you specify.

\psionicList{Brain Lock}\textsuperscript{A}: Subject cannot move or take any mental actions.

\psionicList{Read Thoughts}: Detect surface thoughts of creatures in range.

\psionicList{Suggestion, Psionic}\textsuperscript{A}: Compels subject to follow stated course of 
action.
\item \psionicList{Crisis of Breath}\textsuperscript{A}: Disrupt subject's breathing.

\psionicList{Empathic Transfer, Hostile}\textsuperscript{A}: Your touch transfers your hurt to 
another.

\psionicList{False Sensory Input}\textsuperscript{A}: Subject sees what isn't there.

\item \psionicList{Dominate, Psionic}\textsuperscript{A}: Control target telepathically.

\psionicList{Hallucination}\textsuperscript{A}: Phantasm cause psychosomatic damage. %

\psionicList{Mindlink, Thieving}\textsuperscript{A}: Borrow knowledge of a subject's power.

\psionicList{Modify Memory, Psionic}: Changes 5 minutes of subject's memories.

\psionicList{Schism}: Your partitioned mind can manifest lower level powers.

\item \psionicList{Metaconcert}\textsuperscript{A}: Mental concert of two or more increases the total power of the participants.

\psionicList{Mind Probe}: You discover the subject's secret thoughts.

\item \psionicList{Mind Switch}\textsuperscript{AX}: You switch minds with another.
\item \psionicList{Crisis of Life}\textsuperscript{A}: Stop subject's heart.
\item \psionicList{Mind Seed}\textsuperscript{X}: Subject slowly becomes you.
\item \psionicList{Mind Switch, True}\textsuperscript{X}: A permanent brain swap.

\psionicList{Psychic Chirurgery}\textsuperscript{X}: You repair psychic damage or impart 
knowledge of new powers.
\end{enumerate*}