\section{Psion/Wilder Powers}




\subsection{1st-Level Psion/Wilder Powers}

\psionicList{Astral Traveler}: Enable yourself or another to join an astral  aravan-enabled trip.

\psionicList{Attraction}\textsuperscript{A}: Subject has an attraction you specify.

\psionicList{Aura Reading}: Reveal personal details about the target.

\psionicList{Bioflexibilty}: You gain a bonus to Escape Artist checks.

\psionicList{Bolt}\textsuperscript{A}: You create a few enhanced short-lived bolts, arrows, or bullets.

\psionicList{Call to Mind}: Gain additional Knowledge check with +4 competence bonus.

\psionicList{Cast Missiles}: You can launch missiles without a bow or other weapon.

\psionicList{Catfall}\textsuperscript{A}: Instantly save yourself from a fall.

\psionicList{Cause Sleep}\textsuperscript{A}: Puts 4 HD of creatures into deep slumber.

\psionicList{Conceal Thoughts}: You conceal your motives.

\psionicList{Control Flames}\textsuperscript{A}: Take control of nearby open flame.

\psionicList{Control Light}: Adjust ambient light levels.

\psionicList{Create Sound}: Create the sound you desire.

\psionicList{Cryokinesis}: You cool a creature or object.

\psionicList{Crystal Shard}\textsuperscript{A}: Ranged touch attack for 1d6 points of piercing damage.

\psionicList{Daze, Psionic}\textsuperscript{A}: Humanoid creature of 4 HD or less loses next action.

\psionicList{Deceleration}\textsuperscript{A}: Target's speed is halved.

\psionicList{Deflect Strike}: You psychokinetically deflect the next attack of a creature within range.

\noindent\textit{\hyperref[psionic:Deja Vu]{Déjà Vu}}\textsuperscript{A}: Your target repeats his last action.

\psionicList{Demoralize}\textsuperscript{A}: Enemies become shaken.

\psionicList{Detect Poison, Psionic}: Detects poison in one creature or object.

\psionicList{Detect Psionics}: You detect the presence of psionics.

\psionicList{Disable}\textsuperscript{A}: Subjects incorrectly believe they are disabled.

\psionicList{Dissipating Touch}\textsuperscript{A}: Touch deals 1d6 damage.

\psionicList{Distract}: Target gets -4 bonus on Listen, Search, Sense Motive, and Spot checks.

\psionicList{Ecto Protection}\textsuperscript{A}: An astral construct gains bonus against dismiss ectoplasm.

\psionicList{Empathy}\textsuperscript{A}: You know the subject's surface emotions.

\psionicList{Empty Mind}\textsuperscript{A}: You gain +2 on Will saves until your next action.

\psionicList{Energy Ray}\textsuperscript{A}: Deal 1d6 energy (cold, electricity, fire, or sonic) damage.

\psionicList{Entangling Ectoplasm}: You entangle a foe in sticky goo.

\psionicList{Far Hand}\textsuperscript{A}: Move small objects at a limited distance.

\psionicList{Float}: You buoy yourself in water or other liquid.

\psionicList{Force Screen}\textsuperscript{A}: Invisible disc provides +4 shield bonus to AC.

\psionicList{Ghost Writing}: Creatures writing on a distant surface or creature touched.

\psionicList{Grease, Psionic}: Makes 10-ft. square or one object slippery.

\psionicList{Hammer}\textsuperscript{A}: Melee touch attack deals 1d8/round.

\psionicList{Hush}\textsuperscript{A}: Subjects become utterly silent.

\psionicList{Inertial Armor}\textsuperscript{A}: Tangible field of force provides you with +4 armor bonus to AC.

\psionicList{Know Direction and Location}: You discover where you are and what direction you face.

\psionicList{Matter Agitation}: You heat a creature or object.

\psionicList{Mind Thrust}\textsuperscript{A}: Deal 1d10 damage.

\psionicList{Missive}\textsuperscript{A}: Send a one-way telepathic message to subject.

\psionicList{My Light}\textsuperscript{A}: Your eyes emit 20-ft. cone of light.

\psionicList{Photosynthesis}\textsuperscript{A}: Transform light into healing.

\psionicList{Precognition, Defensive}\textsuperscript{A}: Gain +1 insight bonus to AC and saving throws.

\psionicList{Precognition, Offensive}\textsuperscript{A}: Gain +1 insight bonus on your attack rolls.

\psionicList{Prescience, Offensive}\textsuperscript{A}: Gain +2 insight bonus on your damage rolls.

\psionicList{Psionic Draw}: Instantly draw a weapon.

\psionicList{Psychic Tracking}: Track a creature using \skill{Psicraft}.

\psionicList{Sense Link}\textsuperscript{A}: You sense what the subject senses (single sense).

\psionicList{Skate}: Subject slides skillfully along the ground.

\psionicList{Synesthete}: You receive one kind of sense when another sense is stimulated.

\psionicList{Tattoo Animation}\textsuperscript{A}: Animates your tattoos or steals another's.

\psionicList{Telempathic Projection}: Alter the subject's mood.

\psionicList{Trail of Destruction}: Detects recent defiling.

\psionicList{Vigor}\textsuperscript{A}: Gain 5 temporary hit points.

\psionicList{Wild Leap}\textsuperscript{A}: Make an additional leap and gain a bonus to Jump checks.




\subsection{2nd-Level Psion/Wilder Powers}

\psionicList{Alter Self, Psionic}\textsuperscript{A}: Assume form of a similar creature.

\psionicList{Bestow Power}\textsuperscript{A}: Subject receives 2 power points.

\psionicList{Biofeedback}\textsuperscript{A}: Gain damage reduction 2/-.

\psionicList{Body Equilibrium}: You can walk on nonsolid surfaces.

\psionicList{Calm Emotions, Psionic}: Calms creatures, negating emotion effects.

\psionicList{Cloud Mind}: You erase knowledge of your presence from target's mind.

\psionicList{Concealing Amorpha}: Quasi-real membrane grants you concealment.

\psionicList{Concentrate Water}: Collects water from surrounding area.

\psionicList{Concussion Blast}\textsuperscript{A}: Deal 1d6 force damage to target.

\psionicList{Control Sound}: Create very specific sounds.

\psionicList{Detect Hostile Intent}: You can detect hostile creatures within 30 ft. of you.

\psionicList{Detect Life}: Reveals living creatures.

\psionicList{Ego Whip}\textsuperscript{A}: Deal 1d4 Cha damage and daze for 1 round.

\psionicList{Elfsight}: Gain low-light vision, +2 bonus on Search and Spot checks, and notice secret doors.

\psionicList{Energy Adaptation, Specified}\textsuperscript{A}: Gain resistance 10 against one energy type.

\psionicList{Energy Push}\textsuperscript{A}: Deal 2d6 damage and knock subject back.

\psionicList{Energy Stun}\textsuperscript{A}: Deal 1d6 damage and stun target if it fails both saves.

\psionicList{Feat Leech}\textsuperscript{A}: Borrow another's psionic or metapsionic feats.

\psionicList{Id Insinuation}\textsuperscript{A}: Swift tendrils of thought disrupt and confuse your target.

\psionicList{Identify, Psionic}: Learn the properties of a psionic item.

\psionicList{Inflict Pain}\textsuperscript{A}: Telepathic stab gives your foe -4 on attack rolls, or -2 if he makes the save.

\psionicList{Knock, Psionic}: Opens locked or psionically sealed door.

\psionicList{Levitate, Psionic}: Subject moves up and down at your direction.

\psionicList{Mental Disruption}\textsuperscript{A}: Daze creatures within 10 feet for 1 round.

\psionicList{Missive, Mass}\textsuperscript{A}: You send a one-way telepathic message to an area.

\psionicList{Molecular Bonding}: Temporarily glue two surfaces together.

\psionicList{Pheromone Discharge}: Vermin react well to you.

\psionicList{Psionic Lock}: Secure a door, chest, or portal.

\psionicList{Recall Agony}\textsuperscript{A}: Foe takes 2d6 damage.

\psionicList{Return Missile}\textsuperscript{A}: Make one weapon return to you after thrown.

\psionicList{Sense Link, Forced}: Sense what subject senses.

\psionicList{Sensory Suppression}: Victim loses one sense---sight, hearing, smell.

\psionicList{Sever the Tie}\textsuperscript{A}: Disrupt an undead's tie to the Gray, damaging or destroying it.

\psionicList{Share Pain}: Willing subject takes some of your damage.

\psionicList{Sustenance}: Go without food and water for one day.

\psionicList{Swarm of Crystals}\textsuperscript{A}: Crystal shards are sprayed forth doing 3d4 slashing damage.

\psionicList{Thought Shield}\textsuperscript{A}: Gain PR 13 against mind-affecting powers.

\psionicList{Tongues, Psionic}: You can communicate with intelligent creatures.

\psionicList{Watcher Ward}\textsuperscript{A}: You are aware of creature within the warded area.

\psionicList{Weather Prediction}: Predicts weather for next 24 hours.




\subsection{3rd-Level Psion/Wilder Powers}

\psionicList{Antidote Simulation}\textsuperscript{A}: Detoxifies venom in your system.

\psionicList{Beacon}\textsuperscript{A}: Creates a ball on light that can become much larger with concentration.

\psionicList{Blink, Psionic}\textsuperscript{A}: You randomly vanish and reappear for 1 round/level.

\psionicList{Body Adjustment}\textsuperscript{A}: You heal 1d12 damage.

\psionicList{Body Purification}\textsuperscript{A}: You restore 2 points of ability damage.

\psionicList{Danger Sense}\textsuperscript{A}: You gain +4 bonus against traps.

\psionicList{Darkvision, Psionic}: See 60 ft. in total darkness.

\psionicList{Dismiss Ectoplasm}: Dissipates ectoplasmic targets and effects.

\psionicList{Dispel Psionics}\textsuperscript{A}: Cancels psionic powers and effects.

\psionicList{Energy Bolt}\textsuperscript{A}: Deal 5d6 energy damage in 120-ft. line.

\psionicList{Energy Burst}\textsuperscript{A}: Deal 5d6 energy damage in 40-ft. burst.

\psionicList{Energy Retort}\textsuperscript{A}: Ectoburst of energy automatically targets your attacker for 4d6 damage once each round.

\psionicList{Energy Wall}: Create wall of your chosen energy type.

\psionicList{Eradicate Invisibility}\textsuperscript{A}: Negate invisibility in 50-ft. burst.

\psionicList{Keen Edge, Psionic}: Doubles normal weapon's threat range.

\psionicList{Lighten Load, Psionic}: Increases Strength for carrying capacity only.

\psionicList{Mass Manipulation}\textsuperscript{A}: Alter the weight of a creature or object.

\psionicList{Mental Barrier}\textsuperscript{A}: Gain +4 deflection bonus to AC until your next action.

\psionicList{Mind Trap}\textsuperscript{A}: Drain 1d6 power points from anyone who attacks you with a telepathy power.

\psionicList{Nerve Manipulation}\textsuperscript{A}: Disrupts a creature nervous system.

\psionicList{Psionic Blast}\textsuperscript{A}: Stun creatures in 30-ft. cone for 1 round.

\psionicList{Psionic Sight}\textsuperscript{A}: Psionic auras become visible to you.

\psionicList{Share Pain, Forced}\textsuperscript{A}: Unwilling subject takes some of your damage.

\psionicList{Solicit Psicrystal}\textsuperscript{A}: Your psicrystal takes over your concentration power.

\psionicList{Telekinetic Force}\textsuperscript{A}: Move an object with the sustained force of your mind.

\psionicList{Telekinetic Thrust}\textsuperscript{A}: Hurl objects with the force of your mind.

\psionicList{Time Hop}\textsuperscript{A}: Subject hops forward in time 1 round/level.

\psionicList{Touchsight}\textsuperscript{A}: Your telekinetic field tells you where everything is.

\psionicList{Ubiquitous Vision}: You have all-around vision.




\subsection{4th-Level Psion/Wilder Powers}

\psionicList{Aura Sight}\textsuperscript{A}: Reveals creatures, objects, powers, or spells of selected alignment axis.

\psionicList{Correspond}: Hold mental conversation with another creature at any distance.

\psionicList{Death Urge}\textsuperscript{A}: Implant a self-destructive compulsion.

\psionicList{Detect Remote Viewing}: You know when others spy on you remotely.

\psionicList{Detonate}\textsuperscript{A}: Explode one object.

\psionicList{Dimension Door, Psionic}: Teleports you short distance.

\psionicList{Divination, Psionic}: Provides useful advice for specific proposed action.

\psionicList{Empathic Feedback}\textsuperscript{A}: When you are hit in melee, your attacker takes damage.

\psionicList{Energy Adaptation}\textsuperscript{A}: Your body converts energy to harmless light.

\psionicList{Freedom of Movement, Psionic}: You cannot be held or otherwise rendered immobile.

\psionicList{Intellect Fortress}\textsuperscript{A}: Those inside fortress take only half damage from all powers and psi-like abilities until your next action.

\psionicList{Magnetize}\textsuperscript{A}: Make metallic object magnetic.

\psionicList{Mindwipe}\textsuperscript{A}: Subject's recent experiences wiped away, bestowing negative levels.

\psionicList{Personality Parasite}: Subject's mind calves self-antagonistic splinter personality for 1 round/level.

\psionicList{Power Leech}: Drain 1d6 power points/round while you maintain concentration; you gain 1/round.

\psionicList{Psychic Reformation}\textsuperscript{X}: Subject can choose skills, feats, and powers anew for previous levels.

\psionicList{Repugnance}: Make a creature repugnant to others.

\psionicList{Shadow Jump}\textsuperscript{A}: Jump into shadow to travel rapidly.

\psionicList{Telekinetic Maneuver}\textsuperscript{A}: Telekinetically bull rush, disarm, grapple, or trip your target.

\psionicList{Trace Teleport}\textsuperscript{A}: Learn destination of subject's teleport.

\psionicList{Wall of Ectoplasm}: You create a protective barrier.




\subsection{5th-Level Psion/Wilder Powers}

\psionicList{Adapt Body}: Your body automatically adapts to hostile environments.

\psionicList{Catapsi}\textsuperscript{A}: Psychic static inhibits power manifestation.

\psionicList{Ectoplasmic Shambler}: Foglike predator deals 1 point of damage/two levels each round to an area.

\psionicList{Electroerosion}\textsuperscript{A}: Create a ray that erodes iron and alloys.

\psionicList{Incarnate}\textsuperscript{X}: Make some powers permanent.

\psionicList{Leech Field}\textsuperscript{A}: Leech power points each time you make a saving throw.

\psionicList{Major Creation, Psionic}: As psionic minor creation, plus stone and metal.

\psionicList{Plane Shift, Psionic}: Travel to other planes.

\psionicList{Power Resistance}: Grant PR equal to 12 + level.

\psionicList{Psychic Crush}\textsuperscript{A}: Brutally crush subject's mental essence, reducing subject to -1 hit points.

\psionicList{Shatter Mind Blank}: Cancels target's mind blank effect.

\psionicList{Tower of Iron Will}\textsuperscript{A}: Grant PR 19 against mind-affecting powers to all creatures within 10 ft. until your next turn.

\psionicList{True Seeing, Psionic}: See all things as they really are.




\subsection{6th-Level Psion/Wilder Powers}

\psionicList{Aura Alteration}\textsuperscript{A}: Repairs psyche or makes subject seem to be something it is not.

\psionicList{Breath of the Black Dragon}\textsuperscript{A}: Breathe acid for 11d6 damage.

\psionicList{Cloud Mind, Mass}: Erase knowledge of your presence from the minds of one creature/level.

\psionicList{Co-opt Concentration}: Take control of foe's concentration power.

\psionicList{Contingency, Psionic}\textsuperscript{X}: Sets trigger condition for another power.

\psionicList{Dimensional Screen}: Create a shimmering screen that diverts attacks.

\psionicList{Disintegrate, Psionic}\textsuperscript{A}: Turn one creature or object to dust.

\psionicList{Fuse Flesh}\textsuperscript{A}: Fuse subject's flesh, creating a helpless mass.

\psionicList{Overland Flight, Psionic}: You fly at a speed of 40 ft. and can hustle over long distances.

\psionicList{Remote View Trap}: Deal 8d6 points electricity damage to those who seek to view you at a distance.

\psionicList{Retrieve}\textsuperscript{A}: Teleport to your hand an item you can see.

\psionicList{Suspend Life}: Put yourself in a state akin to suspended animation.

\psionicList{Temporal Acceleration}\textsuperscript{A}: Your time frame accelerates for 1 round.




\subsection{7th-Level Psion/Wilder Powers}

\psionicList{Decerebrate}: Remove portion of subject's brain stem.

\psionicList{Divert Teleport}: Choose destination for another's teleport.

\psionicList{Energy Conversion}: Offensively channel energy you've absorbed.

\psionicList{Energy Wave}\textsuperscript{A}: Deal 13d4 damage of your chosen energy type in 120-ft. cone.

\psionicList{Evade Burst}\textsuperscript{A}: You take no damage from a burst on a successful Reflex save.

\psionicList{Incorporeality}\textsuperscript{A}: You become incorporeal for 1 round/level.

\psionicList{Insanity}\textsuperscript{A}: Subject is permanently confused.

\psionicList{Mind Blank, Personal}: You are immune to scrying and mental effects.

\psionicList{Mindflame}: Kills, paralyzes, weakens, or dazes subjects.

\psionicList{Moment of Prescience, Psionic}: You gain insight bonus on single attack roll, check, or save.

\psionicList{Oak Body}\textsuperscript{A}: Your body becomes as hard as oak.

\psionicList{Phase Door, Psionic}: Invisible passage through wood or stone.

\psionicList{Sequester, Psionic}\textsuperscript{X}: Subject invisible to sight and remote viewing; renders subject comatose.

\psionicList{Ultrablast}\textsuperscript{A}: Deal 13d6 damage in 15-ft. radius.




\subsection{8th-Level Psion/Wilder Powers}

\psionicList{Bend Reality}\textsuperscript{X}: Alters reality within power limits.

\psionicList{Iron Body, Psionic}: Your body becomes living iron.

\psionicList{Matter Manipulation}\textsuperscript{X}: Increase or decrease an object's base hardness by 5.

\psionicList{Mind Blank, Psionic}: Subject immune to mental/emotional effects, scrying, and remote viewing.

\psionicList{Recall Death}: Subject dies or takes 5d6 damage.

\psionicList{Shadow Body}: You become a living shadow (not the creature).

\psionicList{Teleport, Psionic Greater}: As psionic teleport, but no range limit and no off-target arrival.

\psionicList{True Metabolism}: You regenerate 10 hit points/round.




\subsection{9th-Level Psion/Wilder Powers}

\psionicList{Affinity Field}: Effects that affect you also affect others.

\psionicList{Apopsi}\textsuperscript{X}: You delete target's psionic powers.

\psionicList{Assimilate}: Incorporate creature into your own body.

\psionicList{Etherealness, Psionic}: Become ethereal for 1 min./level.

\psionicList{Microcosm}\textsuperscript{A}: Creature or creature lives forevermore in world of his own imagination.

\psionicList{Reality Revision}\textsuperscript{X}: As bend reality, but fewer limits.

\psionicList{Timeless Body}: Ignore all harmful, and helpful, effects for 1 round.