\section{Psychic Warrior Powers}




\subsection{1st-Level Psychic Warrior Powers}

\psionicList{Astral Traveler}: Enable yourself or another to join an astral caravan-enabled trip.

\psionicList{Biofeedback}\textsuperscript{A}: Gain DR 2/--.

\psionicList{Bioflexibility}: Gain +10 competence bonus on \skill{Escape Artist} checks. %

\psionicList{Bite of the Wolf}: Gain bite attack for 1d8 damage.

\psionicList{Burst}: Gain +3 m to speed this round.

\psionicList{Call Weaponry}\textsuperscript{A}: Create temporary weapon.

\psionicList{Cast Missiles}: You can launch missiles without a bow or other weapon. %

\psionicList{Catfall}\textsuperscript{A}: Instantly save yourself from a fall.

\psionicList{Chameleon}: Gain +10 enhancement bonus on \skill{Hide} checks.

\psionicList{Claws of the Beast}\textsuperscript{A}: Your hands become deadly claws.

\psionicList{Compression}\textsuperscript{A}: You grow smaller.

\psionicList{Conceal Thoughts}: You conceal your motives.

\psionicList{Deflect Strike}: You psychokinetically deflect the next attack of a creature within range. %

\psionicList{Detect Psionics}: You detect the presence of psionics.

\psionicList{Dissipating Touch}\textsuperscript{A}: Touch deals 1d6 damage.

\psionicList{Distract}: Subject gets -4 on Listen, Search, Sense Motive, and Spot checks.

\psionicList{Elfsight}: Gain low-light vision, +2 bonus on Search and Spot checks, and notice secret doors.

\psionicList{Empty Mind}\textsuperscript{A}: Gain +2 on Will saves until your next action.

\psionicList{Expansion}\textsuperscript{A}: Become one size category larger.

\psionicList{Float}: Buoy yourself in water or other liquid.

\psionicList{Force Screen}\textsuperscript{A}: Invisible disc provides +4 shield bonus to AC.

\psionicList{Grip of Iron}\textsuperscript{A}: Your iron grip gives +4 bonus on grapple checks.

\psionicList{Hammer}\textsuperscript{A}: Melee touch attack deals 1d8/round.

\psionicList{Inertial Armor}\textsuperscript{A}: Tangible field of force provides you with +4 armor bonus to AC.

\psionicList{Metaphysical Claw}\textsuperscript{A}: Your natural weapon gains +1 bonus.

\psionicList{Metaphysical Weapon}\textsuperscript{A}: Weapon gains +1 bonus.

\psionicList{My Light}\textsuperscript{A}: Your eyes emit 6-m cone of light.

\psionicList{Precognition, Defensive}\textsuperscript{A}: Gain +1 insight bonus to AC and saving throws.

\psionicList{Precognition, Offensive}\textsuperscript{A}: Gain +1 insight bonus on your attack rolls.

\psionicList{Prescience, Offensive}\textsuperscript{A}: Gain +2 insight bonus on your damage rolls.

\psionicList{Prevenom Weapon}\textsuperscript{A}: Your weapon is mildly venomous.

\psionicList{Prevenom}\textsuperscript{A}: Your claws gain a poison coating.

\psionicList{Psionic Draw}: Instantly draw a weapon. %

\psionicList{Skate}: Subject slides skillfully along the ground.

\psionicList{Stomp}\textsuperscript{A}: Subjects fall prone and take 1d4 nonlethal damage.

\psionicList{Synesthete}: You receive one kind of sense when another sense is stimulated.

\psionicList{Tattoo Animation}\textsuperscript{A}: Animates your tattoos or steals another's. %

\psionicList{Thicken Skin}\textsuperscript{A}: Gain +1 enhancement bonus to your AC for 10 min./level.

\psionicList{Vigor}\textsuperscript{A}: Gain 5 temporary hit points.

\psionicList{Wild Leap}\textsuperscript{A}: Make an additional leap and gain a bonus to Jump checks. %




\subsection{2nd-Level Psychic Warrior Powers}

\psionicList{Animal Affinity}\textsuperscript{A}: Gain +4 enhancement to one ability.

\psionicList{Antidote Simulation}\textsuperscript{A}: Detoxifies venom in your system. %

\psionicList{Body Adjustment}\textsuperscript{A}: Heal 1d12 damage.

\psionicList{Body Equilibrium}: You can walk on nonsolid surfaces.

\psionicList{Body Purification}\textsuperscript{A}: Restore 2 points of ability damage.

\psionicList{Concealing Amorpha}: Quasi-real membrane grants you concealment.

\psionicList{Darkvision, Psionic}: See 60 ft. in total darkness.

\psionicList{Detect Hostile Intent}: You can detect hostile creatures within 30 ft. of you.

\psionicList{Dimension Swap}\textsuperscript{A}: You and an ally switch positions.

\psionicList{Dissolving Touch}\textsuperscript{A}: Your touch deals 4d6 acid damage.

\psionicList{Dissolving Weapon}\textsuperscript{A}: Your weapon deals 4d6 acid damage.

\psionicList{Empathic Transfer}\textsuperscript{A}: Transfer another's wounds to yourself.

\psionicList{Energy Adaptation, Specified}\textsuperscript{A}: Gain resistance 10 to one energy type.

\psionicList{Feat Leech}\textsuperscript{A}: Borrow another's psionic or metapsionic feats.

\psionicList{Hustle}: Instantly gain a move action.

\psionicList{Levitate, Psionic}: Subject moves up and down at your direction.

\psionicList{Lion's Charge, Psionic}\textsuperscript{A}: You can make full attack in same round you charge.

\psionicList{Painful Strike}\textsuperscript{A}: Your natural weapons deal an extra 1d6 nonlethal damage.

\psionicList{Prowess}: Instantly gain another attack of opportunity.

\psionicList{Psionic Scent}: Gain the scent ability.

\psionicList{Return Missile}\textsuperscript{A}: Make one weapon return to you after thrown. %

\psionicList{Share Strength}\textsuperscript{A}: Temporarily transfer your Strength to another. %

\psionicList{Strength of My Enemy}\textsuperscript{A}: Siphon away your enemy's strength and grow stronger.

\psionicList{Sustenance}: You can go without food and water for one day.

\psionicList{Thought Shield}\textsuperscript{A}: Gain PR 13 against mind-affecting powers.

\psionicList{Wall Walker}: Grants ability to walk on walls and ceilings.



\subsection{3rd-Level Psychic Warrior Powers}

\psionicList{Accelerate}\textsuperscript{A}: Move faster, +1 on attack rolls, AC, and Reflex saves. %

\psionicList{Claws of the Vampire}: Heal half of your claw's base damage.

\psionicList{Concealing Amorpha, Greater}: Quasi-real membrane grants you total concealment.

\psionicList{Danger Sense}\textsuperscript{A}: Gain +4 bonus against traps.

\psionicList{Death Field}\textsuperscript{A}: Release an energy burst from the Gray that drains vital energy. %

\psionicList{Dimension Slide}\textsuperscript{A}: Teleports you very short distance.

\psionicList{Duodimensional Claw}: Increases your natural weapon's threat range.

\psionicList{Ectoplasmic Form}: You gain benefits of being insubstantial and can fly slowly.

\psionicList{Empathic Feedback}\textsuperscript{A}: When you are hit in melee, your attacker takes damage.

\psionicList{Empathic Transfer, Hostile}\textsuperscript{A}: Your touch transfers your hurt to another.

\psionicList{Escape Detection}: You become difficult to detect with clairsentience powers.

\psionicList{Evade Burst}\textsuperscript{A}: You take no damage from a burst on a successful Reflex save.

\psionicList{Exhalation of the Black Dragon}\textsuperscript{A}: Your acid breath deals 3d6 damage to a close target.

\psionicList{Graft Weapon}: Your hand is replaced seamlessly by your weapon.

\psionicList{Keen Edge, Psionic}: Doubles normal weapon's threat range.

\psionicList{Mental Barrier}\textsuperscript{A}: Gain +4 deflection bonus to AC until your next action.

\psionicList{Ubiquitous Vision}: You have all-around vision.

\psionicList{Vampiric Blade}: You heal half of your base weapon damage.




\subsection{4th-Level Psychic Warrior Powers}

\psionicList{Claw of Energy}: Your claws deal additional energy damage.

\psionicList{Dimension Door, Psionic}: Teleports you short distance.

\psionicList{Energy Adaptation}\textsuperscript{A}: Your body converts energy to harmless light.

\psionicList{Freedom of Movement, Psionic}: You cannot be held or otherwise rendered immobile.

\psionicList{Immovability}\textsuperscript{A}: You are almost impossible to move and gain DR 15/-.

\psionicList{Inertial Barrier}: Gain DR 5/--.

\psionicList{Psychic Vampire}: Touch attack drains 2 power points/level from foe.

\psionicList{Shadow Jump}\textsuperscript{A}: Jump into shadow to travel rapidly. %

\psionicList{Steadfast Perception}: Gain immunity to illusory effects, +6 bonus on \skill{Spot} and \skill{Search} checks.

\psionicList{Truevenom}: Your natural weapons are covered in horrible poison.

\psionicList{Truevenom Weapon}: Your weapon is horribly poisonous.

\psionicList{Weapon of Energy}: Weapon deals additional energy damage.




\subsection{5th-Level Psychic Warrior Powers}

\psionicList{Adapt Body}: Your body automatically adapts to hostile environments.

\psionicList{Catapsi}\textsuperscript{A}: Psychic static inhibits power manifestation.

\psionicList{Metaconcert}\textsuperscript{A}: Mental concert of two or more increases the total power of the participants.

\psionicList{Nerve Manipulation}\textsuperscript{A}: Disrupts a creature nervous system. %

\psionicList{Oak Body}\textsuperscript{A}: Your body becomes as hard as oak.

\psionicList{Psychofeedback}: Boost Str, Dex, or Con at the expense of one or more other scores.




\subsection{6th-Level Psychic Warrior Powers}

\psionicList{Breath of the Black Dragon}\textsuperscript{A}: Breathe acid for 11d6 damage.

\psionicList{Dispelling Buffer}: You are buffered from one \psionic{dispel psionics} effect.

\psionicList{Form of Doom}\textsuperscript{A}: You transform into a frightening tentacled beast.

\psionicList{Mind Blank, Personal}: You are immune to scrying and mental effects.

\psionicList{Poison Simulation}\textsuperscript{A}: Coat surface with potent poisons. %

\psionicList{Suspend Life}: Put yourself into a state akin to suspended animation.
