\subsubsection{Snake, Giant Constrictor}
\begin{MonsterStats}
{Huge Animal}
{11d8+14 (63 hp)}
{+3}
{6 m (4 squares), climb 6 m, swim 6 m}
{15 ($-2$ size, +3 Dex, +4 natural), touch 11, flat-footed 12}
{+8/+23}
{Bite +13 melee (1d8+10)}
{Bite +13 melee (1d8+10)}
{4.5 m/3 m}
{Constrict 1d8+10, improved grab}
{Scent}
{Fort +8, Ref +10, Will +4}
{Str 25, Dex 17, Con 13, Int 1, Wis 12, Cha 2}
{\skill{Balance} +11, \skill{Climb} +17, \skill{Hide} +10, \skill{Listen} +9, \skill{Spot} +9, \skill{Swim} +16}
{\feat{Alertness}, \feat{Endurance}, \feat{Skill Focus} (\skill{Hide}), \feat{Toughness}}
{Warm forests}
{Solitary}
{5}
{None}
{Always neutral}
{12--16 HD (Huge); 17--33 HD (Gargantuan)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Giant constrictor snakes are more aggressive than their smaller cousins, principally because they need a great amount of food to survive.
}

Constrictor snakes hunt by grabbing prey with their mouths and then squeezing it with their powerful bodies.

\textbf{Constrict (Ex):} On a successful grapple check, a giant constrictor snake deals 1d8+10 points of damage.

\textbf{Improved Grab (Ex):} To use this ability, a giant constrictor snake must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can constrict.

\textbf{Skills:} Snakes have a +4 racial bonus on \skill{Hide}, \skill{Listen}, and \skill{Spot} checks and a +8 racial bonus on \skill{Balance} and \skill{Climb} checks.

A snake can always choose to take 10 on a \skill{Climb} check, even if rushed or threatened.

Snakes use either their Strength modifier or Dexterity modifier for \skill{Climb} checks, whichever is higher.

A snake has a +8 racial bonus on any \skill{Swim} check to perform some special action or avoid a hazard. It can always choose to take 10 on a \skill{Swim} check, even if distracted or endangered. It can use the run action while swimming, provided it swims in a straight line.
