\subsubsection{Face}


\textbf{Eyes of Charming:} These two crystal lenses fit over the user's eyes. The wearer is able to use \spell{charm person} (one target per round) as a gaze attack. Those failing a DC 16 Will save are charmed as per the spell. If the wearer has only one lens, the DC of the saving throw is reduced to 10.

Moderate enchantment; CL 7th; \feat{Craft Wondrous Item}, \feat{Heighten Spell}, \spell{charm person}; Price 56,000 cp for a pair.


\textbf{Eyes of Doom:} These crystal lenses fit over the user's eyes, enabling him to cast \spell{doom} upon those around him (one target per round) as a gaze attack, except that the wearer must take a standard action, and those merely looking at the wearer are not affected. Those failing a DC 11 Will save are affected as by the \spell{doom} spell. If the wearer has only one lens, the DC of the saving throw is reduced to 10. However, if the wearer has both lenses, he gains the additional power of a continual \spell{deathwatch} effect and can use \spell{fear} (Will DC 16 partial) as a normal gaze attack once per week.

Moderate necromancy; CL 11th; \feat{Craft Wondrous Item}, \spell{doom}, \spell{deathwatch}, \spell{fear}; Price 25,000 cp.


\textbf{Eyes of the Eagle:} These items are made of special crystal and fit over the eyes of the wearer. These lenses grant a +5 competence bonus on \skill{Spot} checks. Wearing only one of the pair causes a character to become dizzy and, in effect, stunned for 1 round. Thereafter, the wearer can use the single lens without being stunned so long as she covers her other eye. Of course, she can remove the single lens and see normally at any time, or wear both lenses to end or avoid the dizziness.

Faint divination; CL 3rd; \feat{Craft Wondrous Item}, \spell{clairaudience/clairvoyance}; Price 2,500 cp.


\textbf{Eyes of Petrification:} These items are made of special crystal and fit over the eyes of the wearer. They allow her to use a petrification gaze attack (Fortitude DC 19 negates) for 10 rounds per day. Both lenses must be worn for the magic to be effective.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{flesh to stone}; Price 98,000 cp.


\textbf{Goggles of Minute Seeing:} The lenses of this item are made of special crystal. When placed over the eyes of the wearer, the lenses enable her to see much better than normal at distances of 30 centimeters or less, granting her a +5 competence bonus on \skill{Search} checks to find secret doors, traps, and similar concealed objects. Both lenses must be worn for the magic to be effective.

Faint divination; CL 3rd; \feat{Craft Wondrous Item}, \spell{true seeing}; Price 1,250 cp.


\textbf{Goggles of Night:} The lenses of this item are made of dark crystal. Even though the lenses are opaque, when placed over the eyes of the wearer they enable him to see normally and also grant him 18-meter darkvision. Both lenses must be worn for the magic to be effective.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{darkvision}; Price 12,000 cp.


\textbf{Mask of the Skull:} This ivory mask has been fashioned into the likeness of a human skull. Once per day, after it has been worn for at least 1 hour, the mask can be loosed to fly from the wearer's face. It travels up to 15 meters away from the wearer and attacks a target assigned to it. The grinning skull mask makes a touch attack against the target based on the wearer's base attack bonus. If the attack succeeds, the target must make a DC 20 Fortitude save or be struck dead, as if affected by a finger of death spell. If the target succeeds on his saving throw, he nevertheless takes 3d6+13 points of damage. After attacking (whether successful or not), the mask flies back to its user. The mask has AC 16, 10 hit points, and hardness 6.

Strong necromancy and transmutation; CL 13th; \feat{Craft Wondrous Item}, \spell{animate objects}, \spell{finger of death}, \spell{fly}; Price 22,000 cp; Weight 1.5 kg.

