\subsubsection{Use Special Ability}
Using a special ability is usually a standard action, but whether it is a standard action, a full-round action, or not an action at all is defined by the ability.

\textbf{Spell-Like Abilities:} Using a spell-like ability works like casting a spell in that it requires concentration and provokes attacks of opportunity. Spell-like abilities can be disrupted. If your concentration is broken, the attempt to use the ability fails, but the attempt counts as if you had used the ability. The casting time of a spell-like ability is 1 standard action, unless the ability description notes otherwise.

\textit{Using a Spell-Like Ability on the Defensive:} You may attempt to use a spell-like ability on the defensive, just as with casting a spell. If the \skill{Concentration} check (DC 15 + spell level) fails, you can't use the ability, but the attempt counts as if you had used the ability.

\textbf{Supernatural Abilities:} Using a supernatural ability is usually a standard action (unless defined otherwise by the ability's description). Its use cannot be disrupted, does not require concentration, and does not provoke attacks of opportunity.

\textbf{Extraordinary Abilities:} Using an extraordinary ability is usually not an action because most extraordinary abilities automatically happen in a reactive fashion. Those extraordinary abilities that are actions are usually standard actions that cannot be disrupted, do not require concentration, and do not provoke attacks of opportunity.