\subsubsection{Full Attack}
If you get more than one attack per round because your base attack bonus is high enough, because you fight with two weapons or a double weapon or for some special reason you must use a full-round action to get your additional attacks. You do not need to specify the targets of your attacks ahead of time. You can see how the earlier attacks turn out before assigning the later ones.

The only movement you can take during a full attack is a 1.5-meter step. You may take the step before, after, or between your attacks.

If you get multiple attacks because your base attack bonus is high enough, you must make the attacks in order from highest bonus to lowest. If you are using two weapons, you can strike with either weapon first. If you are using a double weapon, you can strike with either part of the weapon first.

\textbf{Deciding between an Attack or a Full Attack:} After your first attack, you can decide to take a move action instead of making your remaining attacks, depending on how the first attack turns out. If you've already taken a 1.5-meter step, you can't use your move action to move any distance, but you could still use a different kind of move action.

\textbf{Fighting Defensively as a Full-Round Action:} You can choose to fight defensively when taking a full attack action. If you do so, you take a $-4$ penalty on all attacks in a round to gain a +2 dodge bonus to AC for the same round.

\textbf{Cleave:} The extra attack granted by the \feat{Cleave} feat or \feat{Great Cleave} feat can be taken whenever they apply. This is an exception to the normal limit to the number of attacks you can take when not using a full attack action.