\SubCity{Pterran Vale}
{4,000 (99\% pterran, 1\% other)}
{bones tools, livestock}
{Pterran}
{
	Pterran Vale is the largest community of civilized pterrans in the Hinterlands. The buildings are lodges constructed from the bones and hides of large creatures, such as mekillots, built over hollowed out pits. Each building has steps leading down into the interior.
}
{
	The pterrans of Pterran Vale survive by hunting, farming, and herding. In addition to using bone in the construction of their buildings, they make fine bone weapons and tools.

	Each pterran must choose a life path when they come of age. There are three main Life Paths, the Path of the Warrior, the Path of the Druid, and the Path of the Psion. However, other lesser Life Paths, farmer, crafter, traders, and herders, also exist. Those pterrans following one of the lesser Life Paths are treated with respect but the three primary Life Paths are more prestigious. All leaders are in pterran society are selected from the primary Life Paths.

	The pterrans revere Athas as the Earth Mother, and their religious ceremonies and celebrations are devoted to her. After the Great Earthquake, the pterrans became convinced that the earthquake was a call from the Earth Mother to them, directing them to become more involved with the affairs of others. In response, explorers have been sent out resulting in contact with the city-state of Tyr on the other side of the Ringing Mountains. Trade routes are being established with Tyr and areas beyond.
}
{
	As in all pterran communities, Pterran Vale is lead by a Triumvirate. The Triumvirate is made up of the eldest member from each of the three primary Life Paths. The Triumvirate has the power to make all decisions for the community. However, before important decisions are made the entire community gathers to debate the question in front of the Triumvirate. Only after all pterrans have had their say does the Triumvirate make their decision.
}
{
	\textbf{Traders:} Recently, the prestige of the merchants of Pterran Vale, lead by Ptellac Goldeye, has been growing. Since they are at the forefront of the pterrans' new push to make contact with civilizations outside of their vale, the traders have become well respected. In addition, the new trade routes they have developed to the cities of the Tablelands have brought them increased wealth.

	The traders are not an organized group as yet. Thought the different merchants are business rivals some have begun to recognize their new found status and how if they united, they could exert significant influence over the pterran society of the Hinterlands.
}
{
	\textbf{Lost Scale (Small Town, 2,000):} Centuries ago, a religious dispute resulted in a schism in Pterran Vale. One group found itself in the minority and chose to leave Pterran Vale and establish their own community, and founding Lost Scale. Today the disagreement has long been settled and the two communities work together.

	Lost Scale is noted for its legion of expert pterrax riders. Each of these warriors searches rocky badlands and canyons for a pterrax egg. The baby pterrax that hatches is raised and trained from birth by its rider.
}
{}
{
	\item After the success of Ptellac Goldeye's effort to make contact with the cities of the Tablelands, the leaders of Pterran Vale have decided to send emissaries to the south, where rumors state long lost communities of pterrans exist. While the rumors are indeed true, the pterrans of the south have long ago degenerated into barbarism and cannibalism, making the expedition fraught with peril.
	\item Pterran scouts have witnessed thri-kreen with unusual coloration herding trin packs into a large enclosure in the desert. Concerned as to who these strange thri-kreen are and why they are herding trin, the leaders of Pterran Vale send the PCs to investigate.
	\item The crops in the fields around Pterran Vale are not growing as healthily as they normal do. The farmers quickly discovered why. Blood grass has sprouted up throughout the fields, stealing nutrients from the crops and attacking farmers who approach too close. Adventurers are needed to clear the blood grass from the fields, as well as discover how the blood grass came to be there in the first place.
	\item The pterrax riders of Lost Scale are having a problem locating pterrax eggs. It seems the pterrax have been driven from their normal nesting areas by an unusually large concentration of giant hornets. The pterrans hope the PCs can kill or drive off enough giant hornets to reduce the number to a balanced level so that the pterrax could return to their nesting area.
	\item The Dark One is a pterran outcast from Pterran Vale. An earth cleric, the Dark One was exiled for claiming the Great Earthquake and the aftershocks were calls from the Earth Mother demanding sacrifices of young pterrans. Now a hermit in the wilderness, the Dark One believes he has developed direct communication with the Earth Mother through a large hole in the ground. At the direction of the voice from this hole, the Dark One makes sacrifices to the Earth Mother by kidnapping and throwing pterrans into the hole. However, the Dark One is being manipulated by an earth drake, who poses as the Earth Mother to have the Dark One drop food into its lair.
	\item A pack of dune freaks have migrated to an oasis near Pterran Vale, posing a hazard to travelers going north. The PCs could be asked to clean out the dune freaks; however, they are only a lesser evil. The dune freaks were forced out of their normal hunting grounds by the increased patrols of zik-trin coming from the Great Rift.
}
