\SubCity{Thamasku}
{12,000 (99\% rhul-thaun, 1\% other)}
{Life-shapes, fish}
{Rhul-thaun}
{
	The ancient rhul-thaun city of Thamasku sits next to Ghavin Lake a t the top of the Jagged Cliffs. The city is surrounded by a forest of hardwood trees. Like all rhul-thaun communities, the buildings are constructed of organically grown material. The architecture focuses on the vertical, with most buildings having many storeys. There is one difference from other rhul-thaun settlements. Because the city is not cramped onto a ledge of the Jagged Cliffs, the buildings of Thamasku are not crowded together allowing for wider streets and a more open feel for the city.
}
{
Rhul-thaun society is highly ritualized. Each aspect of their lives has a ritual attached to it, and throughout the day the rhul-thaun perform various rituals. Simple rituals from the greeting ritual to the payment ritual, to the before meal ritual last less than a minute, while more complex rituals such as those for legal procedures may last hours. Often the ritual is just as or more important than the associated action it is attached to, and if one of the participants makes a mistake the entire ritual is begun again. The rituals are more akin to superstitions than to a religious devotion, and allow a rhul-thaun to feel he has some control over the chaotic forces that rule his life.

As the center of the rhul-thaun society, Thamasku has a diverse population. The wealthiest rhul-thaun live side by side with the poorest of the cliff dwellers. The citizens of Thamasku are some of the few individuals on Athas who do not have to struggle daily to survive. Life-shaped devices provide a vast array of conveniences and basic needs, from nourishment to waste disposal. Most homes have indoor plumbing, operated by life-shaped engines that pump water from the lake.

Because they do not struggle daily for survival, the rhul-thaun of Thamasku have developed a rich culture of the arts and entertainment. Dance halls, theaters, art galleries, and auditoriums are numerous throughout the city, with many located in the Art Quarter on the city's eastern side.
}
{
	The rhul-thaun of Thamasku are divided into 28 different clans. The clan leaders are called Har-etuil. The Har-etuil act as judges for matters within their clans. Disputes between clans are settled by a council of Har-etuil. The collective of Har-etuil appoints the city administrator.

	Currently, Vher-asach (LN female rhul-thaun, rogue 10) holds the title of city administrator, since she inherited the position from her mother. She has proved herself a capable administrator and most expect she will remain in the position for the time being.
}
{
	\textbf{Ban-ghesh}: A guild of thieves, assassins, and hired thugs, the ban-ghesh runs the criminal activities in Thamasku. Extortion is the guild's main source of income, though their activities include burglary, smuggling, and gambling. There is little to challenge the ban-ghesh as they have a network of corrupt lawkeepers and administrative officials protecting their organization. The ban-ghesh also enters into legitimate business with merchants, providing financial support in exchange for a percentage of the merchant's profits.

	\textbf{Chahn}: The Chahn is a revolutionary organization which does not hesitate to use violence to achieve their goals. Their goal is the complete overthrow of rhul-thaun society. The Chahn are against almost every tradition in rhul-thaun society from clan-rule, the mastery of the life-shapers, to the daily rituals that dominate rhul-thaun life. The lawkeepers have branded them a terrorist group and most rhul-thaun live in fear of them.

	\textbf{Life-Shapers}: The life-shapers are a secret society that holds the knowledge of life-shaped creations. They hold a place of reverence by the rhul-thaun as the entire society is based on their works. Through the study of life-shaping the life-shapers feel a strong connection with the past back to the rhulisti, the inventors of life-shaping. The life-shapers feel they are superior to the rest of the rhul-thaun, because of this connection.

	The life-shapers guard their knowledge protectively, letting no one outside of their order learn their secrets. Because they control the creation of all life-shaped items the life-shapers can exert control over the all of the rhul-thaun, forcing the Har-etuil to listen to the life-shapers' opinions strongly.

	The life-shapers are led by Loi Far-oneth (LG male rhul-thaun, bard 7/life-shaper 5) and his chief lieutenant, Gil-ogres (LE male rhul-thaun, rogue 5/graftwarrior 7), who reside at the Sanctuary in Thamasku. Each rhul-thaun settlement has a life-shaper sanctuary with a head life-shaper who reports directly to Loi Far-oneth and his lieutenant.

	\textbf{Windriders}: Windrider is the name given to the rhul-thaun who dare to fly on the backs of various life-shaped creatures through the high winds and mist that plague the Jagged Cliff. Traveling between the rhul-thaun communities, they transport messages and merchant goods, allowing trade and communication between all their settlements. Windrider is the most glamorous position in rhul-thaun society. Though there is a windriders guild, it maintains a loose organization with little structure or hierarchy. The windriders typically work in small independent groups of 2 to 8 windriders.
}
{
	\textbf{Sol-fehn (Hamlet, 300)}: Sol-fehn is a small village located at the top of a waterfall created by a river flowing from Ghavin Lake. The village serves as a hub for goods and rhul-thaun leaving Thamasku for the rest of the settlements scattered across the Jagged Cliffs. Almost all of the villagers make their living through transportation. The villagers are members of two clans that are centered in the city of Thamasku, so there is no Har-etuil in the village. An administrator appointed by the administrator of Thamasku runs the city. The current administrator is Rath-omak (LN male rhul-thaun, fighter 5).
}
{
	\textbf{Air Temple}: The air temple is located in one of the tallest of the city's spires. A dozen clerics of air staff the temple, but they have little interaction with most of the city's population. There are few devout followers in the city, and the clerics take no interest in politics. The air clerics do interact with the windriders regularly. In fact they have turned their temple into a safehome for windriders, where they can receive free food, a free room and lodging for their mounts. The clerics look on windriding as the ideal way to commune with the air spirits and treat the windriders as holy men.

	\textbf{Aviary}: The tall tower known as the aviary is home to hundreds of birds that fly about the city. The eclectic rhul-thaun known only as the Birdmaster cares for and watches over the birds. The tower is large enough for large flying creatures to roost there, and the Birdmaster allows windriders to stable their mounts at the aviary for free when in the city.

	\textbf{Conclave}: The Conclave is the meeting hall of the Har-etuil. It is a grand structure that sees little use when the Har-etuil council is not in session.

	\textbf{The Sanctuary}: The Sanctuary is the headquarters and workplace of the life-shapers in Thamasku. The mushroom shaped structure is located some 300 feet below the surface of Ghavin Lake. This masterpiece of life-shaping technology maintains fresh air within the structure by extracting it from the surrounding water through a complex gill-system. Over 150 life-shapers work at the Sanctuary creating and maintaining the life-shaped items that are used throughout Thamasku.
}
{
	\item No one has seen the Birdmaster of Thamasku for many weeks, but because of his reclusive nature, few citizens have realized this. So why are some of his birds following the PCs everywhere they go? Are the birds trying to send the PCs a message?
	\item The Ban-ghesh claim they have managed to infiltrate the Sanctuary of Thamasku and steal a wonderful new type of life-shaped item. There are rumors that the Ban-ghesh plan to sell this new item to the Chahn. The life-masters hire the PCs to recover the stolen item. The life-masters are unconcerned with the item falling into the hands of the Chahn, because there is really nothing extraordinary about the item. It is simply an unfinished common life-shaped tool. The life-masters are more concerned about the slight of someone stealing from the Sanctuary.
	\item A high-level reggelid believes that the secrets of Rajaat may be hidden in Thamasku. He has charmed a rhul-thaun climber named Bal-orean, and sent him to the rhul-thaun capital. The reggelid seeks to create a web of charmed agents throughout the city, and so has Bal-orean lure other rhul-thaun to a secluded part of the Jagged Cliffs where the reggelid has its lair. Once there the victim is charmed and sent back to Thamasku, as the reggelid attempts to create a spy network in Thamasku to root out the location of Rajaat's secrets.
	\item A wealthy benefactor hires the PCs to accompany him on a journey down the Jagged Cliffs to the Crimson Savanna to recover a long lost life-shaped artifact hidden on the Savanna. Their employer is not who he claims to be however. Taen-ofuth is really the high priest of the forbidden temple of fire in Thamasku. Frustrated with his lack of opportunity to demonstrate his devotion to his element, Taen-ofuth desires to travel to the Crimson Savanna to set a massive brush fire. He seeks to revel in the fire's destruction but also hopes to impress other rhul-thaun into seeing the benefits of devotion to the element of fire.
	\item Two weeks ago, a windrider arrived at the air temple and went immediately into a private meeting with Thim-obec, high priest of the temple. Two days later, Thim-obec left Thamasku with the windrider and a high ranking life-master on the windrider's gon-evauth. They have not been seen since, and the temple of air is seeking adventurers to find the high priest.
	\item Ghoun-awir is famous windancer, known throughout Thamasku for her daring performances. After a recent performance, a wealthy citizen claimed that Ghoun-awir is a thief and burglarized his home during her performance. The citizen's home was used as part of the performance. Ghoun-awir proclaimed her innocence before the lawkeepers arrived, but when they tried to arrest her she escaped. Since windancers wear face paint and costumes, no one is sure what Ghoun-awir really looks like. PCs could be hired to track Ghoun-awir down, or Ghoun-awir could approach the PCs to help prove her innocence by finding the true criminal.
}