\subsection{House Stel}
\textbf{Location:} Urik.

\textbf{Banner:} A pair of crossed black scimitars on a white field.

\textbf{Trade Goods:} Slaves, iron, gold, weapons, plundered items.

\textbf{Troops:} 3,000+ soldiers (3rd level or higher).

Closely associated with the warrior culture of Urik, Stel is without question the most aggressive and militaristic of the merchant houses. While Stel also maintains regular trade routes (albeit heavily guarded ones) and engages in ordinary trade, the house is best known for their specialization in the spoils of war.

\subsubsection{Brief History}
No one who lives in Urik for any amount of time remains unaffected by the city's omnipresent militarism; House Stel is no exception. Founded by a small group of warriors and gladiators nearly 300 years ago, and led by a soldier of fortune named Korvo Stel, the house would not have lasted long without the assistance and good will of the sorcerer-king.

Korvo built up an impressive trade house whose bases, outposts, and caravans were organized along strict military lines. But what the House Stel had in military strength, they lacked in business insight---they had little talent for selecting profitable cargoes or for managing the money the caravans brought in.

After several years of hiring outsiders to help the House's financial disaster, Iol, leader of Korvo's advisors and a talented psionicist, came to Korvo with an ultimatum. He wanted to be made a full partner in House Stel, and his fellows to be made part owners as well. Korvo eventually agreed, and within a decade following his mysterious death, Iol had taken the name Stel and was head of the household.

Today, the descendants of Iol and Korvo continue to control the house. Any bad blood that might once have existed has been swept away by the affection and brotherhood engendered by a far greater force---prosperity. Many competitors consider House Stel to be little more than a nest of bandits masquerading under the guise of a legitimate trading house, but the good will between the house and most sorcerer-kings keeps Stel in business.

\subsubsection{Stel's Assets}
House Stel deals in the usual variety of trade goods---in fact, most of its wealth is brought in by traditional items, such as weapons, ceramics, and especially iron from Tyr, a vital item for Urik's war industries. Stel is best known, however, for trading in items seized during Urik's conquests---slaves, gold, and a miscellany of stolen cargoes.

\textbf{Caravans:} House Stel has 20 to 30 caravans traveling at the same time. These caravans are slow and heavily guarded, under the strict command of the caravan master, with numerous guards and missile-armed skirmishers. Mekillot wagons, often loaded more with soldiers than cargo and mounting ballistae and even an occasional catapult, are favored. These are accompanied by swift crodlu cavalry and slave archers under whip-wielding mul or half-giant guards. A typical caravan includes up to ten wagons of various sizes (larger wagons are favored) and up to 100 foot soldiers and 30 to 40 cavalrymen.

\textbf{Facilities:} Outposts, trade villages, and the house headquarters in Urik are all built like fortresses. They are sometimes hired out as such, when sorcerer-kings or nomads wish a secure base of operations.

\textit{Fort Courage:} 150 employees, 200 slaves. Supply point and military base near the Smoking Crown on the route between Urik and Makla.

\textit{Fort Iron:} 75 employees, 100 slaves. Supply point and military base 45 kilometers west of Silver Spring. This base represented an important advance position during the recent war between Urik and Tyr.

\textit{Fort Sandol:} 20 employees, 50 slaves. Outpost and trading post in the Tablelands, approximately 50 miles north of Gulg. This distant, lonely outpost occasionally services caravans, but its primary function is as a trading post for the various nomads who travel throughout the Tablelands. Nomads of all races may be found here, selling artwork, weapons, or slaves taken in raids.

\subsubsection{House Stel in Athas}
Stel's aggressive policies and militaristic nature have made more than a few enemies among their fellow merchants. House Tsalaxa, with its long memory for slights, is a particularly vehement enemy, as is House Inika, whose caravans have been raided and trade routes plundered far too often. Neutral relations are maintained with House Wavir, with a tacit agreement that the two powerful houses will not interfere with each other, lest disaster befall them both.

Stel's attitude toward the elven houses and small traders is nothing short of murderous. Stel's leaders are known to harbor a deep dislike of nonhumans in general and elves in particular. In contrast, Stel maintains good relations with all of the sorcerer-kings, particularly those of Urik, Raam, and Draj, which lie along Stel's major trade routes. City law is obeyed to the letter, and Stel never engages in smuggling or trade in illegal items.

\subsubsection{Stel Lore}
Characters with ranks in \skill{Knowledge} (local [Urik]) or \skill{Gather Information} can research House Stel to learn more about it. When a character makes a skill check, read or paraphrase the following, including the information from lower DCs.

\textbf{DC 10:} House Stel is the major merchant house in Urik.

\textbf{DC 15:} Stel is dedicated in slaves, iron, gold, weapons, plundered items. Sometimes they rent their outposts and trade villages as fortress, when sorcerer-kings or nomads wish a secure base of operations.

\textbf{DC 20:} Their caravans are slow and heavily guarded, often loaded more with soldiers than cargo. They maintain a strict chain of command, with superior officers taking responsibility for the actions of those under them and underlings accepting orders without question.

\textbf{DC 25:} King Hamanu often lends the services of his elite troops or even, on occasion, his templars, to help guard Stel's caravans and outposts. House Stel also keeps the merchants obligated to Hamanu. Other merchant houses have complained that accepting these warriors violates the spirit of the Merchants' Code, but Stel's obvious power and influence have kept such complaints quiet.

\textbf{DC 30:} Stel also engages, behind closed doors, in kidnapping for ransom, although this is considered a violation of the Merchants' Code and is never discussed in public.

A bardic knowledge check can reveal the same information as these knowledge checks, but in each case the DC is 5 higher than the given value.

\subsubsection{Agents}
House Stel requires the services of a wide variety of hirelings, with an emphasis on those with military or combat skills. Mages with offensive spells, fire clerics, and warriors of all sorts---House Stel is always looking for more guards, mercenaries, spies, gladiators, and the like.

Particularly promising hirelings are often promoted to agent status. Agents are rarely asked to join the family, however, but exceptional acts of bravery or skill have resulted in such invitations in the past. Admission into the family itself is a long, arduous process, reserved only for the most loyal agents.

\textbf{Wages:} Average pay or above.

\textbf{Additional Requirements:} Base attack bonus +3; or able to cast 2nd-level evocation spells.

\textbf{Desired Roles:} Any with combat skills---mages with offensive spells, fire clerics, and warriors of all sorts.