\subsection{Alignment Traits}
Some planes have a predisposition to a certain alignment. Most of the inhabitants of these planes also have the plane's particular alignment, even powerful creatures such as deities. In addition, creatures of alignments contrary to the plane have a tougher time dealing with its natives and situations.

The alignment trait of a plane affects social interactions there. Characters who follow other alignments than most of the inhabitants do may find life more difficult.

Alignment traits have multiple components. First are the moral (good or evil) and ethical (lawful or chaotic) components; a plane can have either a moral component, an ethical component, or one of each. Second, the specific alignment trait indicates whether each moral or ethical component is mildly or strongly evident.

\textbf{Good-Aligned/Evil-Aligned:} These planes have chosen a side in the battle of good versus evil. No plane can be both good-aligned and evil-aligned.

\textbf{Law-Aligned/Chaos-Aligned:} Law versus chaos is the key struggle for these planes and their residents. No plane can be both law-aligned and chaos-aligned.

Each part of the moral/ethical alignment trait has a descriptor, either ``mildly'' or ``strongly,'' to show how powerful the influence of alignment is on the plane.

\textbf{Mildly Aligned:} Creatures who have an alignment opposite that of a mildly aligned plane take a $-2$ circumstance penalty on all Charisma-based checks.

\textbf{Strongly Aligned:} On planes that are strongly aligned, a $-2$ circumstance penalty applies on all Charisma-based checks made by all creatures not of the plane's alignment. In addition, the $-2$ penalty affects all Intelligence-based and Wisdom-based checks, too.

The penalties for the moral and ethical components of the alignment trait do stack.

\textbf{Neutral-Aligned:} A mildly neutral-aligned plane does not apply a circumstance penalty to anyone.

The Material Plane is considered mildly neutral-aligned, though it may contain high concentrations of evil or good, law or chaos in places.

A strongly neutral-aligned plane would stand in opposition to all other moral and ethical principles: good, evil, law, and chaos. Such a plane may be more concerned with the balance of the alignments than with accommodating and accepting alternate points of view. In the same fashion as for other strongly aligned planes, strongly neutral-aligned planes apply a $-2$ circumstance penalty to Intelligence-, Wisdom-, or Charisma-based checks by any creature that isn't neutral. The penalty is applied twice (once for law/chaos, and once for good/evil), so neutral good, neutral evil, lawful neutral, and chaotic neutral creatures take a $-2$ penalty and lawful good, chaotic good, chaotic evil, and lawful evil creatures take a $-4$ penalty.