\subsection{Armor Class}
Your Armor Class (AC) represents how hard it is for opponents to land a solid, damaging blow on you. It's the attack roll result that an opponent needs to achieve to hit you. Your AC is equal to the following:

{
	\centering
	\vskip1em
	{\Large 10 + \textit{armor bonus} + \textit{shield bonus}\\+ \textit{Dex. modifier} + \textit{size modifier}}
	\vskip1em
}

Note that armor limits your Dexterity bonus, so if you're wearing armor, you might not be able to apply your whole Dexterity bonus to your AC.

Sometimes you can't use your Dexterity bonus (if you have one). If you can't react to a blow, you can't use your Dexterity bonus to AC. (If you don't have a Dexterity bonus, nothing happens.)

\textbf{Other Modifiers:} Many other factors modify your AC.

\textit{Enhancement Bonuses:} Enhancement effects make your armor better.

\textit{Deflection Bonus:} Magical deflection effects ward off attacks and improve your AC.

\textit{Natural Armor:} Natural armor improves your AC.

\textit{Dodge Bonuses:} Some other AC bonuses represent actively avoiding blows. These bonuses are called dodge bonuses. Any situation that denies you your Dexterity bonus also denies you dodge bonuses. (Wearing armor, however, does not limit these bonuses the way it limits a Dexterity bonus to AC.) Unlike most sorts of bonuses, dodge bonuses stack with each other.

\textbf{Touch Attacks:} Some attacks disregard armor, including shields and natural armor. In these cases, the attacker makes a touch attack roll (either ranged or melee). When you are the target of a touch attack, your AC doesn't include any armor bonus, shield bonus, or natural armor bonus. All other modifiers, such as your size modifier, Dexterity modifier, and deflection bonus (if any) apply normally.