\subsection{Saving Throws}
Generally, when you are subject to an unusual or magical attack, you get a saving throw to avoid or reduce the effect. Like an attack roll, a saving throw is a d20 roll plus a bonus based on your class, level, and an ability score. Your saving throw modifier is:

{
	\centering
	\vskip1em
	\Large \textit{Base save bonus} + \textit{ability modifier}
	\vskip1em
}

\textbf{Base Save Bonus:} A saving throw modifier derived from character class and level. Base save bonuses increase at different rates for different character classes. Base save bonuses gained from different classes, such as when a character is a multiclass character, stack.

\textbf{Saving Throw Types:} The three different kinds of saving throws are Fortitude, Reflex, and Will:

\textit{Fortitude:} These saves measure your ability to stand up to physical punishment or attacks against your vitality and health. Apply your Constitution modifier to your Fortitude saving throws.

\textit{Reflex:} These saves test your ability to dodge area attacks. Apply your Dexterity modifier to your Reflex saving throws.

\textit{Will:} These saves reflect your resistance to mental influence as well as many magical effects. Apply your Wisdom modifier to your Will saving throws.

\textbf{Saving Throw Difficulty Class:} The DC for a save is determined by the attack itself.

\textbf{Automatic Failures and Successes:} A natural 1 (the d20 comes up 1) on a saving throw is always a failure (and may cause damage to exposed items; see Items Surviving after a Saving Throw). A natural 20 (the d20 comes up 20) is always a success.