\subsectionA{Cognizance Crystals}
\emph{Cognizance crystals} store power points that psionic characters can use to pay for manifesting their powers.

\Table{}{CR}{
  \tableheader Maximum Power Point Storage
& \tableheader Market Price \\
 5 & 1,000 cp \\
10 & 4,000 cp \\
15 & 9,000 cp \\
20 & 16,000 cp \\
25 & 25,000 cp \\
30 & 36,000 cp \\
35 & 49,000 cp \\
40 & 64,000 cp \\
45 & 81,000 cp \\
}

\textbf{Physical Description:} A \emph{cognizance crystal} consists of a core crystal and two or three smaller crystals arranged in specific positions around it on strands of silver wire. The crystals give off a faint glow. A typical \emph{cognizance crystal} weighs approximately 1 pound, has AC 7, 10 hit points, a hardness of 8, and a break DC of 16.

\textbf{Activation:} The user must merely hold or have a crystal on her person for a period of at least 10 minutes (which is long enough to attune oneself to the crystal). Thereafter, the owner can use power points stored in the crystal to manifest powers she knows.

The maximum number of points a \emph{cognizance crystal} can store is always a number multiple of five and is never more than 45. It can store only as many power points as its original maximum, set at the time of its creation. When a \emph{cognizance crystal}'s power points are used up, the glow of the crystal dims. However, the user can recharge it by paying power points on a 1-for-1 basis. While doing this depletes the user's own power point reserve for the day, those power points remain available in the \emph{cognizance crystal} until used.

A user cannot directly replenish her personal power points from those stored in a \emph{cognizance crystal}, nor can she draw power points from more than one source to manifest a power. See \chapref{Psionics} for more information.

Faint to strong psychokinesis; ML equal to maximum power point storage divided by 5; \feat{Craft Cognizance Crystal}; Weight 0.5 kg.
