\subsectionA{Intelligent Items}
Items of power (either magical or psionic) sometimes have intelligence of their own. Psionically imbued with sentience, these items think and feel the same way characters do and should be treated as NPCs. Intelligent items have extra abilities and sometimes extraordinary powers and special purposes.

Intelligent items can actually be considered creatures because they have Intelligence, Wisdom, and Charisma scores. Treat them as constructs with the psionic subtype. Intelligent items often have the ability to illuminate their surroundings at will (as psionic weapons do); many cannot see otherwise.

Intelligent items can activate their own powers without waiting for a command word from their owner. Intelligent items act during their owner's turn in the initiative order.

\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/intelligent-item-alignment.tex}

\subsubsection{Languages Spoken By Item}
Like a character, an intelligent item speaks Common plus one additional language per point of Intelligence bonus. Choose appropriate languages, taking into account the item's origin and purposes.

\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/intelligent-item-powers.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/intelligent-item-skills.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/intelligent-item-purpose.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/dedicated-power.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/item-ego.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/intelligent-item-table.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/items-against-characters.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/intelligent-item-examples.tex}
\input{subsections/magic-items/psionic-item-descriptions/intelligent-items/unique-intelligent-items.tex}
