\subsubsection{Specific Cursed Items}
Specific Cursed Items are provided as examples of cursed items. They are given creation prerequisites, should someone want to intentionally create them (although that does not need to be the origin of the item). Note, however, two exceptions: The \emph{crystal hypnosis ball} cannot be created by any known means.

A simple \spell{detect magic} spell yields a misleading aura and strength, often indicating that the item is a noncursed item of similar sort. An \spell{identify} spell only has a 1\% chance per caster level to reveal a cursed item's true properties, including the cursed aspect. \spellref{analyze dweomer}{Analyze dweomer} reveals the true nature of a cursed item.

\Table{Specific Cursed Items}{lR}{
  \tableheader Item
& \tableheader Market Price\\
Ring of clumsiness              & 500 cp \\
Amulet of inescapable location  & 1,000 cp \\
Stone of weight                 & 1,000 cp \\
Bracers of defenselessness      & 1,200 cp \\
Gauntlets of fumbling           & 1,300 cp \\
$-2$ sword, cursed              & 1,500 cp \\
Armor of rage                   & 1,600 cp \\
Medallion of thought projection & 1,800 cp \\
Flask of curses                 & 2,100 cp \\
Dust of sneezing and choking    & 2,400 cp \\
Amulet of psionic interference  & 3,000 cp \\
Helm of opposite alignment      & 4,000 cp \\
Potion of poison                & 5,000 cp \\
Broom of animated attack        & 5,200 cp \\
Robe of powerlessness           & 5,500 cp \\
Vacuous grimoire                & 6,000 cp \\
Spear, cursed backbiter         & 7,500 cp \\
Armor of arrow attraction       & 9,000 cp \\
Net of snaring                  & 10,000 cp \\
Mace of blood                   & 16,000 cp \\
Robe of vermin                  & 16,500 cp \\
Periapt of foul rotting         & 17,000 cp \\
Sword, berserking               & 17,500 cp \\
Boots of dancing                & 30,000 cp \\
Necklace of strangulation       & 60,000 cp \\
Cloak of poisonousness          & 62,000 cp \\
Scarab of death                 & 80,000 cp \\
Crystal hypnosis ball           & --- \\
}

% Dark Sun specific
\textbf{Amulet of Psionic Interference:} This amulet appears to be an \emph{amulet ???}. This item scrambles the wearer's psionic abilities. The wearer is unable to make any power checks. Only the person who places the amulet around someone's neck can remove it. Otherwise, the amulet can only be removed by a \spell{remove curse}, a \spell{wish}, or a \spell{miracle} spell.

Strong abjuration; CL 16th; \feat{Craft Wondrous Item}, \spell{bestow curse}; Price 3,000 cp.

\textbf{Armor of Arrow Attraction:} Magical analysis indicates that this armor is a normal suit of \emph{+3 full plate}. However, the armor is cursed. It works normally with regard to melee attacks but actually serves to attract ranged weapons. The wearer takes a $-15$ penalty to AC against any attack by a ranged weapon. The true nature of the armor does not reveal itself until the character is fired upon in earnest.

Strong abjuration; CL 16th; \feat{Craft Magic Arms and Armor}, \spell{bestow curse}; Price 9,000 cp.

\textbf{Armor of Rage:} This armor is similar in appearance to armor of command and functions as a suit of +1 full plate. However, when it is worn, the armor causes the character to take a $-4$ penalty to Charisma. All unfriendly characters within 90 meters have a +1 morale bonus on attack rolls against her. The effect is not noticeable to the wearer or those affected. (In other words, the wearer does not immediately notice that donning the armor is the cause of her problems, nor do foes understand the reason for the depth of their enmity.)

Strong necromancy; CL 16th; \feat{Craft Magic Arms and Armor}, \spell{bestow curse}; Price 1,600 cp.

\textbf{Broom of Animated Attack:} This item is indistinguishable in appearance from a normal broom. It is identical to a \emph{broom of flying} by all tests short of attempted use.

If a command is spoken, the broom does a loop-the-loop with its hopeful rider, dumping him on his head from 1d4+5 feet off the ground (no falling damage, since the fall is less than 3 meters). The broom then attacks the victim, swatting the face with the straw or twig end and beating him with the handle end.

The broom gets two attacks per round with each end (two swats with the straw and two with the handle, for a total of four attacks per round). It attacks with a +5 bonus on each attack roll. The straw end causes a victim to be blinded for 1 round when it hits. The handle deals 1d6 points of damage when it hits. The broom has AC 13, 18 hit points, and hardness 4.

Moderate transmutation; CL 10th; \feat{Craft Wondrous Item}, \spell{fly}, \spell{animate objects}; Price 5,200 cp.

\textbf{Cloak of Poisonousness:} This cloak is usually made of a woolen material, although it can be made of leather. A \spell{detect poison} spell can reveal the presence of poison impregnated in the cloak's fabric. The garment can be handled without harm, but as soon as it is actually donned the wearer is killed instantly unless she succeeds on a DC 28 Fortitude save.

Once donned, a \emph{cloak of poisonousness} can be removed only with a \spell{remove curse} spell; doing this destroys the magical property of the cloak. If a \spell{neutralize poison} spell is then used, it is possible to revive the victim with a \spell{raise dead} or \spell{resurrection} spell, but not before.

Strong abjuration; CL 15th; \feat{Craft Wondrous Item}, \spell{poison}, and \spell{limited wish} or \spell{miracle}; Price 62,000 cp.

\textbf{Crystal Hypnosis Ball:} This cursed item is indistinguishable from a normal \emph{crystal ball}. However, anyone attempting to use the scrying device becomes fascinated for 1d6 minutes, and a telepathic \spell{suggestion} is implanted in his mind (Will DC 19 negates).

The user of the device believes that the desired creature or scene was viewed, but actually he came under the influence of a powerful wizard, lich, or even some power or being from another plane. Each further use brings the \emph{crystal hypnosis ball} gazer deeper under the influence of the controller, either as a servant or a tool. Note that throughout this time, the user remains unaware of his subjugation.

Moderate divination; CL 17th; In effect, this is a minor artifact and cannot be created; Price n/a.

\textbf{Dust of Sneezing and Choking:} This fine dust appears to be \emph{dust of appearance}. If cast into the air, it causes those within a 6-meter spread to fall into fits of sneezing and coughing. Those failing a DC 15 Fortitude save take 2d6 points of Constitution damage immediately. In addition, those failing a second DC 15 Fortitude save 1 minute later are dealt 1d6 points of Constitution damage. Those who succeed on either saving throw are nonetheless disabled by choking (treat as stunned) for 5d4 rounds.

Faint conjuration; CL 7th; \feat{Craft Wondrous Item}, \spell{poison}; Price 2,400 cp.

\textbf{Flask of Curses:} This item looks like an ordinary beaker, bottle, container, decanter, flask, or jug. It may contain a liquid, or it may emit smoke. When the flask is first unstoppered, all within 9 meters must make a DC 17 Will save or be cursed, taking a $-2$ penalty on attack rolls, saving throws, and skill checks until a \spell{remove curse} spell is cast upon them.

Moderate conjuration; CL 7th; \feat{Craft Wondrous Item}, \spell{bestow curse}; Price 2,100 cp.

\textbf{Gauntlets of Fumbling:} These gauntlets may be of supple leather or heavy protective material suitable for use with armor. In the former instance, they appear to be \emph{gloves of Dexterity}. In the latter case, they appear to be \emph{gauntlets of ogre power}. The gauntlets perform according to every test as if they were \emph{gloves of Dexterity} or \emph{gauntlets of ogre power} until the wearer finds herself under attack or in a life-and-death situation. At that time, the curse is activated. The wearer becomes fumble-fingered, with a 50\% chance each round of dropping anything held in either hand. The gauntlets also lower Dexterity by 2 points. Once the curse is activated, the gloves can be removed only by means of a \spell{remove curse} spell, a \spell{wish}, or a \spell{miracle}.

Moderate transmutation; CL 7th; \feat{Craft Wondrous Item}, \spell{bestow curse}; Price 1,300 cp.

\textbf{Helm of Opposite Alignment:} This metal hat looks like a typical helmet. When placed upon the head, however, its curse immediately takes effect (Will DC 15 negates). On a failed save, the alignment of the wearer is radically altered to an alignment as different as possible from the former alignment---good to evil, chaotic to lawful, neutral to some extreme commitment (LE, LG, CE, or CG). Alteration in alignment is mental as well as moral, and the individual changed by the magic thoroughly enjoys his new outlook. A character who succeeds on his save can continue to wear the helmet without suffering the effect of the curse, but if he takes it off and later puts it on again, another save is required. The curse only works once; that is, a character whose alignment has been changed cannot change it again by donning the helmet a second time.

Only a \spell{wish} or a \spell{miracle} can restore former alignment, and the affected individual does not make any attempt to return to the former alignment. (In fact, he views the prospect with horror and avoids it in any way possible.) If a character of a class with an alignment requirement is affected, an \spell{atonement} spell is needed as well if the curse is to be obliterated. When a \emph{helm of opposite alignment} has functioned once, it loses its magical properties.

Strong transmutation; CL 12th; \feat{Craft Wondrous Item}, creator must be 12th level; Price 4,000 cp; Weight 1.5 kg.

\textbf{Mace of Blood:} This \emph{+3 heavy mace} must be coated in blood every day, or its bonus fades away (until the mace is coated again). The character using this mace must make a DC 13 Will save every day it is within his possession or become chaotic evil.

Moderate abjuration; CL 8th; \feat{Craft Magic Arms and Armor}, creator must be at least 9th level and chaotic evil; Price 16,000 cp.

\textbf{Medallion of Thought Projection:} This device seems like a \emph{medallion of thoughts}, even down to the range at which it functions, except that the thoughts overheard are muffled and distorted, requiring a DC 15 Will save to sort out. However, while the user thinks she is picking up the thoughts of others, all she is really hearing are figments created by the medallion itself. These illusory thoughts always seem plausible and thus can seriously mislead any who rely upon them. What's worse, unknown to her, the cursed medallion actually broadcasts her thoughts to creatures in the path of the beam, thus alerting them to her presence.

Faint divination; CL 7th; \feat{Craft Wondrous Item}, \spell{detect thoughts}, \spell{ghost sound}; Price 1,800 cp.

\textbf{Necklace of Strangulation:} A necklace of strangulation appears to be a rare and wondrous piece of valuable jewelry and, short of the use of something as powerful as a miracle or a wish, can only be identified as a cursed item when placed around a character's neck. The necklace immediately constricts, dealing 6 points of damage per round. It cannot be removed by any means short of a \spell{limited wish}, \spell{wish}, or \spell{miracle} and remains clasped around the victim's throat even after his death. Only when he has decayed to a dry skeleton (after approximately one month) does the necklace loosen, ready for another victim.

Strong conjuration; CL 18th; \feat{Craft Wondrous Item}, \spell{slay living}; Price 60,000 cp.

\textbf{Net of Snaring:} This net provides a +3 bonus on attack rolls but can only be used underwater, thus making it a somewhat useful item rather than what most would really call a cursed item. Underwater, it can be commanded to shoot forth up to 9 meters to trap a creature.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{freedom of movement}; Price 10,000 cp.

\textbf{Periapt of Foul Rotting:} This engraved gem appears to be of little value. If any character keeps the periapt in her possession for more than 24 hours, she contracts a terrible rotting affliction that permanently drains 1 point of Dexterity, Constitution, and Charisma every week. The periapt (and the affliction) can be removed only by application of a \spell{remove curse} spell followed by a \spell{remove disease} and then a \spell{heal}, \spell{miracle}, \spell{limited wish}, or \spell{wish} spell. The rotting can also be countered by crushing a \emph{periapt of health} and sprinkling its dust upon the afflicted character (a full-round action), whereupon the \emph{periapt of foul rotting} likewise crumbles to dust.

Faint abjuration; CL 10th; \feat{Craft Wondrous Item}, \spell{contagion}; Price 17,000 cp.

\textbf{Potion of Poison:} This potion has lost its once beneficial magical abilities and has become a potent poison. The imbiber must make a DC 16 Fortitude save or take 1d10 points of Constitution damage. A minute later he must save again (DC 16) or take 1d10 points of Constitution damage.

Moderate conjuration; CL 12th; \feat{Craft Wondrous Item}, \spell{poison}; Price 5,000 cp.

\textbf{Robe of Powerlessness:} A robe of powerlessness appears to be a magic robe of another sort. As soon as a character dons this garment, she takes a $-10$ penalty to Strength and Intelligence, forgetting spells and magic knowledge accordingly. The robe can be removed easily, but in order to restore mind and body, the character must receive a \spell{remove curse} spell followed by \spell{heal}.

Moderate transmutation; CL 13th; \feat{Craft Wondrous Item}, \spell{bestow curse}, \spell{permanency}; Price 5,500 cp.

\textbf{Robe of Vermin:} The wearer notices nothing unusual when the robe is donned, other than that it offers great magical defense (as a cloak of resistance +4). However, as soon as he is in a situation requiring concentration and action against hostile opponents, the true nature of the garment is revealed: The wearer immediately suffers a multitude of bites from the insects that magically infest the garment. He must cease all other activities in order to scratch, shift the robe, and generally show signs of the extreme discomfort caused by the bites and movement of these pests.

The wearer takes a $-5$ penalty on initiative checks and a $-2$ penalty on all attack rolls, saves, and skill checks. If he tries to cast a spell, he must make a \skill{Concentration} check (DC 20 + spell level) or lose the spell.

Moderate abjuration; CL 13th; \feat{Craft Wondrous Item}, \spell{summon swarm}, creator must be at least 13th level; Price 16,500 cp.

\textbf{Ring of Clumsiness:} This ring operates exactly like a \emph{ring of feather falling}. However, it also makes the wearer clumsy. She takes a $-4$ penalty to Dexterity and has a 20\% chance of spell failure when trying to cast any arcane spell that has a somatic component. (This chance of spell failure stacks with other arcane spell failure chances.)

Strong transmutation; CL 15th; \feat{Forge Ring}, \spell{feather fall}, \spell{bestow curse}; Price 500 cp.

\textbf{Scarab of Death:} This small pin appears to be any one of the various beneficial amulets, brooches, or scarabs. However, if it is held for more than 1 round or carried by a living creature for 1 minute, it changes into a horrible burrowing beetlelike creature. The thing tears through any leather or cloth, burrows into flesh, and reaches the victim's heart in 1 round, causing death. A DC 25 Reflex save allows the wearer to tear the scarab away before it burrows out of sight, but he still takes 3d6 points of damage. The beetle then returns to its scarab form. Placing the scarab in a container of wood, ceramic, bone, ivory, or metal prevents the monster from coming to life and allows for long-term storage of the item.

Strong abjuration; CL 19th; \feat{Craft Wondrous Item}, \spell{slay living}; Price 80,000 cp.

\textbf{Spear, Cursed Backbiter:} This is a \emph{+2 shortspear}, but each time it is used in melee against a foe and the attack roll is a natural 1, it damages its wielder instead of her intended target. When the curse takes effect, the spear curls around to strike its wielder in the back, automatically dealing the damage to the wielder. The curse even functions when the spear is hurled, and in such a case the damage to the hurler is doubled.

Moderate evocation; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{bestow curse}; Price 7,500 cp.

\textbf{Stone of Weight (Loadstone):} This stone appears to be a dark, smoothly polished stone. It reduces the possessor's base land speed to one-half of normal. Once picked up, the stone cannot be disposed of by any nonmagical means---if it is thrown away or smashed, it reappears somewhere on his person. If a \spell{remove curse} spell is cast upon a loadstone, the item may be discarded normally and no longer haunts the individual.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{slow}; Price 1,000 cp.

\textbf{-2 Sword, Cursed:} This longsword performs well against targets in practice, but when used against an opponent in combat, it causes its wielder to take a $-2$ penalty on attack rolls.

All damage dealt is also reduced by 2 points, but never below a minimum of 1 point of damage on any successful hit. After one week in a character's possession, the sword always forces that character to employ it rather than another weapon. The sword's owner automatically draws it and fights with it even when she meant to draw or ready some other weapon. The sword can be gotten rid of only by means of \spell{limited wish}, \spell{wish}, or \spell{miracle}.

Strong evocation; CL 15th; \feat{Craft Magic Arms and Armor}, \spell{bestow curse}, and \spell{limited wish} or \spell{miracle}; Price 1,500 cp.

\textbf{Sword, Berserking:} This item appears to have the characteristics of a \emph{+2 greatsword}. However, whenever the sword is used in battle, its wielder goes berserk (gaining all the benefits and drawbacks of the barbarian's rage ability). He attacks the nearest creature and continues to fight until unconscious or dead or until no living thing remains within 9 meters. Although many see this sword as a cursed object, others see it as a boon.

Moderate evocation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{rage}, \spell{bestow curse}; Price 17,500 cp.

\textbf{Vacuous Grimoire:} A book of this sort looks like a normal one on some mildly interesting topic. Any character who opens the work and reads so much as a single word therein must make two DC 15 Will saves. The first is to determine if the reader takes 1 point of permanent Intelligence drain. The second is to find out if the reader takes 2 points of permanent Wisdom drain. To destroy the book, a character must burn it while casting \spell{remove curse}. If the grimoire is placed with other books, its appearance instantly alters to conform to the look of those other works.

Strong enchantment; CL 20th; \feat{Craft Wondrous Item}, \spell{feeblemind}; Price 6,000 cp.

