\subsection{Major Artifacts}
Major artifacts are unique items—only one of each such item exists. These are the most potent of magic items, capable of altering the balance of a campaign.

Unlike all other magic items, major artifacts are not easily destroyed. Each should have only a single, specific means of destruction.

\subsubsection{Major Artifact Descriptions}

\textbf{The Moaning Diamond:} The \emph{Moaning Diamond} appears to be an uncut diamond the size of a human fist. At all times, it gives forth a baleful moaning sound, as if in pain. Despite the noise, the \emph{Moaning Diamond} is not evil. The wielder of the stone can, three times per day, call upon it to reshape earth and stone as if by the spell stone shape, affecting 5,000 cubic feet of material. The \emph{Moaning Diamond} can summon an elder earth elemental with maximum hit points that serves the caster until it is slain. Only one such elemental can be summoned at a time; if it is slain, a new creature cannot be summoned for 24 hours.

\textbf{The Saint's Mace:} This relic appears to be a simple, well-used cudgel, but its simple appearance hides great power. The saint's mace has a +5 enhancement bonus and functions as a heavy mace with the holy, lawful, and disruption special abilities. The wielder can project \spell{searing light} from the mace at will, at caster level 20th.

\textbf{The Shadowstaff:} This artifact was crafted centuries ago, weaving together the wispy strands of shadow itself into a twisted black staff. The \emph{Shadowstaff} makes the wielder slightly shadowy and incorporeal, granting him a +4 bonus to AC and Reflex saves (which stacks with any other bonuses). However, in bright light (such as that of the sun, but not a torch) or in absolute darkness, the wielder takes a $-2$ penalty on all attack rolls, saves, and checks.

The \emph{Shadowstaff} also has these powers.
\begin{itemize*}
\item \textit{Summon Shadows:} Three times per day the staff may summon 2d4 shadows. Immune to turning, they serve the wielder as if called by a \spell{summon monster V} spell cast at 20th level.
\item \textit{Summon Nightshade:} Once per month, the staff can summon a nightcrawler nightshade that serves the wielder as if called by a \spell{summon monster IX} spell cast at 20th level.
\item \textit{Shadow Form:} Three times per day the wielder can become a living shadow, with all the movement powers granted by the \spell{gaseous form} spell.
\item \textit{Shadow Bolt:} Three times per day the staff can project a ray attack that deals 10d6 points of cold damage to a single target. The shadow bolt has a range of 30 meters.
\end{itemize*}
