\chapter{Changes from d20 System}
\label{apx:Changes from d20 System}

\section{Core Mechanic}
\begin{itemize*}
\item Added advantage and disadvantage, from \textbf{D\&D} 5e.
\item Simplified XP table for combat encounters (500 XP $\times$ CR).
\item Added new XP table for skill checks.
\item Added new XP table for racial roleplaying.
\item Added multiclass prerequisites for base classes.
\item Using a contact mechanic based on: influence contacts, skill contacts, and trade contacts.
\end{itemize*}

\section{Base Classes}
In general, warriors and thieves have gotten a boost via either bonus feats or new class features. Some class features were rearranged so that their progression is scales well until the 30th level. The goal of these changes was to make the power gap between spellcasters and psionicists and these classes more manageable.

One change made on all base classes: Swim is not a class skill for any class (except water clerics).

There are two new classes: \textbf{Gladiator} and \textbf{Templar}.

These classes were removed: \textbf{Monk}, \textbf{Paladin}, and \textbf{Sorcerer}.

\subsection{Barbarian}
\begin{itemize*}
\item Swapped trap sense to wasteland trap sense, that gives bonus to natural hazards as well.
\item Gained bonus feats beginning at 8th level, from a select list.
\item Rearranged the level of rage abilities, improving rage in earlier levels.
\item Added new class skills: Autohypnosis and Knowledge (nature).
\end{itemize*}

\subsection{Bard}
\begin{itemize*}
\item Inspire courage improves every six levels after the 1st, improving the bonus one level earlier than originally.
\item Skill points per level increased to 8.
\item Added new class skills: Forgery, Heal, Intimidate, Ride, Use Psionic Device, and Use Rope.
\item Removed class skills: Concentration, Spellcraft.
\item Removed spellcasting.
\item Fortitude as good save as well.
\item New class feature: trade secret at 4th and every four levels thereafter.
\item New class feature: special ability at 10th and every five levels thereafter.
\item And many more class features.
\end{itemize*}
% Improved inspire courage progression, and skill points per level.

\subsection{Cleric}
\begin{itemize*}
\item Each element or paraelement gives a class skill.
\item Duties of clerics of each element are defined.
\item Domain spells can be prepared in his normal spell slots.
% \item Elemental domains were reworked to match {\tableheader AD\&D} concepts.
\item New class feature: sacrifice at 5th.
\item New class feature: combine casting at 7th.
\end{itemize*}

\subsection{Druid}
\begin{itemize*}
\item Lost animal companion---this ability was reserved to the ranger.
\item Skills points per level reduced to 2.
\item Rearranged the wild shape progression:
	\begin{itemize*}
	\item One additional daily use every three levels after 6th.
	\item Venom immunity one level earlier.
	\item A thousand faces and timeless body one level later each.
	\end{itemize*}
\item Removed elemental wild shape---Druids can wild shape into vermin instead, and it uses two normal uses, instead of a different pool.
\item Reduced spell slots progression after 15th level.
\end{itemize*}

\subsection{Fighter}
\begin{itemize*}
\item Skill points per level increased to 4.
\item Added new class skills: Autohypnosis, Knowledge (warcraft), and Spot.
\item New class feature: martial prowess at 5th and every two levels thereafter.
\end{itemize*}

\subsection{Psion/Wilder}
\begin{itemize*}
\item Reduced power point progression.
\end{itemize*}

\subsection{Psychic Warrior}
\begin{itemize*}
\item Must be lawful or chaotic.
\item Improved power point progression.
\item Skill points per level increased to 4.
\end{itemize*}

\subsection{Ranger}
\begin{itemize*}
\item Improved animal companion: equivalent to original druid level $-3$, instead of one-half ranger level.
\item Improved spell slot progression.
\end{itemize*}

\subsection{Rogue}
\begin{itemize*}
\item Gained bonus feats beginning at 5th level, from skill feats or ambush feats\textsuperscript{CS}.
\item Skill points per level increased to 10.
\item Added new class skill: Use Psionic Device.
\item New special abilities:
	\begin{itemize*}
	\item \textit{False vulnerability:} no penalties on AC while prone, and feint with advantage.
	\item \textit{Infiltrator:} roll first checks of Bluff, Disguise, and Forgery with advantage.
	\item \textit{Psionic Harrier:} flanked manifesters can't manifest defensively.
	\item \textit{Silver Tongue:} retry one skill check with disadvantage.
	\item \textit{Thief's Luck:} 1/day reroll one failed attack, check or saving throw.
	\item \textit{Trap Sense:} entitled to Search check when within 1.5 m of a trap, as if actively looking for it.
	\end{itemize*}
\end{itemize*}

\subsection{Wizard}
\begin{itemize*}
\item Learn one additional spell per level from specific schools, depending on the path choice (preserver or defiler).
\end{itemize*}

\section{Skills}
Non-synergy bonuses require 10 ranks in a skill, instead of 5 (Balance, Survival, and Tumble).

\Table{}{Xl}{
\tableheader Conditional Modifiers & \tableheader Effect \\
1 favorable condition     & +2 circumstance bonus\\
2 or more favorable conditions   & Advantage\\
1 unfavorable condition   & $-2$ penalty\\
2 or more unfavorable conditions & Disadvantage\\
}
% Conditional modifiers don't scale indefinitely. One favorable condition gives +2 bonus. If there are two or more favorable conditions, they give advantage (besides +2 bonus). At the same time, one unfavorable condition gives $-2$ penalty. If there are two or more unfavorable conditions, they give disadvantage (besides $-2$ penalty).

\subsection{New skills}
\begin{itemize*}
\item \textbf{Knowledge (ancient history)}: History from before the sorcerer-kings rule.
\item \textbf{Knowledge (warcraft)}: Supervision of construction of siege engines and war tactics.
\item \textbf{Literacy}: Reading and writing is forbidden in most of Athas.
\end{itemize*}

\subsection{New synergies}
\Table{}{lX}{
\tableheader 5 ranks in... & \tableheader Gives +2 bonus on...\\
Appraise & Diplomacy checks to bargain \\
Balance & Tumble checks \\
Decipher Script & Forgery checks \\
Diplomacy & Gather Information checks \\
Disable Device & Open Locks checks \\
Knowledge (warcraft) & Diplomacy checks dealing with troops\\
Open Locks & Disable Device checks \\
Ride & Handle Animal checks involving mounts \\
Use Magic Device & Appraise checks involving magic items \\
Use Psionic Device & Appraise checks involving psionic items \\
}

\subsection{New uses}
\begin{itemize*}
\item \textit{Appraise:} identify magic or psionic item.
\item \textit{Craft:} create poison.
\item \textit{Diplomacy:} bargain a discount.
\item \textit{Disguise:} conceal spellcasting.
\end{itemize*}

\subsection{Changed uses}
\begin{itemize*}
\item \textit{Craft:} crating metal items has a $-5$ penalty.
\item \textit{Heal:} long-term care can heal up to double the healer's ranks per character level.
\item \textit{Survival:} endure the elements and get along in the wild each has a table since the difficulty depends on the terrain.
\end{itemize*}

\subsection{Removed uses}
\begin{itemize*}
\item \textit{Use Psionic Device:} address power stone, use dorje, use power stone.
\end{itemize*}

\section{Feats}
\begin{itemize*}
\item General feats that give +2 bonus to two skills were separated into \textit{skill feats}.
\item General feats available to fighters were separated into \textit{fighter feats}.
\end{itemize*}

\subsection{New feats}
\Table{}{XX}{

\multicolumn{2}{l}{\tableheader General Feats}\\
\feat{Ancestral Knowledge} & \feat{Grovel} \\
\feat{Arena Clamor} & \feat{Hard as Rock} \\
\feat{Arena Fighter} & \feat{Improved Counterspell} \\
\feat{Arena Performer} & \feat{Improved Sigil} \\
\feat{Arena Psionicist} & \feat{Innate Hunter} \\
\feat{Armored Stealth} & \feat{Kiltektet} \\
\feat{Brutal Attack} & \feat{Linguist} \\
\feat{Bug Trainer} & \feat{Martial Performer} \\
\feat{Cloak Dance} & \feat{Martial Psionicist} \\
\feat{Cornered Fighter} & \feat{Mastyrial Blood} \\
\feat{Deadly Precision} & \feat{Open Minded} \\
\feat{Defender of the Land} & \feat{Protective} \\
\feat{Dissimulated} & \feat{Psionic Mimicry} \\
\feat{Drake's Child} & \feat{Psionic Schooling} \\
\feat{Druidic Hunter} & \feat{Psychic Hunter} \\
\feat{Elemental Cleansing} & \feat{Raised by Beasts} \\
\feat{Extra Music} & \feat{Rapid Metabolism} \\
\feat{Extra Performance} & \feat{Reckless Offense} \\
\feat{Faithful Follower} & \feat{Reign of Terror} \\
\feat{Favorite} & \feat{Rogue Performer} \\
\feat{Fearsome} & \feat{Secular Authority} \\
\feat{Greasing the Wheels} & \feat{Sniper} \\
\feat{Greater Counterspell} & \feat{Wastelander} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Skill Feats}\\
\feat{Field Officer} & \feat{Trader}\\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Racial Feats}\\
\feat{Active Glands} & \feat{Elfeater} \\
\feat{Advanced Antennae} & \feat{Improved Gyth'sa} \\
\feat{Blend} & \feat{Longshanks} \\
\feat{Blessed by the Ancestors} & \feat{Tikchak} \\
\feat{Cannibalism Ritual} & \feat{Tokchak} \\
\feat{Dwarven Vision} & \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Fighter Feats}\\
\feat{Commanding Presence} & \feat{Rotate Lines} \\
\feat{Concentrated Fire} & \feat{Shield Evasion} \\
\feat{Implacable Defender} & \feat{Shield Wall} \\
\feat{Greater Critical} & \feat{Spear Wall} \\
\feat{Intimidating Presence} & \feat{Tactical Expertise} \\
\feat{Inspiring Presence} & \feat{Teamwork} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Divine Feats}\\
\feat{Elemental Affinity} & \feat{Elemental Vengeance} \\
\feat{Elemental Might} & \feat{Superior Blessing} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Psionic Feats}\\
\feat{Elemental Manifestation} & \feat{Improved Elf Run} \\
\feat{Focused Mind} & \feat{Jump Charge} \\
\feat{Improved Dwarven Focus} & \feat{Pterran Telepathy} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Item Creation Feats}\\
\feat{Craft Psionic Item} & \\
}

\subsection{Removed feats}
\begin{itemize*}
\item Craft Dorje
\item Craft Psicrown
\item Craft Psionic Arms and Armor
\item Craft Psionic Construct
\item Craft Universal Item
\item Imprint Stone
\end{itemize*}

\section{Prestige Classes}

\subsection{New Prestige Classes}
\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Prestige Classes}\\
Arch defiler           & Elite sniper\\
Arena champion         & Exterminator\\
Battle dancer          & Grove master\\
Beastmaster psionicist & Jazst\\
Cerulean               & Master scout\\
Chasseur               & Poisonmaster\\
Convict                & Psiologist\\
Divine mind            & Restorationist\\
Dune trader            & Sensei\\
Earth defender         & Shadow wizard\\
Elemental singer       & Wanderer\\
}

\subsection{Removed Prestige Classes}
\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Prestige Classes}\\
Arcane Archer   & Duelist \\
Blackguard      & Dwarf Defender \\
Dragon Disciple & Eldritch Knight \\
}
