\chapter{Changes from d20 System}
\label{apx:Changes from d20 System}

\section{Core Mechanic}
\begin{itemize*}
\item Added advantage and disadvantage, from \textbf{D\&D} 5e.
\item Simplified XP table for combat encounters (500 XP $\times$ CR).
\item Added new XP table for skill checks.
\item Added new XP table for racial role playing.
\item Added multiclass prerequisites for base classes.
\item Using a contact mechanic based on: influence contacts, skill contacts, and trade contacts.
\item Spellcasters can cast one additional spell of their highest level per new class level.
\item Attribute checks are made using the whole attribute, instead of modifier.
\end{itemize*}

\section{Base Classes}
In general, warriors and thieves have gotten a boost via either bonus feats or new class features. Some class features were rearranged so that their progression is well behaved until the 30th level. The goal of these changes was to make the power gap between spellcasters and psionicists and these classes more manageable.

One change made on all base classes: Swim is not a class skill for any class (except water clerics).

Rogue has been renamed to \textbf{Thief}.

There are three new classes: \textbf{Gladiator}, \textbf{Scout} (different from \emph{Complete Adventurer}'s class), and \textbf{Templar}.

These classes were removed: \textbf{Monk}, \textbf{Paladin}, \textbf{Psychic Warrior}, \textbf{Sorcerer}, and \textbf{Wilder}.

\subsection{Barbarian}
\begin{itemize*}
\item Swapped trap sense to wasteland sense, that adds Constitution bonus to his AC, and to his Reflex saves against traps and natural hazards.
\item Rearranged the level of rage abilities, improving rage in earlier levels.
\item Added new class skills: Autohypnosis and Knowledge (nature).
\item New class feature: martial prowess at 4th and every three levels thereafter.
\item New class feature: bonus feats beginning at 5th and every three levels thereafter, from a select list.
\item New class feature: resilience at 14th.
\end{itemize*}

\subsection{Bard}
\begin{itemize*}
\item Skill points per level increased to 8.
\item Inspire courage improves every six levels after the 1st, improving the bonus one level earlier.
\item Added new class skills: Forgery, Heal, Intimidate, Ride, Use Psionic Device, and Use Rope.
\item Removed class skills: Concentration, Spellcraft.
\item Removed spellcasting.
\item Fortitude as good save as well.
\item Bardic music: Inspire courage improves at 7th and every 6 levels thereafter.
\item Bardic music: Inspire competence gives advantage to skill checks, instead of +2 competence bonus.
\item New class feature: trade secret at 4th and every four levels thereafter.
\item New class feature: special ability at 10th and every five levels thereafter.
\item And many more class features.
\end{itemize*}
% Improved inspire courage progression, and skill points per level.

\subsection{Cleric}
\begin{itemize*}
\item Each element or paraelement gives a class skill.
\item Duties of clerics of each element are defined.
\item Domain spells can be prepared in his normal spell slots.
\item New domains---the original domains are reserved for templars.
% \item Elemental domains were reworked to match {\tableheader AD\&D} concepts.
\item New class feature: sacrifice at 5th.
\item New class feature: combine casting at 7th.
\item New class feature: bonus feats beginning at 10th and every five levels thereafter, from a select list.
\end{itemize*}

\subsection{Druid}
\begin{itemize*}
\item Removed animal companion.%---this ability was reserved to the ranger.
\item Removed elemental wild shape.
\item Skills points per level reduced to 2.
\item Spells with element descriptors must match the guarded lands.
\item Rearranged the wild shape progression:
	\begin{itemize*}
	 	\item One additional daily use every three levels after 6th.
	 	\item One different size category at 9th and every four levels there after (Large, Tiny, and Huge).
	 	\item One different type at 12th and 18th (plant and vermin).
 	\end{itemize*}
\item Venom immunity at 8th.
\item A thousand faces at 14th.
\item Timeless body at 16th.
\item Reduced spell slots progression after 15th level.
\end{itemize*}

\subsection{Fighter}
\begin{itemize*}
\item Skill points per level increased to 4.
\item Added new class skills: Autohypnosis, Knowledge (warcraft), and Spot.
\item New class feature: martial prowess at 5th and every two levels thereafter.
\end{itemize*}

\subsection{Psion}
\begin{itemize*}
\item \textbf{Reworked psionics}.
\item Increased power points at lower levels.
\item Decreased power point progression.
\item Acquire access to disciplines over the levels.
\item Requires Constitution, Intelligence, and Wisdom to manifest psionic powers depending on the discipline.
	\begin{itemize*}
	\item \textit{Psychometabolism:} Constitution.
	\item \textit{Psychoportation:} Constitution.
	\item \textit{Psychokinesis:} Intelligence.
	\item \textit{Metacreativity:} Intelligence.
	\item \textit{Clairscience:} Wisdom.
	\item \textit{Telepathy:} Wisdom.
	\end{itemize*}
\end{itemize*}

% \subsection{Psychic Warrior}
% \begin{itemize*}
% \item Must be lawful or chaotic.
% \item Improved power point progression.
% \item Skill points per level increased to 4.
% \end{itemize*}

\subsection{Ranger}
\begin{itemize*}
\item Must be good.
\item Animal companion is based on Challenge Rating, starts at CR \onehalf and then uses ranger level minus 4 for improved companions.
\item Improved spell slot progression.
\item Spells only from the domains of their chosen element.
\item Wild empathy at 2nd.
\item Camouflage at 12th.
\item Hide in plain sight at 16th.
\item New class feature: favored terrain at 1st and every five levels thereafter.
\item New class feature: martial prowess at 6th and every four levels thereafter.
\item New class feature: scent at 17th.
\end{itemize*}

\subsection{Thief}
\begin{itemize*}
\item Added new class skill: Use Psionic Device.
\item Swapped trap sense to thief sense, that adds Intelligence bonus to initiative, and to his Reflex saves against traps and natural hazards. Maximum bonus equal to \onehalf thief level.
\item New class feature: trade secret at 6th and every four levels thereafter.
\item New special abilities:
	\begin{itemize*}
	\item \textit{False vulnerability:} no penalties on AC while prone, and feint with advantage.
	\item \textit{Infiltrator:} roll first checks of Bluff, Disguise, and Forgery with advantage.
	\item \textit{Psionic Harrier:} flanked manifesters can't manifest defensively.
	\item \textit{Silver Tongue:} retry one skill check with disadvantage.
	\item \textit{Thief's Luck:} 1/day reroll one failed attack, check or saving throw.
	\item \textit{Trap Sense:} entitled to Search check when within 1.5 m of a trap, as if actively looking for it.
	\end{itemize*}
\end{itemize*}

\subsection{Wizard}
\begin{itemize*}
\item Learn one additional spell per level from specific schools, depending on the path choice (preserver or defiler).
\end{itemize*}

\subsection{Multiclass}
\begin{itemize*}
\item Instead of XP penalty, characters must have prerequisite ability scores for both classes.
\item Favored class allows a character to ignore the class prerequisites.
\end{itemize*}

\section{Skills}
Non-synergy bonuses require 10 ranks in a skill, instead of 5 (Balance, Survival, and Tumble).

\Table{}{Xl}{
\tableheader Conditional Modifiers & \tableheader Effect \\
1 favorable condition            & +2 circumstance bonus\\
2 or more favorable conditions   & Advantage\\
1 unfavorable condition          & $-2$ penalty\\
2 or more unfavorable conditions & Disadvantage\\
}
% Conditional modifiers don't scale indefinitely. One favorable condition gives +2 bonus. If there are two or more favorable conditions, they give advantage (besides +2 bonus). At the same time, one unfavorable condition gives $-2$ penalty. If there are two or more unfavorable conditions, they give disadvantage (besides $-2$ penalty).

\subsection{New skills}
\begin{itemize*}
\item \textbf{Knowledge (ancient history)}: History from before the sorcerer-kings rule.
\item \textbf{Knowledge (warcraft)}: Supervision of construction of siege engines and knowledge of war tactics.
\item \textbf{Literacy}: Reading and writing is forbidden in most of Athas.
\end{itemize*}

\subsection{New synergies}
\Table{}{lX}{
\tableheader 5 ranks in... & \tableheader Gives +2 bonus on...\\
Appraise             & Diplomacy checks to bargain \\
Balance              & Tumble checks \\
Decipher Script      & Forgery checks \\
Diplomacy            & Gather Information checks \\
Disable Device       & Open Locks checks \\
Knowledge (warcraft) & Diplomacy checks dealing with troops\\
Open Locks           & Disable Device checks \\
Ride                 & Handle Animal checks involving mounts \\
Use Magic Device     & Appraise checks involving magic items \\
Use Psionic Device   & Appraise checks involving psionic items \\
}

\subsection{New uses}
\begin{itemize*}
\item \textit{Appraise:} identify magic or psionic item.
\item \textit{Autohypnosis:} rejuvenate (recover power points as if sleeping).
\item \textit{Craft:} create poison.
\item \textit{Diplomacy:} bargain a discount.
\item \textit{Disguise:} conceal spellcasting.
\item \textit{Heal:} treat hypothermia.
\item \textit{Knowledge (warcraft):} identify tactics.
\item \textit{Ride:} improve chariot maneuverability.
\item \textit{Spot:} spot moving target, spot still target, identify race or affiliation, identify individual, detect spellcasting, spot details.
\item \textit{Survival:} find shelter.
\end{itemize*}

\subsection{Changed uses}
\begin{itemize*}
\item \textit{Craft:} crating metal items has a $-5$ penalty.
\item \textit{Heal:} first-aid can heal hit points up to $-1$, and long-term care can heal up to double the healer's ranks per character level.
\item \textit{Survival:} ``avoid getting lost'', ``endure the elements'', and ``getting along in the wild'' each has a table since the difficulty depends on the terrain.
\item \textit{Swim:} aggregated swim rules from Water Dangers, and add new water strength: violent waters.
\end{itemize*}

\subsection{Removed uses}
\begin{itemize*}
\item \textit{Use Psionic Device:} address power stone, use dorje, use power stone.
\end{itemize*}

\section{Feats}
\begin{itemize*}
\item General feats that give +2 bonus to two skills were separated into \textit{skill feats}.
\item General feats available to fighters were separated into \textit{fighter feats}.
\item Added \textit{raze feats} to improve defiling effects (see Magic, below).
\end{itemize*}

\subsection{New feats}
\Table{}{XX}{

\multicolumn{2}{l}{\tableheader General Feats}\\
\feat{Ancestral Knowledge}  & \feat{Greater Counterspell}  \\
\feat{Arena Clamor}         & \feat{Hard as Rock}          \\
\feat{Arena Fighter}        & \feat{Improved Counterspell} \\
\feat{Arena Performer}      & \feat{Improved Dirty Trick}  \\
\feat{Armored Stealth}      & \feat{Improved Sigil}        \\
\feat{Brutal Attack}        & \feat{Innate Hunter}         \\
\feat{Bug Trainer}          & \feat{Kiltektet}             \\
\feat{Cloak Dance}          & \feat{Linguist}              \\
\feat{Cornered Fighter}     & \feat{Martial Performer}     \\
\feat{Deadly Precision}     & \feat{Mastyrial Blood}       \\
\feat{Defender of the Land} & \feat{Open Minded}           \\
\feat{Dissimulated}         & \feat{Protective}            \\
\feat{Drake's Child}        & \feat{Psionic Mimicry}       \\
\feat{Druidic Hunter}       & \feat{Raised by Beasts}      \\
\feat{Elemental Cleansing}  & \feat{Rapid Metabolism}      \\
\feat{Extra Music}          & \feat{Reckless Offense}      \\
\feat{Extra Performance}    & \feat{Rogue Performer}       \\
\feat{Faithful Follower}    & \feat{Sniper}                \\
\feat{Fearsome}             & \feat{Wastelander}           \\
\feat{Greasing the Wheels}  &\\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Skill Feats}\\
\feat{Field Officer} & \feat{Trader}\\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Racial Feats}\\
\feat{Active Glands}      & \feat{Hardened Body}       \\
\feat{Advanced Antennae}  & \feat{Improved Relisience} \\
\feat{Blend}              & \feat{Longshanks}          \\
\feat{Cannibalism Ritual} & \feat{Rock Throw}          \\
\feat{Dwarven Vision}     \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Fighter Feats}\\
\feat{Commanding Presence}   & \feat{Rotate Lines} \\
\feat{Concentrated Fire}     & \feat{Shield Evasion} \\
\feat{Implacable Defender}   & \feat{Shield Wall} \\
\feat{Greater Critical}      & \feat{Spear Wall} \\
\feat{Intimidating Presence} & \feat{Tactical Expertise} \\
\feat{Inspiring Presence}    & \feat{Teamwork} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Divine Feats}\\
\feat{Elemental Affinity} & \feat{Elemental Vengeance} \\
\feat{Elemental Might}    & \feat{Superior Blessing} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Psionic Feats}\\
\feat{Elemental Manifestation} & \feat{Improved Elf Run} \\
\feat{Focused Mind}            & \feat{Jump Charge} \\
\feat{Improved Dwarven Focus}  & \feat{Pterran Telepathy} \\
}

\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Item Creation Feats}\\
\feat{Craft Psionic Item} & \feat{Scribe Tattoo}\\
}

\subsection{Removed feats}
\begin{itemize*}
\item Craft Dorje
\item Craft Psicrown
\item Craft Psionic Arms and Armor
\item Craft Psionic Construct
\item Craft Universal Item
\item Imprint Stone
\end{itemize*}

\subsection{Changed feats}
\begin{itemize*}
	\item \textit{Psicrystal Affinity:} Changed personalities, so they can add +1 bonus to power checks of a single discipline.
	\item \textit{Scribe Tattoo:} Tattoos are permanent, and have increased cost.
	\item \textit{Metapsionic feats:} Psionics has been reworked, and now the additional costs are multiplied by 5.
	\item \textit{Urban Tracking:} Changed the community size labels, added megalopolis as the biggest size.
\end{itemize*}

\section{Prestige Classes}

\subsection{New Prestige Classes}
\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Prestige Classes}\\
Arch defiler           & Elite sniper\\
Arena champion         & Exterminator\\
Battle dancer          & Grove master\\
Beastmaster psionicist & Jazst\\
Cerulean               & Master scout\\
Chasseur               & Poisonmaster\\
Convict                & Psiologist\\
Divine mind            & Restorationist\\
Dune trader            & Sensei\\
Earth defender         & Shadow wizard\\
Elemental singer       & Wanderer\\
}

\subsection{Removed Prestige Classes}
\Table{}{XX}{
\multicolumn{2}{l}{\tableheader Prestige Classes}\\
Arcane Archer   & Duelist \\
Blackguard      & Dwarf Defender \\
Dragon Disciple & Eldritch Knight \\
}

\section{Equipment}
\begin{itemize*}
	\item Updated monetary system.
	\item Simple and martial crossbows function as composite bows, with a strength rating.
	\begin{itemize*}
		\item Light crossbows add Str modifier on damage.
		\item Heavy crossbows add 1.5 $\times$ Str modifier on damage.
		\item Fixed crossbows add 2 $\times$ Str modifier on damage.
	\end{itemize*}
	\item Metal weapons deal +1 damage.
	\item All shields (but not bucklers) give 1 more AC.
	\item Poisons can be crafted as masterwork, increasing save DC by 1.
	\item Drugs added, similar to poisons but give good effects at first.
	\item Metaempiric and psychoactive components added, as material components that enhance spells and psionic powers respectively.
	\item New special materials: dasl, drake ivory, gray-forged steel.
	\item Removed mithril.
\end{itemize*}

\section{Combat}
\begin{itemize*}
	\item Advantage and disadvantage instead of some bonuses.
	\begin{itemize*}
		\item Flanking gives advantage on attack rolls
		\item Lack of proficiency gives disadvantage on attack rolls
		\item Prone and squeezing give disadvantage on attack rolls
		\item Aid another gives either advantage to an ally or disadvantage to an opponent
		\item Wielding two-handed weapons gives advantage in disarm and sunder checks
		\item Wielding light weapons gives disadvantage in disarm and sunder checks
		\item Wielding an item that is not a melee weapon gives disadvantage on defending from disarm attempts
		\item Having more than two legs or being otherwise stable give advantage on defending from bull rush, overrun, and trip attempts
		\item Charging gives advantage to bull rush attempts
		\item Feinting against a creature of different shape gives disadvantage
	\end{itemize*}
\end{itemize*}

\section{Magic Items}
\begin{itemize*}
\item Added setting-specific magic items.
\item Removed magic items that did not belong to the setting:
	\begin{itemize*}
	\item Removed all magic items that refer to aquatic and freezing environments.
	\item Removed all magic items related to horses.
	\item Removed all magic items related to titans.
	\item Removed all magic items related to other religions (e.g. \emph{horns of Valhalla}).
	\item Removed all magic items made of iron.
	\item Removed all magical tomes and books.
	\item Removed \emph{elven chain}, \emph{candle of invocation}.
	\end{itemize*}
\item Changed intelligent items: they are functionally manifesters with a daily power point pool and known powers.
\item Changed cognizance crystals: increased the power point storage.
\item Added psionic tattoos: permanent psionic effects for personal maintainable powers.
\end{itemize*}


\section{Magic}
\begin{itemize*}
\item Spells have sensory effects that become greater with the spell level, so you can't easily hide the effects a high-level spell.
\item Arcane spell DCs and caster level checks receive modifiers depending on the environment.
\item \textbf{Defiling:} arcane spellcasters can impose penalties in a radius. It can be used to increase the caster level by 1.
\item Add Ritual descriptor, from \textbf{D\&D} 5e.
\item \spellref{raise dead}{Raise dead}, \spell{resurrection}, and \spell{true resurrection} belong to the necromancy school.
\end{itemize*}

\section{Psionics}
Most of the d20 System psionics mechanics was scraped, in an attempt to reconcile AD\&D's \emph{Complete Psionics Handbook} with D\&D 3.5's \emph{Expanded Psionics Handbook}.
\begin{itemize*}
\item Each discipline has a key ability.
\item Power check before manifesting, using the power's discipline key ability.
\item Manifestation cost is 5 $\times$ power level.
\item Maintenance cost returns, and it is equal to the power level.
\item Power points can be restored while resting, albeit in a very slow manner.
\item Psychic contests rules for targeting the same creature or object.
\item Telepathic attacks have special rules to allow for \emph{contacting} another mind.
\item Powers may have prerequisites, which one must know before learning the power.
\item There is no hard limit to learn a power, it only depends on the character's key ability and prerequisites.
\end{itemize*}

\section{Campaign}
\begin{itemize*}
\item All NPC classes collapsed under Settler.
\item Rules for Contacts---NPCs who can help the players periodically.
\item New system for Hirelings.
\item Settlement sizes refactored into tribes (small and large), villages, towns (small and large), cities (small and large), metropolis, and megalopolis.
\end{itemize*}

\section{Planes}
Heavy gravity incurs $-2$ circumstance penalty on all Strength- and Dexterity-based skill checks, not only on select skills.

\section{Traps}
\begin{itemize*}
\item Attack bonus greater than +24 are described for CR Modifiers.
\item Melee mechanical traps can have multiple attacks, up to 4.
\item Changed CR modifiers for poison, to use the same formula for {\tableheader Dark Sun} specific poisons.
\item Add new Craft (trapmaking) DC for high level mechanical traps.
\end{itemize*}

\section{Epic Levels}
The whole d20 System epic mechanics was scraped, and the new mechanics bring most of what was in \emph{Dragon Kings} into the d20 System.

\begin{itemize*}
\item Evolution up to 30th level, and no more than 30.
\item Base attack and save bonuses continue the normal progression.
\item Class features with any improvement rate, continue improving at the same rate.
\item Some previous epic feats were turned into class features (incite rage, deafening song, wild shape feats, etc).
\item \textbf{Psionic Enchantment:} 10th-level spells that require manifesting psionic powers.
\end{itemize*}
