\subsubsection{Jaguar}
\begin{MonsterStats}
{Medium Animal}
{4d8+8 (26 hp)}
{+3}
{12 m (8 squares), climb 6 m, swim 6 m}
{16 (+3 Dex, +3 natural), touch 13, flat-footed 13}
{+3/+8}
{Claw +8 melee (1d3+5)}
{2 claws +8 melee (1d3+5) and bite +3 melee (1d8+2)}
{1.5 m/1.5 m}
{Improved grab, pounce, rake 1d3+2}
{Low-light vision, scent}
{Fort +6, Ref +7, Will +2}
{Str 21, Dex 17, Con 15, Int 2, Wis 12, Cha 6}
{
    \skill{Balance} +11,
    \skill{Climb} +13,
    \skill{Hide} +8*,
    \skill{Jump} +17,
    \skill{Listen} +6,
    \skill{Move Silently} +7,
    \skill{Spot} +6,
    \skill{Swim} +13
}
{\feat{Alertness}, \feat{Improved Natural Attack} (bite)}
{Any land}
{Solitary or pair}
{2}
{None}
{Always neutral}
{5--6 HD (Large)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    These apex predators are about 1.8 meter long and weigh about 160 kilograms. Their activity depends on their prey, some hunt at night while others are active during the day.
}

\textbf{Improved Grab (Ex):} To use this ability, a jaguar must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can rake.

\textbf{Pounce (Ex):} If a jaguar charges a foe, it can make a full attack, including two rake attacks.

\textbf{Rake (Ex):} Attack bonus +8 melee, damage 1d3+2.

\textbf{Skills:} Jaguars have a +4 racial bonus on \skill{Hide} and \skill{Move Silently} checks. Jaguars have a +8 racial bonus on \skill{Balance}, \skill{Climb}, \skill{Jump}, and \skill{Swim} checks.

A jaguar can always choose to take 10 on a \skill{Climb} or \skill{Swim} check, even if rushed or threatened.

*In areas of tall grass or heavy undergrowth, the \skill{Hide} bonus improves to +8.

