\subsubsection{Lizard, Giant}
\begin{MonsterStats}
{Large Animal}
{3d8+15 (28 hp)}
{+7}
{12 m (8 squares), burrow 6 m}
{16 (-1 size, +3 Dex, +4 natural), touch 12, flat-footed 13}
{+2/+10}
{Bite +5 melee (1d8+6)}
{Bite +5 melee (1d8+6)}
{3 m/1.5 m}
{Improved grab, swallow whole}
{Low-light vision}
{Fort +8, Ref +6, Will +1}
{Str 18, Dex 17, Con 20, Int 1, Wis 10, Cha 9}
{\skill{Climb} +5, \skill{Hide} +4*, \skill{Listen} +4, \skill{Move Silently} +4, \skill{Spot} +3}
{\feat{Alertness}, \feat{Improved Initiative}}
{Deserts}
{Solitary, or herd (2--12)}
{2}
{None}
{Always neutral}
{4--6 HD (Large); 7--9 HD (Huge)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Giant lizards are just that---oversized versions of the numerous reptilian species that populate the Athasian landscape.

    These ponderous beasts are at home anywhere from the depths of the desert to the swamps and savannah beyond the Jagged Cliffs. The giant lizards are one of Athas' few success stories.
}

Like their smaller cousins, giant lizards fight aggressively with their bite attack, attempting to swallow whole any victim smaller than themselves.

\textbf{Improved Grab (Ex):} If the giant lizard hits with its bite it can initiate a grapple check as a free action without provoking an attack of opportunity. If it wins the grapple check it establishes a hold and can attempt to swallow whole the next round.

\textbf{Swallow Whole (Ex):} The giant lizard can try to swallow a grabbed opponent of Medium or smaller size by making a successful grapple check. Once inside, the opponent takes 1d6+4 points of crushing damage plus 1d8+4 points of acid damage per round from the giant lizard's digestive juices. A swallowed creature can cut its way out by dealing 15 points of damage to the giant lizard's digestive tract (AC 12). Once the creature exits, muscular action closes the hole; another swallowed opponent must cut its own way out. The giant lizard's gullet can hold 2 Medium, 4 Small, or 8 Tiny or smaller creatures.

\textbf{Skills:} *Giant lizards gain a +8 bonus to \skill{Hide} checks when attempting to hide in the sand.
