\subsubsection{Snake, Constrictor}
\begin{MonsterStats}
{Medium Animal}
{3d8+6 (19 hp)}
{+7}
{6 m (4 squares), climb 6 m, swim 6 m}
{15 (+3 Dex, +2 natural), touch 13, flat-footed 12}
{+2/+5}
{Bite +5 melee (1d3+4)}
{Bite +5 melee (1d3+4)}
{1.5 m/1.5 m}
{Constrict 1d3+4, improved grab}
{Scent}
{Fort +4, Ref +6, Will +2}
{Str 17, Dex 17, Con 13, Int 1, Wis 12, Cha 2}
{\skill{Balance} +11, \skill{Climb} +14, \skill{Hide} +10, \skill{Listen} +7, \skill{Spot} +7, \skill{Swim} +11}
{\feat{Alertness}, \feat{Improved Initiative}, \feat{Toughness}}
{Warm forests}
{Solitary}
{2}
{None}
{Always neutral}
{4--5 HD (Medium); 6--10 HD (Large)}
{---}
\end{MonsterStats}

\textbf{Constrict (Ex):} On a successful grapple check, a constrictor snake deals 1d3+4 points of damage.

\textbf{Improved Grab (Ex):} To use this ability, a constrictor snake must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can constrict.

\textbf{Skills:} Snakes have a +4 racial bonus on \skill{Hide}, \skill{Listen}, and \skill{Spot} checks and a +8 racial bonus on \skill{Balance} and \skill{Climb} checks.

A snake can always choose to take 10 on a \skill{Climb} check, even if rushed or threatened.

Snakes use either their Strength modifier or Dexterity modifier for \skill{Climb} checks, whichever is higher.

A snake has a +8 racial bonus on any \skill{Swim} check to perform some special action or avoid a hazard. It can always choose to take 10 on a \skill{Swim} check, even if distracted or endangered. It can use the run action while swimming, provided it swims in a straight line.
