\Spell{Awaken Water Spirits}{awaken water spirits}
{Transmutation [Water]}
{
	\textbf{Level:}
	Drd 6\\
	\textbf{Components:}
	V, S, DF\\
	\textbf{Casting Time:}
	1 hour\\
	\textbf{Range:}
	See text\\
	\textbf{Target:}
	1 body of water; see text\\
	\textbf{Duration:}
	Permanent\\
	\textbf{Saving Throw:}
	No\\
	\textbf{Spell Resistance:}
	No\\
}
{
	You give sentience to a natural body of water. To \emph{awaken} a body of water, you must touch the water's surface while calling on a water spirit.

	You can communicate with any body of water that you have \emph{awakened} from any distance on the same plane. \emph{Awakened water spirits} are initially friendly towards you, but not obliged to follow you. The \emph{awakened water spirit} has no offensive or defensive combat ability and cannot move; it has no Strength, Dexterity, or Constitution score. The \emph{awakened water spirit} has an Intelligence, Wisdom and Charisma of 3d6. The \emph{water spirit} can sense any creature within 60 meters of its location. The \emph{water spirit} can also channel spells cast by you. Any spell of 3rd level or lower can be cast through the \emph{water spirit} as if the caster was actually in the location of the \emph{water spirit}. The \emph{water spirit} must be willing for you to use this function of the spell.

	\spell{Dispel Magic} and similar spells and powers destroy the water spirit if successful---the water spirit gets no saving throw to resist being dispelled. The spirit is treated as a 10-HD creature for purposes of turning and rebuking water creatures.
}