\Spell{Bless Element}{bless element}
{Transmutation [Good]}
{
	\textbf{Level:}
	Clr 1\\
	\textbf{Components:}
	V, S, M, DF\\
	\textbf{Casting Time:}
	1 minute\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	Element touched\\
	\textbf{Duration:}
	Instantaneous\\
	\textbf{Saving Throw:}
	Will negates (object)\\
	\textbf{Spell Resistance:}
	Yes (object)\\
}
{
	This transmutation imbues a small amount (no more than 0.5 kg of solid, or 500 ml of fluid) of your patron element with positive energy, turning it into a holy element. Holy elements deal 2d4 points of damage to creatures vulnerable to them, such as undead and evil outsiders. Using a holy elçement in this way expends the positive energy. No matter the element, it functions as a grenade---like weapon with a range increment of 3 m and deals 1 point of splash damage to creatures within 1.5 m of impact. Specifics for the elements follow:

	\textit{Air:} An air cleric can bless the air around him. After this spell is cast, the air remains blessed for 1d4 minutes. As a standard action, the cleric can direct the blessed air at a creature.

	\textit{Earth:} An earth cleric can bless dirt, soil or sand.

	\textit{Fire:} A fire cleric can bless flames (ranging in size from candles to torches) or obsidian. Blessed fire may deal fire damage in addition to any damage to undead or evil outsiders.

	\textit{Magma:} A magma cleric can bless lava or any igneous rock. Blessed lava may deal fire damage in addition to any damage to undead or evil outsiders.

	\textit{Rain:} A rain cleric can bless rain in a 1.5-m---radius area within 9 m that is currently receiving rain.

	\textit{Silt:} A silt cleric can bless silt or dust.

	\textit{Sun:} A sun cleric can bless the light around him. The light remains blessed for 1d4 minutes. As a standard action, the cleric can direct the blessed light at a creature.

	\textit{Water:} A water cleric can bless water in a flask.

	Alternatively, he can throw a small amount of water into the air. This water forms a blessed cloud that lasts 1d4 minutes and can be directed as a standard action.

	\textit{Material Component:} A small amount of powdered silver worth 25 cp.
}
