\Spell{Brain Spider}{brain spider}
{Divination [Mind-Affecting]}
{
	\textbf{Level}: Clr 8, Mind 7\\
	\textbf{Components}: V, S, M, DF\\
	\textbf{Casting Time}: 1 round\\
	\textbf{Range}: Long (120 m + 12 m/level)\\
	\textbf{Targets}: Up to eight living creatures\\
	\textbf{Duration}: 1 min./level\\
	\textbf{Saving Throw}: Will negates\\
	\textbf{Spell Resistance}: Yes\\
}
{
	This spell allows you to eavesdrop as a standard action on the thoughts of up to eight other creatures at once, hearing as desired:
	\begin{itemize*}
		\item Individual trains of thought in whatever order you desire.
		\item Information from all minds about one particular topic, thing, or being, one nugget of information per caster level.
		\item A study of the thoughts and memories of one creature of the group in detail.
	\end{itemize*}

	Once per round, if you do not perform a detailed study of one creature’s mind, you can attempt (as a standard action) to implant a suggestion in the mind of any one of the affected creatures. The creature can make another Will saving throw to resist the suggestion, using the save DC of the brain spider spell. (Creatures with special resistance to enchantment spells can use this resistance to keep from being affected by the suggestion.) Success on this saving throw does not negate the other effects of the brain spider spell for that creature.

	You can affect all intelligent beings of your choice within range (up to the limit of eight), beginning with known or named beings. Language is not a barrier, and you need not personally know the beings The spell cannot reach those who make a successful Will save.

	\textit{Material Component}: A spider of any size or kind. It can be dead, but must still have all eight legs.
}