\Spell{Conversion}{conversion}
{Abjuration}
{
	\textbf{Level:}
	Drd 5\\
	\textbf{Components:}
	V, S, M, F, XP\\
	\textbf{Casting Time:}
	1 hour\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	Living creature touched\\
	\textbf{Duration:}
	Instantaneous\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	Yes (harmless)\\
}
{
	This spell removes the burden of acts of defiling from an arcane spellcaster. The wizard seeking atonement must be truly repentant and desirous of setting right their destruction of plant life. If the subject defiled while under some sort of magical or psionic compulsion or was otherwise unwilling, \emph{conversion} operates normally at no cost to you. However, if the defiling was deliberate and willful, you must expend personal energy to cleanse the subject. This costs the caster 500 XP to expunge the subject's taint of defiling. Naturally, many casters first assign the subject some sort of quest (via \spell{geas/quest}) or similar penance to make sure the creature is truly repentant before casting conversion on its behalf. The caster must be at least one level higher that the subject.

	\emph{Conversion} may be cast for one of several purposes, depending on being cast on a preserver or a defiler:	
	\begin{itemize*}
	\item \textit{Preserver:} This removes all taint of defiling from the spellcaster. Thus, the Will save DC to resist falling to the path of the defiler is now reset to 10 + level of spell cast by defiling.
	\item \textit{Defiler:} A repentant defiler becomes a preserver and can cast spells without damaging plant life.
	\end{itemize*}

	\textit{XP Cost:} When cast for the benefit of a creature whose guilt was the result of deliberate acts, the cost to you is 500 XP. If the subject is a defiler, this cost is doubled.

	\textit{Material Component:} Burning incense.

	\textit{Focus:} Rare plants and herbs worth at least 500 Cp.
}
