\Spell{Create Oasis}{create oasis}
{Conjuration (Creation)}
{
	\textbf{Level:}
	Drd 6\\
	\textbf{Components:}
	V, S, M, DF, XP\\
	\textbf{Casting Time:}
	10 minutes\\
	\textbf{Range:}
	See text\\
	\textbf{Effect:}
	A magic oasis\\
	\textbf{Duration:}
	See text\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	No\\
}
{
	You create a lush oasis within the confines of a ring of standing stones of your creation. The maximum radius of the oasis is 15 meters per caster level beyond 10th; you may create a smaller oasis if desired.

	Before the spell can be cast, you must erect a circle of stones. Each stone must be at least 3 meters tall and no more than 1 meter wide or thick, rough-hewn and oblong, and set into the ground to stand on end. Four stones must be placed around the area the oasis will fill: one to the north, east, south and west points of the oasis. Cutting and placing a single stone requires 48 worker-hours, provided stones are readily available in the area and the workers have appropriate tools (chisels, spikes, hammers, rollers). If tools or ready stones aren't available, this time may increase or, at the DM's discretion, the preparation may be impossible. Also, particularly skilled or capable workers may cut the time by as much as half. You can erect the stones yourself through physical or magical labor, or you may enlist the help of any number of other creatures. After the last stone is placed, you must cast create oasis from the exact center of the ring. Interruptions during the placement of stones do not negate the spell, provided all the stones are in place at the time of casting.

	Once cast, the circle inside the stones is instantly transformed into a plant-filled, water-rich oasis. The trees and bushes are laden with nourishing, delicious fruits, and small game birds and animals appear, supported by springs and pools of fresh, cool water. The oasis can also sustain one Medium creature for every 50 square feet of the oasis. Each night, lost animals, fruits, and water are automatically replenished. Defiling magic still causes permanent damage; subtract the damaged area when considering the oasis' ability to support living creatures.

	The oasis remains intact until you physically move beyond the ring of standing stones or until you voluntarily end the spell. Once ended, the oasis and the standing stones vanish, leaving the exact terrain that existed before. The spell also ends if you are slain.

	\textit{Material Component:} Four standing stones.

	\textit{XP Cost:} 100 XP per 15-m-radius of oasis created.
}
