\Spell{Elemental Armor}{elemental armor}
{Transmutation [see text]}
{
	\textbf{Level:}
	Clr 4\\
	\textbf{Components:}
	V, S, DF\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	Your shield or armor\\
	\textbf{Duration:}
	1 min./level\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	No\\
}
{
	Your armor glows with energy as it is imbued with elemental power, granting you additional protection. You imbue a suit of armor or a shield with the powers of your patron element or paraelement. The armor gains a +1 enhancement bonus for the duration of the spell, and an additional special quality depending on your patron element or paraelement (see the list below). You become proficient in the armor this spell is cast upon for the duration of the spell. Creatures other than you wearing the armor enjoy no benefits from the spell's effects. At 9th level and every 3 levels thereafter, the enhancement bonus of the armor or shield increases by 1, to a maximum of +5 at 18th level.
	\begin{itemize*}
	\item \textit{Air:} Ghost touch.
	\item \textit{Earth:} Moderate fortification.
	\item \textit{Fire:} Fire resistance.
	\item \textit{Magma:} Fire resistance.
	\item \textit{Rain:} Electricity resistance.
	\item \textit{Silt:} Acid resistance.
	\item \textit{Sun:} Gleaming*.
	\item \textit{Water:} Cold resistance.
	\end{itemize*}

	* This property can be applied to shields with \emph{elemental armor}.

	This spell's subtype is the same as the type of energy you cast.
}
