\Spell{Elemental Chariot, Greater}{greater elemental chariot}
{Transmutation [see text]}
{
	\textbf{Level:}
	Clr 7\\
	\textbf{Duration:}
	1 hour/level\\
}
{

	This spell functions as \spell{elemental chariot}, except as noted above and as follows.

	The spell provides the following additional benefits depending on the element imbued:
	\begin{itemize*}
	\item \textit{Air:} The chariot and crodlu gain a fly speed equal to the crodlu's base land speed (poor maneuverability).
	\item \textit{Earth:} The chariot and crodlu can burrow through earth or solid rock at the crodlu's base land speed. The chariot leaves no tunnel.
	\item \textit{Fire:} You can concentrate to make the chariot leave a \spell{wall of fire} in its wake (on one edge of each square it leaves). This fire acts as the spell, except that it emits heat at half range on both sides and lasts 1 round per caster level. The chariot cannot leave a wake two rounds in a row.
	\item \textit{Magma:} You can concentrate to make the chariot leave molten lava in its wake (on one edge of each square it leaves) that takes 1 round per caster level to cool. Heat rising from the lava has the same effect as a \spell{wall of fire}, as the spell, except it emits heat at half range on both sides.
	\item The chariot cannot leave a wake two rounds in a row.
	\item \textit{Silt:} You can concentrate to make the chariot leave a wake of \spell{cloudkill}. This wake acts as the spell, except that it only fills each square the chariot leaves, the cloud doesn't move, and it lasts 1 round per caster level. The chariot cannot leave a wake two rounds in a row.
	\item \textit{Sun:} The chariot shines with such dazzling brightness that anyone within 18 meters that looks directly at the chariot must make a Fortitude save or be blinded for 1d4 rounds. Those who succeed at the save are instead dazzled for the same duration.
	\item \textit{Water or Rain:} The chariot, crodlu, and crew all enjoy the benefits of the \spell{displacement} spell, and the chariot may pass underwater for up to 1 round per caster level at a time without the animals or passengers needing air. The chariot and crodlu have a swim speed equal to the crodlu's base land speed.
	\end{itemize*}

	This spell's subtype is the same as the type of energy you cast.
}
