\Spell{Feather Fall}{feather fall}
{Transmutation}
{
	\textbf{Level:}
	Ass 1, Forecasting 1, Wiz 1\\
	\textbf{Components:}
	V\\
	\textbf{Casting Time:}
	1 immediate action\\
	\textbf{Range:}
	Close (7.5 m + 1.5 m/2 levels)\\
	\textbf{Targets:}
	One Medium or smaller freefalling object or creature/level, no two of which may be more than 6 m apart\\
	\textbf{Duration:}
	Until landing or 1 round/level\\
	\textbf{Saving Throw:}
	Will negates (harmless) or Will negates (object)\\
	\textbf{Spell Resistance:}
	Yes (object)\\
}
{
	The affected creatures or objects fall slowly. \emph{Feather fall} instantly changes the rate at which the targets fall to a mere 18 meters per round (equivalent to the end of a fall from a few feet), and the subjects take no damage upon landing while the spell is in effect. However, when the spell duration expires, a normal rate of falling resumes.

	The spell affects one or more Medium or smaller creatures (including gear and carried objects up to each creature's maximum load) or objects, or the equivalent in larger creatures: A Large creature or object counts as two Medium creatures or objects, a Huge creature or object counts as two Large creatures or objects, and so forth.

	You can cast this spell with an instant utterance, quickly enough to save yourself if you unexpectedly fall. Casting the spell is a immediate action, allowing you to cast this spell even when it isn't your turn.

	This spell has no special effect on ranged weapons unless they are falling quite a distance. If the spell is cast on a falling item the object does half normal damage based on its weight, with no bonus for the height of the drop.

	\emph{Feather fall} works only upon free-falling objects. It does not affect a sword blow or a charging or flying creature.

}
