\Spell{Fire Track}{fire track}
{Divination [Fire]}
{
    \textbf{Level:}
    Wrath 4\\
    \textbf{Components:}
    V, S, M, DF\\
    \textbf{Casting Time:}
    1 round\\
    \textbf{Range:}
    Medium (30 m + 3 m/level)\\
    \textbf{Target:}
    One creature\\
    \textbf{Duration:}
    1 round/level\\
    \textbf{Saving Throw:}
    None\\
    \textbf{Spell Resistance:}
    Yes\\
}
{
    The caster identifies a target when casting the spell, either by name or by physical description (e.g., ``the man who stole the high templar's purse today,'' or ``the woman I saw wearing the gray eye patch''). A spark of flame appears harmlessly at the caster's fingertip---the faithful ``hound'' ready for the hunt.

    If the target has not been within range during the last 24 hours, then the flame leaps off the caster's finger, lands on the ground nearby, and extinguishes itself. If the target has been within range, the flame leaps off the caster's fingertip and flies toward the target's trail, striking the ground as soon as it ``picks up the scent.''

    The \emph{fire track} is like a brilliant flame traveling along a fuse. In its wake is a faint line of scorched earth and dust, marking the path of its prey. (The scorch marks are easily swept clean.) The flame moves from 0 to 72 meters per round, at a speed chosen by the caster, which can be changed as a free action once per round. The \emph{fire track} burns with the strength and brightness of a torch. It inflicts 1d6 points of damage upon those who get in its way and sets combustible materials aflame. (A wise spellcaster does not use this spell to investigate burglaries in a cotton warehouse.)

    The \emph{fire track} can be foiled in a number of ways. It cannot cross water and is extinguished by doing so, but it can cross silt. It can be snuffed out while in motion by strong breezes, blowing sand, and heavy rain. If the pursued individual takes to the air or \spellref[teleport]{teleports}, the \emph{fire track} circles in place until its time expires. Mere climbing, leaping, or jumping (even across a chasm), however, cannot foil the \emph{fire track}, which always pursues in the correct direction.

    \textit{Material Component:} A fragment of antennae from a cilops, wrapped in wax. The wax is melted to cast the spell.
}
