\Spell{Fire Trap}{fire trap}
{Abjuration [Fire, Ritual]}
{
	\textbf{Level:}
	Cleansing 2, Drd 2, Rng 2, Wiz 4\\
	\textbf{Components:}
	V, S, M\\
	\textbf{Casting Time:}
	10 minutes\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	Object touched\\
	\textbf{Duration:}
	Permanent until discharged (D)\\
	\textbf{Saving Throw:}
	Reflex half; see text\\
	\textbf{Spell Resistance:}
	Yes\\
}
{
	\emph{Fire trap} creates a fiery explosion when an intruder opens the item that the trap protects. A \emph{fire trap} can ward any object that can be opened and closed.

	When casting \emph{fire trap}, you select a point on the object as the spell's center. When someone other than you opens the object, a fiery explosion fills the area within a 1.5-meter radius around the spell's center. The flames deal 1d4 points of fire damage +1 point per caster level (maximum +20). The item protected by the trap is not harmed by this explosion.

	A \emph{fire trapped} item cannot have a second closure or warding spell placed on it.

	A \spell{knock} spell does not bypass a \emph{fire trap}.  An unsuccessful \spell{dispel magic} spell does not detonate the spell.

	Underwater, this ward deals half damage and creates a large cloud of steam.

	You can use the \emph{fire trapped} object without discharging it, as can any individual to whom the object was specifically attuned when cast. Attuning a \emph{fire trapped} object to an individual usually involves setting a password that you can share with friends.

	\textit{Note:} Magic traps such as \emph{fire trap} are hard to detect and disable. A rogue (only) can use the \skill{Search} skill to find a \emph{fire trap} and \skill{Disable Device} to thwart it. The DC in each case is 25 + spell level (DC 27 for a druid's fire trap or DC 29 for the arcane version).

	\textit{Material Component:}
	A half-pound of gold dust (cost 25 gp) sprinkled on the warded object.

}
