\Spell{Forcecage}{forcecage}
{Evocation [Force]}
{
	\textbf{Level:}
	Wiz 7\\
	\textbf{Components:}
	V, S, M\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Close (7.5 m + 1.5 m/2 levels)\\
	\textbf{Area:}
	Barred cage (6-m cube) or windowless cell (10-ft. cube)\\
	\textbf{Duration:}
	2 hours/level (D)\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	No\\
}
{
	This powerful spell brings into being an immobile, invisible cubical prison composed of either bars of force or solid walls of force (your choice).

	Creatures within the area are caught and contained unless they are too big to fit inside, in which case the spell automatically fails. Teleportation and other forms of astral travel provide a means of escape, but the force walls or bars extend into the Ethereal Plane, blocking ethereal travel.

	Like a wall of force spell, a forcecage resists dispel magic, but it is vulnerable to a disintegrate spell, and it can be destroyed by a sphere of annihilation or a rod of cancellation.

	\textit{Barred Cage}:
	This version of the spell produces a 6-meter cube made of bands of force (similar to a wall of force spell) for bars. The bands are a half-inch wide, with half-inch gaps between them. Any creature capable of passing through such a small space can escape; others are confined. You can't attack a creature in a barred cage with a weapon unless the weapon can fit between the gaps. Even against such weapons (including arrows and similar ranged attacks), a creature in the barred cage has cover. All spells and breath weapons can pass through the gaps in the bars.

	\textit{Windowless Cell}:
	This version of the spell produces a 3-meter cube with no way in and no way out. Solid walls of force form its six sides.

	\textit{Material Component}:
	Ruby dust worth 1,500 gp, which is tossed into the air and disappears when you cast the spell.

}
