\Spell{Guards and Wards}{guards and wards}
{Abjuration [Ritual]}
{
	\textbf{Level:}
	Wiz 6\\
	\textbf{Components:}
	V, S, M, F\\
	\textbf{Casting Time:}
	30 minutes\\
	\textbf{Range:}
	Anywhere within the area to be warded\\
	\textbf{Area:}
	Up to 18 m$^2$/level (S)\\
	\textbf{Duration:}
	2 hours/level (D)\\
	\textbf{Saving Throw:}
	See text\\
	\textbf{Spell Resistance:}
	See text\\
}
{
	This powerful spell is primarily used to defend your stronghold. The ward protects 18 square meters per caster level. The warded area can be as much as 6 meters high, and shaped as you desire. You can ward several stories of a stronghold by dividing the area among them; you must be somewhere within the area to be warded to cast the spell. The spell creates the following magical effects within the warded area.

	\textit{Fog:}
	Fog fills all corridors, obscuring all sight, including darkvision, beyond 1.5 meter. A creature within 1.5 meter has concealment (attacks have a 20\% miss chance). Creatures farther away have total concealment (50\% miss chance, and the attacker cannot use sight to locate the target). Saving Throw: None. Spell Resistance: No.

	\textit{Arcane Locks:}
	All doors in the warded area are \spellref{arcane lock}{arcane locked}. Saving Throw: None. Spell Resistance: No.

	\textit{Webs:}
	Webs fill all stairs from top to bottom. These strands are identical with those created by the \spell{web} spell, except that they regrow in 10 minutes if they are burned or torn away while the \emph{guards and wards} spell lasts. Saving Throw: Reflex negates; see text for \spell{web}. Spell Resistance: No.

	\textit{Confusion:}
	Where there are choices in direction---such as a corridor intersection or side passage---a minor confusion-type effect functions so as to make it 50\% probable that intruders believe they are going in the opposite direction from the one they actually chose. This is an enchantment, mind-affecting effect. Saving Throw: None. Spell Resistance: Yes.

	\textit{Lost Doors:}
	One door per caster level is covered by a \spell{silent image} to appear as if it were a plain wall. Saving Throw: Will disbelief (if interacted with). Spell Resistance: No.

	In addition, you can place your choice of one of the following five magical effects.

	\begin{enumerate*}
		\item \spellref{dancing lights}{Dancing lights} in four corridors. You can designate a simple program that causes the lights to repeat as long as the \emph{guards and wards} spell lasts. Saving Throw: None. Spell Resistance: No.
		\item A \spell{magic mouth} in two places. Saving Throw: None. Spell Resistance: No.
		\item A \spell{stinking cloud} in two places. The vapors appear in the places you designate; they return within 10 minutes if dispersed by wind while the \emph{guards and wards} spell lasts. Saving Throw: Fortitude negates; see text for stinking cloud. Spell Resistance: No.
		\item A \spell{gust of wind} in one corridor or room. Saving Throw: Fortitude negates. Spell Resistance: Yes.
		\item A \spell{suggestion} in one place. You select an area of up to 1.5 meter square, and any creature who enters or passes through the area receives the suggestion mentally. Saving Throw: Will negates. Spell Resistance: Yes.
	\end{enumerate*}

	The whole warded area radiates strong magic of the abjuration school. A \spell{dispel magic} cast on a specific effect, if successful, removes only that effect. A successful \spell{disjunction} destroys the entire \emph{guards and wards} effect.

	\textit{Material Component:}
	Burning incense, a small measure of brimstone and oil, a knotted string, and a small amount of blood.

	\textit{Focus:}
	A small silver rod.

}
