\Spell{Hallow}{hallow}
{Evocation [Good]}
{
	\textbf{Level:}
	Clr 5, Drd 5\\
	\textbf{Components:}
	V, S, M, DF\\
	\textbf{Casting Time:}
	24 hours\\
	\textbf{Range:}
	Touch\\
	\textbf{Area:}
	12-m radius emanating from the touched point\\
	\textbf{Duration:}
	Instantaneous\\
	\textbf{Saving Throw:}
	See text\\
	\textbf{Spell Resistance:}
	See text\\
}
{
	\emph{Hallow} makes a particular site, building, or structure a holy site. This has four major effects.

	First, the site or structure is guarded by a \spell{magic circle against evil} effect.

	Second, all Charisma checks made to turn undead gain a +4 sacred bonus, and Charisma checks to command undead take a $-4$ penalty. Spell resistance does not apply to this effect. (This provision does not apply to the druid version of the spell.)

	Third, any dead body interred in a hallowed site cannot be turned into an undead creature.

	Finally, you may choose to fix a single spell effect to the hallowed site. The spell effect lasts for one year and functions throughout the entire site, regardless of the normal duration and area or effect. You may designate whether the effect applies to all creatures, creatures who share your faith or alignment, or creatures who adhere to another faith or alignment. At the end of the year, the chosen effect lapses, but it can be renewed or replaced simply by casting \emph{hallow} again.

	Spell effects that may be tied to a hallowed site include \spell{aid}, \spell{bane}, \spell{bless}, \spell{cause fear}, \spell{darkness}, \spell{daylight}, \spell{death ward}, \spell{deeper darkness}, \spell{detect evil}, \spell{detect magic}, \spell{dimensional anchor}, \spell{discern lies}, \spell{dispel magic}, \spell{endure elements}, \spell{freedom of movement}, \spell{invisibility purge}, \spell{protection from energy}, \spell{remove fear}, \spell{resist energy}, \spell{silence}, \spell{tongues}, and \spell{zone of truth}. Saving throws and spell resistance might apply to these spells' effects. (See the individual spell descriptions for details.)

	An area can receive only one \emph{hallow} spell (and its associated spell effect) at a time. \emph{Hallow} counters but does not dispel \spell{unhallow}.

	\textit{Material Component:}
	Herbs, oils, and incense worth at least 1,000 cp, plus 1,000 cp per level of the spell to be included in the hallowed area.

}
