\Spell{Limited Wish}{limited wish}
{Universal}
{
	\textbf{Level:}
	Wiz 7\\
	\textbf{Components:}
	V, S, XP\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	See text\\
	\textbf{Target, Effect, or Area:}
	See text\\
	\textbf{Duration:}
	See text\\
	\textbf{Saving Throw:}
	None; see text\\
	\textbf{Spell Resistance:}
	Yes\\
}
{
	A \emph{limited wish} lets you create nearly any type of effect. For example, a \emph{limited wish} can do any of the following things.

	\begin{itemize*}
	\item Duplicate any wizard spell of 6th level or lower, provided the spell is not of a school prohibited to you.
	\item Duplicate any other spell of 5th level or lower, provided the spell is not of a school prohibited to you.
	\item Duplicate any wizard spell of 5th level or lower, even if it's of a prohibited school.
	\item Duplicate any other spell of 4th level or lower, even if it's of a prohibited school.
	\item Undo the harmful effects of many spells, such as geas/quest or insanity.
	\item Produce any other effect whose power level is in line with the above effects, such as a single creature automatically hitting on its next attack or taking a $-7$ penalty on its next saving throw.
	\end{itemize*}

	A duplicated spell allows saving throws and spell resistance as normal (but the save DC is for a 7th-level spell). When a \emph{limited wish} duplicates a spell that has an XP cost, you must pay that cost or 300 XP, whichever is more. When a \emph{limited wish} spell duplicates a spell with a material component that costs more than 1,000 cp, you must provide that component.

	\textit{XP Cost}:
	300 XP or more (see above).

}
