\Spell{Mental Pinnacle}{mental pinnacle}
{Transmutation}
{
	\textbf{Level:} Wiz 6\\
	\textbf{Components:} V, S, M\\
	\textbf{Casting Time:} 1 standard action\\
	\textbf{Range:} Personal\\
	\textbf{Target:} You\\
	\textbf{Duration:} 1 round/level\\
}
{
	For a brief time, you achieve the mental dominance of a powerful psion, able to lash out at enemies using only the power of your mind. Your revel in your new mental powers to the point that you disdain using spells, even in the form of effects from magic items. You gain a +4 enhancement bonus to Intelligence and Wisdom, 3 power points per caster level, and access to the following powers.

	\begin{itemize*}
		\item \psionic{Mind Thrust}\textsuperscript{A:} Deal 1d10 damage.
		\item \psionic{Ego Whip}\textsuperscript{A:} Deal 1d4 Cha damage and daze for 1 round.
		\item \psionic{Psionic Blast}\textsuperscript{A:} Stun creatures in 9-m cone for 1 round.
		\item \psionic{Id Insinuation}\textsuperscript{A:} Swift tendrils of thought disrupt and confuse your target.
		\item \psionic{Psychic Crush}\textsuperscript{A:} Brutally crush subject's mental essence, reducing subject to $-1$ hit points.
	\end{itemize*}

	You manifest the powers as a psion of your caster level does, creating displays as described in each power's description. You lose your spellcasting ability, including your ability to use spell trigger or spell completion magic items, just as if those spells were no longer on your class list. For the duration of this spell, you use magic items and psionic items as if you were a psion with only the five powers given above on your class list.

	Any unspent power points dissipate when the spell ends.

	\textit{Material Component:} A potion of \spell{fox's cunning}, which you drink (its effect is overridden by the effect of this spell).
}