\Spell{Phantom Steed}{phantom steed}
{Conjuration (Creation)}
{
	\textbf{Level:}
	Travel 3, Wiz 3\\
	\textbf{Components:}
	V, S\\
	\textbf{Casting Time:}
	10 minutes\\
	\textbf{Range:}
	0 m\\
	\textbf{Effect:}
	One quasi-real, horselike creature\\
	\textbf{Duration:}
	1 hour/level (D)\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	No\\
}
{
	You conjure a Large, quasi-real, horselike creature. The steed can be ridden only by you or by the one person for whom you specifically created the mount. A phantom steed has a black head and body, gray mane and tail, and smoke-colored, insubstantial hooves that make no sound. It has what seems to be a saddle, bit, and bridle. It does not fight, but animals shun it and refuse to attack it.

	The mount has an AC of 18 (-1 size, +4 natural armor, +5 Dex) and 7 hit points +1 hit point per caster level. If it loses all its hit points, the phantom steed disappears. A phantom steed has a speed of 6 meters per caster level, to a maximum of 72 meters. It can bear its rider's weight plus up to 5 kilograms per caster level.

	These mounts gain certain powers according to caster level. A mount's abilities include those of mounts of lower caster levels.

	\textit{8th Level:}
	The mount can ride over sandy, muddy, or even swampy ground without difficulty or decrease in speed.

	\textit{10th Level:}
	The mount can use water walk at will (as the spell, no action required to activate this ability).

	\textit{12th Level:}
	The mount can use air walk at will (as the spell, no action required to activate this ability) for up to 1 round at a time, after which it falls to the ground.

	\textit{14th Level:}
	The mount can fly at its speed (average maneuverability).

}
