\Spell{Polymorph Any Object}{polymorph any object}
{Transmutation}
{
	\textbf{Level:}
	Wiz 8, Trickery 8\\
	\textbf{Components:}
	V, S, M/DF\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Close (7.5 m + 1.5 m/2 levels)\\
	\textbf{Target:}
	One creature, or one nonmagical object of up to 100 cu. ft./level\\
	\textbf{Duration:}
	See text\\
	\textbf{Saving Throw:}
	Fortitude negates (object); see text\\
	\textbf{Spell Resistance:}
	Yes (object)\\
}
{
	This spell functions like \spell{polymorph}, except that it changes one object or creature into another. The duration of the spell depends on how radical a change is made from the original state to its enchanted state. The duration is determined by using the following guidelines.

\Table{}{XX}{
	\tableheader Changed Subject Is: & \tableheader Increase to Duration Factor\footnotemark[1]\\
	Same kingdom (animal, vegetable, mineral) & +5\\
	Same class (mammals, fungi, metals, etc.) & +2\\
	Same size & +2\\
	Related (twig is to tree, wolf fur is to wolf, etc.) & +2\\
	Same or lower Intelligence & +2\\

\TableNote{2}{1 Add all that apply. Look up the total on the next table.}
}

\Table{}{XXX}{
\tableheader Duration Factor & \tableheader Duration & \tableheader Example\\
	0 & 20 minutes & Pebble to human\\
	2 & 1 hour & Marionette to human\\
	4 & 3 hours & Human to marionette\\
	5 & 12 hours & Lizard to manticore\\
	6 & 2 days & Sheep to wool coat\\
	7 & 1 week & Shrew to manticore\\
	9+ & Permanent & Manticore to shrew\\
}

	Unlike polymorph, polymorph any object does grant the creature the Intelligence score of its new form. If the original form didn't have a Wisdom or Charisma score, it gains those scores as appropriate for the new form.

	Damage taken by the new form can result in the injury or death of the polymorphed creature. In general, damage occurs when the new form is changed through physical force.

	A nonmagical object cannot be made into a magic item with this spell. Magic items aren't affected by this spell.

	This spell cannot create material of great intrinsic value, such as copper, silver, gems, silk, gold, platinum, mithral, or adamantine. It also cannot reproduce the special properties of cold iron in order to overcome the damage reduction of certain creatures.

	This spell can also be used to duplicate the effects of baleful polymorph, polymorph, flesh to stone, stone to flesh, transmute mud to rock, transmute metal to wood, or transmute rock to mud.

	\textit{Arcane Material Component}:
	Mercury, gum arabic, and smoke.

}
