\Spell{Simulacrum}{simulacrum}
{Illusion (Shadow)}
{
	\textbf{Level:}
	Mirage 8, Wiz 7\\
	\textbf{Components:}
	V, S, M, XP\\
	\textbf{Casting Time:}
	12 hours\\
	\textbf{Range:}
	0 m\\
	\textbf{Effect:}
	One duplicate creature\\
	\textbf{Duration:}
	Instantaneous\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	No\\
}
{
	\emph{Simulacrum} creates an illusory duplicate of any creature. The duplicate creature is partially real and formed from ice or snow. It appears to be the same as the original, but it has only one-half of the real creature's levels or Hit Dice (and the appropriate hit points, feats, skill ranks, and special abilities for a creature of that level or HD). You can't create a \emph{simulacrum} of a creature whose Hit Dice or levels exceed twice your caster level. You must make a \skill{Disguise} check when you cast the spell to determine how good the likeness is. A creature familiar with the original might detect the ruse with a successful \skill{Spot} check (opposed by the caster's \skill{Disguise} check) or a DC 20 \skill{Sense Motive} check.

	At all times the \emph{simulacrum} remains under your absolute command. No special telepathic link exists, so command must be exercised in some other manner. A \emph{simulacrum} has no ability to become more powerful. It cannot increase its level or abilities. If reduced to 0 hit points or otherwise destroyed, it reverts to snow and melts instantly into nothingness. A complex process requiring at least 24 hours, 100 cp per hit point, and a fully equipped magical laboratory can repair damage to a \emph{simulacrum}.

	\textit{Material Component:}
	The spell is cast over the rough snow or ice form, and some piece of the creature to be duplicated (hair, nail, or the like) must be placed inside the snow or ice. Additionally, the spell requires powdered ruby worth 100 cp per HD of the \emph{simulacrum} to be created.

	\textit{XP Cost:}
	100 XP per HD of the \emph{simulacrum} to be created (minimum 1,000 XP).

}
