\Spell{Spike Growth}{spike growth}
{Transmutation}
{
	\textbf{Level:}
	Drd 3, Rgr 2\\
	\textbf{Components:}
	V, S, DF\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Medium (30 m + 3 m/level)\\
	\textbf{Area:}
	One 6-m square/level\\
	\textbf{Duration:}
	1 hour/level (D)\\
	\textbf{Saving Throw:}
	Reflex partial\\
	\textbf{Spell Resistance:}
	Yes\\
}
{
	Any ground-covering vegetation in the spell's area becomes very hard and sharply pointed without changing its appearance.

	In areas of bare earth, roots and rootlets act in the same way. Typically, \emph{spike growth} can be cast in any outdoor setting except open water, ice, heavy snow, sandy desert, or bare stone. Any creature moving on foot into or through the spell's area takes 1d4 points of piercing damage for each 1.5 meter of movement through the spiked area.

	Any creature that takes damage from this spell must also succeed on a Reflex save or suffer injuries to its feet and legs that slow its land speed by one-half. This speed penalty lasts for 24 hours or until the injured creature receives a cure spell (which also restores lost hit points). Another character can remove the penalty by taking 10 minutes to dress the injuries and succeeding on a \skill{Heal} check against the spell's save DC.

	\emph{Spike growth} can't be disabled with the \skill{Disable Device} skill.

	\textit{Note:} Magic traps such as \emph{spike growth} are hard to detect. A rogue (only) can use the \skill{Search} skill to find a \emph{spike growth}. The DC is 25 + spell level, or DC 28 for \emph{spike growth} (or DC 27 for \emph{spike growth} cast by a ranger).

}
