\Spell{Summon Monster I}{summon monster i}
{



May be summoned only into an aquatic or watery environment.

	\\


Monster
Alignment
	Celestial dog\\
	LG\\
	Celestial owl\\
	LG\\
	Celestial giant fire beetle\\
	NG\\
	Celestial porpoise1\\
	NG\\
	Celestial badger\\
	CG\\
	Celestial monkey\\
	CG\\
	Fiendish dire rat\\
	LE\\
	Fiendish raven\\
	LE\\
	Fiendish monstrous centipede, Medium\\
	NE\\
	Fiendish monstrous scorpion, Small\\
	NE\\
	Fiendish hawk\\
	CE\\
	Fiendish monstrous spider, Small\\
	CE\\
	Fiendish octopus1\\
	CE\\
	Fiendish snake, Small viper\\
	CE\\

}
{
{Conjuration (Summoning) [see text]}
{
	\textbf{Level:}
	Clr 1, Wiz 1\\
	\textbf{Components:}
	V, S, F/DF\\
	\textbf{Casting Time:}
	1 round\\
	\textbf{Range:}
	Close (7.5 m + 1.5 m/2 levels)\\
	\textbf{Effect:}
	One summoned creature\\
	\textbf{Duration:}
	1 round/level (D)\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	No\\
}
{
	This spell summons an extraplanar creature (typically an outsider, elemental, or magical beast native to another plane). It appears where you designate and acts immediately, on your turn. It attacks your opponents to the best of its ability. If you can communicate with the creature, you can direct it not to attack, to attack particular enemies, or to perform other actions.

	The spell conjures one of the creatures from the 1st-level list on the accompanying Summon Monster table. You choose which kind of creature to summon, and you can change that choice each time you cast the spell.

	A summoned monster cannot summon or otherwise conjure another creature, nor can it use any teleportation or planar travel abilities. Creatures cannot be summoned into an environment that cannot support them.

	When you use a summoning spell to summon an air, chaotic, earth, evil, fire, good, lawful, or water creature, it is a spell of that type.

	\textit{Arcane Focus:}
	A tiny bag and a small (not necessarily lit) candle.

}
