\Spell{Telekinetic Sphere}{telekinetic sphere}
{Evocation [Force]}
{
	\textbf{Level:}
	Wiz 8\\
	\textbf{Components:}
	V, S, M\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Close (7.5 m + 1.5 m/2 levels)\\
	\textbf{Effect:}
	1-ft.-diameter/level sphere, centered around creatures or objects\\
	\textbf{Duration:}
	1 min./level (D)\\
	\textbf{Saving Throw:}
	Reflex negates (object)\\
	\textbf{Spell Resistance:}
	Yes (object)\\
}
{
	This spell functions like resilient sphere, with the addition that the creatures or objects inside the globe are nearly weightless. Anything contained within an telekinetic sphere weighs only one-sixteenth of its normal weight. You can telekinetically lift anything in the sphere that normally weighs 2,500 kilograms or less. The telekinetic control extends from you out to medium range (30 meters + 3 meters per caster level) after the sphere has succeeded in encapsulating its contents.

	You can move objects or creatures in the sphere that weigh a total of 2,500 kilograms or less by concentrating on the sphere. You can begin moving a sphere in the round after casting the spell. If you concentrate on doing so (a standard action), you can move the sphere as much as 9 meters in a round. If you cease concentrating, the sphere does not move in that round (if on a level surface) or descends at its falling rate (if aloft) until it reaches a level surface, or the spell's duration expires, or you begin concentrating again. If you cease concentrating (voluntarily or due to failing a \skill{Concentration} check), you can resume concentrating on your next turn or any later turn during the spell's duration.

	The sphere falls at a rate of only 18 meters per round, which is not fast enough to cause damage to the contents of the sphere.

	You can move the sphere telekinetically even if you are in it.

	\textit{Material Component}:
	A hemispherical piece of clear crystal, a matching hemispherical piece of gum arabic, and a pair of small bar magnets.

}
