\Spell{True Seeing}{true seeing}
{Divination [Ritual]}
{
	\textbf{Level:}
	Clr 5, Drd 7, Knowledge 5, Wiz 6\\
	\textbf{Components:}
	V, S, M\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Touch\\
	\textbf{Target:}
	Creature touched\\
	\textbf{Duration:}
	1 min./level\\
	\textbf{Saving Throw:}
	Will negates (harmless)\\
	\textbf{Spell Resistance:}
	Yes (harmless)\\
}
{
	You confer on the subject the ability to see all things as they actually are. The subject sees through normal and magical darkness, notices secret doors hidden by magic, sees the exact locations of creatures or objects under \spell{blur} or \spell{displacement} effects, sees invisible creatures or objects normally, sees through illusions, and sees the true form of \spellref{polymorph}{polymorphed}, changed, or transmuted things. Further, the subject can focus its vision to see into the Ethereal Plane (but not into extradimensional spaces). The range of \emph{true seeing} conferred is 36 meters.

	\emph{True seeing}, however, does not penetrate solid objects. It in no way confers X-ray vision or its equivalent. It does not negate concealment, including that caused by fog and the like. \emph{True seeing} does not help the viewer see through mundane disguises, spot creatures who are simply hiding, or notice secret doors hidden by mundane means. In addition, the spell effects cannot be further enhanced with known magic, so one cannot use \emph{true seeing} through a crystal ball or in conjunction with \spell{clairaudience/clairvoyance}.

	\textit{Material Component:}
	An ointment for the eyes that costs 250 cp and is made from mushroom powder, saffron, and fat.

}
