\Spell{Wall of Fire}{wall of fire}
{Evocation [Fire]}
{
	\textbf{Level:}
	Drd 5, Fire 4, Wiz 4\\
	\textbf{Components:}
	V, S, M/DF\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Medium (30 m + 3 m/level)\\
	\textbf{Effect:}
	Opaque sheet of flame up to 6 m long/level or a ring of fire with a radius of up to 1.5 m per two levels; either form 6 m high\\
	\textbf{Duration:}
	Concentration + 1 round/level\\
	\textbf{Saving Throw:}
	None\\
	\textbf{Spell Resistance:}
	Yes\\
}
{
	An immobile, blazing curtain of shimmering violet fire springs into existence. One side of the wall, selected by you, sends forth waves of heat, dealing 2d4 points of fire damage to creatures within 3 meters and 1d4 points of fire damage to those past 3 meters but within 6 meters. The wall deals this damage when it appears and on your turn each round to all creatures in the area. In addition, the wall deals 2d6 points of fire damage +1 point of fire damage per caster level (maximum +20) to any creature passing through it. The wall deals double damage to undead creatures.

	If you evoke the wall so that it appears where creatures are, each creature takes damage as if passing through the wall. If any 1.5-meter length of wall takes 20 points of cold damage or more in 1 round, that length goes out. (Do not divide cold damage by 4, as normal for objects.)

	\emph{Wall of fire} can be made permanent with a \spell{permanency} spell. A permanent \emph{wall of fire} that is extinguished by cold damage becomes inactive for 10 minutes, then reforms at normal strength.

	\textit{Arcane Material Component}:
	A small piece of phosphorus.

}
