\Spell{Web}{web}
{Conjuration (Creation)}
{
	\textbf{Level:}
	Wiz 2\\
	\textbf{Components:}
	V, S, M\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	Medium (30 m + 3 m/level)\\
	\textbf{Effect:}
	Webs in a 6-m-radius spread\\
	\textbf{Duration:}
	10 min./level (D)\\
	\textbf{Saving Throw:}
	Reflex negates; see text\\
	\textbf{Spell Resistance:}
	No\\
}
{
	\emph{Web} creates a many-layered mass of strong, sticky strands. These strands trap those caught in them. The strands are similar to spider webs but far larger and tougher. These masses must be anchored to two or more solid and diametrically opposed points or else the \emph{web} collapses upon itself and disappears. Creatures caught within a web become entangled among the gluey fibers. Attacking a creature in a web won't cause you to become entangled.

	Anyone in the effect's area when the spell is cast must make a Reflex save. If this save succeeds, the creature is entangled, but not prevented from moving, though moving is more difficult than normal for being entangled (see below). If the save fails, the creature is entangled and can't move from its space, but can break loose by spending 1 round and making a DC 20 Strength check or a DC 25 \skill{Escape Artist} check. Once loose (either by making the initial Reflex save or a later Strength check or \skill{Escape Artist} check), a creature remains entangled, but may move through the web very slowly. Each round devoted to moving allows the creature to make a new Strength check or \skill{Escape Artist} check. The creature moves 1.5 meter for each full 5 points by which the check result exceeds 10.

	If you have at least 1.5 meter of web between you and an opponent, it provides cover. If you have at least 6 meters of web between you, it provides total cover.

	The strands of a \emph{web} spell are flammable. A magic flaming sword can slash them away as easily as a hand brushes away cobwebs. Any fire can set the webs alight and burn away 0.5 square meter in 1 round. All creatures within flaming webs take 2d4 points of fire damage from the flames.

	\emph{Web} can be made permanent with a \spell{permanency} spell. A permanent \emph{web} that is damaged (but not destroyed) regrows in 10 minutes.

	\textit{Material Component:}
	A bit of spider web.

}
