\Spell{Word of Chaos}{word of chaos}
{Evocation [Chaotic, Sonic]}
{
	\textbf{Level:}
	Chaos 7, Clr 7\\
	\textbf{Components:}
	V\\
	\textbf{Casting Time:}
	1 standard action\\
	\textbf{Range:}
	12 m\\
	\textbf{Area:}
	Nonchaotic creatures in a 12-m-radius spread centered on you\\
	\textbf{Duration:}
	Instantaneous\\
	\textbf{Saving Throw:}
	None or Will negates; see text\\
	\textbf{Spell Resistance:}
	Yes\\
}
{
	Any nonchaotic creature within the area who hears the word of chaos suffers the following ill effects.

	The effects are cumulative and concurrent. No saving throw is allowed against these effects.

\Table{}{XX}{
\tableheader HD & \tableheader Effect\\
	Equal to caster level & Deafened\\
	Up to caster level $-1$ & Stunned, deafened\\
	Up to caster level $-5$ & Confused, stunned, deafened\\
	Up to caster level $-10$ & Killed, confused, stunned, deafened\\
}

	\textit{Deafened}:
	The creature is deafened for 1d4 rounds.

	\textit{Stunned}:
	The creature is stunned for 1 round.

	\textit{Confused}:
	The creature is confused, as by the confusion spell, for 1d10 minutes. This is a mind-affecting enchantment effect.

	\textit{Killed}:
	Living creatures die. Undead creatures are destroyed.

	Furthermore, if you are on your home plane when you cast this spell, nonchaotic extraplanar creatures within the area are instantly banished back to their home planes. Creatures so banished cannot return for at least 24 hours. This effect takes place regardless of whether the creatures hear the word of chaos. The banishment effect allows a Will save (at a $-4$ penalty) to negate.

	Creatures whose HD exceed your caster level are unaffected by word of chaos.

}
