\subsection{Casting Time}
Most spells have a casting time of 1 standard action. Others take 1 round or more, while a few require only a free action.

A spell that takes 1 round to cast is a full-round action. It comes into effect just before the beginning of your turn in the round after you began casting the spell. You then act normally after the spell is completed.

A spell that takes 1 minute to cast comes into effect just before your turn 1 minute later (and for each of those 10 rounds, you are casting a spell as a full-round action, just as noted above for 1-round casting times). These actions must be consecutive and uninterrupted, or the spell automatically fails.

When you begin a spell that takes 1 round or longer to cast, you must continue the concentration from the current round to just before your turn in the next round (at least). If you lose concentration before the casting is complete, you lose the spell.

A spell with a casting time of 1 free action doesn't count against your normal limit of one spell per round. However, you may cast such a spell only once per round. Casting a spell with a casting time of 1 free action doesn't provoke attacks of opportunity.

You make all pertinent decisions about a spell (range, target, area, effect, version, and so forth) when the spell comes into effect.

\subsection{Range}
A spell's range indicates how far from you it can reach, as defined in the Range entry of the spell description. A spell's range is the maximum distance from you that the spell's effect can occur, as well as the maximum distance at which you can designate the spell's point of origin. If any portion of the spell's area would extend beyond this range, that area is wasted. Standard ranges include the following.

\textbf{Personal:} The spell affects only you.

\textbf{Touch:} You must touch a creature or object to affect it. A touch spell that deals damage can score a critical hit just as a weapon can. A touch spell threatens a critical hit on a natural roll of 20 and deals double damage on a successful critical hit. Some touch spells allow you to touch multiple targets. You can touch as many willing targets as you can reach as part of the casting, but all targets of the spell must be touched in the same round that you finish casting the spell.

\textbf{Close:} The spell reaches as far as 7.5 meters away from you. The maximum range increases by 1.5 meter for every two full caster levels.

\textbf{Medium:} The spell reaches as far as 30 meters + 3 meters per caster level.

\textbf{Long:} The spell reaches as far as 120 meters + 12 meters per caster level.

\textbf{Unlimited:} The spell reaches anywhere on the same plane of existence.

\textbf{Range Expressed in Meters:} Some spells have no standard range category, just a range expressed in meters.