\subsubsection{Magic Armor and Shield Special Ability Descriptions}
Most magic armor and shields only have enhancement bonuses. Such items can also have one or more of the special abilities detailed below. Armor or a shield with a special ability must have at least a +1 enhancement bonus.

\Table{Armor Special Abilities}{lR}{
\tableheader Special Ability & \tableheader Base Price Modifier\\
Glamered & +2,700 cp \\
Fortification, light & +1 bonus \\
Quickness & +1 bonus \\
Shade & +1 bonus \\
Shadow & +3,750 cp \\
Silent moves & +3,750 cp \\
Slick & +3,750 cp \\
Invulnerability & +4,000 cp \\
Landing & +5,000 cp \\
Lifewall & +6,000 cp \\
% Linked & +2 bonus \\
Spell resistance (13) & +2 bonus \\
Malleable & +10,800 cp \\
Shadow, improved & +15,000 cp \\
Silent moves, improved & +15,000 cp \\
Slick, improved & +15,000 cp \\
Acid resistance & +18,000 cp \\
Cold resistance & +18,000 cp \\
Eletric resistance & +18,000 cp \\
Fire resistance & +18,000 cp \\
Sonic resistance & +18,000 cp \\
% Mindarmor & +24,000 cp \\
Fortification, moderate & +3 bonus \\
Ghost touch & +3 bonus \\
Gleaming & +3 bonus \\
Spell resistance (15) & +3 bonus \\
% Vanishing & +3 bonus \\
Wild & +3 bonus \\
Psychic & +30,000 cp \\
Shadow, greater & +33,750 cp \\
Silent moves, greater & +33,750 cp \\
Slick, greater & +33,750 cp \\
Acid resistance, improved & +42,000 cp \\
Cold resistance, improved & +42,000 cp \\
Eletric resistance, improved & +42,000 cp \\
Fire resistance, improved & +42,000 cp \\
Sonic resistance, improved & +42,000 cp \\
Spell resistance (17) & +4 bonus \\
Etherealness & +49,000 cp \\
Undead controlling & +49,000 cp \\
Fortification, heavy & +5 bonus \\
Spell resistance (19) & +5 bonus \\
Phasing & +65,520 cp \\
Acid resistance, greater & +66,000 cp \\
Cold resistance, greater & +66,000 cp \\
Eletric resistance, greater & +66,000 cp \\
Fire resistance, greater & +66,000 cp \\
Sonic resistance, greater & +66,000 cp \\
}

\Table{Shield Special Abilities}{lR}{
\tableheader Special Ability & \tableheader Base Price Modifier\\
Arrow Catching & +1 bonus \\
Bashing & +1 bonus \\
Blinding & +1 bonus \\
% Linked & +6,000 cp \\
Animated & +2 bonus \\
Arrow Deflection & +2 bonus \\
Manifester & +10,800 cp\\
% Mindarmor & +24,000 cp\\
Ghost Touch & +3 bonus \\
% Vanishing & +3 bonus \\
Wild & +3 bonus \\
Undead Controlling & +49,000 cp \\
Reflecting & +5 bonus \\
% Time Buttress & +5 bonus \\
}

\textbf{Animated:} Upon command, an animated shield floats within 60 centimeters of the wielder, protecting her as if she were using it herself but freeing up both her hands. Only one shield can protect a character at a time. A character with an animated shield still takes any penalties associated with shield use, such as armor check penalty, arcane spell failure chance, and nonproficiency.

Strong transmutation; CL 12th; \feat{Craft Magic Arms and Armor}, \spell{animate objects}; Price +2 bonus.

\textbf{Arrow Catching:} A shield with this ability attracts ranged weapons to it. It has a deflection bonus of +1 against ranged weapons because projectiles and thrown weapons veer toward it. Additionally, any projectile or thrown weapon aimed at a target within 1.5 meter of the shield's wearer diverts from its original target and targets the shield's bearer instead. (If the wielder has total cover relative to the attacker, the projectile or thrown weapon is not diverted.) Additionally, those attacking the wearer with ranged weapons ignore any miss chances that would normally apply. Projectiles and thrown weapons that have an enhancement bonus higher than the shield's base AC bonus are not diverted to the wearer (but the shield's increased AC bonus still applies against these weapons). The wielder can activate or deactivate this ability with a command word.

Moderate abjuration; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{entropic shield}; Price +1 bonus.

\textbf{Arrow Deflection:} A shield with this ability protects the wielder from ranged attacks. Once per round when he would normally be struck by a ranged weapon, he can make a DC 20 Reflex save. If the ranged weapon has an enhancement bonus, the DC increases by that amount. If he succeeds, the shield deflects the weapon. He must be aware of the attack and not flat-footed. Attempting to deflect a ranged weapon doesn't count as an action. Exceptional ranged weapons, such as boulders hurled by giants or acid arrows, can't be deflected.

Faint abjuration; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{shield}; Price +2 bonus.

\textbf{Bashing:} A shield with this special ability is designed to perform a shield bash. A bashing shield deals damage as if it were a weapon of two size categories larger (a Medium light shield thus deals 1d6 points of damage and a Medium heavy shield deals 1d8 points of damage). The shield acts as a +1 weapon when used to bash. (Only light and heavy shields can have this ability.)

Moderate transmutation; CL 8th; \feat{Craft Magic Arms and Armor}, \spell{bull's strength}; Price +1 bonus.

\textbf{Blinding:} A shield with this ability flashes with a brilliant light up to twice per day upon command of the wielder. Anyone within 6 meters except the wielder must make a DC 14 Reflex save or be blinded for 1d4 rounds.

Moderate evocation; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{searing light}; Price +1 bonus. 

\textbf{Energy Resistance:} This armor absorbs the first points of one specific type of energy damage per attack that the wearer would normally take (similar to the \spell{resist energy} spell). Each type of energy has a different visual:

\textit{Acid Resistance:} A suit of armor or a shield with this property normally has a dull gray appearance.

\textit{Cold Resistance:} A suit of armor or a shield with this property normally has a bluish, icy hue or is adorned with furs and shaggy pelts.

\textit{Eletric Resistance:} A suit of armor or a shield with this property normally has a bluish hue and often bears a storm or lightning motif.

\textit{Fire Resistance:} A suit of armor with this ability normally has a reddish hue and often is decorated with a draconic motif.

\textit{Sonic Resistance:} A suit of armor or a shield with this property normally has a glistening appearance.

\Table{}{XCr{22mm}}{
\tableheader Strength & \tableheader Energy Resistance & \tableheader Base Price Modifier\\
Normal & 10 & +18,000 cp \\
Improved & 20 & +42,000 cp \\
Greater & 30 & +66,000 cp \\
}

Faint abjuration (light), or moderate abjuration (improved or greater); CL 3rd (light), 7th (improved), or 11th (greater); \feat{Craft Magic Arms and Armor}, \spell{resist energy}; Price varies (see above).

\textbf{Etherealness:} On command, this ability allows the wearer of the armor to become ethereal (as the \spell{ethereal jaunt} spell) once per day. The character can remain ethereal for as long as desired, but once he returns to normal, he cannot become ethereal again that day.

Strong transmutation; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{ethereal jaunt}; Price +49,000 cp. 

\textbf{Fortification:} This suit of armor or shield produces a magical force that protects vital areas of the wearer more effectively. When a critical hit or sneak attack is scored on the wearer, there is a chance that the critical hit or sneak attack is negated and damage is instead rolled normally.

\Table{}{lCr{22mm}}{
\tableheader Fortification Type & \tableheader Chance for Normal Damage & \tableheader Base Price Modifier \\
Light & 25\% & +1 bonus\\
Moderate & 75\% & +3 bonus\\
Heavy & 100\% & +5 bonus\\
}

Strong abjuration; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{limited wish} or \spell{miracle}; Price varies (see above).

\textbf{Ghost Touch:} This armor or shield seems almost translucent. Both its enhancement bonus and its armor bonus count against the attacks of incorporeal creatures. It can be picked up, moved, and worn by incorporeal creatures at any time. Incorporeal creatures gain the armor or shield's enhancement bonus against both corporeal and incorporeal attacks, and they can still pass freely through solid objects.

Strong transmutation; CL 15th; \feat{Craft Magic Arms and Armor}, \spell{etherealness}; Price +3 bonus.

\textbf{Glamered:} A suit of armor with this ability appears normal. Upon command, the armor changes shape and form to assume the appearance of a normal set of clothing. The armor retains all its properties (including weight) when glamered. Only a \spell{true seeing} spell or similar magic reveals the true nature of the armor when disguised.

Moderate illusion; CL 10th; \feat{Craft Magic Arms and Armor}, \spell{disguise self}; Price +2,700 cp.

\textbf{Gleaming:} Gleams and flashes from the armor give the wearer and his armor a ``fuzzy'' appearance, granting the wearer concealment.

Faint illusion; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{blur}; Price +3 bonus.

\textbf{Invulnerability:} This suit of armor grants the wearer damage reduction of 5/magic.

Strong abjuration and perhaps evocation (if \spell{miracle} is used); CL 18th; \feat{Craft Magic Arms and Armor}, \spell{stoneskin}, \spell{wish} or \spell{miracle}; Price +3 bonus.

\textbf{Landing:} A suit of armor with this capability allows the wearer to ignore any damage dealt by the first 18 meters of a fall. Regardless of the height of a fall, the wearer always lands on her feet.

Faint transmutation; CL 4th; \feat{Craft Magic Arms and Armor}, \spell{feather fall}; Price +4,000 cp.

\textbf{Lifewall:} This suit of armor protects the wearer from the effects of being caught in the defiling radius of a spellcasting defiler. The wearer is immune to all penalties and damage associated with the defiling radius, even when augmented with raze feats or magical items.

Moderate abjuration; CL 11th; \feat{Craft Magic Arms and Armor}, \spell{allegiance of the land}; Price +5,000 cp.

% \textbf{Linked:} This kind of armor or shield allows the wearer to form a telepathic bond with other wearers of linked armor or shields within 15 kilometers. This ability is otherwise similar to the \psionic{mindlink} power.

% Moderate divination; CL 6th; \feat{Craft Magic Arms and Armor}, \psionic{mindlink}; Price +6,000 cp.

\textbf{Malleable:} Malleable armor seems thinner, lighter, and a little more flexible than its mundane counterpart. Spell failure chances for malleable armor are decreased by 10\%, the maximum Dexterity bonus is increased by 2, and armor check penalties are lessened by 3 (to a minimum of 0). If the armor is medium or heavy armor, it is treated as light armor for all purposes, such as when sleeping in armor or when determining the character's movement speed.

Faint transmutation; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{gaseous form}; Price +2 bonus.

\textbf{Manifester:} This kind of shield generates 3 power points once per day that the wearer can use when manifesting a power he knows. These power points must all be used on the same power. As usual, a psionic character cannot pay a power's cost with power points from more than one source, so the power points in the shield must be used for discrete manifestations.

Moderate transmutation; CL 7th; \feat{Craft Magic Arms and Armor}, \spell{dweomer of transference}, knowledge of any 2nd-level psionic power; Price +10,800 cp.

% \textbf{Mindarmor:} This kind of armor or shield grants the wearer a +3 insight bonus on Will saving throws to resist all mind-affecting and/or compulsion powers.

% Faint abjuration; CL 5th; \feat{Craft Magic Arms and Armor}, \psionic{empty mind}; Price +24,000 cp.

\textbf{Phasing:} The wearer of this kind of armor can move through wooden, plaster, or stone walls, but not other materials. The wearer can call on this special ability as a standard action. When the phasing ability is active, the wearer can pass through a wall or some other kind of appropriate object for a total distance of 18 meters per day (see below), breaking this distance up into several smaller passages or one long one, as desired. A wearer who exceeds this daily distance limit while inside solid material is ejected from the material at the point of entry, ending up prone in front of the now impassable barrier.

Phasing through a wall that separates two adjacent squares on the grid counts as 1.5 meter of distance. Phasing through a wall or barrier of any greater thickness counts as a distance equal to the barrier's thickness plus 1.5 meter.

Strong conjuration; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{phase door}; Price +65,520 cp.

\textbf{Psychic:} A psychic armor's power depends on its wearer. When worn by a nonpsionic creature, the armor possesses the qualities of a nonmagical, nonpsionic suit of masterwork armor. When worn by a psionic creature, this armor has an enhancement bonus based on the wearer's current power points reserve, as shown on the following table. The armor's enhancement bonus decreases as the wearer spends power points, and it increases whenever the wearer gains enough power points (by any means) to put his power points reserve into the next higher category.

\Table{}{r{1cm}lClr{1cm}}{
& \tableheader Power Point Reserve & \tableheader Enhancement Bonus & \\
& 1--4 & +1 & \\
& 5--29 & +2 & \\
& 30--79 & +3 & \\
& 80--129 & +4 & \\
& 130 or higher & +5 & \\
}

Strong abjuration; CL 17th; \feat{Craft Magic Arms and Armor}, \spell{dweomer of transference}, \spell{wish} or \spell{miracle}, must have a power point reserve; Price +30,000 cp.

\textbf{Quickness:} This kind of armor increases the wearer's speed by 1.5 meter. Thus, a character whose normal speed in armor is 6 meters moves 7.5 meters in \emph{armor of quickness}.

Faint transmutation; CL 4th; \feat{Craft Magic Arms and Armor}, \spell{expeditious retreat} or \psionic{burst}; Price +1 bonus.

\textbf{Reflecting:} This shield seems like a mirror. Its surface is completely reflective. Once per day, it can be called on to reflect a spell back at its caster exactly like the \spell{spell turning} spell.

Strong abjuration; CL 14th; \feat{Craft Magic Arms and Armor}, \spell{spell turning}; Price +5 bonus. 

\textbf{Shade:} Armor made with this ability is very beneficial to their wearer's when under the Athasian sun. The wearer is considered to be in shade for all purposes, and only require half their normal water intake to prevent dehydration. The wearer is not considered to be wearing armor for the purpose of Fortitude saves dealt by heat exposure from the environment.

Faint conjuration; CL 1st, \feat{Craft Magical Arms and Armor}, \spell{cooling canopy}; Price +1 bonus.

\textbf{Shadow:} This armor is jet black and blurs the wearer whenever she tries to hide, granting a competence bonus on \skill{Hide} checks. (The armor's armor check penalty still applies normally.)

\Table{}{XCr{22mm}}{
\tableheader Strength & \tableheader \skill{Hide} bonus & \tableheader Base Price Modifier\\
Normal & +5 & +3,750 cp \\
Improved & +10 & +15,000 cp \\
Greater & +20 & +33,750 cp \\
}

Faint illusion (light), moderate illusion (improved or greater); CL 5th (light), 10th (improved), 15th (greater); \feat{Craft Magic Arms and Armor}, \spell{invisibility}; Price varies (see above).

\textbf{Silent Moves:} This armor is well oiled and magically constructed so that it not only makes little sound, but it dampens sound around it. It provides a competence bonus on its wearer's \skill{Move Silently} checks. (The armor's armor check penalty still applies normally.)

\Table{}{XCr{22mm}}{
\tableheader Strength & \tableheader \skill{Move Silently} bonus & \tableheader Base Price Modifier\\
Normal & +5 & +3,750 cp \\
Improved & +10 & +15,000 cp \\
Greater & +20 & +33,750 cp \\
}

Faint illusion (light), moderate illusion (improved or greater); CL 5th (light), 10th (improved), 15th (greater); \feat{Craft Magic Arms and Armor}, \spell{silence}; Price varies (see above).

\textbf{Slick:} Slick armor seems coated at all times with a slightly greasy oil. It provides a competence bonus on its wearer's \skill{Escape Artist} checks. (The armor's armor check penalty still applies normally.)

\Table{}{XCr{22mm}}{
\tableheader Strength & \tableheader \skill{Escape Artist} bonus & \tableheader Base Price Modifier\\
Normal & +5 & +3,750 cp \\
Improved & +10 & +15,000 cp \\
Greater & +20 & +33,750 cp \\
}

Faint conjuration (light), moderate conjuration (improved or greater); CL 5th (light), 10th (improved), 15th (greater); \feat{Craft Magic Arms and Armor}, \spell{grease}; Price varies (see above).

\textbf{Spell Resistance:} This property grants the armor's wearer spell resistance while the armor is worn. The spell resistance can be 13, 15, 17, or 19, depending on the armor.

Strong abjuration; CL 15th; \feat{Craft Magic Arms and Armor}, \spell{spell resistance}; Price +2 bonus (SR 13), +3 bonus (SR 15), +4 bonus (SR 17), or +5 bonus (SR 19).

% \textbf{Time Buttress:} This kind of shield gives the wielder a chance to avoid telling blows by using time itself as a shield. Once per day, the wielder can use \psionic{timeless body} as though manifesting the power.

% Strong transmutation; CL 17th; \feat{Craft Magic Arms and Armor}, \psionic{timeless body}; Price +5 bonus.

\textbf{Undead Controlling:} The wearer of a suit of armor or a shield with this property may control up to 26 HD of undead per day, as the control undead spell. At dawn each day, the wearer loses control of any undead still under his sway. Armor or a shield with this ability appears to be made of bone; this feature is entirely decorative and has no other effect on the armor.

Strong necromancy; CL 13th; \feat{Craft Magic Arms and Armor}, \spell{control undead}; Price +49,000 cp.

% \textbf{Vanishing:} On command, this suit of armor or shield renders its wearer and all the wearer's equipment invisible to the minds of others, as if he had manifested the power \psionic{cloud mind}. The wearer can use this ability twice per day.

% Faint enchantment; CL 5th; \feat{Craft Magic Arms and Armor}, \psionic{cloud mind}; Price +3 bonus.

\textbf{Wild:} The wearer of a suit of armor or a shield with this ability preserves his armor bonus (and any enhancement bonus) while in a wild shape. Armor and shields with this ability usually appear to be made covered in leaf patterns. While the wearer is in a wild shape, the armor cannot be seen.

Moderate transmutation; CL 9th; \feat{Craft Magic Arms and Armor}, \spell{baleful polymorph}; Price +3 bonus. 