\subsubsection{Specific Shields}
The following specific shields usually are preconstructed with exactly the qualities described here.

\textbf{Absorbing Shield:} This \emph{+1 heavy darkwood shield} is flat black and seems to absorb light. Once every two days, on command, it can disintegrate an object that it touches, as the spell but requiring a melee touch attack.

Strong transmutation; CL 17th; \feat{Craft Magic Arms and Armor}, \spell{disintegrate}; Price 50,257 cp; Cost 25,257 cp + 2,000 XP.

\textbf{Caster's Shield:} This \emph{+1 light wooden shield} has a small leather strip on the back on which a spellcaster can scribe a single spell as on a scroll. A spell so scribed has only half the base raw material cost. Experience point and component costs remain the same. The strip cannot accommodate spells of higher than 3rd level. The strip is reusable.

A random caster's shield has a 50\% chance of having a single medium scroll spell on it. The spell is divine (01--80 on d\%) or arcane (81--100).

A caster's shield has a 5\% arcane spell failure chance.

Moderate abjuration; CL 6th; \feat{Craft Magic Arms and Armor}, \feat{Scribe Scroll}, creator must be at least 6th level; Price 3,153 cp (plus the value of the scroll spell if one is currently scribed); Cost 1,653 cp + 120 XP.

\textbf{Darkwood Buckler:} This nonmagical light wooden shield is made out of darkwood. It has no enhancement bonus, but its construction material makes it lighter than a normal wooden shield. It weighs 1.25 kilograms and has no armor check penalty.

No aura (nonmagical); Price 205 cp.

\textbf{Darkwood Shield:} This nonmagical heavy wooden shield is made out of darkwood. It has no enhancement bonus, but its construction material makes it lighter than a normal wooden shield. It weighs 2.5 kilograms and has no armor check penalty.

No aura (nonmagical); Price 257 cp.

\textbf{Lion's Shield:} This \emph{+2 heavy darkwood shield} is fashioned to appear to be a roaring lion's head. Three times per day as a free action, the lion's head can be commanded to attack (independently of the shield wearer), biting with the wielder's base attack bonus (including multiple attacks, if the wielder has them) and dealing 2d6 points of damage. This attack is in addition to any actions performed by the wielder.

Moderate conjuration; CL 10th; \feat{Craft Magic Arms and Armor}, \emph{summon nature's ally IV}; Price 9,257 cp; Cost 4,757 cp + 360 XP.

\textbf{Spined Shield:} This \emph{+1 heavy steel shield} is covered in spines. It acts as a normal spiked shield. On command up to three times per day, the shield's wearer can fire one of the shield's spines. A fired spine has a +1 enhancement bonus, a range increment of 36 meters, and deals 1d10 points of damage (19--20/$\times$2). Fired spines regenerate each day.

Moderate evocation; CL 6th; \feat{Craft Magic Arms and Armor}, \emph{magic missile}; Price 5,580 cp; Cost 2,740 cp + 223 XP.

\textbf{Winged Shield:} This round heavy wooden shield has a +3 enhancement bonus. Small, feathered wings encircle the shield.

Once per day it can be commanded to \spell{fly} (as the spell), carrying the wielder. The shield can carry up to 66.5 kilograms and move at 18 meters per round, or up to 133 kilograms and move at 12 meters per round.

Faint transmutation; CL 5th; \feat{Craft Magic Arms and Armor}, \spell{fly}; Price 17,257 cp; Cost 8,628 cp and 5 bits + 690 XP.
