\subsection{Adventuring Gear}

\Table{Adventuring Gear}{l RRRR}{
&& \multicolumn{3}{c}{\tableheader Weight}\\
\cmidrule[0.5pt]{3-5}
\tableheader Goods & \tableheader Cost & \tableheader M & \tableheader S & \tableheader L\\
Backpack (empty) & 2 cp & 1 kg & 0.25 kg & 4 kg\\
Barrel (empty) & 2 cp & 15 kg & &\\
Basket (empty) & 4 bits & 0.5 kg & &\\
Bedroll & 1 bits & 2.5 kg & 2.5 kg & 2.5 kg\\
Bell & 1 cp & & &\\
Blanket, winter & 5 bits & 1.5 kg & 0.37 kg & 6 kg\\
Block and tackle & 5 cp & 2.5 kg & &\\
Bottle, wine, glass & 2 cp & & &\\
Bucket (empty) & 5 bits & 1 kg & &\\
Caltrops & 1 cp & 1 kg & &\\
Candle & 1 bd & & &\\
Canvas (sq. m.) & 1 bits & 0.5 kg & &\\
Case, map or scroll & 1 cp & 0.25 kg & &\\
Chain (3 m.) & 30 cp & 1 kg & &\\
Chalk, 1 piece & 1 bd & & &\\
Chest (empty) & 2 cp & 12.5 kg & &\\
Crowbar & 2 cp & 2.5 kg & &\\
Firewood (per day) & 1 bd & 10 kg & &\\
Fishhook & 1 bits & & &\\
Fishing net, 2 sq. m. & 4 cp & 2.5 kg & &\\
Flask (empty) & 3 bd & 0.75 kg & &\\
Flint and steel & 1 cp & & &\\
Grappling hook & 1 cp & 2 kg & &\\
Hammer & 5 bits & 1 kg & &\\
Ink (30 ml vial) & 8 cp & & &\\
Inkpen & 1 bits & & &\\
Jug, clay & 3 bd & 9 lb. & &\\
Ladder, 3-meter & 5 bd & 10 kg & &\\
Lamp, common & 1 bits & 0.5 kg & &\\
Lantern, bullseye & 12 cp & 1.5 kg & &\\
Lantern, hooded & 7 cp & 1 kg & &\\
Lock (very simple) & 20 cp & 0.5 kg & &\\
Lock (average) & 40 cp & 0.5 kg & &\\
Lock (good) & 80 cp & 0.5 kg & &\\
Lock (amazing) & 150 cp & 0.5 kg & &\\
Manacles & 15 cp & 1 kg & &\\
Manacles, masterwork & 50 cp & 1 kg & &\\
Mirror, small steel & 10 cp & 0.25 kg & &\\
Mug/Tankard, clay & 2 bd & 0.5 kg & &\\
Oil (500 ml flask) & 1 bits & 0.5 kg & &\\
Paper (sheet) & 4 bits & & &\\
Parchment (sheet) & 2 bits & & &\\
Pick, miner's & 3 cp & 5 kg & &\\
Pitcher, clay & 2 bd & 2.5 kg & &\\
Piton & 1 bits & 0.25 kg & &\\
Pole, 3-meter & 2 bits & 4 kg & &\\
Pot, iron & 5 bits & 5 kg & &\\
Pouch, belt (empty) & 1 cp & 0.25 kg & 0.06 kg & 1 kg\\
Ram, portable & 10 cp & 10 kg & &\\
Rations, trail (per day) & 5 bits & 0.5 kg & 0.12 kg & 2 kg\\
Rope, giant hair (15 m.) & 50 cp & 5 kg & &\\
Rope, hempen (15 m.) & 1 cp & 5 kg & &\\
Rope, silk (15 m.) & 10 cp & 2.5 kg & &\\
Sack (empty) & 1 bits & 0.25 kg & 0.06 kg & 1 kg\\
Sealing wax & 1 cp & 0.5 kg & &\\
Sewing needle & 5 bits & & &\\
Signal whistle & 8 bits & & &\\
Signet ring & 5 cp & & &\\
Sledge & 1 cp & 5 kg & &\\
Soap (per 0.5 kg) & 5 bits & 0.5 kg & &\\
Spade or shovel & 2 cp & 4 kg & &\\
Spyglass & 10 gp & 0.5 kg & &\\
Tent & 10 cp & 10 kg & 2.5 kg & 40 kg\\
Torch & 1 bd & 0.5 kg & &\\
Vial, ink or potion & 1 cp & 0.05 kg & &\\
Waterskin & 1 cp & 2 kg & 0.5 kg & 8 kg\\
Whetstone & 2 bd & 0.5 kg & &\\
}


Some items weight differently for Small or Large characters, these items weigh one-quarter of the Medium-sized when made for Small characters and weigh four times as much the normal weight when made for Large characters. Containers for Small characters also carry one-quarter the normal amount, while containers for Large characters carry four times as much the normal amount.

A few of the pieces of adventuring gear are described below, along with any special benefits they confer on the user (``you'').


\textbf{Caltrops:} A caltrop is a four-pronged iron spike crafted so that one prong faces up no matter how the caltrop comes to rest. You scatter caltrops on the ground in the hope that your enemies step on them or are at least forced to slow down to avoid them. One 1-kilogram bag of caltrops covers an area 1.5 meter square.

Each time a creature moves into an area covered by caltrops (or spends a round fighting while standing in such an area), it might step on one. The caltrops make an attack roll (base attack bonus +0) against the creature. For this attack, the creature's shield, armor, and deflection bonuses do not count. If the creature is wearing shoes or other footwear, it gets a +2 armor bonus to AC. If the caltrops succeed on the attack, the creature has stepped on one. The caltrop deals 1 point of damage, and the creature's speed is reduced by one-half because its foot is wounded. This movement penalty lasts for 24 hours, or until the creature is successfully treated with a DC 15 \skill{Heal} check, or until it receives at least 1 point of magical curing. A charging or running creature must immediately stop if it steps on a caltrop. Any creature moving at half speed or slower can pick its way through a bed of caltrops with no trouble.

Caltrops may not be effective against unusual opponents.

\textbf{Candle:} A candle dimly illuminates a 1.5-meter radius and burns for 1 hour.

\textbf{Chain:} Chain has hardness 10 and 5 hit points. It can be burst with a DC 26 Strength check.

\textbf{Crowbar:} A crowbar grants +2 circumstance bonus on Strength checks made for such purposes. If used in combat, treat a crowbar as a one-handed improvised weapon that deals bludgeoning damage equal to that of a club of its size.

\textbf{Flint and Steel:} Lighting a torch with flint and steel is a full-round action, and lighting any other fire with them takes at least that long.

\textbf{Grappling Hook:} Throwing a grappling hook successfully requires a \skill{Use Rope} check (DC 10, +2 per 3 meters of distance thrown).

\textbf{Hammer:} If a hammer is used in combat, treat it as a one-handed improvised weapon that deals bludgeoning damage equal to that of a spiked gauntlet of its size.

\textbf{Ink:} This is black ink. You can buy ink in other colors, but it costs twice as much.

\textbf{Jug, Clay:} This basic ceramic jug is fitted with a stopper and holds 4 liters of liquid.

\textbf{Lamp, Common:} A lamp clearly illuminates a 4.5-meter radius, provides shadowy illumination out to a 9-meter radius, and burns for 6 hours on 500 ml of oil. You can carry a lamp in one hand.

\textbf{Lantern, Bullseye:} A bullseye lantern provides clear illumination in a 18-meter cone and shadowy illumination in a 36-meter cone. It burns for 6 hours on 500 ml of oil. You can carry a bullseye lantern in one hand.

\textbf{Lantern, Hooded:} A hooded lantern clearly illuminates a 9-meter radius and provides shadowy illumination in a 18-meter radius. It burns for 6 hours on 500 ml of oil. You can carry a hooded lantern in one hand.

\textbf{Lock:} The DC to open a lock with the \skill{Open Lock} skill depends on the lock's quality: simple (DC 20), average (DC 25), good (DC 30), or superior (DC 40).

\textbf{Manacles and Manacles, Masterwork:} Manacles can bind a Medium creature. A manacled creature can use the \skill{Escape Artist} skill to slip free (DC 30, or DC 35 for masterwork manacles). Breaking the manacles requires a Strength check (DC 26, or DC 28 for masterwork manacles). Manacles have hardness 10 and 10 hit points.

Most manacles have locks; add the cost of the lock you want to the cost of the manacles.

For the same cost, you can buy manacles for a Small creature.

For a Large creature, manacles cost ten times the indicated amount, and for a Huge creature, one hundred times this amount. Gargantuan, Colossal, Tiny, Diminutive, and Fine creatures can be held only by specially made manacles.

\textbf{Oil:} A pint of oil burns for 6 hours in a lantern. You can use a flask of oil as a splash weapon. Use the rules for alchemist's fire, except that it takes a full round action to prepare a flask with a fuse. Once it is thrown, there is a 50\% chance of the flask igniting successfully.

You can pour a pint of oil on the ground to cover an area 1.5 meter square, provided that the surface is smooth. If lit, the oil burns for 2 rounds and deals 1d3 points of fire damage to each creature in the area.

\textbf{Ram, Portable:} This iron-shod wooden beam gives you +2 circumstance bonus on Strength checks made to break open a door and it allows a second person to help you without having to roll, increasing your bonus by 2.

\textbf{Rope, Giant Hair:} This rope has 5 hardness, 2 hit points and can be burst with a DC 30 Strength check.

\textbf{Rope, Hempen:} This rope has 2 hit points and can be burst with a DC 23 Strength check.

\textbf{Rope, Silk:} This rope has 4 hit points and can be burst with a DC 24 Strength check. It is so supple that it provides +2 circumstance bonus on \skill{Use Rope} checks.

\textbf{Spyglass:} Objects viewed through a spyglass are magnified to twice their size.

\textbf{Torch:} A torch burns for 1 hour, clearly illuminating a 6-meter radius and providing shadowy illumination out to a 12-meter radius. If a torch is used in combat, treat it as a one-handed improvised weapon that deals bludgeoning damage equal to that of a gauntlet of its size, plus 1 point of fire damage.

\textbf{Vial:} A vial holds 30 milliliters of liquid. The stoppered container usually is no more than 3 centimeters wide and 8 centimeters high.
