\subsectionA{Clothing}
Clothes weigh one-quarter the normal amount when made for Small characters, and four times as much when made for Large characters.

\Table{Clothing}{lRRRR}{
&& \multicolumn{3}{c}{\tableheader Weight}\\
\cmidrule[0.25pt]{3-5}
\tableheader Item & \tableheader Cost & \tableheader S & \tableheader M & \tableheader L\\
Artisan's outfit & 1 cp & 0.5 kg & 2 kg & 8 kg\\
Cleric's vestments & 5 cp & 0.75 kg & 3 kg & 12 kg\\
% Cold weather outfit & 8 cp & 3.5 kg & 3.5 kg & 15 kg\\
Courtier's outfit & 30 cp & 0.75 kg & 3 kg & 12 kg\\
Elven outfit & 30 cp & 0.62 kg & 2.5 kg & 10 kg\\
Entertainer's outfit & 3 cp & 0.5 kg & 2 kg & 8 kg\\
Explorer's outfit & 10 cp & 1 kg & 4 kg & 16 kg\\
High templar's outfit & 100 cp & 0.62 kg & 2.5 kg & 10 kg\\
% Monk's outfit & 5 cp & 1 kg & 1 kg & 1 kg\\
Noble's outfit & 75 cp & 1.25 kg & 5 kg & 20 kg\\
Peasant's outfit & 1 sp & 0.25 kg & 1 kg & 4 kg\\
Royal defiler's outfit & 80 cp & 0.62 kg & 2.5 kg & 10 kg\\
Royal outfit & 200 cp & 1.87 kg & 7.5 kg & 30 kg\\
Scholar's outfit & 5 cp & 0.75 kg & 3 kg & 12 kg\\
Slave's outfit & 2 bd & 0.12 kg & 0.5 kg & 2 kg\\
Traveler's outfit & 1 cp & 0.62 kg & 2.5 kg & 10 kg\\
Wastelander outfit & 20 cp & 0.75 kg & 3 kg & 12 kg\\
}


\textbf{Artisan's Outfit:} This outfit includes a shirt with buttons, a skirt or pants with a drawstring, shoes, and perhaps a cap or hat. It may also include a belt or a leather or cloth apron for carrying tools.

\textbf{Cleric's Vestments:} These ecclesiastical clothes are for performing priestly functions, not for adventuring.

% \textbf{Cold Weather Outfit:} A cold weather outfit includes a wool coat, linen shirt, wool cap, heavy cloak, thick pants or skirt, and boots. This outfit grants a +5 circumstance bonus on Fortitude saving throws against exposure to cold weather.

\textbf{Courtier's Outfit:} This outfit includes fancy, tailored clothes in whatever fashion happens to be the current style in the courts of the nobles. Anyone trying to influence nobles or courtiers while wearing street dress will have a hard time of it (-2 penalty on Charisma-based skill checks to influence such individuals). If you wear this outfit without jewelry (costing an additional 50 cp), you look like an out-of-place commoner.

\textbf{Elven Outfit:} Although varying greatly from tribe to tribe, all elven clothing is based around two concepts: functionality and flattery. This set of clothes most often includes a hooded cloak or stylized robes, although some outfits make do with tight leather wrappings or other heat-shielding and water-retaining materials. In regards to its other aspect---visual appeal---every elven outfit is, no matter how functional, also designed to complement the wearer's form. Each outfit is tailor-made by elves, following a particular tribal pattern, and are normally not for sale. In addition, various portions of this outfit---such as a cloak, thick shoulder scarf, or even an entire tunic---are colored, patterned, or designed to be reversible in such a way as to blend in with the Athasian landscape, helping the wearer to blend in with the terrain in sandy areas: this provides a +3 circumstance bonus on \skill{Hide} checks while in desert terrain. For twice the listed price, this outfit can be made to fit over light armor.

\textbf{Entertainer's Outfit:} This set of flashy, perhaps even gaudy, clothes is for entertaining. While the outfit looks whimsical, its practical design lets you tumble, dance, walk a tightrope, or just run (if the audience turns ugly).

\textbf{Explorer's Outfit:} This is a full set of clothes for someone who never knows what to expect. It includes sturdy boots, leather breeches or a skirt, a belt, a shirt (perhaps with a vest or jacket), gloves, and a cloak. Rather than a leather skirt, a leather overtunic may be worn over a cloth skirt. The clothes have plenty of pockets (especially the cloak). The outfit also includes any extra items you might need, such as a scarf or a wide-brimmed hat.

\textbf{High Templar's Outfit:} High templar's outfits differ for each of the Tablelands' cities. This set of clothing is made of the best material produced by a city-state's artisans and exemplifies that city's templarate. Wearing the proper high templar outfit for a city's templarate gives advantage to \skill{Diplomacy} checks in contests of the \feat{Secular Authority} feat made within that city.

% \textbf{Monk's Outfit:} This simple outfit includes sandals, loose breeches, and a loose shirt, and is all bound together with sashes. The outfit is designed to give you maximum mobility, and it's made of high-quality fabric. You can hide small weapons in pockets hidden in the folds, and the sashes are strong enough to serve as short ropes.

\textbf{Noble's Outfit:} This set of clothes is designed specifically to be expensive and to show it. Precious metals and gems are worked into the clothing. To fit into the noble crowd, every would-be noble also needs a signet ring (see Adventuring Gear, above) and jewelry (worth at least 100 cp).

\textbf{Peasant's Outfit:} This set of clothes consists of a loose shirt and baggy breeches, or a loose shirt and skirt or overdress. Cloth wrappings are used for shoes.

\textbf{Royal Defiler's Outfit:} Royal defilers, who practice sorcery with the full legal backing of a sorcerer-king, must clearly indicate their protected status if they are to be spared the mob's wrath. This set of clothing is made from the best materials available to a city-state's artisans, and is second in quality only to a templar's outfit. The outfit varies greatly from city to city. In Raam, for example, this outfit is a checkered silk robe adorned with a silver brooch denoting royal defiler status. Wearing the proper defiler outfit for a city gives advantage to \skill{Intimidate} checks against citizens who aren't part of the templarate.

\textbf{Royal Outfit:} This is just the clothing, not the royal scepter, crown, ring, and other accoutrements. Royal clothes are ostentatious, with gems, gold, silk, and fur in abundance.

\textbf{Scholar's Outfit:} Perfect for a scholar, this outfit includes a robe, a belt, a cap, soft shoes, and possibly a cloak.

\textbf{Slave's Outfit:} This simple set of clothes consists of a loincloth, or a short skirt and sleeveless tunic, all made of rough-hewn materials.

\textbf{Traveler's Outfit:} This set of clothes consists of boots, a wool skirt or breeches, a sturdy belt, a shirt (perhaps with a vest or jacket), and an ample cloak with a hood.

\textbf{Wastelander's Outfit:} Similar to clothing worn by the many elven tribes dotting the Athasian landscape, this set of clothes commonly includes a large hooded cloak, multiple layers of heat-resistant, porous cloth, and reinforced leather padding designed to protect against blowing sand, sharp rocks and the ever-present cacti needles. In addition, this outfit is colored to blend in with whatever environment the wastelander has chosen as his home, helping the wearer to blend in with rocky surroundings. This provides advantage on \skill{Hide} checks while in the appropriate terrain; each wastelander's outfit provides this bonus for a single terrain type only. For twice the price, this outfit can be made to fit over light armor.