\subsection{Food, Drink, and Lodging}
Many Athasian travelers are lodged by merchant houses, elemental temples, psionic academies, or family. Adventurers, however, pay for hospitality.

\Table{Food, Drink, and Lodging}{XRR}{
\tableheader Item & \tableheader Cost & \tableheader Weight\\
\TableSubheader{Broy} &&\\
~ Keg (4 liters) & 2 cp & 5 kg\\
~ Mug & 4 bits & \onehalf kg\\
\TableSubheader{Inn stay (per day)} &&\\
~ Good & 2 sp & \\
~ Common & 5 cp & \\
~ Poor & 2 cp & \\
\TableSubheader{Meals (per day)} &&\\
~ Good & 5 bits & \\
~ Common & 3 bits & \\
~ Poor & 1 bit & \\
\TableSubheader{Water} &&\\
~ Keg (4 liters) & 2 bits & 5 kg\\
~ Mug & 1 bd & \onehalf kg\\
}

\textbf{Broy}: Broy is made from fermented kank nectar. Spiced broy and watered‐down broy are also available. When served plain, it is potent and foul tasting. However, broy can be served warm and spiced with a pungent herb that disguises its sourness, as well as enhancing its enrapturing powers.

\textbf{Inn}: Poor accommodations at an inn amount to a place on the floor near the hearth. Common accommodations consist of a place on a raised, heated floor, the use of a blanket and a pillow. Good accommodations consist of a small, private room with one bed, some amenities, and a covered chamber pot in the corner.

\textbf{Meals}: Poor meals might be composed of bread, baked turnips, onions, and water. Common meals might consist of bread, chicken stew, carrots, and watered-down ale or wine. Good meals might be composed of bread and pastries, beef, peas, and ale or wine.