\subsection{Metaempiric Components}
\ItemTable{Metaempiric Components}{
Aviarag horn & 1,350 cp & 2.5 kg\\
Beasthead blood & 45 cp & 0.5 kg\\
Dagorran crystal, diminutive & 100 cp &\\
Dagorran crystal, tiny & 300 cp & 0.25 kg\\
Defiler's ash & 1,700 cp &\\
Defiled poisonweed petals & 350 cp &\\
Eagle beasthead feather & 40 cp &\\
Roc feather & 450 cp &\\
Royal justice token & 1,375 cp & 0.5 kg\\
Shadow giant fumes & 390 cp & 0.5 kg\\
Sun paraelemental essence & 935 cp & 0.5 kg\\
T'chowb's thalamus & 1,250 cp & 0.25 kg\\
}

Useful for spellcasters, these items are special material components that have a chance of influencing the casting of certain spells while held in hand. Since a metempiric component must be held in one hand to use, it cannot be used in conjunction with the \feat{Still Spell} feat and, being optional for the casting of a spell, does not count as a normal material component for the purpose of the \feat{Eschew Materials} feat. Metempiric components are consumed during the casting of a spell, unless otherwise noted.

\textbf{Aviarag Horn:} A horn willingly given by an aviarag for use by someone after its passing into death is a powerful weapon for those seeking to do good. When presented while casting a spell, the goodness still emanating from the beast's horn is so tangible that the spell itself benefits from it. When used as a component for any spell with the good descriptor, the aviarag horn increases the spell's effective caster level by 1d4. An aviarag horn is not consumed after being used.

\textbf{Beasthead Blood:} As sorcerous mutations of normal Athasian giants, the blood of beasthead giants has some magical properties. When beasthead blood is used as a component in any transmutation spell, it increases the spell's saving throw DC by +1. Inexplicably, only druids and preservers may use beasthead blood this way; it provides no benefit for other types of spellcasters.

\textbf{Dagorran Crystal:} This green crystal growth is extracted from the body of a daggoran. Daggorans come in two sizes, which affect the size and potency of the crystal: a Medium daggoran provides a Diminutive crystal while a Large daggoran provides a Tiny crystal. When used as a component for a spell with the mind-affecting descriptor, a Diminutive daggoran crystal increases the spell's saving throw DC by +2.

\textbf{Defiler's Ash:} Mixed in with a special mixture of blood, these ashes must be taken from at least three different spellcasters' ashen circles caused by powerful spellcasting (spell level 6th and above). When used in the casting of a spell with the necromancy descriptor, defiler's ash empower the spell as if the caster had applied the Empower Spell feat (but without changing the spell's effective level or increasing its casting time).

\textbf{Defiled Poisonweed Petals:} The bright orange petals of a poisonweed plant turned undead by the action of defiling represent the epitome of noxiousness. When used as a component for any spell with the death descriptor, the petals of a defiled poisonweed increase the spell's saving throw DC by +2.

\textbf{Eagle Beasthead Feather:} If a feather from an eagle-headed beasthead giant is in hand when falling, it can be used as a component when casting feather fall, doubling the duration of the spell.

\textbf{Roc Feather:} These huge feathers---from anywhere between 2 and 4 feet long---come from an Athasian rock. When used as a component for a spell confering flight, a roc feather doubles the spell's duration.

\textbf{Royal Justice Token:} Only used by templars in the service of the sorcerer-monarch for which the token was created, the royal justice token shows graven symbols associated with the justice system used in a particular city-state. Symbols include ever-vigilant eyes, readied swords, and open hand or closed fist. When used as a component for the wrath of the sorcerer-king spell, the token increases the spell's effective caster level by +2. A royal justice token is not consumed after being used.

\textbf{Shadow Giant Fumes:} If bottled, the black, cold fumes that emanate from a shadow giant's mouth as it speaks can be used to enhance spells that have a connection to the Black. When used as a component for the spells greater shadow conjuration, shades, or shadow conjuration, the potency of the spell is one-fifth (20\%) better than normal.

\textbf{Sun Paraelemental Essence:} This bright and blinding essence comes from a dead sun paraelemental of at least Huge size. The essence must be trapped in a clear crystal container within one minute of the elemental's death and must always be kept under the light of the sun during the day, or else losing its potency. During the night, the light fades and gives off the same illumination as a candle. When used as a component for any spell with the light descriptor, the essence increases the effective caster level by +2.

\textbf{T'chowb's Thalamus:} The thalamus of a recently fed (within the last 24 hours) t'chowb is said to be seething with absorbed intelligence. When used as a metempiric component, the t'chowb's thalamus gives the caster a +10 circumstance bonus on caster level checks made to overcome a target's spell resistance.