\subsection{Mounts and Related Gear}

\Table{Mounts and Related Gear}{XRR}{
\tableheader Goods or Services & \tableheader Cost & \tableheader Weight \\
\TableSubheader{Barding} &&\\
~ Medium creature & $\times$2 & $\times$1 \\
~ Large creature & $\times$4 & $\times$2 \\
Bit and bridle & 2 cp & \onehalf kg \\
Feed (per day) & 1 bit & 5 kg \\
\TableSubheader{Mounts} &&\\
~ \TableSubheader{Birds} &&\\
~ Erdland & 25 cp &\\
~ Erdlu & 10 cp &\\
~ \TableSubheader{Reptiles} &&\\
~ Crodlu, riding & 200 cp & \\
~ Crodlu, warmount & 400 cp & \\
~ Inix & 100 cp & \\
~ Mekillot & 200 cp & \\
~ \TableSubheader{Insects} &&\\
~ Kank, herding & 50 cp &\\
~ Kank, riding & 125 cp &\\
~ Kank, warmount & 250 cp &\\
\TableSubheader{Saddle} &&\\
~ Military & 20 cp & 15 kg \\
~ Pack & 5 cp & 7.5 kg \\
~ Riding & 10 cp & 12.5 kg \\
\TableSubheader{Saddle, Exotic} &&\\
~ Military & 60 cp & 20 kg \\
~ Pack & 15 cp & 10 kg \\
~ Riding & 30 cp & 15 kg \\
Saddlebags & 4 cp & 4 kg \\
Stabling (per day) & 5 bits &\\
}

\textbf{Barding, Medium Creature and Large Creature:} Barding is a type of armor that covers the head, neck, chest, body, and possibly legs of a horse or other mount. Barding made of medium or heavy armor provides better protection than light barding, but at the expense of speed. Barding can be made of any of the armor types found on \tabref{Armor and Shields}.

Armor for a horse (a Large nonhumanoid creature) costs four times as much as armor for a human (a Medium humanoid creature) and also weighs twice as much as the armor found on \tabref{Armor and Shields} (see Armor for Unusual Creatures). If the barding is for a pony or other Medium mount, the cost is only double, and the weight is the same as for Medium armor worn by a humanoid. Medium or heavy barding slows a mount that wears it, as shown on the table below.

Flying mounts can't fly in medium or heavy barding.

Removing and fitting barding takes five times as long as the figures given on \tabref{Donning Armor}. A barded animal cannot be used to carry any load other than the rider and normal saddlebags.

\Table{Barding}{XCCC}{
 & \multicolumn{3}{c}{\tableheader Base Speed}\\
\cmidrule[0.5pt]{2-4}
\tableheader Barding & \tableheader (12 m) & \tableheader (15 m) & \tableheader (18 m)\\
Medium & 9 m & 10.5 m & 12 m\\
Heavy & 9 m\footnotemark[1] & 10.5 m\footnotemark[1] & 12 m\footnotemark[1]\\

\TableNote{4}{1 A mount wearing heavy armor moves at only triple its normal speed when running instead of quadruple.}\\
}

\textbf{Crodlu:} A crodlu is a large bipedal lizard mount, resembling a scaled ostrich. A crodlu is appropriate as a mount for a Medium humanoid creature. Crodlu are hard to control in battle, while war crodlu can be ridden into battle easily. Crodlu benefit from stabling, can wear barding, and require feed like normal mounts.

\textbf{Erdland:} These creatures are large, flightless birds used as mounts or to pull caravans. They weigh around 2 tons and can stand up to 4.5 meters tall. An erdland is appropriate as a mount for a Medium humanoid creature. Erdlands can be ridden into battle easily. Erdlands benefit from stabling, can wear barding, and require feed like normal mounts.

\textbf{Erdlu:} Erdlus are a smaller variety of erdland, mostly used as herd beasts. They stand 2.1 meters tall and weigh around 100 kg. An erdlu is appropriate as a mount for a Medium humanoid creature. Erdlus are hard to control in battle. Erdlus benefit from stabling, can wear barding, and require feed like normal mounts.

\textbf{Feed:} Crodlus, erdlands, erdlus, inixes require feeding. Mekillots require eight times more than normal mounts.

\textbf{Inix:} The inix is a large, 5.5-meter long reptile commonly used for riding and as a beast of burden. An inix is appropriate as a mount for a Medium or Large humanoid creature. Inixes can be ridden into battle easily. Inixes benefit from stabling, can wear custom barding (specially constructed, adding an additional 50\% to the price), and require feed like normal mounts.

\textbf{Kank:} A kank is a large, 2.4-meter long insect, commonly used as a personal mount. These insects cannot be used as food, for their meat smells atrocious, but they produce highly nutritious globules of honey. A kank is appropriate as a mount for a Medium humanoid creature. Kanks are hard to control in battle. Kanks benefit from stabling, cannot wear barding, and do not require feeding.

\textbf{Mekillot:} A mekillot is a huge, 3,000-kg. lizard, used for hauling large cargo or serving as transportation for troops. These beasts are hard to control in combat and usually require a psionic handler. Mekillots benefit from stabling, can wear barding, and require feed eight times more than a normal mount.

\textbf{Saddle, Exotic:} An exotic saddle is like a normal saddle of the same sort except that it is designed for an unusual mount. Exotic saddles come in military, pack, and riding styles.

\textbf{Saddle, Military:} A military saddle braces the rider, providing a +2 circumstance bonus on \skill{Ride} checks related to staying in the saddle. If you're knocked unconscious while in a military saddle, you have a 75\% chance to stay in the saddle (compared to 50\% for a riding saddle).

\textbf{Saddle, Pack:} A pack saddle holds gear and supplies, but not a rider. It holds as much gear as the mount can carry.

\textbf{Saddle, Riding:} The standard riding saddle supports a rider.