\subsectionA{Services}

\Table{Services}{lR}{
\tableheader Services & \tableheader Cost\\
Messenger         & 1 bit/km\\
Road or gate toll & 1 bit\\

\multicolumn{2}{l}{\TableSubheader{Hirelings, Military}}\\
Archer              & 1 bit/day  \\
Cavalry, heavy      & 3 bits/day \\
Cavalry, light      & 1 bit/day  \\
Crossbowman         & 5 bd/day   \\
Engineer            & 5 cp/day   \\
Infantry, heavy     & 5 bd/day   \\
Infantry, light     & 2 bd/day   \\
Infantry, irregular & 1 bd/day   \\

\multicolumn{2}{l}{\TableSubheader{Hirelings, Civilian}}\\
Draqoman                        & Level in cp/day \\
Craftsman\footnotemark[1]       & 1 bit/day      \\
Professional\footnotemark[2]    & 5 bd/day       \\
Specialist\footnotemark[3]      & 3 bits/day     \\
Spellcaster                     & 5 bits/day     \\
Unskilled labor\footnotemark[4] & 2 bd/day       \\


\multicolumn{2}{l}{\TableSubheader{Manifesting}}\\
Power, 1st--level & Manifester level $\times$ 10 cp\footnotemark[5]\\
Power, 2nd--level & Manifester level $\times$ 20 cp\footnotemark[5]\\
Power, 3rd--level & Manifester level $\times$ 30 cp\footnotemark[5]\\
Power, 4th--level & Manifester level $\times$ 40 cp\footnotemark[5]\\
Power, 5th--level & Manifester level $\times$ 50 cp\footnotemark[5]\\
Power, 6th--level & Manifester level $\times$ 60 cp\footnotemark[5]\\
Power, 7th--level & Manifester level $\times$ 70 cp\footnotemark[5]\\
Power, 8th--level & Manifester level $\times$ 80 cp\footnotemark[5]\\
Power, 9th--level & Manifester level $\times$ 90 cp\footnotemark[5]\\

\multicolumn{2}{l}{\TableSubheader{Spellcasting}}\\
Spell,   0--level & Caster level $\times$  5 sp\footnotemark[5]\footnotemark[6]\\
Spell, 1st--level & Caster level $\times$ 10 sp\footnotemark[5]\footnotemark[6]\\
Spell, 2nd--level & Caster level $\times$ 20 sp\footnotemark[5]\footnotemark[6]\\
Spell, 3rd--level & Caster level $\times$ 30 sp\footnotemark[5]\footnotemark[6]\\
Spell, 4th--level & Caster level $\times$ 40 sp\footnotemark[5]\footnotemark[6]\\
Spell, 5th--level & Caster level $\times$ 50 sp\footnotemark[5]\footnotemark[6]\\
Spell, 6th--level & Caster level $\times$ 60 sp\footnotemark[5]\footnotemark[6]\\
Spell, 7th--level & Caster level $\times$ 70 sp\footnotemark[5]\footnotemark[6]\\
Spell, 8th--level & Caster level $\times$ 80 sp\footnotemark[5]\footnotemark[6]\\
Spell, 9th--level & Caster level $\times$ 90 sp\footnotemark[5]\footnotemark[6]\\

\TableNote{2}{1 Any \skill{Craft} skill available.}\\
\TableNote{2}{2 Any \skill{Profession} skill available.}\\
\TableNote{2}{3 Any skill, other than Craft and Profession.}\\
\TableNote{2}{4 Jobs that do not require associated skills.}\\
\TableNote{2}{5 See its description for additional costs. If the additional costs put the total cost above 3,000 cp, that service is not generally available.}\\
\TableNote{2}{6 Spellcasting is considered high treason and spellcasters are not comfortable offering their services.}\\
}

Sometimes the best solution for a problem is to hire someone else to take care of it. Spellcasting, unless divine, is rarely, if ever, for sale on Athas. However, the manifesting of psionic powers for cash is much more common.

\textbf{Archer:} A 2nd-level fighter specialized in longbows, weilding a composite longbow (Str +2), and wearing studded leather and a buckler.

\textbf{Cavalry, Heavy:} A 2nd-level fighter wearing scale mail, and wielding a lance two-handed. They mount a heavy crodlu wearing a scale mail, as well.

\textbf{Cavalry, Light:} A 1st-level fighter wearing a studded leather and a wooden shield, and wielding a lance. They mount a light crodlu with no armor.

\textbf{Craftsman:} Usually a 2nd-level settler, but they can be of any class. This pays for any \skill{Craft} check of DC 20 or lower. Higher DC checks double the price for each 5 points of difference. 

\textbf{Crossbowman:} A 1st-level fighter specialized in crossbows, weilding a composite heavy crossbow (Str +4), and wearing studded scale mail and a tower shield.

\textbf{Draqoman:} A bard of 6th or higher level with at least one contact (see Alternative Class Features). Their wages depends on the bard's level and are the default price for skill contacts. If the draqoman has different types of contact, then they might double the price.

\textbf{Engineer:} A 5th-level fighter with 8 ranks of \skill{Knowledge} (warcraft) and a martial prowess that depend on this skill. They are equipped with \emph{breastplate +1} and a \emph{tower shield +1}. Although a military engineer has combat capabilities, their function is to oversee construction of siege engines and of static defenses.

\textbf{Infantry, Heavy:} A 2nd-level fighter, wearing a half-plate and tower shield, wielding a one-handed weapon. 

\textbf{Infantry, Light:} A 1st-level fighter, specialized either in spear and shields, or longswords. Light infantry usually wears studded leather, but caravan's infantry wear caravan armor.

\textbf{Infantry, Irregular:} A 2nd-level barbarian or gladiator. Their specialization is atypical, and they typically use gladiator armor or shell armor.

\textbf{Messenger:} This entry includes mounted messengers and runners. Those willing to carry a message to a place they were going anyway may ask for only half the indicated amount.

\textbf{Power:} The indicated amount is how much it costs to get a manifester to manifest a power for you. This cost assumes that you can go to the manifester and have the power manifested at his or her convenience. If you want to bring the manifester somewhere to manifest a power you need to negotiate with the manifester, otherwise the default answer is no.

The cost given is for a power with no XP cost. If the power has an XP cost, add 5 cp per XP lost.

Furthermore, if a power has dangerous consequences, the manifester will certainly require proof that you can and will pay for dealing with any such consequences (that is, assuming that the manifester even agrees to manifest such a power, which isn't certain). In the case of powers that transport the manifester and characters over a distance, you will likely have to pay for two manifestations of the power, even if you aren't returning with the manifester.

In addition, not every town or village has a manifester of sufficient level to manifest any power. In general, you must travel to a small town (or larger settlement) to be reasonably assured of finding a manifester capable of manifesting 1st--level powers, a large town for 2nd--level powers, a small city for 3rd-- or 4th--level powers, a large city for 5th-- or 6th--level powers, and a metropolis for 7th-- or 8th--level powers. Even a metropolis isn't guaranteed to have a local manifester able to cast 9th--level powers.

\textbf{Professional:} Usually a 2nd-level settler, but they can be of any class. This pays for any \skill{Profession} check of DC 20 or lower. Higher DC checks double the price for each 5 points of difference.

\textbf{Road or Gate Toll:} A toll is sometimes charged to cross a well-trodden, well-kept, and well-guarded road to pay for patrols on it and for its upkeep. Occasionally, a large walled city charges a toll to enter or exit (or sometimes just to enter).

\textbf{Specialist:} A 2nd-level NPC with \feat{Skill Focus} on the corresponding skill speciality, who can deliver a skill check of DC 20. Scouts are usually hired for \skill{Knowledge} (geography), \skill{Spot}, or \skill{Survival}. Thieves for \skill{Disable Device}, \skill{Forgery}, \skill{Open Lock}, \skill{Search}, or \skill{Sleight of Hand}. Bards for \skill{Appraise}, \skill{Diplomacy}, or \skill{Perform}. Wizards for \skill{Decipher Script}, any \skill{Knowledge}, or \skill{Spellcraft}. These are guidelines, but the wages are the same for any class.

\textbf{Spell:} The indicated amount is how much it costs to get a spellcaster to cast a spell for you. This cost assumes that you can go to the spellcaster and have the spell cast at his or her convenience (generally at least 24 hours later, so that the spellcaster has time to prepare the spell in question). If you want to bring the spellcaster somewhere to cast a spell you need to negotiate with him or her, and the default answer is no.

The cost given is for a spell with no cost for a material component or focus component and no XP cost. If the spell includes a material component, add the cost of that component to the cost of the spell.

If the spell has a focus component (other than a divine focus), add 1/10 the cost of that focus to the cost of the spell. If the spell has an XP cost, add 5 cp per XP lost.

Furthermore, if a spell has dangerous consequences, the spellcaster will certainly require proof that you can and will pay for dealing with any such consequences (that is, assuming that the spellcaster even agrees to cast such a spell, which isn't certain). In the case of spells that transport the caster and characters over a distance, you will likely have to pay for two castings of the spell, even if you aren't returning with the caster.

In addition, not every town or village has a spellcaster of sufficient level to cast any spell. In general, you must travel to a small town (or larger settlement) to be reasonably assured of finding a spellcaster capable of casting 1st--level spells, a large town for 2nd--level spells, a small city for 3rd-- or 4th--level spells, a large city for 5th-- or 6th--level spells, and a metropolis for 7th-- or 8th--level spells. Even a metropolis isn't guaranteed to have a local spellcaster able to cast 9th--level spells.

\textbf{Spellcaster:} A 3rd-level cleric or wizard. These wages do not pay for expensive material components, which must be given by the employer.

\textbf{Unskilled Labor:} Any job that a freeman might do that does not require a skill check.

