\subsubsection{Erdlu}
\begin{MonsterStats}
{Medium Animal}
{2d8+2 (11 hp)}
{+2}
{12 m (8 squares)}
{13 (+2 Dex, +1 natural), touch 12, flat-footed 11}
{+1/+2}
{Claw +2 melee (1d4+1)}
{2 claws +2 melee (1d4+1) and bite $-3$ melee (1d6)}
{1.5 m/1.5 m}
{---}
{Low-light vision}
{Fort +4, Ref +5, Will +1}
{Str 12, Dex 14, Con 13, Int 2, Wis 12, Cha 3}
{\skill{Jump} +16, \skill{Listen} +5, \skill{Spot} +5}
{\feat{Alertness}}
{Any (Tablelands)}
{Solitary, pair, or flock (10-500)}
{1}
{None}
{Always neutral}
{3--4 HD (Medium); 5--6 HD (Large)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Erdlu are large, flightless birds often used as livestock. They can weigh up to one hundred kilograms and stand almost two meters tall. Erdlu are covered in thick, flexible, scale-like feathers, ranging in color from dust-grey to soft reddish-brown. An erdlu's legs are long and strong, propelling it rapidly over the desert sands; the head, at the end of a long neck, is rounded, with a wicked, wedgeshaped beak.

    The omnivorous erdlu is a very common herd animal with many uses. Aside from its value as a meat animal, the erdlu's beak, wing scales, and claws all find their way into various weapon heads and tools, and the egg of an erdlu is an excellent source of food and water. Cooked, a single large egg can provide about three days' worth of food for a human. Raw, the egg's liquid contents can be substituted for about four liters of water.
}

Erdlu, both singly and in flocks, usually flee rather than fight. If forced into combat, the skittish birds kick with their powerful, clawed legs or bite with their heavy beaks.

\textbf{Skills:} Erdlu receive a +10 racial bonus to all \skill{Jump} checks.
