\subsubsection{Jhakar}
\begin{MonsterStats}
{Small Animal}
{2d8 (9 hp)}
{+3}
{6 m (8 squares)}
{16 (+1 size, +3 Dex, +2 natural), touch 14, flat-footed 13}
{+1/$-1$}
{Bite +5 melee (1d6$-2$)}
{Bite +5 melee (1d6$-2$)}
{1.5 m/1.5 m}
{Improved grab, pulldown}
{Low-light vision, scent}
{Fort +3, Ref +6, Will +1}
{Str 7, Dex 17, Con 11, Int 2, Wis 12, Cha 4}
{\skill{Listen} +3, \skill{Spot} +2, \skill{Survival} +3*}
{\feat{Track}, \feat{Weapon Finesse}\textsuperscript{B}}
{Any (Tablelands)}
{Solitary or pack (2--5)}
{1}
{None}
{Always neutral}
{3--4 HD (Small); 5--6 HD (Medium)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    Jhakars are predators whose pugnacious behavior makes them a bane to humanoids and animals alike. Their appearance is similar to that of a reptilian bulldog, and their characters are fierce and aggressive to match.

    Jhakars hunt in small packs in the wild, and fiercely attack all but the most dangerous of prey, pulling larger creatures down with their numbers and savagery.

    Sometimes jhakars are found in cities as domesticated guard-beasts, or serve as trackers, finding escaped slaves and so are also greatly feared by most thieves. Jhakars are mortal enemies of tembo, as the two species are often in competition for territory and prey. Needless to say, jhakars often come off the worst in such conflicts.

    A jhakar's scaly hide is thick and wrinkled, sporting a webbed, bony spine that protrudes from its back and ends just before its stump of a tail. Its eyes and ears, well protected by bony ridges and double-lids respectively, are dwarfed by the huge, fang-filled mouth. The bulk of the body is a rich, sandy-brown color, darkening at the snout and claws.
}

Jhakars are notorious for their tenacity and singleminded attacks. A pack of jhakars will attack as a group, seeking to drag their prey to the ground and savage it with multiple bites. Such is their instinctive coordination that the pack often seems to attack with one mind, jointly bent on ravaging its prey. The ferocity of a jhakar pack is significantly greater than the sum of its individual members.

\textbf{Improved Grab (Ex):} If a jhakar hits with its bite it may initiate a grapple check as a free action without provoking an attack of opportunity. *A jhakar has a +4 racial bonus on grapple checks.

\textbf{Pulldown (Ex):} Once per round, a jhakar can either make a trip attack as a free action or aid another jhakar in a trip attack as a free action (but not both). If it wins the Strength check ($-2$ check modifier*), it may immediately make a melee attack against the tripped opponent. If the attempt fails, the opponent cannot react to trip the jhakar.

* A jhakar has a +4 racial bonus on Strength checks made to trip an opponent.

\textbf{Skills:} Jhakars receive a +4 racial bonus to Survival checks when tracking by scent.
