\subsubsection{Leopard}
\begin{MonsterStats}
{Medium Animal}
{3d8+6 (19 hp)}
{+4}
{12 m (8 squares), climb 6 m}
{15 (+4 Dex, +1 natural), touch 14, flat-footed 11}
{+2/+5}
{Bite +6 melee (1d6+3)}
{Bite +6 melee (1d6+3) and 2 claws +1 melee (1d3+1)}
{1.5 m/1.5 m}
{Improved grab, pounce, rake 1d3+1}
{Low-light vision, scent}
{Fort +5, Ref +7, Will +2}
{Str 16, Dex 19, Con 15, Int 2, Wis 12, Cha 6}
{
    \skill{Balance} +12, %4 8
    \skill{Climb} +11, %3 8
    \skill{Hide} +8*, %4 4
    \skill{Jump} +15, %7 8
    \skill{Listen} +6, %3 3
    \skill{Move Silently} +8, %4 4
    \skill{Spot} +6} %3 3
{\feat{Alertness}, \feat{Weapon Finesse}}
{Warm forests}
{Solitary or pair}
{1}
{None}
{Always neutral}
{4--5 HD (Medium)}
{---}
\end{MonsterStats}

\MonsterStatsDescription{
    These jungle cats are about 1.2 meter long and weigh about 60 kilograms. They usually hunt at night. The statistics presented here can describe any feline of similar size, such as panthers and mountain lions.
}

\textbf{Improved Grab (Ex):} To use this ability, a leopard must hit with its bite attack. It can then attempt to start a grapple as a free action without provoking an attack of opportunity. If it wins the grapple check, it establishes a hold and can rake.

\textbf{Pounce (Ex):} If a leopard charges a foe, it can make a full attack, including two rake attacks.

\textbf{Rake (Ex):} Attack bonus +6 melee, damage 1d3+1.

\textbf{Skills:} Leopards have a +4 racial bonus on \skill{Hide} and \skill{Move Silently} checks. Leopards have a +8 racial bonus on \skill{Balance}, \skill{Climb}, and \skill{Jump} checks.

A leopard can always choose to take 10 on a \skill{Climb} check, even if rushed or threatened.

*In areas of tall grass or heavy undergrowth, the \skill{Hide} bonus improves to +8.

