\subsectionA{Infinite Layers of The Abyss}
The Abyss is all that is ugly, all that is evil, and all that is chaotic reflected in infinite variety through layers beyond count. Its virtually endless layers spiral downward into ever more atrocious forms. Conventional wisdom places the number of layers of the Abyss at 666, though there may be far more. The whole point of the Abyss, after all, is that it's far more terrible than conventional wisdom could ever encompass.

Each layer of the Abyss has its own unique, horrific environment. No theme unifies the multifarious layers other than their harsh, inhospitable nature. Lakes of caustic acid, clouds of noxious fumes, caverns of razor-sharp spikes, and landscapes of magma are all possibilities. So are less immediately deadly terrains such as parched salt deserts, subtly poisonous winds, and plains of biting insects.

The Abyss is home to demons, creatures devoted to death and destruction. A demon in the Abyss looks upon visitors as food or a source of amusement. Some see powerful visitors as potential recruits (willing or not) in the never-ending war that pits demons against devils: the Blood War.

Demon lords and deities inhabit the Abyss, including Demogorgon, Graz'zt, Pazuzu, Blibdoolpoolp (deity of kuo-toa), Diirinka (deity of the derro), the Great Mother (deity of beholders), Gruumsh (deity of orcs), Hruggek (deity of bugbears), and many others, including the well-known deity Lolth (draw deity and queen of the demonweb pits). Other demon princes include Yeenoghu, Alzrius, Baphomet, Eldanoth, Fraz Urblu, Juiblex, Kostchtchie, Lissa'aera, Lupercio, Lynkhab, Pale Night, Verin, and Vucarik.

As noted before, the Abyss has layers beyond count, though the top layer is well-known: the Plain of Infinite Portals.

It has the following traits.
\begin{itemize*}
\item \textbf{Divinely Morphic:} Entities at least as powerful as lesser deities can alter the Abyss. Less powerful creatures find the Abyss indistinguishable from a normal Material Plane (alterable morphic trait) in that the plane can be changed by spells and physical effort.
\item \textbf{Mixed Elemental and Energy Traits:} This trait varies widely from layer to layer. In the Abyss as a whole, no one element or energy constantly dominates, though certain layers have a dominant element or energy, or a mixture of two or more.
\item \textbf{Mildly Chaos-Aligned and Mildly Evil-Aligned:} Lawful characters in the Abyss suffer a $-2$ penalty on all Charisma-based checks, and good characters suffer the same penalty. Lawful good characters suffer a $-4$ penalty on all Charisma-based checks.
\end{itemize*}

\subsubsection{Plain of Infinite Portals}
This is the topmost of the uncountable Abyssal layers. It is a barren, dusty place without life or greenery, baking beneath a hell-red sun. The dusty plains are broken by three features: huge pits in the earth, great iron strongholds, and the River Styx.

The pits of this first layer are portals to deeper layers. Dropping down a given pit soon deposits the traveler into the associated layer, though jumping into random pits that lead to unknown planes of the Abyss is insanely dangerous. Most of the pits are two-way portals, but some are only one-way, leaving travelers stranded on the new layer.

Iron strongholds here most often house powerful demons and their court. Such fortresses often serve as a rallying point for demonic armies on their way to join the endless Blood War. Some of that war's greatest battles take plane in this layer, deeper layers, and nearby Outer Planes.

The River Styx flows a winding course on this layer. Some channels pour into the pits, while other pits well up with foul water, serving as tributaries of the mighty river.

A character entering a new, unknown layer of the Abyss via a pit (or another method) can wind up in almost any sort of terrain. Develop this layer of the Abyss yourself, or use \tabref{Random Abyssal Layers} to provide guidance.

\textbf{Broken Reach:} Red Shroud, a succubus sorcerer, rules the town of Broken Reach, which serves as a gathering point for Blood War mercenaries, a way spot for travelers insane enough to explore the Abyss, and a place for trade. The town is a set of crumbling towers surrounded by outworks of trenches, walls, and spiky barricades.

Several important precincts are underground. The portal to Plague-Mort, a town in the Outlands, is beneath the main hall, for example. The food stores, the arsenal, the interrogation halls, and the crypts are likewise underground, connected by narrow tunnels. Rooms for visiting mercenaries and merchants are above ground, off the main towered hall. The inhabitants are a mix of petitioner slaves, demons of all types, and mercenaries from the Material Plane and beyond.

\textbf{Ferrug:} An abandoned iron stronghold is situated near the Lakes of Molten Iron, a series of natural whitehot crucibles filled with molten iron. Ferrug's former demonic lord was slain as she lay senseless while astrally traveling to the Material Plane to corrupt mortal hearts. Since then, Ferrug has hosted countless armies of demons interested in gathering workable iron to build other iron strong- holds. Because the demons highly value iron, devil strike forces often attack the Lakes of Molten Iron, so Ferrug currently serves as a command center for a force of demons charged by Demogorgon to protect the lakes.

\subsubsection{Random Abyssal Layers}
What if your characters wind up being sent to the Abyss as a result of an adventure gone wrong? Or what if they flee powerful demons on the Plain of Infinite Portals by jumping down the nearest pit?

Use the following table to randomly determine the general terrain type of an unknown layer. If desired, roll twice (or more) and combine the results.

\Table{Random Abyssal Layers}{lX}{
  \tableheader d\%
& \tableheader Type of Layer\\
01--05  & Air-dominant \\
06--10  & Blood War battleground (demons against devils) \\
11--15  & Burning hellscape \\
16--20  & Demonic city \\
21--25  & Desert of sand, ice, salt, or ash \\
26--30  & Earth-dominant \\
31--35  & Fire-dominant \\
36--40  & Grass plain (filled with predators) \\
41--45  & Mixed elemental-dominant (as Limbo) \\
46--50  & Mountainous \\
51--55  & Negative-dominant (minor or major) \\
56--60  & Normal (as the Material Plane) \\
61--65  & Ocean of water \\
66--70  & Realm of powerful Abyssal entity \\
71--75  & Sea of acid \\
76--80  & Sea of insects \\
81--85  & Sea of magma \\
86--90  & Subterranean \\
91--95  & Undead realm \\
96--100 & Water-dominant \\
}
