\subsection{Elevation}
Elevations usually require extra forethought on your part because players will naturally want to know which direction is uphill. Draw your map in a way that uphill and downhill are clear and logical. Decide the shape of the lower part and the shape of the upper part, then surround them with rings of slopes and cliffs. Finally, draw arrows pointing downhill.

Gradual slopes, steep slopes, cliffs, and chasms are mutually exclusive. However,
gradual and steep slopes might include vegetation, scree, or rubble. Cliffs are placed next to steep slopes.

\subsubsection{Plains}
Flat ground that cover a huge area, plains are generally covered by grassland when there is vegetation. Elevation does not change much in plains, with very smooth inclinations occurring.

% Farms are common in settled areas, of course, while grasslands represent untamed plains. Battlefields represent a third terrain category because adventurers tend to spend a lot of time there, not because they're particularly prevalent.

\textbf{Stealth and Detection in Plains:} In plains, the maximum distance at which a \skill{Spot} check for detecting the nearby presence of others can succeed is 6d6 $\times$ 12 meters, although the specifics of your map may restrict line of sight. Plains provide no bonuses or penalties on \skill{Listen} and \skill{Spot} checks. Cover and concealment are not uncommon, so a good place of refuge is often nearby, if not right at hand.

\subsubsection{Depression}
Depressions are caused by different mechanisms. Sinkholes happen when the soil collapses above a hollow---a volcano's caldera is a type of sinkhole. Basins are eroded by the body of water it used to contain and have an extensive flat plain at their lowest point. Trenches are valleys formed by a block of land moving downward, instead of being eroded away.

\Table{Depression Features}{lCCC}{
& \multicolumn{3}{c}{\tableheader Depression Category}\\
\cmidrule[0.5pt]{2-4}

  \tableheader Terrain Feature
& \tableheader Sinkhole
& \tableheader Basin
& \tableheader Trench \\

Chasm         &  5\% &      &  5\% \\
Cliff         & 20\% &  5\% & 25\% \\
Gradual slope &  5\% & 30\% & 10\% \\
Steep slope   & 15\% &  5\% &      \\
Light rubble  &  5\% & 25\% & 25\% \\
}

\textbf{Cliff:} A depression cliff is 2d6 $\times$ 3 meters tall, except for basin cliffs that are 1d4 $\times$ 3 meters tall.

\textbf{Stealth and Detection in Depressions:} Characters in depressions can only \skill{Spot} creatures that are also inside it, or at the edge. In sinkholes or trenches, the maximum distance at which a \skill{Spot} check for detecting the nearby presence of others can succeed is 2d6 $\times$ 3 meters. In basins, this distance is 4d10 $\times$ 3 meters.

Depressions provide enough cover to hide from anyone in the surface. A basin or sinkhole does not provide easy cover to hide from creatures inside the depression, but trenches are rougher and can provide cover with their twists.

Basins don't affect \skill{Listen} or \skill{Move Silently} checks, but in sinkholes and trenches sound echoes so much, the DC of \skill{Listen} checks increases by 2.

\subsubsection{Hills}
Hills are divided into two categories: gentle hills and rugged hills. Hills  often serve as a transition zone between plains and mountains.

\Table{Hills Features}{lCC}{
& \multicolumn{2}{c}{\tableheader Hills Category}\\
\cmidrule[0.5pt]{2-3}

  \tableheader Terrain Feature
& \tableheader Gentle
& \tableheader Rugged \\

Cliff         &  5\% & 10\% \\
Gradual slope & 75\% & 40\% \\
Steep slope   & 20\% & 50\% \\
}

\textbf{Cliff:} A hill cliff is 1d4 $\times$ 3 meters tall.

\textbf{Stealth and Detection in Hills:} In gentle hills, the maximum distance at which a \skill{Spot} check for detecting the nearby presence of others can succeed is 2d10 $\times$ 3 meters. In rugged hills, this distance is 2d6 $\times$ 3 meters.

Hiding in hills terrain can be difficult if there isn't undergrowth around. A hilltop or ridge provides enough cover to hide from anyone below the hilltop or ridge.

Hills don't affect \skill{Listen} or \skill{Move Silently} checks.

\subsubsection{Badlands}
The result of thousands of years of wind or water erosion, badlands are mazes of canyons, gorges, tunnels, and cliff sides carved out of solid rock. Badlands appear in one of two categories: rugged (where the bare rock is mostly smooth) or forbidding (where the bare rock is mostly rough).

Since badlands are solid rock with little to no soil, they can't hold vegetation.

\Table{Badlands Features}{lCC}{
& \multicolumn{2}{c}{\tableheader Badlands Category}\\
\cmidrule[0.5pt]{2-3}

  \tableheader Terrain Feature
& \tableheader Rugged
& \tableheader Forbidding \\

Chasm         &  5\% & 10\% \\
Cliff         & 10\% & 20\% \\
Gradual slope & 60\% & 20\% \\
Steep slope   & 40\% & 60\% \\
Dense rubble  & 20\% & 30\% \\
}

\textbf{Cliff:} A badlands cliff is 1d4 $\times$ 3 meters tall.

\textbf{Rockslides:} A rockslide occurs when rocks dislodged from a slope gather momentum and tumble rapidly downhill. For the effects of rockslides, see Avalanches below.

\textbf{Stealth and Detection in Badlands:} For most purposes, the maximum distance in badlands terrain at which a \skill{Spot} check for detecting the nearby presence of others can succeed is 4d10 $\times$ 3 meters. The twisting, winding nature of badlands makes spotting at greater distances nearly impossible (which is why badlands are so favored by raiders and outlaws as hideouts). Cover in badlands is plentiful, from ridgelines and hilltops to caves and hollows.

Because sound echoes so much in badlands, the DC of \skill{Listen} checks increases by 2.

\subsubsection{Mountains}
The three mountain terrain categories are alpine meadows, rugged mountains, and forbidding mountains. As characters ascend into a mountainous area, they're likely to face each terrain category in turn, beginning with alpine meadows, extending through rugged mountains, and reaching forbidding mountains near the summit.

Mountains have an important terrain element, the rock wall, that is marked on the border between squares rather than taking up squares itself. Rock walls are placed adjacent to steep slope or cliff squares.

\Table{Mountain Features}{lCCC}{
& \multicolumn{3}{c}{\tableheader Mountain Category}\\
\cmidrule[0.5pt]{2-4}

  \tableheader Terrain Feature
& \tableheader Alpine Meadow
& \tableheader Rugged
& \tableheader Forbidding \\

Chasm         &      &  5\% & 10\% \\
Cliff         & 10\% & 15\% & 20\% \\
Gradual slope & 50\% & 25\% & 15\% \\
Steep slope   & 40\% & 55\% & 55\% \\
Scree         &      & 20\% & 30\% \\
Dense rubble  &      & 20\% & 30\% \\
}

\textbf{Cliff:} A mountain cliff is 2d6 $\times$ 3 meters tall.

\textbf{Rock Wall:} A vertical plane of stone, rock walls require DC 25 \skill{Climb} checks to ascend. A typical rock wall is 2d4 $\times$ 3 meters tall in rugged mountains and 2d8 $\times$ 3 meters tall in forbidding mountains. Rock walls are drawn on the edges of squares, not in the squares themselves.

\textbf{Stealth and Detection in Mountains:} As a guideline, the maximum distance in mountain terrain at which a \skill{Spot} check for detecting the nearby presence of others can succeed is 4d10 $\times$ 3 meters. Certain peaks and ridgelines afford much better vantage points, of course, and twisting valleys and canyons have much shorter spotting distances. Because there's little vegetation to obstruct line of sight, the specifics on your map are your best guide for the range at which an encounter could begin. As in hills terrain, a ridge or peak provides enough cover to hide from anyone below the high point.

It's easier to hear faraway sounds in the mountains. The DC of \skill{Listen} checks increases by 1 per 6 meters between listener and source, not per 3 meters.

\subsubsection{Elevation Features}
\textbf{Gradual Slopes:} This incline isn't steep enough to affect movement, but characters gain a +1 bonus on melee attacks against foes downhill from them.

\textbf{Steep Slope:} Characters moving uphill (to an adjacent square of higher elevation) must spend 2 squares of movement to enter each square of steep slope. Characters running or charging downhill (moving to an adjacent square of lower elevation) must succeed on a DC 10 \skill{Balance} check upon entering the first steep slope square. Mounted characters make a DC 10 \skill{Ride} check instead. Characters who fail this check stumble and must end their movement 1d2 $\times$ 1.5 meter later. Characters who fail by 5 or more fall prone in the square where they end their movement. A steep slope increases the DC of \skill{Tumble} checks by 2.

\textbf{Chasm:} Usually formed by natural geological processes, chasms function like pits in a dungeon setting. Chasms aren't hidden, so characters won't fall into them by accident (although bull rushes are another story). A typical chasm is 2d4 $\times$ 3 meters deep, at least 6 meters long, and anywhere from 1.5 meter to 6 meters wide. It takes a DC 15 \skill{Climb} check to climb out of a chasm. In forbidding mountain terrain, chasms are typically 2d8 $\times$ 3 meters deep.

\textbf{Cliff:} A cliff typically requires a DC 15 \skill{Climb} check to scale. A cliff isn't perfectly vertical, taking up 1.5-meter squares if it's less than 9 meters tall, 3-meter squares if it's up to 24 meters, and 6 meters of horizontal space if it's taller than 24 meters.

\textbf{Scree:} A field of shifting gravel, scree doesn't affect speed, but it can be treacherous on a slope. The DC of \skill{Balance} and \skill{Tumble} checks increases by 2 if there's scree on a gradual slope and by 5 if there's scree on a steep slope. The DC of \skill{Move Silently} checks increases by 2 if the scree is on a slope of any kind.

\textbf{Dense Rubble:} The ground is covered with rocks of all sizes. It costs 2 squares of movement to enter a square with dense rubble. The DC of \skill{Balance} and \skill{Tumble} checks on dense rubble increases by 5, and the DC of \skill{Move Silently} checks increases by +2.

\textbf{Cave Entrance:} Found in cliff and steep slope squares and next to rock walls, cave entrances are typically between 1.5 and 6 meters wide and 1.5 meter deep. Beyond the entrance, a cave could be anything from a simple chamber to the entrance to an elaborate dungeon. Caves used as monster lairs typically have 1d3 rooms that are 1d4 $\times$ 3 meters across.

\textbf{Streambed:} Result of drier and hotter weathers, a dry streambed functions as a low wall, except that it provides no cover against adjacent foes. It costs 2 squares of movement to leave a streambed, but it costs nothing extra to enter one. Creatures outside a streambed who make a melee attack against a creature inside the streambed gain a +1 bonus on melee attacks because they have higher ground.

\textbf{Other Features:} Elevated terrain can include active streams (1.5 to 3 meters wide and no more than 1.5 meter deep) or dry streambeds (1.5 to 3 meters across) in them. If you add a stream or streambed, remember that water always flows downhill.

Most alpine meadows begin above the tree line, so trees and other forest elements are rare in the mountains. Particularly high-altitude areas tend to be colder than the lowland areas that surround them, so they may be covered in ice sheets (described below).

\subsubsection{Avalanches (CR 7)}
The combination of high peaks and heavy snowfalls means that avalanches are a deadly peril in many mountainous areas. While avalanches of snow and ice are common, it's also possible to have an avalanche of rock and soil.

An avalanche can be spotted from as far away as 1d10 $\times$ 150 meters downslope by a character who makes a DC 20 \skill{Spot} check, treating the avalanche as a Colossal creature. If all characters fail their \skill{Spot} checks to determine the encounter distance, the avalanche moves closer to them, and they automatically become aware of it when it closes to half the original distance. It's possible to hear an avalanche coming even if you can't see it. Under optimum conditions (no other loud noises occurring), a character who makes a DC 15 \skill{Listen} check can hear the avalanche or landslide when it is 1d6 $\times$ 150 meters away. This check might have a DC of 20, 25, or higher in conditions where hearing is difficult (such as in the middle of a thunderstorm).

A landslide or avalanche consists of two distinct areas: the bury zone (in the direct path of the falling debris) and the slide zone (the area the debris spreads out to encompass). Characters in the bury zone always take damage from the avalanche; characters in the slide zone may be able to get out of the way. Characters in the bury zone take 8d6 points of damage, or half that amount if they make a DC 15 Reflex save. They are subsequently buried (see below). Characters in the slide zone take 3d6 points of damage, or no damage if they make a DC 15 Reflex save. Those who fail their saves are buried.

Buried characters take 1d6 points of nonlethal damage per minute. If a buried character falls unconscious, he or she must make a DC 15 Constitution check or take 1d6 points of lethal damage each minute thereafter until freed or dead.

The typical avalanche has a width of 1d6 $\times$ 30 meters, from one edge of the slide zone to the opposite edge. The bury zone in the center of the avalanche is half as wide as the avalanche's full width.

To determine the precise location of characters in the path of an avalanche, roll 1d6 $\times$ 6; the result is the number of meters from the center of the path taken by the bury zone to the center of the party's location. Avalanches of snow and ice advance at a speed of 150 meters per round, and rock avalanches travel at a speed of 75 meters per round.

\subsubsection{Mountain Travel}
High altitude can be extremely fatiguing---or sometimes deadly---to creatures that aren't used to it. Cold becomes extreme, and the lack of oxygen in the air can wear down even the most hardy of warriors.

\textbf{Acclimated Characters:} Creatures accustomed to high altitude generally fare better than lowlanders. Any creature with an Environment entry that includes mountains is considered native to the area, and acclimated to the high altitude. Characters can also acclimate themselves by living at high altitude for a month. Characters who spend more than two months away from the mountains must reacclimate themselves when they return. Undead, constructs, and other creatures that do not breathe are immune to altitude effects.

\textbf{Altitude Zones:} In general, mountains present three possible altitude bands: low pass, low peak/high pass, and high peak.

\textit{Low Pass (lower than 1,500 meters):} Most travel in low mountains takes place in low passes, a zone consisting largely of alpine meadows and forests. Travelers may find the going difficult (which is reflected in the movement modifiers for traveling through mountains), but the altitude itself has no game effect.

\textit{Low Peak or High Pass (1,500 to 4,500 meters):} Ascending to the highest slopes of low mountains, or most normal travel through high mountains, falls into this category. All nonacclimated creatures labor to breathe in the thin air at this altitude. Characters must succeed on a Fortitude save each hour (DC 15, +1 per previous check) or be fatigued. The fatigue ends when the character descends to an altitude with more air. Acclimated characters do not have to attempt the Fortitude save.

Temperature at this altitude is one temperature band colder and winds speeds are one category stronger than at sea level.

\textit{High Peak (more than 4,500 meters):} The highest mountains exceed 6,000 meters in height. At these elevations, creatures are subject to both high altitude fatigue (as described above) and altitude sickness, whether or not they're acclimated to high altitudes. Altitude sickness represents long-term oxygen deprivation, and it affects mental and physical ability scores. After each 6-hour period a character spends at an altitude of over 4,500 meters, he must succeed on a Fortitude save (DC 15, +1 per previous check) or take 1 point of damage to all ability scores. Creatures acclimated to high altitude receive a +4 competence bonus on their saving throws to resist high altitude effects and altitude sickness, but eventually even seasoned mountaineers must abandon these dangerous elevations.

Temperature at this altitude is two temperature bands colder and winds speeds are two categories stronger than at sea level.
