\subsectionA{The Astral Plane}
The Astral Plane is the medium through which creatures move between planes, the void between the Outer Planes and the Gray, where they were build upon. The plane is a huge argent emptiness occasionally punctuated by large stars, which is why it is also called the Silvery Void. The Astral Plane is almost always deafening quiet and disturbingly still. The only changes one might find in their stay in the plane are tiny color pools and floating islands---chunks of rock and earth pulled from another plane.

The plane is home to creatures like the astral stalker\textsuperscript{MM3} and the astral kraken\textsuperscript{PH}, and it also harbors the githyanki, a race of reavers who travel through the plane in astral ships. They are the ancestors of the Athasian gith, and far more cunning and dangerous.

The Astral Plane is devoid of concepts of space or time. It is fueled by thoughts, emotions, perceptions, and dreams---a more esoteric plane, where the sensations and memories are carried by the wind. Entering the plane means that the Astral Plane translates the character and their equipment into an astral projection, because nothing physical actually enters the plane.

\textbf{Astral Form:} An astral form is a silvery, ghostly image of a creature that used the \spell{astral projection} spell or the \psionic{psionic astral projection} power. A silver cord trails behind it for about 1.5 meter, then disappears into the astral haze. Astral forms have all the abilities from its native body, with the following differences. An astral form can return to its original body as a standard action.

\textit{Dying:} If an astral form is killed, the astral traveler's soul returns to its original body, which remains unharmed.

\textit{Entering Color Pools:} If an astral form passes through a color pool, it forms a new body from the building blocks of the plane itself. That body is identical to the original body, except it is immune to the natural hazards of that particular plane. The silver cord becomes attached to the pool, allowing the traveler to return to its original body regardless of the pool's direction.

\textit{Healing:} On the Astral Plane, natural healing does not occur. Magical healing functions normally on astral forms.

\textit{Severing the Silver Cord:} Very few dangers can sever the silver cord, but doing so kills the traveler's original body. Only the silver swords of the githyanki can sever this cord. Monster, items, and circumstances cannot sever a silver cord unless this ability is specifically noted. An astral traveler is automatically aware if their silver cord is threatened. A traveler's silver cord has its owner's AC, hardness 10, and 20 hit points.

\Table{Color Pools}{Xl}{
  \tableheader Plane
& \tableheader Color \\

Ysgard      & Indigo \\
Limbo       & Jet \\
Pandemonium & Magenta \\
Abyss       & Amethyst \\
Carceri     & Olive \\
Hades       & Rust \\
Gehenna     & Russet \\
Baator      & Ruby \\
Acheron     & Flame \\
Mechanus    & Diamond \\
Arcadia     & Saffron \\
Celestia    & Gold \\
Bytopia     & Amber \\
Elysium     & Opal \\
Beastlands  & Emerald \\
Arborea     & Sapphire \\
Outlands    & Leather brown \\
}

\textbf{Color Pools:} Color pools are irregular disks of a particular color floating in the vastness of the Astral Plane. The color of the pool tells the astral traveler what plane is on the other end of the color pool. Seven out of every ten color pools are one-way portals leading only to the plane in question. The remaining three out of ten allow two-way access.

\textbf{Movement:} Creatures move at a maximum speed equal to 3 m $\times$ their Intelligence score (minimum 3 m) as if they are flying with perfect maneuverability. They can double move dropping the maneuverability to average, or run with clumsy maneuverability.

Creatures with an Intelligence score of 0 or without Intelligence (such as golems) can move with a speed of 3 m, and then only by pushing off other solid objects. They cannot double move or run. If they are grounded and able to walk, they can move normally.

Travelers suffer no movement penalty for armor or weight, but they can carry no more than a heavy load while moving.

Movement through the Astral Plane is silent.

\textbf{Traveling:} Distances are deceptive on the Astral Plane, and maps are almost completely useless in the hazy expanse. The time it takes an individual or a group of individuals to reach a particular part of the Astral Plane depends on how familiar the travelers are with that area.

\Table{}{XX}{
  \tableheader Familiarity
& \tableheader Travel Time\\
Very familiar & 2d6 hours \\
Studied carefully & 1d4 $\times$ 6 hours \\
Seen casually & 1d4 $\times$ 10 hours \\
Viewed once & 1d6 $\times$ 20 hours \\
Description only & 1d10 $\times$ 50 hours \\
}

``Very familiar'' describes a place the traveler has been to very often and feels at home with. ``Studied carefully'' is a well-known place from regular visits, including most color pools the traveler has used before. ``Seen casually'' is a place known from occasional visits, including a color pool of a particular type but not a specific color pool (any color pool to Ysgard as opposed to a specific color pool to Ysgard, for example). ``Viewed once'' is for a place seen one time only, or a place that has been seen only by magic. ``Description only'' can be verbal or written, although a map to the location would be useless on a plane so devoid of landmarks.


\subsubsection{Astral Plane Traits}
\begin{itemize*}
\item \textbf{Subjective directional gravity:} Inhabitants of the plane determine their own ``down'' direction. Objects not under the motive force of others do not move.
\item \textbf{Timeless:} Age, hunger, thirst, poison, and natural healing don't function in the Astral Plane, though they resume functioning when the traveler leaves the Astral Plane.
\item \textbf{Mildly neutral-aligned.}
\item \textbf{Enhanced magic:} All spells and spell-like abilities used within the Astral Plane may be employed as if they were improved by the \feat{Quicken Spell} feat. Already quickened spells and spell-like abilities are unaffected, as are spells from magic items. Spells so quickened are still prepared and cast at their unmodified level. As with the \feat{Quicken Spell} feat, only one quickened spell can be cast per round.
\end{itemize*}
