\section{Spell Descriptions}
The description of each spell is presented in a standard format. Each category of information is explained and defined below.

\subsection{Name}
The first line of every spell description gives the name by which the spell is generally known.

\input{subsections/magic/spell-descriptions/school.tex}

\subsection{[Descriptor]}
Appearing on the same line as the school and subschool, when applicable, is a descriptor that further categorizes the spell in some way. Some spells have more than one descriptor.

The descriptors are acid, air, chaotic, cold, darkness, death, earth, electricity, evil, fear, fire, force, good, language-dependent, lawful, light, mind-affecting, sonic, and water.

Most of these descriptors have no game effect by themselves, but they govern how the spell interacts with other spells, with special abilities, with unusual creatures, with alignment, and so on.

A language-dependent spell uses intelligible language as a medium for communication. If the target cannot understand or cannot hear what the caster of a language-dependant spell says the spell fails.

A mind-affecting spell works only against creatures with an Intelligence score of 1 or higher.

\subsection{Level}
The next line of a spell description gives the spell's level, a number between 0 and 9 that defines the spell's relative power. This number is preceded by an abbreviation for the class whose members can cast the spell. The Level entry also indicates whether a spell is a domain spell and, if so, what its domain and its level as a domain spell are. A spell's level affects the DC for any save allowed against the effect.

Names of spellcasting classes are abbreviated as follows: cleric Clr; druid Drd; ranger Rgr; templar Tmp; wizard Wiz.

The domains a spell can be associated with include Agriculture, Air, Animal, Chaos, Charm, Cleansing, Cycle, Death, Decay, Destruction, Drought, Earth, Fire, Forecasting, Freedom, Glory, Growth, Knowledge, Law, Madness, Magic, Magma, Mind, Mirage, Nobility, Plant, Protection, Purity, Rain, Replenishment, Silt, Strength, Sun, Travel, Trickery, War, Water, and Wrath.

\input{subsections/magic/spell-descriptions/components.tex}
\input{subsections/magic/spell-descriptions/casting-time.tex}
\input{subsections/magic/spell-descriptions/aiming-a-spell.tex}
\input{subsections/magic/spell-descriptions/duration.tex}
\input{subsections/magic/spell-descriptions/saving-throw.tex}

\subsection{Spell Resistance}
Spell resistance is a special defensive ability. If your spell is being resisted by a creature with spell resistance, you must make a caster level check (1d20 + caster level) at least equal to the creature's spell resistance for the spell to affect that creature. The defender's spell resistance is like an Armor Class against magical attacks. Include any adjustments to your caster level to this caster level check.

The Spell Resistance entry and the descriptive text of a spell description tell you whether spell resistance protects creatures from the spell. In many cases, spell resistance applies only when a resistant creature is targeted by the spell, not when a resistant creature encounters a spell that is already in place.

The terms ``object'' and ``harmless'' mean the same thing for spell resistance as they do for saving throws. A creature with spell resistance must voluntarily lower the resistance (a standard action) in order to be affected by a spell noted as harmless. In such a case, you do not need to make the caster level check described above.

\subsection{Descriptive Text}
This portion of a spell description details what the spell does and how it works. If one of the previous entries in the description included ``see text,'' this is where the explanation is found.