\subsubsection{Arms}

\textbf{Bracelet of Friends:} This silver charm bracelet has four charms upon it when created. The owner may designate one person known to him to be keyed to one charm. (This designation takes a standard action, but once done it lasts forever or until changed.) When a charm is grasped and the name of the keyed individual is spoken, that person is called to the spot (a standard action) along with his or her gear, as long as the owner and the called person are on the same plane. The keyed individual knows who is calling, and the bracelet of friends only functions on willing travelers. Once a charm is activated, it disappears. Charms separated from the bracelet are worthless. A bracelet found with fewer than four charms is worth 25\% less for each missing charm.

Strong conjuration; CL 15th; \feat{Craft Wondrous Item}, \spell{refuge}; Price 19,000 cp.

\textbf{Bracers of Archery, Greater:} These wristbands look like normal protective wear. The bracers empower the wearer to use any bow (not including crossbows) as if she were proficient in its use. If she already has proficiency with any type of bow, she gains a +2 competence bonus on attack rolls and a +1 competence bonus on damage rolls whenever using that type of bow. Both bracers must be worn for the magic to be effective.

Moderate transmutation; CL 8th; \feat{Craft Wondrous Item}, \feat{Craft Magic Arms and Armor}; Price 25,000 cp; Weight 0.5 kg.

\textbf{Bracers of Archery, Lesser:} These wristbands function as greater bracers of archery, except that they grant a +1 competence bonus on attack rolls and no bonus on damage rolls.

Faint transmutation; CL 4th; \feat{Craft Wondrous Item}, \feat{Craft Magic Arms and Armor}; Price 5,000 cp; Weight 0.5 kg.

\textbf{Bracers of Armor:} These items appear to be wrist or arm guards. They surround the wearer with an invisible but tangible field of force, granting him an armor bonus of +1 to +8, just as though he were wearing armor. Both bracers must be worn for the magic to be effective.

Moderate conjuration; CL 7th; \feat{Craft Wondrous Item}, \spell{mage armor}, creator's caster level must be at least two times that of the bonus placed in the bracers; Price 1,000 cp (+1), 4,000 cp (+2), 9,000 cp (+3), 16,000 cp (+4), 25,000 cp (+5), 36,000 cp (+6), 49,000 cp (+7), 64,000 cp (+8); Weight 0.5 kg.
