\subsubsection{Body}

\textbf{Robe of the Archmagi:} This normal-appearing garment can be white (01-45 on d\%, good alignment), gray (46-75, neither good nor evil alignment), or black (76-100, evil alignment). Its wearer, if an arcane spellcaster, gains the following powers.

\begin{itemize*}
\item +5 armor bonus to AC.
\item Spell resistance 18.
\item +4 resistance bonus on all saving throws.
\item +2 enhancement bonus on caster level checks made to overcome spell resistance.
\end{itemize*}

If a white robe is donned by an evil character, she immediately gains three negative levels. The reverse is true with respect to a black robe donned by a good character. An evil or good character who puts on a gray robe, or a neutral character who dons either a white or black robe, gains two negative levels. While these negative levels never result in lost levels, they remain as long as the garment is worn and cannot be overcome in any way (including \spell{restoration} spells).

Strong varied; CL 14th; \feat{Craft Wondrous Item}, \spell{antimagic field}, \spell{mage armor} or \spell{shield of faith}, creator must be of same alignment as robe; Price 75,000 cp; Weight 0.5 kg.

\textbf{Robe of Blending:} When this robe is put on, the wearer intuitively knows that the garment has very special properties. A \emph{robe of blending} enables its wearer to appear to be part of his surroundings. This allows him a +10 competence bonus on \skill{Hide} checks. The wearer can adopt the appearance of another creature, as with the \spell{disguise self} spell, at will. All creatures acquainted with and friendly to the wearer see him normally.

Moderate illusion; CL 10th; \feat{Craft Wondrous Item}, \spell{disguise self}; Price 30,000 cp; Weight 0.5 kg.

\textbf{Robe of Bones:} This handy item functions much like a \emph{robe of useful items} for the serious necromancer. It appears to be an unremarkable robe, but a character who dons it notes that it is adorned with small embroidered figures representing undead creatures. Only the wearer of the robe can see the embroidery and recognize them for the creatures they become, and detach them. One figure can be detached each round. Detaching a figure causes it to become an actual undead creature (see the list below). The skeleton or zombie is not under the control of the wearer of the robe, but may be subsequently commanded, rebuked, turned, or destroyed. A newly created \emph{robe of bones} always has two embroidered figures of each of the following undead:

\begin{itemize*}
\item Small goblin skeleton
\item Medium human commoner skeleton
\item Medium wolf skeleton
\item Small goblin zombie
\item Medium human commoner zombie
\item Medium wolf zombie
\end{itemize*}

Moderate necromancy [evil]; CL 6th; \feat{Craft Wondrous Item}, \spell{animate dead}; Price 2,400 cp; Weight 0.5 kg.

\textbf{Robe of Eyes:} This valuable garment appears to be a normal robe until it is put on. Its wearer is able to see in all directions at the same moment due to scores of visible, magical eyelike patterns that adorn the robe. She also gains 36-meter darkvision.

The \emph{robe of eyes} sees all forms of invisible or ethereal things within 36 meters.

The wearer of a \emph{robe of eyes} gains a +10 competence bonus on \skill{Search} checks and \skill{Spot} checks. She retains her Dexterity bonus to AC even when flat-footed, and she can't be flanked. However, she is not able to avert her eyes or close her eyes when confronted by a creature with a gaze attack.

A \spell{light} or \spell{continual flame} spell cast directly on a \emph{robe of eyes} causes it to be blinded for 1d3 minutes. A \spell{daylight} spell blinds it for 2d4 minutes.

Moderate divination; CL 11th; \feat{Craft Wondrous Item}, \spell{true seeing}; Price 120,000 cp; Weight 0.5 kg.

\textbf{Robe of Scintillating Colors:} The wearer of this robe can cause the garment to display a shifting pattern of incredible hues, color after color cascading from the upper part of the robe to the hem in sparkling rainbows of dazzling light. The colors daze those near the wearer, conceal the wearer, and illuminate the surroundings. It takes 1 full round after the wearer speaks the command word for the colors to start flowing on the robe. The colors create the equivalent of a gaze attack with a 9-meter range. Those who look at the wearer are dazed for 1d4+1 rounds (Will DC 16 negates). This is a mind-affecting pattern effect.

Every round of continuous scintillation of the robe gives the wearer better concealment. The miss chance on attacks against the wearer starts at 10\% and increases by 10\% each round until it reaches 50\% (total concealment).

The robe illuminates a 9-meter radius continuously.

The effect can be used no more than a total of 10 rounds per day.

Moderate illusion; CL 11th; \feat{Craft Wondrous Item}, \spell{blur}, \spell{rainbow pattern}; Price 27,000 cp; Weight 0.5 kg.

\textbf{Robe of Stars:} This garment is typically black or dark blue and embroidered with small white or silver stars. The robe has three magical powers.

\begin{itemize*}
\item It enables its wearer to travel physically to the Astral Plane, along with all that she is wearing or carrying.
\item It gives its wearer a +1 luck bonus on all saving throws.
\item Its wearer can use up to six of the embroidered stars on the chest portion of the robe as \emph{+5 shuriken}. The robe grants its wearer proficiency with such weapons. Each shuriken disappears after it is used.
\end{itemize*}

Strong varied; CL 15th; \feat{Craft Wondrous Item}, magic missile, astral projection or plane shift; Price 58,000 cp; Weight 0.5 kg.

\textbf{Robe of Useful Items:} This appears to be an unremarkable robe, but a character who dons it notes that it is adorned with small cloth patches of various shapes. Only the wearer of the robe can see these patches, recognize them for what items they become, and detach them. One patch can be detached each round. Detaching a patch causes it to become an actual item, as indicated below. A newly created robe of useful items always has two each of the following patches:

\begin{itemize*}
\item Dagger
\item Bullseye lantern (filled and lit)
\item Mirror (a highly polished 0.5 m $\times$ 1 m steel mirror)
\item Pole (3-meter length)
\item Hempen rope (15-meter coil)
\item Sack
\end{itemize*}

In addition, the robe has several other patches. Roll 4d4 for the number of other patches and then roll for each patch on the table below to determine its nature.

\Table{}{cL}{
  \tableheader d\%
& Result \\
01-08  & Bag of 100 ceramic pieces \\
09-15  & Coffer, silver (15 cm by 15 cm by 30 cm), 500 cp value \\
16-22  & Door, iron (up to 3 m wide and 3 m high and barred on one side---must be placed upright, attaches and hinges itself) \\
23-30  & Gems, 10 (100 cp value each) \\
31-44  & Ladder, wooden (7 m long) \\
45-51  & Mule (with saddle bags) \\
52-59  & Pit, open (3 m by 3 m by 3 m) \\
60-68  & Potion of cure serious wounds \\
69-75  & Rowboat (3.5 m long) \\
76-83  & Minor scroll of one randomly determined spell \\
84-90  & War dogs, pair (treat as riding dogs) \\
91-96  & Window (0.5 m by 1.2 m, up to 0.5 m deep) \\
97-100 & Portable ram \\
}

Multiple items of the same kind are permissible. Once removed, a patch cannot be replaced.

Moderate transmutation; CL 9th; \feat{Craft Wondrous Item}, \spell{fabricate}; Price 7,000 cp; Weight 0.5 kg.
