\subsubsection{Feet}

\textbf{Boots of Elvenkind:} These soft boots enable the wearer to move quietly in virtually any surroundings, granting a +5 competence bonus on Move Silently checks.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, creator must be an elf; Price 2,500 cp; Weight 1 lb.

\textbf{Boots of Levitation:} On command, these leather boots allow the wearer to levitate as if she had cast levitate on herself.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{levitate}; Price 7,500 cp; Weight 1 lb.

\textbf{Boots of Speed:} As a free action, the wearer can click her boot heels together, enabling her to act as though affected by a haste spell for up to 10 rounds each day. The duration of the haste effect need not be consecutive rounds.

Moderate transmutation; CL 10th; \feat{Craft Wondrous Item}, \spell{haste}; Price 12,000 cp; Weight 1 lb.

\textbf{Boots of Striding and Springing:} These boots increase the wearer's base land speed by 10 feet. In addition to this striding ability (considered an enhancement bonus), these boots allow the wearer to make great leaps. She can jump with a +5 competence bonus on Jump checks.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, longstrider, creator must have 5 ranks in the Jump skill; Price 5,500 cp; Weight 1 lb.

\textbf{Boots of Teleportation:} Any character wearing this footwear may teleport three times per day, exactly as if he had cast the spell of the same name.

Moderate conjuration; CL 9th; \feat{Craft Wondrous Item}, \spell{teleport}; Price 49,000 cp; Weight 3 lb.

\textbf{Boots of the Winterlands:} This footgear bestows many powers upon the wearer. First, he is able to travel across snow at his normal speed, leaving no tracks. The boots also enable him to travel at normal speed across the most slippery ice (horizontal surfaces only, not vertical or sharply slanted ones) without falling or slipping. Finally, boots of the winterlands warm the wearer, as if he were affected by an endure elements spell.

Faint abjuration and transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{cat's grace}, \spell{endure elements}, \spell{pass without trace}; Price 2,500 cp; Weight 1 lb.

\textbf{Boots, Winged:} These boots appear to be ordinary footgear. On command, the boots sprout wings at the heel and let the wearer fly, without having to maintain concentration, as if affected by a fly spell. He can fly three times per day for up to 5 minutes per flight.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{fly}; Price 16,000 cp; Weight 1 lb.

\textbf{Horseshoes of Speed:} These iron shoes come in sets of four like ordinary horseshoes. When affixed to an animal's hooves, they increase the animal's base land speed by 30 feet; this counts as an enhancement bonus. As with other effects that increase speed, jumping distances increase proportionally. All four shoes must be worn by the same animal for the magic to be effective.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{haste}; Price 3,000 cp; Weight 12 lb. (for four).

\textbf{Horseshoes of a Zephyr:} These four iron shoes are affixed like normal horseshoes. They allow a horse to travel without actually touching the ground. The horse must still run above (always around 4 inches above) a roughly horizontal surface. This means that nonsolid or unstable surfaces can be crossed, and that movement is possible without leaving tracks on any sort of ground. The horse moves at its normal base land speed. All four shoes must be worn by the same animal for the magic to be effective.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{levitate}; Price 6,000 cp; Weight 4 lb. (for four).