\subsubsection{Hands}

\textbf{Gauntlets of Half-Giant Power:} These gauntlets are made of tough leather with iron studs running across the back of the hands and fingers. When in a character's possession, their Strength score becomes 19. Both gauntlets must be worn for the magic to be effective.

Faint transmutation; CL 6th; \feat{Craft Wondrous Item}, \spell{bull's strength}; Price 16,000 cp; Weight 2 kg.

\textbf{Gauntlet of Rust:} This single metal gauntlet looks rusted and pitted but is actually quite powerful. Once per day, it can affect an object as with the rusting grasp spell. It also completely protects the wearer and her gear from rust (magical or otherwise), including the attack of a rust monster.

Moderate transmutation; CL 7th; \feat{Craft Wondrous Item}, \spell{rusting grasp}; Price 11,500 cp; Weight 1 kg.

\textbf{Gloves of Arrow Snaring:} Once snugly worn, these gloves seem to meld with the hands, becoming almost invisible. Twice per day, the wearer can act as if he had the \feat{Snatch Arrows} feat, even if he does not meet the prerequisites for it. Both gloves must be worn for the magic to be effective. At least one hand must be free to take advantage of the magic.

Faint abjuration; CL 3rd; \feat{Craft Wondrous Item}, \spell{shield}; Price 4,000 cp.

\textbf{Gloves of Dexterity:} These thin leather gloves are very flexible and allow for delicate manipulation. When in a character's possession, their Dexterity score becomes 19. Both gloves must be worn for the magic to be effective.

Moderate transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{cat's grace}; Price 16,000 cp.

\textbf{Glove of Storing:} This device is a simple leather glove. On command, one item held in the hand wearing the glove disappears. The item can weigh no more than 20 pounds and must be able to be held in one hand. While stored, the item has negligible weight. With a snap of the fingers wearing the glove, the item reappears. A glove can only store one item at a time. Storing or retrieving the item is a free action. The item is held in stasis and shrunk down so small within the palm of the glove that it cannot be seen. Spell durations are not suppressed, but continue to expire. If an effect is suppressed or dispelled, the stored item appears instantly.

Faint transmutation; CL 6th; \feat{Craft Wondrous Item}, \spell{shrink item}; Price 10,000 cp (one glove).

% \textbf{Gloves of Swimming and Climbing:} These apparently normal lightweight gloves grant a +5 competence bonus on \skill{Swim} checks and \skill{Climb} checks. Both gloves must be worn for the magic to be effective.

% Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{bull's strength}, \spell{cat's grace}; Price 6,250 cp.
