\subsubsection{Head}

\textbf{Circlet of Blasting, Minor:} On command, this simple golden headband projects a blast of \spell{searing light} (3d8 points of damage) once per day.

Faint evocation; CL 6th; \feat{Craft Wondrous Item}, \spell{searing light}; Price 6,480 cp.


\textbf{Circlet of Blasting, Major:} On command, this elaborate golden headband projects a blast of \spell{searing light} (5d8 maximized for 40 points of damage) once per day.

Strong evocation; CL 17th; \feat{Craft Wondrous Item}, \feat{Maximize Spell}, \spell{searing light}; Price 23,760 cp.


\textbf{Circlet of Persuasion:} This silver headband grants a +3 competence bonus on the wearer's Charisma-based checks.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{eagle's splendor}; Price 4,500 cp.


\textbf{Hat of Disguise:} This apparently normal hat allows its wearer to alter her appearance as with a \spell{disguise self} spell. As part of the disguise, the hat can be changed to appear as a comb, ribbon, headband, cap, coif, hood, helmet, and so on.

Faint illusion; CL 1st; \feat{Craft Wondrous Item}, \spell{disguise self}; Price 1,800 cp.


\textbf{Headband of Intellect:} This device is a light cord with a small gem set so that it rests upon the forehead of the wearer. When in a character's possession, their Intelligence score becomes 19. This does not earn the wearer extra skill points when a new level is attained; use the unenhanced Intelligence bonus to determine skill points.

Moderate transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{fox's cunning}; Price 16,000 cp.


\textbf{Helm of Brilliance:} This normal-looking helm takes its true form and manifests its powers when the user dons it and speaks the command word. Made of brilliant silver and polished steel, a newly created helm is set with large magic gems: ten diamonds, twenty rubies, thirty fire opals, and forty opals. When struck by bright light, the helm scintillates and sends forth reflective rays in all directions from its crownlike, gem-tipped spikes. The jewels' functions are as follows:

\begin{itemize*}
\item Diamond: \spellref{prismatic spray}{Prismatic spray} (save DC 20)
\item Ruby: \spellref{wall of fire}{Wall of fire}
\item Fire opal: \spell{Fireball} (10d6, Reflex DC 20 half)
\item Opal: \spell{Daylight}
\end{itemize*}

The helm may be used once per round, but each gem can perform its spell-like power just once. Until all its jewels are depleted, a helm of brilliance also has the following magical properties when activated.

\begin{itemize*}
\item It emanates a bluish light when undead are within 9 meters. This light causes 1d6 points of damage per round to all such creatures within that range.
\item The wearer may command any weapon he wields to become a flaming weapon. This is in addition to whatever abilities the weapon may already have (unless the weapon already is a flaming weapon). The command takes 1 round to take effect.
\item The helm provides resistance to fire 30. This protection does not stack with similar protection from other sources.
\item Once all its jewels have lost their magic, the helm loses its powers and the gems turn to worthless powder. Removing a jewel destroys it.
\end{itemize*}

If a creature wearing the helm is damaged by magical fire (after the fire protection is taken into account) and fails an additional DC 15 Will save, the remaining gems on the helm overload and detonate. Remaining diamonds become prismatic sprays that each randomly target a creature within range (possibly the wearer), rubies become straight-line walls of fire extending outward in a random direction from the helm wearer, and fire opals become fireballs centered on the helm wearer. The opals and the helm itself are destroyed.

Strong varied; CL 13th; \feat{Craft Wondrous Item}, \spell{detect undead}, \spell{fireball}, \spell{flame blade}, \spell{light}, \spell{prismatic spray}, \spell{protection from energy}, \spell{wall of fire}; Price 125,000 cp; Weight 1.5 kg.


\textbf{Helm of Comprehend Languages and Read Magic:} Appearing as a normal helmet, a helm of comprehend languages and read magic grants its wearer the ability to understand the spoken words of any creature and to read text in any language and any magical writing. The wearer gains a +5 competence bonus on Decipher Script checks to understand messages written in incomplete, archaic, or exotic forms. Note that understanding a magical text does not necessarily imply spell use.

Faint divination; CL 4th; \feat{Craft Wondrous Item}, \spell{comprehend languages}, \spell{read magic}; Price 5,200 cp; Weight 1.5 kg.


\textbf{Helm of Telepathy:} The wearer can use \spell{detect thoughts} at will. Furthermore, he can send a telepathic message to anyone whose surface thoughts he is reading (allowing two-way communication). Once per day, the wearer of the helm can implant a \spell{suggestion} (as the spell, Will DC 14 negates) along with his telepathic message.

Faint divination and enchantment; CL 5th; \feat{Craft Wondrous Item}, \spell{detect thoughts}, \spell{suggestion}; Price 27,000 cp; Weight 1.5 kg.


\textbf{Helm of Teleportation:} A character wearing this device may teleport three times per day, exactly as if he had cast the spell of the same name.

Moderate conjuration; CL 9th; \feat{Craft Wondrous Item}, \spell{teleport}; Price 73,500 cp; Weight 1.5 kg.


\textbf{Helm of Underwater Action:} The wearer of this helmet can see underwater. Drawing the small lenses in compartments on either side into position before the wearer's eyes activates the visual properties of the helm, allowing her to see five times farther than water and light conditions would allow for normal human vision. (Weeds, obstructions, and the like block vision in the usual manner.) If the command word is spoken, the helm of underwater action creates a globe of air around the wearer's head and maintains it until the command word is spoken again, enabling her to breathe freely.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{water breathing}; Price 24,000 cp; Weight 1.5 kg.


\textbf{Phylactery of Faithfulness:} This item is a small box containing religious scripture affixed to a leather cord and tied around the forehead. There is no mundane way to determine what function this religious item performs until it is worn. The wearer of a \emph{phylactery of faithfulness} is aware of any action or item that could adversely affect his alignment and his standing with his deity, including magical effects. He acquires this information prior to performing such an action or becoming associated with such an item if he takes a moment to contemplate the act.

Faint divination; CL 1st; \feat{Craft Wondrous Item}, \spell{detect chaos}, \spell{detect evil}, \spell{detect good}, \spell{detect law}; Price 1,000 cp.


\textbf{Phylactery of Undead Turning:} This item is a boon to any character able to turn undead, allowing him to do so as if his class level were four levels higher than it actually is.

Moderate necromancy [good]; CL 10th; \feat{Craft Wondrous Item}, 10th-level cleric; Price 11,000 cp.
