\subsubsection{Miscellaneous}



\textbf{Apparatus of the Crab:} This item appears to be a large, sealed iron barrel, but it has a secret catch (Search DC 20 to locate) that opens a hatch in one end. Anyone who crawls inside finds ten (unlabeled) levers: The device has the following characteristics: hp 200; hardness 15; Spd 6 m, swim 6 m; AC 20 ($-1$ size, +11 natural); Atk +12 melee (2d8, 2 pincers).

\Table{}{cL}{
  \tableheader Lever (1d10)
& \tableheader Lever Function\\
1  & Extend/retract legs and tail\\
2  & Uncover/cover forward porthole\\
3  & Uncover/cover side portholes\\
4  & Extend/retract pincers and feelers\\
5  & Snap pincers\\
6  & Move forward/backward\\
7  & Turn left/right\\
8  & Open ``eyes'' with continual flame inside/close ``eyes''\\
9  & Rise/sink in water\\
10 & Open/close hatch\\
}

Operating a lever is a full-round action, and no lever may be operated more than once per round. However, since two Medium characters can fit inside, the apparatus can move and attack in the same round. The device can function in water up to 270 meters deep. It holds enough air for a crew of two to survive 1d4+1 hours (twice as long for a single occupant). When activated, the apparatus looks something like a giant lobster.

Strong evocation and transmutation; CL 19th; \feat{Craft Wondrous Item}, \spell{animate objects}, \spell{continual flame}, creator must have 8 ranks in the Knowledge (architecture and engineering) skill; Price 90,000 cp; Weight 250 kg.



\textbf{Bag of Holding:} This appears to be a common cloth sack about 60 centimeters by 1.2 meter in size. The \emph{bag of holding} opens into a nondimensional space: Its inside is larger than its outside dimensions. Regardless of what is put into the bag, it weighs a fixed amount. This weight, and the limits in weight and volume of the bag's contents, depend on the bag's type, as shown on the table below.

\Table{}{llCCR}{
  \tableheader Bag
& \tableheader Bag Weight
& \tableheader Contents Weight Limit
& \tableheader Contents Volume Limit
& \tableheader Market Price \\
Type I   &  7.5 kg & 125 kg &   850 L & 2,500 cp \\
Type II  & 12.5 kg & 250 kg & 2,000 L & 5,000 cp \\
Type III & 17.5 kg & 500 kg & 4,250 L & 7,400 cp \\
Type IV  & 30   kg & 750 kg & 7,000 L & 10,000 cp \\
}

If the bag is overloaded, or if sharp objects pierce it (from inside or outside), the bag ruptures and is ruined. All contents are lost forever. If a \emph{bag of holding} is turned inside out, its contents spill out, unharmed, but the bag must be put right before it can be used again. If living creatures are placed within the bag, they can survive for up to 10 minutes, after which time they suffocate. Retrieving a specific item from a \emph{bag of holding} is a move action---unless the bag contains more than an ordinary backpack would hold, in which case retrieving a specific item is a full-round action.

If a \emph{bag of holding} is placed within a \emph{portable hole} a rift to the Astral Plane is torn in the space: Bag and hole alike are sucked into the void and forever lost. If a \emph{portable hole} is placed within a \emph{bag of holding}, it opens a gate to the Astral Plane: The hole, the bag, and any creatures within a 3-meter radius are drawn there, destroying the \emph{portable hole} and \emph{bag of holding} in the process.

Moderate conjuration; CL 9th; \feat{Craft Wondrous Item}, \spell{secret chest}.



\textbf{Bag of Tricks:} This small sack appears normal and empty. However, anyone reaching into the bag feels a small, fuzzy ball. If the ball is removed and tossed up to 6 meters away, it turns into an animal. The animal serves the character who drew it from the bag for 10 minutes (or until slain or ordered back into the bag), at which point it disappears. It can follow any of the commands described in the \skill{Handle Animal} skill. Each of the three kinds of a bag of tricks produces a different set of animals. Use the following tables to determine what animals can be drawn out of each.

The heavy warhorse appears with harness and tack and accepts the character who drew it from the bag as a rider.

Animals produced are always random, and only one may exist at a time. Up to ten animals can be drawn from the bag each week.

Faint or moderate conjuration; CL 3rd (gray), 5th (rust), 9th (tan); \feat{Craft Wondrous Item}, \spell{summon nature's ally II} (gray), \spell{summon nature's ally III} (rust), or \spell{summon nature's ally V} (tan); Price 900 cp (gray); 3,000 cp (rust); 6,300 cp (tan).

\Table{}{cl|cX|cl}{
\multicolumn{2}{c}{\tableheader Gray}
& \multicolumn{2}{c}{\tableheader Rust}
& \multicolumn{2}{c}{\tableheader Tan} \\
\cmidrule[0.5pt]{1-6}
  \tableheader d\%
& \tableheader Animal
& \tableheader d\%
& \tableheader Animal
& \tableheader d\%
& \tableheader Animal\\

01--30  & Bat    & 01--30  & Wolverine  & 01--30  & Brown bear \\
31--60  & Rat    & 31--60  & Wolf       & 31--60  & Lion \\
61--75  & Cat    & 61--85  & Boar       & 61--80  & Heavy warhorse \\
76--90  & Weasel & 86--100 & Black bear & 81--90  & Tiger \\
91--100 & Badger &         &            & 91--100 & Rhinoceros \\
}



\textbf{Bead of Force:} This small black sphere appears to be a lusterless pearl. You can throw it up to 18 meters with no range penalties. Upon sharp impact, the bead explodes, sending forth a burst that deals 5d6 points of force damage to all creatures within a 3-meter radius.

It functions like a \spell{resilient sphere} spell (Reflex DC 16 negates) with a radius of 3 meters and a duration of 10 minutes. A globe of shimmering force encloses a creature, provided the latter is small enough to fit within the diameter of the sphere. The sphere contains its subject for the spell's duration. The sphere is not subject to damage of any sort except from a rod of cancellation, a rod of negation, disintegrate, or a targeted \spell{dispel magic} spell. These effects destroy the sphere without harm to the subject. Nothing can pass through the sphere, inside or out, though the subject can breathe normally. The subject may struggle, but the globe cannot be physically moved either by people outside it or by the struggles of those within.

The explosion completely consumes the bead, making this a one-use item.

Moderate evocation; CL 10th; \feat{Craft Wondrous Item}, \spell{resilient sphere}; Price 3,000 cp.



% \textbf{Blessed Book:} This well-made tome is always of small size, typically no more than 30 centimeters tall, 20 centimeters wide, and 3 centimeters thick. All such books are durable, waterproof, bound with iron overlaid with silver, and locked.

% A wizard can fill the 1,000 pages of a blessed book with spells without paying the 100 cp per page material cost. This book is never found as randomly generated treasure with spells already inscribed in it.

% Moderate transmutation; CL 7th; \feat{Craft Wondrous Item}, \spell{secret page}; Price 12,500 cp; Weight 0.5 kg.



\textbf{Boat, Folding:} A folding boat looks like a small wooden box---about 30 centimeters long, 15 centimeters wide, and 15 centimeters deep. It can be used to store items like any other box. If a command word is given, however, the box unfolds itself to form a boat 3 meters long, 1.2 meter wide, and 60 centimeters in depth. A second command word causes it to unfold to a ship 7.3 meters long, 2.4 meters wide, and 1.8 meter deep. Any objects formerly stored in the box now rest inside the boat or ship.

In its smaller form, the boat has one pair of oars, an anchor, a mast, and a lateen sail. In its larger form, the boat has a deck, single rowing seats, five sets of oars, a steering oar, an anchor, a deck cabin, and a mast with a square sail. The boat can hold four people comfortably, while the ship carries fifteen with ease.

A third word of command causes the boat or ship to fold itself into a box once again.

Faint transmutation; CL 6th; \feat{Craft Wondrous Item}, \spell{fabricate}, creator must have 2 ranks in the Craft (shipmaking) skill; Price 7,200 cp; Weight 2 kg.



\textbf{Bottle of Air:} This item appears to be a normal glass bottle with a cork. When taken to any airless environment it retains air within it at all times, continually renewing its contents. This means that a character can draw air out of the bottle to breathe. The bottle can even be shared by multiple characters who pass it around. Breathing out of the bottle is a standard action, but a character so doing can then act for as long as she can hold her breath.

Moderate transmutation; CL 7th; \feat{Craft Wondrous Item}, \spell{water breathing}; Price 7,250 cp; Weight 1 kg.



\textbf{Bowl of Commanding Water Elementals:} This large container is usually fashioned from blue or green semiprecious stone. It is about 30 centimeters in diameter, half that deep, and relatively fragile. When the bowl is filled with fresh water, and certain words are spoken, a Large water elemental appears. The summoning words require 1 full round to speak. In all ways the bowl functions as the \spell{summon monster VI} spell. Only one elemental can be called at a time. A new elemental requires the bowl to be filled with new water, which cannot happen until after the first elemental disappears (is dispelled, dismissed, or slain).

If salt water is used, the elemental is Huge rather than Large (as if \spell{summon monster VII} had been cast).

Strong conjuration; CL 13th; \feat{Craft Wondrous Item}, \spell{summon monster VI}, \spell{summon monster VII}; Price 100,000 cp; Weight 1.5 kg.



\textbf{Brazier of Commanding Fire Elementals:} This device appears to be a normal container for holding burning coals. When a fire is lit in the brazier and the proper summoning words are spoken, a Large fire elemental appears. The summoning words require 1 full round to speak. In all ways the brazier functions as the \spell{summon monster VI} spell. If brimstone is added, the elemental is Huge instead of Large, and the brazier works as a \spell{summon monster VII} spell. Only one elemental can be summoned at a time. A new elemental requires a new fire, which cannot be lit until after the first elemental disappears (is dispelled, dismissed, or slain).

Strong conjuration; CL 13th; \feat{Craft Wondrous Item}, \spell{summon monster VI}, \spell{summon monster VII}; Price 100,000 cp; Weight 2.5 kg.



\textbf{Brooch of Shielding:} This appears to be a piece of silver or gold jewelry used to fasten a cloak or cape. In addition to this mundane task, it can absorb \spell{magic missiles} of the sort generated by spell or spell-like ability. A brooch can absorb up to 101 points of damage from \spell{magic missiles} before it melts and becomes useless.

Faint abjuration; CL 1st; \feat{Craft Wondrous Item}, \spell{shield}; Price 1,500 cp.



\textbf{Broom of Flying:} This broom is able to fly through the air as if affected by an \spell{overland flight} spell (average maneuverability) for up to 9 hours per day (split up as its owner desires). The broom can carry 200 pounds and fly at a speed of 12 meters, or up to 200 kilograms at a speed at 9 meters. In addition, the broom can travel alone to any destination named by the owner as long as she has a good idea of the location and layout of that destination. It comes to its owner from as far away as 270 meters when she speaks the command word. The broom of flying has a speed of 12 meters when it has no rider.

Moderate transmutation; CL 9th; \feat{Craft Wondrous Item}, \spell{overland flight}, \spell{permanency}; Price 17,000 cp; Weight 1.5 kg.



\textbf{Candle of Invocation:} Each of these special tapers is dedicated to one of the nine alignments. Simply burning the candle generates a favorable aura for the individual so doing if the candle's alignment matches that of the character. Characters of the same alignment as the burning candle add a +2 morale bonus on attack rolls, saving throws, and skill checks while within 9 meters of the flame.

A cleric whose alignment matches the candle's operates as if two levels higher for purposes of determining spells per day if he burns the candle during or just prior to his spell preparation time. He can even cast spells normally unavailable to him, as if he were of that higher level, but only so long as the candle continues to burn. Except in special cases (see below), a candle burns for 4 hours.

In addition, burning a candle also allows the owner to cast a \spell{gate} spell, the respondent being of the same alignment as the candle, but the taper is immediately consumed in the process. It is possible to extinguish the candle simply by blowing it out, so users often place it in a lantern to protect it from drafts and the like. Doing this doesn't interfere with its magical properties.

Strong conjuration; CL 17th; \feat{Craft Wondrous Item}, \spell{gate}, creator must be same alignment as candle created; Price 8,400 cp; Weight 0.25 kg.



\textbf{Candle of Truth:} This white tallow candle, when burned, calls into place a \spell{zone of truth} spell (Will DC 13 negates) in a 1.5-meter radius centered on the candle. The zone lasts for 1 hour, as the candle burns. If the candle is snuffed before that time, the effect is canceled and the candle ruined.

Faint enchantment; CL 3rd; \feat{Craft Wondrous Item}, \spell{zone of truth}; Price 2,500 cp; Weight 0.25 kg.



\textbf{Cape of the Mountebank:} On command, this bright red and gold cape allows the wearer to use the magic of the \spell{dimension door} spell once per day. When he disappears, he leaves behind a cloud of smoke, appearing in a similar fashion at his destination.

Moderate conjuration; CL 9th; \feat{Craft Wondrous Item}, \spell{dimension door}; Price 10,080 cp; Weight 0.5 kg.



\textbf{Carpet of Flying:} This rug is able to fly through the air as if affected by an \spell{overland flight} spell of unlimited duration. The size, carrying capacity, and speed of the different carpets of flying are shown on the table below. Beautifully and intricately made, each carpet has its own command word to activate it---if the device is within voice range, the command word activates it, whether the speaker is on the rug or not. The carpet is then controlled by spoken directions.

\Table{}{*4cR}{
  \tableheader Size
& \tableheader Capacity
& \tableheader Speed
& \tableheader Weight
& \tableheader Market Price \\

1.5 m by 1.5 m & 100 kg & 12 m &   4 kg & 20,000 cp \\
1.5 m by 3 m   & 200 kg & 12 m &   5 kg & 35,000 cp \\
3 m by 3 m     & 400 kg & 12 m & 7.5 kg & 60,000 cp \\
}

A carpet of flying can carry up to double its capacity, but doing so reduces its speed to 9 meters. It has average maneuverability, but a carpet of flying can still hover.

Moderate transmutation; CL 10th; \feat{Craft Wondrous Item}, \spell{overland flight}, \spell{permanency}.



\textbf{Censer of Controlling Air Elementals:} This 15-centimeter-wide, 3-centimeter-high perforated golden vessel resembles a thurible found in a place of worship. If it is filled with incense and lit, summoning words spoken over it summon forth a Large air elemental. The summoning words require 1 full round to speak. In all ways the censer functions as the \spell{summon monster VI} spell. If \emph{incense of meditation} is burned within the censer, the air elemental is an elder air elemental instead (as if \spell{summon monster IX} had just been cast). Only one elemental can be summoned at a time. A new elemental requires a new piece of incense, which cannot be lit until after the first elemental disappears (is dispelled, dismissed, or slain).

Strong conjuration; CL 17th; \feat{Craft Wondrous Item}, \spell{summon monster VI}, \spell{summon monster IX}; Price 100,000 cp; Weight 0.5 kg.



\textbf{Chaos Diamond:} This lustrous gemstone is uncut and about the size of a human fist. The gem grants its possessor the following powers:

\begin{itemize*}
\item \spellref{lesser confusion}{Confusion, lesser}
\item \spellref{magic circle against law}{Magic circle against law}
\item \spellref{word of chaos}{Word of chaos}
\item \spellref{cloak of chaos}{Cloak of chaos}
\end{itemize*}

Each power is usable 1d4 times per day. This is rolled for each power individually and the character does not know the result.

A nonchaotic character who possesses a chaos diamond gains one negative level. Although this level never results in actual level loss, it remains as long as the diamond is in the character's possession and cannot be overcome in any way (including restoration spells).

Strong varied; CL 19th; \feat{Craft Wondrous Item}, \spell{cloak of chaos}, \spell{magic circle against law}, \spell{lesser confusion}, \spell{word of chaos}, creator must be chaotic; Price 160,000 cp; Weight 0.5 kg.



\textbf{Chime of Interruption:} This instrument can be struck once every 10 minutes, and its resonant tone lasts for 3 full minutes.

While the chime is resonating, no spell requiring a verbal component can be cast within a 9-meter radius of it unless the caster can make a \skill{Concentration} check (DC 15 + the spell's level).

Moderate evocation; CL 7th; \feat{Craft Wondrous Item}, \spell{shout}; Price 16,800 cp; Weight 0.5 kg.



\textbf{Chime of Opening:} A \emph{chime of opening} is a hollow mithral tube about 30 centimeters long. When struck, it sends forth magical vibrations that cause locks, lids, doors, valves, and portals to open. The device functions against normal bars, shackles, chains, bolts, and so on. A \emph{chime of opening} also automatically dispels a \spell{hold portal} spell or even an \spell{arcane lock} cast by a wizard of lower than 15th level.

The chime must be pointed at the item or gate to be loosed or opened (which must be visible and known to the user). The chime is then struck, a clear tone rings forth, and in 1 round the target lock is unlocked, the shackle is loosed, the secret door is opened, or the lid of the chest is lifted. Each sounding only opens one form of locking, so if a chest is chained, padlocked, locked, and \emph{arcane locked}, it takes four uses of a \emph{chime of opening} to get it open. A \spell{silence} spell negates the power of the device. A brand-new chime can be used a total of ten times before it cracks and becomes useless.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{knock}; Price 3,000 cp; Weight 0.5 kg.



\textbf{Crystal Ball:} This is the most common form of scrying device, a crystal sphere about 15 centimeters in diameter. A character can use the device to see over virtually any distance or into other planes of existence, as with the spell \spell{scrying} (Will DC 16 negates).

Certain crystal balls have additional powers that can be used through the crystal ball on the target viewed.

\Table{}{Lr{15mm}}{
  \tableheader Crystal Ball Type
& \tableheader Market Price \\
Crystal ball                                                   & 42,000 cp \\
Crystal ball with \spell{see invisibility}                     & 50,000 cp \\
Crystal ball with \spell{detect thoughts} (Will DC 13 negates) & 51,000 cp \\
Crystal ball with telepathy\footnotemark[1]                    & 70,000 cp \\
Crystal ball with \spell{true seeing}                          & 80,000 cp \\
\TableNote{2}{1 The viewer is able to send and receive silent mental messages with the person appearing in the crystal ball. Once per day the character may attempt to implant a \spell{suggestion} (as the spell, Will DC 14 negates) as well.}
}

Moderate divination; CL 10th; \feat{Craft Wondrous Item}, \spell{scrying} (plus any additional spells put into item); Weight 3.5 kg.



\textbf{Cube of Force:} This device is about 2 centimeters across and can be made of ivory, bone, or any hard mineral. It enables its possessor to put up a special wall of force 3 meters on a side around her person. This cubic screen moves with the character and is impervious to the attack forms mentioned on the table below. The cube has 36 charges, which are renewed each day. The possessor presses one face of the cube to activate a particular type of screen or to deactivate the device. Each effect costs a certain number of charges to maintain for every minute (or portion of a minute) it is in operation. Also, when an effect is active, the possessor's speed is limited to the maximum value given on the table.

When the \emph{cube of force} is active, attacks dealing more than 30 points of damage drain 1 charge for every 10 points of damage beyond 30 that they deal. Spells that affect the integrity of the screen also drain extra charges. These spells (given in the list below) cannot be cast into or out of the cube:

\Table{}{CCcl}{
  \tableheader Cube Face
& \tableheader Charge Cost per Minute
& \tableheader Maximum Speed
& \tableheader Effect\\
1 & 1 & 9 m       & Keeps out gases, wind, etc. \\
2 & 2 & 6 m       & Keeps out nonliving matter \\
3 & 3 & 4.5 m     & Keeps out living matter \\
4 & 4 & 3 m       & Keeps out magic \\
5 & 6 & 3 m       & Keeps out all things \\
6 & 0 & As normal & Deactivates \\
}

\Table{}{LC}{
  \tableheader Attack Form
& \tableheader Extra Charges\\
\emph{Horn of blasting}  & 6 \\
\spellref{wall of fire}{Wall of fire}     & 2 \\
\spell{Passwall}         & 3 \\
\spell{Disintegrate}     & 6 \\
\spellref{phase door}{Phase door}       & 5 \\
\spellref{prismatic spray}{Prismatic spray}  & 7 \\
}

Moderate evocation; CL 10th; \feat{Craft Wondrous Item}, \spell{wall of force}; Price 62,000 cp.



\textbf{Cube of Frost Resistance:} This cube is activated or deactivated by pressing one side. When activated, it creates a cube-shaped area 3 meters on a side centered on the possessor (or on the cube itself, if the item is later placed on a surface). The temperature within this area is always at least 18°C. The field absorbs all cold-based attacks. However, if the field is subjected to more than 50 points of cold damage in 1 round (from one or multiple attacks), it collapses into its portable form and cannot be reactivated for 1 hour. If the field absorbs more than 100 points of cold damage in a 10-round period, the cube is destroyed.

Faint abjuration; CL 5th; \feat{Craft Wondrous Item}, \spell{protection from energy}; Price 27,000 cp.



\textbf{Cubic Gate:} This item is fashioned from carnelian. Each of the six sides of the cube is keyed to a plane, one of which is the Material Plane. The character creating the item should choose the planes to which the other five sides are keyed.

If a side of the \emph{cubic gate} is pressed once, it opens a gate to a random point on the plane keyed to that side. There is a 10\% chance per minute that an outsider from that plane (determine randomly) comes through it looking for food, fun, or trouble. Pressing the side a second time closes the gate. It is impossible to open more than one gate at a time.

If a side is pressed twice in quick succession, the character so doing is transported to a random point on the other plane, along with all creatures in adjacent squares. (The other creatures may avoid this fate by succeeding on DC 23 Will saves).

Strong conjuration; CL 13th; \feat{Craft Wondrous Item}, \spell{plane shift}; Price 164,000 cp.



\textbf{Darkskull:} This skull, carved from ebony, is wholly evil. Wherever the skull goes, the area around it is treated as though an \spell{unhallow} spell had been cast with the skull as the touched point of origin (except that no additional spell effect is tied or fixed to the \emph{darkskull}).

Moderate evocation [evil]; CL 9th; \feat{Craft Wondrous Item}, \spell{unhallow}, creator must be evil; Price 60,000 cp; Weight 2.5 kg.



\textbf{Decanter of Endless Water:} If the stopper is removed from this ordinary-looking flask and a command word spoken, an amount of fresh or salt water pours out. Separate command words determine the type as well as the volume and velocity.

\begin{itemize*}
\item ``Stream'' pours out 4 liters per round.
\item ``Fountain'' produces a 1.5-meter-long stream at 20 liters per round.
\item ``Geyser'' produces a 6-meter-long, 30-centimeter-wide stream at 135 liters per round.
\end{itemize*}

The geyser effect causes considerable back pressure, requiring the holder to make a DC 12 Strength check to avoid being knocked down. The force of the geyser deals 1d4 points of damage but can only affect one target per round. The command word must be spoken to stop it.

Moderate transmutation; CL 9th; \feat{Craft Wondrous Item}, \spell{control water}; Price 9,000 cp; Weight 1 kg.



\textbf{Deck of Illusions:} This set of parchment cards is usually found in an ivory, leather, or wooden box. A full deck consists of thirty-four cards. When a card is drawn at random and thrown to the ground, a major image of a creature is formed. The figment lasts until dispelled. The illusory creature cannot move more than 9 meters away from where the card landed, but otherwise moves and acts as if it were real. At all times it obeys the desires of the character who drew the card. When the illusion is dispelled, the card becomes blank and cannot be used again. If the card is picked up, the illusion is automatically and instantly dispelled. The cards in a deck and the illusions they bring forth are summarized on the following table. (Use one of the first two columns to simulate the contents of a full deck using either ordinary playing cards or tarot cards.)

\Table{Deck of Illusions}{llL}{
  \tableheader Playing Card
& \tableheader Tarot Card
& \tableheader Creature\\

Ace of hearts     & IV. The Emperor        & Red dragon \\
King of hearts    & Knight of swords       & Male human fighter and four guards \\
Queen of hearts   & Queen of staves        & Female human wizard \\
Jack of hearts    & King of staves         & Male human druid \\
Ten of hearts     & VII. The Chariot       & Cloud giant \\
Nine of hearts    & Page of staves         & Ettin \\
Eight of hearts   & Ace of cups            & Bugbear \\
Two of hearts     & Five of staves         & Goblin \\
Ace of diamonds   & III. The Empress       & Glabrezu (demon) \\
King of diamonds  & Two of cups            & Male elf wizard and female apprentice \\
Queen of diamonds & Queen of swords        & Half-elf ranger (female) \\
Jack of diamonds  & XIV. Temperance        & Harpy \\
Ten of diamonds   & Seven of staves        & Male half-orc barbarian \\
Nine of diamonds  & Four of pentacles      & Ogre mage \\
Eight of diamonds & Ace of pentacles       & Gnoll \\
Two of diamonds   & Six of pentacles       & Kobold \\
Ace of spades     & II. The High Priestess & Lich \\
King of spades    & Three of staves        & Three male human clerics \\
Queen of spades   & Four of cups           & Medusa \\
Jack of spades    & Knight of pentacles    & Male dwarf paladin \\
Ten of spades     & Seven of swords        & Frost giant \\
Nine of spades    & Three of swords        & Troll \\
Eight of spades   & Ace of swords          & Hobgoblin \\
Two of spades     & Five of cups           & Goblin \\
Ace of clubs      & VIII. Strength         & Iron golem \\
King of clubs     & Page of pentacles      & Three male halfling rogues \\
Queen of clubs    & Ten of cups            & Pixies \\
Jack of clubs     & Nine of pentacles      & Female half-elf bard \\
Ten of clubs      & Nine of staves         & Hill giant \\
Nine of clubs     & King of swords         & Ogre \\
Eight of clubs    & Ace of staves          & Orc \\
Two of clubs      & Five of cups           & Kobold \\
Joker             & Two of pentacles       & Illusion of deck's owner \\
Joker             & Two of staves          & Illusion of deck's owner (sex reversed) \\
}

A randomly generated deck is usually complete (11-100 on d\%), but may be discovered (01-10) with 1d20 of its cards missing. If cards are missing, reduce the price by a corresponding amount.

Faint illusion; CL 6th; \feat{Craft Wondrous Item}, \spell{major image}; Price 8,100 cp; Weight 0.25 kg.



\textbf{Dimensional Shackles:} These shackles have golden runes traced across their cold iron surface. Any creature bound within them is affected as if a \spell{dimensional anchor} spell were cast upon her (no save). They fit any Small to Large creature. The DC to break or slip out of the shackles is 30.

Moderate abjuration; CL 11th; \feat{Craft Wondrous Item}, \spell{dimensional anchor}; Price 28,000 cp; Weight 2.5 kg.



\textbf{Drums of Panic:} These drums are kettle drums (hemispheres about 45 centimeters in diameter on stands). They come in pairs and are unremarkable in appearance. If both of the pair are sounded, all creatures within 36 meters (with the exception of those within a 6-meter-radius safe zone around the drums) are affected as by a \spell{fear} spell (Will DC 16 partial). \emph{Drums of panic} can be used once per day.

Moderate necromancy; CL 7th; \feat{Craft Wondrous Item}, \spell{fear}; Price 30,000 cp; Weight 5 kg. for the pair.



\textbf{Dust of Appearance:} This fine powder appears to be a very fine, very light metallic dust. A single handful of this substance flung into the air coats objects within a 3-meter radius, making them visible even if they are invisible. It likewise negates the effects of \spell{blur} and \spell{displacement}. (In this, it works just like the \spell{faerie fire} spell). The dust also reveals figments, \spell{mirror images}, and projected images for what they are. A creature coated with the dust takes a $-30$ penalty on its \skill{Hide} checks. The dust's effect lasts for 5 minutes.

\emph{Dust of appearance} is typically stored in small silk packets or hollow bone tubes.

Faint conjuration; CL 5th; \feat{Craft Wondrous Item}, \spell{glitterdust}; Price 1,800 cp.



\textbf{Dust of Disappearance:} This dust looks just like \emph{dust of appearance} and is typically stored in the same manner. A creature or object touched by it becomes invisible (as \spell{greater invisibility}). Normal vision can't see dusted creatures or objects, nor can they be detected by magical means, including \spell{see invisibility} or \spell{invisibility purge}. \emph{Dust of appearance}, however, does reveal people and objects made invisible by \emph{dust of disappearance}. Other factors, such as sound and smell, also allow possible detection.

The \spell{greater invisibility} bestowed by the dust lasts for 2d6 rounds.The invisible creature doesn't know when the duration will end.

Moderate illusion; CL 7th; \feat{Craft Wondrous Item}, \spell{greater invisibility}; Price 3,500 cp.



\textbf{Dust of Dryness:} This special dust has many uses. If it is thrown into water, a volume of as much as 450 liters is instantly transformed to nothingness, and the dust becomes a marble-sized pellet, floating or resting where it was thrown. If this pellet is hurled down, it breaks and releases the same volume of water. The dust affects only water (fresh, salt, alkaline), not other liquids.

If the dust is employed against an elemental with the water subtype, the creature must make a DC 18 Fortitude save or be destroyed. The dust deals 5d6 points of damage to the creature even if its saving throw succeeds.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{control water}; Price 850 cp.



\textbf{Dust of Illusion:} This unremarkable powder resembles chalk dust or powdered graphite. Stare at it, however, and the dust changes color and form. Put dust of illusion on a creature, and that creature is affected as if by a \spell{disguise self} glamer, with the individual who sprinkles the dust envisioning the illusion desired. An unwilling target is allowed a DC 11 Reflex save to avoid the dust. The glamer lasts for 2 hours.

Faint illusion; CL 6th; \feat{Craft Wondrous Item}, \spell{disguise self}; Price 1,200 cp.



\textbf{Dust of Tracelessness:} This normal-seeming dust is actually a magic powder that can conceal the passage of its possessor and his companions. Tossing a handful of this dust into the air causes a chamber of up to 9 square meters of floor space to become as dusty, dirty, and cobweb-laden as if it had been abandoned and disused for a decade.

A handful of dust sprinkled along a trail causes evidence of the passage of as many as a dozen men and horses to be obliterated for 75 meters back into the distance. The results of the dust are instantaneous, and no magical aura lingers afterward from this use of the dust. \skill{Survival} checks made to track a quarry across an area affected by this dust have a DC 20 higher than normal.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{pass without trace}; Price 250 cp.



\textbf{Efficient Quiver:} This appears to be a typical arrow container capable of holding about twenty arrows. It has three distinct portions, each with a nondimensional space allowing it to store far more than would normally be possible. The first and smallest one can contain up to sixty objects of the same general size and shape as an arrow. The second slightly longer compartment holds up to eighteen objects of the same general size and shape as a javelin. The third and longest portion of the case contains as many as six objects of the same general size and shape as a bow (spears, staffs, or the like). Once the owner has filled it, the quiver can produce any item she wishes, as if from a regular quiver or scabbard. The \emph{efficient quiver} weighs the same no matter what's placed inside it.

Moderate conjuration; CL 9th; \feat{Craft Wondrous Item}, \spell{secret chest}; Price 1,800 cp; Weight 1 kg.



\textbf{Efreeti Bottle:} This item is typically fashioned of brass or bronze, with a lead stopper bearing special seals. A thin stream of smoke is often seen issuing from it. The bottle can be opened once per day. When opened, the efreeti imprisoned within issues from the bottle instantly. There is a 10\% chance (01-10 on d\%) that the efreeti is insane and attacks immediately upon being released. There is also a 10\% chance (91-100) that the efreeti of the bottle grants three wishes. In either case, the efreeti afterward disappears forever. The other 80\% of the time (11-90), the inhabitant of the bottle loyally serves the character for up to 10 minutes per day (or until the efreeti's death), doing as she commands. Roll each day the bottle is opened for that day's effect.

Strong conjuration; CL 14th; \feat{Craft Wondrous Item}, \spell{summon monster VII}; Price 145,000 cp; Weight 0.5 kg.



\textbf{Elemental Gem:} This gem contains a conjuration spell attuned to a specific Elemental Plane (Air, Earth, Fire, or Water).

When the gem is crushed, smashed, or broken (a standard action), a Large elemental appears as if summoned by a \spell{summon nature's ally} spell. The elemental is under the control of the creature that broke the gem.

The coloration of the gem varies with the type of elemental it summons. \emph{Air elemental gems} are transparent, \emph{earth elemental gems} are light brown, \emph{fire elemental gems} are reddish orange, and \emph{water elemental gems} are blue-green.

Moderate conjuration; CL 11th; \feat{Craft Wondrous Item}, \spell{summon nature's ally V}; Price 2,250 cp.



\textbf{Elixir of Fire Breath:} This strange elixir bestows upon the drinker the ability to spit gouts of flame. He can breathe fire up to three times, each time dealing 4d6 points of fire damage to a single target up to 7.5 meters away. The victim can attempt a DC 13 Reflex save for half damage. Unused blasts dissipate 1 hour after the liquid is consumed.

Moderate evocation; CL 11th; \feat{Craft Wondrous Item}, \spell{scorching ray}; Price 1,100 cp.



\textbf{Elixir of Hiding:} A character drinking this liquid gains an intuitive ability to hide (+10 competence bonus on \skill{Hide} checks for 1 hour).

Faint illusion; CL 5th; \feat{Craft Wondrous Item}, \spell{invisibility}; Price 250 cp.



\textbf{Elixir of Love:} This sweet-tasting liquid causes the character drinking it to become charmed with the first creature she sees after consuming the draft (as \spell{charm person}---the drinker must be a humanoid of Medium or smaller size, Will DC 14 negates). The charm effects wear off in 1d3 hours.

Faint transmutation; CL 4th; \feat{Craft Wondrous Item}, \spell{charm person}; Price 150 cp.



\textbf{Elixir of Sneaking:} This draught of liquid grants the drinker the ability to walk softly and dampens sound around her slightly, granting a +10 competence bonus on \skill{Move Silently} checks for 1 hour.

Faint illusion; CL 5th; \feat{Craft Wondrous Item}, \spell{silence}; Price 250 cp.



\textbf{Elixir of Swimming:} This elixir bestows swimming ability. An almost imperceptible magic sheath surrounds the drinker, allowing him to glide through the water easily (+10 competence bonus on \skill{Swim} checks for 1 hour).

Faint illusion; CL 2nd; \feat{Craft Wondrous Item}, creator must have 5 ranks in the \skill{Swim} skill; Price 250 cp.



\textbf{Elixir of Truth:} This elixir forces the individual drinking it to say nothing but the truth for 10 minutes (Will DC 13 negates).

She is compelled to answer any questions put to her in that time, but with each question she is free to make a separate DC 13 Will save. If one of these secondary saves is successful, she doesn't break free of the truth-compelling enchantment but also doesn't have to answer that particular question. No more than one question can be asked each round. This is a mind-affecting compulsion enchantment.

Faint enchantment; CL 5th; \feat{Craft Wondrous Item}, \spell{zone of truth}; Price 500 cp.



\textbf{Elixir of Vision:} Drinking this elixir grants the imbiber the ability to notice acute details with great accuracy (+10 competence bonus on \skill{Search} checks for 1 hour).

Faint divination; CL 2nd; \feat{Craft Wondrous Item}, \spell{true seeing}; Price 250 cp.



\textbf{Eversmoking Bottle:} This metal urn is identical in appearance to an \emph{efreeti bottle}, except that it does nothing but smoke. The amount of smoke is great if the stopper is pulled out, pouring from the bottle and totally obscuring vision across a 15-meter spread in 1 round. If the bottle is left unstoppered, the smoke billows out another 3 meters per round until it has covered a 30-meter radius. This area remains smoke-filled until the \emph{eversmoking bottle} is stoppered.

The bottle must be resealed by a command word, after which the smoke dissipates normally. A moderate wind (16+ km/h) disperses the smoke in 4 rounds; a strong wind (36+ km/h) disperses the smoke in 1 round.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{pyrotechnics}; Price 5,400 cp; Weight 0.5 kg.



\textbf{Figurines of Wondrous Power:} Each of the several kinds of figurines of wondrous power appears to be a miniature statuette of a creature an inch or so high (with one exception). When the figurine is tossed down and the correct command word spoken, it becomes a living creature of normal size (except when noted otherwise below). The creature obeys and serves its owner. Unless stated otherwise, the creature understands Common but does not speak.

If a figurine of wondrous power is broken or destroyed in its statuette form, it is forever ruined. All magic is lost, its power departed. If slain in animal form, the figurine simply reverts to a statuette that can be used again at a later time.

\textit{Bronze Griffon:} When animated, a bronze griffon acts in all ways like a normal griffon under the command of its possessor. The item can be used twice per week for up to 6 hours per use. When 6 hours have passed or when the command word is spoken, the bronze griffon once again becomes a tiny statuette.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 10,000 cp.

\textit{Ebony Fly:} When animated, an ebony fly is the size of a pony and has all the statistics of a hippogriff but can make no attacks. The item can be used three times per week for up to 12 hours per use. When 12 hours have passed or when the command word is spoken, the ebony fly again becomes a tiny statuette.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 10,000 cp.

\textit{Golden Lions:} These figurines come in pairs. They become normal adult male lions. If slain in combat, the lions cannot be brought back from statuette form for one full week. Otherwise, they can be used once per day for up to 1 hour. They enlarge and shrink upon speaking the command word.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 16,500 cp.

\textit{Ivory Goats:} These figurines come in threes. Each goat of this trio looks slightly different from the others, and each has a different function:

\begin{itemize*}
\item \emph{The Goat of Traveling:} This statuette provides a speedy and enduring mount equal to that of a heavy horse in every way except appearance. The goat can travel for a maximum of one day each week---continuously or in any combination of periods totaling 24 hours. At this point, or when the command word is uttered, it returns to its statuette form for not less than one day before it can again be used.
\item \emph{The Goat of Travail:} This statuette becomes an enormous creature, larger than a bull, with the statistics of a nightmare except for the addition of a pair of wicked horns of exceptional size (damage 1d8+4 for each horn). If it is charging to attack, it may only use its horns (but add 6 points of damage to each successful attack in that round). It can be called to life just once per month for up to 12 hours at a time.
\item \emph{The Goat of Terror:} When called upon with the proper command word, this statuette becomes a destrier-like mount, with the statistics of a light warhorse. However, its rider can employ the goat's horns as weapons (one horn as a +3 lance, the other as a +5 longsword). When ridden in an attack against an opponent, the goat of terror radiates fear as the spell in a 9-meter radius (Will DC 16 partial). It can be used once every two weeks for up to 3 hours per use.
\end{itemize*}

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 21,000 cp.

\textit{Marble Elephant:} This is the largest of the figurines, the statuette being about the size of a human hand. Upon utterance of the command word, a marble elephant grows to the size and specifications of a true elephant. The animal created from the statuette is fully obedient to the figurine's owner, serving as a beast of burden, a mount, or a combatant. The statuette can be used four times per month for up to 24 hours at a time.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 17,000 cp.

\textit{Obsidian Steed:} This figurine appears to be a small, shapeless lump of black stone. Only careful inspection reveals that it vaguely resembles some form of quadruped. On command, the near-formless piece of obsidian becomes a fantastic mount. Treat it as a heavy warhorse with the following additional powers usable once per round at will: \spell{overland flight}, \spell{plane shift}, and \spell{ethereal jaunt}. The steed allows itself to be ridden, but if the rider is of good alignment, the steed is 10\% likely per use to carry him to the lower planes and then return to its statuette form. The statuette can be used once per week for one continuous period of up to 24 hours. Note that when an \emph{obsidian steed} becomes ethereal or \spellref{plane shift}{plane shifts}, its rider and his gear follow suit.

Thus, the user can travel to other planes via this means.

Strong conjuration and transmutation; CL 15th; \feat{Craft Wondrous Item}, \spell{animate objects}, \spell{etherealness}, \spell{fly}, \spell{plane shift}; Price 28,500 cp.

\textit{Onyx Dog:} When commanded, this statuette changes into a creature with the same properties as a riding dog except that it is endowed with an Intelligence of 8, can communicate in Common, and has exceptional olfactory and visual abilities. (It has the scent ability and adds +4 to its \skill{Spot} and \skill{Search} checks.) It has 18-meter darkvision, and it can see invisibility. An \emph{onyx dog} can be used once per week for up to 6 hours. It obeys only its owner.

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 15,500 cp.

\textit{Serpentine Owl:} This figurine becomes either a normal-sized horned owl or a giant owl according to the command word used. The transformation can take place once per day, with a maximum duration of 8 continuous hours. However, after three transformations into giant owl form, the statuette loses all its magical properties. The owl communicates with its owner by telepathic means, informing her of all it sees and hears. (Remember the limitations of its Intelligence.)

Moderate transmutation; CL 11th; \feat{Craft Wondrous Item}, \spell{animate objects}; Price 9,100 cp.

\textit{Silver Raven:} This silver figurine turns into a raven on command (but it retains its metallic consistency, which gives it hardness 10). Another command sends it off into the air, bearing a message just like a creature affected by an \spell{animal messenger} spell. If not commanded to carry a message, the raven obeys the commands of its owner, although it has no special powers or telepathic abilities. It can maintain its nonfigurine status for only 24 hours per week, but the duration need not be continuous.

Faint enchantment and transmutation; CL 6th; \feat{Craft Wondrous Item}, \spell{animal messenger}, \spell{animate objects}; Price 3,800 cp.



\textbf{Feather Token:} Each of these items is a small feather that has a power to suit a special need. The kinds of tokens are described below. Each token is usable once.

\begin{itemize*}
\item \textit{Anchor:} A token useful to moor a craft in water so as to render it immobile for up to one day.
\item \textit{Bird:} A token that can be used to deliver a small written message unerringly to a designated target as would a carrier pigeon. The token lasts as long as it takes to carry the message.
\item \textit{Fan:} A token that forms a huge flapping fan, causing a breeze of sufficient strength to propel one ship (about 25 mph). This wind is not cumulative with existing wind speed. The token can, however, be used to lessen existing winds, creating an area of relative calm or lighter winds (but wave size in a storm is not affected). The fan can be used for up to 8 hours. It does not function on land.
\item \textit{Swan Boat:} A token that forms a swanlike boat capable of moving on water at a speed of 18 meters. It can carry eight horses and gear or thirty-two Medium characters or any equivalent combination. The boat lasts for one day.
\item \textit{Tree:} A token that causes a great oak to spring into being (5-foot diameter trunk, 18-meter height, 12-meter top diameter). This is an instantaneous effect.
\item \textit{Whip:} A token that forms into a huge leather whip and wields itself against any opponent desired just like a dancing weapon. The weapon has a +10 base attack bonus, does 1d6+1 points of damage, has a +1 enhancement bonus on attack and damage rolls, and a makes a free grapple attack (with a +15 attack bonus) if it hits. The whip lasts no longer than 1 hour.
\end{itemize*}

Moderate conjuration; CL 12th; \feat{Craft Wondrous Item}, \spell{major creation}; Price 50 cp (anchor), 300 cp (bird), 200 cp (fan), 450 cp (swan boat), 400 cp (tree), 500 cp (whip).



\textbf{Gem of Brightness:} This crystal appears to be a long, rough prism. Upon utterance of a command word, the crystal emits bright light of one of three sorts.

\begin{itemize*}
\item One command word causes the gem to shed light as a hooded lantern. This use of the gem does not expend any charges.
\item Another command word causes the gem of brightness to send out a bright ray 30 centimeters in diameter and 15 meters long. This strikes as a ranged touch attack, and any creature struck by this beam is blinded for 1d4 rounds unless it makes a DC 14 Fortitude save. This use of the gem expends 1 charge.
\item The third command word causes the gem to flare in a blinding flash of light that fills a 9-meter cone. Although this glare lasts but a moment, any creature within the cone must make a DC 14 Fortitude save or be blinded for 1d4 rounds. This use expends 5 charges.
\end{itemize*}

A newly created gem of brightness has 50 charges. When all its charges are expended, the gem becomes nonmagical.

Faint evocation; CL 6th; \feat{Craft Wondrous Item}, \spell{daylight}; Price 13,000 cp.



\textbf{Gem of Seeing:} This finely cut and polished stone is indistinguishable from an ordinary jewel in appearance. When it is gazed through, a gem of seeing enables the user to see as though she were affected by the \spell{true seeing} spell. A gem of seeing can be used for as much as 30 minutes a day, divided up into periods of minutes or rounds as the user sees fit.

Moderate divination; CL 10th; \feat{Craft Wondrous Item}, \spell{true seeing}; Price 75,000 cp.



% \textbf{Golem Manual:} A \emph{golem manual} contains information, incantations and magical power that help a character to craft a golem. The instructions therein grant a +5 competence bonus on skill checks made to craft the golem's body. Each manual also holds the prerequisite spells needed for a specific golem, effectively grants the builder use of the \feat{Craft Construct} feat during the construction of the golem, and grants the character an increase to her caster level for the purpose of crafting a golem. Any golem built using a \emph{golem manual} does not cost the creator any XP, since the requisite XP are ``contained'' in the book and ``expended'' by the book during the creation process.

% The spells included in a \emph{golem manual} require a spell trigger activation and can be activated only to assist in the construction of a golem. The cost of the book does not include the cost of constructing the golem's body. Once the golem is finished, the writing in the manual fades and the book is consumed in flames. When the book's ashes are sprinkled upon the golem, it becomes fully animated.

% \textit{Clay Golem Manual:} The book contains \spell{animate objects}, \spell{bless}, \spell{commune}, and \spell{resurrection}. The reader may treat her caster level as two levels higher than normal for the purpose of crafting a clay golem. The book supplies 1,540 XP for the creation of a clay golem.

% Moderate conjuration, divination, enchantment, and transmutation; CL 11th; \feat{Craft Construct}, creator must be caster level 11th, \spell{animate objects}, \spell{commune}, \spell{prayer}, \spell{resurrection}; Price 12,000 cp; Cost 2,150 cp + 1,712 XP; Weight 2.5 kg.

% \textit{Flesh Golem Manual:} The book contains \spell{animate dead}, \spell{bull's strength}, \spell{geas/quest}, and \spell{limited wish}. The reader may treat her caster level as one level higher than normal for the purpose of crafting a flesh golem. The book supplies 780 XP for the creation of a flesh golem.

% Moderate enchantment, necromancy [evil], and transmutation; CL 8th; \feat{Craft Construct}, creator must be caster level 8th, \spell{animate dead}, \spell{bull's strength}, \spell{geas/quest}, \spell{limited wish}; Price 8,000 cp; Cost 2,050 cp + 944 XP; Weight 2.5 kg.

% \textit{Iron Golem Manual:} The book contains \spell{cloudkill}, \spell{geas/quest}, \spell{limited wish}, and \spell{polymorph any object}. The reader may treat her caster level as four levels higher than normal for the purpose of crafting a iron golem. The book supplies 5,600 XP for the creation of a iron golem.

% Strong conjuration, enchantment and transmutation; CL 16th; \feat{Craft Construct}, creator must be caster level 16th, \spell{cloudkill}, \spell{geas/quest}, \spell{limited wish}, \spell{polymorph any object}; Price 35,000 cp; Cost 3,500 cp + 5,880 XP; Weight 2.5 kg.

% \textit{Stone Golem Manual:} The book contains \spell{antimagic field}, \spell{geas/quest}, \spell{slow}, and \spell{symbol of stunning}. The reader may treat her caster level as three levels higher than normal for the purpose of crafting a stone golem. The book supplies 3,400 XP for the creation of a stone golem.

% Strong abjuration and enchantment; CL 14th; \feat{Craft Construct}, creator must be caster level 14th, \spell{antimagic field}, \spell{geas/quest}, \spell{slow}, \spell{symbol of stunning}; Price 22,000 cp; Cost 2,500 cp + 3,600 XP; Weight 2.5 kg.

% \textit{Stone Golem Manual, Greater:} The book contains \spell{antimagic field}, \spell{geas/quest}, \spell{slow}, and \spell{symbol of stunning}. The reader may treat her caster level as three levels higher than normal for the purpose of crafting a greater stone golem. The book supplies 7,640 XP for the creation of a greater stone golem.

% Strong abjuration and enchantment; CL 16th; \feat{Craft Construct}, creator must be caster level 16th, \spell{antimagic field}, \spell{geas/quest}, \spell{slow}, \spell{symbol of stunning}; Price 44,000 cp; Cost 2,900 cp + 7,872 XP; Weight 2.5 kg.



\textbf{Handy Haversack:} A backpack of this sort appears to be well made, well used, and quite ordinary. It is constructed of finely tanned leather, and the straps have brass hardware and buckles. It has two side pouches, each of which appears large enough to hold about a quart of material. In fact, each is like a \emph{bag of holding} and can actually hold material of as much as 2 cubic feet in volume or 10 kilograms in weight. The large central portion of the pack can contain up to 8 cubic feet or 80 pounds of material. Even when so filled, the backpack always weighs only 2.5 kilograms.

While such storage is useful enough, the pack has an even greater power in addition. When the wearer reaches into it for a specific item, that item is always on top. Thus, no digging around and fumbling is ever necessary to find what a haversack contains. Retrieving any specific item from a haversack is a move action, but it does not provoke the attacks of opportunity that retrieving a stored item usually does.

Moderate conjuration; CL 9th; \feat{Craft Wondrous Item}, secret chest; Price 2,000 cp; Weight 2.5 kg.



\textbf{Harp of Charming:} This instrument is a golden, intricately carved harp. When played, it enables the performer to work one \spell{suggestion} (as the spell, Will DC 14 negates) into the music for each 10 minutes of playing if he can succeed on a DC 14 \skill{Perform} (string instruments) check. If the check fails, the audience cannot be affected by any further performances from the harpist for 24 hours.

Faint enchantment; CL 5th; \feat{Craft Wondrous Item}, \spell{suggestion}; Price 7,500 cp; Weight 2.5 kg.



\textbf{Horn of Blasting:} This horn appears to be a normal trumpet. It can be sounded as a normal horn, but if the command word is spoken and the instrument is then played, it deals 5d6 points of sonic damage to creatures within a 12-meter cone and causes them to be deafened for 2d6 rounds (a DC 16 Fortitude save reduces the damage by half and negates the deafening). Crystalline objects and creatures take 7d6 points of sonic damage, with no save unless they're held, worn, or carried by creatures (Will DC 16 negates).

If a \emph{horn of blasting} is used magically more than once in a given day, there is a 20\% cumulative chance with each extra use that it explodes and deals 10d6 points of damage to the person sounding it.

Moderate evocation; CL 7th; \feat{Craft Wondrous Item}, \spell{shout}; Price 20,000 cp; Weight 0.5 kg.



\textbf{Horn of Blasting, Greater:} This horn functions as a \emph{horn of blasting}, except that it deals 10d6 points of sonic damage, stuns creatures for 1 round, and deafens them for 4d6 rounds (a DC 19 Fortitude reduces the damage by half and negates the stunning and deafening). Crystalline objects take 16d6 points of sonic damage as described for the \emph{horn of blasting}. A \emph{greater horn of blasting} also has a 20\% cumulative chance of exploding.

Strong evocation; CL 16th; \feat{Craft Wondrous Item}, \spell{greater shout}; Price 70,000 cp; Weight 0.5 kg.



\textbf{Horn of Fog:} This small bugle allows its possessor to blow forth a thick cloud of heavy fog similar to that of an \spell{obscuring mist} spell. The fog covers a 3-meter square next to the horn blower each round that the user continues to blow the horn; fog clouds travel 3 meters each round in a straight line from the emanation point unless blocked by something substantial such as a wall. The device makes a deep, foghorn-like noise, with the note dropping abruptly to a lower register at the end of each blast. The fog dissipates after 3 minutes. A moderate wind (16+ km/h) disperses the fog in 4 rounds; a strong wind (36+ km/h) disperses the fog in 1 round.

Faint conjuration; CL 3rd; \feat{Craft Wondrous Item}, \spell{obscuring mist}; Price 2,000 cp; Weight 0.5 kg.



\textbf{Horn of Goodness/Evil:} This trumpet adapts itself to its owner, so it produces either a good or an evil effect depending on the owner's alignment. If the owner is neither good nor evil, the horn has no power whatsoever. If he is good, then blowing the horn has the effect of a \spell{magic circle against evil}. If he is evil, then blowing the horn has the effect of a \spell{magic circle against good}. In either case, this ward lasts for 1 hour. The horn can be blown once per day.

Faint abjuration; CL 6th; \feat{Craft Wondrous Item}, \spell{magic circle against good}, \spell{magic circle against evil}; Price 6,500 cp; Weight 0.5 kg.



\textbf{Horn of the Tritons:} This device is a conch shell that can be blown once per day except by a triton which can sound it three times per day. A \emph{horn of the tritons} can perform any one of the following functions when blown.

\begin{itemize*}
\item Calm rough waters in a 1.5-kilometer radius. This effect dispels a summoned water elemental if it fails a DC 16 Will save.
\item Attract 5d4 Large sharks (01--30 on d\%), 5d6 Medium sharks (31--80), or 1d10 sea cats (81--100) if the character is in a body of water in which such creatures dwell. The creatures are friendly and obey, to the best of their ability, the one who sounded the horn.
\item Causes aquatic creatures with Intelligence scores of 1 or 2 within 150 meters to become panicked as if they had been targeted by a \spell{fear} spell (Will DC 16 partial). Those who successfully save are shaken for 3d6 rounds.
\end{itemize*}

Any sounding of a \emph{horn of the tritons} can be heard by all tritons within a 5-kilometer radius.

Moderate conjuration and transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{fear}, \spell{summon monster V}, \spell{control water}, creator must be a triton or get construction aid from a triton; Price 15,100 cp; Weight 1 kg.



\textbf{Horn of Valhalla:} This magic instrument comes in four varieties. Each appears to be normal until someone speaks its command word and blows the horn. Then the horn summons a number of human barbarians to fight for the character who summoned them. Each horn can be blown just once every seven days. Roll d\% and refer to the table below to see what type of horn is found. The horn's type determines what barbarians are summoned and what prerequisite is needed to use the horn. Any character who uses a \emph{horn of Valhalla} but doesn't have the prerequisite is attacked by the barbarians she herself summoned.

\Table{}{cllX} {
  \tableheader d\%
& \tableheader Type of Horn
& \tableheader Barbarians Summoned
& \tableheader Prerequisite\\
01--40  & Silver & 2d4+2, 2nd level & None \\
41--75  & Brass  & 2d4+1, 3rd level & Spellcaster level 1st \\
76--90  & Bronze & 2d4, 4th level   & Proficiency with all martial weapons or bardic music ability \\
91--100 & Iron   & 1d4+1, 5th level & Proficiency with all martial weapons or bardic music ability \\
}

Summoned barbarians are constructs, not actual people (though they seem to be); they arrive with the starting equipment for barbarians. They attack anyone the possessor of the horn commands them to fight until they or their opponents are slain or until 1 hour has elapsed, whichever comes first.

Strong conjuration; CL 13th; \feat{Craft Wondrous Item}, \spell{summon monster VI}; Price 50,000 cp; Weight 1 kg.



\textbf{Incense of Meditation:} This small rectangular block of sweet smelling incense is visually indistinguishable from nonmagical incense until lit. When it is burning, the special fragrance and pearly-hued smoke of this special incense are recognizable by anyone making a DC 15 \skill{Spellcraft} check.

When a divine spellcaster lights a block of incense of meditation and then spends 8 hours praying and meditating nearby, the incense enables him to prepare all his spells as though affected by the \feat{Maximize Spell} feat. However, all the spells prepared in this way are at their normal level, not at three levels higher (as with the regular metamagic feat).

Each block of incense burns for 8 hours, and the effects persist for 24 hours.

Moderate enchantment; CL 7th; \feat{Craft Wondrous Item}, \feat{Maximize Spell}, \spell{bless}; Price 4,900 cp; Weight 0.5 kg.



\textbf{Instant Fortress:} This metal cube is small, but when activated by speaking a command word it grows to form a tower 6 meters square and 9 meters high, with arrow slits on all sides and a crenellated battlement atop it. The metal walls extend 3 meters into the ground, rooting it to the spot and preventing it from being tipped over. The fortress has a small door that opens only at the command of the owner of the fortress---even knock spells can't open the door.

The adamantine walls of instant fortress have 100 hit points and hardness 20. The fortress cannot be repaired except by a wish or a miracle, which restores 50 points of damage taken.

The fortress springs up in just 1 round, with the door facing the device's owner. The door opens and closes instantly at his command. People and creatures nearby (except the owner) must be careful not to be caught by the fortress's sudden growth. Anyone so caught takes 10d10 points of damage (Reflex DC 19 half).

The fortress is deactivated by speaking a command word (different from the one used to activate it). It cannot be deactivated unless it is empty.

Strong conjuration; CL 13th; \feat{Craft Wondrous Item}, \spell{mage's magnificent mansion}; Price 55,000 cp.


\BigTableBottom{Ioun Stones}{llXr{15mm}}{
  \tableheader Color
& \tableheader Shape
& \tableheader Effect
& \tableheader Market Price\\
Clear              & Spindle   & Sustains creature without food or water                                      & 4,000 cp \\
Dusty rose         & Prism     & +1 insight bonus to AC                                                       & 5,000 cp \\
Deep red           & Sphere    & +2 enhancement bonus to Dexterity                                            & 8,000 cp \\
Incandescent blue  & Sphere    & +2 enhancement bonus to Wisdom                                               & 8,000 cp \\
Pale blue          & Rhomboid  & +2 enhancement bonus to Strength                                             & 8,000 cp \\
Pink               & Rhomboid  & +2 enhancement bonus to Constitution                                         & 8,000 cp \\
Pink and green     & Sphere    & +2 enhancement bonus to Charisma                                             & 8,000 cp \\
Scarlet and blue   & Sphere    & +2 enhancement bonus to Intelligence                                         & 8,000 cp \\
Dark blue          & Rhomboid  & Alertness (as the feat)                                                      & 10,000 cp \\
Vibrant purple     & Prism     & Stores three levels of spells, as a ring of spell storing, minor             & 36,000 cp \\
Iridescent         & Spindle   & Sustains creature without air                                                & 18,000 cp \\
Pale lavender      & Ellipsoid & Absorbs spells of 4th level or lower\footnotemark[1]                         & 20,000 cp \\
Pearly white       & Spindle   & Regenerate 1 point of damage per hour                                        & 20,000 cp \\
Pale green         & Prism     & +1 competence bonus on attack rolls, saves, skill checks, and ability checks & 30,000 cp \\
Orange             & Prism     & +1 caster level                                                              & 30,000 cp \\
Lavender and green & Ellipsoid & Absorbs spells of 8th level or lower\footnotemark[2]                         & 40,000 cp \\
\BigTableNote{4}{1 After absorbing twenty spell levels, the stone burns out and turns to dull gray, forever useless.}\\
\BigTableNote{4}{2 After absorbing fifty spell levels, the stone burns out and turns dull gray, forever useless.}\\
}


\textbf{Ioun Stones:} These crystalline stones always float in the air and must be within 1 meter of their owner to be of any use. When a character first acquires a stone, she must hold it and then release it, whereupon it takes up a circling orbit 1d10$\times$ 10 centimeters from her head. Thereafter, a stone must be grasped or netted to separate it from its owner. The owner may voluntarily seize and stow a stone (to keep it safe while she is sleeping, for example), but she loses the benefits of the stone during that time. \emph{Ioun stones} have AC 24, 10 hit points, and hardness 5.

Regeneration from the \emph{pearly white ioun stone} works like a \emph{ring of regeneration}. (It only cures damage taken while the character is using the stone.) The pale lavender and lavender and green stones work like a \emph{rod of absorption}, but absorbing a spell requires a readied action, and these stones cannot be used to empower spells. Stored spells in the \emph{vibrant purple stone} must be placed by a spellcaster but can be used by anyone (see \emph{ring of minor spell storing}).

Moderate varied; CL 12th; \feat{Craft Wondrous Item}, creator must be 12th level.



\textbf{Iron Bands of Binding:} When initially discovered, this very potent item appears to be a 7-centimeter-diameter rusty iron sphere with bandings on the globe.

When the proper command word is spoken and the spherical iron device is hurled at an opponent, the bands expand and then contract to bind the target creature on a successful ranged touch attack. A single Large or smaller creature can be captured thus and held immobile until the command word is spoken to bring the bands into spherical form again. The creature can break (and ruin) the bands with a DC 30 Strength check or escape them with a DC 30 \skill{Escape Artist} check. Iron bands of binding are usable once per day.

Strong evocation; CL 13th; \feat{Craft Wondrous Item}, \spell{grasping hand}; Price 26,000 cp; Weight 0.5 kg.



\textbf{Iron Flask:} These special containers are typically inlaid with runes of silver and stoppered by a brass plug bearing a seal engraved with sigils, glyphs, and special symbols. When the user speaks the command word, he can force any creature from another plane into the container, provided that creature fails a DC 19 Will save. The range of this effect is 18 meters. Only one creature at a time can be so contained. Loosing the stopper frees the captured creature.

The command word can be given only once per day.

If the individual freeing the captured creature speaks the command word, the creature can be forced to serve for 1 hour. If freed without the command word, the creature acts according to its natural inclinations. (It usually attacks the user, unless it perceives a good reason not to.) Any attempt to force the same creature into the flask a second time provides it a +2 bonus on its saving throw and makes it hostile. A newly discovered bottle might contain any of the following:

\Table{}{cXcX}{
  \tableheader d\%
& \tableheader Contents
& \tableheader d\%
& \tableheader Contents\\
01--50 & Empty                 & 89  & Glabrezu (demon) \\
51--54 & Large air elemental   & 90  & Succubus (demon) \\
55--58 & Arrowhawk             & 91  & Osyluth (devil) \\
59--62 & Large earth elemental & 92  & Barbazu (devil) \\
63--66 & Xorn                  & 93  & Erinyes (devil) \\
67--70 & Large fire elemental  & 94  & Cornugon (devil) \\
71--74 & Salamander            & 95  & Avoral (celestial) \\
75--78 & Large water elemental & 96  & Ghaele (celestial) \\
79--82 & Adult tojanida        & 97  & Formian myrmarch \\
83--84 & Chaos Beast           & 98  & Arrowhawk, elder \\
85--86 & Formian taskmaster    & 99  & Rakshasa \\
87     & Vrock (demon)         & 100 & Balor (demon) or pit fiend (devil)---equal chance for either \\
88     & Hezrou (demon)		   &     & \\
}

Strong conjuration; CL 20th; \feat{Craft Wondrous Item}, \spell{trap the soul}; Price 170,000 cp (empty); Weight 0.5 kg.



\textbf{Lantern of Revealing:} This lantern operates as a normal hooded lantern. While it is lit, it also reveals all invisible creatures and objects within 7.5 meters of it, just like the spell \spell{invisibility purge}.

Faint evocation; CL 5th; \feat{Craft Wondrous Item}, \spell{invisibility purge}; Price 30,000 cp; Weight 1 kg.



\textbf{Lens of Detection:} This circular prism enables its user to detect minute details, granting a +5 bonus on \skill{Search} checks.

It also aids in following tracks, adding a +5 bonus on \skill{Survival} checks when tracking. The lens is about 15 centimeters in diameter and set in a frame with a handle.

Moderate divination; CL 9th; \feat{Craft Wondrous Item}, \spell{true seeing}; Price 3,500 cp; Weight 0.5 kg.



\textbf{Lyre of Building:} If the proper chords are struck, a single use of this lyre negates any attacks made against all inanimate construction (walls, roof, floor, and so on) within 90 meters. This includes the effects of a \emph{horn of blasting}, a \spell{disintegrate} spell, or an attack from a ram or similar siege weapon. The lyre can be used in this way once per day, with the protection lasting for 30 minutes.

The lyre is also useful with respect to building. Once a week its strings can be strummed so as to produce chords that magically construct buildings, mines, tunnels, ditches, or whatever. The effect produced in but 30 minutes of playing is equal to the work of 100 humans laboring for three days. Each hour after the first, a character playing the lyre must make a DC 18 \skill{Perform} (string instruments) check. If it fails, she must stop and cannot play the lyre again for this purpose until a week has passed.

Faint transmutation; CL 6th; \feat{Craft Wondrous Item}, \spell{fabricate}; Price 13,000 cp; Weight 2.5 kg.



% \textbf{Manual of Bodily Health:} This thick tome contains tips on health and fitness, but entwined within the words is a powerful magical effect. If anyone reads this book, which takes a total of 48 hours over a minimum of six days, he gains an inherent bonus of from +1 to +5 (depending on the type of manual) to his Constitution score. Once the book is read, the magic disappears from the pages and it becomes a normal book.

% Strong evocation (if \spell{miracle} is used); CL 17th; \feat{Craft Wondrous Item}, \spell{wish} or \spell{miracle}; Price 27,500 cp (+1), 55,000 cp (+2), 82,500 cp (+3), 110,000 cp (+4), 137,500 cp (+5); Cost 1,250 cp + 5,100 XP (+1), 2,500 cp + 10,200 XP (+2), 3,750 cp + 15,300 XP (+3), 5,000 cp + 20,400 XP (+4), 6,250 cp + 25,500 XP (+5); Weight 2.5 kg.



% \textbf{Manual of Gainful Exercise:} This thick tome contains exercise descriptions and diet suggestions, but entwined within the words is a powerful magical effect. If anyone reads this book, which takes a total of 48 hours over a minimum of six days, she gains an inherent bonus of from +1 to +5 (depending on the type of manual) to her Strength score. Once the book is read, the magic disappears from the pages and it becomes a normal book.

% Strong evocation (if \spell{miracle} is used); CL 17th; \feat{Craft Wondrous Item}, \spell{wish} or \spell{miracle}; Price 27,500 cp (+1), 55,000 cp (+2), 82,500 cp (+3), 110,000 cp (+4), 137,500 cp (+5); Cost 1,250 cp + 5,100 XP (+1), 2,500 cp + 10,200 XP (+2), 3,750 cp + 15,300 XP (+3), 5,000 cp + 20,400 XP (+4), 6,250 cp + 25,500 XP (+5); Weight 2.5 kg.



% \textbf{Manual of Quickness of Action:} This thick tome contains tips on coordination exercises and balance, but entwined within the words is a powerful magical effect. If anyone reads this book, which takes a total of 48 hours over a minimum of six days, he gains an inherent bonus of from +1 to +5 (depending on the type of manual) to his Dexterity score. Once the book is read, the magic disappears from the pages and it becomes a normal book.

% Strong evocation (if \spell{miracle} is used); CL 17th; \feat{Craft Wondrous Item}, \spell{wish} or \spell{miracle}; Price 27,500 cp (+1), 55,000 cp (+2), 82,500 cp (+3), 110,000 cp (+4), 137,500 cp (+5); Cost 1,250 cp + 5,100 XP (+1), 2,500 cp + 10,200 XP (+2), 3,750 cp + 15,300 XP (+3), 5,000 cp + 20,400 XP (+4), 6,250 cp + 25,500 XP (+5); Weight 2.5 kg.



\textbf{Marvelous Pigments:} These magic emulsions enable their possessor to create actual, permanent objects simply by depicting their form in two dimensions. The pigments are applied by a stick tipped with bristles, hair, or fur. The emulsion flows from the application to form the desired object as the artist concentrates on the desired image. One pot of \emph{marvelous pigments} is sufficient to create a 28,000-liter object by depicting it two-dimensionally over a 9-square-meters surface.

Only normal, inanimate objects can be created. Creatures can't be created. The pigments must be applied to a surface. It takes 10 minutes and a DC 15 \skill{Craft} (painting) check to depict an object with the pigments. \emph{Marvelous pigments} cannot create magic items. Objects of value depicted by the pigments ---precious metals, gems, jewelry, ivory, and so on--- appear to be valuable but are really made of tin, lead, paste, brass, bone, and other such inexpensive materials. The user can create normal weapons, armor, and any other mundane item (including foodstuffs) whose value does not exceed 2,000 cp.

Items created are not magical; the effect is instantaneous.

Strong conjuration; CL 15th; \feat{Craft Wondrous Item}, \spell{major creation}; Price 4,000 cp.



\textbf{Mattock of the Titans:} This digging tool is 3 meters long. Any creature of at least Huge size can use it to loosen or tumble earth or earthen ramparts (a 3-meter cube every 10 minutes). It also smashes rock (a 3-meter cube per hour). If used as a weapon, it is the equivalent of a Gargantuan \emph{+3 adamantine warhammer}, dealing 4d6 points of base damage.

Strong transmutation; CL 16th; \feat{Craft Wondrous Item}, \feat{Craft Magic Arms and Armor}, \spell{move earth}; Price 23,348 cp; Cost 13,348 cp + 800 XP; Weight 60 kg.



\textbf{Maul of the Titans:} This mallet is 25 centimeters long. If used as a weapon, it is the equivalent of a \emph{+3 greatclub} and deals triple damage against inanimate objects. However, the wielder must have a Strength of at least 18 to wield it properly. Otherwise, she takes a $-4$ penalty on attack rolls.

Strong evocation; CL 15th; \feat{Craft Wondrous Item}, \feat{Craft Magic Arms and Armor}, \spell{clenched fist}; Price 25,305 cp; Cost 12,305 cp + 480 XP; Weight 80 kg.



\textbf{Mirror of Life Trapping:} This crystal device is usually about 1.2 meter square and framed in metal or wood. It can be hung or placed on a surface and then activated by giving a command word. The same command word deactivates the mirror. A \emph{mirror of life trapping} has fifteen nonspatial extradimensional compartments within it. Any creature coming within 9 meters of the device and looking at its own reflection must make a DC 23 Will save or be trapped within the mirror in one of the cells. A creature not aware of the nature of the device always sees its own reflection. The probability of a creature seeing its reflection, and thus needing to make the saving throw, drops to 50\% if the creature is aware that the mirror traps life and seeks to avoid looking at it (treat as a gaze attack).

When a creature is trapped, it is taken bodily into the mirror. Size is not a factor, but constructs and undead are not trapped, nor are inanimate objects and other nonliving matter. A victim's equipment (including clothing and anything being carried) remains behind. If the mirror's owner knows the right command word, he can call the reflection of any creature trapped within to its surface and engage his powerless prisoner in conversation. Another command word frees the trapped creature. Each pair of command words is specific to each prisoner.

If the mirror's capacity is exceeded, one victim (determined randomly) is set free in order to accommodate the latest one. If the mirror is broken, all victims currently trapped in it are freed.

Strong abjuration; CL 17th; \feat{Craft Wondrous Item}, \spell{imprisonment}; Price 200,000 cp; Weight 25 kg.



\textbf{Mirror of Mental Prowess:} This mirror resembles an ordinary looking glass 1.5 meter tall by 60 centimeters wide. The possessor who knows the proper commands can cause it to perform as follows.

\begin{itemize*}
\item Read the thoughts of any creature reflected therein, as long as the owner is within 7.5 meters of the mirror, even if those thoughts are in an unknown language.
\item View other places as if with \spellref{clairaudience/clairvoyance}{clairvoyance}, but vision extends even onto other planes if the viewer is sufficiently familiar with them.
\item Use it as a portal to visit other places. The user first views the place with the \spellref{clairaudience/clairvoyance}{clairvoyance} function, then steps through the mirror to the place pictured. Others can follow her through the mirror if they like. An invisible portal remains on the other side where she arrives, and she can return through that portal. Once she returns, the portal closes. The portal closes on its own after 24 hours (trapping the user if she's still in the other place), and the user can also close it with a command word. Creatures with Intelligence of 12 or higher might notice the portal just as they might notice a magical sensor from a \spell{scrying} spell. Any creature who steps through the portal appears in front of the mirror.
\item Once per week the mirror accurately answers one short question regarding a creature whose image is shown on its surface (giving answers similar to those from the \spell{legend lore} spell).
\end{itemize*}


Strong conjuration and divination; CL 17th; \feat{Craft Wondrous Item}, \spell{detect thoughts}, \spell{clairaudience/clairvoyance}, \spell{gate}, \spell{legend lore}; Price 175,000 cp; Weight 20 kg.



\textbf{Mirror of Opposition:} This item resembles a normal mirror about 1.2 meter long and 1 meter wide. It can be hung or placed on a surface and then activated by speaking a command word. The same command word deactivates the mirror. If a creature sees its reflection in the mirror's surface, an exact duplicate of that creature comes into being. This opposite immediately attacks the original. The duplicate has all the possessions and powers of its original (including magic). Upon the defeat or destruction of either the duplicate or the original, the duplicate and her items disappear completely. The mirror functions up to four times per day.

Strong necromancy; CL 15th; \feat{Craft Wondrous Item}, clone; Price 92,000 cp; Weight 22.5 kg.



\textbf{Orb of Storms:} This glass sphere is 8 inches in diameter. The possessor can call forth all manner of weather, even supernaturally destructive storms. Once per day she can call upon the orb to use a \spell{control weather} spell, Once per month, she can conjure a \spell{storm of vengeance}. The possessor of the orb is continually protected by an \spell{endure elements} effect.

Strong varied; CL 18th; \feat{Craft Wondrous Item}, \spell{control weather}, \spell{endure elements}, \spell{storm of vengeance}; Price 48,000 cp; Weight 3 kg.



\textbf{Pearl of Power:} This seemingly normal pearl of average size and luster is a potent aid to all spellcasters who prepare spells (clerics, druids, rangers, and wizards). Once per day on command, a \emph{pearl of power} enables the possessor to recall any one spell that she had prepared and then cast. The spell is then prepared again, just as if it had not been cast. The spell must be of a particular level, depending on the pearl. Different pearls exist for recalling one spell per day of each level from 1st through 9th and for the recall of two spells per day (each of a different level, 6th or lower).

Strong transmutation; CL 17th; \feat{Craft Wondrous Item}, creator must be able to cast spells of the spell level to be recalled; Price 1,000 cp (1st), 4,000 cp (2nd), 9,000 cp (3rd), 16,000 cp (4th), 25,000 cp (5th), 36,000 cp (6th), 49,000 cp (7th), 64,000 cp (8th), 81,000 cp (9th), or 70,000 cp (two spells).



\textbf{Pearl of the Sirines:} This normal-seeming pearl is beautiful and worth at least 1,000 cp on that basis alone. If it is clasped firmly in hand or held to the breast while the possessor attempts actions related to the pearl's powers, she understands and is able to employ the item.

The pearl enables its possessor to breathe in water as if she were in clean, fresh air. Her swim speed is 18 meters, and she can cast spells and act underwater without hindrance.

Moderate abjuration and transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{freedom of movement}, \spell{water breathing}; Price 15,300 cp.



\textbf{Pipes of Haunting:} This magic item appears to be a small set of pan pipes. When played by a person who succeeds on a DC 15 \skill{Perform} (wind instruments) check, the pipes create an eerie, spellbinding tune. Those within 9 meters who hear the tune must succeed on a DC 13 Will save or become frightened for 4 rounds. Creatures with 6 or more Hit Dice are unaffected. \emph{Pipes of haunting} can be sounded twice a day.

Faint necromancy; CL 4th; \feat{Craft Wondrous Item}, \spell{scare}; Price 6,000 cp; Weight 1.5 kg.



\textbf{Pipes of Pain:} These appear to be like any other standard set of pipes with nothing to reveal their true nature. When played by someone who succeeds on a DC 15 \skill{Perform} (wind instruments) check, the pipes create a wondrous melody. All within 9 meters must make a DC 14 Will save or be fascinated by the sound. (This is a mind-affecting sonic compulsion.)

As soon as the piping stops, all those affected are stricken by intense pain at even the slightest noise. Unless a character is in a totally silent area, she takes 1d4 points of damage per round for 2d4 rounds. During this time, damage from sonic attacks is doubled. Thereafter, the least noise causes an affected character to become shaken (except when she is in a totally silent area). This hypersensitivity is a curse and therefore hard to remove (see the \spell{bestow curse} spell).

Faint enchantment and evocation; CL 6th; \feat{Craft Wondrous Item}, creator must have the bardic music class feature, \spell{sound burst}; Price 12,000 cp; Weight 1.5 kg.



\textbf{Pipes of the Sewers:} These wooden pipes appear ordinary, but if the possessor learns the proper tune, he can attract 1d3 rat swarms if rats are within 120 meters. For each 15-meter distance the rats have to travel, there is a 1-round delay. The piper must continue playing until the rats appear, and when they do so, the piper must make a DC 10 Perform (wind instruments) check. Success means that they obey the piper's telepathic commands so long as he continues to play. Failure indicates that they turn on the piper. If for any reason the piper ceases playing, the rats leave immediately. If they are called again within a day, the \skill{Perform} check DC is 15.

If the rats are under the control of another creature, add the HD of the controller to the \skill{Perform} check DC. Once control is assumed, another check is required each round to maintain it if the other creature is actively seeking to reassert its control.

Faint conjuration; CL 2nd; \feat{Craft Wondrous Item}, \spell{charm animal}, \spell{summon nature's ally I}, wild empathy ability; Price 1,150 cp; Weight 1.5 kg.



\textbf{Pipes of Sounding:} When played by a character who has the \spell{Perform} (wind instruments) skill, these pipes create a variety of sounds. The figment sounds are the equivalent of \spell{ghost sound} (caster level 2nd).

Faint illusion; CL 2nd; \feat{Craft Wondrous Item}, \spell{ghost sound}; Price 1,800 cp; Weight 1.5 kg.



\textbf{Portable Hole:} A \emph{portable hole} is a circle of cloth spun from the webs of a phase spider interwoven with strands of ether and beams of starlight. When opened fully, a \emph{portable hole} is 6 feet in diameter, but it can be folded up to be as small as a pocket handkerchief. When spread upon any surface, it causes an extradimensional space 3 meters deep to come into being. This hole can be picked up from inside or out by simply taking hold of the edges of the cloth and folding it up. Either way, the entrance disappears, but anything inside the hole remains.

The only air in the hole is that which enters when the hole is opened. It contains enough air to supply one Medium creature or two Small creatures for 10 minutes. The cloth does not accumulate weight even if its hole is filled. Each \emph{portable hole} opens on its own particular nondimensional space. If a \emph{bag of holding} is placed within a \emph{portable hole}, a rift to the Astral Plane is torn in that place. Both the bag and the cloth are sucked into the void and forever lost. If a \emph{portable hole} is placed within a \emph{bag of holding}, it opens a gate to the Astral Plane. The hole, the bag, and any creatures within a 3-meter radius are drawn there, the portable hole and \emph{bag of holding} being destroyed in the process.

Moderate conjuration; CL 12th; \feat{Craft Wondrous Item}, plane shift; Price 20,000 cp.



\textbf{Restorative Ointment:} A jar of this unguent is 7 centimeters in diameter and 2 centimeters deep and contains five applications. Placed upon a poisoned wound or swallowed, the ointment detoxifies any poison (as \spell{neutralize poison}). Applied to a diseased area, it removes disease (as \spell{remove disease}). Rubbed on a wound, the ointment cures 1d8+5 points of damage (as \spell{cure light wounds}).

Faint conjuration; CL 5th;\feat{Craft Wondrous Item}, \spell{cure light wounds}, \spell{neutralize poison}, \spell{remove disease}; Price 4,000 cp; Weight 0.25 kg.



\textbf{Ring Gates:} These always come in pairs---two iron rings, each about 45 centimeters in diameter. The rings must be on the same plane of existence and within 150 kilometers of each other to function. Whatever is put through one ring comes out the other, and up to 50 kilograms of material can be transferred each day. (Objects only partially pushed through and then retracted do not count.) This useful device allows for instantaneous transport of items or messages, and even attacks. A character can reach through to grab things near the other ring, or even stab a weapon through if so desired. Alternatively, a character could stick his head through to look around. A spellcaster could even cast a spell through a \emph{ring gate}. A Small character can make a DC 13 \skill{Escape Artist} check to slip through. Creatures of Tiny, Diminutive, or Fine size can pass through easily. Each ring has a ``entry side'' and an ``exit side,'' both marked with appropriate symbols.

Strong conjuration; CL 17th; \feat{Craft Wondrous Item}, \spell{gate}; Price 40,000 cp; Weight 0.5 kg each.



\textbf{Rope of Climbing:} A 18-meter-long \emph{rope of climbing} is no thicker than a wand, but it is strong enough to support 1,500 kilograms. Upon command, the rope snakes forward, upward, downward, or in any other direction at 3 meters per round, attaching itself securely wherever its owner desires. It can unfasten itself and return in the same manner.

A \emph{rope of climbing} can be commanded to knot or unknot itself. This causes large knots to appear at 30-cm intervals along the rope. Knotting shortens the rope to a 15-meter length until the knots are untied but lowers the DC of \skill{Climb} checks while using it by 10. A creature must hold one end of the rope when its magic is invoked.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}, \spell{animate rope}; Price 3,000 cp; Weight 1.5 kg.



\textbf{Rope of Entanglement:} A \emph{rope of entanglement} looks just like any other hempen rope about 9 meters long. Upon command, the rope lashes forward 6 meters or upward 3 meters to entangle a victim. An entangled creature can break free with a DC 20 Strength check or a DC 20 \skill{Escape Artist} check.

The rope has AC 22, 12 hit points, and hardness 10, and it has damage reduction 5/slashing as well. The rope repairs damage to itself at a rate of 1 point per 5 minutes, but if a \emph{rope of entanglement} is severed (all 12 hit points lost to damage), it is destroyed.

Moderate transmutation; CL 12th; \feat{Craft Wondrous Item}, \emph{animate objects}, \spell{animate rope}, entangle; Price 21,000 cp; Weight 2.5 kg.



\textbf{Salve of Slipperiness:} This substance provides a +20 competence bonus on all \skill{Escape Artist} checks, meaning that it is almost impossible to grapple such a character or to tie or chain him up. In addition, such obstructions as webs (magical or otherwise) do not affect an anointed individual. Magic ropes and the like do not avail against this salve. If it is smeared on a floor or on steps, the area should be treated as a long-lasting grease spell. The salve requires 8 hours to wear off normally, or it can be wiped off with an alcohol solution (even wine).

\emph{Salve of slipperiness} is needed to coat the inside of a container that is meant to hold \emph{sovereign glue} (see below).

Faint conjuration; CL 6th; \feat{Craft Wondrous Item}, grease; Price 1,000 cp.



\textbf{Shrouds of Disintegration:} These burial wrappings look to be made of fine, embroidered materials. When a body is placed inside, a command word will turn it to dust. The magic of the shrouds is usable only once, after which the wrappings become ordinary, fine cloth.

Strong transmutation; CL 15th; \feat{Craft Wondrous Item}, disintegrate; Price 6,600 cp; Weight 5 kg.



\textbf{Silversheen:} This substance can be applied to a weapon as a standard action. It will give the weapon the properties of alchemical silver for 1 hour, replacing the properties of any other special material it might have. One vial will coat a single melee weapon or 20 units of ammunition.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}; Price 250 cp.



\textbf{Sovereign Glue:} This pale amber substance is thick and viscous. Because of its particular powers, it can be contained only in a flask whose inside has been coated with 30 milliliters of \emph{salve of slipperiness}, and each time any of the bonding agent is poured from the flask, a new application of the \emph{salve of slipperiness} must be put in the flask within 1 round to prevent the remaining glue from adhering to the side of the container. A flask of \emph{sovereign glue}, when found, holds anywhere from 30 to 210 milliliters of the stuff (1d8$-1$, minimum 1), with the other 30 milliliters of the flask's capacity taken up by the \emph{salve of slipperiness}. 30 milliliters of this adhesive covers 1 square foot of surface, bonding virtually any two substances together in a permanent union. The glue takes 1 round to set. If the objects are pulled apart (a move action) before that time has elapsed, that application of the glue loses its stickiness and is worthless. If the glue is allowed to set, then attempting to separate the two bonded objects has no effect, except when universal solvent is applied to the bond. (\emph{Sovereign glue} is dissolved by universal solvent.)

Strong transmutation; CL 20th; \feat{Craft Wondrous Item}, make whole; Price 2,400 cp (per 30 ml).



\textbf{Stone of Alarm:} This stone cube, when given the command word, affixes itself to any object. If that object is touched thereafter by anyone who does not first speak that same command word, the stone emits a piercing screech for 1 hour that can be heard up to a quarter-mile away (assuming no intervening barriers).

Faint abjuration; CL 3rd; \feat{Craft Wondrous Item}, alarm; Price 2,700 cp; Weight 1 kg.



\textbf{Stone of Controlling Earth Elementals:} A stone of this nature is typically an oddly shaped bit of roughly polished rock.

The possessor of such a stone need but utter a few words of summoning, and a Huge earth elemental comes to the summoner. The summoning words require 1 full round to speak, and in all ways the stone functions as the summon monster VII spell. (If sand or rough, unhewn stone is the summoning medium, the elemental that comes is Large instead, and the stone functions as the summon monster VI spell.) The elemental appears in 1d4 rounds. Only one elemental can be summoned at a time. A new elemental requires a new patch of earth or stone, which cannot be accessed until after the first elemental disappears (is dispelled, dismissed, or slain).

Strong conjuration; CL 13th; \feat{Craft Wondrous Item}, summon monster VI, summon monster VII; Price 100,000 cp; Weight 2.5 kg.



\textbf{Stone of Good Luck (Luckstone):} This stone is typically a bit of rough polished agate or some similar mineral. Its possessor gains a +1 luck bonus on saving throws, ability checks, and skill checks.

Faint evocation; CL 5th; \feat{Craft Wondrous Item}, divine favor; Price 20,000 cp.



\textbf{Stone Horse:} Each item of this nature appears to be a fullsized, roughly hewn statue of a horse, carved from some type of hard stone. A command word brings the steed to life, enabling it to carry a burden and even to attack as if it were a real horse of the appropriate kind.

A stone horse can carry 450 kilograms tirelessly and never needs to rest or feed. Damage dealt to it can be repaired by first using a \spell{stone to flesh} spell, thus causing the stone horse to become a normal horse that can be healed normally. When fully healed, it automatically reverts to its stone form. While in its stone form, it can be fed gems, healing 1 point of damage for each 50 cp worth of mineral it is given.

There are two sorts of stone horses.

\begin{itemize*}
\item \textit{Courser:} This item has the statistics of a heavy horse as well as having hardness 10.
\item \textit{Destrier:} This item has the statistics of a heavy warhorse as well as having hardness 10.
\end{itemize*}

Strong transmutation; CL 14th; \feat{Craft Wondrous Item}, \spell{flesh to stone}, \spell{animate objects}; Price 10,000 cp (courser) or 14,800 cp (destrier); Weight 1,350 kg.



\textbf{Stone Salve:} This ointment has two uses. If 30 milliliters of it is applied to the flesh of a petrified creature, it returns the creature to flesh as the \spell{stone to flesh} spell. If 30 milliliters of it is applied to the flesh of a nonpetrified creature, it protects the creature as a \spell{stoneskin} spell.

Strong abjuration and transmutation; CL 13th; \feat{Craft Wondrous Item}, \spell{flesh to stone}, \spell{stoneskin}; Price 4,000 cp per 30 milliliters.



\textbf{Strand of Prayer Beads:} This item appears to be a normal string of prayer beads until the owner casts a divine spell. Once that occurs, the owner instantly knows the powers of the prayer beads and how to activate them. Each strand includes two or more special beads, each with a different magic power.

\Table{}{lX}{
  \tableheader Special Bead Type
& \tableheader Special Bead Ability\\

Bead of blessing     & Wearer can cast \spell{bless}.\\
Bead of healing      & Wearer can cast his choice of \spell{cure serious wounds}, \spell{remove blindness/deafness}, or \spell{remove disease}.\\
Bead of karma        & Wearer casts his spells at +4 caster level. Effect lasts 10 minutes.\\
Bead of smiting      & Wearer can cast \spell{chaos hammer}, \spell{holy smite}, \spell{order's wrath}, or \spell{unholy blight} (Will DC 17 partial).\\
Bead of summons      & Summons a powerful creature of appropriate alignment from the Outer Planes (an angel, devil, etc.) to aid the wearer for one day. (If the wearer uses the \emph{bead of summons} to summon a deity's emissary frivolously, the deity takes that character's items and places a \spell{geas/quest} upon him as punishment in the very least.)\\
Bead of wind walking & Wearer can cast \spell{wind walk}.\\
}

A lesser \emph{strand of prayer beads} has a \emph{bead of blessing} and a \emph{bead of healing}. A \emph{strand of prayer beads} has a \emph{bead of healing}, a \emph{bead of karma}, and a \emph{bead of smiting}. A greater strand of prayer beads has a \emph{bead of healing}, a \emph{bead of karma}, a \emph{bead of summons}, and a \emph{bead of wind walking}.

Each special bead can be used once per day, except for the \emph{bead of summons}, which works only once and then becomes nonmagical. The \emph{beads of blessing, smiting, and wind walking} function as spell trigger items; the \emph{beads of karma and summons} can be activated by any character capable of casting divine spells. The owner need not hold or wear the \emph{strand of prayer beads} in any specific location, as long as he carries it somewhere on his person.

The power of a special bead is lost if it is removed from the strand. Reduce the price of a \emph{strand of prayer beads} that is missing one or more beads by the following amounts: \emph{bead of blessing} $-600$ cp, \emph{bead of healing} $-9,000$ cp, \emph{bead of karma} $-20,000$ cp, \emph{bead of smiting} $-16,800$ cp, \emph{bead of summons} $-20,000$ cp, \emph{bead of wind walking} $-46,800$ cp.

Faint, moderate or strong (many schools); CL 1st (blessing), 5th (healing), 7th (smiting), 9th (karma), 11th (wind walking), 17th (summons); \feat{Craft Wondrous Item} and one of the following spells per bead, as appropriate: \spell{bless} (blessing); \spell{cure serious wounds}, \spell{remove blindness/deafness}, or \spell{remove disease} (healing); righteous might (karma); gate (summons); \spell{chaos hammer}, \spell{holy smite}, \spell{order's wrath}, or \spell{unholy blight} (smiting), \spell{wind walk} (wind walking); Price 9,600 cp (lesser), 45,800 cp (standard), 95,800 cp (greater).



\textbf{Sustaining Spoon:} This unremarkable eating utensil is typically fashioned from horn. If the spoon is placed in an empty container the vessel fills with a thick, pasty gruel. Although this substance has a flavor similar to that of warm, wet cardboard, it is highly nourishing and contains everything necessary to sustain any herbivorous, omnivorous, or carnivorous creature. The spoon can produce sufficient gruel each day to feed up to four humans.

Faint conjuration; CL 5th; \feat{Craft Wondrous Item}, \spell{create food and water}; Price 5,400 cp.



% \textbf{Tome of Clear Thought:} This heavy book contains instruction on improving memory and logic, but entwined within the words is a powerful magical effect. If anyone reads this book, which takes a total of 48 hours over a minimum of six days, she gains an inherent bonus of from +1 to +5 (depending on the type of tome) to her Intelligence score. Once the book is read, the magic disappears from the pages and it becomes a normal book. Because the \emph{tome of clear thought} provides an inherent bonus, the reader will earn extra skill points when she attains a new level.

% Strong evocation (if \spell{miracle} is used); CL 17th; \feat{Craft Wondrous Item}, \spell{miracle} or \spell{wish}; Price 27,500 cp (+1), 55,000 cp (+2), 82,500 cp (+3), 110,000 cp (+4), 137,500 cp (+5); Cost 1,250 cp + 5,100 XP (+1), 2,500 cp + 10,200 XP (+2), 3,750 cp + 15,300 XP (+3), 5,000 cp + 20,400 XP (+4), 6,250 cp + 25,500 XP (+5); Weight 2.5 kg.



% \textbf{Tome of Leadership and Influence:} This ponderous book details suggestions for persuading and inspiring others, but entwined within the words is a powerful magical effect. If anyone reads this book, which takes a total of 48 hours over a minimum of six days, he gains an inherent bonus of from +1 to +5 (depending on the type of tome) to his Charisma score. Once the book is read, the magic disappears from the pages and it becomes a normal book.

% Strong evocation (if \spell{miracle} is used); CL 17th; \feat{Craft Wondrous Item}, \spell{miracle} or \spell{wish}; Price 27,500 cp (+1), 55,000 cp (+2), 82,500 cp (+3), 110,000 cp (+4), 137,500 cp (+5); Cost 1,250 cp + 5,100 XP (+1), 2,500 cp + 10,200 XP (+2), 3,750 cp + 15,300 XP (+3), 5,000 cp + 20,400 XP (+4), 6,250 cp + 25,500 XP (+5); Weight 2.5 kg.



% \textbf{Tome of Understanding:} This thick book contains tips for improving instinct and perception, but entwined within the words is a powerful magical effect. If anyone reads this book, which takes a total of 48 hours over a minimum of six days, she gains an inherent bonus of from +1 to +5 (depending on the type of tome) to her Wisdom score. Once the book is read, the magic disappears from the pages and it becomes a normal book.

% Strong evocation (if \spell{miracle} is used); CL 17th; \feat{Craft Wondrous Item}, \spell{miracle} or \spell{wish}; Price 27,500 cp (+1), 55,000 cp (+2), 82,500 cp (+3), 110,000 cp (+4), 137,500 cp (+5); Cost 1,250 cp + 5,100 XP (+1), 2,500 cp + 10,200 XP (+2), 3,750 cp + 15,300 XP (+3), 5,000 cp + 20,400 XP (+4), 6,250 cp + 25,500 XP (+5); Weight 2.5 kg.



\textbf{Unguent of Timelessness:} When applied to any matter that was once alive this ointment allows that substance to resist the passage of time. Each year of actual time affects the substance as if only a day had passed. The coated object gains a +1 resistance bonus on all saving throws. The unguent never wears off, although it can be magically removed (by dispelling the effect, for instance). One flask contains enough material to coat eight Medium or smaller objects. A Large object counts as two Medium objects, and a Huge object counts as two Large objects.

Faint transmutation; CL 3rd; \feat{Craft Wondrous Item}; Price 150 cp.



\textbf{Universal Solvent:} This substance has the unique property of being able to dissolve \emph{sovereign glue} and tanglefoot bags. Applying the solvent is a standard action.

Strong transmutation; CL 20th; \feat{Craft Wondrous Item}, {disintegrate}; Price 50 cp.



\textbf{Well of Many Worlds:} This strange, interdimensional device looks just like a portable hole. Anything placed within it is immediately cast to another world---a parallel world, another planet, or a different plane (chosen randomly). If the well is moved, the random factor again comes into play. It can be picked up, folded, or rolled, just as a portable hole can be. Objects from the world the well touches can come through the opening just as easily as from the initiating place. (It is a two-way portal.)

Strong conjuration; CL 17th; \feat{Craft Wondrous Item}, \spell{gate}; Price 82,000 cp.



\textbf{Wind Fan:} A \emph{wind fan} appears to be nothing more than a wood and papyrus or cloth instrument with which to create a cooling breeze. By uttering the command word, its possessor causes the fan to generate air movement duplicating a \spell{gust of wind} spell. The fan can be used once per day with no risk. If it is used more frequently, there is a 20\% cumulative chance per usage during that day that the device tears into useless, nonmagical tatters.

Faint evocation; CL 5th; \feat{Craft Wondrous Item}, \spell{gust of wind}; Price 5,500 cp.
