\subsubsection{Neck}

\textbf{Amulet of Health:} This amulet is a golden disk on a chain. It usually bears the image of a lion or other powerful animal. The wearer's Constitution score is 19 while they wear this amulet. It has no effect if their Constitution is already 19 or higher.

Moderate transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{bear's endurance}; Price 16,000 cp.


\textbf{Amulet of Mighty Fists:} This amulet grants an enhancement bonus of +1 to +5 on attack and damage rolls with unarmed attacks and natural weapons.

Faint evocation; CL 5th; \feat{Craft Wondrous Item}, \spell{greater magic fang}, creator's caster level must be at least three times the amulet's bonus; Price 6,000 cp (+1), 24,000 cp (+2), 54,000 cp (+3), 96,000 cp (+4), 150,000 cp (+5).


\textbf{Amulet of Natural Armor:} This amulet, usually crafted from bone or beast scales, toughens the wearer's body and flesh, giving him an enhancement bonus to his natural armor bonus of from +1 to +5, depending on the kind of amulet.

Faint transmutation; CL 5th; \feat{Craft Wondrous Item}, \spell{barkskin}, creator's caster level must be at least three times the amulet's bonus; Price 2,000 cp (+1), 8,000 cp (+2), 18,000 cp (+3), 32,000 cp (+4), or 50,000 cp (+5).


\textbf{Amulet of the Planes:} This device usually appears to be a black circular amulet, although any character looking closely at it sees a dark, moving swirl of color. The amulet allows its wearer to utilize plane shift. However, this is a difficult item to master. The user must make a DC 15 Intelligence check in order to get the amulet to take her to the plane (and the specific location on that plane) that she wants. If she fails, the amulet transports her and all those traveling with her to a random location on that plane (01--60 on d\d) or to a random plane (61--100).

Strong conjuration; CL 15th; \feat{Craft Wondrous Item}, \spell{plane shift}; Price 120,000 cp.


\textbf{Amulet of Proof against Detection and Location:} This silver amulet protects the wearer from scrying and magical location just as a \spell{nondetection} spell does. If a divination spell is attempted against the wearer, the caster of the divination must succeed on a caster level check (1d20 + caster level) against a DC of 19 (as if the caster had cast \spell{nondetection} on herself).

Moderate abjuration; CL 8th; \feat{Craft Wondrous Item}, \spell{nondetection}; Price 35,000 cp.


\textbf{Hand of Glory:} This mummified human hand hangs by a leather cord around a character's neck (taking up space as a magic necklace would). If a magic ring is placed on one of the fingers of the hand, the wearer benefits from the ring as if wearing it herself, and it does not count against her two-ring limit. The hand can wear only one ring at a time. Even without a ring, the hand itself allows its wearer to use \spell{daylight} and \spell{see invisibility} each once per day.

Faint varied; CL 5th; \feat{Craft Wondrous Item}, \spell{animate dead}, \spell{daylight}, \spell{see invisibility}; Price 8,000 cp; Weight 1 kg.


\textbf{Hand of the Mage:} This mummified elf hand hangs by a golden chain around a character's neck (taking up space as a magic necklace would). It allows the wearer to utilize the spell \spell{mage hand} at will.

Faint transmutation; CL 2nd; \feat{Craft Wondrous Item}, \spell{mage hand}; Price 900 cp; Weight 1 kg.


\textbf{Medallion of Thoughts:} This appears to be a normal pendant disk hung from a neck chain. Usually fashioned from bronze, copper, or nickel-silver, the medallion allows the wearer to read the thoughts of others, as with the spell \spell{detect thoughts}.

Faint divination; CL 5th; \feat{Craft Wondrous Item}, \spell{detect thoughts}; Price 12,000 cp.


\textbf{Necklace of Adaptation:} This necklace is a heavy chain with a platinum medallion. The magic of the necklace wraps the wearer in a shell of fresh air, making him immune to all harmful vapors and gases (such as cloudkill and stinking cloud effects, as well as inhaled poisons) and allowing him to breathe, even underwater or in a vacuum.

Moderate transmutation; CL 7th; \feat{Craft Wondrous Item}, \spell{alter self}; Price 9,000 cp.


\textbf{Necklace of Fireballs:} This device appears to be nothing but beads on a string, sometimes with the ends tied together to form a necklace. (It does not count as an item worn around the neck for the purpose of determining which of a character's worn magic items is effective.) If a character holds it, however, all can see the strand as it really is---a golden chain from which hang a number of golden spheres. The spheres are detachable by the wearer (and only by the wearer), who can easily hurl one of them up to 70 feet. When a sphere arrives at the end of its trajectory, it detonates as a \spell{fireball} spell (Reflex DC 14 half).

Spheres come in different strengths, ranging from those that deal 2d6 points of fire damage to those that deal 10d6. The market price of a sphere is 150 cp for each die of damage it deals.

Each \emph{necklace of fireballs} contains a combination of spheres of various strengths. Some traditional combinations, designated types I through VII, are detailed below.

\Table{}{l *9c R}{
  \tableheader Necklace
& \tableheader 10d6
& \tableheader 9d6
& \tableheader 8d6
& \tableheader 7d6
& \tableheader 6d6
& \tableheader 5d6
& \tableheader 4d6
& \tableheader 3d6
& \tableheader 2d6
& \tableheader Market Price \\
Type I   &   &   &   &   &   & 1 &   & 2 &   & 1,650 cp \\
Type II  &   &   &   &   & 1 &   & 2 &   & 2 & 2,700 cp \\
Type III &   &   &   & 1 &   & 2 &   & 4 &   & 4,350 cp \\
Type IV  &   &   & 1 &   & 2 &   & 2 &   & 4 & 5,400 cp \\
Type V   &   & 1 &   & 2 &   & 2 &   & 2 &   & 5,850 cp \\
Type VI  & 1 &   & 2 &   & 2 &   & 4 &   &   & 8,100 cp \\
Type VII & 1 & 2 &   & 2 &   & 2 &   & 2 &   & 8,700 cp \\
}

If the necklace is being worn or carried by a character who fails her saving throw against a magical fire attack, the item must make a saving throw as well (with a save bonus of +7). If the necklace fails to save, all its remaining spheres detonate simultaneously, often with regrettable consequences for the wearer.

Moderate evocation; CL 10th; \feat{Craft Wondrous Item}, \spell{fireball}.


\textbf{Periapt of Health:} The wearer of this blue gem on a silver chain is immune to disease, including supernatural diseases.

Faint conjuration; CL 5th; \feat{Craft Wondrous Item}, \spell{remove disease}; Price 7,400 cp.


\textbf{Periapt of Proof against Poison:} This item is a brilliant-cut black gem on a delicate silver chain. The wearer is immune to poison, although poisons still active when the periapt is first donned still run their course.

Faint conjuration; CL 5th; \feat{Craft Wondrous Item}, \spell{neutralize poison}; Price 27,000 cp.


\textbf{Periapt of Wisdom:} Although it appears to be a normal pearl on a light chain, a \emph{periapt of wisdom} actually changes increases the possessor's Wisdom score to 19. It has no effect if their Wisdom is already 19 or higher.

Moderate transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{owl's wisdom}; Price 16,000 cp.


\textbf{Periapt of Wound Closure:} This stone is bright red and dangles on a gold chain. The wearer of this periapt automatically becomes stable if his hit points drop to between $-1$ and $-9$ inclusive. The periapt doubles the wearer's normal rate of healing or allows normal healing of wounds that would not do so normally. Hit point damage that involves bleeding is negated for the wearer of the periapt, but he is still susceptible to damage from bleeding that causes Constitution loss, such as that dealt by a wounding weapon.

Moderate conjuration; CL 10th; \feat{Craft Wondrous Item}, \spell{heal}; Price 15,000 cp.


\textbf{Scarab of Protection:} This device appears to be a silver medallion in the shape of a beetle. If it is held for 1 round, an inscription appears on its surface letting the holder know that it is a protective device.

The scarab's possessor gains spell resistance 20. The scarab can also absorb energy-draining attacks, death effects, and negative energy effects. Upon absorbing twelve such attacks, the scarab turns to powder and is destroyed.

Strong abjuration and necromancy; CL 18th; \feat{Craft Wondrous Item}, \spell{death ward}, \spell{spell resistance}; Price 38,000 cp.


\textbf{Scarab, Golembane:} This beetle-shaped pin enables its wearer to detect any golem within 18 meters, although he must concentrate (a standard action) in order for the detection to take place. A scarab enables its possessor to combat golems with weapons, unarmed attacks, or natural weapons as if those golems had no damage reduction.

Moderate divination; CL 8th; \feat{Craft Wondrous Item}, \spell{detect magic}, creator must be at least 10th level; Price 2,500 cp.
