\subsubsection{Shoulders}

\textbf{Cloak of Arachnida:} This black garment, embroidered with a weblike pattern in silk, gives the wearer the ability to climb as if a \spell{spider climb} spell had been placed upon her. In addition, the cloak grants her immunity to entrapment by \spell{web} spells or webs of any sort---she can actually move in webs at half her normal speed. Once per day, the wearer of this cloak can cast \spell{web}. She also gains a +2 luck bonus on all Fortitude saves against poison from spiders.

Faint conjuration and transmutation; CL 6th; \feat{Craft Wondrous Item}, \spell{spider climb}, \spell{web}; Price 14,000 cp; Weight 0.5 kg.


\textbf{Cloak of the Bat:} Fashioned of dark brown or black cloth, this cloak bestows a +5 competence bonus on \skill{Hide} checks. The wearer is also able to hang upside down from the ceiling, like a bat.

By holding the edges of the garment, the wearer is able to fly as per the spell. If he desires, the wearer can actually \spell{polymorph} himself into an ordinary bat and fly accordingly. (All possessions worn or carried are part of the transformation.) Flying, either with the cloak or in bat form, can be accomplished only in darkness (either under the night sky or in a lightless or near-lightless environment underground). Either of the flying powers is usable for up to 7 minutes at a time, but after a flight of any duration the cloak cannot bestow any flying power for a like period of time.

Moderate transmutation; CL 7th; \feat{Craft Wondrous Item}, \spell{fly}, \spell{polymorph}; Price 26,000 cp; Weight 0.5 kg.


\textbf{Cloak of Charisma:} This lightweight and fashionable cloak has a highly decorative silver trim. When in a character's possession, their Charisma score becomes 19.

Moderate transmutation; CL 8th; \feat{Craft Wondrous Item}, \spell{eagle's splendor}; Price 16,000 cp; Weight 1 kg.


\textbf{Cloak of Displacement, Minor:} This item appears to be a normal cloak, but when worn by a character its magical properties distort and warp light waves. This displacement works similar to the \spell{displacement} spell except that it only grants a 20\% miss chance on attacks against the wearer. It functions continually.

Faint illusion; CL 3rd; \feat{Craft Wondrous Item}, \spell{displacement}; Price 24,000 cp; Weight 0.5 kg.


\textbf{Cloak of Displacement, Major:} This item appears to be a normal cloak, but on command its magical properties distort and warp light waves. This displacement works just like the \spell{displacement} spell and lasts for a total of 15 rounds per day, which the wearer can divide up as she sees fit.

Moderate illusion; CL 7th; \feat{Craft Wondrous Item}, Extend Spell, \spell{displacement}; Price 50,000 cp; Weight 0.5 kg.


\textbf{Cloak of Elvenkind:} This cloak of neutral gray cloth is indistinguishable from an ordinary cloak of the same color. However, when worn with the hood drawn up around the head, it gives the wearer a +5 competence bonus on \skill{Hide} checks.

Faint illusion; CL 3rd; \feat{Craft Wondrous Item}, invisibility, creator must be an elf; Price 2,500 cp; Weight 0.5 kg.


\textbf{Cloak of Etherealness:} This silvery-gray cloak seems to absorb light rather than be illuminated by it. On command, the cloak makes its wearer ethereal (as the \spell{ethereal jaunt} spell). The effect is dismissible. The cloak works for a total of up to 10 minutes per day. This duration need not be continuous.

Strong transmutation; CL 15th; \feat{Craft Wondrous Item}, \spell{ethereal jaunt}; Price 55,000 cp; Weight 0.5 kg.


\textbf{Cloak of the Manta Ray:} This cloak appears to be made of leather until the wearer enters salt water. At that time the cloak of the manta ray adheres to the individual, and he appears nearly identical to a manta ray (as the \spell{polymorph} spell, except that it allows only manta ray form). He gains a +3 natural armor bonus, the ability to breathe underwater, and a swim speed of 60 feet, like a real manta ray.

Although the cloak does not enable the wearer to bite opponents as a manta ray does, it does have a tail spine that can be used to strike at opponents behind the wearer, dealing 1d6 points of damage. This attack can be used in addition to any other attack the character has, using his highest melee attack bonus. The wearer can release his arms from the cloak without sacrificing underwater movement if so desired.

Moderate transmutation; CL 9th; \feat{Craft Wondrous Item}, \spell{polymorph}, water breathing; Price 7,200 cp; Weight 0.5 kg.


\textbf{Cloak of Resistance:} These garments offer magic protection in the form of a +1 to +5 resistance bonus on all saving throws (Fortitude, Reflex, and Will).

Faint abjuration; CL 5th; \feat{Craft Wondrous Item}, \spell{resistance}, creator's caster level must be at least three times the cloak's bonus; Price 1,000 cp (+1), 4,000 cp (+2), 9,000 cp (+3), 16,000 cp (+4), 25,000 cp (+5); Weight 0.5 kg.


\textbf{Mantle of Faith:} This holy garment, worn over normal clothing, grants damage reduction 5/evil to the character wearing it.

Strong abjuration [good]; CL 20th; \feat{Craft Wondrous Item}, \spell{stoneskin}; Price 76,000 cp.


\textbf{Mantle of Spell Resistance:} This garment, worn over normal clothing or armor, grants the wearer spell resistance 21.

Moderate abjuration; CL 9th; \feat{Craft Wondrous Item}, \spell{spell resistance}; Price 90,000 cp.


\textbf{Wings of Flying:} A pair of these wings might appear to be nothing more than a plain cloak of old, black cloth, or they could be as elegant as a long cape of blue feathers. When the wearer speaks the command word, the cloak turns into a pair of bat or bird wings that empower her to fly with a speed of 60 feet (good maneuverability).

Moderate transmutation; CL 10th; \feat{Craft Wondrous Item}, \spell{fly}; Price 54,000 cp; Weight 1 kg.
