\section{Vital Statistics}
The details of your character's age, gender, height, weight, and appearance are up to you. However, if you prefer some rough guidelines in determining those details, refer to the tables in this section.

\subsection{Character Age}
You can choose or randomly generate your character's age. If you choose it, it must be at least the minimum for the character's race and class (see \tabref{Random Starting Ages}). Your character's minimum starting age is the adulthood age of their race plus the number of dice indicated in the entry corresponding to the character's race and class on \tabref{Random Starting Ages}.

Alternatively, you may roll dice to determine how old your character is, as specified in \tabref{Random Starting Ages}.

\Table{Random Starting Ages}{X l Z{1.2cm} Z{1.2cm} Z{1.2cm}}{
\tableheader Race & \tableheader Adulthood & \tableheader Barbarian Rogue & \tableheader Bard Fighter Gladiator Ranger & \tableheader Cleric Druid Psion Templar Wizard \\
Human      & 15 years & +1d4 & +1d6 & +2d6\\
Aarakocra  &  8 years & +1d4 & +1d6 & +2d4\\
Dwarf      & 30 years & +2d6 & +4d6 & +6d6\\
Elf        & 20 years & +1d4 & +1d6 & +2d6\\
Half-elf   & 15 years & +1d6 & +2d6 & +3d6\\
Half-giant & 25 years & +1d6 & +2d6 & +4d6\\
Halfling   & 20 years & +3d6 & +3d6 & +4d6\\
Mul        & 14 years & +1d4 & +1d6 & +2d6\\
Pterran    & 10 years & +1d6 & +1d6 & +1d6\\
Thri-kreen &  4 years & +1d4 & +1d4 & +1d4\\
}

With age, a character's physical ability scores decrease and his or her mental ability scores increase. The effects of each aging step are cumulative. However, none of a character's ability scores can be reduced below 1 in this way.

\Table{}{b{1cm} lC b{1cm}}{
& \tableheader Aging Step & \tableheader Ability Score Changes & \\

& & $-1$ to Str, Dex, and Con  & \\
\cmidrule[0pt]{2-3}
\rowcolor{TableColor}
& \multirow{-2}{*}{{Middle Age}} & $+1$ to Int, Wis, and Cha  & \\

& & $-2$ to Str, Dex, and Con  & \\
\cmidrule[0pt]{2-3}
& \multirow{-2}{*}{{Old}} & $+1$ to Int, Wis, and Cha & \\

& & $-3$ to Str, Dex, and Con  & \\
\cmidrule[0pt]{2-3}
\rowcolor{TableColor}
& \multirow{-2}{*}{{Venerable}} & $+1$ to Int, Wis, and Cha & \\
}

% \begin{itemize*}
% \item \textbf{Middle Age:} $-1$ to Str, Dex, and Con; $+1$ to Int, Wis, and Cha.
% \item \textbf{Old:} $-2$ to Str, Dex, and Con; $+1$ to Int, Wis, and Cha.
% \item \textbf{Venerable:} $-3$ to Str, Dex, and Con; $+1$ to Int, Wis, and Cha.
% \end{itemize*}

Aarakocra, pterrans, and thri-kreens do not suffer aging penalties or gain aging bonuses until they reach venerable age, at which point all cumulative effects apply.

When a character reaches venerable age, secretly roll his or her maximum age, which is the number from the Venerable column on \tabref{Aging Effects} plus the result of the dice roll indicated on the Maximum Age column on that table, and records the result, which the player does not know. A character who reaches his or her maximum age dies of old age at some time during the following year.

The maximum ages are for player characters. Most people in the world at large die from pestilence, accidents, infections, or violence before getting to venerable age.

\Table{Aging Effects}{X c c c c}{
\tableheader Race & \tableheader Middle Age & \tableheader Old & \tableheader Venerable & \tableheader Max. Age\\
Human      &  35 yrs. &  53 yrs. &  70 yrs. &  +2d20 yrs. \\
Aarakocra  &          &          &  36 yrs. &  +1d10 yrs. \\
Dwarf      & 100 yrs. & 150 yrs. & 200 yrs. &  +4d20 yrs. \\
Elf        &  50 yrs. &  75 yrs. & 100 yrs. &  +3d20 yrs. \\
Half-elf   &  45 yrs. &  60 yrs. &  90 yrs. &  +2d20 yrs. \\
Half-giant &  60 yrs. &  90 yrs. & 120 yrs. & +1d100 yrs. \\
Halfling   &  50 yrs. &  75 yrs. & 100 yrs. &  +5d10 yrs. \\
Mul        &  30 yrs. &  45 yrs. &  60 yrs. &  +2d10 yrs. \\
Pterran    &          &          &  40 yrs. &  +1d10 yrs. \\
Thri-kreen &          &          &  25 yrs. &  +1d10 yrs. \\
}

\subsection{Height and Weight}
Choose your character's height and weight from the ranges mentioned on the racial description, or roll randomly on \tabref{Random Height and Weight}.

The dice roll given in the Height Modifier column determines the character's extra height beyond the base height. That same number multiplied by the dice roll or quantity given in the Weight Modifier column determines the character's extra weight beyond the base weight.

Thri-kreen characters are 1.20 meter longer than they are tall.

\Table{Random Height and Weight}{X r{1cm} b{1.2cm} r{1cm} b{1.2cm}}{
\tableheader Race & \tableheader Base Height & \tableheader Height Modifier ($\times 2.5$ cm) & \tableheader Base Weight & \tableheader Weight Modifier ($\times 0.5$ kg)\\
Human, male        & 1.47 m & +2d10 &   60 kg & $\times$ 2d4\\
Human, female      & 1.35 m & +2d10 & 42.5 kg & $\times$ 2d4\\
Aarakocra, male    & 1.93 m & +2d8  &   35 kg & $\times$ 1d4\\
Aarakocra, female  & 1.87 m & +2d8  &   30 kg & $\times$ 1d4\\
Dwarf, male        & 1.30 m & +2d4  &   65 kg & $\times$ 2d6\\
Dwarf, female      & 1.25 m & +2d4  &   50 kg & $\times$ 2d6\\
Elf, male          &    2 m & +2d6  &   65 kg & $\times$ 2d4\\
Elf, female        & 1.95 m & +2d6  &   55 kg & $\times$ 2d4\\
Half-elf, male     & 1.52 m & +2d10 &   65 kg & $\times$ 2d4\\
Half-elf, female   & 1.47 m & +2d10 &   45 kg & $\times$ 2d4\\
Half-giant, male   &    3 m & +2d12 &  700 kg & $\times$ 3d4\\
Half-giant, female &    3 m & +2d12 &  500 kg & $\times$ 3d4\\
Halfling, male     & 0.81 m & +2d4  &   15 kg & $\times$ 1\\
Halfling, female   & 0.76 m & +2d4  & 12.5 kg & $\times$ 1\\
Mul, male          & 1.47 m & +2d10 &   65 kg & $\times$ 2d6\\
Mul, female        & 1.37 m & +2d10 &   50 kg & $\times$ 2d6\\
Pterran, male      & 1.47 m & +2d10 &   65 kg & $\times$ 2d6\\
Pterran, female    & 1.40 m & +2d10 &   55 kg & $\times$ 2d6\\
Thri-kreen         & 2.08 m & +1d6  &  225 kg & $\times$ 1d4\\
}