\section{Assassin Spells}




\subsection{1st-Level Assassin Spells}

\spellList{Disguise Self}: Changes your appearance.

\spellList{Detect Poison}: Detects poison in one creature or object.

\spellList{Feather Fall}: Objects or creatures fall slowly.

\spellList{Ghost Sound}: Figment sounds.

\spellList{Jump}: Subject gets bonus on \skill{Jump} checks.

\spellList{Obscuring Mist}: Fog surrounds you.

\spellList{Slave Scent}: Divines target's social class. %%

\spellList{Sleep}: Puts 4 HD of creatures into magical slumber.

\spellList{True Strike}: +20 on your next attack roll.




\subsection{2nd-Level Assassin Spells}

\spellList{Alter Self}: Assume form of a similar creature.

\spellList{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\spellList{Darkness}: 6-m radius of supernatural shadow.

\spellList{Death Mark}: Target becomes sickened. %%

\spellList{Fox's Cunning}: Subject gains +4 Int for 1 min./level.

\spellList{Illusory Script}\textsuperscript{M}: Only intended reader can decipher.

\spellList{Invisibility}: Subject is invisible for 1 min./level or until it attacks.

\spellList{Pass without Trace}: One subject/level leaves no tracks.

\spellList{Spider Climb}: Grants ability to walk on walls and ceilings.

\spellList{Undetectable Alignment}: Conceals alignment for 24 hours.




\subsection{3rd-Level Assassin Spells}

\spellList{Boneclaw's Cut}\textsuperscript{F}: Deals damage that continues to cause bleeding damage.%%

\spellList{Death Whip}\textsuperscript{F}: Whip deals temporary Strength damage. %%

\spellList{Deep Slumber}: Puts 10 HD of creatures to sleep.

\spellList{Deeper Darkness}: Object sheds supernatural shadow in 18-m radius.

\spellList{False Life}: Gain 1d10 temporary hp +1/level (max +10).

\spellList{Magic Circle against Good}: As \spell{protection from good}, but 3-m radius and 10 min./level.

\spellList{Misdirection}: Misleads divinations for one creature or object.

\spellList{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.




\subsection{4th-Level Assassin Spells}

\spellList{Clairaudience/Clairvoyance}: Hear or see at a distance for 1 min./level.

\spellList{Claws of the Tembo}: Deals 1d6 Str damage and transfers hp. %%

\spellList{Dimension Door}: Teleports you short distance.

\spellList{Freedom of Movement}: Subject moves normally despite impediments.

\spellList{Glibness}: You gain +30 bonus on \skill{Bluff} checks, and your lies can escape magical discernment.

\spellList{Invisibility, Greater}: As \spell{invisibility}, but subject can attack and stay invisible.

\spellList{Locate Creature}: Indicates direction to familiar creature.

\spellList{Mage Seeker}\textsuperscript{F}: Locate nearby wizard. %%

\spellList{Modify Memory}: Changes 5 minutes of subject’s memories.

\spellList{Poison}: Touch deals 1d10 Con damage, repeats in 1 min.

\spellList{Rangeblade}: Can strike with melee weapons at a distance. %%

\spellList{Scapegoat}\textsuperscript{M}: Put the blame on a nearby target. %%
