\section{Cleric Spells}



\subsection{0-Level Cleric Spells (Orisons)}

\spellList{Create Element}\textsuperscript{R}: Create a small amount of patron element.

\spellList{Cure Minor Wounds}: Cures 1 point of damage.

\spellList{Detect Magic}\textsuperscript{R}: Detects spells and magic items within 18 m.

\spellList{Detect Poison}: Detects poison in one creature or object.

\spellList{Guidance}: +1 on one attack roll, saving throw, or skill check.

\spellList{Inflict Minor Wounds}: Touch attack, 1 point of damage.

\spellList{Light}\textsuperscript{R}: Object shines like a torch.

\spellList{Mending}: Makes minor repairs on an object.

\spellList{Purify Food and Drink}\textsuperscript{R}: Purifies 0.3 m$^3$/level of food or water.

\spellList{Read Magic}\textsuperscript{R}: Read scrolls and spellbooks.

\spellList{Resistance}: Subject gains +1 on saving throws.

\spellList{Virtue}: Subject gains 1 temporary hp.



\subsection{1st-Level Cleric Spells}

\spellList{Bane}: Enemies take $-1$ on attack rolls and saves against fear.

\spellList{Bless}: Allies gain +1 on attack rolls and saves against fear.

% \spellList{Bless Water}\textsuperscript{M}: Makes holy water.
\spellList{Bless Element}\textsuperscript{M}: Makes holy element. %%

\spellList{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.

\spellList{Command}: One subject obeys selected command for 1 round.

\spellList{Comprehend Languages}\textsuperscript{R}: You understand all spoken and written languages.

\spellList{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

% \spellList{Curse Water}\textsuperscript{M}: Makes unholy water.
\spellList{Curse Element}\textsuperscript{M}: Makes unholy element. %%

\spellList{Deathwatch}\textsuperscript{R}: Reveals how near death subjects within 9 m are.

\noindent\textit{\hyperref[spell:Detect Chaos]{Detect Chaos}/\hyperref[spell:Detect Evil]{Evil}/\hyperref[spell:Detect Good]{Good}/\hyperref[spell:Detect Law]{Law}}\textsuperscript{R}: Reveals creatures, spells, or objects of selected alignment.

\spellList{Detect Undead}\textsuperscript{R}: Reveals undead within 18 m.

\spellList{Divine Favor}: You gain +1 per three levels on attack and damage rolls.

\spellList{Doom}: One subject takes $-2$ on attack rolls, saves, and checks.

\spellList{Endure Elements}: Exist comfortably in hot or cold environments.

\spellList{Entropic Shield}: Ranged attacks against you have 20\% miss chance.

\spellList{Heat Lash}: Creature suffers 1d4+1 damage and is knocked back 1.5 m. %%

\spellList{Hide from Undead}: Undead can't perceive one subject/level.

\spellList{Inflict Light Wounds}: Touch deals 1d8 damage +1/level (max +5).

% \spellList{Magic Stone}: Three stones gain +1 on attack, deal 1d6 +1 damage.

\spellList{Magic Weapon}: Weapon gains +1 bonus.

\spellList{Obscuring Mist}: Fog surrounds you.

\noindent\textit{\hyperref[spell:Protection from Chaos]{Protection from Chaos}/\hyperref[spell:Protection from Evil]{Evil}/\hyperref[spell:Protection from Good]{Good}/\hyperref[spell:Protection from Law]{Law}}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\spellList{Remove Fear}: Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.

\spellList{Sanctuary}: Opponents can't attack you, and you can't attack.

\spellList{Shield of Faith}: Aura grants +2 or higher deflection bonus.

\spellList{Summon Monster I}\footnotemark[1]: Calls extraplanar creature to fight for you.

\noindent 1 Cast only to summon from your element's plane.



\subsection{2nd-Level Cleric Spells}

\spellList{Aid}: +1 on attack rolls and saves against fear, 1d8 temporary hp +1/level (max +10).

\spellList{Align Weapon}: Weapon becomes good, evil, lawful, or chaotic.

\spellList{Augury}\textsuperscript{MFR}: Learns whether an action will be good or bad.

\spellList{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\spellList{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\spellList{Calm Emotions}: Calms creatures, negating emotion effects.

\spellList{Consecrate}\textsuperscript{MR}: Fills area with positive energy, making undead weaker.

\spellList{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\spellList{Darkness}: 6-m radius of supernatural shadow.

\spellList{Death Knell}: Kills dying creature; you gain 1d8 temporary hp, +2 to Str, and +1 level.

\spellList{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\spellList{Desecrate}\textsuperscript{MR}: Fills area with negative energy, making undead stronger.

\spellList{Eagle's Splendor}: Subject gains +4 to Cha for 1 min./level.

\spellList{Enthrall}: Captivates all within 30 m + 3 m/level.

\spellList{Find Traps}: Notice traps as a rogue does.

\spellList{Gentle Repose}: Preserves one corpse.

\spellList{Hold Person}: Paralyzes one humanoid for 1 round/level.

\spellList{Inflict Moderate Wounds}: Touch attack, 2d8 damage +1/level (max +10).

\spellList{Make Whole}: Repairs an object.

\spellList{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\spellList{Remove Paralysis}: Frees one or more creatures from paralysis or slow effect.

\spellList{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\spellList{Restoration, Lesser}: Dispels magical ability penalty or repairs 1d4 ability damage.

\spellList{Return to the Earth}\textsuperscript{R}: Turns dead and undead bodies into dust. %%

\spellList{Shatter}: Sonic vibration damages objects or crystalline creatures.

\spellList{Shield Other}\textsuperscript{F}: You take half of subject's damage.

\spellList{Silence}: Negates sound in 6-m radius.

\spellList{Sound Burst}: Deals 1d8 sonic damage to subjects; may stun them.

\spellList{Spiritual Weapon}: Magic weapon attacks on its own.

\spellList{Status}: Monitors condition, position of allies.

\spellList{Summon Monster II}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Undetectable Alignment}: Conceals alignment for 24 hours.

\spellList{Zone of Truth}: Subjects within range cannot lie.

\noindent 1 Cast only to summon from your element's plane.



\subsection{3rd-Level Cleric Spells}

\spellList{Animate Dead}\textsuperscript{M}: Creates undead skeletons and zombies.

\spellList{Bestow Curse}: $-6$ to an ability score; $-4$ on attack rolls, saves, and checks; or 50\% chance of losing each action.

\spellList{Blindness/Deafness}: Makes subject blinded or deafened.

\spellList{Contagion}: Infects subject with chosen disease.

% \spellList{Continual Flame}\textsuperscript{M}: Makes a permanent, heatless torch.

% \spellList{Create Food and Water}: Feeds three humans (or one horse)/level.

\spellList{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

% \spellList{Daylight}: 18-m radius of bright light.

\spellList{Deeper Darkness}: Object sheds supernatural shadow in 18-m radius.

\spellList{Dispel Magic}: Cancels spells and magical effects.

\spellList{Eye of the Storm}: Protects 9-m radius from effects of storm for 1 hour/level. %%

\spellList{Glyph of Warding}\textsuperscript{MR}: Inscription harms those who pass it.

\spellList{Helping Hand}: Ghostly hand leads subject to you.

\spellList{Inflict Serious Wounds}: Touch attack, 3d8 damage +1/level (max +15).

\spellList{Invisibility Purge}: Dispels invisibility within 1.5 m/level.

\spellList{Lighten Load}: Increases Strength for carrying capacity only. %%

\spellList{Locate Object}: Senses direction toward object (specific or type).

\noindent\textit{\hyperref[spell:Magic Circle against Chaos]{Magic Circle against Chaos}/\hyperref[spell:Magic Circle against Evil]{Evil}/\hyperref[spell:Magic Circle against Good]{Good}/\hyperref[spell:Magic Circle against Law]{Law}}: As \emph{protection} spells, but 3-m radius and 10 min./level.

\spellList{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.

% \spellList{Meld into Stone}: You and your gear merge with stone.

\spellList{Obscure Object}: Masks object against scrying.

\spellList{Prayer}: Allies +1 bonus on most rolls, enemies $-1$ penalty.

\spellList{Protection from Energy}: Absorb 12 points/level of damage from one kind of energy.

\spellList{Remove Blindness/Deafness}: Cures normal or magical conditions.

\spellList{Remove Curse}: Frees object or person from curse.

\spellList{Remove Disease}: Cures all diseases affecting subject.

\spellList{Sand Pit}: Excavates sand in a 9 m wide and 15 m deep cone. %%

\spellList{Searing Light}: Ray deals 1d8/two levels damage, more against undead.

\spellList{Speak with Dead}: Corpse answers one question/two levels.

% \spellList{Stone Shape}: Sculpts stone into any shape.

\spellList{Summon Monster III}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Surface Walk}\textsuperscript{R}: Subject treads on unstable surfaces as if solid. %%

\spellList{Telepathic Bond, Lesser}\textsuperscript{R}: As \spell{telepathic bond}, but you and one other creature.

% \spellList{Water Breathing}: Subjects can breathe underwater.

% \spellList{Water Walk}: Subject treads on water as if solid.

% \spellList{Wind Wall}: Deflects arrows, smaller creatures, and gases.

\noindent 1 Cast only to summon from your element's plane.



\subsection{4th-Level Cleric Spells}

% \spellList{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle).

% \spellList{Control Water}: Raises or lowers bodies of water.

\spellList{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\spellList{Death Ward}: Grants immunity to death spells and negative energy effects.

\spellList{Dimensional Anchor}: Bars extradimensional movement.

\spellList{Discern Lies}: Reveals deliberate falsehoods.

\spellList{Dismissal}: Forces a creature to return to native plane.

\spellList{Divination}\textsuperscript{MR}: Provides useful advice for specific proposed actions.

\spellList{Divine Power}: You gain attack bonus, +6 to Str, and 1 hp/level.

\spellList{Dweomer of Transference}: Convert spellcasting into psionic power points.

\spellList{Elemental Armor}: Armor or shield gains enhancement bonus and special quality. %%

\spellList{Elemental Weapon}: Weapon gains enhancement bonus and special quality. %%

\spellList{Freedom of Movement}: Subject moves normally despite impediments.

\spellList{Giant Vermin}: Turns centipedes, scorpions, or spiders into giant vermin.

\spellList{Imbue with Spell Ability}: Transfer spells to subject.

\spellList{Inflict Critical Wounds}: Touch attack, 4d8 damage +1/level (max +20).

\spellList{Magic Weapon, Greater}: +1 bonus/four levels (max +5).

\spellList{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\spellList{Planar Ally, Lesser}\textsuperscript{X}: Exchange services with a 6 HD extraplanar creature.

\spellList{Poison}: Touch deals 1d10 Con damage, repeats in 1 min.

\spellList{Repel Vermin}: Insects, spiders, and other vermin stay 3 m away.

\spellList{Restoration}\textsuperscript{MR}: Restores level and ability score drains.

\spellList{Sending}: Delivers short message anywhere, instantly.

\spellList{Spell Immunity}: Subject is immune to one spell per four levels.

\spellList{Summon Monster IV}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Tongues}: Speak any language.

\noindent 1 Cast only to summon from your element's plane.



\subsection{5th-Level Cleric Spells}

\spellList{Atonement}\textsuperscript{FXR}: Removes burden of misdeeds from subject.

\spellList{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrification.

\spellList{Command, Greater}: As \spell{command}, but affects one subject/level.

\spellList{Commune}\textsuperscript{XR}: Deity answers one yes-or-no question/level.

\spellList{Cure Light Wounds, Mass}: Cures 1d8 damage +1/level for many creatures.

\noindent\textit{\hyperref[spell:Dispel Chaos]{Dispel Chaos}/\hyperref[spell:Dispel Evil]{Evil}/\hyperref[spell:Dispel Good]{Good}/\hyperref[spell:Dispel Law]{Law}}: 4 bonus against attacks.

\spellList{Disrupting Weapon}: Melee weapon destroys undead.

% \spellList{Flame Strike}: Smite foes with divine fire (1d6/level damage).

\spellList{Hallow}\textsuperscript{MR}: Designates location as holy.

\spellList{Inflict Light Wounds, Mass}: Deals 1d8 damage +1/level to many creatures.

\spellList{Insect Plague}: Locust swarms attack creatures.

\spellList{Mark of Justice}: Designates action that will trigger curse on subject.

\spellList{Plane Shift}\textsuperscript{F}: As many as eight subjects travel to another plane.

\spellList{Psychic Turmoil}: Invisible field leeches psionic power points away.

\spellList{Raise Dead}\textsuperscript{M}: Restores life to subject who died as long as one day/level ago.

\spellList{Rangeblade}: Can strike with melee weapons at a distance. %%

\spellList{Righteous Might}: Your size increases, and you gain combat bonuses.

\spellList{Scrying}\textsuperscript{F}: Spies on subject from a distance.

\spellList{Slay Living}: Touch attack kills subject.

\spellList{Spell Resistance}: Subject gains SR 12 + level.

\spellList{Summon Monster V}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Symbol of Pain}\textsuperscript{M}: Triggered rune wracks nearby creatures with pain.

\spellList{Symbol of Sleep}\textsuperscript{M}: Triggered rune puts nearby creatures into catatonic slumber.

\spellList{True Seeing}\textsuperscript{MR}: Lets you see all things as they really are.

\spellList{Unhallow}\textsuperscript{MR}: Designates location as unholy.

% \spellList{Wall of Stone}: Creates a stone wall that can be shaped.

\noindent 1 Cast only to summon from your element's plane.


\subsection{6th-Level Cleric Spells}

\spellList{Animate Objects}: Objects attack your foes.

\spellList{Antilife Shell}: 3-m field hedges out living creatures.

\spellList{Banishment}: Banishes 2 HD/level of extraplanar creatures.

\spellList{Bear's Endurance, Mass}: As \spell{bear's endurance}, affects one subject/ level.

\spellList{Blade Barrier}: Wall of blades deals 1d6/level damage.

\spellList{Braxatskin}: Your skin hardens, granting armor bonus and damage reduction. %%

\spellList{Bull's Strength, Mass}: As \spell{bull's strength}, affects one subject/level.

\spellList{Create Undead}: Create ghouls, ghasts, mummies, or mohrgs.

\spellList{Cure Moderate Wounds, Mass}: Cures 2d8 damage +1/level for many creatures.

\spellList{Dispel Magic, Greater}: As \spell{dispel magic}, but up to +20 on check.

\spellList{Eagle's Splendor, Mass}: As \spell{eagle's splendor}, affects one subject/level.

\spellList{Find the Path}: Shows most direct way to a location.

\spellList{Forbiddance}\textsuperscript{MR}: Blocks planar travel, damages creatures of different alignment.

\spellList{Geas/Quest}: As \spell{lesser geas}, plus it affects any creature.

\spellList{Glyph of Warding, Greater}\textsuperscript{M}: As \spell{glyph of warding}, but up to 10d8 damage or 6th-level spell.

\spellList{Harm}: Deals 10 points/level damage to target.

\spellList{Heal}: Cures 10 points/level of damage, all diseases and mental conditions.

\spellList{Heroes' Feast}: Food for one creature/level cures and grants combat bonuses.

\spellList{Inflict Moderate Wounds, Mass}: Deals 2d8 damage +1/level to many creatures.

\spellList{Owl's Wisdom, Mass}: As \spell{owl's wisdom}, affects one subject/level.

\spellList{Planar Ally}\textsuperscript{X}: As \spell{lesser planar ally}, but up to 12 HD.

\spellList{Summon Monster VI}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Symbol of Fear}\textsuperscript{M}: Triggered rune panics nearby creatures.

\spellList{Symbol of Persuasion}\textsuperscript{M}: Triggered rune charms nearby creatures.

\spellList{Undeath to Death}\textsuperscript{M}: Destroys 1d4 HD/level undead (max 20d4).

% \spellList{Wind Walk}: You and your allies turn vaporous and travel fast.

\spellList{Word of Recall}: Teleports you back to designated place.

\noindent 1 Cast only to summon from your element's plane.



\subsection{7th-Level Cleric Spells}

\spellList{Blasphemy}: Kills, paralyzes, weakens, or dazes nonevil subjects.

\spellList{Control Weather}: Changes weather in local area.

\spellList{Cure Serious Wounds, Mass}: Cures 3d8 damage +1/level for many creatures.

\spellList{Destruction}\textsuperscript{F}: Kills subject and destroys remains.

\spellList{Dictum}: Kills, paralyzes, slows, or deafens nonlawful subjects.

\spellList{Elemental Chariot}: Enhances chariot with elemental effects. %%

\spellList{Ethereal Jaunt}: You become ethereal for 1 round/level.

\spellList{Holy Word}: Kills, paralyzes, blinds, or deafens nongood subjects.

\spellList{Inflict Serious Wounds, Mass}: Deals 3d8 damage +1/level to many creatures.

\spellList{Psychic Turmoil, Greater}: As \spell{psychic turmoil}, but you gain power points as temporary hp.

\spellList{Refuge}\textsuperscript{M}: Alters item to transport its possessor to you.

\spellList{Regenerate}: Subject's severed limbs grow back, cures 4d8 damage +1/level (max +35).

\spellList{Repulsion}: Creatures can't approach you.

\spellList{Restoration, Greater}\textsuperscript{X}: As \spell{restoration}, plus restores all levels and ability scores.

\spellList{Resurrection}\textsuperscript{M}: Fully restore dead subject.

\spellList{Sands of Time}\textsuperscript{F}: Reverses or accelerates aging of a non-living object. %%

\spellList{Scrying, Greater}: As \spell{scrying}, but faster and longer.

\spellList{Summon Monster VII}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Symbol of Stunning}\textsuperscript{M}: Triggered rune stuns nearby creatures.

\spellList{Symbol of Weakness}\textsuperscript{M}: Triggered rune weakens nearby creatures.

\spellList{Unliving Identity}\textsuperscript{MX}: Transforms a zombie into a thinking zombie. %%

\spellList{Word of Chaos}: Kills, confuses, stuns, or deafens nonchaotic subjects.

\noindent 1 Cast only to summon from your element's plane.



\subsection{8th-Level Cleric Spells}

\spellList{Antimagic Field}: Negates magic within 3 m.

\spellList{Brain Spider}: Listen to thoughts of up to eight other creatures.

\spellList{Cloak of Chaos}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against lawful spells.

\spellList{Create Greater Undead}\textsuperscript{M}: Create shadows, wraiths, spectres, or devourers.

\spellList{Cure Critical Wounds, Mass}: Cures 4d8 damage +1/level for many creatures.

\spellList{Dimensional Lock}: Teleportation and interplanar travel blocked for one day/level.

\spellList{Discern Location}: Reveals exact location of creature or object.

% \spellList{Earthquake}: Intense tremor shakes 24-m radius.

% \spellList{Fire Storm}: Deals 1d6/level fire damage.

\spellList{Holy Aura}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against evil spells.

\spellList{Inflict Critical Wounds, Mass}: Deals 4d8 damage +1/level to many creatures.

\spellList{Planar Ally, Greater}\textsuperscript{X}: As \spell{lesser planar ally}, but up to 18 HD.

\spellList{Shield of Law}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against chaotic spells.

\spellList{Spell Immunity, Greater}: As \spell{spell immunity}, but up to 8th-level spells.

\spellList{Summon Monster VIII}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{Symbol of Death}\textsuperscript{M}: Triggered rune slays nearby creatures.

\spellList{Symbol of Insanity}\textsuperscript{M}: Triggered rune renders nearby creatures insane.

\spellList{Unholy Aura}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against good spells.

\noindent 1 Cast only to summon from your element's plane.



\subsection{9th-Level Cleric Spells}

\spellList{Astral Projection}\textsuperscript{M}: Projects you and companions onto Astral Plane.

\spellList{Elemental Chariot, Greater}: As \spell{elemental chariot}, but with greater effects. %%

\spellList{Energy Drain}: Subject gains 2d4 negative levels.

\spellList{Etherealness}: Travel to Ethereal Plane with companions.

\spellList{Gate}\textsuperscript{X}: Connects two planes for travel or summoning.

\spellList{Heal, Mass}: As \spell{heal}, but with several subjects.

\spellList{Implosion}: Kills one creature/round.

\spellList{Miracle}\textsuperscript{X}: Requests a deity's intercession.

\spellList{Soul Bind}\textsuperscript{F}: Traps newly dead soul to prevent resurrection.

% \spellList{Storm of Vengeance}: Storm rains acid, lightning, and hail.

\spellList{Summon Monster IX}\footnotemark[1]: Calls extraplanar creature to fight for you.

\spellList{True Resurrection}\textsuperscript{M}: As \spell{resurrection}, plus remains aren't needed.

\noindent 1 Cast only to summon from your element's plane.
