\section{Cleric Domains}

\Domain{Agriculture}
{Earth}
{Whenever a wizard tries to defile the ground with a spell, you can halve the defiled radius with a successful Wisdom check (DC 10 + spell level).}
{
	\item \spellList{Pass without Trace}: One subject/level leaves no tracks.
	\item \spellList{Soften Earth and Stone}: Turns stone to clay or dirt to sand or mud.
	\item \spellList{Plant Growth}: Grows vegetation, improves crops.
	\item \spellList{Wall of Stone}: Creates a stone wall that can be shaped.
	\item \spellList{Transmute Rock to Mud}: Transforms two 3 m cubes per level.
	\item \spellList{Rejuvenate}: Increase the fertility of the land.
	\item \spellList{Transmute Metal to Wood}: Metal within 12 m becomes wood.
	\item \spellList{Antipathy}: Object or location affected by spell repels certain creatures.
	\item \spellList{Heartseeker}\textsuperscript{X}: Creates a deadly piercing weapon.
}

\Domain{Air}
{Air}
{For a total time per day of 1 round per cleric level you possess, you may hold your breath regardless of any effects. You are treated as if you were breathing normally.

This effect occurs automatically as soon as it applies, lasts until it runs out or is no longer needed, and can operate multiple times per day (up to the total daily limit of rounds).}
{
	\item \spellList{Endure Elements}: Exist comfortably in hot or cold environments.
	\item \spellList{Whispering Wind}: Sends a short message 1.5 km/level.
	\item \spellList{Gust of Wind}: Blows away or knocks down smaller creatures.
	\item \spellList{Air Lens}: Directs intensified sunlight at foes within range.
	\item \spellList{Control Winds}: Change wind direction and speed.
	\item \spellList{Drown on Dry Land}: Targets can only breathe water.
	\item \spellList{Sirocco}: You conjure a legendary desert wind.
	\item \spellList{Whirlwind}: Cyclone deals damage and can pick up creatures.
	\item \spellList{Etherealness}: Travel to Ethereal Plane with companions.
}

\Domain{Cleansing}
{Fire}
{Once per day, you may step into a fire the size of a campfire. This fulfills half your daily need for food and water, cleans your body of dirt and filth, cures 1d4 points of damage, and allows for a second save to resist poison.}
{
	\item \spellList{Faerie Fire}: Outlines subjects with light, canceling blur, concealment, and the like.
	\item \spellList{Fire Trap}\textsuperscript{M}: Opened object deals 1d4 +1/level damage.
	\item \spellList{Invisibility Purge}: Dispels invisibility within 1.5 m/level.
	\item \spellList{Clues of Ash}: You receive a vision of an item's destruction.
	\item \spellList{Cleansing Flame}: 1d6/level fire damage (max 10d6).
	\item \spellList{Heroes' Feast}: Food for one creature/level cures and grants combat bonuses.
	\item \spellList{Flame Harvest}: Creates a timed fire trap.
	\item \spellList{Mind Blank}: Subject is immune to mental/emotional magic and scrying.
	\item \spellList{Blazing Wreath}: Shrouds you in elemental flame.
}

\Domain{Cycle}
{Earth}
{You leave no trail and cannot be tracked while in sand or hard earth. You may choose to leave a trail if so desired.}
{
	\item \spellList{Return to the Earth}: Turns dead and undead bodies into dust.
	\item \spellList{Rusting Grasp}: Your touch corrodes iron and alloys.
	\item \spellList{Curse of the Black Sands}: Target leaves black oily footprints.
	\item \spellList{Giant Vermin}: Turns centipedes, scorpions, or spiders into giant vermin.
	\item \spellList{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.
	\item \spellList{Infestation}: Tiny parasites infect creatures within area.
	\item \spellList{Sands of Time}\textsuperscript{F}: Reverses or accelerates aging of a nonliving object.
	\item \spellList{Iron Body}: Your body becomes living iron.
	\item \spellList{Imprisonment}: Entombs subject beneath the earth.
}

\Domain{Decay}
{Silt}
{Once per day, you can control nearby silt to drown a creature unless it succeeds against a Fortitude save (DC 10 + \onehalf your cleric level + your Wis modifier). This ability only works near silt.}
{
	\item \spellList{Death Knell}: Kills dying creature; you gain 1d8 temporary hp, +2 Str and +1 level.
	\item \spellList{Rusting Grasp}: Your touch corrodes iron and alloys.
	\item \spellList{Vampiric Touch}: Touch deals 1d6/two levels damage; caster gains damage as hp.
	\item \spellList{Curse of the Choking Sands}: Victim's touch turns water to dust.
	\item \spellList{Slay Living}: Touch attack kills subject.
	\item \spellList{Drown on Dry Land}: Targets can only breathe water.
	\item \spellList{Sands of Time}\textsuperscript{F}: Reverses or accelerates aging of a nonliving object.
	\item \spellList{Horrid Wilting}: Deals 1d6/level damage within 9 m.
	\item \spellList{Vampiric Youthfulness}: Increases your lifespan at the expense of another's.
}

\Domain{Drought}
{Magma}
{Once per day, you can evaporate up to 20 liters of water per cleric level. You need to touch the water source. This ability takes one hour for each 20 liters of water evaporated.}
{
	\item \spellList{Return to the Earth}: Turns dead and undead bodies into dust.
	\item \spellList{Pyrotechnics}: Turns fire into blinding light or choking smoke.
	\item \spellList{Curse of the Black Sands}: Target leaves black oily footprints.
	\item \spellList{Clues of Ash}: You receive a vision of an item's destruction.
	\item \spellList{Blindscorch}: Fire burns the face of one opponent.
	\item \spellList{Flesh to Stone}: Turns subject creature into statue.
	\item \spellList{Hardening}: Permanently increase by 1/two levels the hardness of an item.
	\item \spellList{Horrid Wilting}: Deals 1d6/level damage within 9 m.
	\item \spellList{Magma Tunnel}: Tunnels through solid rock.
}

\Domain{Earth}
{Earth}
{You can bury yourself beneath loose earth, sand, or top soil for up to a total of eight hours per day. If you slept eight hours buried this way, you heal double the amount of a full night's rest. You may bury yourself multiple times per day (up to the total daily limit of hours).}
{
	\item \spellList{Magic Stone}: Three stones gain +1 on attack rolls, deal 1d6+1 damage.
	\item \spellList{Meld into Stone}: You and your gear merge with stone.
	\item \spellList{Stone Shape}: Sculpts stone into any shape.
	\item \spellList{Spike Stones}: Creatures in area take 1d8 damage, may be slowed.
	\item \spellList{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.
	\item \spellList{Stone Tell}: Talk to natural or worked stone.
	\item \spellList{Create Oasis}: Conjures a temporary oasis.
	\item \spellList{Earthquake}: Intense tremor shakes 24-m radius.
	\item \spellList{Elemental Swarm}\footnotemark[1]: Summons multiple elementals.
}
\noindent 1 Cast as an earth spell only.

\Domain{Fire}
{Fire}
{As a standard action, you may create a flame the size of a match stick, at a range of up to 1.5 m for each two cleric levels (minimum 1.5 m). This ability ignites materials normally. You may use this ability at will.}
{
	\item \spellList{Produce Flame}: 1d6 damage +1/ level, touch or thrown.
	\item \spellList{Pyrotechnics}: Turns fire into blinding light or choking smoke.
	\item \spellList{Continual Flame}\textsuperscript{M}: Makes a permanent, heatless torch.
	\item \spellList{Watch Fire}: Spies through campfires within range.
	\item \spellList{Wall of Fire}: Deals 2d4 fire damage out to 3 m and 1d4 out to 6 m. Passing through wall deals 2d6 damage +1/level.
	\item \spellList{Fire Seeds}: Acorns and berries become grenades and bombs.
	\item \spellList{Fire Storm}: Deals 1d6/level fire damage.
	\item \spellList{Incendiary Cloud}: Cloud deals 4d6 fire damage/round.
	\item \spellList{Meteor Swarm}: Four exploding spheres each deal 6d6 fire damage.
}

\Domain{Forecasting}
{Air}
{You gain the ranged smite power, the supernatural ability to make a single ranged attack with a +4 bonus on attack rolls and a bonus on damage rolls equal to your cleric level (if you hit). You must declare the ranged smite before making the attack. This ability is usable once per day.}
{
	\item \spellList{Feather Fall}: Objects or creatures fall slowly.
	\item \spellList{Wind Wall}: Deflects arrows, smaller creatures, and gases.
	\item \spellList{Eye of the Storm}: Protects 9-m radius from effects of storm for 1 hour/level.
	\item \spellList{Divination}\textsuperscript{M}: Provides useful advice for specific proposed actions.
	\item \spellList{True Seeing}\textsuperscript{M}: See all things as they really are.
	\item \spellList{Ragestorm}\textsuperscript{M}: Summons a storm with high winds, hail, and lightning.
	\item \spellList{Control Weather}: Changes weather in local area.
	\item \spellList{Reverse Gravity}: Objects and creatures fall upward.
	\item \spellList{Storm of Vengeance}: Storm rains acid, lightning, and hail.
}

\Domain{Freedom}
{Air}
{You gain +1 dodge AC against ranged attacks made with missile weapons.}
{
	\item \spellList{Slave Scent}: Divines target's social class.
	\item \spellList{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle). 
	\item \spellList{Fly}: Subject flies at speed of 18 m.
	\item \spellList{Freedom of Movement}: Subject moves normally despite impediments.
	\item \spellList{Plane Shift}\textsuperscript{F}: As many as eight subjects travel to another plane.
	\item \spellList{Wind Walk}: You and your allies turn vaporous and travel fast.
	\item \spellList{Repulsion}: Creatures can't approach you.
	\item \spellList{Storm Legion}: Transports willing creatures via a natural storm.
	\item \spellList{Freedom}: Releases creature from \spell{imprisonment}.
}

\Domain{Growth}
{Rain}
{You move and attack normally over mudded areas.}
{
	\item \spellList{Entangle}: Plants entangle everyone in 12-m radius.
	\item \spellList{Grease}: Makes 3-m square or one object slippery.
	\item \spellList{Plant Growth}: Grows vegetation, improves crops.
	\item \spellList{Freedom of Movement}: Subject moves normally despite impediments.
	\item \spellList{Transmute Rock to Mud}: Transforms two 3 m cubes per level.
	\item \spellList{Rejuvenate}: Increase the fertility of the land.
	\item \spellList{Animate Plants}: One or more plants animate and fight for you.
	\item \spellList{Flash Flood}: Conjures a flood.
	\item \spellList{Miracle}\textsuperscript{X}: Requests a deity's intercession.
}

\Domain{Magma}
{Magma}
{You do not suffer armor check penalties and encumbrance penalties to \skill{Climb} checks.}
{
	\item \spellList{Magic Stone}: Three stones gain +1 on attack rolls, deal 1d6+1 damage.
	\item \spellList{Heat Metal}: Hot metal damages those who touch it.
	\item \spellList{Fire Shield}: Creatures attacking you take fire damage; you're protected from heat or cold.
	\item \spellList{Oil Spray}: A fountain of flammable oil gushes from the ground.
	\item \spellList{Stinking Cloud}: Nauseating vapors, 1 round/level.
	\item \spellList{Flesh to Stone}: Turns subject creature into statue.
	\item \spellList{Fire Storm}: Deals 1d6/level fire damage.
	\item \spellList{Molten}: Melt sand into glass, or rock into magma.
	\item \spellList{Fissure}\textsuperscript{M}: Opens a volcanic fissure in natural stone.
}

\Domain{Mirage}
{Sun}
{You are not affected by the natural light of the sun. You also gain +2 bonus on any save against illusion and magical blinding effects.}
{
	\item \spellList{Color Spray}: Knocks unconscious, blinds, and/or stuns weak creatures.
	\item \spellList{Hypnotic Pattern}: Fascinates (2d4 + level) HD of creatures.
	\item \spellList{Invisibility Purge}: Dispels invisibility within 1.5 m/level.
	\item \spellList{Hallucinatory Terrain}: Makes one type of terrain appear like another (field into forest, or the like).
	\item \spellList{Shining Sands}: Affected sand reflects light, blinding foes.
	\item \spellList{Mislead}: Turns you invisible and creates illusory double.
	\item \spellList{Power Word Blind}: Blinds creature with 200 hp or less.
	\item \spellList{Simulacrum}\textsuperscript{MX}: Creates partially real double of a creature.
	\item \spellList{Screen}: Illusion hides area from vision, scrying.
}

\Domain{Purity}
{Water}
{You gain +4 bonus on Fortitude saving throws against poison.}
{
	\item \spellList{Clear Water}: Doubles the benefit of water.
	\item \spellList{Surface Tension}: Affected water acquires rubbery surface.
	\item \spellList{Clear-river}: Blows aways or knocks creatures.
	\item \spellList{Freedom of Movement}: Subject moves normally despite impediments.
	\item \spellList{Coat of Mists}\textsuperscript{M}: Coalesce a magical mist about the subject's body.
	\item \spellList{Heal}: Cures 10 points/level of damage, all diseases and mental conditions.
	\item \spellList{Spell Turning}: Reflect 1d4+6 spell levels back at caster.
	\item \spellList{Antimagic Field}: Negates magic within 10 ft.
	\item \spellList{Heal, Mass}: As \spell{heal}, but with several subjects.
}

\Domain{Rain}
{Rain}
{You are automatically successful in all Fortitude saves against wind effects from natural weather. You are also never hit by natural lightning.}
{
	\item \spellList{Cooling Canopy}: Summons a cloud to provide shade and prevent dehydration.
	\item \spellList{Fog Cloud}: Fog obscures vision.
	\item \spellList{Call Lightning}: Calls down lightning bolts (3d6 per bolt) from sky.
	\item \spellList{Acid Rain}: Conjures an acidic shower.
	\item \spellList{Water Trap}: Body of water becomes death trap.
	\item \spellList{Call Lightning Storm}: As \spell{call lightning}, but 5d6 damage per bolt.
	\item \spellList{Control Weather}: Changes weather in local area.
	\item \spellList{Storm Legion}: Transports willing creatures via a natural storm.
	\item \spellList{Storm of Vengeance}: Storm rains acid, lightning, and hail.
}

\Domain{Replenishment}
{Water}
{You can turn a skin of water into a special healing potion, after a 1 hour ritual. Anyone who drinks from the skin will be healed 1 point of damage. The holy skin can heal up to 10 people. You can have only one holy skin at a time.

If you are 11th level or higher, you may heal a fallen ally to 1 hit point. The target must be dying or unconscious. This use spends the whole holy skin. }
{
	\item \spellList{Cooling Canopy}: Summons a cloud to provide shade and prevent dehydration.
	\item \spellList{Restoration, Lesser}: Dispels magical ability penalty or repairs 1d4 ability damage.
	\item \spellList{Create Food and Water}: Feeds three humans (or one horse)/level.
	\item \spellList{Control Tides}\footnotemark[1]: Raises, lowers, or parts bodies of water or silt.
	\item \spellList{Sweet Water}: Enhances water with life-preserving properties.
	\item \spellList{Rejuvenate}: Increase the fertility of the land.
	\item \spellList{Create Oasis}: Conjures a temporary oasis.
	\item \spellList{Flash Flood}: Conjures a flood.
	\item \spellList{Heal, Mass}: As \spell{heal}, but with several subjects.
}
\noindent 1 Cast only to control water.

\Domain{Silt}
{Silt}
{For a total time per day of 1 round per cleric level you possess, you can walk on silt as if it was solid. This effect occurs automatically as soon as it applies, lasts until it runs out or is no longer needed, and can operate multiple times per day (up to the total daily limit of rounds).}
{
	\item \spellList{Worm's Breath}\footnotemark[1]: Subjects can breathe underwater, in silt or earth.
	\item \spellList{Curse of the Black Sands}: Target leaves black oily footprints.
	\item \spellList{Sand Spray}: Sprays sand or silt as an area attack.
	\item \spellList{Whirlpool of Doom}: You stir the ground into a whirlpool.
	\item \spellList{Control Tides}\footnotemark[2]: Raises, lowers, or parts bodies of water or silt.
	\item \spellList{Gray Beckoning}: Summons zombies from the Gray.
	\item \spellList{Glass Storm}: Creates a whirlwind of broken glass.
	\item \spellList{Sirocco}: You conjure a legendary desert wind.
	\item \spellList{Storm of Vengeance}: Storm rains acid, lightning, and hail.
}
\noindent 1 Cast only to breathe in silt or earth.

\noindent 2 Cast only to control silt.

\Domain{Sun}
{Sun}
{You are automatically successful in all Fortitude saves against heat from natural weather. You are also treated as if you were continually in the shade for water consumption.}
{
	\item \spellList{Faerie Fire}: Outlines subjects with light, canceling blur, concealment, and the like.
	\item \spellList{Daylight}: 18-m radius of bright light.
	\item \spellList{Searing Light}: Ray deals 1d8/two levels, more against undead.
	\item \spellList{Air Lens}: Directs intensified sunlight at foes within range.
	\item \spellList{Flame Strike}: Smite foes with divine fire (1d6/level damage).
	\item \spellList{Sunstroke}\textsuperscript{F}: Ray attacks induce sunstroke.
	\item \spellList{Sunbeam}: Beam blinds and deals 4d6 damage.
	\item \spellList{Sunburst}: Blinds all within 3 m, deals 6d6 damage.
	\item \spellList{Prismatic Sphere}: As \spell{prismatic wall}, but surrounds on all sides.
}

\Domain{Travel}
{}
{You are always considered to be in a highway for overland movement.}
{
	\item \spellList{Longstrider}: Increases your speed.
	\item \spellList{Whispering Wind}: Sends a short message 1.5 km/level.
	\item \spellList{Phantom Steed}: Magic horse appears for 1 hour/level.
	\item \spellList{Haste}: One creature/level moves faster, +1 on attack rolls, AC, and Reflex saves.
	\item \spellList{Tree Stride}: Step from one tree to another far away.
	\item \spellList{Find the Path}: Shows most direct way to a location.
	\item \spellList{Legend Lore}\textsuperscript{MF}: Lets you learn tales about a person, place, or thing.
	\item \spellList{Discern Location}: Reveals exact location of creature or object.
	\item \spellList{Foresight}: ``Sixth sense'' warns of impending danger.
}

\Domain{Water}
{Water}
{You can extract up to half your daily needs of water from any natural source. Mud, plant, even rock.}
{
	\item \spellList{Worm's Breath}\footnotemark[1]: Subjects can breathe underwater, in silt or earth.
	\item \spellList{Water Shock}: Entraps water with electric charge.
	\item \spellList{Quench}: Extinguishes nonmagical fires or one magic item.
	\item \spellList{Lungs of Water}: Conjures water inside victim's lungs.
	\item \spellList{Water Trap}: Body of water becomes death trap.
	\item \spellList{Waters of Life}\textsuperscript{M}: Absorb another creature's ailments.
	\item \spellList{Water Light}: Water within range emits light.
	\item \spellList{Horrid Wilting}: Deals 1d6/level damage within 9 m.
	\item \spellList{Heartseeker}\textsuperscript{X}: Creates a deadly piercing weapon.
}
\noindent 1 Cast only to breathe underwater.

\Domain{Wrath}
{Fire}
{You gain the ability to ignite your melee weapon in divine flames. Wrath strike deals bonus fire damage equal to twice your cleric level (if you hit). You must declare the wrath strike before making the attack. This ability is usable once per day. This ability breaks nonmetal weapons after the strike, even if it misses.}
{
	\item \spellList{Divine Favor}: You gain attack, damage bonus, +1/three levels.
	\item \spellList{Flame Blade}: Touch attack deals 1d8 +1/two levels damage.
	\item \spellList{Heroism}: Gives +2 bonus on attack rolls, saves, skill checks.
	\item \spellList{Fire Track}: Fiery spark follows tracks.
	\item \spellList{Flame Strike}: Smite foes with divine fire (1d6/level damage).
	\item \spellList{Blade Barrier}: Wall of blades deals 1d6/level damage.
	\item \spellList{Heroism, Greater}: Gives +4 bonus on attack rolls, saves, skill checks; immunity to fear; temporary hp.
	\item \spellList{Confessor's Flame}: Uses threat of flame to extract confession.
	\item \spellList{Conflagration}: Incinerates a living creature and animates its remains.
}