\section{Druid Spells}



\subsection{0-Level Druid Spells (Orisons)}

\spellList{Create Water}: Creates 2 liters/level of pure water.

\spellList{Cure Minor Wounds}: Cures 1 point of damage.

\spellList{Defiler Scent}: Smells the presence or absence of defilers.

\spellList{Detect Magic}: Detects spells and magic items within 18 m.

\spellList{Detect Poison}: Detects poison in one creature or object.

\spellList{Flare}: Dazzles one creature ($-1$ penalty on attack rolls).

\spellList{Guidance}: +1 on one attack roll, saving throw, or skill check.

\spellList{Know Direction}: You discern north.

\spellList{Light}: Object shines like a torch.

\spellList{Mending}: Makes minor repairs on an object.

\spellList{Nurturing Seeds}: Makes 10 seeds or cuttings hardy and easy to transplant.

\spellList{Purify Food and Drink}: Purifies 0.3 m$^3$/level of food or water.

\spellList{Read Magic}: Read scrolls and spellbooks.

\spellList{Resistance}: Subject gains +1 bonus on saving throws.

\spellList{Virtue}: Subject gains 1 temporary hp.



\subsection{1st-Level Druid Spells}

\spellList{Backlash}\textsuperscript{M}: 1d6+1 damage/2 levels to defilers.

\spellList{Black Cairn}\textsuperscript{F}: Locates a corpse nearby.

\spellList{Calm Animals}: Calms (2d4 + level) HD of animals.

\spellList{Charm Animal}: Makes one animal your friend.

\spellList{Cooling Canopy}: Summons a cloud to provide shade and prevent dehydration.

\spellList{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\spellList{Detect Animals or Plants}: Detects kinds of animals or plants.

\spellList{Detect Snares and Pits}: Reveals natural or primitive traps.

\spellList{Detect Undead}: Reveals undead within 18 meters.

\spellList{Endure Elements}: Exist comfortably in hot or cold environments.

\spellList{Entangle}: Plants entangle everyone in 12-m-radius.

\spellList{Faerie Fire}: Outlines subjects with light, canceling blur, concealment, and the like.

\spellList{Goodberry}: 2d4 berries each cure 1 hp (max 8 hp/24 hours).

\spellList{Hide from Animals}: Animals can't perceive one subject/level.

\spellList{Jump}: Subject gets bonus on \skill{Jump} checks.

\spellList{Longstrider}: Your speed increases by 3 m.

\spellList{Magic Fang}: One natural weapon of subject creature gets +1 on attack and damage rolls.

\spellList{Magic Stone}: Three stones gain +1 on attack rolls, deal 1d6+1 damage.

\spellList{Obscuring Mist}: Fog surrounds you.

\spellList{Pass without Trace}: One subject/level leaves no tracks.

\spellList{Plant Renewal}: Brings one plant back from near destruction.

\spellList{Produce Flame}: 1d6 damage +1/level, touch or thrown.

\spellList{Proof Against Undeath}: Prevents dead subject from being raised as undead.

\spellList{Shillelagh}: Cudgel or quarterstaff becomes +1 weapon and deals damage as if two sizes larger.

\spellList{Speak with Animals}: You can communicate with animals.

\spellList{Summon Nature's Ally I}: Calls creature to fight.



\subsection{2nd-Level Druid Spells}

\spellList{Animal Messenger}: Sends a Tiny animal to a specific place.

\spellList{Animal Trance}: Fascinates 2d6 HD of animals.

\spellList{Barkskin}: Grants +2 (or higher) enhancement to natural armor.

\spellList{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\spellList{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\spellList{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\spellList{Chill Metal}: Cold metal damages those who touch it.

\spellList{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\spellList{Fire Trap}\textsuperscript{M}: Opened object deals 1d4 +1/level damage.

\spellList{Flame Blade}: Touch attack deals 1d8 +1/two levels damage.

\spellList{Flaming Sphere}: Creates rolling ball of fire, 2d6 damage, lasts 1 round/level.

\spellList{Fog Cloud}: Fog obscures vision.

\spellList{Gust of Wind}: Blows away or knocks down smaller creatures.

\spellList{Heat Metal}: Make metal so hot it damages those who touch it.

\spellList{Hold Animal}: Paralyzes one animal for 1 round/level.

\spellList{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\spellList{Reduce Animal}: Shrinks one willing animal.

\spellList{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\spellList{Restoration, Lesser}: Dispels magical ability penalty or repairs 1d4 ability damage.

\spellList{Soften Earth and Stone}: Turns stone to clay or dirt to sand or mud.

\spellList{Spider Climb}: Grants ability to walk on walls and ceilings.

\spellList{Summon Nature's Ally II}: Calls creature to fight.

\spellList{Summon Swarm}: Summons swarm of bats, rats, or spiders.

\spellList{Tree Shape}: You look exactly like a tree for 1 hour/level.

\spellList{Warp Wood}: Bends wood (shaft, handle, door, plank).

\spellList{Wood Shape}: Rearranges wooden objects to suit you.



\subsection{3rd-Level Druid Spells}

\spellList{Boneclaw's Cut}\textsuperscript{F}: Deals damage that continues to cause bleeding damage.%%

\spellList{Call Lightning}: Calls down lightning bolts (3d6 per bolt) from sky.

\spellList{Claws of the Tembo}: Deals 1d6 Str damage and transfers hp.

\spellList{Clear-river}: Blows aways or knocks creatures.

\spellList{Contagion}: Infects subject with chosen disease.

\spellList{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\spellList{Curse of the Black Sands}: Target leaves black oily footprints.%%

\spellList{Daylight}: 18-m radius of bright light.

\spellList{Deeper Darkness}: Object sheds absolute darkness in 18-m radius.

\spellList{Diminish Plants}: Reduces size or blights growth of normal plants.

\spellList{Dominate Animal}: Subject animal obeys silent mental commands.

\spellList{Eye of the Storm}: Protects 9-m radius from effects of storm for 1 hour/level.%%

\spellList{Magic Fang, Greater}: One natural weapon of subject creature gets +1/four levels on attack and damage rolls (max +5).

\spellList{Meld into Stone}: You and your gear merge with stone.

\spellList{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\spellList{Plant Growth}: Grows vegetation, improves crops.

\spellList{Poison}: Touch deals 1d10 Con damage, repeats in 1 min.

\spellList{Protection from Energy}: Absorb 12 points/level of damage from one kind of energy.

\spellList{Quench}: Extinguishes nonmagical fires or one magic item.

\spellList{Remove Curse}: Frees object or person from curse.

\spellList{Remove Disease}: Cures all diseases affecting subject.

\spellList{Return to the Earth}: Turns dead and undead bodies into dust.

\spellList{Searing Light}: Ray deals 1d8/two levels against undead.

\spellList{Sleet Storm}: Hampers vision and movement.

\spellList{Snare}: Creates a magic booby trap.

\spellList{Speak with Plants}: You can talk to normal plants and plant creatures.

\spellList{Spike Growth}: Creatures in area take 1d4 damage, may be slowed.

\spellList{Stone Shape}: Sculpts stone into any shape.

\spellList{Summon Nature's Ally III}: Calls creature to fight.

\spellList{Surface Walk}: Subject treads on unstable surfaces as if solid.

% \spellList{Water Breathing}: Subjects can breathe underwater.

\spellList{Wind Wall}: Deflects arrows, smaller creatures, and gases.

\spellList{Worm's Breath}: Subjects can breathe underwater, in silt, or earth.

\spellList{Zombie Berry}: 1d4 berries from the zombie plant become attuned to you.



\subsection{4th-Level Druid Spells}

\spellList{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle).

\spellList{Antiplant Shell}: Keeps animated plants at bay.

\spellList{Blight}: Withers one plant or deals 1d6/level damage to plant creature.

\spellList{Command Plants}: Sway the actions of one or more plant creatures.

\spellList{Control Tides}: Raises, lowers, or parts bodies of water or silt.

\spellList{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\spellList{Dispel Magic}: Cancels spells and magical effects.

\spellList{Flame Strike}: Smite foes with divine fire (1d6/level damage).

\spellList{Freedom of Movement}: Subject moves normally despite impediments.

\spellList{Giant Vermin}: Turns centipedes, scorpions, or spiders into giant vermin.

\spellList{Ice Storm}: Hail deals 5d6 damage in cylinder 12 m across.

\spellList{Klar's Heart}: Enhances combat abilities of all creatures within range.

\spellList{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.

\spellList{Reincarnate}: Brings dead subject back in a random body.

\spellList{Repel Vermin}: Insects, spiders, and other vermin stay 3 m away.

\spellList{Rusting Grasp}: Your touch corrodes iron and alloys.

\spellList{Scrying}\textsuperscript{F}: Spies on subject from a distance.

\spellList{Spike Stones}: Creatures in area take 1d8 damage, may be slowed.

\spellList{Summon Nature's Ally IV}: Calls creature to fight.



\subsection{5th-Level Druid Spells}

\spellList{Animal Growth}: One animal/two levels doubles in size.

\spellList{Atonement}: Removes burden of misdeeds from subject.

\spellList{Awaken}\textsuperscript{X}: Animal or tree gains human intellect.

\spellList{Baleful Polymorph}: Transforms subject into harmless animal.

\spellList{Braxatskin}: Your skin hardens, granting armor bonus and damage reduction.

\spellList{Call Lightning Storm}: As call lightning, but 5d6 damage per bolt.

\spellList{Cleansing Flame}: 1d6/level fire damage (max 10d6).

\spellList{Coat of Mists}\textsuperscript{M}: Coalesce a magical mist about the subject's body.

\spellList{Commune with Nature}: Learn about terrain for 1.5 kilometer/level.

\spellList{Control Winds}: Change wind direction and speed.

\spellList{Conversion}\textsuperscript{FX}: Removes burden of acts of defiling from a wizard.

\spellList{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\spellList{Death Ward}: Grants immunity to all death spells and negative energy effects.

\spellList{Groundflame}: Mist deals 1d6/level acid damage (max 15d6).

\spellList{Hallow}\textsuperscript{M}: Designates location as holy.

\spellList{Insect Plague}: Locust swarms attack creatures.

\spellList{Mark of Justice}: Designates action that will trigger curse on subject.

\spellList{Rejuvenate}: Increase the fertility of the land.

\spellList{Righteous Might}: Your size increases, and you gain +4 Str.

\spellList{Skyfire}: Three exploding spheres each deal 3d6 fire damage.

\spellList{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.

\spellList{Summon Nature's Ally V}: Calls creature to fight.

\spellList{Transmute Mud to Rock}: Transforms two 3-m cubes per level.

\spellList{Transmute Rock to Mud}: Transforms two 3-m cubes per level.

\spellList{Tree Stride}: Step from one tree to another far away.

\spellList{Unhallow}\textsuperscript{M}: Designates location as unholy.

\spellList{Wall of Fire}: Deals 2d4 fire damage out to 3 m and 1d4 out to 6 m. Passing through wall deals 2d6 damage +1/level.

\spellList{Wall of Thorns}: Thorns damage anyone who tries to pass.



\subsection{6th-Level Druid Spells}

\spellList{Allegiance of the Land}: Grants bonus to AC, temporary hit points, and energy resistance.

\spellList{Antilife Shell}: 3-m radius field hedges out living creatures.

\spellList{Awaken Water Spirits}: Gives sentience to a natural body of water.

\spellList{Bear's Endurance, Mass}: As bear's endurance, affects one subject/ level.

\spellList{Bull's Strength, Mass}: As bull's strength, affects one subject/level.

\spellList{Cat's Grace, Mass}: As cat's grace, affects one subject/level.

\spellList{Create Oasis}: Conjures a temporary oasis.

\spellList{Cure Light Wounds, Mass}: Cures 1d8 damage +1/level for many creatures.

\spellList{Dispel Magic, Greater}: As \spell{dispel magic}, but +20 on check.

\spellList{Find the Path}: Shows most direct way to a location.

\spellList{Fire Seeds}: Acorns and berries become grenades and bombs.

\spellList{Infestation}: Tiny parasites infect creatures within area.

\spellList{Ironwood}: Magic wood is strong as steel.

\spellList{Liveoak}: Oak becomes treant guardian.

\spellList{Move Earth}: Digs trenches and builds hills.

\spellList{Owl's Wisdom, Mass}: As owl's wisdom, affects one subject/level.

\spellList{Raise Dead}\textsuperscript{M}: Restores life to subject who died up to 1 day/level ago.

\spellList{Repel Wood}: Pushes away wooden objects.

\spellList{Spellstaff}: Stores one spell in wooden quarterstaff.

\spellList{Stone Tell}: Talk to natural or worked stone.

\spellList{Summon Nature's Ally VI}: Calls creature to fight.

\spellList{Transport via Plants}: Move instantly from one plant to another of the same kind.

\spellList{Wall of Stone}: Creates a stone wall that can be shaped.



\subsection{7th-Level Druid Spells}

\spellList{Animate Plants}: One or more plants animate and fight for you.

\spellList{Changestaff}: Your staff becomes a treant on command.

\spellList{Control Weather}: Changes weather in local area.

\spellList{Creeping Doom}: Swarms of centipedes attack at your command.

\spellList{Cure Moderate Wounds, Mass}: Cures 2d8 damage +1/level for many creatures.

\spellList{Fire Storm}: Deals 1d6/level fire damage.

\spellList{Heal}: Cures 10 points/level of damage, all diseases and mental conditions.

\spellList{Scrying, Greater}: As scrying, but faster and longer.

\spellList{Summon Nature's Ally VII}: Calls creature to fight.

\spellList{Sunbeam}: Beam blinds and deals 4d6 damage.

\spellList{Transmute Metal to Wood}: Metal within 12 m becomes wood.

\spellList{True Seeing}\textsuperscript{M}: Lets you see all things as they really are.

\spellList{Waters of Life}\textsuperscript{M}: Absorb another creature's ailments.

\spellList{Wind Walk}: You and your allies turn vaporous and travel fast.



\subsection{8th-Level Druid Spells}

\spellList{Animal Shapes}: One ally/level polymorphs into chosen animal.

\spellList{Control Plants}: Control actions of one or more plant creatures.

\spellList{Cure Serious Wounds, Mass}: Cures 3d8 damage +1/level for many creatures.

\spellList{Earthquake}: Intense tremor shakes 24-m radius.

\spellList{Finger of Death}: Kills one subject.

\spellList{Flame Harvest}: Creates a timed fire trap.

\spellList{Repel Metal or Stone}: Pushes away metal and stone.

\spellList{Reverse Gravity}: Objects and creatures fall upward.

\spellList{Sirocco}: You conjure a legendary desert wind.

\spellList{Summon Nature's Ally VIII}: Calls creature to fight.

\spellList{Sunburst}: Blinds all within 3 m, deals 6d6 damage.

\spellList{Whirlwind}: Cyclone deals damage and can pick up creatures.

\spellList{Word of Recall}: Teleports you back to designated place.



\subsection{9th-Level Druid Spells}

\spellList{Antipathy}: Object or location affected by spell repels certain creatures.

\spellList{Cure Critical Wounds, Mass}: Cures 4d8 damage +1/level for many creatures.

\spellList{Elemental Swarm}: Summons multiple elementals.

\spellList{Flash Flood}: Conjures a flood.

\spellList{Foresight}: ``Sixth sense'' warns of impending danger.

\spellList{Heartseeker}\textsuperscript{X}: Creates a deadly piercing weapon.

\spellList{Regenerate}: Subject's severed limbs grow back, cures 4d8 damage +1/level (max +35).

\spellList{Shambler}: Summons 1d4+2 shambling mounds to fight for you.

\spellList{Shapechange}\textsuperscript{F}: Transforms you into any creature, and change forms once per round.

\spellList{Storm Legion}: Transports willing creatures via a natural storm.

\spellList{Storm of Vengeance}: Storm rains acid, lightning, and hail.

\spellList{Summon Nature's Ally IX}: Calls creature to fight.

\spellList{Swarm of Anguish}: Transforms you into a swarm of agony beetles.

\spellList{Sympathy}\textsuperscript{M}: Object or location attracts certain creatures.

\spellList{Wild Lands}: Attract wild creatures to an area.