\section{Elemental Champion Spells}




\subsection{1st-Level Elemental Champion Spells}

\spellList{Bane}: Enemies take $-1$ on attack rolls and saves against fear.

\spellList{Bless}: Allies gain +1 on attack rolls and saves against fear.

\spellList{Bless Element}\textsuperscript{M}: Makes holy element. %%

\spellList{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.

\spellList{Create Element}: Create a small amount of patron element. %%

\spellList{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\spellList{Curse Element}\textsuperscript{M}: Makes unholy element. %%

\spellList{Detect Poison}: Detects poison in one creature or object.

\spellList{Divine Favor}: You gain +1 per three levels on attack and damage rolls.

\spellList{Endure Elements}: Exist comfortably in hot or cold environments.

\spellList{Guidance}: +1 on one attack roll, saving throw, or skill check.

\spellList{Inflict Light Wounds}: Touch deals 1d8 damage +1/level (max +5).

\spellList{Magic Weapon}: Weapon gains +1 bonus.

\spellList{Purify Food and Drink}: Purifies 30 cm$^3$/level of food or water.

\spellList{Remove Fear}: Suppresses fear or gives +4 on saves against fear for one subject + one per four levels.

\spellList{Sanctuary}: Opponents can't attack you, and you can't attack.

\spellList{Shield of Faith}: Aura grants +2 or higher deflection bonus.

\spellList{True Strike}: +20 on your next attack roll.




\subsection{2nd-Level Elemental Champion Spells}

\spellList{Align Weapon}: Weapon becomes good, evil, lawful, or chaotic.

\spellList{Augury}\textsuperscript{MF}: Learns whether an action will be good or bad.

\spellList{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\spellList{Bull's Strength}: Subject gains +4 to Str for 1 min./level.

\spellList{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\spellList{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\spellList{Eagle's Splendor}: Subject gains +4 to Cha for 1 min./level.

\spellList{Inflict Moderate Wounds}: Touch attack, 2d8 damage +1/level (max +10).

\spellList{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.




\subsection{3rd-Level Elemental Champion Spells}

\spellList{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\spellList{Dispel Magic}: Cancels spells and magical effects.

\spellList{Elemental Armor}: Armor or shield gains enhancement bonus and special quality. %%

\spellList{Elemental Weapon}: Weapon gains enhancement bonus and special quality. %%

\spellList{Haste}: One creature/level moves faster, +1 on attack rolls, AC, and Reflex saves.

\spellList{Magic Weapon, Greater}: +1 bonus/four levels (max +5).

\spellList{Inflict Serious Wounds}: Touch attack, 3d8 damage +1/level (max +15).

\spellList{Surface Walk}: Subject treads on unstable surfaces as if solid. %%

\spellList{Worm's Breath}: Subjects can breathe underwater, in silt or earth. %%




\subsection{4th-Level Elemental Champion Spells}

\spellList{Bestow Curse}: $-6$ to an ability score; $-4$ on attack rolls, saves, and checks; or 50\% chance of losing each action.

\spellList{Cure Critical Wounds}: Cures 4d8 damage +1/level (max +20).

\spellList{Death Ward}: Grants immunity to death spells and negative energy effects.

\spellList{Divination}\textsuperscript{M}: Provides useful advice for specific proposed actions.

\spellList{Divine Power}: You gain attack bonus, +6 to Str, and 1 hp/level.

\spellList{Freedom of Movement}: Subject moves normally despite impediments.

\spellList{Inflict Critical Wounds}: Touch attack, 4d8 damage +1/level (max +20).
