\section{Ranger Spells}



\subsection{1st-Level Ranger Spells}

\spellList{Alarm}: Wards an area for 2 hours/level.

\spellList{Animal Messenger}: Sends a Tiny animal to a specific place.

\spellList{Calm Animals}: Calms (2d4 + level) HD of animals.

\spellList{Charm Animal}: Makes one animal your friend.

\spellList{Cooling Canopy}: Summons a cloud to provide shade and prevent dehydration. %%

\spellList{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\spellList{Detect Animals or Plants}: Detects kinds of animals or plants.

\spellList{Detect Poison}: Detects poison in one creature or object.

\spellList{Detect Snares and Pits}: Reveals natural or primitive traps.

\spellList{Endure Elements}: Exist comfortably in hot or cold environments.

\spellList{Entangle}: Plants entangle everyone in 12-m radius circle.

\spellList{Hide from Animals}: Animals can't perceive one subject/level.

\spellList{Jump}: Subject gets bonus on Jump checks.

\spellList{Longstrider}: Increases your speed.

\spellList{Magic Fang}: One natural weapon of subject creature gets +1 on attack and damage rolls.

\spellList{Nurturing Seeds}: Makes 10 seeds or cuttings hardy and easy to transplant. %%

\spellList{Pass without Trace}: One subject/level leaves no tracks.

\spellList{Plant Renewal}: Brings one plant back from near destruction. %%

\spellList{Read Magic}: Read scrolls and spellbooks.

\spellList{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\spellList{Speak with Animals}: You can communicate with animals.

\spellList{Summon Nature's Ally I}: Calls animal to fight for you.



\subsection{2nd-Level Ranger Spells}

\spellList{Barkskin}: Grants +2 (or higher) enhancement to natural armor.

\spellList{Bear's Endurance}: Subject gains +4 to Con for 1 min./level.

\spellList{Cat's Grace}: Subject gains +4 to Dex for 1 min./level.

\spellList{Cure Light Wounds}: Cures 1d8 damage +1/level (max +5).

\spellList{Echo of the Lirr}: Stuns creatures in a cone. %%

\spellList{Footsteps of the Quarry}\textsuperscript{M}: Track a specific creature or person. %%

\spellList{Hold Animal}: Paralyzes one animal for 1 round/level.

\spellList{Owl's Wisdom}: Subject gains +4 to Wis for 1 min./level.

\spellList{Protection from Energy}: Absorb 12 points/level of damage from one kind of energy.

\spellList{Snare}: Creates a magic booby trap.

\spellList{Speak with Plants}: You can talk to normal plants and plant creatures.

\spellList{Spike Growth}: Creatures in area take 1d4 damage, may be slowed.

\spellList{Sting of the Gold Scorpion}: Enlivens scorpion barb to strike with poison of real scorpion once. %%

\spellList{Summon Nature's Ally II}: Calls animal to fight for you.

\spellList{Wind Wall}: Deflects arrows, smaller creatures, and gases.



\subsection{3rd-Level Ranger Spells}

% \spellList{Water Walk}: Subject treads on water as if solid.

\spellList{Claws of the Tembo}: Deals 1d6 Str damage and transfers hp. %%

\spellList{Command Plants}: Sway the actions of one or more plant creatures.

\spellList{Cure Moderate Wounds}: Cures 2d8 damage +1/level (max +10).

\spellList{Darkvision}: See 18 m in total darkness.

\spellList{Diminish Plants}: Reduces size or blights growth of normal plants.

\spellList{Eye of the Storm}: Protects 9 m radius from effects of storm for 1 hour/level. %%

\spellList{Magic Fang, Greater}: One natural weapon of subject creature gets +1/three caster levels on attack and damage rolls (max +5).

\spellList{Neutralize Poison}: Immunizes subject against poison, detoxifies venom in or on subject.

\spellList{Plant Growth}: Grows vegetation, improves crops.

\spellList{Reduce Animal}: Shrinks one willing animal.

\spellList{Remove Disease}: Cures all diseases affecting subject.

\spellList{Repel Vermin}: Insects, spiders, and other vermin stay 3 m away.

\spellList{Summon Nature's Ally III}: Calls animal to fight for you.

\spellList{Surface Walk}: Subject treads on unstable surfaces as if solid. %%

\spellList{Tree Shape}: You look exactly like a tree for 1 hour/level.

\spellList{Worm's Breath}: Subjects can breathe underwater, in silt or earth. %%



\subsection{4th-Level Ranger Spells}

\spellList{Animal Growth}: One animal/two levels doubles in size.

\spellList{Commune with Nature}: Learn about terrain for 1 mile/level.

\spellList{Cure Serious Wounds}: Cures 3d8 damage +1/level (max +15).

\spellList{Freedom of Movement}: Subject moves normally despite impediments.

\spellList{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.

\spellList{Summon Nature's Ally IV}: Calls animal to fight for you.

\spellList{Tree Stride}: Step from one tree to another far away.
