\section{Templar Spells}



\subsection{0-Level Templar Spells (Orisons)}

\spellList{Cure Minor Wounds}: Cures 1 point of damage.

\spellList{Defiler Scent}: Smells presence or absence of defilers.

\spellList{Detect Magic}: Detects spells and magical items within 18 m.

\spellList{Detect Poison}: Detects poison in one creature or small object.

\spellList{Guidance}: +1 on one attack roll, saving throw, or skill check.

\spellList{Inflict Minor Wounds}: Touch attack, 1 point of damage.

\spellList{Light}: Object shines like a torch.

\spellList{Mending}: Makes minor repairs on an object.

\spellList{Read Magic}: Read scrolls and spellbooks

\spellList{Resistance}: Subject gains +1 on saving throws.

\spellList{Virtue}: Subject gains 1 temporary hp.



\subsection{1st-Level Templar Spells}

\spellList{Black Cairn}\textsuperscript{F}: Locates a corpse nearby.

\spellList{Command}: One subject obeys selected command for 1 round.

\spellList{Comprehend Languages}: Understand all spoken and written languages.

\spellList{Cure Light Wounds}: Cures 1d8+1/level damage (max +5).

\spellList{Deathwatch}: Sees how wounded subjects within 9 m are.

\spellList{Detect Undead}: Reveals undead within 18 m.

\spellList{Divine Favor}: You gain attack, damage bonus, +1/three levels.

\spellList{Doom}: One subject suffers $-2$ on attacks, damage, saves, and checks.

\spellList{Endure Elements}: Exist comfortably in hot or cold environments.

\spellList{Hand of the Sorcerer-King}: Protects caster from spells.

\spellList{Hide From Undead}: Undead can't perceive one subject/level.

\spellList{Inflict Light Wounds}: Touch deals 1d8 damage +1/level (max +5).

\spellList{Remove Fear}: +4 on saves against fear for one subject +1/four levels.

\spellList{Protection from Evil/Good}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.

\spellList{Shield of Faith}: Aura grants +2 or higher deflection bonus.



\subsection{2nd-Level Templar Spells}

\spellList{Battlefield Healing}: Stabilizes one creature/level.

\spellList{Bear's Endurance}: Subject gains +4 Con for 1 min./level.

\spellList{Cure Moderate Wounds}: Cures 2d8+1/level damage (max +10).

\spellList{Delay Poison}: Stops poison from harming subject for 1 hour/level.

\spellList{Enthrall}: Captivates all within 30 m + 3 m/level.

\spellList{Footsteps of the Quarry}\textsuperscript{M}: Track a specific creature or person.

\spellList{Hold Person}: Holds one person helpless; 1 round/level.

\spellList{Inflict Moderate Wounds}: Touch attack, 2d8 damage +1/level (max +10).

\spellList{Remove Paralysis}: Frees one or more creatures from paralysis, hold, or slow.

\spellList{Resist Energy}: Ignores 10 (or more) points of damage/attack from specified energy type.

\spellList{Restoration, Lesser}: Dispels magic ability penalty or repairs 1d4 ability damage.

\spellList{Return to the Earth}: Turns dead and undead bodies into dust.

\spellList{Silence}: Negates sound in 4.5-mradius.

\spellList{Undetectable Alignment}: Conceals alignment for 24 hours.

\spellList{Zone of Truth}: Subjects within range cannot lie.



\subsection{3rd-Level Templar Spells}

\spellList{Cure Serious Wounds}: Cures 3d8+1/level damage (max +15).

\spellList{Dedication}: Allows target to avoid sleep, consume half food and water, and +1 to attack, damage, saves, ability, and skill checks while pursuing a specified task.

\spellList{Discern Lies}: Reveals deliberate falsehoods.

\spellList{Dispel Magic}: Cancels magical spells and effects.

\spellList{Glyph of Warding}: Inscription harms those who pass it.

\spellList{Image of the Sorcerer-King}: Touched creatures must save or become affected by cause fear.

\spellList{Inflict Serious Wounds}: Touch attack, 3d8 damage +1/level (max +15).

\spellList{Lightning Bolt}: Electricity deals 1d6/level damage.

\spellList{Locate Object}: Senses direction toward object (specific or type).

\spellList{Magic Circle against Evil/Good}: As \emph{protection} spells, but 3-m radius and 10 min./level.

\spellList{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.

\spellList{Protection from Energy}: Absorb 12 points/level of damage from one kind of energy.

\spellList{Remove Disease}: Cures all diseases affecting subject.

\spellList{Sand Pit}: Excavates sand in a 9 m wide and 15 m deep cone.

\spellList{Speak with Dead}: Corpse answers one question/two levels.

\spellList{Surface Walk}: Subject treads on unstable surfaces as if solid.

\spellList{Wind Wall}: Deflects arrows, smaller creatures, and gases.

\spellList{Worm's Breath}: Subjects can breathe underwater, in silt, or earth.



\subsection{4th-Level Templar Spells}

\spellList{Air Walk}: Subject treads on air as if solid (climb at 45-degree angle).

\spellList{Command, Greater}: As command, but affects one subject/level.

\spellList{Cure Critical Wounds}: Cures 4d8+1/level damage (max +20).

\spellList{Dimensional Anchor}: Bars extradimensional movement.

\spellList{Fool's Feast}: Enhances food for one creature/level and blesses.

\spellList{Freedom of Movement}: Subject moves normally despite impediments.

\spellList{Geas, Lesser}: Commands subject of 7 HD or less.

\spellList{Inflict Critical Wounds}: Touch attack, 4d8 damage +1/level (max +20).

\spellList{Mage Seeker}\textsuperscript{F}: Locate nearby wizard.

\spellList{Magic Weapon, Greater}: +1 bonus/four levels (max +5).

\spellList{Neutralize Poison}: Detoxifies venom in or on subject.

\spellList{Sending}: Delivers a short message anywhere, instantly.

\spellList{Status}: Monitors condition, position of allies.

\spellList{Tongues}: Speak any language.

\spellList{Wrath of the Sorcerer-King}: Know if a creature has broken the law, and punish him.



\subsection{5th-Level Templar Spells}

\spellList{Air Lens}: Directs intensified sunlight at foes within range.

\spellList{Break Enchantment}: Frees subjects from enchantments, alterations, curses, and petrifaction.

\spellList{Elemental Strike}: Smites foes with 1d6/level of divine and elemental energy (max 15d6).

\spellList{Fire Track}: Fiery spark follows tracks.

\spellList{Klar's Heart}: Enhances combat abilities of all creatures within range.

\spellList{Mark of Justice}: Designates action that will trigger curse on subject.

\spellList{Scrying}: Spies on subject from a distance.

\spellList{Symbol of Pain}\textsuperscript{M}: Triggered rune wracks nearby creatures with pain.

\spellList{Symbol of Sleep}\textsuperscript{M}: Triggered rune puts nearby creatures into catatonic slumber.

\spellList{True Seeing}: See all things as they really are.



\subsection{6th-Level Templar Spells}

\spellList{Control Tides}: Raises, lowers, or parts bodies of water or silt.

\spellList{Dispel Magic, Greater}: As \spell{dispel magic}, but up to +20 on check.

\spellList{Forbiddance}\textsuperscript{M}: Blocks planar travel, damages creatures of different alignment.

\spellList{Glyph of Warding, Greater}: As glyph of warding, but up to 10d8 damage or 6th level spell.

\spellList{Raise Dead}: Restores life to subject who died up to 1 day/level ago.

\spellList{Symbol of Fear}\textsuperscript{M}: Triggered rune panics nearby creatures.

\spellList{Symbol of Persuasion}\textsuperscript{M}: Triggered rune charms nearby creatures.

\spellList{Wisdom of the Sorcerer-King}: Apply metamagic to one spell of up to 4th level.

\spellList{Word of Recall}: Teleports you back to designated place.



\subsection{7th-Level Templar Spells}

\spellList{Confessor's Flame}: Uses threat of flame to extract confession.

\spellList{Crusade}: Allies receive +4 bonus to attack rolls, damage rolls, and saving throws, 2d8 hit points, and immunity to magical fear.

\spellList{Refuge}: Alters item to transport its possessor to you.

\spellList{Scrying, Greater}: As scrying, but faster and longer.

\spellList{Symbol of Stunning}\textsuperscript{M}: Triggered rune stuns nearby creatures.

\spellList{Symbol of Weakness}\textsuperscript{M}: Triggered rune weakens nearby creatures.



\subsection{8th-Level Templar Spells}

\spellList{Antipathy}: Object or location affected by spell repels certain creatures.

\spellList{Discern Location}: Exact location of creature or object.

\spellList{Finger of Death}: Kills one subject.

\spellList{Poisoned Gale}: Poisonous cloud (3 m wide, 3 m high) emanates out from you to the extreme of the range.

\spellList{Regenerate}: Subject's severed limbs grow back.

\spellList{Symbol of Death}\textsuperscript{M}: Triggered rune slays nearby creature.



\subsection{9th-Level Templar Spells}

\spellList{Energy Drain}: Subject gains 2d4 negative levels.

\spellList{Gray Rift}: A hovering rift to the Gray bolsters
undead.

\spellList{Power Word, Blind}: Blinds 200 hp worth of creatures.

\spellList{Soul Bind}: Traps newly dead soul to prevent
resurrection.