\section{Templar Domains}

\Domain{Animal}
{Lalali-Puy}
{You can use \spell{speak with animals} once per day as a spell-like ability.

Add \skill{Knowledge} (nature) to your list of cleric class skills.}
{
	\item \spellList{Calm Animals}: Calms (2d4 + level) HD of animals.
	\item \spellList{Hold Animal}: Paralyzes one animal for 1 round/level.
	\item \spellList{Dominate Animal}: Subject animal obeys silent mental commands.
	\item \spellList{Summon Nature's Ally IV}\footnotemark[1]: Calls creature to fight.
	\item \spellList{Commune with Nature}: Learn about terrain for 1 mile/level.
	\item \spellList{Antilife Shell}: 3-m field hedges out living creatures.
	\item \spellList{Animal Shapes}: One ally/level polymorphs into chosen animal.
	\item \spellList{Summon Nature's Ally VIII}\footnotemark[1]: Calls creature to fight.
	\item \spellList{Shapechange}\textsuperscript{F}: Transforms you into any creature, and change forms once per round.
}
\noindent 1 Can only summon animals.


\Domain{Chaos}
{Abalach-Re, Daskinor}
{You cast chaos spells at +1 caster level.}
{
	\item \spellList{Protection from Law}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
	\item \spellList{Shatter}: Sonic vibration damages objects or crystalline creatures.
	\item \spellList{Magic Circle against Law}: As \spell{protection spells}, but 3-m radius and 10 min./level.
	\item \spellList{Chaos Hammer}: Damages and staggers lawful creatures.
	\item \spellList{Dispel Law}: +4 bonus against attacks by lawful creatures.
	\item \spellList{Animate Objects}: Objects attack your foes.
	\item \spellList{Word of Chaos}: Kills, confuses, stuns, or deafens nonchaotic subjects.
	\item \spellList{Cloak of Chaos}\textsuperscript{F}: +4 to AC, +4 resistance, SR 25 against lawful spells.
	\item \spellList{Summon Monster IX}\footnotemark[1]: Calls extraplanar creature to fight for you.
}
\noindent 1 Cast as a chaos spell only.

\Domain{Charm}
{Abalach-Re}
{You can boost your Charisma by 4 points once per day. Activating this power is a free action. The Charisma increase lasts 1 minute.}
{
	\item \spellList{Charm Person}: Makes one person your friend.
	\item \spellList{Calm Emotions}: Calms creatures, negating emotion effects.
	\item \spellList{Suggestion}: Compels subject to follow stated course of action.
	\item \spellList{Heroism}: Gives +2 on attack rolls, saves, skill checks.
	\item \spellList{Charm Monster}: Makes monster believe it is your ally.
	\item \spellList{Geas/Quest}: As \spell{lesser geas}, plus it affects any creature.
	\item \spellList{Insanity}: Subject suffers continuous confusion.
	\item \spellList{Demand}: As \spell{sending}, plus you can send suggestion.
	\item \spellList{Dominate Monster}: As \spell{dominate person}, but any creature.
}

\Domain{Death}
{Dregoth}
{You may use a death touch once per day. Your death touch is a supernatural ability that produces a death effect. You must succeed on a melee touch attack against a living creature (using the rules for touch spells). When you touch, roll 1d6 per cleric level you possess. If the total at least equals the creature's current hit points, it dies (no save).}
{
	\item \spellList{Cause Fear}: One creature of 5 HD or less flees for 1d4 rounds.
	\item \spellList{Death Knell}: Kill dying creature and gain 1d8 temporary hp, +2 to Str, and +1 caster level.
	\item \spellList{Animate Dead}\textsuperscript{M}: Creates undead skeletons and zombies.
	\item \spellList{Death Ward}: Grants immunity to death spells and negative energy effects.
	\item \spellList{Slay Living}: Touch attack kills subject.
	\item \spellList{Create Undead}\textsuperscript{M}: Create ghouls, ghasts, mummies, or mohrgs.
	\item \spellList{Destruction}\textsuperscript{F}: Kills subject and destroys remains.
	\item \spellList{Create Greater Undead}\textsuperscript{M}: Create shadows, wraiths, spectres, or devourers.
	\item \spellList{Wail of the Banshee}: Kills one creature/level.
}

\Domain{Destruction}
{Borys, Dregoth}
{You gain the smite power, the supernatural ability to make a single melee attack with a +4 bonus on attack rolls and a bonus on damage rolls equal to your cleric level (if you hit). You must declare the smite before making the attack. This ability is usable once per day.}
{
	\item \spellList{Inflict Light Wounds}: Touch attack, 1d8 damage +1/level (max +5).
	\item \spellList{Shatter}: Sonic vibration damages objects or crystalline creatures.
	\item \spellList{Contagion}: Infects subject with chosen disease.
	\item \spellList{Inflict Critical Wounds}: Touch attack, 4d8 damage +1/level (max +20).
	\item \spellList{Inflict Light Wounds, Mass}: Deals 1d8 damage +1/level to any creatures.
	\item \spellList{Harm}: Deals 10 points/level damage to target.
	\item \spellList{Disintegrate}: Makes one creature or object vanish.
	\item \spellList{Earthquake}: Intense tremor shakes 24-m radius.
	\item \spellList{Implosion}: Kills one creature/round.
}

\Domain{Glory}
{Tectuktilay}
{You gain a +2 bonus on turning checks and +1d6 to turning damage rolls.}
{
	\item \spellList{Disrupt Undead}: Deals 1d6 damage to one undead.
	\item \spellList{Bless Weapon}: Weapon strikes true against evil foes.
	\item \spellList{Searing Light}: Ray deals 1d8/two levels damage, more against undead.
	\item \spellList{Holy Smite}: Damages and blinds evil creatures.
	\item \spellList{Holy Sword}: Weapon becomes +5, deals +2d6 damage against evil.
	\item \spellList{Bolt of Glory}: Positive energy ray deals extra damage to evil outsiders and undead.
	\item \spellList{Sunbeam}: Beam blinds and deals 4d6 damage.
	\item \spellList{Crown of Glory}: You gain +4 Charisma and enthrall those who hear you.
	\item \spellList{Gate}\textsuperscript{X}: Connects two planes for travel or summoning.
}

\Domain{Knowledge}
{Oronis}
{Add all \skill{Knowledge} skills to your list of cleric class skills.

You cast divination spells at +1 caster level.}
{
	\item \spellList{Detect Secret Doors}: Reveals hidden doors within 18 m.
	\item \spellList{Detect Thoughts}: Allows ``listening'' to surface thoughts.
	\item \spellList{Clairaudience/Clairvoyance}: Hear or see at a distance for 1 min./level.
	\item \spellList{Divination}\textsuperscript{M}: Provides useful advice for specific proposed actions.
	\item \spellList{True Seeing}\textsuperscript{M}: Lets you see all things as they really are.
	\item \spellList{Find the Path}: Shows most direct way to a location.
	\item \spellList{Legend Lore}\textsuperscript{MF}: Lets you learn tales about a person, place, or thing.
	\item \spellList{Discern Location}: Reveals exact location of creature or object.
	\item \spellList{Foresight}: ``Sixth sense'' warns of impending danger.
}

\Domain{Law}
{Andropinis}
{You cast law spells at +1 caster level.}
{
	\item \spellList{Protection from Chaos}: +2 to AC and saves, counter mind control, hedge out elementals and outsiders.
	\item \spellList{Calm Emotions}: Calms creatures, negating emotion effects.
	\item \spellList{Magic Circle against Chaos}: As \spell{protection spells}, but 3-m radius and 10 min./level.
	\item \spellList{Order's Wrath}: Damages and dazes chaotic creatures.
	\item \spellList{Dispel Chaos}: +4 bonus against attacks by chaotic creatures.
	\item \spellList{Hold Monster}: As \spell{hold person}, but any creature.
	\item \spellList{Dictum}: Kills, paralyzes, slows, or deafens nonlawful subjects.
	\item \spellList{Shield of Law}\textsuperscript{F}: +4 to AC, +4 resistance, and SR 25 against chaotic spells.
	\item \spellList{Summon Monster IX}\footnotemark[1]: Calls extraplanar creature to fight for you.
}
\noindent 1 Cast as a law spell only.

\Domain{Madness}
{Daskinor}
{You have a $-1$ penalty for each three cleric levels on all Wisdom-based skills.

Once per day, you can see and act with the clarity of true madness. You can add one-half your cleric levels on a single Wisdom-based skill check or Will save. You must choose to use this power before the roll is made.}
{
	\item \spellList{Confusion, Lesser}: One creature is confused for 1 round.
	\item \spellList{Touch of Madness}: Dazes one creature for 1 round/level.
	\item \spellList{Rage}: Gives +2 to Str and Con, +1 on Will saves, $-2$ to AC.
	\item \spellList{Confusion}: Subjects behave oddly for 1 round/level.
	\item \spellList{Bolts of Bedevilment}: One ray/round, dazes 1d3 rounds.
	\item \spellList{Phantasmal Killer}: Fearsome illusion kills subject or deals 3d6 damage.
	\item \spellList{Insanity}: Subject suffers continuous confusion.
	\item \spellList{Maddening Scream}: Subject has $-4$ AC, no shield, Reflex save on 20 only.
	\item \spellList{Weird}: As \spell{phantasmal killer}, but affects all within 30 ft.
}

\Domain{Magic}
{Kalak, Nibenay}
{Use scrolls, wands, and other devices with spell completion or spell trigger activation as a wizard of one-half your cleric level (at least 1st level). For the purpose of using a scroll or other magic device, if you are also a wizard, actual wizard levels and these effective wizard levels stack.}
{
	\item \spellList{Magic Aura}: Alters object's magic aura.
	\item \spellList{Identify}: Determines properties of magic item.
	\item \spellList{Dispel Magic}: Cancels magical spells and effects.
	\item \spellList{Imbue with Spell Ability}: Transfer spells to subject.
	\item \spellList{Spell Resistance}: Subject gains SR 12 + level.
	\item \spellList{Antimagic Field}: Negates magic within 3 m.
	\item \spellList{Spell Turning}: Reflect 1d4+6 spell levels back at caster.
	\item \spellList{Protection from Spells}\textsuperscript{M}\textsuperscript{F}: Confers +8 resistance bonus.
	\item \spellList{Mage's Disjunction}: Dispels magic, disenchants magic items.
}

\Domain{Mind}
{Nibenay}
{Gain a +2 bonus on \skill{Bluff}, \skill{Diplomacy}, and \skill{Sense Motive} checks. Gain a +2 bonus on Will saves against enchantment spells and effects.}
{
	\item \spellList{Comprehend Languages}: You understand all spoken and written languages.
	\item \spellList{Detect Thoughts}: Allows ``listening'' to surface thoughts.
	\item \spellList{Telepathic Bond, Lesser}: Link with subject within 9 m for 10 min./level.
	\item \spellList{Discern Lies}: Reveals deliberate falsehoods.
	\item \spellList{Telepathic Bond}: Link lets allies communicate.
	\item \spellList{Probe Thoughts}: Read subject's memories, one question/round.
	\item \spellList{Brain Spider}: Eavesdrop on thoughts of up to eight other creatures.
	\item \spellList{Mind Blank}: Subject is immune to mental/emotional magic and scrying.
	\item \spellList{Weird}: Fearful illusion affects all within 9 m, either killing or dealing 3d6 damage.
}

\Domain{Nobility}
{Andropinis}
{You have the spell-like ability to inspire allies, giving you a +2 morale bonus on saving throws, attack rolls, ability checks, skill checks, and weapon damage rolls. Allies must be able to hear the character speak for 1 round. Using this ability is a standard action. It lasts a number of rounds equal to your Charisma bonus and can be used once per day.}
{
	\item \spellList{Divine Favor}: You gain +1 per three levels on attack and damage rolls.
	\item \spellList{Enthrall}: Captivates all within 30 m + 3 m/level.
	\item \spellList{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.
	\item \spellList{Discern Lies}: Reveals deliberate falsehoods.
	\item \spellList{Command, Greater}: As \spell{command}, but affects one subject/level.
	\item \spellList{Geas/Quest}: As \spell{lesser geas}, plus it affects any creature.
	\item \spellList{Repulsion}: Creatures can't approach you.
	\item \spellList{Demand}: As \spell{sending}, plus you can send suggestion.
	\item \spellList{Storm of Vengeance}: Storm rains acid, lightning, and hail.
}

\Domain{Plant}
{Lalali-Puy}
{Rebuke or command plant creatures as an evil cleric rebukes or commands undead. Use this ability a total number of times per day equal to 3 + your Charisma modifier. This granted power is a supernatural ability.

Add \skill{Knowledge} (nature) to your list of cleric class skills.}
{
	\item \spellList{Entangle}: Plants entangle everyone in 12-m radius.
	\item \spellList{Barkskin}: Grants +2 (or higher) enhancement to natural armor.
	\item \spellList{Plant Growth}: Grows vegetation, improves crops.
	\item \spellList{Command Plants}: Sway the actions of one or more plant creatures.
	\item \spellList{Wall of Thorns}: Thorns damage anyone who tries to pass.
	\item \spellList{Repel Wood}: Pushes away wooden objects.
	\item \spellList{Animate Plants}: One or more trees animate and fight for you.
	\item \spellList{Control Plants}: Control actions of one or more plant creatures.
	\item \spellList{Shambler}: Summons 1d4+2 shambling mounds to fight for you.
}

\Domain{Protection}
{Borys, Oronis}
{You can generate a protective ward as a supernatural ability. Grant someone you touch a resistance bonus equal to your cleric level on his or her next saving throw. Activating this power is a standard action. The protective ward is an abjuration effect with a duration of 1 hour that is usable once per day.}
{
	\item \spellList{Sanctuary}: Opponents can't attack you, and you can't attack.
	\item \spellList{Shield Other}\textsuperscript{F}: You take half of subject's damage.
	\item \spellList{Protection from Energy}: Absorb 12 points/level of damage from one kind of energy.
	\item \spellList{Spell Immunity}: Subject is immune to one spell per four levels.
	\item \spellList{Spell Resistance}: Subject gains SR 12 + level.
	\item \spellList{Antimagic Field}: Negates magic within 3 m.
	\item \spellList{Repulsion}: Creatures can't approach you.
	\item \spellList{Mind Blank}: Subject is immune to mental/emotional magic and scrying.
	\item \spellList{Prismatic Sphere}: As \spell{prismatic wall}, but surrounds on all sides.
}

\Domain{Strength}
{Hamanu, Tectuktilay}
{You can perform a feat of strength as a supernatural ability. You gain an enhancement bonus to Strength equal to your cleric level. Activating the power is a free action, the power lasts 1 round, and it is usable once per day.}
{
	\item \spellList{Enlarge Person}: Humanoid creature doubles in size.
	\item \spellList{Bull's Strength}: Subject gains +4 to Str for 1 min./level.
	\item \spellList{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.
	\item \spellList{Spell Immunity}: Subject is immune to one spell per four levels.
	\item \spellList{Righteous Might}: Your size increases, and you gain combat bonuses.
	\item \spellList{Stoneskin}\textsuperscript{M}: Ignore 10 points of damage per attack.
	\item \spellList{Grasping Hand}: Large hand provides cover, pushes, or grapples.
	\item \spellList{Clenched Fist}: Large hand provides cover, pushes, or attacks your foes.
	\item \spellList{Crushing Hand}: Large hand provides cover, pushes, or crushes your foes.
}


\Domain{Trickery}
{Kalak}
{Add \skill{Bluff}, \skill{Disguise}, and \skill{Hide} to your list of cleric class skills.}
{
	\item \spellList{Disguise Self}: Disguise own appearance.
	\item \spellList{Invisibility}: Subject invisible 1 min./level or until it attacks.
	\item \spellList{Nondetection}\textsuperscript{M}: Hides subject from divination, scrying.
	\item \spellList{Confusion}: Subjects behave oddly for 1 round/level.
	\item \spellList{False Vision}\textsuperscript{M}: Fools scrying with an illusion.
	\item \spellList{Mislead}: Turns you invisible and creates illusory double.
	\item \spellList{Screen}: Illusion hides area from vision, scrying.
	\item \spellList{Polymorph Any Object}: Changes any subject into anything else.
	\item \spellList{Time Stop}: You act freely for 1d4+1 rounds.
}


\Domain{War}
{Hamanu}
{Free \feat{Martial Weapon Proficiency} with deity's favored weapon (if necessary) and \feat{Weapon Focus} with the deity's favored weapon.}
{
	\item \spellList{Magic Weapon}: Weapon gains +1 bonus.
	\item \spellList{Spiritual Weapon}: Magical weapon attacks on its own.
	\item \spellList{Magic Vestment}: Armor or shield gains +1 enhancement per four levels.
	\item \spellList{Divine Power}: You gain attack bonus, +6 to Str, and 1 hp/level.
	\item \spellList{Flame Strike}: Smite foes with divine fire (1d6/level damage).
	\item \spellList{Blade Barrier}: Wall of blades deals 1d6/level damage.
	\item \spellList{Power Word Blind}: Blinds creature with 200 hp or less.
	\item \spellList{Power Word Stun}: Stuns creature with 150 hp or less.
	\item \spellList{Power Word Kill}: Kills creature with 100 hp or less.
}
