\subsection{Fighter Feats}
\Feat[Epic, Fighter]{Armor Skin}
{}{}
{You gain a +1 natural armor bonus to Armor Class, or your existing natural armor bonus increases by 1.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic, Fighter]{Damage Reduction}
{}
{Con 21.}
{You gain damage reduction 3/--. This does not stack with damage reduction granted by magic items or nonpermanent magical effects, but it does stack with any damage reduction granted by permanent magical effects, class features, or this feat itself.}
{}{You can gain this feat multiple times. Each time you gain the feat, your damage reduction increases by 3.}

\Feat[Epic, Fighter]{Devastating Critical}
{}
{Str 25, \feat{Cleave}, \feat{Great Cleave}, \feat{Improved Critical} with weapon, \feat{Overwhelming Critical} with weapon, \feat{Power Attack}, \feat{Weapon Focus} with weapon.}
{Whenever you score a critical hit with the chosen weapon, the target must make a Fortitude save (DC 10 + \onehalf your level + your Strength modifier) or die instantly. (Creatures immune to critical hits can't be affected by this feat.)}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different type of weapon.}

\GFeat[Epic, Fighter]{Distant Shot}
{Dex 25, \feat{Far Shot}, \feat{Point Blank Shot}, \skill{Spot} 20 ranks.}
{You may throw or fire a ranged weapon at any target within line of sight, with no penalty for range.}

\GFeat[Epic, Fighter]{Epic Feint}
{\skill{Bluff} 24 ranks, \feat{Improved Feint}.}
{You can ignore any check penalties applied to feinting against nonhumanoid opponents.}

\GFeat[Epic, Fighter]{Epic Grapple}
{Str 21, Dex 21, \feat{Improved Unarmed Strike}, \feat{Improved Grapple}.}
{You gain a +10 bonus on all grapple checks.}

\Feat[Epic, Fighter]{Epic Manyshot}
{}
{Dex 19, base attack bonus +21, \feat{Manyshot}, \feat{Point Blank Shot}, \feat{Rapid Shot}.}
{As \feat{Manyshot}, but the number of arrows you can fire is limited only by your base attack bonus (two arrows, plus one arrow for every 5 points of base attack bonus above +6).}
{With the \feat{Manyshot} feat, you are limited to a maximum of four arrows fired (when your base attack bonus is +16 or higher).}
{Regardless of the number of arrows you fire, you only apply precision-based damage (such as sneak attack damage or the ranger's favored enemy bonus) once. If you score a critical hit, only one of the arrows deals critical damage (your choice); all others deal normal damage.}

\Feat[Epic, Fighter]{Epic Weapon Focus}
{}
{\feat{Weapon Focus} with weapon, \feat{Greater Weapon Focus} with weapon, fighter level 21st.}
{Add a +2 bonus to all attack rolls you make using the selected weapon.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different type of weapon.}

\Feat[Epic, Fighter]{Epic Weapon Specialization}
{}
{\feat{Epic Weapon Focus} with weapon, \feat{Greater Weapon Focus} with weapon, \feat{Greater Weapon Specialization} with weapon, \feat{Weapon Focus} with weapon, \feat{Weapon Specialization} with weapon, fighter level 24th.}
{Add +4 to all damage you deal using the selected weapon.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat it applies to a different type of weapon.}

\GFeat[Epic, Fighter]{Exceptional Deflection}
{Dex 21, Wis 19, \feat{Deflect Arrows}, \feat{Improved Unarmed Strike}.}
{You can deflect any ranged attacks (including spells that require ranged touch attacks) as if they were arrows.}

\GFeat[Epic, Fighter]{Exotic Mastery}
{\feat{Exotic Weapon Proficiency} with five or more weapons.}
{You are proficient with all exotic weapons.}

\GFeat[Epic, Fighter]{Improved Combat Reflexes}
{Dex 21, \feat{Combat Reflexes}.}
{There is no limit to the number of attacks of opportunity you can make in one round. (you still can't make more than one attack of opportunity for a given opportunity.)}

\Feat[Epic, Fighter]{Improved Whirlwind Attack}
{}
{Int 13, Dex 23, \feat{Combat Expertise}, \feat{Dodge}, \feat{Mobility}, \feat{Spring Attack}, \feat{Whirlwind Attack}.}
{As a standard action, you can make one melee attack for every five points of your base attack bonus.

You cannot attack any one opponent more than once as part of this action. These attacks (as well as all other attacks made until the start of your next turn) suffer a $-4$ penalty.

When using the Improved Whirlwind Attack feat, you also forfeit any bonus or extra attacks granted by other spells or abilities (such as the \feat{Cleave} feat or the \spell{haste} spell).

Since these attacks are made as part of a standard action, you can't make a 1.5-meter step between any two of the attacks.}
{Without this feat, using the Whirlwind Attack feat requires a full attack action, and you can take a 1.5-meter step between any two of the attacks.}
{}

\GFeat[Epic, Fighter]{Infinite Deflection}
{Dex 25, \feat{Combat Reflexes}, \feat{Deflect Arrows}, \feat{Improved Unarmed Strike}.}
{You may perform any number of deflections each round, as the \feat{Deflect Arrows} feat.}

\Feat[Epic, Fighter]{Instant Reload}
{}
{\feat{Quick Draw}, \feat{Rapid Reload} with crossbow type chosen, \feat{Weapon Focus} with crossbow type chosen.}
{You may fire the selected type of crossbow at your full normal attack rate. Reloading the crossbow does not provoke attacks of opportunity.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different type of crossbow.}

\Feat[Epic, Fighter]{Overwhelming Critical}
{}
{Str 23, \feat{Cleave}, \feat{Great Cleave}, \feat{Improved Critical} with weapon, \feat{Power Attack}, \feat{Weapon Focus} with weapon.}
{When using the weapon you have selected, you deal an extra 1d6 points of bonus damage on a successful critical hit. If the weapon's critical multiplier is $\times$3, add +2d6 points of bonus damage instead, and if the multiplier is $\times$4, add +3d6 points of bonus damage instead. Creatures immune to critical hits can't be affected by this feat.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take this feat, it applies to a different type of weapon.}


\Feat[Epic, Fighter]{Perfect Multiweapon Fighting}
{}
{Dex 25, three or more hands, base attack bonus +25, \feat{Greater Multiweapon Fighting}, \feat{Multiweapon Fighting}.}
{You can make as many attacks with each extra weapon as with your primary weapon, using the same base attack bonus. You still take the normal penalties for fighting with two weapons.}
{Without this feat, you can make only one attack per round with each extra weapon (or two attacks per round with each weapon if you have \feat{Multiweapon Fighting}, or three attacks per round with each extra weapon if you have \feat{Greater Multiweapon Fighting}). Each attack after the first extra attack has a cumulative $-5$ penalty.}
{This feat replaces the \feat{Perfect Two-Weapon Fighting} feat for creatures with more than two arms.}

\Feat[Epic, Fighter]{Perfect Two-Weapon Fighting}
{}
{Dex 25, bonus attack bonus +21, \feat{Greater Two-Weapon Fighting}, \feat{Improved Two-Weapon Fighting}, \feat{Two-Weapon Fighting}.}
{You can make as many attacks with your off-hand weapon as with your primary weapon, using the same base attack bonus. You still take the normal penalties for fighting with two weapons.}
{Without this feat, you can only get a single attack with an off-hand weapon (or two attacks with an off-hand weapon if you have \feat{Improved Two-Weapon Fighting}, or three attacks with an off-hand weapon if you have \feat{Greater Two-Weapon Fighting}).}
{A 21st level ranger who has chosen the two-weapon combat style is treated as having Perfect Two-Weapon Fighting, even if he does not have the prerequisites for it, but only when he is wearing light or no armor.}

\GFeat[Epic, Fighter]{Spellcasting Harrier}
{\feat{Combat Reflexes}.}
{Any spellcaster you threaten in melee provokes an attack of opportunity if they try to cast defensively. You get a +4 bonus on this attack roll.}

\GFeat[Epic, Fighter]{Storm of Throws}
{Dex 23, \feat{Point Blank Shot}, \feat{Quick Draw}, \feat{Rapid Shot}.}
{As a full-round action, you may throw a light weapon at your full base attack bonus at each opponent within 9 meters. All light weapons thrown need not be the same type.}

\GFeat[Epic, Fighter]{Swarm of Arrows}
{Dex 23, \feat{Point Blank Shot}, \feat{Rapid Shot}, \feat{Weapon Focus} with bow.}
{As a full-round action, you may fire an arrow at your full base attack bonus at each opponent within 9 meters.}

\Feat[Epic, Fighter]{Uncanny Accuracy}
{}
{Dex 21, base attack bonus +11, \feat{Point Blank Shot}, \feat{Precise Shot}, \feat{Improved Precise Shot}, \skill{Spot} 20 ranks.}
{Your ranged attacks ignore the miss chance granted to targets by total concealment. You must aim your attacks at the correct square to take advantage of this feat.}
{Without this feat, you suffer a 50\% miss chance when making a ranged attack against a target with total concealment.}
{A 21st level ranger who has chosen the archery combat style is treated as having Uncanny Accuracy, even if he does not have the prerequisites for it, but only when he is wearing light or no armor.}
