\subsection{General Feats}
\Feat[Epic]{Advanced Armor Optimization}
{}
{Armor optimization 4 or more.}
{Your armor optimization improvement increases by 1.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Advanced Dirty Trick}
{}
{Dirty trick $\pm8$/$\pm10$.}
{Your dirty trick bonuses and penalties increases by 1.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Advanced Favored Enemy}
{}
{Five or more favored enemies.}
{Add +1 to the bonus on \skill{Bluff}, \skill{Listen}, \skill{Sense Motive}, \skill{Spot}, and \skill{Survival} checks and damage rolls against all your favored enemies.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Advanced Favored Terrain}
{}
{Four or more favored enemies.}
{Add +1 to the bonus on \skill{Hide}, \skill{Listen}, \skill{Move Silently}, \skill{Search}, \skill{Spot}, and \skill{Survival} checks and initiative checks within your favored terrains. Likewise, add +1 to the bonus on \skill{Knowledge} (geography) and \skill{Knowledge} (nature) checks about your favored terrains.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Advanced Inspiration}
{}
{Cha 25, \skill{Perform} 30 ranks, bardic music class feature.}
{All competence bonuses, dodge bonuses, and morale bonuses granted by your bardic music ability increase by +1. If you have the inspire greatness bardic music ability, it grants one additional bonus HD.}
{}{You can gain this feat multiple times. Its effects stack.}

\GFeat[Epic]{Advanced Metamagic}
{Four metamagic feats, \skill{Spellcraft} 30 ranks.}
{The spell slot modifier of all your metamagic feats is reduced by one level, to a minimum of +1. This feat has no effect on metamagic feats whose spell slot modifier is +1 or less.}

\Feat[Epic]{Advanced Skirmish}
{}
{Skirmish +4d6/+4 AC.}
{
If the bonus to AC granted when you use your skirmish ability is equal to or higher than the number of dice of extra damage granted by your skirmish ability, your extra damage on skirmish attacks increases by 1d6.

If the bonus to AC granted by your skirmish ability is less than the number of dice of extra damage granted by your skirmish ability, the bonus to AC when skirmishing increases by 1 instead.
}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Advanced Sneak Attack}
{}
{Sneak attack +8d6.}
{Your sneak attack increases by 1d6.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Advanced Spell Resistance}
{}
{Spell resistance.}
{The spell slot modifier of all your metamagic feats is reduced by one level, to a minimum of +1. This feat has no effect on metamagic feats whose spell slot modifier is +1 or less.}
{}{You can gain this feat multiple times. Its effects stack.}

\GFeat[Epic]{Augmented Poison}
{Int 21, \skill{Craft} (poisonmaking) 24 ranks.}
{Whenever creating a poison, you can make it more potent than normal by adding +20 to the DC required to create it and multiplying its price by 5. You increase its damage by 100\%.}

\GFeat[Epic]{Bane Of Enemies}
{\skill{Survival} 24 ranks, five or more favored enemies.}
{Any weapon you wield against one of your favored enemies is treated as a bane weapon for that creature type (thus, its enhancement bonus is increased by +2 and it deals +2d6 points of damage). This ability doesn't stack with similar abilities.}

\GFeat[Epic]{Chaotic Rage}
{Rage 5/day, chaotic alignment.}
{Any weapon you wield while in a rage is treated as an anarchic weapon (it is chaos-aligned and deals an extra 2d6 points of damage against creatures of lawful alignment). This ability does not stack with similar abilities.}

\Feat[Epic]{Efficient Item Creation}
{}
{
Item creation feat to be selected, \skill{Knowledge} (arcana) or \skill{Knowledge} (psionics) 24 ranks, \skill{Psicraft} or \skill{Spellcraft} 24 ranks.}
{Select an item creation feat. Creating a magic item using that feat requires one day per 10,000 cp of the item's market price, with a minimum of one day.

Psionic item creation feats require \skill{Knowledge} (psionics) and \skill{Psicraft}, while magic item creation feats require \skill{Knowledge} (arcana) and \skill{Spellcraft}.
}
{Without this feat, creating a magic item requires one day for each 1,000 cp of the item's market price.}
{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different item creation feat.}

\Feat[Epic]{Energy Resistance}
{}{}
{Choose a type of energy (acid, cold, electricity, fire, or sonic). You gain resistance 10 to that type of energy, or your existing resistance to that type of energy increases by 10. This feat does not stack with energy resistance granted by magic items or nonpermanent magical effects.}
{}{You can gain this feat multiple times. If the same type of energy is chosen, the effects stack.}

\GFeat[Epic]{Epic Dodge}
{Dex 25, \feat{Dodge}, \skill{Tumble} 30 ranks, improved evasion, defensive roll class feature.}
{Once per round, when struck by an attack from an opponent you have designated as the object of your dodge, you may automatically avoid all damage from the attack.}

\GFeat[Epic]{Epic Endurance}
{Con 25, \feat{Endurance}.}
{Whenever you make a check for performing a physical action that extends over a period of time, you get a +10 bonus on the check.}

\GFeat[Epic]{Epic Fortitude}
{}{You gain a +4 bonus on all Fortitude saving throws.}

\GFeat[Epic]{Epic Initiative}
{\feat{Improved Initiative}.}
{You get a +8 bonus on initiative checks. This bonus overlaps (does not stack with) the bonus from Improved Initiative.}

\Feat[Epic]{Epic Leadership}
{}
{Cha 25, \feat{Leadership}, \feat{Leadership} score 25.}
{You attract a cohort and followers as shown on \tabref{Epic Leadership}. In all other ways Epic Leadership functions as the \feat{Leadership} feat.

\Table{Epic Leadership}{CC*9c}{
  && \multicolumn{9}{c}{\tableheader Number of Followers by Level}\\
\cmidrule[0.5pt]{3-11}
  \tableheader Leadership Score
& \tableheader Cohort Level
& \tableheader 1st
& \tableheader 2nd
& \tableheader 3rd
& \tableheader 4th
& \tableheader 5th
& \tableheader 6th
& \tableheader 7th
& \tableheader 8th
& \tableheader 9th\\

25 & 17th & 135  & 13  & 7  & 4  & 2  & 2 &   &   &   \\
26 & 18th & 160  & 16  & 8  & 4  & 2  & 2 & 1 &   &   \\
27 & 18th & 190  & 19  & 10 & 5  & 3  & 2 & 1 &   &   \\
28 & 19th & 220  & 22  & 11 & 6  & 3  & 2 & 1 &   &   \\
29 & 19th & 260  & 26  & 13 & 7  & 4  & 2 & 1 &   &   \\
30 & 20th & 300  & 30  & 15 & 8  & 4  & 2 & 1 &   &   \\
31 & 20th & 350  & 35  & 18 & 9  & 5  & 3 & 2 & 1 &   \\
32 & 21st & 400  & 40  & 20 & 10 & 5  & 3 & 2 & 1 &   \\
33 & 21st & 460  & 46  & 23 & 12 & 6  & 3 & 2 & 1 &   \\
34 & 22nd & 520  & 52  & 26 & 13 & 6  & 3 & 2 & 1 &   \\
35 & 22nd & 590  & 59  & 30 & 15 & 8  & 4 & 2 & 1 &   \\
36 & 23rd & 660  & 66  & 33 & 17 & 9  & 5 & 3 & 2 & 1 \\
37 & 23rd & 740  & 74  & 37 & 19 & 10 & 5 & 3 & 2 & 1 \\
38 & 24th & 820  & 82  & 41 & 21 & 11 & 6 & 3 & 2 & 1 \\
39 & 24th & 910  & 91  & 46 & 23 & 12 & 6 & 3 & 2 & 1 \\
40 & 25th & 1000 & 100 & 50 & 25 & 13 & 7 & 4 & 2 & 1 \\
  per +1
& +\onehalf
& +100\footnotemark[1]
& $\star$
& $\star$
& $\star$
& $\star$
& $\star$
& $\star$
& $\star$
& $\star$\\

\TableNote{11}{\textit{Leadership Score:} Your Leadership score equals your level plus any Charisma modifier. Outside factors can affect a character's Leadership score, as detailed in the Leadership feat.}\\

\TableNote{11}{\textit{Cohort Level:} You can attract a cohort of up to this level. Regardless of your Leadership score, you can't recruit a cohort of your level or higher.}\\

\TableNote{11}{\textit{Number of Followers by Level:} You can lead up to the indicated number of characters of each level.}\\

\TableNote{11}{1 The number of 1st-level followers increases by 100 for every point of \feat{Leadership} score above 40.}\\

\TableNote{11}{$\star$ You can command one-tenth as many 2nd-level followers as 1st-level followers. You can command one-half as many 3rd-level followers as 2nd-level followers, one-half as many 4th-level followers as 3rd-level followers, and so on (round fractions up, except any fraction less than 1 rounds to 0). You can't have a follower of higher than 20th level.}
}
}
{The \feat{Leadership} feat provides no benefit for leadership scores beyond 25.}{}

\GFeat[Epic]{Epic Reflex}
{}{You gain a +4 bonus on all Reflex saving throws.}

\Feat[Epic]{Epic Skill Focus}
{}
{\feat{Skill Focus} in the selected skill, 20 ranks in the selected skill.}
{You gain a +10 bonus on all checks with that skill.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different skill.}

\Feat[Epic]{Epic Speed}
{}
{Dex 21, \feat{Run}.}
{Your speed increases by 9 meters. This is considered an enhancement bonus.}
{}{This feat only functions when you are wearing medium armor, light armor, or no armor.}

\Feat[Epic]{Epic Spell Focus}
{}
{\feat{Greater Spell Focus} in school, \feat{Spell Focus} in school, ability to cast at least one 9th-level spell of the school to be chosen.}
{Add +1 to the Difficulty Class for all saving throws against spells from the school of magic you select to focus on. This stacks with the bonuses from \feat{Spell Focus} and \feat{Greater Spell Focus}.}
{}{You can gain this feat multiple times. Its effects do not stack. Each time you take the feat, it applies to a different school of magic.}






\FeatTable{General}{
\feat{Advanced Armor Optimization}\footnotemark[1] & Armor optimization 4 or more & Increase armor optimization improvement by 1 \\
\feat{Advanced Dirty Trick}\footnotemark[1] & Dirty trick $\pm8$/$\pm10$ & Increase dirty trick bonuses and penalties by 1 \\
\feat{Advanced Favored Enemy}\footnotemark[1] & Five or more favored enemies & Improve all favored enemy bonus by +1 \\
\feat{Advanced Favored Terrain}\footnotemark[1] & Four or more favored terrain & Improve all favored terrain bonus by +1 \\
\feat{Advanced Inspiration}\footnotemark[1] & Cha 25, \skill{Perform} 30 ranks, bardic music class feature & Improve all bardic music bonus by +1\\
\feat{Advanced Metamagic} & Four metamagic feats, \skill{Spellcraft} 30 ranks & Reduce metamagic spell slot modifier by 1\\
\feat{Advanced Skirmish}\footnotemark[1] & Skirmish +4d6/+4 AC & Increase skirmish by +1d6 or +1 AC\\
\feat{Advanced Sneak Attack}\footnotemark[1] & Sneak attack +8d6 & Increase sneak attack by +1d6\\
\feat{Advanced Spell Resistance}\footnotemark[1] & Spell resistance & Increase your spell resistance by 2\\

\feat{Augmented Poison} & Int 21, \skill{Craft} (poisonmaking) 24 ranks & Double the poison damage \\
\feat{Bane Of Enemies} & \skill{Survival} 24 ranks, five or more favored enemies & Weapons are treated as bane against favored enemies \\
\feat{Chaotic Rage} & Rage 5/day, chaotic alignment & Weapons are treated as anarchic while raging \\
\feat{Efficient Item Creation}\footnotemark[2] & Item creation feat to be selected, \skill{Knowledge} (arcana) or \skill{Knowledge} (psionics) 24 ranks, \skill{Psicraft} or \skill{Spellcraft} 24 ranks & Using selected item creation feat requires 1 day per 10,000 cp \\
\feat{Energy Resistance}\footnotemark[1] && Energy resistance 10 for one energy type\\

\feat{Epic Dodge} & Dex 25, \feat{Dodge}, \skill{Tumble} 30 ranks, improved evasion, defensive roll class feature & Once per round avoid all damage from one attack \\
\feat{Epic Endurance} & Con 25, \feat{Endurance} & +10 on checks to resist nonlethal damage \\
\feat{Epic Fortitude} && +4 bonus on Fortitude saves\\
\feat{Epic Initiative} & \feat{Improved Initiative} & +8 on initiative checks \\
\feat{Epic Leadership} & Cha 25, \feat{Leadership}, \feat{Leadership} score 25 & Access to more followers and higher-leveled cohorts\\
~ \feat{Legendary Commander} & Cha 25, \feat{Epic Leadership}, \feat{Leadership}, \skill{Diplomacy} 30 ranks, must rule own kingdom and have a stronghold & Multiply number of followers by 10\\
\feat{Epic Reflex} && +4 bonus on Reflex saves\\
\feat{Epic Skill Focus}\footnotemark[2] & \feat{Skill Focus} in the selected skill, 20 ranks in the selected skill & +10 bonus on checks of selected skill \\
\feat{Epic Speed} & Dex 21, \feat{Run} & Speed +9 m while not in heavy armor \\
\feat{Epic Spell Focus}\footnotemark[2] & \feat{Greater Spell Focus} in school, \feat{Spell Focus} in school, ability to cast at least one 9th-level spell of the school & +1 bonus to DC on spells of chosen school \\
\feat{Epic Spell Penetration} & \feat{Greater Spell Penetration}, \feat{Spell Penetration} & +2 bonus on caster level check to defeat spell resistance\\
\feat{Epic Toughness} && +30 hit points\\
\feat{Epic Will} && +4 bonus on Will saves\\

\feat{Extended Life Span}\footnotemark[1] && Increase the threshold for each of your age categories\\
% \feat{Familiar Spell}\footnotemark[1] & Int 25 & Familiar gains a spell-like ability 1/day\\
\feat{Fast Healing}\footnotemark[1] & Con 25 & Fast healing 3\\

\feat{Great Charisma}\footnotemark[1] && Increase your Charisma by 1\\
\feat{Great Constitution}\footnotemark[1] && Increase your Constitution by 1\\
\feat{Great Dexterity}\footnotemark[1] && Increase your Dexterity by 1\\
\feat{Great Intelligence}\footnotemark[1] && Increase your Intelligence by 1\\
\feat{Great Strength}\footnotemark[1] && Increase your Strength by 1\\
\feat{Great Wisdom}\footnotemark[1] && Increase your Wisdom by 1\\

\feat{Ignore Material Components} & \feat{Eschew Materials}, \skill{Spellcraft} 25 ranks, ability to cast 9th-level arcane or divine spells & Cast spells without any material components\\
\feat{Lasting Inspiration} & \skill{Perform} 25 ranks, bardic music & Bardic music lasts 10$\times$ longer after singing stops\\

\feat{Legendary Acrobat} & \skill{Balance} 12 ranks, \skill{Jump} 12 ranks, \skill{Tumble} 24 ranks & Ignore penalties for accelerated tumbling\\
\feat{Legendary Climber} & Dex 21, \skill{Balance} 12 ranks, \skill{Climb} 24 ranks & Ignore penalties for accelerated climbing\\
\feat{Legendary Detective} & Cha 25, \feat{Urban Tracking}, \skill{Diplomacy} 24 ranks, \skill{Gather Information} 24 ranks & Reduce time to track and ignore penalty to avoid suspicion\\
\feat{Legendary Equilibrist} & \skill{Balance} 24 ranks & Ignore penalties for accelerated balancing\\
\feat{Legendary Leaper} & \skill{Jump} 24 ranks & Move only 1.5 meter to make running jump\\
\feat{Legendary Poisoner} & \skill{Craft} (poisonmaking) 24 ranks & +2 DC to all poisons you apply\\
\feat{Legendary Prowler} & \skill{Hide} 27 ranks, \skill{Move Silently} 27 ranks & Ignore penalties for accelerated movement \\
\feat{Legendary Rider} & \skill{Ride} 24 ranks & No penalty riding bareback and no checks to control mount in combat\\
\feat{Legendary Tracker} & Wis 25, \feat{Track}, \skill{Knowledge} (nature) 30 ranks, \skill{Survival} 30 ranks & Track across water, underwater or through the air \\

\feat{Perfect Health} & Con 25, \feat{Great Fortitude} & Become immune to diseases and poisons\\
\feat{Permanent Emanation} & \feat{Persistent Spell}, \skill{Spellcraft} 25 ranks, ability to cast the spell to be made permanent & One emanation spell becomes permanent\\
\feat{Poison Penetration} & Int 21, \skill{Craft} (poisonmaking) 24 ranks & Your poisons affect creatures with poison immunity\\
\feat{Polyglot} & Int 25, \skill{Speak Language} (five languages) & Speak all languages\\

\feat{Ranged Inspiration} & \skill{Perform} 25 ranks, bardic music & Double the range of bardic music\\
\feat{Rapid Inspiration} & \skill{Perform} 25 ranks, bardic music & Use move action for bardic music\\

\feat{Spontaneous Domain Access} & Wis 25, \skill{Spellcraft} 30 ranks, ability to cast 9th-level divine spells & Convert prepared spells into a domain spell of the same level\\

\TableNote{3}{1 You can take this feat multiple times. Its effects stack.}\\
\TableNote{3}{2 You can take this feat multiple times. Its effects do not stack.}\\
}










\GFeat[Epic]{Epic Spell Penetration}
{\feat{Greater Spell Penetration}, \feat{Spell Penetration}.}
{You get a +2 bonus on caster level checks to beat a creature's spell resistance. This stacks with the bonuses from \feat{Spell Penetration} and \feat{Greater Spell Penetration}.}

\GFeat[Epic]{Epic Toughness}
{}
{You gain +30 hit points.}

\GFeat[Epic]{Epic Will}
{}{You gain a +4 bonus on all Will saving throws.}

\Feat[Epic]{Extended Life Span}
{}{}
{Add one-half the maximum result of your race's maximum age modifier to your normal middle age, old, and venerable age categories. Calculate your maximum age using the new venerable number. This feat can't lower your current age category.}
{}{You can gain this feat multiple times. Its effects stack.}

% \Feat[Epic]{Familiar Spell}
% {}
% {Int 25.}
% {Choose one arcane spell you know of 8th level or lower. Your familiar can now use this spell once per day as a spell-like ability, at a caster level equal to your caster level. Your cannot bestow a spell to your familiar if the spell normally has a material component cost of more than 1 gp or an XP cost.}
% {}{You can gain this feat multiple times. Each time you take the feat, you can give your familiar a different spell-like ability or another daily use of the same spell-like ability.}

\Feat[Epic]{Fast Healing}
{}
{Con 25.}
{You gain fast healing 3, or your existing fast healing increases by 3.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Charisma}
{}{}
{Your Charisma increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Constitution}
{}{}
{Your Constitution increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Dexterity}
{}{}
{Your Dexterity increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Intelligence}
{}{}
{Your Intelligence increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Strength}
{}{}
{Your Strength increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\Feat[Epic]{Great Wisdom}
{}{}
{Your Wisdom increases by 1 point.}
{}{You can gain this feat multiple times. Its effects stack.}

\GFeat[Epic]{Ignore Material Components}
{\feat{Eschew Materials}, \skill{Spellcraft} 25 ranks, ability to cast 9th-level arcane or divine spells.}
{You may cast spells without any material components. This feat does not affect the need for a focus or divine focus.}

\GFeat[Epic]{Lasting Inspiration}
{\skill{Perform} 25 ranks, bardic music class feature.}
{The effects of your bardic music inspiration abilities last for ten times as long as normal after you stop singing. This feat has no effect on inspiration abilities that have no duration after you stop singing.}

\Feat[Epic]{Legendary Acrobat}
{}
{\skill{Balance} 12 ranks, \skill{Jump} 12 ranks, \skill{Tumble} 24 ranks.}
{
  You can ignore any check penalties applied for accelerated movement while balancing, for accelerated tumbling, or for running while balancing on a narrow surface or while tumbling.

  You also need only move 1.5 meter in a straight line to make a running jump.
}
{
  Without this feat, you take a $-10$ penalty on \skill{Tumble} checks when attempting to move your full speed as a move action, or a $-20$ penalty on \skill{Tumble} checks when attempting to run while tumbling.
}{}

\Feat[Epic]{Legendary Climber}
{}
{Dex 21, \skill{Balance} 12 ranks, \skill{Climb} 24 ranks.}
{You can ignore any check penalties applied for accelerated climbing or rapid climbing.}
{Without this feat, you take a $-5$ penalty on \skill{Climb} checks when attempting to cover your full speed in climbing distance in a round, or a $-20$ penalty when attempting to cover twice your speed in climbing distance in a round.}{}

\GFeat[Epic]{Legendary Commander}
{Cha 25, \feat{Epic Leadership}, \feat{Leadership}, \skill{Diplomacy} 30 ranks, must rule own kingdom and have a stronghold.}
{Multiply the number of followers of each level that you can lead by 10. This has no effect on cohorts.}

\Feat[Epic]{Legendary Equilibrist}
{}
{\skill{Balance} 24 ranks.}
{
  You can ignore any check penalties applied for accelerated movement while balancing or for running while balancing on a narrow surface.
}
{
  Without this feat, you take a $-5$ penalty on \skill{Balance} checks when attempting to move your full speed as a move action, or a $-20$ penalty on \skill{Balance} when attempting to run while balancing on a narrow surface.
}{}

\Feat[Epic]{Legendary Leaper}
{}
{\skill{Jump} 24 ranks.}
{You need only move 1.5 meter in a straight line to make a running jump.}
{Without this feat, you must move at least 6 meters in a straight line before attempting a running jump.}{}

\GFeat[Epic]{Legendary Poisoner}
{\skill{Craft} (poisonmaking) 24 ranks.}
{Add 2 to the save DC of all poisons applied by you.}

\Feat[Epic]{Legendary Prowler}
{}
{\skill{Hide} 24 ranks.}
{
  You can ignore any check penalties applied for accelerated movement while hiding or for running while hiding.
}
{
  Without this feat, you take a $-5$ penalty on \skill{Hide} checks when attempting to move your full speed as a move action, or a $-20$ penalty on \skill{Hide} when attempting to run while moving silently.
}{}

\Feat[Epic]{Legendary Rider}
{}
{\skill{Ride} 24 ranks.}
{You don't take a penalty on \skill{Ride} checks when riding a mount without a saddle (bareback). You never need to make a \skill{Ride} check to control a mount in combat (and even controlling a mount not trained for combat doesn't require an action).}
{Without this feat, you take a -5 penalty on \skill{Ride} checks without a saddle, and must make a \skill{Ride} check to control a mount in combat (and controlling a mount not trained for combat requires a move action).}{}

\GFeat[Epic]{Legendary Tracker}
{Wis 25, \feat{Track}, \skill{Knowledge} (nature) 30 ranks, \skill{Survival} 30 ranks.}
{You can track creatures across water, under-water, or through the air. This adds the surfaces of water, underwater, and air to the list of surfaces found under the \feat{Track} feat.}

\Table{}{XC}{
  \tableheader Surface
& \tableheader DC\\
Water      & 60  \\
Underwater & 80  \\
Air        & 120 \\
}

\GFeat[Epic]{Perfect Health}
{Con 25, \feat{Great Fortitude}.}
{You are immune to all nonmagical diseases, as well as to all poisons whose Fortitude save DC is 25 or less.}

\Feat[Epic]{Permanent Emanation}
{}
{\feat{Persistent Spell}, \skill{Spellcraft} 25 ranks, ability to cast the spell to be made permanent.}
{Designate any one of your spells whose area is an emanation centered on you. This spell's effect is permanent (though you can dismiss or restart it as a free action). Effects that would normally dispel this spell instead suppress it for 2d4 rounds.}
{}{You can gain this feat multiple times. Each time, select a different spell to become permanent.}

\GFeat[Epic]{Poison Penetration}
{Int 21, \skill{Craft} (poisonmaking) 24 ranks.}
{Whenever you attack a creature with immunity to poison, you deal \onehalf of the damage it would otherwise deal as if it didn't have immunity.}

\GFeat[Epic]{Polyglot}
{Int 25, \skill{Speak Language} (five languages).}
{You can speak all languages. If you are literate, you can also read and write all languages (not including magical script).}

\Feat[Epic]{Ranged Inspiration}
{}
{\skill{Perform} 25 ranks, bardic music class feature.}
{Double the range of any bardic music ability that has a range. (If the creature must hear you to be affected by the ability, that requirement doesn’t change regardless of any extended range your ability may have.)}
{}{You can gain this feat multiple times. Its effects stack. Remember that two doublings equals a tripling, and so forth.}

\GFeat[Epic]{Rapid Inspiration}
{\skill{Perform} 25 ranks, bardic music class feature.}
{You can use any of your bardic music inspiration abilities as a move action. The inspiration takes effect immediately after you conclude the action.}