\subsection{Psionic Feats}
\GFeat[Epic, Psionic]{Advanced Metapsionics}
{Four metapsionic feats, \skill{Psicraft} 30 ranks.}
{Metapsionic powers you manifest cost 10 power points less than normal (to a minimum of 5 power point).

This feat has no effect on metapsionic powers that inflate the cost by only 10 power points.}

\Feat[Epic, Psionic]{Improved Manifestation}
{}
{Access to six disciplines.}
{When you select this feat, you gain 50 power points.}
{}{You can gain this feat multiple times.}

\Feat[Epic, Psionic]{Epic Psionic Focus}
{}
{Access to six disciplines.}
{When you expend your psionic focus, you can simultaneously use two feats that require a psionic focus to be expended, instead of just one. The feats must be stackable. You must still spend the requisite power points required to use each metapsionic feat, and you cannot exceed the power point limit set by your manifester level.}
{}{You can take this feat multiple times. Each time you do so, you can simultaneously use one additional feat that requires a psionic focus to be expended.}

\Feat[Epic, Psionic]{Epic Psionic Meditation}
{}
{Wis 21, \feat{Psionic Meditation}, \skill{Concentration} 24 ranks.}
{You can become psionically focused as a free action, but only once per round.}
{Without this feat, you must take a full-round action to become psionically focused (or a move action if you have \feat{Psionic Meditation}).}
{}

\Feat[Epic, Psionic]{Power Knowledge}
{}
{Access to six disciplines.}
{You learn two new powers of any level up to the highest level of power you can manifest. The powers you select must be on your class list or the list for your discipline.}
{}{You can gain this feat multiple times. Each time, you learn two new powers at any level up to the highest level of power you can manifest.}

\Feat[Epic, Psionic]{Psicrystal Power}
{}
{Int 25, \feat{Psicrystal Affinity}, access to six disciplines.}
{Choose one power you know of 8th level or lower. Your psicrystal can now manifest this power once per day at your manifester level (the psicrystal gains sufficient power points to manifest the power once). You cannot bestow a power upon your psicrystal if the power normally has any experience point cost.}
{}{You can gain this feat multiple times. Each time you take the feat, you can give your psicrystal knowledge of a new power (and it gains sufficient power points to manifest that power once).

All power points gained by a psicrystal from multiple applications of this feat go into its reserve and can be used to manifest the powers it knows as you desire.
}
