\subsection{Settler}
Settlers are the people who live in cities and towns around Athas. Living in settlements is a quite tame endeavor, so settlers do not have the inclination or training to be adventurers. Settlers can be of any social class: nobles who were born into high position, craftsmen who produce the goods in the world around the adventurers, or slaves who farm the fields and staff the shops.

\begin{itemize*}
\item Nobles are the wealthy or politically influential people in the world. They are given the freedom to train in the fields of their choice, for the most part, and often travel widely. With access to all the best goods and opportunities, many nobles become formidable individuals. Some even go on adventures with fighters, wizards, and members of other classes, although usually such activities are nothing more than a lark.
\item Craftsmen operate as professionals in the world. They normally do not have the inclination or training to be adventurers, but they are capable in their own field. The skilled blacksmith, the astute barrister, the canny merchant, the educated sage, and the master shipwright are all craftsmen.
\item Enslaved farmers and laborers are the basis of the Athasian society. They urge for freedom at any cost they lack the martial training or the skills to survive on their own in the wastes. Laborers are usually owned by craftsmen, and they work in their shops, or building new merchant emporiums. Farmers are usually owned by noble families, and they are the most eager to escape since noble farms are one of the most cruel places on Athas.
\end{itemize*}

\Table{The Settler}{lX *{3}{Z{12mm}}}{
  \tableheader Level
& \tableheader Base Attack Bonus
& \tableheader Fort Save
& \tableheader Ref Save
& \tableheader Will Save\\

1st  & +0     & +0 & +0 & +0 \\
2nd  & +1     & +0 & +0 & +0 \\
3rd  & +1     & +1 & +1 & +1 \\
4th  & +2     & +1 & +1 & +1 \\
5th  & +2     & +1 & +1 & +1 \\
6th  & +3     & +2 & +2 & +2 \\
7th  & +3     & +2 & +2 & +2 \\
8th  & +4     & +2 & +2 & +2 \\
9th  & +4     & +3 & +3 & +3 \\
10th & +5     & +3 & +3 & +3 \\
11th & +5     & +3 & +3 & +3 \\
12th & +6/+1  & +4 & +4 & +4 \\
13th & +6/+1  & +4 & +4 & +4 \\
14th & +7/+2  & +4 & +4 & +4 \\
15th & +7/+2  & +5 & +5 & +5 \\
16th & +8/+3  & +5 & +5 & +5 \\
17th & +8/+3  & +5 & +5 & +5 \\
18th & +9/+4  & +6 & +6 & +6 \\
19th & +9/+4  & +6 & +6 & +6 \\
20th & +10/+5 & +6 & +6 & +6 \\
}

\textbf{Hit Die:} d4.

\subsubsection{Class Skills}
\skill{Craft} (Int), \skill{Diplomacy} (Cha), \skill{Handle Animal} (Cha), and \skill{Profession} (Wis). The settler can choose any two additional skills to be class skill. See \chapref{Skills} for skill descriptions.

\textbf{Skill Points per Level:} 4 + Int. modifier ($\times$4 at 1st level).

\subsubsection{Class Features}
\textbf{Weapon and Armor Proficiency:} The settler is proficient with one simple weapon. They are not proficient with any other weapons, nor are they proficient with any type of armor or shields.


\subsubsection{Starting Gear}
Depends on the social status:
\begin{itemize*}
\item Noble: 5d4 $\times$ 20 cp worth of equipment.
\item Craftsmen: 5d4 $\times$ 6 cp worth of equipment.
\item Slave: 5d4 cp worth of equipment.
\end{itemize*}